### 2019-11-21 draft2.tex
updating

\documentclass{article}
\usepackage{amssymb, amsmath, amsthm, mathtools, bbm, tikz-cd,stmaryrd,enumerate}
%-------------------
\usepackage{fancyhdr}
\pagestyle{fancy}
\fancyhf{}
\fancyhead[L]{\leftmark}
\fancyhead[R]{\thepage}
%----------------
\newcommand{\TT}{{T\oplus T^*}}
\newcommand{\JJ}{\mathcal{J}}
\newcommand{\KK}{\mathcal{K}}
\newcommand{\GG}{\mathcal{G}}
\newcommand{\Cc}{\mathbf{C}}
\newcommand{\RR}{\mathbb{R}}
\newcommand{\XX}{\mathfrak{X}}
\newcommand{\HH}{\mathcal{H}}
\newcommand{\FF}{\mathcal{F}}
\newcommand{\QQ}{\mathcal{Q}}
\newcommand{\cE}{\mathcal{E}}
%----------------------------------------
\newcommand{\PP}{\mathrm{P}}
\newcommand{\PPt}{\tilde{\mathrm{P}}}
\newcommand{\id}{\mathbbm{1}}
\newcommand{\nlr}{\overset{\leftrightarrow}{\n}}
\newcommand{\lc}{\mathring{\n}}
\newcommand{\im}{\mathrm{Im}\,}
\newcommand{\Ker}{\mathrm{Ker}\,}
\newcommand{\Lie}{\mathcal{L}}
\newcommand{\PS}{\mathcal{P}}
\newcommand{\ap}{\alpha}
\newcommand{\bt}{\beta}
\def\w{\wedge}
\newcommand{\p}{\partial}
\newcommand{\pt}{\tilde{\partial}}
\newcommand{\xt}{{\tilde{x}}}
\newcommand{\n}{\nabla}
\newcommand{\rd}{\mathrm{d}}
\newcommand{\PH}{(\PS,\eta,\omega)}
\newcommand{\Lt}{\tl{L}}
\newcommand{\Lb}{\mathbb{L}}
\newcommand{\s}{\mathbf{s}}
\newcommand{\se}{\Gamma}
\newcommand{\Endo}{\text{End}}
\newcommand{\ellt}{{\tl{\ell}}}
\newcommand{\ot}{{1/2}}
\newcommand{\inv}{{-1}}
\newcommand{\Aa}{\mathcal{A}}
\newcommand{\la}{\langle}
\newcommand{\ra}{\rangle}
\newcommand{\lara}{\la\ ,\ \ra}
\newcommand{\brac}{[\ ,\ ]}
\newcommand{\bl}{[\![}
\newcommand{\br}{]\!]}
\newcommand{\bracd}{\bl \ ,\ \br}
\newcommand{\yt}{\tl{y}}
\newcommand{\zt}{\tl{z}}
\newcommand{\tth}{\tl{\theta}}
\newcommand{\kk}{\mathrm{k}}
\newcommand{\Mt}{\tl{M}}
\newcommand{\pd}{\p\!\!\!\p}
%----------------------------------------
\def\gld{generalized Lie derivative }
\def\glds{generalized Lie derivatives }
\def\tl{\tilde}

\def\xto{\xrightarrow}

% These will be typeset in italics
\newtheorem{theorem}{Theorem}[section]
\newtheorem{proposition}[theorem]{Proposition}
\newtheorem{lemma}[theorem]{Lemma}
\newtheorem{corollary}[theorem]{Corollary}
\newtheorem{fact}[theorem]{Fact}
\newtheorem*{theorem*}{Theorem}
\newtheorem*{lemma*}{Lemma}
\newtheorem*{proposition*}{Proposition}
\newtheorem{Rem}[theorem]{Remark}

% These will be typeset in Roman
\theoremstyle{definition}
\newtheorem{Def}[theorem]{Definition}
\newtheorem{Conj}[theorem]{Conjecture}
\newtheorem{remark}[theorem]{Remark}

\newtheorem*{notation*}{Notation}

\theoremstyle{remark}
\newtheorem{Ex}[theorem]{Example}
\newtheorem{question}[theorem]{Question}
\newenvironment{claim}[1]{\par\noindent\underline{Claim:}\space#1}{}
\newenvironment{claimproof}[1]{\par\noindent\underline{Proof:}\space#1}{\hfill $[acksquare$}

\input xy

\xyoption{all}

\DeclareMathOperator{\End}{End}
\DeclareMathOperator{\rk}{rk}

\def\brian{\textcolor{blue}{BM: }\textcolor{blue}}
\def\david{\textcolor{red}{DB: }\textcolor{red}}

\title{Topological Sigma Models for Generalized Para-Complex Geometry}

\begin{document}

\maketitle
\begin{abstract}
We study a class of $2d$ topological sigma models that are formulated on generalized para-complex target manifolds via the AKSZ framework. When the target is additionally generalized para-K\"ahler, these topological theories can be realized as topological twists of $(2,2)$ para-supersymmetric sigma models of Abou-Zeid and Hull. We compare our results to the case of generalized complex and generalized K\"ahler geometry, where similar results have been described in the context of the usual $(2,2)$ SUSY by Kapustin and Li. We present several examples and show that our construction recovers the A-model and the Poisson sigma model as special cases. Moreover, we also introduce new examples of topological theories inherently tied to the para-complex geometry, the para-B-model and a para-complex version of the Landau-Ginzburg model.

\end{abstract}
\newpage
\tableofcontents
\newpage
\section{Introduction}
Since the work of (..) \cite{?} it has been known that on any K\"ahler manifold $(M,I,\omega)$, one can define a $2d$ sigma model admitting a $(2,2)$ supersymmetry (SUSY) and such model has a simple local description in terms of the K\"ahler potential.  Moreover, Witten has shown \cite{?} that such sigma model gives rise to two distinct topological theories -- the A- and B-models -- via a procedure called topological twisting. These topological theories have an important interpretation in terms of their underlying geometry: the A-model only depends on the symplectic structure $(M,\omega)$, while the B-model only depends on the complex structure $(M,I)$. Additionally, there exists an ${\mathbb Z}_2$ automorphism acting on the original $(2,2)$ supersymmetric theory that exchanges its A- and B-models. This is the simplest way one can observe the phenomenon of mirror symmetry in the context of $2d$ sigma models.

The K\"ahler geometry does not describe the most general $(2,2)$ sigma model, as was shown in \cite{Gates-hull-rocek-biherm}. Instead, the most general geometry is described by a bi-Hermitian geometry, defined by a pair of complex structures $I_\pm$ compatible with the same Riemannian metric $g$ and satisfying the compatibility relation
\begin{align*}
\rd^c_\pm\omega_\pm=\pm H \in \Omega^3_{cl.}(M),
\end{align*}
$\omega_\pm$ being the fundamental forms of $I_\pm$ and $\rd^c_\pm$ the associated $\rd^c$-operators. For this geometry, the local description is more complicated than in the K\"ahler case, in particular because the analogue of the K\"ahler potential is much harder to describe. Consequently, the topological twists are also  more complicated.

This problem is nevertheless partially mitigated by an alternative geometric formulation in terms of generalized K\"ahler (GK) geometry, which has been shown in \cite{Gualtieri:2003dx} to be equivalent to the above-described bi-Hermitian geometry $(g,I_\pm,H)$. A GK structure on $M$ is given by the data of two complex endomorphisms $\JJ_\pm$ of the bundle $(\TT)M$:
\begin{align*}
\JJ_\pm \in \End((\TT)M),\quad \JJ_\pm^2=-\id, \quad \la \JJ \cdot,\JJ\cdot \ra= \lara,
\end{align*}
where $\lara$ denotes the natural duality pairing on $(\TT)M$:
\begin{align*}
\la X+\ap,Y+\bt\ra=\ap(Y)+\bt(X),\quad X,Y\in \se(TM),\quad \ap,\bt \in \se(T^*M).
\end{align*}
Additionally, $\JJ_\pm$ are required to commute and their product $\GG\coloneqq -\JJ_+\JJ_-$ to define a

\subsection{Notations and conventions}

\brian{Conventions for odd Lie brackets $[-,-]$ and $\{-,-\}$.}

\section{Background on paracomplex and generalized geometry}
\david{would just put the introduction of paracomplex geometry (minus the generalized part) in appendix, we did that even in the other paper which is literally a differential geometry paper}

\subsection{Paracomplex geometry}

In this section we introduce para-complex geometry with emphasis on the analogy with complex geometry. More details can be found in \cite{Hu:2019zro} or \cite[Ch.~15]{Cortes:2010ykx}, for example. \brian{I think you should cite your work here too.}

\begin{Def}\label{def:paracpx}
An (almost) {\bf product structure} on a smooth manifold $\PS$ is an endomorphism $K\in \Endo(T\PS)$ which squares to the identity, $K^2=\id_{T\PS}$, $K\neq \id$. An (almost) \textbf{para-complex structure} is a product structure such that the $+1$ and $-1$ eigenbundles of $K$ have the same rank.
\end{Def}
A direct consequence of above definition is that any para-complex manifold is of even dimension. From now on, the $+1$ and $-1$ eigenbundles of an almost product/para-complex structure will be denoted $L$ and $\Lt$, respectively.

\paragraph{Integrability} The use of the word {\it almost} as usual refers to integrability of the endomorphism, i.e. whether its eigenbundles are involutive with respect to the Lie bracket and therefore define a foliation of the underlying manifold. Similarly to the complex case, the integrability is governed by the \textbf{Nijenhuis tensor}
\begin{align}\label{eq:nijenhuis}
\begin{aligned}
N_K(X,Y)&=[X,Y]+[KX,KY]-K([KX,Y]+[X,KY])\\
&=(\n_{KX}K)Y+(\n_XK)KY-(\n_{KY}K)X-(\n_YK)KX\\
&=4(\PP[\PPt X,\PPt Y]+\PPt[\PP X,\PP Y]),
\end{aligned}
\end{align}
where $\n$ is any torsionless connection and $\PP\coloneqq\frac{1}{2}(\id+K)$ and $\PPt\coloneqq\frac{1}{2}(\id-K)$ are the projections onto $L$ and $\Lt$, respectively. We say $K$ is integrable and call $K$ a product/para-complex manifold if $N_K=0$. From \eqref{eq:nijenhuis} it is apparent that $K$ is integrable if and only if {\it both} eigenbundles are simultaneously Frobenius integrable, i.e. involutive distributions in $T\PS$. This is one of the main differences between complex and para-complex geometry; one of the eigenbundles can be integrable while the other is not. In such cases, we call $\PS$ {\bf half-integrabile}. For more details, see for example \cite{??,??}.

\paragraph{Type decomposition} The splitting of the tangent bundle $T\PS=L\oplus \Lt$ gives rise to a decomposition of tensors analogous to the $(p,q)$-decomposition in complex geometry. For differential forms, we denote the decomposition as
\begin{align}\label{eq_plusminus_decomp}
\Lambda^k (T^*\mathcal{P})&=\bigoplus_{k=m+n}\Lambda^{(m,n)}(T^*\mathcal{P}),
\end{align}
where $\Lambda^{(m,n)}(T^*\mathcal{P})=\Lambda^m(T^{*}_{1,0})\otimes \Lambda^n(T^{*}_{0,1})$ and the corresponding sections are denoted by $\Omega^{(m,n)}(\mathcal{P})$. The bigradings \eqref{eq_plusminus_decomp} yield the natural projections
\begin{align*}
\Pi^{(p,q)}:\Lambda^k(T^*\mathcal{P})&\rightarrow \Lambda^{(p,q)}(T^*\mathcal{P}),
\end{align*}
so that when $K$ is integrable, the de-Rham differential splits as $\rd=\p+\tl{\p}$, where
\begin{align*}
\begin{array}{cc}
\p \coloneqq \Pi^{(p+1,q)}\circ \rd, & \tl{\p} \coloneqq \Pi^{(p,q+1)}\circ \rd,
\end{array}
\end{align*}
are the \textbf{para-complex Dolbeault operators}, satisfying
\begin{align*}
\p^2=\tl{\p}^2=\p\tl{\p}+\tl{\p}\p=0.
\end{align*}

One can also introduce the {\it twisted differential $\rd^p\coloneqq(\Lambda^{k+1}K^*)\circ\rd\circ (\Lambda^kK^*)$}. When $K$ is integrable, it can be simply written as $\rd^p=(\p_++\p_-)$ on real forms and $\rd^p=\kk (\p+\bar{\p})$ on para-complex forms.

\paragraph{Para-Holomorphic structure}
Let now $(\mathcal{P},K)$ be an almost para-complex manifold of dimension $2n$. If $K$ is integrable, we get a set of $2n$ coordinates $(x^i,\tilde{x}_i)$ called {\bf adapted coordinates}, $\mathcal{P}$ locally splits as $M\times \tilde{M}$, and $K$ acts as identity on $TM=L$ and negative identity on $T\tilde{M}=\tilde{L}$. The adapted coordinates therefore define two complimentary foliations that we will call {\bf canonical foliations} of the para-complex manifold $\PS$ and denote $M$ and $\Mt$. Both $M$ and $\Mt$ are therefore $n$-dimensional manifolds composed of connected components called leafs $M_i$, $\Mt_i$:
\begin{align*}
M=\bigcup_i M_i,\quad \Mt=\bigcup_i \Mt_i,
\end{align*}
and each are as sets equal to $\PS$.

As usual, a map of para-complex manifolds is called para-holomorphic if its pushforward commutes with the respective para-complex structures
\begin{Def}
Let $(M,K_M)$ and $(N,K_N)$ be para-complex manifolds. A map $F:M\rightarrow N$ is called para-holomorphic if
\begin{align}\label{eq:def_parahol}
K_N\circ F_*=F_*\circ K_M
\end{align}
\end{Def}
\begin{remark}
In the following we will omit the prefix ``para-'' in para-holomorphic whenever no confusion with complex holomorphicity is possible.
\end{remark}

Locally, the map $F:M\rightarrow N$ of para-complex manifolds can be understood via composition of coordinates as a
\begin{align*}
F&: \RR^{2n}\rightarrow \RR^{2m}\\
F=(f^i,\tl{f}_j)&=(y^i(x^k,\xt_l),\yt_j(x^k,\xt_l))^{i,j=1,\cdots,m}_{k,l=1,\cdots, n}, 
\end{align*}
where $(x^k,\xt_l)$ and $(y^i,\yt_j)$ are adapted local coordinates on $M$ and $N$, respectively. It is easy to check from \eqref{eq:def_parahol} that $F$ is a holomorphic map iff the components satisfy
\begin{align}\label{eq:holomorphic_real}
\frac{\p}{\p \xt_i}f^j=\frac{\p}{\p x^i}\tl{f}_j=0.
\end{align}

The conditions \eqref{eq:holomorphic_real} tell us that the holomorphic functions map the canonical foliations of the para-complex manifolds $M$ and $N$. This also means that the transition functions on a para-complex manifold (seen as maps $\RR^{2n}\rightarrow \RR^{2m}$) are holomorphic since the foliations must be preserved, i.e. the coordinates transform as
\begin{align}\label{para-coordinate-transf}
(x^i,\xt_i)\mapsto (y^j(x^i),\yt_j(\xt_i)).
\end{align}

This also gives us an intuition into what holomorphic bundles and their holomorphic sections look like. First, we notice that the tangent bundle $T\PS$ itself is a holomorphic bundle (see for example \cite{Cortes:2003zd,Hu:2019zro}); this is simply because of the form of the transition functions \eqref{para-coordinate-transf} that induce a holomorphic structure on the tangent bundle. The holomorphic sections of $T\PS$ -- the holomorphic vector fields -- are locally of the form
\begin{align*}
X= X^i(x)\p_i+\tl{X}_i(\xt)\pt^i,
\end{align*}
i.e. the components in $L$ and $\Lt$ individually define vector fields on the foliations $M$ and $\Mt$, respectively.

Similarly, the cotangent bundle is a holomorphic bundle. For the higher wedge powers, we find that only $\Lambda^{(k,0)+(0,k)}(T^*\PS)$, $1\leq k\leq n$, are holomorphic bundles. The {\bf para-complex Dolbeault complex} is therefore given by
\begin{align}
\left(\Omega^{(\bullet,0)}\otimes\Omega^{(0,\bullet)},(\p,\pt)\right)\coloneqq \left(\mathbf{\Omega}^{\bullet,0},\pd\right).
\end{align}
%\begin{lemma}
%Let $(\PS,K)$ be a paracomplex manifold. Then $\rd^p\coloneqq(\Lambda^{k+1}K)\circ\rd\circ (\Lambda^kK)$ can be expressed as
%\begin{align}\label{eq:dp-operator}
%\rd^p=\p_+-\p_-.
%\end{align}
%\end{lemma}
%\begin{proof}
%Let $\ap \in \Omega^{+m,-n}(\PS)$. Then we have
%\begin{align*}
%\rd^p\ap=(-1)^n(\Lambda^kK)\rd\ap=(-1)^{2n}\p_+ \ap +(-1)^{2n+1}\p_-\ap=(\p_+-\p_-)\ap,
%\end{align*}
%\end{proof}

\subsection{Generalized para-geometry}
In this paper, the term {\it generalized geometry} is used for the study of geometric \brian{geometrical is not a word} structures on the bundle $TM \oplus T^*M$ over some manifold $M$. We will typically abbreviate this bundle to $\TT$ whenever the base is understood or unimportant for the discussion.

\subsubsection{The exact Courant algebroid structure}
\brian{David, how do you feel about moving this later in the Courant/AKSZ section?}
We recall basic facts about Courant algebroids in Section \ref{sec: courant}. 
For now, we record a relationship between generalized paracomplex structures and exact Courant algebroids.

The bundle $\TT$ has a natural Courant algebroid structure given by the symmetric pairing
\begin{align*}
\langle X+\ap,Y+\bt\rangle=\ap(Y)+\bt(Y),
\end{align*}
the Dorfman bracket,
\begin{align}\label{eq:dorfman}
[ X+\ap,Y+\bt]=[X,Y]+\Lie_X\bt-\imath_Y\rd \ap, 
\end{align}
and the anchor $\pi:X+\ap\mapsto X$. In the above, $X+\ap$ denotes a section of $\TT$ with the splitting to tangent and cotangent parts given explicitly. The Dorfman bracket can be thought of as an extension of the Lie bracket from $T$ to $\TT$ and therefore we opt to use the same notation for both brackets; the expression $[X,Y]$ is always the Lie bracket of vector fields whether we think of $\brac$ as the Lie bracket or the Dorfman bracket and no confusion is therefore possible.

The Courant algebroid on $\TT$ is exact, meaning that the associated sequence
\begin{align}\label{eq:exact_seq}
0\longrightarrow T^* \overset{\pi^T}{\longrightarrow} \TT\overset{\pi}{\longrightarrow} T\longrightarrow 0,
\end{align}
is exact. Here, $\pi^T$ is the transpose of $\pi$ with respect to the pairing $\lara$,
%\begin{align*}
%\la \pi^T(\ap),Y+\bt\ra=\la \ap,\pi(Y+\bt)\ra=\la \ap,Y\ra
%\end{align*}
i.e. $\pi^T: \ap \mapsto \ap+0$. In fact, all possible Courant algebroid structures on $\TT$ are parametrized by a closed three-form $H\in \Omega^3_{cl}$, which enters the definition of the bracket \eqref{eq:dorfman}, changing it to a {\it twisted} Dorfman bracket
\begin{align*}
[ X+\ap,Y+\bt]_H=[X,Y]+\Lie_X\bt-\imath_Y\rd \ap+\imath_Y\imath_X H.
\end{align*}
Moreover, any isotropic splitting of \eqref{eq:exact_seq} $s:T\rightarrow \TT$ is given by a two-form $b$, such that $X\overset{s}{\mapsto}X+b(X)$. This is equivalent to an action of a $b$-field transformation on $\TT$\footnote{Here we are using the term $b$-field transformation more liberally as it is customary to use the term only in the cases when $\rd b=0$ so that $e^b$ is a symmetry of $\brac$.}
\begin{align*}
e^b=
\begin{pmatrix}
\id & 0 \\
b & \id
\end{pmatrix}
\in \End(\TT),
\end{align*}
which consequently changes the bracket as
\begin{align*}
[ e^b(X+\ap),e^b(Y+\bt)]_H=e^b([ X+\ap,Y+\bt]_{H+\rd b}),
\end{align*}
which implies that when $H$ is trivial in cohomology, then a choice of a $b$-field transformation such that $\rd b=-H$ brings the twisted bracket $\brac_H$ into the standard form \eqref{eq:dorfman}. When $H$ is cohomologically non-trivial this can be done at least locally. This also means that any choice of splitting with a non-trivial $b$-field can be absorbed in the Courant algebroid bracket in terms of the {\it flux}\footnote{Flux is a term used mainly in physics, in this context simply meaning the ``tensorial contribution to the bracket''.} $\rd b$.

\paragraph{Dirac Structures}
An important object in Dirac geometry are (almost) dirac structures, which are subbundles $L\subset \TT$ with special properties.
\begin{Def}
An {\bf almost Dirac structure} $L$ is a maximally isotropic subbundle of $\TT$, i.e. $\la u,v\ra=0$ for any $u,v \in \se(L)$ and $\text{rank}(L)=\text{rank}(T)$. When $L$ is involutive under the Dorfman bracket, i.e. it satisfies $[L,L]\subset L$, we call $L$ simply a {\bf Dirac structure}.
\end{Def}
An important fact we will repeatedly use is the following:

\begin{proposition}[\cite{courant1990dirac}]\label{prop:dirac_Liealg}
Let $L$ be a Dirac structure in the Courant algebroid $\TT$ with a flux $H$. Then the restriction of the Dorfman bracket to $L$, $\brac\mid_L$ is skew and gives $L$ a structure of a Lie algebroid compatible with the anchor $\pi\mid_L$, a restriction of the projection $\pi:\TT\rightarrow T$ to $L$.
\end{proposition}

We remark here that all the results in this paper remain valid for any exact courant algebroid $E$ (i.e. $E$ fits in the sequence \eqref{eq:exact_seq}), which can be always identified with $\TT$ by the choice of splitting equivalent to a choice of a representative $H\in\Omega^3_{cl}$. This also amounts to setting $b=0$ in all formulas since the $b$-field appears as a difference of two splittings.

\subsection{Generalized para-K\"ahler geometry}
\brian{I don't think this should be the title of this section. It's mostly about paracomplex geometry}

We now recall the notion of a generalized para-complex \cite{wade2004dirac,Zabzine:2006uz,Hu:2019zro} and a generalized para-K\"ahler \cite{Hu:2019zro} structure. We follow the discussion presented in \cite{Hu:2019zro}.

\begin{Def}
A \textbf{(twisted) generalized para-complex} (GpC) structure $\KK$ is an endomorphism of $\TT$, such that $\KK^2=\id$ and $\la\KK,\KK\ra=-\lara$, whose generalized Nijenhuis tensor vanishes:
\begin{align}\label{eq:gen_nijenhuis}
\mathcal{N}_\KK(u,v)=[\KK u,\KK v]_H+\KK^2[ u,v]_H-\KK([\KK u,v]_H+[ u,\KK v]_H)=0.
\end{align}
\end{Def}
It is easy to check that the condition \eqref{eq:gen_nijenhuis} is equivalent to the $\pm 1$ eigenbundles of $\KK$ to be involutive under the twisted Dorfman bracket. Since in this paper the flux $H$ will be generically non-zero but all results hold for the special case $H=0$ as well, we will drop the word ``twisted" from our definitions.

Generalized para-complex structures can be understood as the data one needs to specify a splitting of $\TT$ to a pair of integrable Dirac structures:

\begin{theorem*}[\cite{wade2004dirac}]\label{thm:pairofdirac}
There is a one-to-one correspondence between generalized para-complex structures on $M$ and pairs of transversal Dirac subbundles of $\TT$.
\end{theorem*}

Combining this result with the well-known result of \cite{Liu:1995lsa} which states that any pair of transversal Dirac structures $(L,\Lt)$ forms a Lie bialgebroid $(L,L^*\simeq \Lt)$, one can immediately infer the following

\begin{corollary}
Generalized para-complex structures on $\TT$ are in one-to-one correspondence with Lie bialgebroid pairs $(L,L^*)$ such that $L\oplus L^*=\TT$. 
\end{corollary}

\begin{Ex}[The trivial structure and its deformations]\label{ex:GpC_trivial}
Any manifold supports the following GpC structure
\begin{align*}
\KK_0=
\begin{pmatrix}
\id & 0 \\
0 & -\id
\end{pmatrix},
\end{align*}
that has eigenbundles $T$ and $T^*$ and is always integrable. The following two GpC structures can be seen as deformations of $\KK_0$ by either a two-form $b$ or a bi-vector $\beta$:
\begin{align*}
\KK_b=
\begin{pmatrix}
\id & 0 \\
2b & -\id
\end{pmatrix},\quad
\KK_\beta=
\begin{pmatrix}
\id & 2\beta \\
0 & -\id
\end{pmatrix}.
\end{align*}
$\KK_b$ is integrable iff $\rd b =-H$, and its eigenbundles are $\Lb_b=\text{graph}(b)=\{X+b(X)\mid X \in \XX\}$ and $\widetilde{\Lb}=T^*$. Similarly, $\KK_\beta$ is integrable iff $\beta$ is a Poisson structure, (see \cite[Lemma~2.13]{Hu:2019zro}) and its eigenbundles are $\Lb=T$ and $\widetilde{\Lb}=\text{graph}(-\beta)=\{\ap-\beta(\ap)\}\mid \ap \in \Omega\}$.
\end{Ex}

\begin{Ex}[Para-complex structures]
A para-complex structure $K\in \Endo(T)$, defines the diagonal generalized para-complex structure:
\begin{align*}
\KK_K=
\begin{pmatrix}
K & 0 \\
0 & -K^*
\end{pmatrix}.
\end{align*}
The corresponding Dirac structures are given by $\Lb=T^{(1,0)}\oplus T^{*(0,1)}$ and $\widetilde{\Lb}=T^{(0,1)}\oplus T^{*(1,0)}$, where the bigrading is with respect to $K$. The integrability of $\KK_K$ is equivalent to Frobenius integrability of $K$ , i.e. vanishing of the Nijenhuis tensor of $K$.
%
%The structure $\KK_P$ can be generalized to the following
%\begin{align*}
%\KK=
%\begin{pmatrix}
%P & \Pi \\
%\Omega & -P^*
%\end{pmatrix},
%\end{align*}
%where we can read off from the constraints in \eqref{eq:GpC_generalform} that $P^2=\id$ implies that $\Pi\Omega=0$ and both $\Pi$ and $\Omega$ have to be of type $(2,0)+(0,2)$ with respect to the grading given by $P$.

\end{Ex}

\begin{Ex}[Symplectic structures]\label{ex:GpC_sympl}
A symplectic form $\omega$ defines the anti-diagonal GpC structure
\begin{align*}
\KK_\omega=
\begin{pmatrix}
0 & \omega^{-1} \\
\omega & 0
\end{pmatrix}.
\end{align*}
The $\pm 1$ eigenbundles are given by $\text{graph}(\pm\omega)=\{X\pm\omega(X)\mid X\in \XX\}$, and the integrability of $\KK_\omega$ is equivalent to $\rd\omega=0$.
\end{Ex}

\brian{Can we import some of the other examples here?
Maybe some explicit ones like the toric fibrations you mentioned.}

\paragraph{Comparision with generalized complex structures}
Example \ref{ex:GpC_sympl} shows that a symplectic manifold $(M,\omega)$ is a GpC manifold and it is well-known \cite{Gualtieri:2003dx} that $(M,\omega)$ is also generalized complex (GC). However, while almost GC structures exist only on almost complex manifolds \cite{Gualtieri:2003dx}, Example \ref{ex:GpC_trivial} demonstrates that GpC structures exist on any Poisson manifold and in particular on any smooth manifold (with trivial Poisson structure). Another feature of GpC geometry that is not present in GC geometry is that the GpC structures can be half-integrable (similarly to ordinary para-complex structures): see the cases of $\KK_b$ and $\KK_\beta$ from Example \ref{ex:GpC_trivial} which are always at least half integrable and are fully integrable iff $b$ is closed and $\beta$ is Poisson, respectively. On the other hand, $\KK_\omega$ in Example \ref{ex:GpC_sympl} can only be half-integrable when the $H$-flux is non-zero.

\begin{Def}
A \textbf{generalized para-K\"ahler structure} (GpK) is a commuting pair $(\KK_+,\KK_-)$ of GpC structures, such that their product $\GG=\KK_+\KK_-$ defines a split-signature metric $G$ on $\TT$ via
\begin{align*}
G(\cdot,\cdot)\coloneqq \la \GG\cdot,\cdot\ra.
\end{align*}
\end{Def}

Because $\KK_\pm$ are GpC structures, they induce the splitting $\TT= \Lb_\pm\oplus\widetilde{\Lb}_\pm$. Moreover, because they commute, each of $\Lb_+$ and $\widetilde{\Lb}_+$ further splits to eigenbundles of $\KK_-$, so that one arrives at the decomposition of $\TT$ into four bundles:
\begin{align}\label{GpK_bundles}
\TT=\ell_+\oplus\ell_-\oplus \ellt_+\oplus \ellt_-,
\end{align}
such that the eigenbundles of $\KK_+$ are $\Lb_+=\ell_+\oplus\ell_-$ and $\tl{\Lb}_+=\ellt_+\oplus \ellt_-$, the eigenbundles of $\KK_-$ are $\Lb_-=\ell_+\oplus\ellt_-$ and $\tl{\Lb}_-=\ell_-\oplus \ellt_+$ and the eigenbundles of the generalized metric are $C_\pm=\ell_\pm\oplus\ellt_\pm$. All $\ell_\pm$ and $\ellt_\pm$ are isotropic and integrable under the Dorfman bracket \cite{Hu:2019zro} and bundles with opposite chirality are orthogonal.

Similarly to generalized K\"ahler structures, the GpK structures can be equivalently given in terms of a pair of para-Hermitian structures satisfying a particular integrability condition:
\begin{theorem}[\cite{Hu:2019zro}]
The data of a GpK structure is equivalent to a pair of para-Hermitian structures $(\eta,K_+,K_-)$, such that $\KK_\pm$ are given by
\begin{align}\label{eq:GpK_genform}
\KK_{\pm}=\frac{1}{2}
\begin{pmatrix}
\id & 0 \\
b & \id
\end{pmatrix}
\begin{pmatrix}
K_+\pm K_- & \omega^{-1}_+\mp \omega^{-1}_- \\
\omega_+\mp \omega_- & -(K_+^*\pm K_-^*)
\end{pmatrix}
\begin{pmatrix}
\id & 0 \\
-b & \id
\end{pmatrix},
\end{align}
for some $2$-form $b$. The integrability of $\KK_\pm$ then translates into $K_\pm$ being integrable and satisfying
\begin{align*}
\n^\pm K_\pm=0,
\end{align*}
where the connections $\n^\pm$ are defined by the Levi-Civita connection $\lc$ of $\eta$ and the $H$-flux:
\begin{align*}
\eta(\n^\pm_XY,Z)=\eta(\lc_XY,Z)\pm\frac{1}{2}(H+\rd b).
\end{align*}
\end{theorem}

The additional integrability condition on $K_\pm$, $\n^\pm K_\pm$, can be equivalently expressed using the fundamental forms associated to $K_\pm$, $\omega_\pm=\eta K_\pm$, and a para-complex version of the $\rd^c$-operator, which we call $\rd^p$:
\begin{align*}
\n^\pm K_\pm=0 \Longleftrightarrow \rd^p_\pm\omega_\pm=\pm (H+\rd b).
\end{align*}
$\rd^p_\pm$ here denote the $\rd^p$ operators associated to $K_\pm$, $\rd^p_\pm\coloneqq K_\pm^*\circ \rd\circ K_\pm^*$. We will call the geometry given by the data $(\eta, K_\pm, H+\rd b)$ above a {\bf bi-para-Hermitian} geometry.

\subsubsection{Isomorphism between $\TT$ and $T\oplus T$}\label{sec:isomorphism}
In both the GK and GpK cases, the product of the pair of G(p)C structures defines a generalized (indefinite) metric $\GG$, which means that
\begin{align*}
G(\cdot,\cdot)\coloneqq \la \GG\cdot,\cdot\ra,
\end{align*}
defines a genuine (indefinite) metric on the bundle $\TT$. It can be shown (see eg. \cite{Gualtieri:2003dx,Hu:2019zro}) that such metric can be always locally expressed in terms of a two-form $b$ and a metric $g$
\begin{align*}
\GG=\GG(g,b)=\begin{pmatrix}
\id & 0 \\
b & \id
\end{pmatrix}
\begin{pmatrix}
0 & g^{-1} \\
g & 0
\end{pmatrix}
\begin{pmatrix}
\id & 0 \\
-b & \id
\end{pmatrix},
\end{align*}
and the signature of $g$ then determines the signature of $\GG(g,b)$. Therefore, a generalized metric determines a splitting of $\TT\simeq e^b(T)\oplus T^*$ in which the eigenbundles $C_\pm$ of $\GG$ are $C_\pm=graph(\pm g)$ and the flux of this splitting is given by the closed three-form $H\overset{loc.}{=}\rd b$. In the usual splitting $\TT$, we then have $C_\pm=graph(b\pm g)$.

\begin{remark}
The most general $2D$ $(1,1)$ sigma model on a pseudo-Riemannian target $(M,g)$ is locally given by the action functional
\begin{align}\label{rem:sigmamodel}
S_{(1,1)}(\Phi)&=\int_{\hat{\Sigma}}[g(\Phi)+b(\Phi)]_{ij}D_+\Phi^iD_-\Phi^j,
\end{align}
where $\rd b=H$ is a global closed three-form. Therefore, the data of a generalized metric $\GG$ is equivalent to a specification of the sigma model  \eqref{rem:sigmamodel}.
\end{remark}

An important property of the generalized metric $\GG$ is that its  eigenbundles $C_\pm$ are isomorphic to the tangent bundle $T$ via the projection:
\begin{align}\label{pi_iso}
\begin{aligned}
\pi_\pm:C_\pm &\simeq T,\\
X+\ap &\overset{\pi_\pm}{\longmapsto} X,\\
X+(b\pm g)X &\overset{\pi^{-1}_\pm}{\longmapsfrom} X,
\end{aligned}
\end{align}
where $g$ and $b$ are the defining data of $\GG$. Therefore, since $\TT=C\oplus C_-$, we also have $\TT\simeq T\oplus T$:
\begin{align}
\begin{aligned}
(X_+,X_-)\overset{\pi^{-1}_+\oplus \pi^{-1}_-}{\longmapsto}& X_++(b+g)X_++X_-+(b-g)X_-\\
&=
\begin{pmatrix}
 X_++X_- \\
 g(X_+-X_-)+b(X_++X_-)
\end{pmatrix}.
\end{aligned}\label{map_pi_pm}
\end{align}
In particular, one can check that $\pi_+\oplus \pi_-$ maps the eigenbundles of the generalized structures $\KK_\pm$ ($\JJ_\pm$) to eigenbundles of the corresponding pair of tangent bundle endomorphisms $\KK_\pm$ ($\JJ_\pm$). This is because of the following relationship \cite{Hu:2019zro},
\begin{align*}
K_+=\pi_+\KK_\pm\pi_+^{-1},\quad K_-=\pm\pi_-\KK_\pm\pi_-^{-1},
\end{align*}
and analogously for $\JJ_\pm$ and $J_\pm$. From here, it is easy to see that the $+1$ eigenbundle of $\KK_+$ $\Lb_+$, for example, is given by
\begin{align*}
\Lb_+=\pi_+^{-1}(T^{(1,0)_+})\oplus\pi_-^{-1}(T^{(1,0)_-}),
\end{align*}
where $T^{(1,0)_\pm}$ denotes the $+1$ eigenbundle of $K_\pm$. Analogously, the $-1$ eigenbundle of $\KK_-$,
$\widetilde{\Lb}_-$, is given by
\begin{align*}
\widetilde{\Lb}_-=\pi_+^{-1}(T^{(0,1)_+})\oplus\pi_-^{-1}(T^{(1,0)_-}),
\end{align*}
and so on. Therefore, one should think about the pair $K_\pm$ corresponding to the GpK structure as each of the $K_\pm$ acting on its own copy of $T$, which are then mapped via $\pi_\pm$ to $C_\pm$ in $\TT$.

We will also notice that $\pi_\pm$ map the the pseudo-Riemannian structures $G$ and $g$ on each other:
\begin{align}\label{pi:gG_relationship}
g(X,Y)=\pm\frac{1}{2}\la \pi_\pm^{-1}X,\pi_\pm^{-1}Y\ra = \frac{1}{2}\la \GG \pi_\pm^{-1}X,\pi_\pm^{-1}Y\ra =\frac{1}{2}G(\pi_\pm^{-1}X,\pi_\pm^{-1}Y).
\end{align}
Another important property we will make use of is the fact that the connections $\n^\pm$ give rise via $\pi_\pm$ to a generalized connection $D$ on $\TT$ called the generalized Bismut connection \cite{Gualtieri:2007bq}:
\begin{align}\label{genBismut_pi_nabla_pm}
D_uv=\pi^{-1}_+\n^+_{\pi u}\pi_+ v_++\pi^{-1}_-\n^-_{\pi u}\pi_- v_-.
\end{align}
This connection preserves $\lara$ and $\GG$ and in the case when $\GG$ is a generalized metric corresponding to a GpK structure, $D$ also preserves all the eigenbundles in \eqref{GpK_bundles}.

There is a tensorial quantity associated to any generalized connection called generalized torsion, which is defined as \cite{Gualtieri:2007bq}
\begin{align}\label{gentorsion_def}
T^D(u,v,w)=\la D_uv-D_vu-[u,v]_H,w\ra +\la D_wu,v\ra.
\end{align}
For the generalized Bismut connection, this torsion has only pure components in $\Lambda^3C_\pm$ and satisfies the following formula \cite[Prop.~2.29]{Hu:2019zro}:
\begin{align}\label{gentorsion_H}
T^D(\pi_\pm^{-1}X,\pi_\pm^{-1}Y,\pi_\pm^{-1}Z)=2H_b(X,Y,Z).
\end{align}

%\paragraph*{Relationship to Kapustin-Li}
%On pg. 12 of Kapustin-Li paper they implicitly use the isomorphisms $\pi_\pm$ to map the sections $\chi \in \se(T^{(0,1)_+})$ and $\lambda \in \se(T^{(0,1)_-})$ to the $-i$ eigenbundle of $\JJ_+$ as 
%\begin{align*}
%\begin{pmatrix}
%\chi+\lambda \\
%g(\chi-\lambda)
%\end{pmatrix},
%\end{align*}
%which is the same as \eqref{map_pi_pm} with $b=0$, which they implicitly absorb inside the $H$-flux.

\subsubsection{SKT Geometry and half generalized structures}
\david{will see if we'll be using this}
An {\bf SKT} structure is a Hermitian structure $(I,g)$ for which the fundamental form $\omega$ even though is not closed, is $\rd \rd^c$-closed, i.e. $\rd \rd^c \omega=0$. The version of this geometry is easily formulated for the para- case where we will call it para-SKT. It follows directly from the definition that the bi-para-Hermitian geometry consists of two such structures -- one for each chirality -- and here we will describe how one SKT structure can be described using the language of generalized geometry.

For this purpose we define a positive-chirality\footnote{Similarly one could define a negative-chirality half G(p)C structure by changing $C_+$ for $C_-$} {\bf half generalized almost (para-)complex structure} as a pair $(\GG,\JJ_{C_+})$, where $\GG$ is a (neutral) generalized metric which induces a splitting $\TT=C_+\oplus C_-$ and an isomorphism $C_+\oplus C_-\simeq T\oplus T$, and $\JJ_{C_+}$ is a (para-)complex endomorphism of $C_+$, i.e.
\begin{align*}
\JJ_{C_+}\in \End(C_+),\quad \JJ_{C_+}=\pm \id_{C_+},\quad \la \JJ_{C_+} u_+,v_+\ra=-\la u_+,\JJ_{C_+} v_+\ra,
\end{align*}
for any $u_+,v_+ \in \se(C_+)$. The integrability condition on $\JJ_{C_+}$ is then that its eigenbundles $\ell_+\oplus \ell_-=C_+$ (in the complex case $\ell\oplus \bar{\ell}=C_+\otimes \mathbb{C}$) are involutive with respect to the (twisted) Dorfman bracket. It is easy to see that $\JJ_{C_+}$ defines a (para-)Hermitian structure $(J_+,g)$, where
\begin{align*}
g(X,Y)=\frac{1}{2}\la \pi_+^{-1}X,\pi_+^{-1}Y\ra,\quad J_+=\pi_+\JJ_{C_+}\pi^{-1}_+
\end{align*}
and the integrability condition on $\JJ_{C_+}$ translates into the condition
\begin{align*}
\n^+J_+=0,\ \n^+=\lc+\frac{1}{2}g^{-1}(H+\rd b) \Longleftrightarrow \rd^{c/p}\omega_+=H+\rd b,
\end{align*}
i.e. giving exactly half of the data of a G(p)K geometry. If there is a negative-chirality half structure $\JJ_{C_-}$, then $(\GG,\JJ\coloneqq \JJ_{C_+}\oplus \JJ_{C_-})$ defines a genuine G(p)K structure.

\section{Two-dimensional parasupersymmetry}  \label{sec: parasusy}

In this section we introduce the parasupersymmetry algebra in two-dimensions. 
\brian{add more}

\subsection{A reminder on $(1,1)$ supersymmetry}

The $2$-dimensional $(1,1)$ supertranslation algebra is the super Lie algebra
\[
\mathfrak{t}_{(1,1)} = \RR^{1,1} \oplus \Pi (S_+) \oplus \Pi(S_-)
\]
where $S_\pm \cong \RR$ are the semi-spin representations of ${\rm Spin}(1,1)$ labeled by helicities $\pm \frac{1}{2}$. 
Note that there are natural ${\rm Spin}(1,1)$-equivariant maps
\[
\Gamma_{\pm} : {\rm Sym}^2(S_\pm) \to \RR^{1,1}
\]
which are non-degenerate and whose images hit the subalgebras spanned by $\partial_{\pm}$, respectively. 
The only nonvanishing Lie brackets in $\mathfrak{t}_{(1,1)}$ are defined by
\[
[Q_+, Q_+'] = \Gamma_+(Q_+ \otimes Q_+') \;\; , \;\; [Q_-, Q_-'] = \Gamma_-(Q_- \otimes Q_-')
\]  
where $Q_\pm, Q_\pm'$ are generic elements in $S_\pm$.

We will use the lightcone basis $\p_{\pm}$ for $\RR^{1,1}$ and we also fix a basis $Q_\pm^1$ for $S_{\pm}$ with a relative normalization so that
\begin{align}\label{eq:(1,1)_susy}
[Q^1_\pm,Q^1_\pm] = 2\p_\pm.
\end{align}

\subsubsection{The $(1,1)$ supersymmetric $\sigma$-model}

Let $\Sigma^{2|2}$ be a super Riemann surface with two real odd directions. 
The even part of this supermanifold is a Riemann surface (with coordinates $\sigma$, $\tau$).
For instance, in the flat case we consider the superspace $\RR^{2|2} = \{(x^i , \theta_1^{\pm}) \; | \; i = 1,2\}$, where $\theta_1^{\pm}$ are odd variables.

The most general $(1,1)$ supersymmetric sigma model into a target pseudo-Riemannian manifold $(M,g)$ is given by the action functional
\begin{align}\label{eq:(1,1)action}
S_{(1,1)}(\Phi)=\int_{\Sigma^{2|2}} [g(\Phi)+b(\Phi)]_{ij}D^1_+\Phi^iD^1_-\Phi^j,
\end{align}
where $\Phi=(\Phi^i)_{i=1\cdots n}$ are local representatives for the $(1,1)$ {superfields} which are maps $\Phi: \Sigma^{2|2} \rightarrow M$.
In the action, $b$ denotes a local two-form potential for a closed three-form, $H=\rd b$, and $D_\pm$ are the superderivatives
\begin{align}\label{eq:D1}
D^1_\pm=\frac{\p}{\p \theta_1^\pm}-\theta_1^\pm \p_\pm,
\end{align}
where $\p_\pm=\frac{\p}{\p x_\pm}$ are derivatives along the lightcone coordinates on $\Sigma$, $x_\pm=\tau\pm\sigma$.

In superworldsheet coordinates, the superfields decompose as
\begin{align*}
\Phi^i(\sigma,\tau,\theta_+,\theta_-)=\phi^i(\sigma,\tau)+\psi^i_+(\sigma,\tau)\theta^++\psi_-(\sigma,\tau)\theta^-+F^i(\sigma,\tau)\theta^+\theta^-.
\end{align*}
Here, $(\phi^i)$ are local representatives for a smooth map $\phi: \Sigma \rightarrow M$.

The fact that this action carries $(1,1)$ supersymmetry means that the action \eqref{eq:(1,1)action} is invariant under transformations generated by the two {supercharges} $Q^1_\pm$, 
\begin{align}\label{eq:Q1}
Q^1_\pm=\frac{\p}{\p \theta_1^\pm}+\theta_1^\pm \p_\pm,
\end{align}
obeying the supercommutation relations of the $(1,1)$ supersymmetry algebra (\ref{eq:(1,1)_susy}).

\subsection{$(2,2)$ parasupersymmetry}

\brian{point to references who have also discussed versions of (2,2) para susy}
The {\bf (2,2) parasupersymmetry algebra} has the underlying supervector space
\[
\mathfrak{t}_{(2,2)} = \RR^{1,1} \oplus \Pi(S_+ \oplus S_+) \oplus \Pi(S_- \oplus S_-) .
\]
The Lie brackets are described as follows. 
If we choose a basis $\{Q^1_{\pm}, Q^2_\pm\}$ for $S_\pm \oplus S_\pm$ then the nontrivial brackets read 
\begin{equation}\label{(2,2)para}
(2,2) \; {\rm para} \;\; : \;\; [Q_\pm^1, Q_\pm^1] = 2 \partial_{\pm} \;\; , \;\; [Q_{\pm}^2, Q_{\pm}^2] = -2 \partial_{\pm} .
\end{equation}

\begin{remark}
Note that this differs from ordinary $(2,2)$ supersymmetry by a sign:
\begin{equation}\label{(2,2)para}
(2,2) \; {\rm ordinary} \;\; : \;\; [Q_\pm^1, Q_\pm^1] = 2 \partial_{\pm} \;\; , \;\; [Q_{\pm}^2, Q_{\pm}^2] =  2 \partial_{\pm} .
\end{equation}
\end{remark}

More generally, suppose $W_\pm$ are vector spaces of dimension $k_\pm$, respectively.
In addition, suppose $\eta_\pm$ are symmetric nondegenerate forms on $W_\pm$. 
Then, we can define a super Lie algebra of the form
\[
\mathfrak{t}_{W} =  \RR^{1,1} \oplus \Pi(S_+ \otimes W_+) \oplus \Pi(S_- \otimes W_-)
\]
with brackets defined by
\[
[Q_\pm^{a}, Q_\pm^{b}] = 2 \eta^{ab}_\pm \partial_\pm .
\] 
The case of $\mathfrak{t}_{(2,2)}$, which will be of most interested to us, corresponds to taking $k_+ = k_- = 2$ and $\eta_\pm^{11} = 1$, $\eta^{22}_\pm = - 1$, $\eta^{12}_{\pm} = 0$.

\brian{Can change basis to off diagonal and write in more conventional way.}

\subsubsection{R-symmetry}
We have seen above that the $(2,2)$ para-SUSY algebra $\mathfrak{t}_{(2,2)}$ can be diagonalised in terms of the charges\footnote{Note that for the usual $(2,2)$ SUSY one cannot diagonalize the algebra over $\RR$.}
\begin{align}\label{eq:R-sym_charges}
\begin{aligned}
[Q_\pm^1,Q_\pm^1]&=2\p_\pm\\
[Q_\pm^2,Q_\pm^2]&=-2\p_\pm.
\end{aligned}
\end{align}
We make a change of basis by the formulas $Q_\pm=\frac{1}{\sqrt{2}}(Q^2_\pm+Q^1_\pm)$ and $\tl{Q}_\pm=\frac{1}{\sqrt{2}}(Q^2_\pm-Q^1_\pm)$. 
Equations \eqref{eq:R-sym_charges} can be written collectively as
\begin{align}\label{eq:R-sym_eta}
[Q_\pm^a,Q_\pm^b]=2\eta^{ab}\p_\pm,
\end{align}
where $\eta^{ab}=\begin{pmatrix}
1 & 0 \\
0 & -1
\end{pmatrix}$. From here it is easy to see that matrices $(M_\pm)^a_b$ that rotate the $\pm$-chirality charges among each other while preserving the commutation relations \eqref{eq:R-sym_eta},
\begin{align*}
[(M_\pm)^a_cQ_\pm^c,(M_\pm)^b_dQ_\pm^d]=2\eta^{ab}\p_\pm
\end{align*}
have to satisfy
\begin{align*}
(M_\pm)^a_c\eta^{cd}(M_\pm)^a_d=\eta^{ab},
\end{align*}
i.e. $M_\pm$ have to lie in $SO(1,1)$ for each subscript $\pm$ and the R-symmetry group is therefore $G_R=SO(1,1)_+\times SO(1,1)_-$.
\david{this is only relevant for the (2,2) formalism, will se if we need this or not}
The R-symmetry acts on the odd coordinates accordingly as
\begin{align*}
\begin{pmatrix}
\theta^1_\pm \\
\theta^2_\pm	
\end{pmatrix}
\mapsto
\begin{pmatrix}
\cosh(\alpha_\pm) & \sinh(\alpha_\pm) \\
\sinh(\alpha_\pm) & \cosh(\alpha_\pm)
\end{pmatrix}
\begin{pmatrix}
\theta^1_\pm \\
\theta^2_\pm	
\end{pmatrix}
\end{align*}
or, equivalently, $(\theta^\pm,\tth^\pm)\mapsto (e^{\alpha_\pm} \theta^\pm,e^{-\alpha_\pm}\tth^\pm)$. There are therefore two inequivalent embeddings of the Lorentz group $SO(1,1)$ into the R-symmetry group, we label them by $V$ and $A$:
\begin{align*}
R_V(\alpha)&:(\theta^\pm,\tth^\pm)\mapsto (e^\alpha \theta^\pm,e^{-\alpha}\tth^\pm)\\
R_A(\alpha)&:(\theta^\pm,\tth^\pm)\mapsto (e^{\pm \alpha} \theta^\pm,e^{\mp \alpha}\tth^\pm),
\end{align*}
mapping the supercharges as
\begin{align*}
R_V(\alpha):& (Q_\pm,\tl{Q}_\pm)\mapsto (e^{-\alpha}Q_\pm,e^{\alpha}\tl{Q}_\pm)\\
R_A(\alpha):& (Q_\pm,\tl{Q}_\pm)\mapsto (e^{\mp\alpha}Q_\pm,e^{\pm \alpha}\tl{Q}_\pm).
\end{align*}
The generators of these transformations are
\begin{align*}
F_{V/A}=\theta^+\frac{\p}{\p\theta^+}-\tth^+\frac{\p}{\p\tth^+}\pm \theta^-\frac{\p}{\p\theta^-}\mp\tth^-\frac{\p}{\p\tth^-}.
\end{align*}

Because $F_{V/A}$ has same commutators with other operators as $M$, the Lorentz generator, and additionally all $F_{V/A}$ and $M$ commute among themselves, we can define new "Lorentz" generators in one of the two following ways:
\begin{align*}
M_A=M+F_V,\quad M_B=M+F_A.
\end{align*}

\subsection{The $(2,2)$ parasupersymmetric $\sigma$-model}
It has been known since \cite{Zumino:1979et} that the $(1,1)$ supersymmetric $\sigma$-model \eqref{eq:(1,1)action} admits $(2,2)$ supersymmetry when $(M,g)$ is a K\"{a}hler manifold. In general, $(2,2)$ supersymmetry in fact requires the target to be {\bf generalized K\"ahler} \cite{Gualtieri:2003dx}, which is equivalent to a data of a bi-Hermitian geometry discovered by \cite{Gates:1984nk}. For $(2,2)$ para-SUSY, the story is analogous. It was shown in \cite{HullTwistedSUSY} that in order to extend the $(1,1)$ SUSY of \ref{eq:(1,1)action} to $(2,2)$ para-SUSY, one needs a para-complex version of the biHermitian geometry. In \cite{Hu:2019zro} it was then shown that this can be equivalently described by {\bf generalized para-K\"ahler} geometry.

\paragraph{Expanding the $(1,1)$ action}

First, we further analyze the $(1,1)$ supersymmetric theory. 
Recall the $(1,1)$ supersymmetric $\sigma$-model is described by the action
\begin{align*}
S_{(1,1)}(\Phi)&=\int_{\hat{\Sigma}}[g(\Phi)+b(\Phi)]_{ij}D_+\Phi^iD_-\Phi^j.
\end{align*}
In components, the superfield has the form
\[
\Phi^i =\phi^i+\theta^+\psi^i_++\theta^-\psi^i_-+\theta^+\theta^-F^i
\]
The super covariant derivatives $D_{\pm}$ applied to $\Phi^i$ read
\[
D_\pm\Phi^i =\psi^i_\pm\pm\theta^\mp F^i-\theta^\pm\p_\pm\phi^i\mp\theta^+\theta^-\p_\pm\psi^i_\mp .
\]
Further, we can expand the contributions from the metric and $b$-field as
\begin{align*}
[g(\Phi)+b(\Phi)]_{ij} = & [g(\phi)+b(\phi)]_{ij}+\p_k[g(\phi)+b(\phi)]_{ij}(\theta^+\psi_+^k+\theta^-\psi_-^k+\theta^+\theta^-F^k)\\
& +\frac{1}{2}\p_k\p_l[g(\phi)+b(\phi)]_{ij}(\theta^+\psi_+^k+\theta^-\psi_-^k)(\theta^+\psi_+^l+\theta^-\psi_-^l).
\end{align*}

After performing the odd integration, the only terms that survive are the $\theta^+\theta^-$ coefficients:
\begin{align*}
\theta^+\theta^-&\left[(g+b)_{ij}(\psi_+^i\p_-\psi^j_++\psi^j_-\p_-\psi^i_-+F^iF^j+\p_+\phi^i\p_-\phi^j)\right. \\
&+\p_k(g+b)_{ij}\left(F^k\psi^i_+\psi^j_-+\psi^k_+(-F^i\psi^j_--\psi^i_+\p_-\phi^j)+\psi^k_-(-\p_+\phi^i\psi^j_-+\psi_+^iF^j)\right)\\
&\left. +\frac{1}{2}\p_k\p_l(g+b)_{ij}(-\psi_+^k\psi_-^l\psi_+^i\psi_-^j+\psi_-^k\psi_+^l\psi^i_+\psi^j_-) \right].
\end{align*}

The field $F$ is auxiliary (since it enters only algebraically: no derivations of $F$ appear in the action), and therefore can be integrated out. To obtain the equations of motion for $F$, we use the formula $\p_kg_{ij}=\Gamma_{ikj}+\Gamma_{jki}$ and collect the terms involving $F$:
\begin{align*}
g_{ij}F^iF^j+&(\Gamma_{ikj}+\Gamma_{jki})(F^k\psi^i_+\psi^j_--F^i\psi^k_+\psi^j_-+F^j\psi^k_-\psi_+^i)\\
+&F^k\psi^i_+\psi^j_-(\p_kb_{ij}+\p_ib_{jk}+\p_jb_{ki}).
\end{align*}
Using $\Gamma_{ikj}=\Gamma_{kij}$ and $H_{ijk}=(\p_kb_{ij}+\p_ib_{jk}+\p_jb_{ki})$, we can rewrite this as
\begin{align*}
g_{ij}F^iF^j+2\Gamma_{ikj}F^j\psi^k_-\psi_+^i+F^k\psi^i_+\psi^j_-H_{ijk}=g_{ij}(F^iF^j+2F^j(\Gamma^-)_{lk}^i\psi_-^k\psi_+^l),
\end{align*}
where $\Gamma^-$ are the Christoffel symbols of the connection $\n^-=\lc-\frac{1}{2}g^{-1}H$. This yields the equation of motion for $F$,
\begin{align} \label{F_EoM}
\frac{\delta S_{(1,1)}}{\delta F^i}=0\quad \Longleftrightarrow\quad  F^i=-(\Gamma^-)^i_{jk}\psi^k_-\psi^j_+
\end{align}

%\paragraph{(2,2) SUSY}

%We propose the following symmetry by the $(2,2)$ parasupersymmetry algebra (\ref{(2,2)para}) (setting $\theta^\pm_1\coloneqq \theta^\pm$ for simplicity), which read in superspace notation:
%\begin{align*}
%Q^1_\pm&=\frac{\p}{\p\theta^\pm}+\theta^\pm\p_\pm \\
%Q^2_\pm\Phi^i&=(K_\pm)^i_j(\Phi)D_\pm\Phi^j \\
%\end{align*}
%where $D_\pm =\frac{\p}{\p\theta^\pm}-\theta^\pm\p_\pm$.

\paragraph{Extended supersymmetry}

The $\sigma$-model we have just described has manifest $(1,1)$ supersymmetry. 
We now propose the a symmetry of the action $S_{(1,1)}$ by the extended $(2,2)$ parasupersymmetry algebra (\ref{(2,2)para}).
In general, this extended symmetry exists only after we make some additional assumptions on the geometric data prescribing the action.

Setting $\theta^\pm_1\coloneqq \theta^\pm$ for simplicity, we propose the following $(2,2)$ parasupersymmetry in $(1,1)$ superfield notation:
\begin{align}
\label{q1} Q^1_\pm&=\frac{\p}{\p\theta^\pm}+\theta^\pm\p_\pm \\
\label{q2} Q^2_\pm\Phi^i&=(K_\pm)^i_j(\Phi)D_\pm\Phi^j
\end{align}
where $D_\pm =\frac{\p}{\p\theta^\pm}-\theta^\pm\p_\pm$. 
\brian{We need to either recall what $K_{\pm}$ is geometrically, or state that it is a free parameter which we will interpret momentarily.}
In other words, the infinitesimal action of the element $Q^1_{\pm} \in \mathfrak{t}_{(2,2)}$ is:
\[
\Phi^i \mapsto \Phi^i + \epsilon^{\pm}_1 \left( \frac{\p}{\p\theta^\pm}+\theta^\pm\p_\pm \right) \Phi^i
\]
where $\epsilon^{\pm}_1$ is an infinitesimal parameter. 
Similarly, the infinitesimal action by the element $Q^2_{\pm} \in \mathfrak{t}_{(2,2)}$ is:
\[
\Phi \mapsto \Phi + \epsilon^{\pm}_2 (K_\pm)^i_j(\Phi)D_\pm\Phi^j 
\]
where $\epsilon^\pm_2$ is an infinitesimal parameter.

\begin{lemma}
Expanding out in the components of the $(1,1)$ superfield, the infinitesimal action by $Q^1_{+}$ and in Equation (\ref{q1}) reads:
\[
Q^1_{+} : (\phi^i, \psi^i_+, \psi^i_-, F^i) \mapsto (\phi^i, \psi^i_{\pm}, F^i) + \epsilon^+_1 (\psi^i_+, \partial_+ \phi, F^i, \partial_+ \psi^i_-) . 
\]
and by $Q^1_-$:
\[
Q^1_{-} : (\phi^i, \psi^i_+, \psi^i_-, F^i)  \mapsto (\phi^i, \psi^i_{\pm}, F^i) + \epsilon^-_1 (\psi^i_-, \partial^i_- \phi^i, - F^i, - \partial_- \psi^i_+)
\]
Similarly, the infinitesimal action by $Q^2_{+}$ in Equation (\ref{q2}) reads:
\begin{equation}\label{q2plus}
Q^2_{+} : (\phi^i, \psi^i_+, \psi^i_-, F^i) \mapsto ((K_+)^i_j \psi_+ ^j , - (K_+)^{i}_{j} \partial_+ \phi^j - \partial_k(K_+)^i_j \psi_+^k \psi_+^k, (K_+)^i_j F^j+\p_k(K_+)^i_j\psi^k_-\psi^j_+, \brian{F term})
\end{equation}
and for $Q^2_-$:
\begin{equation}\label{q2minus}
Q^2_{-} : (\phi^i, \psi^i_+, \psi^i_-, F^i) \mapsto ((K_-)^i_j \psi_- ^j , - (K_-)^{i}_{j} \partial_- \phi^j - \partial_k(K_-)^i_j \psi_-^k \psi_-^k, (K_-)^i_j F^j+\p_k(K_-)^i_j\psi^k_+\psi^j_-, \brian{F term})
\end{equation}
\end{lemma}

%\begin{align}\label{Q12_action}
%\begin{aligned}
%[Q_\pm^1 ,\phi^i]&=\psi_\pm^i,& [Q_\pm^2 ,\phi^i] &=(K_\pm)^i_j\psi_\pm^j,\\
%[Q_\pm^1 ,\psi^i_\pm] &=\p_\pm\phi^i,& [Q_\pm^2 ,\psi^i_\pm] &=-(K_\pm)^i_j\p_+\phi^j{\textcolor{red}{+}}\p_k(K_\pm)^i_j\psi_+^k\psi_+^j\\
%[Q_\pm^1 ,\psi^i_\mp]&=\pm F^i,& [Q_\pm^2 ,\psi^i_\mp] &=(K_\pm)^i_jF^j+\p_k(K_\pm)^i_j\psi^k_\mp\psi^j_\pm.
%\end{aligned}
%\end{align}
%
%\textcolor{red}{There's a sign issue above, the $+$ needs to be $-$.}
\begin{proof}
Recall, in components the superfield is of the form
\[
\Phi^i =\phi^i+\theta^+\psi^i_++\theta^-\psi^i_-+\theta^+\theta^-F^i .
\]
The action of the $Q^1_\pm$ charges is straightforward and can be simply read off from the infinitesimal action. 
%\begin{align*}
%[Q^1_\pm,\Phi]=[Q_\pm^1,\phi^i]+[Q_\pm^1,\psi^i_\pm]\theta^\pm+[Q_\pm^1,\psi^i_\mp]\theta^\mp+[Q_\pm^1,F]\theta^\pm\theta^\mp.
%\end{align*}
%For instance $[Q_{\pm}^1, \phi^i] = \theta^{\pm} \partial_{\pm} \phi^i$, thus 
To obtain the action by the charges $Q^2_\pm$ on the individual components we first need to expand $K_\pm(\Phi)$ in terms of the components of the superfield:
\begin{align*}
(K_\pm)^i_j(\Phi)=(K_\pm)^i_j(\phi)+\p_k(K_\pm)^i_j\theta^+\psi_+^k+\p_k(K_\pm)^i_j\theta^-\psi_-^k+\p_k(K_\pm)\theta^+\theta^-F^k,
\end{align*}
so that the infinitesimal action by $Q^2_\pm$ on $\Phi^i$ is:
\begin{align}
\Phi^i + \epsilon_2^\pm (K_\pm)^i_j(\Phi)(\psi^j_\pm\pm\theta^\mp F^j-\theta^\pm\p_\pm\phi^j\mp\theta^+\theta^-\p_\pm\psi^j_\mp) .
\end{align}
Reading off the various components this expression yields Equations (\ref{q2plus}) and (\ref{q2minus}).
\end{proof}

\paragraph{The $(2,2)$ formalism}
\brian{
There is the following superspace model for $(2,2)$ parasupersymmetry. 
Consider the superspace $\RR^{1,1 | 4}$ 
}

\subsection{$(2,1)$ and $(2,0)$ parasupersymmetry}

Many of the constructions above make sense when there is less total supersymmetry, and we briefly mention two important cases.

The first concerns the $(2,1)$ parasupersymmetry algebra.
This algebra $\mathfrak{t}_{(2,1)}$ consists of generators $\{Q^1_\pm, Q^2_+\}$ satisfying the same algebra as in (\ref{(2,2)para}). 
Starting with the $(1,1)$ supersymmetric $\sigma$-model (\ref{eq:(1,1)action}), and labeling the odd coordinates by $\theta^\pm = \theta_1^\pm$, one can ask for an additional odd symmetry 
\[
Q_2^+ :  \Phi \mapsto \Phi + \epsilon_2^+ K_+(\Phi)^j_i D_+ \Phi^i
\]
which determines a symmetry by the $(2,1)$ parasupersymmetry algebra.

\begin{proposition}
The odd vector field $Q_2^+$ is a symmetry of the $(1,1)$ supersymmetric $\sigma$-model provided $(K_+)^{j}_i$ is a paracomplex structure satisfying \brian{What conditions here?}
Thus, the $(1,1)$ supersymmetric $\sigma$-model has $(2,1)$ parasupersymmetry provided the target is \brian{same conditions}. 
\end{proposition}

The next symmetry algebra we wish to consider is the $(2,0)$ parasupersymmetry algebra $\mathfrak{t}_{(2,0)}$. 
This algebra has the same even generators as the $(2,1)$ and $(2,2)$ algebras, and odd generators $\{Q^1_+, Q^2_+\}$ satisfying the relations
\[
[Q^1_+, Q^1_+] =  2 \partial_\pm \;\;\; , \;\;\; [Q^2_+, Q^2_+] = - 2 \partial_\pm
\]

\brian{The (1,0) action}

We propose an extended symmetry of the $(1,0)$ $\sigma$-model by the following action by the odd vector field $Q_+^2$:
\[
Q^2_+ : \Phi \mapsto \Phi + \epsilon_2^+ K_+(\Phi)^j_i D_+ \Phi^i .
\]

\begin{proposition}
The odd vector field $Q_2^+$ is a symmetry of the $(1,0)$ supersymmetric $\sigma$-model provided $(K_+)^{j}_i$ is a paracomplex structure. 
Thus, the $(1,0)$ supersymmetric $\sigma$-model has $(2,0)$ parasupersymmetry provided the target is paracomplex. \brian{there is a version for a target vector bundle as well...}
\end{proposition}

\section{The AKSZ formalism and 3d TFT}
\def\fg{\mathfrak{g}}
In this section we will show how to associate $2D$ topological theories to a generalized (para-)complex structure and relate them to the topological twists of $2D$ $(2,2)$ (para-)SUSY sigma models described in Section \ref{sec:toptwist} and in \cite{Kapustin:2004gv}. 
The key to our construction is to realize the data of a G(p)C structure in terms of its eigenbundles, which are Dirac structures $L$ in the Courant algebroid $\TT$. 
Via the AKSZ construction \cite{AKSZ}, this correspondence translates into the statement that the Dirac structure $L$ defines a topological boundary theory of a $3D$ topological theory defined by the Courant algebroid $\TT$ \cite{Roytenberg:2002nu}.

Throughout, we will use symplectic $NQ$ manifold as our model for shifted symplectic geometry. 
We will recall the general setup of associating a $3D$ topological field theory to the data of a Courant algebroid. 
For a reference, see \cite{Roytenberg:2002nu,??}.

\subsection{Courant algebroids, $3D$ TFTs, and boundary conditions}
From the point of view of topological field theory, Courant algebroids are important because they provide geometric examples of $2$-shifted symplectic spaces. 
Via the AKSZ construction, $2$-shifted symplectic spaces are the natural home for $3$-dimensional topological field theories in the BV formalism. 
\brian{give citations here.}

In \cite{Roytenberg:2002nu}, it is shown how to associate a $2$-shifted symplectic NQ manifold from the data of a Courant algebroid.

\begin{theorem}[\cite{Roytenberg:2002nu}]
There is an equivalence between isomorphism classes of $2$-shifted symplectic NQ manifolds with body $M$ and isomorphism classes of Courant algebroids on $M$.
\end{theorem}

We briefly recall this construction.

Recall, the data of a Courant algebroid on a manifold $M$ is a vector bundle $E$, whose sheaf of sections we denote $\cE$, together with a nondegenerate symmetric bilinear pairing $\langle -, -\rangle : \cE \otimes \cE \to C^\infty(M)$ , an anchor map $a : E \to T M$, and a bilinear operator
\[
[-,-] : \cE \times \cE \to \cE
\]
called the Courant-Dorfman bracket. 
\brian{spell out properties, find a good reference}
Denote by $a^* : T^* M \to E^*$ the bundle map dual to $a$.

To every Courant algebroid we can define the following sequence of vector bundles on $M$
\[
T^*M \xto{a^*} E \xto{a} TM .
\]
A Courant algebroid is called {\em exact} if this sequence of bundles is exact.

\def\Sym{{\rm Sym}}

Using this sequence, we can define the associated $NQ$ manifold $X_E$, following \cite{Ryotenberg:2002nu}.
The body of the NQ manifold is $M$, and the underlying graded vector bundle is given by $T^*[2] \oplus E[1]$. 
Define the degree $+1$ vector field 
\[
Q : \Gamma(M , \Sym \left(T^*[2] \oplus E[1]\right)^*) \to \Gamma(M , \Sym \left(T^*[2] \oplus E[1]\right)^*) 
\]
as follows: for $\psi \in \Sym^{k + \ell + 2} \left(T^*[2] \oplus E[1]\right)^*)$ and
\[
(\xi_0 \otimes \cdots \otimes \xi_k) \otimes (\alpha_0 \otimes \cdots \otimes \alpha_\ell) \in \Sym^{k+1}(T^*[2]) \otimes \Sym^{\ell + 1}(E[1]) 
\]
define
\begin{align*}
(Q \psi) ((\xi_0 \otimes \cdots \otimes \xi_k) \otimes (\alpha_0 \otimes \cdots \otimes \alpha_\ell)) = \brian{finish}
\end{align*}

All that remains is to describe the $2$-shifted symplectic structure on the NQ manifold $X_E$. 
This is defined via the obvious pairing between $T^*[2]$ and $T$ together with the pairing $\langle - ,- \rangle$ on $E[1]$.
In local coordinates \brian{finish}

The simplest type of Courant algebroid is one over a point.

\begin{Ex}\label{ex: cs}
Any Lie algebra $\fg$ together with a non-degenerate invariant pairing defines a $2$-shifted symplectic structure on the graded manifold $\fg[1]$ living over a point. 
The dg algebra of functions is the Chevalley-Eilenberg cochain complex computing Lie algebra cohomology $C^*(\fg)$. 
All such $2$-symplectic NQ manifolds over a point are of this form. 
%The resulting AKSZ theory is Chern-Simons theory. 
\end{Ex}

\subsubsection*{The $2$-shifted symplectic space of an exact Courant Algebroid}

We recall the description of the $2$-shifted symplectic NQ manifold $X_E$ associated to an exact Courant algebroid $E$.
Of course, as a vector bundle $E = \TT$, and hence as a graded manifold $X_E$ is of the form $T^*[2] T[1] M$.
Concretely, the coordinates on this manifold are given by $(x^i,v^a,p_i,\mu_a)_{i,a=1\cdots n}$, where $x^i$ are the usual coordinates on $M$ with degree $0$, $v^a$ are the corresponding ``velocities'', i.e. the fibre coordinates on $T[1]M$ with a degree $1$, and $p_i,\mu_a$ are the momenta corresponding to $x^i,v^a$ with degrees $2,1$, respectively. The canonical symplectic form
\begin{align*}
\Omega= dx^idp_i+dv^ad\mu_a,
\end{align*}
is then of degree $2$. $T^*[2]T[1]M$ is the minimal symplectic realization of the shifted bundle $(\TT)[1]M$, which is recovered by setting $p_i=0$. The symmetric part of $\Omega$ represents the pairing $\lara$ on $(\TT)M$; this is because we can identify $d\mu_a\leftrightarrow \p_i$ and $dv^a\leftrightarrow dx^i$

\brian{Severa classification}

\begin{theorem}\label{thm: severa}
The set of isomorphism classes of exact Courant algebroids is a torsor for $H^3(X)$. 
\end{theorem}

\subsubsection*{The Poisson Courant algebroid}

\brian{Both real and holomorphic versions}

\subsubsection{The AKSZ theory associated to a Courant algebroid}

To any Courant algebroid $E$, we can associate an NQ manifold $X_E$ which carries a $2$-shifted symplectic structure that we denote by $\omega_E$. 
In the case that the Courant algebroid is exact, call the associated $2$-shifted symplectic space $X_H$, where $H$ labels the Severa class.

\def\sA{\mathcal{A}}
\def\d{{\rm d}}
\def\dbar{\Bar{\partial}}

The starting point of the AKSZ construction is the mapping space
\[
{\rm Map}\left((M, (\sA^*_M, \d_M)), X_E\right)
\]
where $(M, (\sA^*_M, \d_M))$ is a dg manifold with body a smooth oriented manifold $M$. 
That is, $\sA^*_M$ is a sheaf of graded commutative algebras over the de Rham complex $\Omega^*_M$ and $\d_M$ is a linear operator of degree $+1$ satisfying:
\begin{itemize}
\item[(1)] $\sA_M$ is concentrated in finitely many degrees;
\item[(2)] For each $k$, $\sA^k_M$ is a locally free sheaf of $C^\infty_M$-modules of finite rank;
\item[(3)] The differential $\d_M : \sA_M^* \to \sA_M^{*+1}$ is square zero differential operator making $(\sA_M , \d_M)$ into a sheaf of commutative dg algebras over the de Rham complex $\Omega^*_M$
\end{itemize}

\begin{Ex}
The most important example for us will be the source dg manifold $(M, \Omega^*_M)$, that is $\sA_M = \Omega^*_M$ with de Rham differential. 
We denote this dg manifold by $M_{\rm dR}$.
\end{Ex}

\begin{Ex}
If $M$ has a para-complex structure, then $(M, \Omega^{0,*}_M)$ has the structure of a dg manifold with differential given by the para $\dbar$-operator. 
\brian{David, is this consistent notation?}
We will denote this dg manifold by $M_{p \dbar}$. 
\end{Ex}

\begin{Ex}
If $\fg$ is a Lie algebra equipped with a non-degenerate invariant pairing, and $X_E = \fg[1]$ as in Example \ref{ex: cs}, then the AKSZ theory (whose target base manifold is a point) is equivalent to Chern-Simons theory on $M$. 
\end{Ex}

\subsubsection{Dirac structures and boundary conditions}

\subsection{Two dimensional TFT from GpC structures}

\brian{Recall that a generalized (para-)complex structure $\JJ$ defines a Dirac structure in $\TT$, and hence a Lagrangian inside of the $2$-shifted symplectic space $\XX_H$.  
%More generally, if $\JJ$ is a generalized complex structure in an arbitrary Courant algebroid $E$, then we obtain a $2$-shifted Lagrangian inside of the $2$-shifted symplectic space $\XX_E$. 
This Lagrangian then defines a boundary condition for the three-dimensional AKSZ theory. }

\subsubsection*{Trivial GpC structure}

\subsubsection*{(Real) Poisson $\sigma$-model}

\subsubsection*{Para-complex $A/B$-models}

We point out two special cases of the above general construction.

\brian{The $A$-model is the usual thing.}

\begin{Def}
The {\bf para-complex $B$-model} with source a closed Riemann surface $\Sigma$ and target a para-complex manifold $X$ is the AKSZ theory with source the de Rham space $\Sigma_{\rm dR}$ and target the $1$-shifted symplectic space $T^*[1] X_{p \dbar}$:
\[
{\rm Map}\left(\Sigma_{dR}, T^*[1]  X_{p \dbar}\right) .
\]
\end{Def}

\brian{Discuss Si's work on perturbative quantization}

\hrulefill

\brian{***para Kahler example, **example where the paracomplex structures commute but are not equal (this is where people see ``twisted chiral"), para version of T-duality, **Poisson $\sigma$-model, going back and forth between generalized (para) complex.
}

 \brian{discuss anomalies}

\subsection{Para holomorphic variants}

So far, in each of the $\sigma$-models we have discussed in the AKSZ formalism, the fields have depended only topologically on the source Riemann surface. 
There are closely related $\sigma$-models which depending {\em para-holomorphically} on the source Riemann surface that we briefly discuss.

\section{Twisted parasupersymmetry}\label{sec:toptwist}

In this section we will present how para-supersymmetry theories can be twisted, in exact analogy with twisting in ordinary supersymmetry.
Applied to the $(2,2)$ parasupersymmetric theories that we have constructed in \S \ref{sec: parasusy}, we find that twisting yield topological field field theories. 
In the next section, we will construct these topological theories geometrically using the AKSZ formalism.

The procedure for twisting will again follow the analogy between generalized K\"{a}hler (GK) and generalized para-K\"{a}hler (GpK). geometries, and we will follow the approach presented in \cite{Kapustin:2004gv} for the GK case.

\brian{geometry, change in gradings}
\david{how does the embedding of $SO(1,1)$ into $G_R$ reflect on the definition of $\QQ$?}

For the topological twist, we will use the following nilpotent supercharge
\begin{align}
\QQ=Q_L+Q_R,\quad Q_L=\frac{1}{2}(Q^1_++Q^2_+),\quad Q_R=\frac{1}{2}(Q^1_-+Q^2_-),
\end{align}
and we also introduce the usual notation 
\begin{align*}
\chi=\frac{1}{2}(\id+K_+)\psi_+=P_+\psi_+=\psi_+^{(1,0)_+},\quad\lambda=\frac{1}{2}(\id+K_-)\psi_-=P_-\psi_-=\psi_-^{(1,0)_-}.
\end{align*}

\begin{proposition}
The action of $Q_{L/R}$ on the fields $\chi$, $\lambda$ and $\phi$ is given by
\begin{align}\label{eq:Qcoh}
\begin{aligned}
[Q_L,\phi^i]&=\chi^i & [Q_R,\phi^i]&=\lambda^i\\
[Q_L,\chi^i]&=0 & [Q_R,\lambda^i]&=0\\
[Q_L,\lambda^i]&=-(\Gamma^-)^i_{jk}\chi^j\lambda^k & [Q_R,\chi^i]&=-(\Gamma^+)^i_{jk}\lambda^j\chi^k.
\end{aligned}
\end{align}
\end{proposition}
\begin{proof}
The action of $Q_{L/R}$ on $\phi$ can be immediately read off \eqref{Q12_action}:
\begin{align}
[Q_L,\phi^i]=\frac{1}{2}[Q_+^1+Q^2_+,\phi^i]=\chi^i.
\end{align}

We now prove the formulas for the action of $Q_{L/R}$ on $\chi$, the action on $\lambda$ is entirely analogous. First, we expand
\begin{align}\label{QL_chi}
[Q_L,\chi^i]=[Q_L,(P_+)^i_j\psi_+^j]=[Q_L,(P_+)^i_j]\psi_+^j\textcolor{red}{+}(P_+)^i_j[Q_L,\psi_+^j].
\end{align}
\textcolor{red}{Or maybe here? I think this is the one}
Because $K_+$ is a function of the bosonic coordinates, we also have $P_+=P_+(\phi)$ and so
\begin{align}\label{QL_P}
[Q_L,(P_+)^i_j]=\p_k(P_+)^i_j[Q_L,\phi^k]=\p_k(P_+)^i_j\chi^k.
\end{align}
Combining \eqref{QL_chi} and \eqref{QL_P} and using \eqref{Q12_action}, we arrive at
\begin{align*}
[Q_L,\chi^i]&=\p_k(P_+)^i_j\chi^k\psi_+^j\textcolor{red}{\overset{?}{\pm}}(P_+)^i_j[(\tl{P}_+)^j_k\p_+\phi^k\textcolor{red}{+}\frac{1}{2}\p_k(K_+)^j_l\psi_+^k\psi_+^l]\\
&=\p_k(P_+)^i_j(P_+)^k_l\psi_+^l\psi_+^j\textcolor{red}{-}(P_+)^i_j\p_k(P_+)^j_l\psi_+^k\psi_+^l,
\end{align*}
where we denoted $\tl{P}_+=\frac{1}{2}(\id-K_+)$ and used $P_+\tl{P}_+=0$. We now expand the projectors, $(P_+)^i_j=\frac{1}{2}(\delta^i_j+(K_+)^i_j)$:

\begin{align*}
[Q_L,\chi^i]&=\p_k(P_+)^i_j(P_+)^k_l\psi_+^l\psi_+^j\textcolor{red}{-}(P_+)^i_j\p_k(P_+)^j_l\psi_+^k\psi_+^l\\
&=\frac{1}{2}(\p_j(K_+)^i_l(P_+)^j_k\textcolor{red}{-}(P_+)^i_j\p_k(K_+)^j_l)\psi_+^k\psi_+^l\\
&=\frac{1}{4}(\p_j(K_+)^i_l(K_+)^j_k\textcolor{red}{-}(K_+)^i_j\p_k(K_+)^j_l)\psi_+^k\psi_+^l\\
&+\frac{1}{4}(\p_j(K_+)^i_l\psi_+^j\psi_+^l\textcolor{red}{-}\p_k(K_+)^i_l\psi_+^k\psi_+^l)=-\frac{1}{2}(N_{K_+})^i_{kl}\psi_+^k\psi^l_+,
\end{align*}
\textcolor{red}{This must be the right sign choice} where in the last line we rewrote $\psi_+^k\psi^l_+=\frac{1}{2}(\psi^k\psi^l-\psi^l\psi^k)$ to get the expression for the Nijenhuis tensor of $K_+$:
\begin{align*}
4(N_{K_+})^i_{kl}=(K_+)^j_k\p_j(K_+)^i_l-(K_+)^j_l\p_j(K_+)^i_k \textcolor{red}{-} (K_+)^i_j(\p_k(K_+)^j_l-\p_l(K_+)^j_k).
\end{align*}
Invoking integrability of $K_+$, $N_{K_+}=$ and we conclude that $[Q_L,\chi^i]=0$.

Similarly, $[Q_L,\lambda]$ can be expanded
\begin{align}\label{QL_lambda}
[Q_L,\lambda^i]&=[Q_L,(P_-)^i_j\psi_-^j]=[Q_L,(P_-)^i_j]\psi_-^j+(P_-)^i_j[Q_L,\psi_-^j]\\
&=\p_k(P_-)^i_j\chi^k\psi_-^j+(P_-)^i_k((P_+)^k_jF^j+\frac{1}{2}\p_l(K_+)^k_j\psi^l_-\psi_+^j),
\end{align}
where we used
\begin{align*}
[Q_L,\psi_-^i]=(P_+)^i_jF^j+\frac{1}{2}\p_k(K_+)^i_j\psi^k_-\psi_+^j.
\end{align*}
Next, we rewrite the derivative in terms of $\n^-$ and use the property $\n^-P_-=0$:
\begin{align*}
\p_k(P_-)^i_j&=\n^-_k(P_-)^i_j-(\Gamma^-)^i_{kl}(P_-)^l_j+(\Gamma^-)^l_{kj}(P_-)^i_l\\
&=-(\Gamma^-)^i_{kl}(P_-)^l_j+(\Gamma^-)^l_{kj}(P_-)^i_l,
\end{align*}
so that
\begin{align}\label{eq:calc1}
\begin{aligned}
\p_k(P_-)^i_j\chi^k\psi_-^j=(-(\Gamma^-)^i_{kl}(P_-)^l_j+(\Gamma^-)^l_{kj}(P_-)^i_l)(P_+)^k_m\psi_+^m\psi_-^j.
\end{aligned}
\end{align}
Similarly,
\begin{align}\label{eq:calc2}
\begin{aligned}
\frac{1}{2}(P_-)^i_k\p_l(K_+)^k_j\psi^l_-\psi_+^j&=(P_-)^i_k\p_l(P_+)^k_j\psi^l_-\psi_+^j\\
&=(P_-)^i_k(-(\Gamma^-)^k_{ml}(P_+)^m_j+(\Gamma^-)^m_{jl}(P_+)^k_m)\psi^l_-\psi_+^j,
\end{aligned}
\end{align}
where we used
\begin{align*}
(\Gamma^+)^i_{jk}=g^{im}(\Gamma_{mjk}+\frac{1}{2}H_{jkm})=g^{im}(\Gamma_{mkj}-\frac{1}{2}H_{kjm})=(\Gamma^-)^i_{kj}.
\end{align*}
Plugging \eqref{eq:calc1} and \eqref{eq:calc2} into \eqref{QL_lambda} with use of the equation of motion for $F$ \eqref{F_EoM} then yields
\begin{align*}
[Q_L,\lambda^i]&=((\Gamma^-)^i_{km}(P_-)^m_l-(\Gamma^-)^m_{kl}(P_-)^i_m)(P_+)^k_j\psi_-^l\psi_+^j\\
&+(P_-)^i_k(-(\Gamma^-)^k_{ml}(P_+)^m_j+(\Gamma^-)^m_{jl}(P_+)^k_m)\psi^l_-\psi_+^j\\
&-(P_-)^i_k(P_+)^k_m(\Gamma^-)^m_{jl}\psi_-^l\psi_+^j
 \end{align*}

 terms cancel (\textcolor{red}{up to another relative minus sign!}) as well as cancelling the term $(P_-)^i_k(P_+)^k_jF^j$ by
\begin{align*}
(P_-)^i_k(\Gamma^+)^m_{lj}(P_+)^k_m\psi^l_-\psi_+^j=(P_-)^i_k(P_+)^k_j(\Gamma^-)^j_{ml}\psi^l_-\psi_+^m=-(P_-)^i_k(P_+)^k_jF^j
\end{align*}
and we arrive at
\begin{align*}
\{Q_L,\lambda^i\}=-(\Gamma^-)^i_{kl}\chi^k\lambda^l.
\end{align*}

Now for $Q_R$, we have
\begin{align*}
\{Q_R,\phi^i\}=\lambda^i
\end{align*}
\end{proof}

The observables of the twisted theory are therefore polynomials in the odd variables $\chi,\lambda$ with even coefficients dependent on $\phi$:
\begin{align*}
{\cal O}_f=f(\phi)_{i_1\cdots i_a,j_1\cdots j_b}\chi^{i_1}\cdots\chi^{i_a}\lambda^{j_1}\cdots\lambda^{j_b}.
\end{align*}
Because $\chi \in \XX^{(1,0)_+}$ and $\lambda \in \XX^{(1,0)_-}$, we can identify ${\cal O}_f$ with a function on the supermanifold $(T^{(1,0)_+}\oplus T^{(1,0)_-})[1]$, which in turn can be identified with differential form
\begin{align*}
\Omega_f=f(\phi)_{i_1\cdots i_a,j_1\cdots j_b}dx^{i_1}_+\cdots dx^{i_a}_+ dx^{j_1}_- \cdots dx^{j_b}_-,
\end{align*}
where $dx_\pm$ are the one-forms satisfying $K_\pm dx_\pm=dx_\pm$, i.e. sections of the bundle $T^{*(1,0)_\pm}$. Via this identification, the operator ${\cal Q}\coloneqq Q_L+Q_R$ defines a differential $\rd_\QQ$, which acts on the sections of $\bigwedge^k(T^{*(1,0)_+}\oplus T^{*(1,0)_-})$ and because $\QQ$ squares to zero $\rd_\QQ$ also squares to zero. Therefore, $\rd_\QQ$ gives rise to a Chevalley-Eilenberg complex $\text{CE}(L)$ of a certain Lie algebroid $L$ which we now describe.

\paragraph{Lie algebroid from bi-para-Hermitian data} The underlying vector bundle of the Lie algebroid is $L=T^{(1,0)_+}\oplus T^{(1,0)_-}$, and the anchor is the sum of the two inclusions $\imath_\pm:\ T^{(1,0)_\pm}\hookrightarrow T$, i.e.
\begin{align*}
a:L=T^{(1,0)_+}\oplus T^{(1,0)_-} &\rightarrow T\\
 e=(x_+,x_-) &\mapsto \imath_+(x_+)+\imath_-(x_-).
\end{align*}
From \eqref{eq:Qcoh} we can read off the action of $\rd_\QQ$ on degree one elements, i.e. sections $\alpha=(\alpha^+,\alpha^-)$ of $L^*=T^*_{(1,0)_+}\oplus T^*_{(1,0)_-}$:
\begin{align*}
\rd_\QQ\alpha&=\p_k\ap_i^+[dx_+^k+dx_-^k]\w dx_+^i-\ap^+_i(\Gamma^+)^i_{jk}dx_-^j\w dx_+^k\\
&+\p_k\ap_i^-[dx_+^k+dx_-^k]\w dx_-^i-\ap^-_i(\Gamma^-)^i_{jk}dx_+^j\w dx_-^k.
\end{align*}
%In coordinate-free form, we get
%\begin{align*}
%\rd_\QQ\ap=(\p_++\n^+_{P_-(\bullet)})\ap^++(\p_-+\n^-_{P_+(\bullet)})\ap^-,
%\end{align*}
By contracting in two sections of $L$, $e_1=x_++x_-$, $e_2=y_-+y_-$, we get the coordinate-free expression
\begin{align}\label{eq:dQ}
\begin{aligned}
(\rd_\QQ\ap)(e_1,e_2)&=(\p_+\ap^+)(x_+,y_+)+\n^+_{x_-}\ap^+(y_+)-\n^+_{y_-}\ap^+(x_+)\\
&+(\p_-\ap^-)(x_-,y_-)+\n^-_{x_+}\ap^-(y_-)-\n^-_{y_+}\ap^-(x_-),
\end{aligned}
\end{align}
where $\p_\pm$ denotes the para-complex Dolbeault operators $\p$ for $K_\pm$. We can further simplify this expression by writing $\ap=(\eta(\tl{z}_+),\eta(\tl{z}_-))$ for $\tl{z}_\pm \in \se(T^{(1,0)_\pm})$, invoking the formula $\p_\pm\ap^\pm(x_\pm,y_\pm)=\lc_{x_\pm}\ap^\pm(y_\pm)-\lc_{y_\pm}\ap^\pm(x_\pm)$ and recalling $\n^\pm=\lc\pm \frac{1}{2}\eta^{-1}H$:
\begin{align}
\begin{aligned}
(\rd_\QQ\ap)(e_1,e_2)&=\eta((\lc_{x_+}+\n_{x_-}^+)\zt_+,y_+)-\eta((\lc_{y_+}+\n_{y_-}^+)\zt_+,x_+)\\
&+\eta((\lc_{x_-}+\n_{x_+}^-)\zt_-,y_-)-\eta((\lc_{y_-}+\n_{y_+}^-)\zt_-,x_-)\\
&=\eta(\n^+_{x_++x_-}\zt_+,y_+)-\eta(\n_{y_++y_-}^+\zt_+,x_+)-H(x_+,\zt_+,y_+)\\
&+\eta(\n_{x_++x_-}^-\zt_-,y_-)-\eta(\n_{y_++y_-}^-\zt_-,x_-)+H(x_-,\zt_-,y_-)
\end{aligned}
\end{align}

\paragraph{Lie algebroid from generalized para-K\"ahler data} Recall that a GpK structure defines the decomposition \eqref{GpK_bundles}
\begin{align*}
\TT=\ell_+\oplus\ell_-\oplus \ellt_+\oplus \ellt_-,
\end{align*}
where the the eigenbundles of $\KK_+$ are $\Lb_+=\ell_+\oplus\ell_-$ and $\tl{\Lb}_+=\ellt_+\oplus \ellt_-$. Because $\Lb$ is a Dirac structure, it defines a Lie algebroid by restriction of the Courant algebroid on $\TT$ to $\Lb$, i.e. the Lie algebroid bracket and anchor are given by the restriction of the Dorfman bracket and the projection onto tangent bundle, respectively (see Proposition \ref{prop:dirac_Liealg}.

\begin{theorem}
The Lie algebroids $(L,a,\rd_\QQ)$ and $(\Lb_+,\pi_T\!\!\mid_{\Lb_+},\brac\!\!\mid_{\Lb_+})$ are isomorphic via the map $\pi=\pi_+\oplus \pi_-$.
\end{theorem}
\begin{proof}
First, we notice that the bundles themselves are related by $\pi$,  $\pi(\Lb_+)=\pi(\ell_+\oplus \ell_-)=\pi_+(\ell_+)\oplus \pi_-(\ell_-)=T^{(1,0)_+}\oplus T^{(1,0)_-}=L$ and also $\pi$ is clearly an isomorphism since both $\pi_\pm$ are. Additionally, the anchors are related by $a\circ\pi=\pi_T\!\!\mid_{\Lb_+}$. The only non-trivial task is therefore to show that the respective differentials satisfy
\begin{align}\label{eq:d_pi}
\pi^*\circ\rd_Q  =\rd_{\Lb_+}\circ \pi^*,
\end{align}
where $\pi^*=\pi^*_+\oplus\pi_-^*$ and $\pi^*_\pm$ are dual maps to $\pi_\pm:\ell_+\rightarrow T^{(1,0)_\pm}$, extended to a map $\pi^*:\Lambda^k(L^*)\rightarrow\Lambda^k(\Lb_+^*)$.

Because of the chain rule, we only need to check this on degree $0$ and degree $1$ elements in the respective complexes. Degree $0$ follows immediately:
\begin{align*}
(\rd_Q f)(\pi(u))= a\circ \pi(u)[f]=\pi_T\!\!\mid_{\Lb_+}(u)[f]=(\rd_{\Lb_+}f)(u),
\end{align*}
%For degree one, we use the decomposition of the respective bundles and check for each component
%\begin{alignat*}{2}
%\rd_Q:&&T^*_{(1,0)_+}\oplus T^*_{(1,0)_-} &\rightarrow \Lambda^2(T^*_{(1,0)_+}\oplus T^*_{(1,0)_-})\\
%\rd_{\Lb_+}:&& \ell_+^*\oplus \ell_-^* &\rightarrow \Lambda^2(\ell_+^*\oplus \ell_-^*)
%\end{alignat*}
and we will now prove \ref{eq:d_pi} for degree $1$ elements. In the following we will make use of the identifications provided by the metric $\eta$ and pairing $\lara$:
\begin{alignat*}{2}
\eta:&& T^*_{(1,0)_\pm} &\leftrightarrow T^{(0,1)_\pm}\\
\lara:&& \ell^*_\pm &\leftrightarrow \ellt_\pm,
\end{alignat*}
so that elements in $T^*_{(1,0)_\pm}$ can be written as $\eta(\tl{z}_\pm)$ with $\tl{z}_\pm$ vector in $T^{(0,1)_\pm}$ and similarly, elements in $\ell^*_\pm$ can be expressed as $\la \tl{w}_\pm, \cdot\ra$ with $\tl{w}_\pm$ section of $\ellt_\pm$. To declutter notation, we shall also denote the bracket and anchor on $\Lb_+$ by $\brac$ and $\pi$, respectively.

The differential $\rd_{\Lb_+}$ is defined by the bracket on the Lie algebroid $\Lb_+$ via the following formula:
\begin{align}\label{eq:proof_Liethm}
\rd_{\Lb_+}  w^* (u,v)=\pi(u) w^*(v)-\pi(u) w^*(v)- w^*([u,v]),
\end{align}
where $ w^* \in \se(\Lb_+^*)$ and $u,v\in \se(\Lb_+)$. Writing $ w^*$ as $\la \tl{w},\cdot\ra$, with $\tl{w}\in\se (\tl{\Lb}_+)$ we can rewrite this as
\begin{align}\label{dL}
\begin{aligned}
\rd_{\Lb_+}  w^* (u,v)&=\pi(u)\la v ,\tl{w}\ra-\pi(v)\la u,\tl{w}\ra-\la [u,v],\tl{w}\ra\\
&=\la D_uv,\tl{w}\ra+\la v,D_u \tl{w}\ra-\la D_v u,\tl{w}\ra-\la u,D_v\tl{w}\ra-\la D_uv-D_vu,\tl{w}\ra\\
&+{T}(u,v,\tl{w})\\
&=\la D_u \tl{w},v\ra-\la D_v\tl{w},u\ra+{T}(u,v,\tl{w})\\
&=\la D_u \tl{w}_+,v_+\ra-\la D_v\tl{w}_+,u_+\ra+{T}(u_+,v_+,\tl{w}_+)\\
&+\la D_u \tl{w}_-,v_-\ra-\la D_v\tl{w}_-,u_-\ra+{T}(u_-,v_-,\tl{w}_-),
\end{aligned}
\end{align}
where we used \eqref{gentorsion_def} to express $\brac$ in terms of $D$, the generalized Bismut connection of the generalized metric for the GpK structure. We then used the fact that $D$ preserves $\lara$, $C_\pm$ as well as $\Lb_+$ and that $T$ only has components in $\Lambda^3 C_+\oplus\Lambda^3 C_-$ \cite{Gualtieri:2010fd}.

We will now show that $\rd_{\Lb_+}$ is related to $\rd_\QQ$ via \eqref{eq:d_pi}, so that $\rd_\QQ=(\pi^{-1})^*\circ \rd_{\Lb_+}\circ \pi^*$, i.e.
\begin{align*}
\rd_\QQ\ap(e_1,e_2)=\rd_{\Lb_+}(\pi^*\ap)(\pi^{-1}e_1,\pi^{-1}e_2).
\end{align*}
To read this off from \eqref{dL} and compare with \eqref{eq:dQ}, we need to express $\pi^*\ap$ as $\pi^*\ap=w^*=\la \tl{w},\cdot\ra$ for some $\tl{w}\in\se (\tl{\Lb}_+)$ and $\ap=(\eta(\zt_+),\eta(\zt_-))$:
\begin{align*}
\pi^*\ap=\pi^*(\eta(\zt_+),\eta(\zt_-))=(\eta(\zt_+,\pi_+\cdot),\eta(\zt_-,\pi_-\cdot))=\frac{1}{2}\la\pi^{-1}(\zt_+,-\zt_-),\cdot\ra,
\end{align*}
where $\zt_\pm\in \se(T^{(1,0)_\pm})$ and we used \eqref{pi:gG_relationship}. Therefore, denoting $e_1=(x_+,x_-)$ and $e_2=(y_+,y_-)$ as in \eqref{eq:dQ}, \eqref{dL} yields (denoting $e_1=(x_+,x_-)$ and $e_2=(y_+,y_-)$ as in \eqref{eq:dQ})
\begin{align*}
\rd_{\Lb_+}(&\pi^*\ap)(\pi^{-1}e_1,\pi^{-1}e_2)\\
&=\eta(\n^+_{x_++x_-}\zt_+,y_+)-\eta(\n^+_{y_++y_-}\zt_+,x_+)+\frac{1}{2}T(\pi_+^{-1}x_+,\pi_+^{-1}y_+,\pi_+^{-1}\zt_+)\\
&+\eta(\n^-_{x_++x_-}\zt_-,y_-)-\eta(\n^-_{y_++y_-}\zt_-,x_-)-\frac{1}{2}T(\pi_-^{-1}x_-,\pi_-^{-1}y_-,\pi_-^{-1}\zt_-),
\end{align*}
where we used \eqref{genBismut_pi_nabla_pm} and once again \eqref{pi:gG_relationship}. Finally, invoking \eqref{gentorsion_H}, we arrive at \eqref{eq:dQ}, showing that \eqref{eq:d_pi} holds and completing the proof.
\end{proof}

\subsection{Topological twists of the $(2,2)$-model}

\subsection{The (para)holomorphic twist of the $(2,0)$-model}

\bibliographystyle{JHEP}
\bibliography{mybib}
\end{document}

### 2019-11-22 draft2.tex
Tried to merge
added new intro, section 2 and refs

@@
 \newcommand{\pd}{\p\!\!\!\p}
+\newcommand{\Mb}{\mathbb{M}}
 %----------------------------------------
@@
 \section{Introduction}
-Since the work of (..) \cite{?} it has been known that on any K\"ahler manifold $(M,I,\omega)$, one can define a $2d$ sigma model admitting a $(2,2)$ supersymmetry (SUSY) and such model has a simple local description in terms of the K\"ahler potential.
-Moreover, Witten has shown \cite{?} that such sigma model gives rise to two distinct topological theories -- the A- and B-models -- via a procedure called topological twisting.
-These topological theories have an important interpretation in terms of their underlying geometry: the A-model only depends on the symplectic structure $(M,\omega)$, while the B-model only depends on the complex structure $(M,I)$.
-Additionally, there exists an ${\mathbb Z}_2$ automorphism acting on the original $(2,2)$ supersymmetric theory that exchanges its A- and B-models.
-This is the simplest way one can observe the phenomenon of mirror symmetry in the context of $2d$ sigma models.
-
-The K\"ahler geometry does not describe the most general $(2,2)$ sigma model, as was shown in \cite{Gates-hull-rocek-biherm}.
-Instead, the most general geometry is described by a bi-Hermitian geometry, defined by a pair of complex structures $I_\pm$ compatible with the same Riemannian metric $g$ and satisfying the compatibility relation
-\begin{align*}
-\rd^c_\pm\omega_\pm=\pm H \in \Omega^3_{cl.}(M),
-\end{align*}
-$\omega_\pm$ being the fundamental forms of $I_\pm$ and $\rd^c_\pm$ the associated $\rd^c$-operators.
-For this geometry, the local description is more complicated than in the K\"ahler case, in particular because the analogue of the K\"ahler potential is much harder to describe.
-Consequently, the topological twists are also  more complicated.
-
-This problem is nevertheless partially mitigated by an alternative geometric formulation in terms of generalized K\"ahler (GK) geometry, which has been shown in \cite{Gualtieri:2003dx} to be equivalent to the above-described bi-Hermitian geometry $(g,I_\pm,H)$.
-A GK structure on $M$ is given by the data of two complex endomorphisms $\JJ_\pm$ of the bundle $(\TT)M$:
-\begin{align*}
-\JJ_\pm \in \End((\TT)M),\quad \JJ_\pm^2=-\id, \quad \la \JJ \cdot,\JJ\cdot \ra= \lara,
-\end{align*}
-where $\lara$ denotes the natural duality pairing on $(\TT)M$:
-\begin{align*}
-\la X+\ap,Y+\bt\ra=\ap(Y)+\bt(X),\quad X,Y\in \se(TM),\quad \ap,\bt \in \se(T^*M).
-\end{align*}
-Additionally, $\JJ_\pm$ are required to commute and their product $\GG\coloneqq -\JJ_+\JJ_-$ to define a
+
+In \cite{HullTwistedSUSY}, Abou-Zeid and Hull studied the target geometry of certain $2D$ $(2,2)$ supersymmetric sigma models, which compared to the usual $(2,2)$ supersymmetry differ by a choice of sign in the supercommutator relations of its $4$ real supercharges:
+\begin{align*}
+\{Q_\pm,\tl{Q}_\pm\}=-2\p_\pm,
+\end{align*}
+with all other anti-brackets vanishing.
+The geometry of the target space of these sigma models reflects this sign change and in contrast to complex geometry needed for the usual supersymmetry, the target needs to be para-complex.
+More precisely, the required target geometry must be bi-para-Hermitian.
+In \cite{HullTwistedSUSY}, this type of supersymmetry was dubbed {twisted} SUSY, while the name {pseudo}-SUSY was used in various other works.
+Here we use the name {\bf para-SUSY} to reflect its relationship to para-complex geometry and to reserve the adjective ``twisted'' for the context of topological twists.
+
+Para-complex structure on a manifold $\Mb$ is given by the data of an integrable endomorphism $K \in \End(T\Mb)$ such that $K^2=\id$ and its two eigenbundles corresponding to the $+1$ and $-1$ eigenvalues have the same rank.
+Consequently, $\Mb$ needs to have an even dimension $2n$.
+A para-Hermitian structure on $(\Mb,\eta)$ is then obtained by adding a compatible metric $\eta$:
+\begin{align*}
+\eta(K\cdot,K\cdot)=-\eta(\cdot,\cdot).
+\end{align*}
+This condition forces $\eta$ to be of signature $(n,n)$ and implies that $\omega=\eta K$ is an almost symplectic structure called the fundamental form of $K$.
+A bi-para-Hermitian geometry is then defined as a pair of para-Hermitian structures $(\eta,K_\pm)$ sharing the same metric and satisfying an additional condition
+\begin{align}
+\rd^p_\pm\omega_\pm=\pm H \in \Omega^3_{cl.}(\Mb),
+\end{align}
+where $\rd^p_\pm=K^*\circ \rd\circ K_\pm^*$ is the para-complex twisted differential and $\omega_\pm=\eta K_\pm$ are the fundamental forms of $K_\pm$.
+
+In \cite{Hu:2019zro}, it is shown that the bi-para-Hermitian geometry $(\Mb,\eta,K_\pm,H)$ is equivalent to the data of a generalized para-K\"ahler geometry, which is defined as a pair of {\it generalized} para-complex (GpC) structures $\KK_\pm$ \cite{wade2004dirac,Zabzine:2006uz,Hu:2019zro} on $\Mb$,
+\begin{align*}
+\KK_\pm \in \End((\TT)\Mb), \quad \KK^2=\id, \quad \la \KK\cdot,\KK\cdot\ra=-\la\cdot,\cdot \ra,
+\end{align*}
+that commute and whose product $\GG=\KK_+\KK_-$ defines a split signature metric $G$ on $(\TT)\Mb$ via $G(\cdot,\cdot)=\la \GG\cdot,\cdot\ra$.
+Here, $\la\cdot,\cdot \ra$ is the symmetric duality pairing on $(\TT)M$ and the generalized para-complex endomorphisms $\KK_\pm$ satisfy a Courant integrability condition which ensures that its $\pm 1$-eigenbundles are Dirac structures \cite{courant1990dirac}.
+
+Para-complex and para-Hermitian geometry was also recently studied as the description of the extended geometry in the context of T-duality \cite{freidel2017generalised,Freidel:2018tkj,Svoboda:2018rci,Marotta:2018myj}, following the earlier work of Vaisman \cite{vaisman2012geometry,vaisman2013towards}.
+In \cite{Marotta:2019eqc}, Szabo and Marotta described the bosonic sector of the $2D$ sigma models targeted in this extended geometry.
+Various topological models in the AKSZ framework on the para-Hermitian manifold $\Mb=T^*M\simeq M^n\times \RR^n$ were studied in \cite{Kokenyesi:2018xgj} and $3D$ membrane sigma models with this target were the subject of \cite{Chatzistavrakidis:2018ztm}.
+The generalized geometry corresponding to Para-Hermitian geometry and its refined version, Born geometry, has been studied in \cite{Hu:2019zro}.
+
+\paragraph{Main results} In this paper, we combine the results of \cite{HullTwistedSUSY} and \cite{Hu:2019zro} to study the $2D$ topological sigma models with a generalized para-complex target manifold $(\Mb,\KK_+)$.
+This geometry leads to a $2D$ topological theory via the AKSZ formalism as follows.
+The Courant algebroid $(\TT)\Mb$ defines a $3D$ topological theory with a $2$-shifted symplectic NQ target space $({\cal E},\Omega)$ \cite{Roytenberg:2002nu}.
+Because the $\pm 1$-eigenbundles of $\KK$ are Dirac structures in $(\TT)\Mb$, they each define a Lagrangian in $({\cal E},\Omega)$, which are $1$-shifted symplectic NQ manifolds and as such define a $2D$ topological boundary theories.
+
+Additionally, we show that when the GpC manifold $(\Mb,\KK_+)$ additionally admits a generalized para-K\"ahler structure $(\Mb,\KK_+,\KK_-)$, the topological theories for $(\Mb,\KK_+)$ described above can be realized as topological twists of the $(2,2)$ para-SUSY theory attached to $(\Mb,\KK_\pm)$.
+
+We also present several explicit examples of our construction. The well-known examples include the Poisson sigma model of a real Poisson manifold $(\Mb,\Pi)$ that is described by the GpC structure
+\begin{align*}
+\KK_\Pi=
+\begin{pmatrix}
+\id & 2\Pi \\
+0 & -\id
+\end{pmatrix},
+\end{align*}
+the A-model of a symplectic manifold $(\Mb,\omega)$ described by the GpC structure
+\begin{align*}
+\KK_\omega=
+\begin{pmatrix}
+0 & \omega^{-1} \\
+\omega & 0
+\end{pmatrix},
+\end{align*}
+and also the BFF theory (?) that is simply given by the trivial GpC structure
+\begin{align*}
+\KK_0=
+\begin{pmatrix}
+\id & 0 \\
+0 & -\id
+\end{pmatrix}.
+\end{align*}
+
+The new examples that we describe are all tied to para-complex geometry. They are the para-complex version of the B-model of a para-complex manifold $(\Mb,K)$ that is given by the GpC structure
+\begin{align*}
+\KK_K=
+\begin{pmatrix}
+K & 0 \\
+0 & -K^*
+\end{pmatrix},
+\end{align*}
+and the para-complex topological Landau-Ginzburg model that can be seen as a deformation of the above geometry by a para-holomorphic poisson bi-vector $Q$
+\begin{align*}
+\KK_Q=
+\begin{pmatrix}
+K & Q \\
+0 & -K^*
+\end{pmatrix}.
+\end{align*}
+
+Importantly, our construction can also be applied to the more notoriously known generalized complex (GC) geometry, which was in the context of topological sigma models extensively studied in \cite{Zucchini:2004ta,Ikeda:2004cm,Kapustin:2004gv,Pestun:2006rj,Cattaneo:2009zx} to name some of the works, but to the authors' knowledge a similar construction to ours via a boundary reduction was not proposed before.
+Similarly in the GpC case, the GC structure defines a pair of Dirac structures (that are now tied by complex conjugation) and the $2D$ topological theory is recovered again as a boundary theory of the $3D$ theory defined by the underlying Courant algebroid.
+The advantage of our approach is that it provides a unified way to extract the data of a topological theory from any GC structure via a clear geometric procedure on the underlying shifted symplectic spaces.
+In the special case when the manifold is generalized K\"ahler \cite{Gualtieri:2003dx,Gualtieri:2010fd} -- implying it admits a $(2,2)$ SUSY --  the topological theories can again be realized as topological twists \cite{Kapustin:2004gv} of the $(2,2)$ theory.
+Here, the main examples are given by the A- and B- model corresponding to the GC structures $\JJ_\omega$ and $\JJ_I$, respectively:
+\begin{align*}
+\JJ_\omega=
+\begin{pmatrix}
+0 & -\omega^{-1} \\
+\omega & 0
+\end{pmatrix}, \quad
+\JJ_I=
+\begin{pmatrix}
+I & 0 \\
+0 & -I^*
+\end{pmatrix},
+\end{align*}
+as well as the topological Landau-Ginzburg model which is again viewed via the deformation of $\JJ_I$ by a holomorphic poisson bi-vector \cite{Gualtieri:2007bq} $\sigma=-\frac{1}{4}(IQ+iQ)$:
+\begin{align*}
+\JJ_Q=
+\begin{pmatrix}
+I & Q \\
+0 & -I^*
+\end{pmatrix}.
+\end{align*}
+
+Notice, however, that for example the usual Poisson sigma model cannot be obtained in the realm of GC geometry because no GC structure is defined by a real Poisson structure $\Pi$.
 

### 2019-11-22 draft2.tex
merge

--- 2019-11-21 draft2.tex
@@
 \documentclass{article}
-\usepackage{amssymb, amsmath, amsthm, mathtools, bbm, tikz-cd,stmaryrd,enumerate}
+\usepackage{amssymb, amsmath, amsthm, mathtools, bbm, tikz-cd,stmaryrd,enumerate,hyperref}
 %-------------------
@@
 \newcommand{\kk}{\mathrm{k}}
-\newcommand{\Mt}{\tl{M}}
-\newcommand{\pd}{\p\!\!\!\p}
+\def\fg{\mathfrak{g}}
 %----------------------------------------
@@
 
-\title{Topological Sigma Models for Generalized Para-Complex Geometry}
+\title{Topological Sigma Models from Generalized Para-Complex Geometry}
 
@@
 This is one of the main differences between complex and para-complex geometry; one of the eigenbundles can be integrable while the other is not.
-In such cases, we call $\PS$ {\bf half-integrabile}.
-For more details, see for example \cite{??,??}.
-
-\paragraph{Type decomposition} The splitting of the tangent bundle $T\PS=L\oplus \Lt$ gives rise to a decomposition of tensors analogous to the $(p,q)$-decomposition in complex geometry.
-For differential forms, we denote the decomposition as
+For this reason, it is useful to introduce the notion of {\bf half-integrability}:
+
+%\begin{Def}
+%Let $K$ be an almost para-complex.
+If the $+1$ (respectively $-1$) eigenbundle is Frobenius integrable, we call $K$ a {\bf p-para-complex} (respectively {\bf $n$-para-complex}) structure.
+A $K$ that is both $p$- and $n$- para-complex is simply a para-complex structure.
+%\end{Def}
+
+%\brian{The slash notation complex/product made it really hard to parse the definition since you already put parentheses. 
+%If you want to add a definition for the product case make it another definition, or say "the same definition applies to integrability of product structures.
+%Though, it doesn't seem like we use product structures at all below this, so maybe there is no point.}
+
+\paragraph{Type decomposition} \david{simplify this section} The splitting of the tangent bundle $T\PS=L\oplus \Lt$ in the real case and $T\PS^\Cc$ in the para-complex case gives rise to a decomposition of tensors analogous to the $(p,q)$-decomposition in complex geometry.
+For differential forms, we denote the real and para-complex decompositions as
 \begin{align}\label{eq_plusminus_decomp}
-\Lambda^k (T^*\mathcal{P})&=\bigoplus_{k=m+n}\Lambda^{(m,n)}(T^*\mathcal{P}),
-\end{align}
-where $\Lambda^{(m,n)}(T^*\mathcal{P})=\Lambda^m(T^{*}_{1,0})\otimes \Lambda^n(T^{*}_{0,1})$ and the corresponding sections are denoted by $\Omega^{(m,n)}(\mathcal{P})$.
+\Lambda^k (T^*\mathcal{P})&=\bigoplus_{k=m+n}\Lambda^{(+m,-n)}(T^*\mathcal{P}),\\
+\Lambda^k (T^*\mathcal{P}^\Cc)&=\bigoplus_{k=m+n}\Lambda^{(m,n)}(T^*\mathcal{P}),
+\end{align}
+where $\Lambda^{(+m,-n)}(T^*\mathcal{P})=\Lambda^m(L^*)\otimes \Lambda^n(\Lt^*)$ and $\Lambda^{(m,n)}(T^*\mathcal{P})=\Lambda^m(T^{(1,0)*})\otimes \Lambda^n(T^{(0,1)*})$.
+The corresponding sections are denoted by $\Omega^{(+m,-n)}(\mathcal{P})$ and $\Omega^{(m,n)}$, respectively.
 The bigradings \eqref{eq_plusminus_decomp} yield the natural projections
 \begin{align*}
-\Pi^{(p,q)}:\Lambda^k(T^*\mathcal{P})&\rightarrow \Lambda^{(p,q)}(T^*\mathcal{P}),
-\end{align*}
-so that when $K$ is integrable, the de-Rham differential splits as $\rd=\p+\tl{\p}$, where
+\Pi^{(+p,-q)}:\Lambda^k(T^*\mathcal{P})&\rightarrow \Lambda^{(+p,-q)}(T^*\mathcal{P}),\\
+\Pi^{(p,q)}:\Lambda^k(T^*\mathcal{P}^\Cc)&\rightarrow \Lambda^{(p,q)}(T^*\mathcal{P}),
+\end{align*}
+so that when $K$ is integrable, the de-Rham differential splits as $\rd=\p_++\p_-$, in the real case and $\rd=\p+\bar{\p}$ in the para-complexified case, where
 \begin{align*}
 \begin{array}{cc}
-\p \coloneqq \Pi^{(p+1,q)}\circ \rd, & \tl{\p} \coloneqq \Pi^{(p,q+1)}\circ \rd,
+\p_+ \coloneqq \Pi^{(+p+1,-q)}\circ \rd, & \p_- \coloneqq \Pi^{(+p,-q-1)}\circ \rd,\\
+\p \coloneqq \Pi^{(p+1,q)}\circ \rd, & \bar{\p} \coloneqq \Pi^{(p,q+1)}\circ \rd,
 \end{array}
@@
 are the \textbf{para-complex Dolbeault operators}, satisfying
-\begin{align*}
-\p^2=\tl{\p}^2=\p\tl{\p}+\tl{\p}\p=0.
+%\begin{align}\label{eq:partials_plusminus}
+%\begin{aligned}
+%\p_+&:\Omega^{(+p,-q)}(\mathcal{P})\rightarrow \Omega^{(+p+1,-q)}(\mathcal{P})\\
+%\p_-&:\Omega^{(+p,-q)}(\mathcal{P})\rightarrow \Omega^{(+p,-q-1)}(\mathcal{P}),
+%\end{aligned}
+%\end{align}
+\begin{align*}
+\p_+^2=\p_-^2=\p_+\p_-+\p_-\p_+&=0\\
+\p^2=\bar{\p}^2=\p\bar{\p}+\bar{\p}\p&=0
 \end{align*}
@@
 
-\paragraph{Para-Holomorphic structure}
-Let now $(\mathcal{P},K)$ be an almost para-complex manifold of dimension $2n$.
-If $K$ is integrable, we get a set of $2n$ coordinates $(x^i,\tilde{x}_i)$ called {\bf adapted coordinates}, $\mathcal{P}$ locally splits as $M\times \tilde{M}$, and $K$ acts as identity on $TM=L$ and negative identity on $T\tilde{M}=\tilde{L}$.
-The adapted coordinates therefore define two complimentary foliations that we will call {\bf canonical foliations} of the para-complex manifold $\PS$ and denote $M$ and $\Mt$.
-Both $M$ and $\Mt$ are therefore $n$-dimensional manifolds composed of connected components called leafs $M_i$, $\Mt_i$:
-\begin{align*}
-M=\bigcup_i M_i,\quad \Mt=\bigcup_i \Mt_i,
-\end{align*}
-and each are as sets equal to $\PS$.
-
-As usual, a map of para-complex manifolds is called para-holomorphic if its pushforward commutes with the respective para-complex structures
-\begin{Def}
-Let $(M,K_M)$ and $(N,K_N)$ be para-complex manifolds. A map $F:M\rightarrow N$ is called para-holomorphic if
-\begin{align}\label{eq:def_parahol}
-K_N\circ F_*=F_*\circ K_M
-\end{align}
-\end{Def}
-\begin{remark}
-In the following we will omit the prefix ``para-'' in para-holomorphic whenever no confusion with complex holomorphicity is possible.
-\end{remark}
-
-Locally, the map $F:M\rightarrow N$ of para-complex manifolds can be understood via composition of coordinates as a
-\begin{align*}
-F&: \RR^{2n}\rightarrow \RR^{2m}\\
-F=(f^i,\tl{f}_j)&=(y^i(x^k,\xt_l),\yt_j(x^k,\xt_l))^{i,j=1,\cdots,m}_{k,l=1,\cdots, n}, 
-\end{align*}
-where $(x^k,\xt_l)$ and $(y^i,\yt_j)$ are adapted local coordinates on $M$ and $N$, respectively.
-It is easy to check from \eqref{eq:def_parahol} that $F$ is a holomorphic map iff the components satisfy
-\begin{align}\label{eq:holomorphic_real}
-\frac{\p}{\p \xt_i}f^j=\frac{\p}{\p x^i}\tl{f}_j=0.
-\end{align}
-
-The conditions \eqref{eq:holomorphic_real} tell us that the holomorphic functions map the canonical foliations of the para-complex manifolds $M$ and $N$.
-This also means that the transition functions on a para-complex manifold (seen as maps $\RR^{2n}\rightarrow \RR^{2m}$) are holomorphic since the foliations must be preserved, i.e.
-the coordinates transform as
-\begin{align}\label{para-coordinate-transf}
-(x^i,\xt_i)\mapsto (y^j(x^i),\yt_j(\xt_i)).
-\end{align}
-
-This also gives us an intuition into what holomorphic bundles and their holomorphic sections look like.
-First, we notice that the tangent bundle $T\PS$ itself is a holomorphic bundle (see for example \cite{Cortes:2003zd,Hu:2019zro}); this is simply because of the form of the transition functions \eqref{para-coordinate-transf} that induce a holomorphic structure on the tangent bundle.
-The holomorphic sections of $T\PS$ -- the holomorphic vector fields -- are locally of the form
-\begin{align*}
-X= X^i(x)\p_i+\tl{X}_i(\xt)\pt^i,
-\end{align*}
-i.e. the components in $L$ and $\Lt$ individually define vector fields on the foliations $M$ and $\Mt$, respectively.
-
-Similarly, the cotangent bundle is a holomorphic bundle.
-For the higher wedge powers, we find that only $\Lambda^{(k,0)+(0,k)}(T^*\PS)$, $1\leq k\leq n$, are holomorphic bundles.
-The {\bf para-complex Dolbeault complex} is therefore given by
-\begin{align}
-\left(\Omega^{(\bullet,0)}\otimes\Omega^{(0,\bullet)},(\p,\pt)\right)\coloneqq \left(\mathbf{\Omega}^{\bullet,0},\pd\right).
-\end{align}
 %\begin{lemma}
@@
 \subsection{Generalized para-geometry}
+
+\brian{motivate generalized geometry through courant algebroids}
+
+\brian{get rid of repetitions and references to dg / NQ manifolds.}
+
 In this paper, the term {\it generalized geometry} is used for the study of geometric \brian{geometrical is not a word} structures on the bundle $TM \oplus T^*M$ over some manifold $M$.
@@
 
+For now, we record a relationship between generalized paracomplex structures and Courant algebroids.
+
+\subsubsection{Background on Courant algebroids}
+
+Recall, a Courant algebroid on a manifold $M$ is a vector bundle $E$, whose sheaf of sections we denote $\cE$, together with a nondegenerate symmetric bilinear pairing $\langle -, -\rangle : \cE \otimes \cE \to C^\infty(M)$ , an anchor map $a : E \to T M$, and a bilinear operator
+\[
+[-,-] : \cE \times \cE \to \cE
+\]
+called the Courant-Dorfman bracket. 
+\brian{spell out properties, find a good reference}
+Denote by $a^* : T^* M \to E^*$ the bundle map dual to $a$.
+
+To every Courant algebroid we can define the following sequence of vector bundles on $M$
+\[
+T^*M \xto{a^*} E \xto{a} TM .
+\]
+A Courant algebroid is called {\em exact} if this sequence of bundles is exact.
+
+The simplest type of Courant algebroid is one over a point.
+
+\begin{Ex}\label{ex: cs}
+Any Lie algebra $\fg$ together with a non-degenerate invariant pairing defines a $2$-shifted symplectic structure on the graded manifold $\fg[1]$ living over a point. 
+The dg algebra of functions is the Chevalley-Eilenberg cochain complex computing Lie algebra cohomology $C^*(\fg)$. 
+All such $2$-symplectic NQ manifolds over a point are of this form. 
+%The resulting AKSZ theory is Chern-Simons theory. 
+\end{Ex}
+
+\paragraph{The $2$-shifted symplectic space of an exact Courant Algebroid}
+
+We recall the description of the $2$-shifted symplectic NQ manifold $X_E$ associated to an exact Courant algebroid $E$.
+Of course, as a vector bundle $E = \TT$, and hence as a graded manifold $X_E$ is of the form $T^*[2] T[1] M$.
+Concretely, the coordinates on this manifold are given by $(x^i,v^a,p_i,\mu_a)_{i,a=1\cdots n}$, where $x^i$ are the usual coordinates on $M$ with degree $0$, $v^a$ are the corresponding ``velocities'', i.e.
+the fibre coordinates on $T[1]M$ with a degree $1$, and $p_i,\mu_a$ are the momenta corresponding to $x^i,v^a$ with degrees $2,1$, respectively.
+The canonical symplectic form
+\begin{align*}
+\Omega= dx^idp_i+dv^ad\mu_a,
+\end{align*}
+is then of degree $2$.
+$T^*[2]T[1]M$ is the minimal symplectic realization of the shifted bundle $(\TT)[1]M$, which is recovered by setting $p_i=0$.
+The symmetric part of $\Omega$ represents the pairing $\lara$ on $(\TT)M$; this is because we can identify $d\mu_a\leftrightarrow \p_i$ and $dv^a\leftrightarrow dx^i$
+
+\brian{Severa classification}
+
+\begin{theorem}\label{thm: severa}
+The set of isomorphism classes of exact Courant algebroids is a torsor for $H^3(X)$. 
+\end{theorem}
+
+\paragraph{The Poisson Courant algebroid}
+
+\brian{Both real and holomorphic versions}
+
 \subsubsection{The exact Courant algebroid structure}
-\brian{David, how do you feel about moving this later in the Courant/AKSZ section?}
-We recall basic facts about Courant algebroids in Section \ref{sec: courant}. 
-For now, we record a relationship between generalized paracomplex structures and exact Courant algebroids.
 
@@
 
-The Courant algebroid on $\TT$ is exact, meaning that the associated sequence
-\begin{align}\label{eq:exact_seq}
-0\longrightarrow T^* \overset{\pi^T}{\longrightarrow} \TT\overset{\pi}{\longrightarrow} T\longrightarrow 0,
-\end{align}
-is exact. Here, $\pi^T$ is the transpose of $\pi$ with respect to the pairing $\lara$,
-%\begin{align*}
-%\la \pi^T(\ap),Y+\bt\ra=\la \ap,\pi(Y+\bt)\ra=\la \ap,Y\ra
-%\end{align*}
-i.e.
-$\pi^T: \ap \mapsto \ap+0$.
+The Courant algebroid on $\TT$ is exact
 In fact, all possible Courant algebroid structures on $\TT$ are parametrized by a closed three-form $H\in \Omega^3_{cl}$, which enters the definition of the bracket \eqref{eq:dorfman}, changing it to a {\it twisted} Dorfman bracket
@@
 This also amounts to setting $b=0$ in all formulas since the $b$-field appears as a difference of two splittings.
-
-\subsection{Generalized para-K\"ahler geometry}
-\brian{I don't think this should be the title of this section. It's mostly about paracomplex geometry}
 
@@
 
+\subsection{Generalized para-K\"ahler geometry}
+\brian{add buffer}
+
 \begin{Def}
@@
 \begin{remark}
+\brian{maybe this should go later?}
 The most general $2D$ $(1,1)$ sigma model on a pseudo-Riemannian target $(M,g)$ is locally given by the action functional
@@
 
-\subsubsection{SKT Geometry and half generalized structures}
-\david{will see if we'll be using this}
-An {\bf SKT} structure is a Hermitian structure $(I,g)$ for which the fundamental form $\omega$ even though is not closed, is $\rd \rd^c$-closed, i.e.
-$\rd \rd^c \omega=0$.
-The version of this geometry is easily formulated for the para- case where we will call it para-SKT.
-It follows directly from the definition that the bi-para-Hermitian geometry consists of two such structures -- one for each chirality -- and here we will describe how one SKT structure can be described using the language of generalized geometry.
-
-For this purpose we define a positive-chirality\footnote{Similarly one could define a negative-chirality half G(p)C structure by changing $C_+$ for $C_-$} {\bf half generalized almost (para-)complex structure} as a pair $(\GG,\JJ_{C_+})$, where $\GG$ is a (neutral) generalized metric which induces a splitting $\TT=C_+\oplus C_-$ and an isomorphism $C_+\oplus C_-\simeq T\oplus T$, and $\JJ_{C_+}$ is a (para-)complex endomorphism of $C_+$, i.e.
-\begin{align*}
-\JJ_{C_+}\in \End(C_+),\quad \JJ_{C_+}=\pm \id_{C_+},\quad \la \JJ_{C_+} u_+,v_+\ra=-\la u_+,\JJ_{C_+} v_+\ra,
-\end{align*}
-for any $u_+,v_+ \in \se(C_+)$.
-The integrability condition on $\JJ_{C_+}$ is then that its eigenbundles $\ell_+\oplus \ell_-=C_+$ (in the complex case $\ell\oplus \bar{\ell}=C_+\otimes \mathbb{C}$) are involutive with respect to the (twisted) Dorfman bracket.
-It is easy to see that $\JJ_{C_+}$ defines a (para-)Hermitian structure $(J_+,g)$, where
-\begin{align*}
-g(X,Y)=\frac{1}{2}\la \pi_+^{-1}X,\pi_+^{-1}Y\ra,\quad J_+=\pi_+\JJ_{C_+}\pi^{-1}_+
-\end{align*}
-and the integrability condition on $\JJ_{C_+}$ translates into the condition
-\begin{align*}
-\n^+J_+=0,\ \n^+=\lc+\frac{1}{2}g^{-1}(H+\rd b) \Longleftrightarrow \rd^{c/p}\omega_+=H+\rd b,
-\end{align*}
-i.e.
-giving exactly half of the data of a G(p)K geometry.
-If there is a negative-chirality half structure $\JJ_{C_-}$, then $(\GG,\JJ\coloneqq \JJ_{C_+}\oplus \JJ_{C_-})$ defines a genuine G(p)K structure.
-
 \section{Two-dimensional parasupersymmetry}  \label{sec: parasusy}
@@
 
-\subsection{$(2,2)$ parasupersymmetry}
+\subsection{$(2,2)$ para-supersymmetry}
+\david{Import paragraph on (2,2)}
 
 \brian{point to references who have also discussed versions of (2,2) para susy}
-The {\bf (2,2) parasupersymmetry algebra} has the underlying supervector space
+
+\begin{Def}
+The {\bf (2,2) para-supersymmetry algebra} has the underlying supervector space
 \[
@@
 \end{equation}
+\end{Def}
 
@@
 \subsubsection{R-symmetry}
+\david{Move to mirror symmetry speculation section}
+
 We have seen above that the $(2,2)$ para-SUSY algebra $\mathfrak{t}_{(2,2)}$ can be diagonalised in terms of the charges\footnote{Note that for the usual $(2,2)$ SUSY one cannot diagonalize the algebra over $\RR$.}
@@
 }
+\brian{maybe leave this as a remark that we are aware of this...but we don't need it.}
 
@@
 which determines a symmetry by the $(2,1)$ parasupersymmetry algebra.
+
+\brian{SKT, Witten-Hull}
 
@@
 
-\section{The AKSZ formalism and 3d TFT}
-\def\fg{\mathfrak{g}}
-In this section we will show how to associate $2D$ topological theories to a generalized (para-)complex structure and relate them to the topological twists of $2D$ $(2,2)$ (para-)SUSY sigma models described in Section \ref{sec:toptwist} and in \cite{Kapustin:2004gv}.
+\section{AKSZ and generailzed para-geometry}
+
+In this section we will show how to associate $2D$ topological theories to a generalized (para-)complex structure.
+Later on, in Section \ref{sec:toptwist}, we relate these theories to topological twists of $2D$ $(2,2)$ para-SUSY sigma models introduced in Section \ref{sec: parasusy}. 
+%and in \cite{Kapustin:2004gv}. 
 The key to our construction is to realize the data of a G(p)C structure in terms of its eigenbundles, which are Dirac structures $L$ in the Courant algebroid $\TT$. 
@@
 For a reference, see \cite{Roytenberg:2002nu,??}.
+Later we will use the idea of Lagrangian intersections \brian{Toen, ButsonYoo, Costello,...}.
 
@@
 
-We briefly recall this construction.
-
-Recall, the data of a Courant algebroid on a manifold $M$ is a vector bundle $E$, whose sheaf of sections we denote $\cE$, together with a nondegenerate symmetric bilinear pairing $\langle -, -\rangle : \cE \otimes \cE \to C^\infty(M)$ , an anchor map $a : E \to T M$, and a bilinear operator
-\[
-[-,-] : \cE \times \cE \to \cE
-\]
-called the Courant-Dorfman bracket. 
-\brian{spell out properties, find a good reference}
-Denote by $a^* : T^* M \to E^*$ the bundle map dual to $a$.
-
-To every Courant algebroid we can define the following sequence of vector bundles on $M$
-\[
-T^*M \xto{a^*} E \xto{a} TM .
-\]
-A Courant algebroid is called {\em exact} if this sequence of bundles is exact.
+We briefly recount this construction.
 
@@
 
-The simplest type of Courant algebroid is one over a point.
-
-\begin{Ex}\label{ex: cs}
-Any Lie algebra $\fg$ together with a non-degenerate invariant pairing defines a $2$-shifted symplectic structure on the graded manifold $\fg[1]$ living over a point. 
-The dg algebra of functions is the Chevalley-Eilenberg cochain complex computing Lie algebra cohomology $C^*(\fg)$. 
-All such $2$-symplectic NQ manifolds over a point are of this form. 
-%The resulting AKSZ theory is Chern-Simons theory. 
-\end{Ex}
-
-\subsubsection*{The $2$-shifted symplectic space of an exact Courant Algebroid}
-
-We recall the description of the $2$-shifted symplectic NQ manifold $X_E$ associated to an exact Courant algebroid $E$.
-Of course, as a vector bundle $E = \TT$, and hence as a graded manifold $X_E$ is of the form $T^*[2] T[1] M$.
-Concretely, the coordinates on this manifold are given by $(x^i,v^a,p_i,\mu_a)_{i,a=1\cdots n}$, where $x^i$ are the usual coordinates on $M$ with degree $0$, $v^a$ are the corresponding ``velocities'', i.e.
-the fibre coordinates on $T[1]M$ with a degree $1$, and $p_i,\mu_a$ are the momenta corresponding to $x^i,v^a$ with degrees $2,1$, respectively.
-The canonical symplectic form
-\begin{align*}
-\Omega= dx^idp_i+dv^ad\mu_a,
-\end{align*}
-is then of degree $2$.
-$T^*[2]T[1]M$ is the minimal symplectic realization of the shifted bundle $(\TT)[1]M$, which is recovered by setting $p_i=0$.
-The symmetric part of $\Omega$ represents the pairing $\lara$ on $(\TT)M$; this is because we can identify $d\mu_a\leftrightarrow \p_i$ and $dv^a\leftrightarrow dx^i$
-
-\brian{Severa classification}
-
-\begin{theorem}\label{thm: severa}
-The set of isomorphism classes of exact Courant algebroids is a torsor for $H^3(X)$. 
-\end{theorem}
-
-\subsubsection*{The Poisson Courant algebroid}
-
-\brian{Both real and holomorphic versions}
-
 \subsubsection{The AKSZ theory associated to a Courant algebroid}
 
-To any Courant algebroid $E$, we can associate an NQ manifold $X_E$ which carries a $2$-shifted symplectic structure that we denote by $\omega_E$. 
+To any Courant algebroid $E$, we associate an NQ manifold $X_E$ which carries a $2$-shifted symplectic structure. 
 In the case that the Courant algebroid is exact, call the associated $2$-shifted symplectic space $X_H$, where $H$ labels the Severa class.
@@
 where $(M, (\sA^*_M, \d_M))$ is a dg manifold with body a smooth oriented manifold $M$. 
-That is, $\sA^*_M$ is a sheaf of graded commutative algebras over the de Rham complex $\Omega^*_M$ and $\d_M$ is a linear operator of degree $+1$ satisfying:
+That is, $\sA^*_M$ is a sheaf of graded commutative algebras over the de Rham complex $\Omega^*_M$ and $\d_M$ is a linear differential operator of degree $+1$ satisfying:
 \begin{itemize}
@@
 \begin{Ex}
-The most important example for us will be the source dg manifold $(M, \Omega^*_M)$, that is $\sA_M = \Omega^*_M$ with de Rham differential. 
+The most important example for us will be the source dg manifold $(M, \Omega^*_M)$, that is $\sA_M = \Omega^*_M$ equipped with de Rham differential. 
 We denote this dg manifold by $M_{\rm dR}$.
@@
 \subsubsection{Dirac structures and boundary conditions}
+
+The AKSZ formalism is a construction which produces a $(-1)$-shifted symplectic space from the data of a closed manifold and a target shifted symplectic manifold. 
+There is a generalization of this construction which produces $(-1)$-shifted symplectic spaces on manifolds with boundary.
+
+Suppose $M$ is a manifold with boundary, and let $\cE(M)$ denote the space of fields of a classical theory on $M$. 
+For instance, $\cE(M)$ will be a mapping space of the form ${\rm Map}(M, X)$ where $X$ is shifted symplectic. 
+Let $\cE(\partial M)$ denote the restriction of the fields to the boundary of $M$. 
+For the mapping space example, this is simply the space of maps ${\rm Map}(\partial M, X)$.
 

### 2019-11-22 draft2.tex
merge2

@@
 Suppose $M$ is a manifold with boundary, and let $\cE(M)$ denote the space of fields of a classical theory on $M$. 
-For instance, $\cE(M)$ will be a mapping space of the form ${\rm Map}(M, X)$ where $X$ is shifted symplectic. 
+For us, $\cE(M)$ will be a mapping space of the form ${\rm Map}(M, X)$ where $X$ is shifted symplectic. 
 Let $\cE(\partial M)$ denote the restriction of the fields to the boundary of $M$. 
 For the mapping space example, this is simply the space of maps ${\rm Map}(\partial M, X)$.
+
+In general, when $M$ is not closed, $\cE(M)$ will not carry a $(-1)$-shifted symplectic structure.
+However,
 

### 2019-11-22 oldstuff/aksz.tex
merge

\documentclass{article}
\usepackage{amssymb, amsmath, amsthm, mathtools, bbm, tikz-cd,stmaryrd,enumerate}
%-------------------
\usepackage{fancyhdr}
\pagestyle{fancy}
\fancyhf{}
\fancyhead[L]{\leftmark}
\fancyhead[R]{\thepage}
%----------------
\newcommand{\TT}{{T\oplus T^*}}
\newcommand{\JJ}{\mathcal{J}}
\newcommand{\KK}{\mathcal{K}}
\newcommand{\GG}{\mathcal{G}}
\newcommand{\Cc}{\mathbf{C}}
\newcommand{\RR}{\mathbb{R}}
\newcommand{\XX}{\mathfrak{X}}
\newcommand{\HH}{\mathcal{H}}
\newcommand{\FF}{\mathcal{F}}
\newcommand{\QQ}{\mathcal{Q}}
\newcommand{\LL}{\mathcal{L}}
%----------------------------------------
\newcommand{\PP}{\mathrm{P}}
\newcommand{\PPt}{\tilde{\mathrm{P}}}
\newcommand{\id}{\mathbbm{1}}
\newcommand{\nlr}{\overset{\leftrightarrow}{\n}}
\newcommand{\lc}{\mathring{\n}}
\newcommand{\im}{\mathrm{Im}\,}
\newcommand{\Ker}{\mathrm{Ker}\,}
\newcommand{\Lie}{\mathcal{L}}
\newcommand{\PS}{\mathcal{P}}
\newcommand{\ap}{\alpha}
\newcommand{\bt}{\beta}
\def\w{\wedge}
\newcommand{\p}{\partial}
\newcommand{\pt}{\tilde{\partial}}
\newcommand{\xt}{{\tilde{x}}}
\newcommand{\n}{\nabla}
\newcommand{\rd}{\mathrm{d}}
\newcommand{\PH}{(\PS,\eta,\omega)}
\newcommand{\Lt}{\tl{L}}
\newcommand{\Lb}{\mathbf{L}}
\newcommand{\s}{\mathbf{s}}
\newcommand{\se}{\Gamma}
\newcommand{\Endo}{\text{End}}
\newcommand{\ellt}{{\tl{\ell}}}
\newcommand{\ot}{{1/2}}
\newcommand{\inv}{{-1}}
\newcommand{\Aa}{\mathcal{A}}
\newcommand{\la}{\langle}
\newcommand{\ra}{\rangle}
\newcommand{\lara}{\la\ ,\ \ra}
\newcommand{\brac}{[\ ,\ ]}
\newcommand{\bl}{[\![}
\newcommand{\br}{]\!]}
\newcommand{\bracd}{\bl \ ,\ \br}
\newcommand{\yt}{\tl{y}}
\newcommand{\zt}{\tl{z}}
\newcommand{\tth}{\tl{\theta}}
\newcommand{\kk}{\mathrm{k}}
\newcommand{\bu}{\bullet}

\def\d{{\rm d}}

\def\brian{\textcolor{blue}{BW: }\textcolor{blue}}
\def\david{\textcolor{green}{DS: }\textcolor{green}}
%----------------------------------------
\def\gld{generalized Lie derivative }
\def\glds{generalized Lie derivatives }
\def\tl{\tilde}

% These will be typeset in italics
\newtheorem{theorem}{Theorem}[section]
\newtheorem{proposition}[theorem]{Proposition}
\newtheorem{lemma}[theorem]{Lemma}
\newtheorem{corollary}[theorem]{Corollary}
\newtheorem{fact}[theorem]{Fact}
\newtheorem*{theorem*}{Theorem}
\newtheorem*{lemma*}{Lemma}
\newtheorem*{proposition*}{Proposition}
\newtheorem{Rem}[theorem]{Remark}

% These will be typeset in Roman
\theoremstyle{definition}
\newtheorem{Def}[theorem]{Definition}
\newtheorem{Conj}[theorem]{Conjecture}

\theoremstyle{definition}
\newtheorem*{notation*}{Notation}
\newtheorem*{definition*}{Definition}

\theoremstyle{remark}
\newtheorem*{remark*}{Remark}
\newtheorem{Ex}[theorem]{Example}
\newtheorem{question}[theorem]{Question}
\newenvironment{claim}[1]{\par\noindent\underline{Claim:}\space#1}{}
\newenvironment{claimproof}[1]{\par\noindent\underline{Proof:}\space#1}{\hfill $[acksquare$}

\input xy

\xyoption{all}

\DeclareMathOperator{\End}{End}
\DeclareMathOperator{\rk}{rk}

\begin{document}
\section{AKSZ stuff}

\subsection{Two-dimensional TFT from GC structures}

In this section, we summarize the work of Kapustin-Li in the AKSZ formalism with an eye towards modification in the para geometric setting.

\subsubsection{A recollection of generalized complex geometry}

Recall, an exact Courant algebroid on a smooth manifold $X$ is determined, up to equivalence, by a class $H \in H^1(X, \Omega^2_{cl})$, called its Severa class, or $H$-flux. 
The underlying vector bundle of an exact Courant algebroid is $TX \oplus T^*X$, and the $H$-flux deforms the standard Dorfman bracket.

An almost generalized complex structure on a manifold $X$ is the data of a smooth bundle map
\[
\JJ : TX \oplus T^*X \to TX \oplus T^*X
\]
satisfying $\JJ^2 = - \id$ and $\langle\JJ u, \JJ v\rangle = \langle u,v\rangle$, where $\langle-,-\rangle$ denotes the obvious pairing between the tangent and cotangent bundle.
Given an almost generalized complex structure, we denote by $L \subset T X^{\Cc} \oplus T^* X^{\Cc}$ the complex $+i$ eigenbundle of $\JJ$.

Fix an exact Courant algebroid on $X$ with class $H$. 
An almost generalized complex structure on $X$ is an $H$-{\em twisted generalized complex structure} if the subbundle $L$ is preserved under the $H$-twisted Dorfman bracket. 
An $H$-twisted generalized complex structure is equivalent to an $H$-twisted complex Dirac structure $L$ \footnote{A complex Dirac structure is a maximally isotropic involutive subbundle of the exact complex Courant algebroid $TX^{\Cc} \oplus T^*X^{\Cc}$} satisfying $L \cap \Bar{L} = \{0\}$. 
When $H = 0$, one simply calls this a generalized complex structure.

\begin{Ex}\label{ex: complexstr}
Every almost complex structure on $X$ determines an almost generalized complex structure on $X$. 
It is a generalized complex structure if the almost complex structure is integrable.

In fact, consider the almost generalized complex structure
\begin{align*}
\JJ=
\begin{pmatrix}
I & 0 \\
0 & -I^*
\end{pmatrix},
\end{align*}
where $I : TX \to TX$ is an almost complex structure, and $I^*$ is the dual bundle map.
The $+i$ eigenbundle is $L=T^{(1,0)}\oplus T^{*(0,1)}$ and the $-i$ eigenbundle is $\bar{L}=T^{(0,1)}\oplus T^{*(1,0)}$. 
Involutivity of $L$ under $\brac_H$ is equivalent to the condition
\begin{align*}
[X+\bar{\ap},Y+\bar{\bt}]=[X,Y]+\Lie_X\bar{\bt}-\imath_Y\rd \bar{\ap}+H(X,Y),
\end{align*}
where $X,Y\in \XX^{(1,0)}$ and $\bar{\ap},\bar{\bt}\in \Omega^{(0,1)}$.
This implies that one must have have $[X,Y]\subset T^{(1,0)}$, meaning $I$ must be a complex structure. 
Moreover, inspecting the cotangent component of the above and splitting $\rd=\p+\bar{\p}$, the non-zero components are
\begin{align*}
\imath_X(\p\bar{\bt})-\imath_Y(\p \bar{\ap})+H(X,Y),
\end{align*}
where $\imath_X\p\bar{\bt}-\imath_Y\p \bar{\ap}$ is always in $T^{*(0,1)}$ and so $H(X,Y)$ must be in $T^{*(0,1)}$ as well, i.e. the $(3,0)$ component of $H$ must vanish. The same argument for $\bar{L}$ gives $H^{(0,3)}=0$.
\end{Ex}

\begin{Ex}
Suppose $\omega \in \Omega^2(X)$ is a nondegenerate $2$-form.
Then, $\omega$ determines an almost generalized complex structure on $X$.
It is a generalized complex structure for $H = \d \omega$.
In particular, every symplectic structure determines a generalized complex structure for $H = 0$.

Indeed, define the almost generalized complex structure
\begin{align*}
\JJ=
\begin{pmatrix}
0 & -\omega^{-1} \\
\omega & 0
\end{pmatrix},
\end{align*}
With eigenbundles given by $X\pm i\omega(X)$ for any $X\in \XX$. Checking the involutivity of these under $\brac_H$:
\begin{align*}
[X\pm i\omega(X),Y\pm i\omega(Y)]=[X,Y]\pm i \omega([X,Y])\pm i\rd \omega (X,Y)+H(X,Y),
\end{align*}
where some identities for Lie derivatives etc. have been used. Clearly $[X,Y]\pm i \omega([X,Y])$ is of the desired form and the remaining terms are in $\Omega^1$ so they have to vanish (cannot be of the form $Z\pm i \omega(Z)$). This gives
\begin{align*}
i\rd \omega (X,Y)+H(X,Y)=0 
\end{align*}
for all $X,Y$. 
\end{Ex}

More generally, one can speak of (almost) generalized complex structures in {\em any} (possibly non exact) Courant algebroid. 
If $E$ is the underlying vector bundle of the Courant algebroid, then an almost generalized complex structure is a bundle map $\JJ : E \to E$ satisfying the same conditions as above, namely $\JJ^2 = - \id$ and $\langle\JJ u, \JJ v\rangle = \langle u,v\rangle$.
It is a generalized complex structure if it is integrable for the bracket defining the Courant algebroid.

Analogous to the exact case, we have the following equivalent characterization of generalized complex structures in $E$.

\begin{proposition}
A generalized complex structure in a Courant algebroid $E$ is equivalent to a Dirac structure $L$ in the complex Courant algebroid $E^{\Cc}$ satisfying $L \cap \Bar{L} = 0$. 
\end{proposition}

\brian{Should I define what a Dirac structure in a general CA is?}

\subsubsection{The associated Lie algebroid and cohomology}

To any (twisted) generalized complex structure there exists a naturally associated (complex) Lie algebroid defined as follows.

Let $\JJ$ be an $H$-twisted generalized complex structure and $\Bar{L} \subset T X^{\Cc} \oplus T^* X^{\Cc}$ the complex $-i$ eigenbundle.
\brian{I think we want to use the $-i$ eigenbundle.}
While the Dorfman bracket does {\em not} define a Lie bracket on $T X^{\Cc} \oplus T^* X^{\Cc}$ it does define one on the subbundle $L$.
Indeed, by definition $\Bar{L}$ is isotropic and integrable, so the Jacobi identity is satisfied. 
The anchor map $a : \Bar{L} \to T X^{\Cc}$ is given by the restriction of the natural projection $T X^{\Cc} \oplus T^* X^{\Cc} \to T X^{\Cc}$ to $L$. 
We denote this Lie algebroid by $\Bar{L}_{\JJ, H}$.

We define {\em cohomology} of an $H$-twisted generalized complex structure $\JJ$ to be the Lie algebroid cohomology of $L_{\JJ, H}$.

\begin{Ex}
When the generalized complex structure $\JJ$ is defined using an ordinary complex structure, as in Example \ref{ex: complexstr} the resulting Lie algebroid is given by 
\[
\Bar{L}_{\JJ, H} = T^{0,1} X \to T X^{\Cc} .
\]
The cohomology of the twisted generalized complex structure is equal to the Dolbeault cohomology $H^{0,*}(X)$. 
\end{Ex}

More generally, there is a (complex) Lie algebroid associated to a generalized complex structure $\JJ$ in any (possibly non exact) Courant algebroid $E$. 
Again, we define $\Bar{L} \subset E^{\Cc} $ to be the $-i$ eigenspace of $\JJ$. 
The same argument as in the exact case shows that $\Bar{L}$ has a natural Lie algebroid structure, where bracket is given by restricting the bracket of $E$ defining the Courant algebroid structure, and the anchor map is given by the composition
\[
a : \Bar{L} \hookrightarrow E^{\Cc} \to T X^{\Cc} .
\]
We denote the resulting Lie algebroid by $\Bar{L}_{\JJ, E}$, and define the cohomology of $\JJ$ to be the Lie algebroid cohomology of $\Bar{L}_{\JJ,E}$.

\subsubsection{The AKSZ theory}

\def\fg{\mathfrak{g}}

From the point of view of topological field theory, Courant algebroids are important because they provide geometric examples of $2$-shifted symplectic spaces. 
Via the AKSZ construction, $2$-shifted symplectic spaces are the natural home for $3$-dimensional topological field theories in the BV formalism.

\begin{Ex}
Any Lie algebra together with a non-degenerate invariant pairing defines a $2$-shifted symplectic structure on the classifying stack $B \fg$. 
The resulting AKSZ theory is Chern-Simons theory. 
\end{Ex}

To any Courant algebroid $E$, we can associate a derived stack $\XX_E$ which carries a $2$-shifted symplectic structure $\omega_E$. 
In the case that the Courant algebroid is exact, we denote the $2$-shifted symplectic space as $\XX_H$ where $H$ is the Severa class.

To a compact, oriented $3$-manifold $M^3$ the AKSZ construction endows the derived mapping space 
\[
{\rm Map}(M^3 , \XX_E) 
\]
with a BV structure.

\brian{Recall Lagrangian of a stack.}

An $H$-twisted generalized complex structure $\JJ$ defines a complex Dirac structure on $TX^{\Cc} \oplus T^*X^{\Cc}$, and hence a $2$-shifted Lagrangian inside of the $2$-shifted symplectic space $\XX_H$.  
More generally, if $\JJ$ is a generalized complex structure in an arbitrary Courant algebroid $E$, then we obtain a $2$-shifted Lagrangian inside of the $2$-shifted symplectic space $\XX_E$.

The Lagrangian in $\XX_E$ associated to a generalized complex structure $\JJ$ defines a boundary condition for the three-dimensional AKSZ theory. 
In the case the the Courant algebroid is exact, the resulting boundary theory is the generalized $A/B$-model of \cite{KapustinLi}.

\subsection{Two dimensional TFT from GpC structures}

The goal in this section is to describe a construction of a two-dimensional topological field theory from the data of a generalized para complex structure. 
This construction is analogous to the generalized A/B-model of \cite{KapustinLi} that we have just recollected.

\end{document}

### 2019-11-22 oldstuff/draft.tex
merge

--- 2019-11-22 draft2.tex
@@
 \newcommand{\kk}{\mathrm{k}}
-\newcommand{\Mt}{\tl{M}}
-\newcommand{\pd}{\p\!\!\!\p}
-\newcommand{\Mb}{\mathbb{M}}
 %----------------------------------------
@@
 
-\title{Topological Sigma Models for Generalized Para-Complex Geometry}
+\title{Twisted parasupersymmetry and paracomplex geometry}
 
@@
 \maketitle
-\begin{abstract}
-We study a class of $2d$ topological sigma models that are formulated on generalized para-complex target manifolds via the AKSZ framework.
-When the target is additionally generalized para-K\"ahler, these topological theories can be realized as topological twists of $(2,2)$ para-supersymmetric sigma models of Abou-Zeid and Hull.
-We compare our results to the case of generalized complex and generalized K\"ahler geometry, where similar results have been described in the context of the usual $(2,2)$ SUSY by Kapustin and Li.
-We present several examples and show that our construction recovers the A-model and the Poisson sigma model as special cases.
-Moreover, we also introduce new examples of topological theories inherently tied to the para-complex geometry, the para-B-model and a para-complex version of the Landau-Ginzburg model.
-
-\end{abstract}
-\newpage
+
 \tableofcontents
-\newpage
+
 \section{Introduction}
-
-In \cite{HullTwistedSUSY}, Abou-Zeid and Hull studied the target geometry of certain $2D$ $(2,2)$ supersymmetric sigma models, which compared to the usual $(2,2)$ supersymmetry differ by a choice of sign in the supercommutator relations of its $4$ real supercharges:
-\begin{align*}
-\{Q_\pm,\tl{Q}_\pm\}=-2\p_\pm,
-\end{align*}
-with all other anti-brackets vanishing.
-The geometry of the target space of these sigma models reflects this sign change and in contrast to complex geometry needed for the usual supersymmetry, the target needs to be para-complex.
-More precisely, the required target geometry must be bi-para-Hermitian.
-In \cite{HullTwistedSUSY}, this type of supersymmetry was dubbed {twisted} SUSY, while the name {pseudo}-SUSY was used in various other works.
-Here we use the name {\bf para-SUSY} to reflect its relationship to para-complex geometry and to reserve the adjective ``twisted'' for the context of topological twists.
-
-Para-complex structure on a manifold $\Mb$ is given by the data of an integrable endomorphism $K \in \End(T\Mb)$ such that $K^2=\id$ and its two eigenbundles corresponding to the $+1$ and $-1$ eigenvalues have the same rank.
-Consequently, $\Mb$ needs to have an even dimension $2n$.
-A para-Hermitian structure on $(\Mb,\eta)$ is then obtained by adding a compatible metric $\eta$:
-\begin{align*}
-\eta(K\cdot,K\cdot)=-\eta(\cdot,\cdot).
-\end{align*}
-This condition forces $\eta$ to be of signature $(n,n)$ and implies that $\omega=\eta K$ is an almost symplectic structure called the fundamental form of $K$.
-A bi-para-Hermitian geometry is then defined as a pair of para-Hermitian structures $(\eta,K_\pm)$ sharing the same metric and satisfying an additional condition
-\begin{align}
-\rd^p_\pm\omega_\pm=\pm H \in \Omega^3_{cl.}(\Mb),
-\end{align}
-where $\rd^p_\pm=K^*\circ \rd\circ K_\pm^*$ is the para-complex twisted differential and $\omega_\pm=\eta K_\pm$ are the fundamental forms of $K_\pm$.
-
-In \cite{Hu:2019zro}, it is shown that the bi-para-Hermitian geometry $(\Mb,\eta,K_\pm,H)$ is equivalent to the data of a generalized para-K\"ahler geometry, which is defined as a pair of {\it generalized} para-complex (GpC) structures $\KK_\pm$ \cite{wade2004dirac,Zabzine:2006uz,Hu:2019zro} on $\Mb$,
-\begin{align*}
-\KK_\pm \in \End((\TT)\Mb), \quad \KK^2=\id, \quad \la \KK\cdot,\KK\cdot\ra=-\la\cdot,\cdot \ra,
-\end{align*}
-that commute and whose product $\GG=\KK_+\KK_-$ defines a split signature metric $G$ on $(\TT)\Mb$ via $G(\cdot,\cdot)=\la \GG\cdot,\cdot\ra$.
-Here, $\la\cdot,\cdot \ra$ is the symmetric duality pairing on $(\TT)M$ and the generalized para-complex endomorphisms $\KK_\pm$ satisfy a Courant integrability condition which ensures that its $\pm 1$-eigenbundles are Dirac structures \cite{courant1990dirac}.
-
-Para-complex and para-Hermitian geometry was also recently studied as the description of the extended geometry in the context of T-duality \cite{freidel2017generalised,Freidel:2018tkj,Svoboda:2018rci,Marotta:2018myj}, following the earlier work of Vaisman \cite{vaisman2012geometry,vaisman2013towards}.
-In \cite{Marotta:2019eqc}, Szabo and Marotta described the bosonic sector of the $2D$ sigma models targeted in this extended geometry.
-Various topological models in the AKSZ framework on the para-Hermitian manifold $\Mb=T^*M\simeq M^n\times \RR^n$ were studied in \cite{Kokenyesi:2018xgj} and $3D$ membrane sigma models with this target were the subject of \cite{Chatzistavrakidis:2018ztm}.
-The generalized geometry corresponding to Para-Hermitian geometry and its refined version, Born geometry, has been studied in \cite{Hu:2019zro}.
-
-\paragraph{Main results} In this paper, we combine the results of \cite{HullTwistedSUSY} and \cite{Hu:2019zro} to study the $2D$ topological sigma models with a generalized para-complex target manifold $(\Mb,\KK_+)$.
-This geometry leads to a $2D$ topological theory via the AKSZ formalism as follows.
-The Courant algebroid $(\TT)\Mb$ defines a $3D$ topological theory with a $2$-shifted symplectic NQ target space $({\cal E},\Omega)$ \cite{Roytenberg:2002nu}.
-Because the $\pm 1$-eigenbundles of $\KK$ are Dirac structures in $(\TT)\Mb$, they each define a Lagrangian in $({\cal E},\Omega)$, which are $1$-shifted symplectic NQ manifolds and as such define a $2D$ topological boundary theories.
-
-Additionally, we show that when the GpC manifold $(\Mb,\KK_+)$ additionally admits a generalized para-K\"ahler structure $(\Mb,\KK_+,\KK_-)$, the topological theories for $(\Mb,\KK_+)$ described above can be realized as topological twists of the $(2,2)$ para-SUSY theory attached to $(\Mb,\KK_\pm)$.
-
-We also present several explicit examples of our construction. The well-known examples include the Poisson sigma model of a real Poisson manifold $(\Mb,\Pi)$ that is described by the GpC structure
-\begin{align*}
-\KK_\Pi=
-\begin{pmatrix}
-\id & 2\Pi \\
-0 & -\id
-\end{pmatrix},
-\end{align*}
-the A-model of a symplectic manifold $(\Mb,\omega)$ described by the GpC structure
-\begin{align*}
-\KK_\omega=
-\begin{pmatrix}
-0 & \omega^{-1} \\
-\omega & 0
-\end{pmatrix},
-\end{align*}
-and also the BFF theory (?) that is simply given by the trivial GpC structure
-\begin{align*}
-\KK_0=
-\begin{pmatrix}
-\id & 0 \\
-0 & -\id
-\end{pmatrix}.
-\end{align*}
-
-The new examples that we describe are all tied to para-complex geometry. They are the para-complex version of the B-model of a para-complex manifold $(\Mb,K)$ that is given by the GpC structure
-\begin{align*}
-\KK_K=
-\begin{pmatrix}
-K & 0 \\
-0 & -K^*
-\end{pmatrix},
-\end{align*}
-and the para-complex topological Landau-Ginzburg model that can be seen as a deformation of the above geometry by a para-holomorphic poisson bi-vector $Q$
-\begin{align*}
-\KK_Q=
-\begin{pmatrix}
-K & Q \\
-0 & -K^*
-\end{pmatrix}.
-\end{align*}
-
-Importantly, our construction can also be applied to the more notoriously known generalized complex (GC) geometry, which was in the context of topological sigma models extensively studied in \cite{Zucchini:2004ta,Ikeda:2004cm,Kapustin:2004gv,Pestun:2006rj,Cattaneo:2009zx} to name some of the works, but to the authors' knowledge a similar construction to ours via a boundary reduction was not proposed before.
-Similarly in the GpC case, the GC structure defines a pair of Dirac structures (that are now tied by complex conjugation) and the $2D$ topological theory is recovered again as a boundary theory of the $3D$ theory defined by the underlying Courant algebroid.
-The advantage of our approach is that it provides a unified way to extract the data of a topological theory from any GC structure via a clear geometric procedure on the underlying shifted symplectic spaces.
-In the special case when the manifold is generalized K\"ahler \cite{Gualtieri:2003dx,Gualtieri:2010fd} -- implying it admits a $(2,2)$ SUSY --  the topological theories can again be realized as topological twists \cite{Kapustin:2004gv} of the $(2,2)$ theory.
-Here, the main examples are given by the A- and B- model corresponding to the GC structures $\JJ_\omega$ and $\JJ_I$, respectively:
-\begin{align*}
-\JJ_\omega=
-\begin{pmatrix}
-0 & -\omega^{-1} \\
-\omega & 0
-\end{pmatrix}, \quad
-\JJ_I=
-\begin{pmatrix}
-I & 0 \\
-0 & -I^*
-\end{pmatrix},
-\end{align*}
-as well as the topological Landau-Ginzburg model which is again viewed via the deformation of $\JJ_I$ by a holomorphic poisson bi-vector \cite{Gualtieri:2007bq} $\sigma=-\frac{1}{4}(IQ+iQ)$:
-\begin{align*}
-\JJ_Q=
-\begin{pmatrix}
-I & Q \\
-0 & -I^*
-\end{pmatrix}.
-\end{align*}
-
-Notice, however, that for example the usual Poisson sigma model cannot be obtained in the realm of GC geometry because no GC structure is defined by a real Poisson structure $\Pi$.
 
@@
 This is one of the main differences between complex and para-complex geometry; one of the eigenbundles can be integrable while the other is not.
-In such cases, we call $\PS$ {\bf half-integrabile}.
-For more details, see for example \cite{??,??}.
-
-\paragraph{Type decomposition} The splitting of the tangent bundle $T\PS=L\oplus \Lt$ gives rise to a decomposition of tensors analogous to the $(p,q)$-decomposition in complex geometry.
-For differential forms, we denote the decomposition as
-\begin{align}\label{eq_plusminus_decomp}
-\Lambda^k (T^*\mathcal{P})&=\bigoplus_{k=m+n}\Lambda^{(m,n)}(T^*\mathcal{P}),
-\end{align}
-where $\Lambda^{(m,n)}(T^*\mathcal{P})=\Lambda^m(T^{*}_{1,0})\otimes \Lambda^n(T^{*}_{0,1})$ and the corresponding sections are denoted by $\Omega^{(m,n)}(\mathcal{P})$.
-The bigradings \eqref{eq_plusminus_decomp} yield the natural projections
-\begin{align*}
-\Pi^{(p,q)}:\Lambda^k(T^*\mathcal{P})&\rightarrow \Lambda^{(p,q)}(T^*\mathcal{P}),
-\end{align*}
-so that when $K$ is integrable, the de-Rham differential splits as $\rd=\p+\tl{\p}$, where
-\begin{align*}
-\begin{array}{cc}
-\p \coloneqq \Pi^{(p+1,q)}\circ \rd, & \tl{\p} \coloneqq \Pi^{(p,q+1)}\circ \rd,
+For this reason, it is useful to introduce the notion of {\bf half-integrability}:
+
+%\begin{Def}
+%Let $K$ be an almost para-complex.
+If the $+1$ (respectively $-1$) eigenbundle is Frobenius integrable, we call $K$ a {\bf p-para-complex} (respectively {\bf $n$-para-complex}) structure.
+A $K$ that is both $p$- and $n$- para-complex is simply a para-complex structure.
+%\end{Def}
+
+%\brian{The slash notation complex/product made it really hard to parse the definition since you already put parentheses. 
+%If you want to add a definition for the product case make it another definition, or say "the same definition applies to integrability of product structures.
+%Though, it doesn't seem like we use product structures at all below this, so maybe there is no point.}
+
+\paragraph{Para-Complexification}
+The analogy between complex and para-complex geometry can be made manifest by {\it para-complexification}. \brian{sentence split} 
+This amounts to introducing the algebra of para-complex numbers $$\Cc=\RR\oplus \kk\RR,$$
+\brian{This does not appear to be the most common mathematical terminology for this algebra. 
+We should at least remark that these are more commonly referred to as ``split complex numbers", or "hyperbolic numbers".}
+where $\kk^2=1$ is the para-complex unit, and take linear combinations over $\Cc$. 
+The algebra $\Cc$ has the familiar natural operations
+\begin{align}
+\begin{aligned}
+&\bullet\quad \text{Conjugation: }x+\kk y\mapsto \overline{x+\kk y}=x-\kk y\\
+&\bullet\quad \text{Real part: } x+\kk y \mapsto \text{Re}(x+\kk y)=x\\
+&\bullet\quad \text{Imaginary part: } x+\kk y \mapsto \text{Im}(x+\kk y)=y.
+\end{aligned}
+\end{align}
+
+All tensorial objects can be extended to be $\Cc$-linear, in particular, the para-complexified tangent bundle decomposes as $T\PS\otimes \Cc\coloneqq T\PS^\Cc=T^{(1,0)}\oplus T^{(0,1)}$ to the $\pm \kk$ eigenbundles of the endomorphism $K$, now extended by linearity to $\End(T\PS^\Cc)$.
+There is an isomorphism between the para-complex vector spaces $\Cc^n$ and $\RR^{2n}$, explicitly (see \cite[Ch.~15]{Cortes:2010ykx} for more details):
+\begin{align}\label{tab:identification}
+\begin{array}{ccc}
+(\Cc^n,\kk)&\simeq &(\RR^{2n},\id\times -\id)\\
+(x^i+\kk y^i)_{i=1,\cdots,n} &\mapsto & (x^i+y^i,x^i-y^i)_{i=1,\cdots,n}\\
+(\frac{x^i+\xt_i}{2}+\kk\frac{x^i-\xt_i}{2})_{i=1,\cdots,n} &\mapsfrom & (x^i,\xt_i)_{i=1,\cdots,n}.
 \end{array}
-\end{align*}
-are the \textbf{para-complex Dolbeault operators}, satisfying
-\begin{align*}
-\p^2=\tl{\p}^2=\p\tl{\p}+\tl{\p}\p=0.
-\end{align*}
-
-One can also introduce the {\it twisted differential $\rd^p\coloneqq(\Lambda^{k+1}K^*)\circ\rd\circ (\Lambda^kK^*)$}.
-When $K$ is integrable, it can be simply written as $\rd^p=(\p_++\p_-)$ on real forms and $\rd^p=\kk (\p+\bar{\p})$ on para-complex forms.
+\end{align}
 
 \paragraph{Para-Holomorphic structure}
-Let now $(\mathcal{P},K)$ be an almost para-complex manifold of dimension $2n$.
+Let now $(\mathcal{P},K)$ be an almost para-complex manifold.
 If $K$ is integrable, we get a set of $2n$ coordinates $(x^i,\tilde{x}_i)$ called {\bf adapted coordinates}, $\mathcal{P}$ locally splits as $M\times \tilde{M}$, and $K$ acts as identity on $TM=L$ and negative identity on $T\tilde{M}=\tilde{L}$.
-The adapted coordinates therefore define two complimentary foliations that we will call {\bf canonical foliations} of the para-complex manifold $\PS$ and denote $M$ and $\Mt$.
-Both $M$ and $\Mt$ are therefore $n$-dimensional manifolds composed of connected components called leafs $M_i$, $\Mt_i$:
-\begin{align*}
-M=\bigcup_i M_i,\quad \Mt=\bigcup_i \Mt_i,
-\end{align*}
-and each are as sets equal to $\PS$.
-
+The adapted coordinates therefore define two complimentary foliations of $\PS$.
+After para-complexification, we get $n$ {\bf holomorphic coordinates} \footnote{We should use the word para-holomorphic instead of holomorphic but we choose to omit the prefix ``para-" whenever no confusion with complex geometry is possible and recovering it only when needed.} $z^i=\frac{x^i+\xt_i}{2}+\kk \frac{x^i-\xt_i}{2}$, and the conjugate {\bf anti-holomorphic coordinates} $\bar{z}^i=\frac{x^i+\xt_i}{2}-\kk \frac{x^i-\xt_i}{2}$.
+The notion of holomorphicity in the context of para-complex geometry is now entirely analogous to complex geometry.
 As usual, a map of para-complex manifolds is called para-holomorphic if its pushforward commutes with the respective para-complex structures
@@
 \end{Def}
-\begin{remark}
-In the following we will omit the prefix ``para-'' in para-holomorphic whenever no confusion with complex holomorphicity is possible.
-\end{remark}
 
@@
 \end{align*}
-where $(x^k,\xt_l)$ and $(y^i,\yt_j)$ are adapted local coordinates on $M$ and $N$, respectively.
-It is easy to check from \eqref{eq:def_parahol} that $F$ is a holomorphic map iff the components satisfy
+where $(x^k,\xt_l)$ and $(y^i,\yt_j)$ are the adapted coordinates on $M$ and $N$, respectively, or (after para-complexification) as a map
+\begin{align*}
+F&: \Cc^n\rightarrow \Cc^m\\
+F&=F^i(z^k,\bar{z}^k)^{i=1,\cdots,m}_{k=1,\cdots, n}, 
+\end{align*}
+It is easy to check from \eqref{eq:def_parahol} that $F$ is a para-holomorphic map iff its components do not depend on anti-holomorphic coordinates on $M$, i.e.
+\begin{align}\label{eq:holomorphic}
+\frac{\p}{\p \bar{z}^k} F^j=\frac{\p}{\p z^k} \bar{F}^j=0.
+\end{align}
+In the real, adapted coordinates, the condition \eqref{eq:def_parahol} reads
 \begin{align}\label{eq:holomorphic_real}
@@
 \end{align}
-
-The conditions \eqref{eq:holomorphic_real} tell us that the holomorphic functions map the canonical foliations of the para-complex manifolds $M$ and $N$.
-This also means that the transition functions on a para-complex manifold (seen as maps $\RR^{2n}\rightarrow \RR^{2m}$) are holomorphic since the foliations must be preserved, i.e.
+The equivalence between \eqref{eq:holomorphic} and \eqref{eq:holomorphic_real} can be checked using the relationships \eqref{tab:identification}.
+
+The conditions \eqref{eq:holomorphic_real} tell us that the holomorphic functions preserve the foliations defined by the adapted coordinates on $M$ and $N$.
+This also means that the transition functions on a para-complex manifold (seen as maps $\RR^{2n}\rightarrow \RR^{2n}$) are holomorphic since the foliations must be preserved, i.e.
 the coordinates transform as
-\begin{align}\label{para-coordinate-transf}
+\begin{align*}
 (x^i,\xt_i)\mapsto (y^j(x^i),\yt_j(\xt_i)).
-\end{align}
-
-This also gives us an intuition into what holomorphic bundles and their holomorphic sections look like.
-First, we notice that the tangent bundle $T\PS$ itself is a holomorphic bundle (see for example \cite{Cortes:2003zd,Hu:2019zro}); this is simply because of the form of the transition functions \eqref{para-coordinate-transf} that induce a holomorphic structure on the tangent bundle.
-The holomorphic sections of $T\PS$ -- the holomorphic vector fields -- are locally of the form
-\begin{align*}
-X= X^i(x)\p_i+\tl{X}_i(\xt)\pt^i,
-\end{align*}
-i.e. the components in $L$ and $\Lt$ individually define vector fields on the foliations $M$ and $\Mt$, respectively.
-
-Similarly, the cotangent bundle is a holomorphic bundle.
-For the higher wedge powers, we find that only $\Lambda^{(k,0)+(0,k)}(T^*\PS)$, $1\leq k\leq n$, are holomorphic bundles.
-The {\bf para-complex Dolbeault complex} is therefore given by
-\begin{align}
-\left(\Omega^{(\bullet,0)}\otimes\Omega^{(0,\bullet)},(\p,\pt)\right)\coloneqq \left(\mathbf{\Omega}^{\bullet,0},\pd\right).
-\end{align}
+\end{align*}
+
+\paragraph{Type decomposition} The splitting of the tangent bundle $T\PS=L\oplus \Lt$ in the real case and $T\PS^\Cc$ in the para-complex case gives rise to a decomposition of tensors analogous to the $(p,q)$-decomposition in complex geometry.
+For differential forms, we denote the real and para-complex decompositions as
+\begin{align}\label{eq_plusminus_decomp}
+\Lambda^k (T^*\mathcal{P})&=\bigoplus_{k=m+n}\Lambda^{(+m,-n)}(T^*\mathcal{P}),\\
+\Lambda^k (T^*\mathcal{P}^\Cc)&=\bigoplus_{k=m+n}\Lambda^{(m,n)}(T^*\mathcal{P}),
+\end{align}
+where $\Lambda^{(+m,-n)}(T^*\mathcal{P})=\Lambda^m(L^*)\otimes \Lambda^n(\Lt^*)$ and $\Lambda^{(m,n)}(T^*\mathcal{P})=\Lambda^m(T^{(1,0)*})\otimes \Lambda^n(T^{(0,1)*})$.
+The corresponding sections are denoted by $\Omega^{(+m,-n)}(\mathcal{P})$ and $\Omega^{(m,n)}$, respectively.
+The bigradings \eqref{eq_plusminus_decomp} yield the natural projections
+\begin{align*}
+\Pi^{(+p,-q)}:\Lambda^k(T^*\mathcal{P})&\rightarrow \Lambda^{(+p,-q)}(T^*\mathcal{P}),\\
+\Pi^{(p,q)}:\Lambda^k(T^*\mathcal{P}^\Cc)&\rightarrow \Lambda^{(p,q)}(T^*\mathcal{P}),
+\end{align*}
+so that when $K$ is integrable, the de-Rham differential splits as $\rd=\p_++\p_-$, in the real case and $\rd=\p+\bar{\p}$ in the para-complexified case, where
+\begin{align*}
+\begin{array}{cc}
+\p_+ \coloneqq \Pi^{(+p+1,-q)}\circ \rd, & \p_- \coloneqq \Pi^{(+p,-q-1)}\circ \rd,\\
+\p \coloneqq \Pi^{(p+1,q)}\circ \rd, & \bar{\p} \coloneqq \Pi^{(p,q+1)}\circ \rd,
+\end{array}
+\end{align*}
+are the \textbf{para-complex Dolbeault operators}, satisfying
+%\begin{align}\label{eq:partials_plusminus}
+%\begin{aligned}
+%\p_+&:\Omega^{(+p,-q)}(\mathcal{P})\rightarrow \Omega^{(+p+1,-q)}(\mathcal{P})\\
+%\p_-&:\Omega^{(+p,-q)}(\mathcal{P})\rightarrow \Omega^{(+p,-q-1)}(\mathcal{P}),
+%\end{aligned}
+%\end{align}
+\begin{align*}
+\p_+^2=\p_-^2=\p_+\p_-+\p_-\p_+&=0\\
+\p^2=\bar{\p}^2=\p\bar{\p}+\bar{\p}\p&=0
+\end{align*}
+
+One can also introduce the {\it twisted differential $\rd^p\coloneqq(\Lambda^{k+1}K^*)\circ\rd\circ (\Lambda^kK^*)$}.
+When $K$ is integrable, it can be simply written as $\rd^p=(\p_++\p_-)$ on real forms and $\rd^p=\kk (\p+\bar{\p})$ on para-complex forms.
+
 %\begin{lemma}

### 2019-11-22 oldstuff/draft2.tex
merge

--- 2019-11-22 oldstuff/draft.tex
@@
 
-\title{Twisted parasupersymmetry and paracomplex geometry}
+\title{Topological Sigma Models for Generalized Para-Complex Geometry}
 
@@
 \maketitle
-
+\begin{abstract}
+We study a class of $2d$ topological sigma models that are formulated on generalized para-complex target manifolds via the AKSZ framework.
+When the target is additionally generalized para-K\"ahler, these topological theories can be realized as topological twists of $(2,2)$ para-supersymmetric sigma models of Abou-Zeid and Hull.
+We compare our results to the case of generalized complex and generalized K\"ahler geometry, where similar results have been described in the context of the usual $(2,2)$ SUSY by Kapustin and Li.
+We present several examples and show that our construction recovers the A-model and the Poisson sigma model as special cases.
+Moreover, we also introduce new examples of topological theories inherently tied to the para-complex geometry, the para-B-model and a para-complex version of the Landau-Ginzburg model.
+
+\end{abstract}
+\newpage
 \tableofcontents
-
+\newpage
 \section{Introduction}
+Since the work of (..) \cite{?} it has been known that on any K\"ahler manifold $(M,I,\omega)$, one can define a $2d$ sigma model admitting a $(2,2)$ supersymmetry (SUSY) and such model has a simple local description in terms of the K\"ahler potential.
+Moreover, Witten has shown \cite{?} that such sigma model gives rise to two distinct topological theories -- the A- and B-models -- via a procedure called topological twisting.
+These topological theories have an important interpretation in terms of their underlying geometry: the A-model only depends on the symplectic structure $(M,\omega)$, while the B-model only depends on the complex structure $(M,I)$.
+Additionally, there exists an ${\mathbb Z}_2$ automorphism acting on the original $(2,2)$ supersymmetric theory that exchanges its A- and B-models.
+This is the simplest way one can observe the phenomenon of mirror symmetry in the context of $2d$ sigma models.
+
+The K\"ahler geometry does not describe the most general $(2,2)$ sigma model, as was shown in \cite{Gates-hull-rocek-biherm}.
+Instead, the most general geometry is described by a bi-Hermitian geometry, defined by a pair of complex structures $I_\pm$ compatible with the same Riemannian metric $g$ and satisfying the compatibility relation
+\begin{align*}
+\rd^c_\pm\omega_\pm=\pm H \in \Omega^3_{cl.}(M),
+\end{align*}
+$\omega_\pm$ being the fundamental forms of $I_\pm$ and $\rd^c_\pm$ the associated $\rd^c$-operators.
+For this geometry, the local description is more complicated than in the K\"ahler case, in particular because the analogue of the K\"ahler potential is much harder to describe.
+Consequently, the topological twists are also  more complicated.
+
+This problem is nevertheless partially mitigated by an alternative geometric formulation in terms of generalized K\"ahler (GK) geometry, which has been shown in \cite{Gualtieri:2003dx} to be equivalent to the above-described bi-Hermitian geometry $(g,I_\pm,H)$.
+A GK structure on $M$ is given by the data of two complex endomorphisms $\JJ_\pm$ of the bundle $(\TT)M$:
+\begin{align*}
+\JJ_\pm \in \End((\TT)M),\quad \JJ_\pm^2=-\id, \quad \la \JJ \cdot,\JJ\cdot \ra= \lara,
+\end{align*}
+where $\lara$ denotes the natural duality pairing on $(\TT)M$:
+\begin{align*}
+\la X+\ap,Y+\bt\ra=\ap(Y)+\bt(X),\quad X,Y\in \se(TM),\quad \ap,\bt \in \se(T^*M).
+\end{align*}
+Additionally, $\JJ_\pm$ are required to commute and their product $\GG\coloneqq -\JJ_+\JJ_-$ to define a
 

### 2019-11-22 oldstuff/gen_paracxp_top_theories.tex
merge

\documentclass{article}
\usepackage{amssymb, amsmath, amsthm, mathtools, bbm, tikz-cd, stmaryrd, enumerate,cite}

\newcommand{\TT}{{T\oplus T^*}}
\newcommand{\JJ}{\mathcal{J}}
\newcommand{\KK}{\mathcal{K}}
\newcommand{\GG}{\mathcal{G}}
\newcommand{\Cc}{\mathbf{C}}
\newcommand{\RR}{\mathbb{R}}
\newcommand{\XX}{\mathfrak{X}}
\newcommand{\FF}{\mathcal{F}}
\newcommand{\MM}{\mathcal{M}}
\newcommand{\bl}{[\![}
\newcommand{\br}{]\!]}
\newcommand{\bbl}{\bl}
\newcommand{\bbr}{\br}
\newcommand{\brac}{[\ ,\ ]}
\newcommand{\bracp}{\{\ ,\ \}}
\newcommand{\bbrac}{\bbl\ ,\ \bbr}
\newcommand{\bracd}{\bl\ ,\ \br}
\newcommand{\la}{{\langle}}
\newcommand{\ra}{{\rangle}}
\newcommand{\Tp}{{T_+}}
\newcommand{\Tm}{{T_-}}
\newcommand{\xp}{{x_+}}
\newcommand{\yp}{{y_+}}
\newcommand{\zp}{{z_+}}
\newcommand{\Sigmah}{\hat{\Sigma}}
%----------------------------------------
\newcommand{\PP}{{\mathrm{P}_{\! +}}}
\newcommand{\PPt}{{\mathrm{P}_{\! -}}}
\newcommand{\PPB}{\mathrm{P}^{B}_{\! +}}
\newcommand{\PPtB}{\mathrm{P}^{B}_{\! -}}
\newcommand{\PPBpm}{{\mathrm{P}^{B}_{\! \pm}}}
\newcommand{\PPpm}{{\mathrm{P}_{\! \pm}}}
\newcommand{\id}{{\mathbbm{1}}}
\newcommand{\nlr}{\overset{\leftrightarrow}{\n}}
\newcommand{\lc}{\mathring{\n}}
\newcommand{\im}{\mathrm{Im}\,}
\newcommand{\Ker}{\mathrm{Ker}\,}
\newcommand{\Lie}{\mathcal{L}}
\newcommand{\PS}{\mathcal{P}}
\newcommand{\ap}{\alpha}
\newcommand{\bt}{\beta}
\def\w{\wedge}
\newcommand{\p}{\partial}
\newcommand{\pt}{\tilde{\partial}}
\newcommand{\xt}{{x_-}}
\newcommand{\yt}{{y_-}}
\newcommand{\zt}{{z_-}}
\newcommand{\n}{\nabla}
\newcommand{\rd}{\mathrm{d}}
\newcommand{\PH}{(\PS,\eta,\omega)}
\newcommand{\Lt}{{\tl{L}}}
\newcommand{\Lb}{\mathbf{L}}
\newcommand{\LL}{\mathbb{L}}
\newcommand{\s}{\mathbf{s}}
\newcommand{\se}{\Gamma}
\newcommand{\Endo}{\text{End}}
\newcommand{\ellt}{{\tl{\ell}}}
\newcommand{\ot}{{1/2}}
\newcommand{\inv}{{-1}}
%----------------------------------------
\def\gld{generalized Lie derivative }
\def\glds{generalized Lie derivatives }
\def\ph{para-Hermitian }
\def\tl{\tilde}

% These will be typeset in italics
\newtheorem{theorem}{Theorem}[section]
\newtheorem{proposition}[theorem]{Proposition}
\newtheorem{lemma}[theorem]{Lemma}
\newtheorem{corollary}[theorem]{Corollary}
\newtheorem{fact}[theorem]{Fact}
\newtheorem*{theorem*}{Theorem}
\newtheorem*{lemma*}{Lemma}
\newtheorem*{proposition*}{Proposition}
\newtheorem{Rem}[theorem]{Remark}

% These will be typeset in Roman
\theoremstyle{definition}
\newtheorem{Def}[theorem]{Definition}
\newtheorem{Conj}[theorem]{Conjecture}

\theoremstyle{definition}
\newtheorem*{notation*}{Notation}
\newtheorem*{definition*}{Definition}

\theoremstyle{remark}
\newtheorem*{remark*}{Remark}
\newtheorem{Ex}[theorem]{Example}
\newtheorem{question}[theorem]{Question}
\newenvironment{claim}[1]{\par\noindent\underline{Claim:}\space#1}{}
\newenvironment{claimproof}[1]{\par\noindent\underline{Proof:}\space#1}{\hfill $\blacksquare$}

\newtheoremstyle{ref}{}{}{\itshape}{}{\bfseries}{.}{.5em}{#1 \thmnote{#3}}
\theoremstyle{ref}
\newtheorem*{reftheorem}{Theorem}
\newtheorem*{refproposition}{Proposition}

\input xy

\xyoption{all}

\DeclareMathOperator{\End}{End}
\DeclareMathOperator{\rk}{rk}
\DeclareMathOperator{\Maps}{Maps}
\title{Topological Sigma Models from Generalized Paracomplex Geometry}
%\author{ Seyed Faroogh Moosavian, David Svoboda\\ \\
%\it{Perimeter Institute For Theoretical Physics}\\
%\it{31 Caroline St. N., N2L2Y5, Waterloo ON, Canada}\thanks{e-mail:dsvoboda@perimeterinstitute.ca}}
\date{}

\begin{document}
\maketitle
\begin{abstract}

\end{abstract}
\newpage
\section*{Random notes}
Here we'll be putting random notes / remarks / calculations when reading various literature and putting pieces together.

\paragraph*{Names of different approaches}
Let's first agree on names we'll be calling the different approaches. 
\begin{itemize}
\item The first is the {\bf Dirac Sigma Model (DSM)} discussed in \cite{DSM1,DSM2} and the gauging procedure is described in \cite{DSMgauge1,DSMgauge2}.
\item Next we have the paper \cite{Pestun:2006rj} by Pestun, we will call this approach the {\bf Pestun's Topological J-model (PTJ)}.
\item Lastly, there is the paper \cite{Cattaneo:2009zx} by Cattaneo, Zabzine and Qiu, which we will call the {\bf CQZ Model} for a lack of better names.
\item Now I also found out about the {\bf Zucchini a.k.a. Hitchin Sigma model (ZSM)} \cite{Zucchini:2004ta} which I believe is the oldest of them all. Also seems like the most straightforward to understand. (edit: not topological, see below)
\end{itemize}

\paragraph*{Comments on relationships between different approaches}
Chronologically, the ZSM was first, then DSM, then the PTJ and CQZ is last. In the introduction of the CQZ paper \cite{Cattaneo:2009zx}, they simply comment they are aware about PTJ and ZSM but do not say anything further. Similarly, in the introduction of PTJ \cite{Pestun:2006rj}, he says DSM is the analogy of his construction in the real case but that is not quite true. I think DSM is closer to be the real version of CQZ than PTJ since CQZ predominantly use Dirac structures as opposed to GC structures. In the DSM paper, the again, note the existence of ZSM and also cite other works related to GC geometry and sigma models. DSM paper also claims they plan to extend their work in the case of GC structures but I did not find anything relevant later. ({\bf edit: I just now realized/noticed that the other approaches, including the ZSM are not topological} I guess the reason they are interesting is that the sigma models usually reproduce some sort of resemblance of integrability conditions on the side of GG)

\paragraph*{Facts about different approaches}
\begin{itemize}
\item Relationship to Poisson sigma model (PSM): ZSM gives PSM only in the case when the poisson structure is invertible to symplectic. DSM reproduces PSM fully. CQZ generalizes it for Lie algebroids (see below). PTJ gives the PSM for invertible symplectic structure.
\item CQZ claim their 2D version is for Dirac structures corresponding to cpx / symplectic form equivalent to B / A models {\it upon gauging}
\end{itemize}

\paragraph*{PTJ}
The data used here is a GC structure $\JJ$ with gen. CY condition. One uses the $\pm i$ eigenbundles of $\JJ$ and a the corresponding bialgebroid to construct a BV algebra and from there uses the AKSZ approach to construct the theory. The AKSZ method does the following: one needs to have a PQ manifold $M$ as a target, which is a supermanifold $\MM$ with a symplectic structure $\omega$, giving the Poisson bracket $\{\ ,\ \}$ on inversion, and a compatible homological vector field $Q$. The compatibility means $\Lie_Q\omega=0$. The homological property $Q^2=0$ then means $\{S,S\}=0$, where $S$ is a Hamiltonian fction of $Q$, $\imath_Q\omega=\rd S$. The source supermanifold is taken to be $T[1]\Sigma$, I think this is the supermanifold people usually use (with coordinates $(\sigma^1, \sigma^, \theta^1,\theta^2)$. This manifold also has a $Q$-structure, simply given by a de-Rham differential on $\hat{\Sigma}$. One then observes the space of maps between $\hat{\Sigma}$ and $\MM$, $\Maps(\hat{\Sigma},\MM)$ is itself a PQ manifold. The symplectic structure comes from a pullback of $\omega$ on $\MM$ and the $\hat{Q}$ structure comes from $Q$'s on $\Sigmah$ and $\MM$. One then simply gets the action $S$ as the Hamiltonian generating the $\hat{Q}$ on $\Maps(\hat{\Sigma},\MM)$.

Here is how the AKSZ procedure applies to the case of the gen. CY case. The target is the shifted bundle of the Lie algebroid, $\MM= L[1]$. We have the BV algebra which in particular gives Q and a Poisson bracket $\bracp$, but this bracket does not come from a symplectic form, i.e. the corresponding poisson structure is not invertible (in general). Pestun then says {\it ``Using only BV algebra, it is possible to define closed topological string
filed theory, which generalizes the Kodaira-Spencer theory. It definitely works in the genus zero and in the sector of topologically trivial maps, but it is not yet clear whether
the BV algebra completely defines the full theory, however there are some indications [ref].} He then says okay well let's just go the simple way, add some assumptions about the poisson structure and try to write down some symplectic realization trick which will provide us with a symplectic structure on $\MM=L[1]$ and we can then go the AKSZ procedure as described above.

{\bf To relate this to the DSM:} Given just a Dirac structure, we get a corresponding Lie algebroid $L$ (as opposed to Lie bialgebroid in the case of PTJ). This gives the $Q$ structure in the following way: part of the Lie algebroid data is a differential $\rd_L$, which acts on sections of $\Lambda^\bullet L^*$. We identify $\se(\Lambda^\bullet L^*) \leftrightarrow C^\infty(L[1])$, therefore through this identification $\rd_L$ maps to $Q$ (properties of $Q$ follow from $\rd_L^2=0$). Therefore, given Dirac structure, we get a $Q$-manifold $L[1]$. We do not, however, get any poisson or symplectic structure on $L[1]$. But (!) the Lie algebroid data on $L$ does define a poisson structure on $L^*$, since we have a bracket on sections of $L$ and this bracket can be extended to arbitrary sections of $\Lambda^\bullet L$ which in turn is identified with $C^\infty(L^*)$, therefore we have a bracket on functions on total space of $L^*$ satisfying Jacobi identity and so this is a Poisson bracket. To sum up, the Lie algebroid data gives:
\begin{align*}
(L,\brac_L,\rd_L)\leftrightarrow \rd_L:& \Lambda^\bullet L^*\rightarrow \Lambda^{\bullet+1} L^* \Leftrightarrow Q: C^\infty(L[1]) \rightarrow C^\infty(L[1])\\
\brac_L:& L \times L \rightarrow L \Leftrightarrow \bracp: C^\infty(L^*) \times C^\infty(L^*) \rightarrow C^\infty(L^*)
\end{align*}
What Pestun does is that he uses $Q$ on $L[1]$ coming from an algebroid $L$ and then, because he has a bialgebroid, i.e. also an independent compatible Lie algebroid structure on $L^*$, he gets via the above a poisson bracket on $L[1]$ as well.

How does it all work for a Poisson sigma model? The corresponding Lie algebroid is $T^*M$ with the usual Poisson Lie algebroid structure. The target is therefore $T^*[1]M$ which already has the canonical symplectic one can use to define the poisson bracket. The Lie algebroid structure in particular gives $d_\pi: \Lambda^\bullet TM\rightarrow \Lambda^{\bullet+1} TM$, therefore induces $Q: C^\infty(T^*[1]M)\rightarrow C^\infty(T^*[1]M)$. Note that the Poisson structure on $M$ is entering the data of Q, not the Poisson bracket we are using (which is just given by the canonical symplectic form on $T^*M$)!!

Now, the {\bf 2D CQZ} uses a generalization of the above in the following way. One starts with a Lie algebroid $L$, which as we saw above, gives a Poisson structure on $L^*$. Therefore $L^*$ is a Poisson manifold and then we can in direct analogy with poisson sigma model just take the target as $T^*[1]L^*$ with its canonical symplectic form and $Q$ from the poisson Lie algebroid on it. Therefore, this construction does NOT generalize the PSM, it just studies a particular example of PSM where the base is a dual of a Lie algebroid, $M=L^*$. In fact, if we started with the Poisson Lie algebroid on $T^*M$ and used this construction, we will get a Poisson sigma model on $T^*[1]TM$ and my guess is that you can probably do some sort of reduction and restrict yourself to zero section of $TM\simeq M$ and get the normal PSM on $T^*[1]M$.

Authors of CQZ then observe that any GC structure gives a Lie algebroid ($+i$ eigenbundle) and therefore gives a topological model through this construction. They then claim that they get a model equivalent to A/B models upon gauging of the models one gets from their construction out of the $\JJ$ corresponding to symplectic / complex structures. Paper in progress is referenced but I couldn't find it.

I think the PTJ construction should be thought of as somewhat of a generalization of the {\it generalized A/B-twists} of a $(2,2)$ theory. The geometry of $(2,2)$ is given by a pair $(\JJ_1,\JJ_2)$ of GC structures (integrable) forming a GK structure, and the A/B twists essentially use the data of one of the $\JJ_i$. This boils down to the usual A/B models when the GK structure is just K\"ahler. In PTJ, one starts with one integrable $\JJ$ and then only uses another $\JJ'$ to gauge fix. This other $\JJ'$ does not need to be integrable. Pestun comments that it would be interesting to compare the gauge fixed PTJ with the top. twisted $(2,2)$. In one of the refs you sent me there is even a comment on what happens when one does not require full integrability. My guess is that the PTJ model simply generalizes the top. twist approach by going from the other side and building a model that a priori does not know it comes from a twist of a $(2,2)$ theory and upon some integrability criteria are satisfied, one can probably realize this $(2,2)$ theory.

\paragraph*{DSM}

\paragraph*{Goals}
\begin{enumerate}
\item Understand DSM and apply to explicit examples of GpC structures
\item Try to reproduce PTJ in the real case. {\it advanced:} try to see if this can be realized as a topological twist of a SUSY theory
\item We will be able to reproduce PSM by DSM approach but we should be able to do it in the PTJ approach as well. In the cpx case this is not possible because there is no GC structure corresponding to real Poisson bivector but there is a GpC structure that does that.
\end{enumerate}
\paragraph*{More stuff to read}
Here's another way to produce some topological models out of GC geometry \cite{Ikeda:2007rn} and here is a paper on `Topological S-duality' between A/B models that has bunch of details about various 2D/3D constructions and relating them by gauge fixing/reductions \cite{Kokenyesi:2018xgj}

\section*{Various Generalized Paracomplex Structures}
\begin{Ex}
The simplest gen. paracomplex structure that exists on any manifold is the following
\begin{align*}
\KK_0=
\begin{pmatrix}
\id & 0 \\
0 & -\id
\end{pmatrix}.
\end{align*}
Its eigenbundles are simply $T$ and $T^*$.
\end{Ex}

\begin{Ex}
\textbf{Product structures}, i.e. tensor fields $P\in \Endo(T)$, such that $P^2=\id$, give the diagonal generalized paracomplex structures:
\begin{align*}
\KK_P=
\begin{pmatrix}
P & 0 \\
0 & -P^*
\end{pmatrix}.
\end{align*}
The corresponding Dirac structures are given by $L=p_+\oplus p^*_-$ and $\Lt=p_-\oplus p^*_+$, where $p_\pm$ are the $\pm 1$ eigenbundles of $P$. When $p_\pm$ have the same rank, $P$ is a paracomplex structure. The integrability of $\KK_P$ is equivalent to Frobenius integrability of $P$ , i.e. vanishing of the Nijenhuis tensor of $P$.
\end{Ex}

\begin{Ex}\label{ex:A-model}
\textbf{Symplectic structures} give the off-diagonal generalized paracomplex structures:
\begin{align*}
\KK_\omega=
\begin{pmatrix}
0 & \omega^{-1} \\
\omega & 0
\end{pmatrix}.
\end{align*}
The $\pm 1$ eigenbundles are given by $\text{graph}(\pm\omega)=\{X\pm\omega(X)\mid X\in \XX\}$, and the integrability of $\KK_\omega$ is equivalent to $\rd\omega=0$. Its type is $(2n,2n)$.
\end{Ex}

\section*{General Prescription for PTJ Model}
We start with a Lie algebroid $L$ that is an eigenbundle of a GC or GpC structure. The differentiable structure gets inherited from the Courant algebroid on $\TT$. This means that the Lie bracket is just the restriction of the Courant bracket
\begin{align*}
[X+\ap,Y+\bt]_c=[X,Y]+\Lie_X\bt-\imath_Y\rd\ap,
\end{align*}
to the sections of $L$. The anchor is projection to $T$. This gives us the the differential $\rd_L:\se(\Lambda^\bullet L^*)\rightarrow \Lambda^{\bullet+1} \se(L^*)$. Because $L^*$ is a Lie algebroid as well and $(L,L^*)$ is a Lie bialgebroid, we have bracket $\brac_{L^*}$ on $\se(L^*)$ which can be extended to $\se(\Lambda^\bullet L^*)$. We now identify $\se(\Lambda^\bullet L^*)$ with functions $C^\infty(L[1])$ polynomial in the fibre coordinates, which need to be shifted so that we get anticommuting coordinates. The identification goes like this:
Let $(e_i)$ be a local frame for $L$ such that every section is written as $\psi^i(x)e_i$. This means $(x^i,\psi^i)$ are coordinates on the total space of $L[1]$. If $e^i$ is a dual frame for $L^*$, any section of $\Lambda^\bullet L^*$ can be written as sum of terms of the form $\alpha(x)_{i\cdots k}e^i\cdots e^k$ and we identify this with the function on $L[1]$
\begin{align*}
\alpha(x)_{i\cdots k}e^i\w \cdots\w e^k \longleftrightarrow \alpha(x)_{i\cdots k} \psi^i\cdots \psi^k.
\end{align*}
We now describe how $\rd_L$ gives a vector field and $\brac_{L^*}$ a Poisson bracket on these functions. The operations of a Lie algebroid can be represented in coordinates as \cite{Roytenberg}:
\begin{align*}
a(e_i)&=A_i^\mu \p_\mu\\
[e_i,e_j]_L&=C_{ij}^ke_k\\
\rd_L&=e^iA_i^\mu\p_\mu-\frac{1}{2}C_{ij}^ke^ie^j\frac{\p}{\p e^k}
\end{align*}
where $a:L\rightarrow TM$ is the anchor map. From here we can define $Q$ in the obvious way
\begin{align*}
Q=\psi^iA_i^\mu\p_\mu-\frac{1}{2}C_{ij}^k\psi^i\psi^j\frac{\p}{\p \psi^k}
\end{align*}
Let $\tl{C}^{ij}_k$ denote the structure constants of the dual Lie algebroid $L^*$:
\begin{align*}
[e^i,e^j]_{L^*}=\tl{C}^{ij}_ke^k.
\end{align*}
This bracket can be extended to arbitrary sections of $\Lambda^\bullet L^*$ and therefore gives a poisson bracket $\bracp$ on $C^\infty(L[1])$. The extension to $\Lambda^\bullet L^*$ is done via
\begin{align*}
[e^i,e^j\w e^k]_{L^*}=[e^i,e^j]_{L^*}\w e^k+e^j\w [e^i,e^k]_{L^*},
\end{align*}
and the action on functions on $M$ is by the anchor $\tl{a}$ or equivalently $\rd_{L^*}$ (definition of Lie algebroid)
\begin{align*}
[e^i,f(x)e^j]_{L^*}=f(x)[e^i,e^j]_{L^*}+\tl{a}(e^i)[f(x)] e^j=f(x)[e^i,e^j]_{L^*}+(\rd_{L^*}f(x))(e^i)e^j.
\end{align*}
The Poisson bracket $\bracp$ then gets inverted to a Symplectic form $\Omega$ and one finds a function $S$ on $L[1]$ such that 
\begin{align}\label{eq:S_def}
\rd S=\imath_Q\Omega.
\end{align}

{\bf To summarize}, the data of Lie algebroid $L$ gives the vector field $Q$ while the data of a Lie algebroid $L^*$ defines $\Omega$.

Let us demonstrate on some examples.
\begin{Ex}{\bf Tangent and cotangent bundles}
Let $(\p_i,dx^i)$ be local frames for $T$ and $T^*$. Denote the coordinates on $T^*M$ by $(x^i,p_i)$ and on $(x^i,v^i)$, where $p_i(dx^i)=\delta_i^j$ and $v^i(\p_i)=\delta^i_j$ (essentially $v^i$ can be identified with $dx^i$ and $p_i$ with $\p_i$). The Lie algebroid structure on $TM$ is given by the de-Rham complex and the Lie bracket
\begin{align*}
[\p_i,\p_j]=0,
\end{align*}
because $\p_i$ are holonomic. The anchor is identity and $\rd_L=dx^i\w \p_i$. The identification between $\se(\Lambda^\bullet T^*)=\Omega^\bullet$ is given by
\begin{align*}
\alpha(x)_{i\cdots k}dx^i\w \cdots\w dx^k \longleftrightarrow \alpha(x)_{i\cdots k} v^i\cdots v^k,
\end{align*}
so that $Q=v^i\p_i$. The Lie algebroid structure on $L=T^*$ is just trivial since the Courant bracket restricts to a zero bracket on one-forms. Therefore we would get a zero Poisson bracket on $C^\infty(L[1]=T[1]M)$.\footnote{In usual geometry the symplectic realization of a Poisson manifold $N$ with zero Poisson structure is $T^*N$ with the canonical symplectic structure but let's not go too into detail here} Even if we take the dual point of view, $L=T^*$, where we would get the canonical symplectic form on $T^*$, the vector field $Q$ would be zero because it would come from the trivial Lie algebroid structure on $T^*$. It is still worth working out how one ends up with the canonical $\Omega$. For this we need to determine the Poisson brackets $\{p_i,x^j\}$, $\{p_i,p_j\}$ and $\{x^i,x^j\}$ on $T^*[1]M$. The bracket $\{p_i,x^j\}$ is identified with $[\p_i,x^j]=\delta_i^j$, similarly $\{p_i,p_j\}=[\p_i,\p_j]=0$ and $\{x^i,x^j\}=[x^i,x^j]=0$ since the Lie bracket is of degree $-1$ and $x^i$ is a function, i.e. degree zero vector field. We therefore see we get the canonical Poisson structure.

This and more general examples are described in the book \cite[pg.~119]{weinsteingeomodels}.
\end{Ex}

\begin{Ex}
{\bf Symplectic structure (A-model)}
We now describe the Lie algebroids corresponding to the Example \eqref{ex:A-model}. Let's just follow the prescription above instead of what Pestun does (realizing the isomorphism between $T$ and $T^*$ given by $\omega$). Denote
\begin{align*}
L=\{X+\omega(X)\mid X \in \se(T)\}
\end{align*}
and 
\begin{align*}
L^*=\{X-\omega(X)=\ap-\omega^{-1}(\ap)\mid \ap \in \se(T^*)\}.
\end{align*}
The frame for $L$ is $e_i=\p_i+\omega_{ij}dx^j$ while the frame for $L^*$ is $e^i=dx^i-\omega^{ij}\p_j$. Coordinates on $L$ are $(x^i,\psi^i=v^i-\omega^{ij}p_j)$ and on $L^*$ $(x^i,\psi_i=p_i+\omega_{ij}v^j)$.

$L$ has the bracket $\brac_L$ given by (by simple calculation)
\begin{align*}
[X+\omega(X),Y+\omega(Y)]=[X,Y]+\omega([X,Y]),
\end{align*}
so that the structure constants for the frame above are $C_{ij}^k=0$. The anchor is $X+\omega(X)\mapsto X$ and $Q$ coming from the differential
\begin{align*}
Q=\psi^iA_i^\mu\p_\mu-\frac{1}{2}C_{ij}^k\psi^i\psi^j\frac{\p}{\p \psi^k}=(v^i-\omega^{ij}p_j)\p_i.
\end{align*}
The anchor of $L^*$ is projection onto the tangent component,
\begin{align*}
\tl{a}(e^i)=\tl{a}(dx^i-\omega^{ij}\p_j)=-\omega^{ij}\p_j \Longrightarrow \tl{A}^{ij}=-\omega^{ij}
\end{align*}
and the structure constants of $L^*$ are
\begin{align*}
\tl{C}^{ij}_ke^k&=[e^i,e^j]_c=[dx^i-\omega^{-1}(dx^i),dx^j-\omega^{-1}(dx^j)]_c\\
&=\omega^{-1}[dx^i,dx^i]_{\omega^{-1}}-[dx^i,dx^j]_{\omega^{-1}},
\end{align*}
where $[dx^i,dx^i]_{\omega^{-1}}$ is the Poisson Lie algebroid bracket on $T^*M$ defined by the Poisson structure $\omega^{-1}$ which satisfies $[dx^i,dx^i]_{\omega^{-1}}=\rd(\omega^{-1})^{ij}=\p_k\omega^{ij}dx^k$. We therefore see that
\begin{align*}
\tl{C}^{ij}_k(dx^k-\omega^{-1}(dx^k))=-(\p_k\omega^{ij}dx^k-\omega^{-1}(\p_k\omega^{ij}dx^k)),
\end{align*}
so that
\begin{align*}
\tl{C}^{ij}_k=-\p_k\omega_{ij}.
\end{align*}
By \cite[pg.~119]{weinsteingeomodels} we therefore see that the poisson bracket on $C^{\infty}(L[1])$ is given by
\begin{align*}
\{x^i,x^j\}&=0\\
\{\psi^i,\psi^j\}&=-\p_k\omega^{ij}\psi^k\\
\{\psi^i,x^j\}&=\omega^{ij}
\end{align*}
Taking now Darboux coordinates in which $\omega^{ij}$ is constant, we can easily invert the above Poisson structure and arrive at (up to sign I didn't bother to check)
\begin{align*}
\Omega=\omega_{ij}dx^i\w d\psi^j
\end{align*}
and since $Q=\psi^i\p_i$, we have $\imath_Q\Omega=\omega_{ij}\psi^i d\psi^j$ so that
\begin{align*}
S=\frac{1}{2}\omega_{ij}\psi^i\psi^j
\end{align*}
satisfies \eqref{eq:S_def}. Had we taken the dual point of view (i.e. switching the roles of $L$ and $L^*$), we would have gotten $Q=-\omega^{ij}\p_j$ with only non-zero Poisson bracket being $\{\psi_i,x^j\}=\delta_i^j$, which inverts to $\Omega=dx^i\w d\psi_j$ and we have $\imath_Q\Omega=\omega^{ij}\psi_i d\psi_j$ so that
\begin{align*}
S=\frac{1}{2}\omega^{ij}\psi_i \psi_j.
\end{align*}

\end{Ex}
\newpage

\section{Deformation by Hol. Poisson bi-vector and the LG model}
Let $I$ be a complex structure and $\beta$ a holomorphic Poisson bi-vector (i.e. a Holomorphic section of $\Lambda^2(T^{(1,0)})$). Decompose $\beta$ into its real and imaginary parts as $\beta=Re(\beta)+iIm(\beta)$. Because $\beta$ is in $\Lambda^2(T^{(1,0)})$, we have $\beta=-\frac{1}{4}(IQ+iQ)$ for some real Poisson bivector $Q$ of type $(2,0)+(0,2)$. Then we can deform the diagonal GC structure:
\begin{align*}
\begin{pmatrix}
-I & 0 \\
0 & I^*
\end{pmatrix}
\overset{\beta}{\longmapsto}
\begin{pmatrix}
-I & Q \\
0 & I^*
\end{pmatrix}.
\end{align*}

The $+i$ eigenbundle of the deformed GC structure is given by
\begin{align*}
L_\beta=\{X+\ap+\beta(\ap)\mid X\in T^{0,1},\ \ap \in T^*_{1,0}\}.
\end{align*}

Let now $E=T^*[2]T[1]M$ be the PQ manifold with coordinates $(x^i,v^a,p_i,\mu_a)$ of degrees $(0,1,2,1)$ corresponding to the CA $(\TT)M$, with the symplectic form
\begin{align*}
\Omega= dx^i\w dp_i+dv^a\w d\mu_a.
\end{align*}

Let now $z^i$ be the holomorphic coordinates on $M$ and we will denote the holomorphic splitting of the bundle $a$-index by $a=(j,\bar{j})$. Then $L_\beta$ defines a Lagrangian in $(E,\Omega)$ given by
\begin{align*}
L_\beta=\text{span}_{\mathbb C}\{x^i,v^j+\beta^{jk}\mu_k,\mu_{\bar{j}}\}
\end{align*}

The para-complex analogue is the following gen. para-cpx. structure
\begin{align*}
\KK_Q=\begin{pmatrix}
-K & 2Q \\
0 & K^*
\end{pmatrix},
\end{align*}
formally, everything is the same except $Q$ {\it is} the real Poisson bivector and the $+1$-eigenbundle is
\begin{align*}
L_Q=\{\tl{x}+\ap+Q(\ap)\mid \tl{x}\in T^{0,1},\ \ap \in T^*_{1,0}\}.
\end{align*}
This defines a Lagrangian in $(E,\Omega)$ is therefore given by
\begin{align*}
L_\beta=\text{span}_{\mathbb R}\{x^i,v^a+Q^{ab}\mu_b,\tl{\mu}_{{a}}\},
\end{align*}
where we introduced the para-complex splitting (given by $K$) of the $2n+2n$ degree $1$ coordinates:
\begin{align*}
v^j&=v^a+\tl{v}^b,\\
\mu_j&=\mu_a+\tl{\mu}_b,\ a=1\cdots n,\ b=n+1\cdots 2n,
\end{align*}
i.e. $v^j=v^a$ for $j=a=1\cdots n$ and $v^j=\tl{v}^b$ for $j+n=b=n+1\cdots 2n$ etc. The $-1$ eigenbundle of $\KK_Q$ is given by $T^{1,0}$, the $+1$-eigenbundle of $K$.

Lastly, there is the gen. para-cpx. structure that should yield the Poisson sigma model:
\begin{align*}
\KK_\Pi=
\begin{pmatrix}
-\id & 2Q \\
0 & \id
\end{pmatrix},
\end{align*}
where $Q$ is a real Poisson bivector. The $-1$ eigenbundle is just $T$ while the $+1$ eigenbundle is
\begin{align*}
L_Q=graph(Q)=\{\ap+Q(\ap)\mid \ap \in T^*\},
\end{align*}
with a corresponding Lagrangian in $(E,\Omega)$:
\begin{align*}
L_Q=\text{span}_{\mathbb R}\{x^i,v^i+Q^{ij}\mu_j\}.
\end{align*}

\bibliographystyle{JHEP}
\bibliography{mybib1}
\end{document}

### 2019-11-22 oldstuff/notes, questions etc.tex
merge

\documentclass{article}
\usepackage{amssymb, amsmath, amsthm, mathtools, bbm, tikz-cd,stmaryrd,enumerate}
%-------------------
\usepackage{fancyhdr}
\pagestyle{fancy}
\fancyhf{}
\fancyhead[L]{\leftmark}
\fancyhead[R]{\thepage}
%----------------
\newcommand{\TT}{{T\oplus T^*}}
\newcommand{\JJ}{\mathcal{J}}
\newcommand{\KK}{\mathcal{K}}
\newcommand{\GG}{\mathcal{G}}
\newcommand{\Cc}{\mathbf{C}}
\newcommand{\RR}{\mathbb{R}}
\newcommand{\XX}{\mathfrak{X}}
\newcommand{\HH}{\mathcal{H}}
\newcommand{\FF}{\mathcal{F}}
\newcommand{\QQ}{\mathcal{Q}}
%----------------------------------------
\newcommand{\PP}{\mathrm{P}}
\newcommand{\PPt}{\tilde{\mathrm{P}}}
\newcommand{\id}{\mathbbm{1}}
\newcommand{\nlr}{\overset{\leftrightarrow}{\n}}
\newcommand{\lc}{\mathring{\n}}
\newcommand{\im}{\mathrm{Im}\,}
\newcommand{\Ker}{\mathrm{Ker}\,}
\newcommand{\Lie}{\mathcal{L}}
\newcommand{\PS}{\mathcal{P}}
\newcommand{\ap}{\alpha}
\newcommand{\bt}{\beta}
\def\w{\wedge}
\newcommand{\p}{\partial}
\newcommand{\pt}{\tilde{\partial}}
\newcommand{\xt}{{\tilde{x}}}
\newcommand{\n}{\nabla}
\newcommand{\rd}{\mathrm{d}}
\newcommand{\PH}{(\PS,\eta,\omega)}
\newcommand{\Lt}{\tl{L}}
\newcommand{\Lb}{\mathbb{L}}
\newcommand{\s}{\mathbf{s}}
\newcommand{\se}{\Gamma}
\newcommand{\Endo}{\text{End}}
\newcommand{\ellt}{{\tl{\ell}}}
\newcommand{\ot}{{1/2}}
\newcommand{\inv}{{-1}}
\newcommand{\Aa}{\mathcal{A}}
\newcommand{\la}{\langle}
\newcommand{\ra}{\rangle}
\newcommand{\lara}{\la\ ,\ \ra}
\newcommand{\brac}{[\ ,\ ]}
\newcommand{\bl}{[\![}
\newcommand{\br}{]\!]}
\newcommand{\bracd}{\bl \ ,\ \br}
\newcommand{\yt}{\tl{y}}
\newcommand{\zt}{\tl{z}}
\newcommand{\tth}{\tl{\theta}}
\newcommand{\kk}{\mathrm{k}}
%----------------------------------------
\def\gld{generalized Lie derivative }
\def\glds{generalized Lie derivatives }
\def\tl{\tilde}

% These will be typeset in italics
\newtheorem{theorem}{Theorem}[section]
\newtheorem{proposition}[theorem]{Proposition}
\newtheorem{lemma}[theorem]{Lemma}
\newtheorem{corollary}[theorem]{Corollary}
\newtheorem{fact}[theorem]{Fact}
\newtheorem*{theorem*}{Theorem}
\newtheorem*{lemma*}{Lemma}
\newtheorem*{proposition*}{Proposition}
\newtheorem{Rem}[theorem]{Remark}

% These will be typeset in Roman
\theoremstyle{definition}
\newtheorem{Def}[theorem]{Definition}
\newtheorem{Conj}[theorem]{Conjecture}

\theoremstyle{definition}
\newtheorem*{notation*}{Notation}
\newtheorem*{definition*}{Definition}

\theoremstyle{remark}
\newtheorem*{remark*}{Remark}
\newtheorem{Ex}[theorem]{Example}
\newtheorem{question}[theorem]{Question}
\newenvironment{claim}[1]{\par\noindent\underline{Claim:}\space#1}{}
\newenvironment{claimproof}[1]{\par\noindent\underline{Proof:}\space#1}{\hfill $[acksquare$}

\input xy

\xyoption{all}

\DeclareMathOperator{\End}{End}
\DeclareMathOperator{\rk}{rk}

\begin{document}
\section{Para-Complex Geometry}
In this section we introduce para-complex geometry with emphasis on the analogy with complex geometry. More details can be found for example in \cite[Ch.~15]{Cortes:2010ykx}.

\begin{Def}\label{def:paracpx}
An (almost) {\bf product structure} on a smooth manifold is an endomorphism $K\in \Endo(T\PS)$ which squares to identity, $K^2=\id_{T\PS}$, $K\neq \id$. An (almost) \textbf{para-complex structure} is a product structure such that the $+1$ and $-1$ eigenbundles of $K$ have the same rank.
\end{Def}
A direct consequence of above definition is that any para-complex manifold is of even dimension. From now on, the $+1$ and $-1$ eigenbundles of an almost product/para-complex structure will be denoted $L$ and $\Lt$, respectively.

\paragraph{(half-)Integrability} The use of the word {\it almost} as usual refers to integrability of the endomorphism, i.e. whether its eigenbundles are involutive with respect to the Lie bracket and therefore define a foliation of the underlying manifold. Similarly to the complex case, the integrability is governed by the \textbf{Nijenhuis tensor}
\begin{align}\label{eq:nijenhuis}
\begin{aligned}
N_K(X,Y)&=[X,Y]+[KX,KY]-K([KX,Y]+[X,KY])\\
&=(\n_{KX}K)Y+(\n_XK)KY-(\n_{KY}K)X-(\n_YK)KX\\
&=4(\PP[\PPt X,\PPt Y]+\PPt[\PP X,\PP Y]),
\end{aligned}
\end{align}
where $\n$ is any torsionless connection and $\PP\coloneqq\frac{1}{2}(\id+K)$ and $\PPt\coloneqq\frac{1}{2}(\id-K)$ are the projections onto $L$ and $\Lt$, respectively. We say $K$ is integrable and call $K$ a product/para-complex manifold if $N_K=0$. From \eqref{eq:nijenhuis} it is apparent that $K$ is integrable if and only if {\it both} eigenbundles are simultaneously Frobenius integrable, i.e. involutive distributions in $T\PS$. This is one of the main differences between complex and para-complex geometry; one of the eigenbundles can be integrable while the other is not. For this reason, it is useful to introduce the notion of {\bf half-integrability}:

\begin{Def}
Let $K$ be an almost para-complex/product structure. If the $+1$ ($-1$) eigenbundle is Frobenius integrable, we call $K$ a {\bf p-para-complex/product} ({\bf n-para-complex/product}) structure. A $K$ that is both p- and n- para-complex/ is simply a para-complex/product structure.
\end{Def}

\paragraph{Para-Complexification}
The analogy between complex and para-complex geometry can be made manifest by {\it para-complexifying} -- this amounts to introducing the algebra of para-complex numbers $\Cc=\RR\oplus \kk\RR$, where $\kk^2=1$ is the para-complex unit, and take linear combinations over $\Cc$. All tensorial objects can be extended to be $\Cc$-linear, in particular, the para-complexified tangent bundle decomposes as $T\PS\otimes \Cc\coloneqq T\PS^\Cc=T^{(1,0)}\oplus T^{(0,1)}$ to the $\pm \kk$ eigenbundles of the endomorphism $K$, now extended by linearity to $\End(T\PS^\Cc)$. The algebra $\Cc$ has the natural operations
\begin{align}
\begin{aligned}
&\bullet\quad \text{Conjugation: }x+\kk y\mapsto \overline{x+\kk y}=x-\kk y\\
&\bullet\quad \text{Real part: } x+\kk y \mapsto \text{Re}(x+\kk y)=x\\
&\bullet\quad \text{Imaginary part: } x+\kk y \mapsto \text{Im}(x+\kk y)=y.
\end{aligned}
\end{align}
There is an isomorphism between the para-complex vector spaces $\Cc^n$ and $\RR^{2n}$, explicitly (see \cite[Ch.~15]{Cortes:2010ykx} for more details):
\begin{align}\label{tab:identification}
\begin{array}{ccc}
(\Cc^n,\kk)&\simeq &(\RR^{2n},\id\times -\id)\\
(x^i+\kk y^i)_{i=1,\cdots,n} &\mapsto & (x^i+y^i,x^i-y^i)_{i=1,\cdots,n}\\
(\frac{x^i+\xt_i}{2}+\kk\frac{x^i-\xt_i}{2})_{i=1,\cdots,n} &\mapsfrom & (x^i,\xt_i)_{i=1,\cdots,n}.
\end{array}
\end{align}

\paragraph{Para-Holomorphic structure}
Let now $(\mathcal{P},K)$ be an almost para-complex manifold. If $K$ is integrable, we get a set of $2n$ coordinates $(x^i,\tilde{x}_i)$ called {\bf adapted coordinates}, $\mathcal{P}$ locally splits as $M\times \tilde{M}$, and $K$ acts as identity on $TM=L$ and negative identity on $T\tilde{M}=\tilde{L}$. The adapted coordinates therefore define two complimentary foliations of $\PS$. After para-complexification, we get $n$ {\bf holomorphic coordinates} \footnote{We should use the word para-holomorphic instead of holomorphic but we choose to omit the prefix ``para-" whenever no confusion with complex geometry is possible and recovering it only when needed.} $z^i=\frac{x^i+\xt_i}{2}+\kk \frac{x^i-\xt_i}{2}$, and the conjugate {\bf anti-holomorphic coordinates} $\bar{z}^i=\frac{x^i+\xt_i}{2}-\kk \frac{x^i-\xt_i}{2}$. The notion of holomorphicity in the context of para-complex geometry is now entirely analogous to complex geometry. As usual, a map of para-complex manifolds is called para-holomorphic if its pushforward commutes with the respective para-complex structures
\begin{Def}
Let $(M,K_M)$ and $(N,K_N)$ be para-complex manifolds. A map $F:M\rightarrow N$ is called para-holomorphic if
\begin{align}\label{eq:def_parahol}
K_N\circ F_*=F_*\circ K_M
\end{align}
\end{Def}

Locally, the map $F:M\rightarrow N$ of para-complex manifolds can be understood via composition of coordinates as a
\begin{align*}
F&: \RR^{2n}\rightarrow \RR^{2m}\\
F=(f^i,\tl{f}_j)&=(y^i(x^k,\xt_l),\yt_j(x^k,\xt_l))^{i,j=1,\cdots,m}_{k,l=1,\cdots, n}, 
\end{align*}
where $(x^k,\xt_l)$ and $(y^i,\yt_j)$ are the adapted coordinates on $M$ and $N$, respectively, or (after para-complexification) as a map
\begin{align*}
F&: \Cc^n\rightarrow \Cc^m\\
F&=F^i(z^k,\bar{z}^k)^{i=1,\cdots,m}_{k=1,\cdots, n}, 
\end{align*}
It is easy to check from \eqref{eq:def_parahol} that $F$ is a para-holomorphic map iff its components do not depend on anti-holomorphic coordinates on $M$, i.e.
\begin{align}\label{eq:holomorphic}
\frac{\p}{\p \bar{z}^k} F^j=\frac{\p}{\p z^k} \bar{F}^j=0.
\end{align}
In the real, adapted coordinates, the condition \eqref{eq:def_parahol} reads
\begin{align}\label{eq:holomorphic_real}
\frac{\p}{\p \xt_i}f^j=\frac{\p}{\p x^i}\tl{f}_j=0.
\end{align}
The equivalence between \eqref{eq:holomorphic} and \eqref{eq:holomorphic_real} can be checked using the relationships \eqref{tab:identification}.

The conditions \eqref{eq:holomorphic_real} tell us that the holomorphic functions preserve the foliations defined by the adapted coordinates on $M$ and $N$. This also means that the transition functions on a para-complex manifold (seen as maps $\RR^{2n}\rightarrow \RR^{2n}$) are holomorphic since the foliations must be preserved, i.e. the coordinates transform as
\begin{align*}
(x^i,\xt_i)\mapsto (y^j(x^i),\yt_j(\xt_i)).
\end{align*}

\paragraph{Type decomposition} The splitting of the tangent bundle $T\PS=L\oplus \Lt$ in the real case and $T\PS^\Cc$ in the para-complex case gives rise to a decomposition of tensors analogous to the $(p,q)$-decomposition in complex geometry. For differential forms, we denote the real and para-complex decompositions as
\begin{align}\label{eq_plusminus_decomp}
\Lambda^k (T^*\mathcal{P})&=\bigoplus_{k=m+n}\Lambda^{(+m,-n)}(T^*\mathcal{P}),\\
\Lambda^k (T^*\mathcal{P}^\Cc)&=\bigoplus_{k=m+n}\Lambda^{(m,n)}(T^*\mathcal{P}),
\end{align}
where $\Lambda^{(+m,-n)}(T^*\mathcal{P})=\Lambda^m(L^*)\otimes \Lambda^n(\Lt^*)$ and $\Lambda^{(m,n)}(T^*\mathcal{P})=\Lambda^m(T^{(1,0)*})\otimes \Lambda^n(T^{(0,1)*})$. The corresponding sections are denoted by $\Omega^{(+m,-n)}(\mathcal{P})$ and $\Omega^{(m,n)}$, respectively. The bigradings \eqref{eq_plusminus_decomp} yield the natural projections
\begin{align*}
\Pi^{(+p,-q)}:\Lambda^k(T^*\mathcal{P})&\rightarrow \Lambda^{(+p,-q)}(T^*\mathcal{P}),\\
\Pi^{(p,q)}:\Lambda^k(T^*\mathcal{P}^\Cc)&\rightarrow \Lambda^{(p,q)}(T^*\mathcal{P}),
\end{align*}
so that when $K$ is integrable, the de-Rham differential splits as $\rd=\p_++\p_-$, in the real case and $\rd=\p+\bar{\p}$ in the para-complexified case, where
\begin{align*}
\begin{array}{cc}
\p_+ \coloneqq \Pi^{(+p+1,-q)}\circ \rd, & \p_- \coloneqq \Pi^{(+p,-q-1)}\circ \rd,\\
\p \coloneqq \Pi^{(p+1,q)}\circ \rd, & \bar{\p} \coloneqq \Pi^{(p,q+1)}\circ \rd,
\end{array}
\end{align*}
are the \textbf{para-complex Dolbeault operators}, satisfying
%\begin{align}\label{eq:partials_plusminus}
%\begin{aligned}
%\p_+&:\Omega^{(+p,-q)}(\mathcal{P})\rightarrow \Omega^{(+p+1,-q)}(\mathcal{P})\\
%\p_-&:\Omega^{(+p,-q)}(\mathcal{P})\rightarrow \Omega^{(+p,-q-1)}(\mathcal{P}),
%\end{aligned}
%\end{align}
\begin{align*}
\p_+^2=\p_-^2=\p_+\p_-+\p_-\p_+&=0\\
\p^2=\bar{\p}^2=\p\bar{\p}+\bar{\p}\p&=0
\end{align*}

One can also introduce the {\it twisted differential $\rd^p\coloneqq(\Lambda^{k+1}K^*)\circ\rd\circ (\Lambda^kK^*)$}. When $K$ is integrable, it can be simply written as $\rd^p=(\p_++\p_-)$ on real forms and $\rd^p=\kk (\p+\bar{\p})$ on para-complex forms.

%\begin{lemma}
%Let $(\PS,K)$ be a paracomplex manifold. Then $\rd^p\coloneqq(\Lambda^{k+1}K)\circ\rd\circ (\Lambda^kK)$ can be expressed as
%\begin{align}\label{eq:dp-operator}
%\rd^p=\p_+-\p_-.
%\end{align}
%\end{lemma}
%\begin{proof}
%Let $\ap \in \Omega^{+m,-n}(\PS)$. Then we have
%\begin{align*}
%\rd^p\ap=(-1)^n(\Lambda^kK)\rd\ap=(-1)^{2n}\p_+ \ap +(-1)^{2n+1}\p_-\ap=(\p_+-\p_-)\ap,
%\end{align*}
%\end{proof}

\section{Generalized Geometry}
In this paper, the term {\it generalized geometry} is used for the study of geometrical structures on the bundle $(\TT)M$ over some manifold $M$. We will typically abbreviate this to $\TT$ whenever the base is understood or unimportant for the discussion.

\subsection{The Exact Courant Algebroid Structure}
The bundle $\TT$ has a natural Courant algebroid structure given by the symmetric pairing
\begin{align*}
\langle X+\ap,Y+\bt\rangle=\ap(Y)+\bt(Y),
\end{align*}
the Dorfman bracket,
\begin{align}\label{eq:dorfman}
[ X+\ap,Y+\bt]=[X,Y]+\Lie_X\bt-\imath_Y\rd \ap, 
\end{align}
and the anchor $\pi:X+\ap\mapsto X$. In the above, $X+\ap$ denotes a section of $\TT$ with the splitting to tangent and cotangent parts given explicitly. The Dorfman bracket can be thought of as an extension of the Lie bracket from $T$ to $\TT$ and therefore we opt to use the same notation for both brackets; the expression $[X,Y]$ is always the Lie bracket of vector fields whether we think of $\brac$ as the Lie bracket or the Dorfman bracket and no confusion is therefore possible.

The Courant algebroid on $\TT$ is exact, meaning that the associated sequence
\begin{align}\label{eq:exact_seq}
0\longrightarrow T^* \overset{\pi^T}{\longrightarrow} \TT\overset{\pi}{\longrightarrow} T\longrightarrow 0,
\end{align}
is exact. Here, $\pi^T$ is the transpose of $\pi$ with respect to the pairing $\lara$,
%\begin{align*}
%\la \pi^T(\ap),Y+\bt\ra=\la \ap,\pi(Y+\bt)\ra=\la \ap,Y\ra
%\end{align*}
i.e. $\pi^T: \ap \mapsto \ap+0$. In fact, all possible Courant algebroid structures on $\TT$ are parametrized by a closed three-form $H\in \Omega^3_{cl}$, which enters the definition of the bracket \eqref{eq:dorfman}, changing it to a {\it twisted} Dorfman bracket
\begin{align*}
[ X+\ap,Y+\bt]_H=[X,Y]+\Lie_X\bt-\imath_Y\rd \ap+\imath_Y\imath_X H.
\end{align*}
Moreover, any isotropic splitting of \eqref{eq:exact_seq} $s:T\rightarrow \TT$ is given by a two-form $b$, such that $X\overset{s}{\mapsto}X+b(X)$. This is equivalent to an action of a $b$-field transformation on $\TT$\footnote{Here we are using the term $b$-field transformation more liberally as it is customary to use the term only in the cases when $\rd b=0$ so that $e^b$ is a symmetry of $\brac$.}
\begin{align*}
e^b=
\begin{pmatrix}
\id & 0 \\
b & \id
\end{pmatrix}
\in \End(\TT),
\end{align*}
which consequently changes the bracket as
\begin{align*}
[ e^b(X+\ap),e^b(Y+\bt)]_H=e^b([ X+\ap,Y+\bt]_{H+\rd b}),
\end{align*}
which implies that when $H$ is trivial in cohomology, then a choice of a $b$-field transformation such that $\rd b=-H$ brings the twisted bracket $\brac_H$ into the standard form \eqref{eq:dorfman}. When $H$ is cohomologically non-trivial this can be done at least locally. This also means that any choice of splitting with a non-trivial $b$-field can be absorbed in the Courant algebroid bracket in terms of the {\it flux}\footnote{Flux is a term used mainly in physics, in this context simply meaning the ``tensorial contribution to the bracket''.} $\rd b$.

We remark here that all the results in this paper remain valid for any exact courant algebroid $E$ (i.e. $E$ fits in the sequence \eqref{eq:exact_seq}), which can be always identified with $\TT$ by the choice of splitting equivalent to a choice of a representative $H\in\Omega^3_{cl}$. This also amounts to setting $b=0$ in all formulas since the $b$-field appears as a difference of two splittings.

\subsection{Generalized Para-K\"ahler Geometry}
We now introduce the notion of a generalized para-complex and a generalized para-K\"ahler structure. More details on this can be found in \cite{inprogress}.
\begin{Def}
A \textbf{(twisted) generalized para-complex} (GpC) structure $\KK$ is an endomorphism of $\TT$, such that $\KK^2=\id$ and $\la\KK,\KK\ra=-\lara$, whose generalized Nijenhuis tensor vanishes:
\begin{align}\label{eq:gen_nijenhuis}
\mathcal{N}_\KK(u,v)=[\KK u,\KK v]_H+\KK^2[ u,v]_H-\KK([\KK u,v]_H+[ u,\KK v]_H)=0.
\end{align}
\end{Def}
It is easy to check that the condition \eqref{eq:gen_nijenhuis} is equivalent to the $\pm 1$ eigenbundles of $\KK$ to be involutive under the twisted Dorfman bracket. Since in this paper the flux $H$ will be generically non-zero but all results hold for the special case $H=0$ as well, we will drop the word ``twisted" from our definitions.
\begin{Def}
An (almost) \textbf{Generalized para-K\"ahler structure} (GpK) is a commuting pair $(\KK_+,\KK_-)$ of GpC structures, such that their product $\GG=\KK_+\KK_-$ defines a split-signature metric $G$ on $\TT$ via
\begin{align*}
G(\cdot,\cdot)\coloneqq \la \GG\cdot,\cdot\ra.
\end{align*}
\end{Def}
Similarly to generalized K\"ahler structures, the GpK structures can be equivalently given in terms of a pair of para-Hermitian structures satisfying a particular integrability condition:
\begin{theorem}[\cite{inprogress}]
The data of a GpK structure is equivalent to a pair of para-Hermitian structures $(\eta,K_+,K_-)$, such that $\KK_\pm$ are given by
\begin{align}\label{eq:GpK_genform}
\KK_{\pm}=\frac{1}{2}
\begin{pmatrix}
\id & 0 \\
b & \id
\end{pmatrix}
\begin{pmatrix}
K_+\pm K_- & \omega^{-1}_+\mp \omega^{-1}_- \\
\omega_+\mp \omega_- & -(K_+^*\pm K_-^*)
\end{pmatrix}
\begin{pmatrix}
\id & 0 \\
-b & \id
\end{pmatrix},
\end{align}
for some $2$-form $b$. The integrability of $\KK_\pm$ then translates into $K_\pm$ being integrable and satisfying
\begin{align*}
\n^\pm K_\pm=0,
\end{align*}
where the connections $\n^\pm$ are defined by the Levi-Civita connection $\lc$ of $\eta$ and the $H$-flux:
\begin{align*}
\eta(\n^\pm_XY,Z)=\eta(\lc_XY,Z)\pm\frac{1}{2}(H+\rd b).
\end{align*}
\end{theorem}

The additional integrability condition on $K_\pm$, $\n^\pm K_\pm$, can be equivalently expressed using the fundamental forms associated to $K_\pm$, $\omega_\pm=\eta K_\pm$, and a para-complex version of the $\rd^c$-operator, which we call $\rd^p$:
\begin{align*}
\n^\pm K_\pm=0 \Longleftrightarrow \rd^p_\pm\omega_\pm=\pm (H+\rd b).
\end{align*}
$\rd^p_\pm$ here denote the $\rd^p$ operators associated to $K_\pm$, $\rd^p_\pm\coloneqq K_\pm^*\circ \rd\circ K_\pm^*$. We will call the geometry given by the data $(\eta, K_\pm, H+\rd b)$ above a {\bf bi-para-Hermitian} geometry.

\subsection{Isomorphism between $\TT$ and $T\oplus T$}\label{sec:isomorphism}
In both the GK and GpK cases we have an isomorphism between $\TT$ and $T\oplus T$ at our disposal. This is because  the bundle $\TT$ splits into eigenbundles $C_\pm$ of the generalized (indefinite) metric $\GG=-\JJ_+\JJ_-$ (in GpK case $\GG=\KK_+\KK_-$). These eigenbundles are isomorphic to the tangent bundle $T$ via:
\begin{align*}
\pi_\pm:C_\pm &\simeq T\\
X+\ap &\overset{\pi_\pm}{\mapsto} X\\
X+(b\pm g)X &\overset{\pi^{-1}_\pm}{\mapsfrom} X,
\end{align*}
where $g$ and $b$ are the defining data of $\GG$. Therefore, since $\TT=C\oplus C_-$, we also have $\TT\simeq T\oplus T$:
\begin{align}
\begin{aligned}
(X_+,X_-)\overset{\pi^{-1}_+\oplus \pi^{-1}_-}{\longmapsto}& X_++(b+g)X_++X_-+(b-g)X_-\\
&=
\begin{pmatrix}
 X_++X_- \\
 g(X_+-X_-)+b(X_++X_-)
\end{pmatrix}.
\end{aligned}\label{map_pi_pm}
\end{align}
In particular, one can check that $\pi_+\oplus \pi_-$ maps the eigenbundles of the tangent bundle structures $J_\pm$ ($K_\pm$) to eigenbundles of the corresponding generalized structures $\JJ_\pm$ ($\KK_\pm$). This is because there is an explicit relationship,
\begin{align*}
J_+=\pi_+\JJ_\pm\pi_+^{-1},\quad J_-=\pm\pi_-\JJ_\pm\pi_-^{-1},
\end{align*}
and analogously between $\KK_\pm$ and $K_\pm$. From here, it is easy to see that the $-i$ eigenbundle of $\JJ_+$ $L^{0,1}_+$, for example, is given by
\begin{align*}
L^{0,1}_+=\pi_+^{-1}(T^{(0,1)_+})\oplus\pi_-^{-1}(T^{(0,1)_-}),
\end{align*}
where $T^{(1,0)_\pm}$ denotes the $+i$ eigenbundle of the structures $J_\pm$. Analogously, the $+i$ eigenbundle of $\JJ_-$,
$L^{1,0}_-$, is given by
\begin{align*}
L^{1,0}_-=\pi_+^{-1}(T^{(1,0)_+})\oplus\pi_-^{-1}(T^{(0,1)_-}),
\end{align*}
and so on. Therefore, one should think about the pair $J_\pm$ corresponding to the GK structure as each of the $J_\pm$ acting on its own copy of $T$, which are then mapped to $C_\pm$ in $\TT$.

\paragraph*{Relationship to Kapustin-Li}
On pg. 12 of Kapustin-Li paper they implicitly use the isomorphisms $\pi_\pm$ to map the sections $\chi \in \se(T^{(0,1)_+})$ and $\lambda \in \se(T^{(0,1)_-})$ to the $-i$ eigenbundle of $\JJ_+$ as 
\begin{align*}
\begin{pmatrix}
\chi+\lambda \\
g(\chi-\lambda)
\end{pmatrix},
\end{align*}
which is the same as \eqref{map_pi_pm} with $b=0$, which they implicitly absorb inside the $H$-flux.

\subsection{SKT Geometry and Half Generalized Structures}
An {\bf SKT} structure is a Hermitian structure $(I,g)$ for which the fundamental form $\omega$ even though is not closed, is $\rd \rd^c$-closed, i.e. $\rd \rd^c \omega=0$. The version of this geometry is easily formulated for the para- case where we will call it para-SKT. It follows directly from the definition that the bi-para-Hermitian geometry consists of two such structures -- one for each chirality -- and here we will describe how one SKT structure can be described using the language of generalized geometry.

For this purpose we define a positive-chirality\footnote{Similarly one could define a negative-chirality half G(p)C structure by changing $C_+$ for $C_-$} {\bf half generalized almost (para-)complex structure} as a pair $(\GG,\JJ_{C_+})$, where $\GG$ is a (neutral) generalized metric which induces a splitting $\TT=C_+\oplus C_-$ and an isomorphism $C_+\oplus C_-\simeq T\oplus T$, and $\JJ_{C_+}$ is a (para-)complex endomorphism of $C_+$, i.e.
\begin{align*}
\JJ_{C_+}\in \End(C_+),\quad \JJ_{C_+}=\pm \id_{C_+},\quad \la \JJ_{C_+} u_+,v_+\ra=-\la u_+,\JJ_{C_+} v_+\ra,
\end{align*}
for any $u_+,v_+ \in \se(C_+)$. The integrability condition on $\JJ_{C_+}$ is then that its eigenbundles $\ell_+\oplus \ell_-=C_+$ (in the complex case $\ell\oplus \bar{\ell}=C_+\otimes \mathbb{C}$) are involutive with respect to the (twisted) Dorfman bracket. It is easy to see that $\JJ_{C_+}$ defines a (para-)Hermitian structure $(J_+,g)$, where
\begin{align*}
g(X,Y)=\frac{1}{2}\la \pi_+^{-1}X,\pi_+^{-1}Y\ra,\quad J_+=\pi_+\JJ_{C_+}\pi^{-1}_+
\end{align*}
and the integrability condition on $\JJ_{C_+}$ translates into the condition
\begin{align*}
\n^+J_+=0,\ \n^+=\lc+\frac{1}{2}g^{-1}(H+\rd b) \Longleftrightarrow \rd^{c/p}\omega_+=H+\rd b,
\end{align*}
i.e. giving exactly half of the data of a G(p)K geometry. If there is a negative-chirality half structure $\JJ_{C_-}$, then $(\GG,\JJ\coloneqq \JJ_{C_+}\oplus \JJ_{C_-})$ defines a genuine G(p)K structure.

\section{Twisted (2,2) SUSY and GpK Geometry}\label{sec:susy_gpk}
In this subsection we explain how GpK geometry naturally appears in $2D$ $(2,2)$ supersymmetric sigma models, more concretely in {\bf twisted} supersymmetric models. We compare this with the well-known story about how GK geometry appears in the usual $(2,2)$ supersymmetry. More details about this can be found in \cite{HullTwistedSUSY,royston2005geometry}.

\paragraph*{$(1,1)$ SUSY} Let $\hat{\Sigma}$ be a superworldsheet, i.e. a Riemann surface (with coordinates $\sigma$, $\tau$) equipped with formal odd coordinates $\theta^\pm_1$. We consider the general $(1,1)$ SUSY sigma model given by the action
\begin{align}\label{eq:(1,1)action}
S_{(1,1)}(\Phi)=\int_{\hat{\Sigma}}[g(\Phi)+b(\Phi)]_{ij}D^1_+\Phi^iD^1_-\Phi^j,
\end{align}
where $\Phi=(\Phi^i)_{i=1\cdots n}$ are $(1,1)$ {\it superfields} -- maps $\phi: \hat{\Sigma} \rightarrow (M,g)$, $(M,g)$ being (for now) arbitrary pseudo-Riemannian manifold, $b$ denotes a local two-form and $D_\pm$ are the superderivatives
\begin{align}\label{eq:D1}
D^1_\pm=\frac{\p}{\p \theta_1^\pm}-\theta_1^\pm \p_\pm.
\end{align}
Here $\p_\pm=\frac{\p}{\p x_\pm}$ are derivatives along the lightcone coordinates on $\Sigma$, $x_\pm=\tau\pm\sigma$. The superfield $\Phi$ can be expanded in powers of $\theta_\pm$:
\begin{align*}
\Phi^i(\sigma,\tau,\theta_+,\theta_-)=\phi^i(\sigma,\tau)+\psi^i_+(\sigma,\tau)\theta^++\psi_-(\sigma,\tau)\theta^-+F^i(\sigma,\tau)\theta^+\theta^-.
\end{align*}
The components $\phi: \Sigma \rightarrow (M,g)$ can be identified with local coordinates on $M$ along the embedding of $\Sigma$. $(1,1)$ supersymmetry means that the action \eqref{eq:(1,1)action} is invariant under transformations generated by the two {\it supercharges} $Q^1_\pm$, 
\begin{align}\label{eq:Q1}
Q^1_\pm=\frac{\p}{\p \theta_1^\pm}+\theta_1^\pm \p_\pm,
\end{align}
obeying the supercommutation relations
\begin{align}\label{eq:(1,1)_susy}
\{Q^1_\pm,Q^1_\pm\}=2\p_\pm.
\end{align}

\paragraph*{$(2,2)$ SUSY} The idea now is to study under which conditions the action $S_{(1,1)}$ admits additional supersymmetries. It turns out that this puts severe restrictions on the required geometry of $M$. In particular, if we are to extend the supersymmetry to $(2,2)$, $(M,g)$ necessarily needs to be a GK manifold. If the $(1,1)$ supersymmetry is to be extended to a twisted $(2,2)$ supersymmetry, the target manifold needs to be a GpK manifold.

The two additional supersymmetries necessarily transform the fields by \cite{HullTwistedSUSY},
\begin{align}\label{eq:extended_susy}
\delta\Phi^i=(\epsilon^+Q_+^2+\epsilon^-Q_-^2)\Phi=\epsilon^+ (T_+)^i_jD^1_+\Phi^j+\epsilon^- (T_-)^i_jD^1_-\Phi^j,
\end{align}
for some target space tensors $T_\pm$. The requirement that the action \eqref{eq:(1,1)action} is invariant under this transformation forces the compatibility between $(g+b)$ and $T$:
\begin{align*}
g(T_\pm\cdot,\cdot)+g(\cdot,T_\pm\cdot)&=0\\
b(T_\pm\cdot,\cdot)+b(\cdot,T_\pm\cdot)&=0,
\end{align*}
along with the condition
\begin{align*}
\n^\pm T_\pm=0,
\end{align*}
where $\n^\pm$ are given by
\begin{align*}
\n^\pm=\lc\pm \frac{1}{2}H,
\end{align*}
$\lc$ being the Levi-Civita connection of $g$ and $H$ a closed global three-form, such that $b$ is locally its potential, $\rd b=H$. The additional requirement that the corresponding supercharges $Q^2_\pm$ generate supersymmetry, i.e. square to translations via \eqref{eq:(1,1)_susy}, imposes additional conditions on $T_\pm$:
\begin{align*}
T_\pm^2=-\id\quad N_\pm=0,
\end{align*}
where $N_\pm$ are the Nijenhuis tensors of $T_\pm$.
This implies that $(g,T_\pm=I_\pm,b)$ defines a bi-Hermitian structure, or equivalently, forces $M$ to be generalized K\"ahler \cite{Gualtieri:2003dx}. Alternatively, we can require that the supercharges $Q'_\pm$ generate para-supersymmetry\footnote{This type of fermionic symmetry was called {\it twisted} in \cite{HullTwistedSUSY} but we intentionally avoid this name because the word {\it twist} is used in this work for at least two different notions already}, i.e.
\begin{align}\label{eq:(1,1)_parasusy}
\{Q^2_\pm,Q^2_\pm\}=-2\p_\pm,
\end{align}
which forces
\begin{align*}
T_\pm^2=\id\quad N_\pm=0,
\end{align*}
rendering $(g,T_\pm,b)$ a bi-para-Hermitian data, or equivalently, $M$ to be a GpK manifold. When we require that the theory is parity-symmetric, we find that the $b$-field term in \eqref{eq:(1,1)action} has to vanish and additionally $T_+=T_-=T$, which gives the (para-)K\"ahler limits of the geometries.

\paragraph*{$(2,1)$ SUSY} The above discussion specializes to a $(2,1)$ (or equivalently $(1,2)$) supersymmetry by simply setting one of the generators in \eqref{eq:extended_susy} to zero, therefore we only get one additional (para-)hermitian structure $T$ that is covariantly constant with respect to $\n=\lc+\frac{1}{2}H$. This geometry is in the complex setting called an {\it SKT} structure -- it is a special type of a Hermitian structure for which the fundamental form $\omega$ is $\rd \rd^c$ closed. In the para-complex setting we will call such geometry a {\it para-SKT} structure.

\paragraph*{$(2,0)$ SUSY} We can also consider the $(2,0)$ SUSY. In this case the geometry is the same as in $(2,1)$ (i.e. para-SKT) except the field content is different, consisting of Chiral and Fermi multiplets.

\paragraph*{Higher SUSY}  One might require additional supersymmetry, which requires additional (para-)complex structure that anti-commutes with $T$, which therefore desribes the (para-)hyper-K\"ahler limit of GK/GpK geometry. Various other heterotic $(p,1)$ supersymmetries can be realized as well, all as special cases of the GK/GpK geometry \cite{HullTwistedSUSY}.

We conclude a remark -- the signature of $g$ is a priori not fixed, therefore the above discussion generalizes to GK (GpK) geometries with different signature metrics and we recover genuine GK or GpK geometry only when we require that $g$ is Riemannian or split, respectively. This is also the case we will study in this paper.

\paragraph{Off-Shell SUSY and Restricted Fields}
It has been shown in \cite{Offshell_GK} that in order for the extended supersymmetries \eqref{eq:extended_susy} to commute with the ones generated by $Q^1_\pm$ and therefore form a $(2,2)$ para-SUSY algebra, either the tensors $T_\pm$ must commute or the equations of motion have to be satisfied. This means that in order to have an off-shell $(2,2)$ SUSY, the two complex structures $J_\pm$ have to commute and accordingly for a $(2,2)$ para-SUSY, the para-complex structures $K_\pm$ have to commute. When they do not commute, the algebra closes only on-shell and one needs to introduce auxiliary fields.

Furthermore, in the case when the complex structures $J_\pm$ commute, the tensor $P\coloneqq J_+J_-$ defines a product structure, $P^2=\id$ and the tangent bundle of the target therefore splits according to its eigenbundles, $TM=P_+\oplus P_-$, where
\begin{align*}
P_\pm=\text{Im}(\id\pm P)=\text{Ker}(J_+\mp J_-).
\end{align*}
It is known \cite{Offshell_GK}[+others] that the sigma model can in this case always be described using only (anti-)chiral and twisted (anti-)chiral $(2,2)$ fields that respectively parametrize the subspaces $P_\pm$.

The same results can be inferred for the case of para-SUSY when we have a pair of para-complex structures $K_pm$. Here again $P\coloneqq K_+K_-$ is a product structure whose eigenbundles are parametrized by (anti-)chiral and twisted (anti-)chiral fields.

In this work we will treat only the case when the (para-)SUSY algebra closes off-shell and the (para-)complex structures commute.

\subsection{$(2,2)$ para-SUSY and Multiplets}
In the above discussion we have started from a $(1,1)$ supersymmetric sigma model with supersymmetries generated by $Q^1_\pm$ and then introduced additional supersymmetries $Q^2_\pm$. This yields $(2,2)$ supersymmetric model written in a $(1,1)$ formalism, meaning the superspace is given only by two real odd coordinates $\theta^\pm$ (in addition to the usual coordinates on the Riemann surface $\Sigma$). The advantage of this approach is that the action $S_{(1,1)}$ \eqref{eq:(1,1)action} is very general, with the disadvantage that the full $(2,2)$ SUSY is non-manifest.

We will now write the $(2,2)$ superalgebra in a $(2,2)$ formalism, introducing now $4$ odd coordinates, $\theta^\pm$, $\bar{\theta}^\pm$ with corresponding $4$ supercharges $Q_\pm$, $\tl{Q}_\pm$,
\begin{align*}
Q_\pm=\frac{\p}{\p \theta^\pm}-\tth^\pm\p_\pm,\quad \tl{Q}_\pm=\frac{\p}{\p \tth^\pm}-\theta^\pm\p_\pm,
\end{align*}
satisfying the (super-)commutation relations
\begin{align}\label{eq:(2,2)_parasusy}
\{Q_\pm,\tl{Q}_\pm\}=-2\p_\pm.
\end{align}
There are also the differential operators $D_\pm,\tl{D}_\pm$:
\begin{align*}
D_\pm=\frac{\p}{\p \theta^\pm}+\tth^\pm\p_\pm,\quad \tl{D}_\pm=\frac{\p}{\p \tth^\pm}+\theta^\pm\p_\pm,
\end{align*}
accordingly satisfying
\begin{align*}
\{D_\pm,\tl{D}_\pm\}=2\p_\pm.
\end{align*}

Notice that in the $(1,1)$ formalism we had charges $Q^1_\pm$ satisfying \eqref{eq:(1,1)_susy} while the charges $Q^2_\pm$ satisfied the opposite relation \eqref{eq:(1,1)_parasusy}.

The $(1,1)$ algebra can be embedded into the above $(2,2)$ formalism in the following way: the $(1,1)$ supercoordinates $\theta_1^\pm$ are given by
\begin{align*}
\theta_1^\pm=\frac{1}{\sqrt{2}}(\theta^\pm-\tth^\pm),
\end{align*}
and we also define additional supercoordinates $\theta_2^\pm$:
\begin{align*}
\theta_2^\pm=\frac{1}{\sqrt{2}}(\theta^\pm+\tth^\pm),
\end{align*}
so that
\begin{align*}
\frac{\p}{\p \theta_1^\pm}=\frac{1}{\sqrt{2}}(\frac{\p}{\p \theta^\pm}-\frac{\p}{\p \tth^\pm}).
\end{align*}

The $(1,1)$ supercharges $Q_\pm^1$ and covariant derivatives $D_\pm^1$ are then given by
\begin{align}\label{eq:(2,2)to(1,1)}
\begin{aligned}
Q_\pm^1&=\frac{1}{\sqrt{2}}(Q_\pm-\tl{Q}_\pm)=\frac{1}{\sqrt{2}}(\frac{\p}{\p \theta^\pm}-\tth^\pm\p_\pm-\frac{\p}{\p \tth^\pm}+\theta^\pm\p_\pm)=\frac{\p}{\p \theta_1^\pm}+\theta^\pm_1\p_\pm\\
D_\pm^1&=\frac{1}{\sqrt{2}}(D_\pm-\tl{D}_\pm)=\frac{1}{\sqrt{2}}(\frac{\p}{\p \theta^\pm}+\tth^\pm\p_\pm-\frac{\p}{\p \tth^\pm}-\theta^\pm\p_\pm)=\frac{\p}{\p \theta_1^\pm}-\theta^\pm_1\p_\pm,
\end{aligned}
\end{align}
matching \eqref{eq:Q1} and \eqref{eq:D1}. The non-manifest SUSY is then generated by the charges
\begin{align}\label{eq:nonmanifest_susy_Ds}
Q_\pm^2=\frac{1}{\sqrt{2}}(Q_\pm+\tl{Q}_\pm)=\frac{\p}{\p \theta_2^\pm}-\theta^\pm_2\p_\pm.
\end{align}
%
%Let now $\mathbf{\Phi}^i=(\Phi^j,\tl{\Phi}^k)$, $i=1,\cdots,2n$, $j,k=1,\cdots, n$ be a para-chiral field, i.e.
%\begin{align}\label{eq:chiral}
%\tl{D}_\pm \Phi^j=D_\pm \Phi^k=0.
%\end{align}
%We will now find the form of the para-complex structures $T_\pm$ generating the non-manifest para-SUSY \eqref{eq:extended_susy}. From \eqref{eq:chiral}, \eqref{eq:(2,2)to(1,1)} and \eqref{eq:nonmanifest_susy_Ds} we infer that $D^1_\pm\Phi^j=Q^2_\pm\Phi^j$ and $D^1_\pm\tl{\Phi}^k=-Q^2_\pm\tl{\Phi}^k$. Therefore, the trasformation by the charges $Q_\pm^2$ is given by
%\begin{align*}
%\delta^2{\bf\Phi}^j&=(\epsilon^+Q^2_++\epsilon^-Q_-^2)(\Phi^j,\tl{\Phi^k})=((\epsilon^+D^1_++\epsilon^-D_-^1)\Phi^j,-(\epsilon^+D^1_++\epsilon^-D_-^1)\tl{\Phi}^k),
%\end{align*}
%but we also have \eqref{eq:extended_susy}
%\begin{align*}
%\delta{\bf\Phi}^i=\epsilon^+ (T_+)^i_jD^1_+{\bf\Phi}^j+\epsilon^- (T_-)^i_jD^1_-{\bf\Phi}^j.
%\end{align*}
%Matching the two expressions yields $T_+=T_-\coloneqq K$ and $K^i_j=\delta^i_j$ for $i,j=1\cdots n$ and $K^i_j=-\delta^i_j$ for $i,j=n+1\cdots 2n$, i.e. $K$ has the canonical block-diagonal form
%\begin{align*}
%K=
%\begin{pmatrix}
%\id & 0 \\
%0 & -\id
%\end{pmatrix}.
%\end{align*}
%Similarly, it is easy to glean that for the anti-para-chiral field $\cdots$ $T_+=T_-=-K$ and for the twisted para-chiral field $\cdots$ we get $\cdots$.

\paragraph*{Restricted fields}
We introduce the following restricted fields
\begin{itemize}
\item {\bf chiral field:} $\tl{D}_\pm \Phi=0$
\item {\bf anti-chiral field:} $D_\pm \tl{\Phi}=0$
\item {\bf twisted chiral field:} $\tl{D}_+U^i=D_-U=0$
\item {\bf twisted anti-chiral field:} $D_+\tl{U}=\tl{D}_-\tl{U}=0$
\end{itemize}
The chiral and anti-chiral fields are easily seen to be given by
\begin{align*}
\Phi&=\phi(y^\pm)+\psi_+(y^\pm)\theta^++\psi_-(y^\pm)\theta^-+F(y^\pm)\theta^+\theta^-\\
\tl{\Phi}&=\tl{\phi}(\tl{y}^\pm)+\tl{\psi}_+(\tl{y}^\pm)\tth^++\tl{\psi}_-(\tl{y}^\pm)\tth^-+\tl{F}(\tl{y}^\pm)\tth^+\tth^-,
\end{align*}
where $y^\pm=x^\pm+\theta^\pm\tth^\pm$ and $\tl{y}^\pm=x^\pm-\theta^\pm\tth^\pm$. This is because, for example for $\Phi$, the only dependence on the $\tth$ coordinates is hidden in $y^\pm$ and the chirality condition can be rewritten as $\frac{\p}{\p \tth^\pm}\Phi=-\theta^\pm\p_\pm \Phi$ which is satisfied for any function of $y^\pm=x^\pm+\theta^\pm\tth^\pm$. Analogously, it is easy to derive that the twisted (anti-)chiral fields take the form
\begin{align*}
U&=v(u^\pm)+\tl{\chi}_+(u^\pm)\theta^++\chi_-(u^\pm)\tl{\theta}^-+E(u^\pm)\theta^+\tl{\theta}^-\\
\tl{U}&=\tl{v}(\tl{u}^\pm)+\chi_+(\tl{u}^\pm)\tl{\theta}^++\tl{\chi}_-(\tl{u}^\pm)\theta^-+\tl{E}(\tl{u}^\pm)\tl{\theta}^+\theta^-
\end{align*}
where $u^\pm=x^\pm\pm\theta^\pm\tth^\pm$ and $\tl{u}^\pm=x^\pm\mp\theta^\pm\tth^\pm$.

\paragraph*{Relationship to $(1,1)$ fields}
The chiral $(2,2)$ field $\Phi$ defines a $(1,1)$ field $\Phi_{(1,1)}$ by $\Phi_{(1,1)}\mid_{\tth^\pm=0}$ which also means that $\Phi_{(1,1)}$ is the lowest component of $\Phi$ in degrees of $\theta,\tth$. Upon taking $\tth^\pm=0$, we get $\theta_1^\pm=\theta_2^\pm$ and $Q^2_\pm=D^1_\pm$. For an anti-chiral field $\tl{\Phi}$, on the other hand, we get a $(1,1)$ field by reducing to a subspace $\theta^\pm=0$, giving $\theta^1=-\theta^2$ and $D^1_\pm=-Q^2_\pm$.

Consider now a $2n$-dimensional vector $(\mathbf{\Phi}^i)_{i=1\cdots 2n}=(\Phi^j,\tl{\Phi}^k)_{j,k=1\cdots n}$ of $n$ chiral and $n$ anti-chiral fields. By considering the lowest component parts of this vector, we can make connection with the expression \eqref{eq:extended_susy} and read off the para-complex structures $T_\pm\coloneqq K_\pm$. We have seen that for the $(1,1)$ component of $\Phi$, we have $D^1_\pm=Q^2_\pm$, therefore $K_\pm$ both act as an identity, while for the $(1,1)$ component of $\tl{\Phi}$, we have $D^1_\pm=-Q^2_\pm$ and $K_\pm$ act as minus identity. Therefore, for a theory given by $n$ chiral and $n$ anti-chiral fields, we have
\begin{align*}
K_+=K_-=\begin{pmatrix}
\id & 0 \\
0 & -\id
\end{pmatrix}.
\end{align*}

\paragraph*{Paracomplexified Version}
We can also introduce $2$ paracomplex odd coordinates $\theta^\pm$

\subsection{R-symmetry}
We have seen above that the $(2,2)$ para-SUSY algebra \eqref{eq:(2,2)_parasusy} can be diagonalised in terms of the charges\footnote{Note that for the usual $(2,2)$ SUSY one cannot diagonalize the algebra over $\RR$.}
\begin{align}\label{eq:R-sym_charges}
\begin{aligned}
\{Q_\pm^1,Q_\pm^1\}&=2\p_\pm\\
\{Q_\pm^2,Q_\pm^2\}&=-2\p_\pm.
\end{aligned}
\end{align}
which are related to $Q_\pm$ by $Q_\pm=\frac{1}{\sqrt{2}}(Q^2_\pm+Q^1_\pm)$ and $\tl{Q}_\pm=\frac{1}{\sqrt{2}}(Q^2_\pm-Q^1_\pm)$. Equations \eqref{eq:R-sym_charges} can be written collectively as
\begin{align}\label{eq:R-sym_eta}
\{Q_\pm^a,Q_\pm^b\}=2\eta^{ab}\p_\pm,
\end{align}
where $\eta^{ab}=\begin{pmatrix}
1 & 0 \\
0 & -1
\end{pmatrix}$. From here it is easy to see that matrices $(M_\pm)^a_b$ that rotate the $\pm$-chirality charges among each other while preserving the commutation relations \eqref{eq:R-sym_eta},
\begin{align*}
\{(M_\pm)^a_cQ_\pm^c,(M_\pm)^b_dQ_\pm^d\}=2\eta^{ab}\p_\pm
\end{align*}
have to satisfy
\begin{align*}
(M_\pm)^a_c\eta^{cd}(M_\pm)^a_d=\eta^{ab},
\end{align*}
i.e. $M_\pm$ have to lie in $SO(1,1)$ for each subscript $\pm$ and the R-symmetry group is therefore $G_R=SO(1,1)_+\times SO(1,1)_-$.

The R-symmetry acts on the odd coordinates accordingly as
\begin{align*}
\begin{pmatrix}
\theta^1_\pm \\
\theta^2_\pm	
\end{pmatrix}
\mapsto
\begin{pmatrix}
\cosh(\alpha_\pm) & \sinh(\alpha_\pm) \\
\sinh(\alpha_\pm) & \cosh(\alpha_\pm)
\end{pmatrix}
\begin{pmatrix}
\theta^1_\pm \\
\theta^2_\pm	
\end{pmatrix}
\end{align*}
or, equivalently, $(\theta^\pm,\tth^\pm)\mapsto (e^{\alpha_\pm} \theta^\pm,e^{-\alpha_\pm}\tth^\pm)$. There are therefore two inequivalent embeddings of the Lorentz group $SO(1,1)$ into the R-symmetry group, we label them by $V$ and $A$:
\begin{align*}
R_V(\alpha)&:(\theta^\pm,\tth^\pm)\mapsto (e^\alpha \theta^\pm,e^{-\alpha}\tth^\pm)\\
R_A(\alpha)&:(\theta^\pm,\tth^\pm)\mapsto (e^{\pm \alpha} \theta^\pm,e^{\mp \alpha}\tth^\pm),
\end{align*}
mapping the supercharges as
\begin{align*}
R_V(\alpha):& (Q_\pm,\tl{Q}_\pm)\mapsto (e^{-\alpha}Q_\pm,e^{\alpha}\tl{Q}_\pm)\\
R_A(\alpha):& (Q_\pm,\tl{Q}_\pm)\mapsto (e^{\mp\alpha}Q_\pm,e^{\pm}\tl{Q}_\pm).
\end{align*}
The generators of these transformations are
\begin{align*}
F_{V/A}=\theta^+\frac{\p}{\p\theta^+}-\tth^+\frac{\p}{\p\tth^+}\pm \theta^-\frac{\p}{\p\theta^-}\mp\tth^-\frac{\p}{\p\tth^-}.
\end{align*}

Because $F_{V/A}$ has same commutators with other operators as $M$, the Lorentz generator, and additionally all $F_{V/A}$ and $M$ commute among themselves, we can define a new "Lorentz" generators in one of the two following ways:
\begin{align*}
M_A=M+F_V,\quad M_B=M+F_A.
\end{align*}

%The translation between the ``diagonalised" algebra in terms of $Q^{1/2}_\pm$ and the algebra \eqref{eq:(2,2)_parasusy} is given by
%\begin{align*}
%Q_\pm=\frac{1}{\sqrt{2}}(Q^2_\pm+Q^1_\pm)\quad \tl{Q}_\pm=\frac{1}{\sqrt{2}}(Q^2_\pm-Q^1_\pm).
%\end{align*}

%The superfield $\Phi(\sigma,\tau,\theta^\pm,\tth^\pm)$ in the $(2,2)$ superspace now has in general $16$ components, but one usually introduces constraints on the fields in order to lower this number as well as to easily write manifestly supersymmetric actions. The constraints one typically imposes on the fields (see \cite{HullTwistedSUSY}) are the Chiral constraints

\paragraph{para-K\"ahler model}
We now show the relationship between the $(1,1)$ and $(2,2)$ formalisms on the simple example when the target is a para-K\"ahler manifold. In the $(1,1)$ superspace, this means that $b=0$ in \eqref{eq:(1,1)action} and $K_+=K_-=K$, giving the only parity-symmetric option for the extended $(2,2)$ SUSY. From the point of view of the $(2,2)$ superspace, this is a theory of chiral superfields.

\section{Topological Twists}
In this section we will present how the para-supersymmetric theories can be twisted, yielding topological sigma models. The procedure will again follow the analogy between GK and GpK geometries and we will follow the approach presented in \cite{Kapustin:2004gv} for the GK case.

As we discussed in Section \ref{sec:susy_gpk}, if the target is a generalized para-K\"ahler, we have the $(2,2)$ para-SUSY generated by the supercharges:
\begin{align*}
\{Q_\pm^1,Q_\pm^1\}&=2\p_\pm\\
\{Q_\pm^2,Q_\pm^2\}&=-2\p_\pm.
\end{align*}
This can be rewritten as
\begin{align*}
\{Q_\pm,\tl{Q}_\pm\}=-2\p_\pm,
\end{align*}
where $Q_\pm=\frac{1}{\sqrt{2}}(Q^2_\pm+Q^1_\pm)$ and $\tl{Q}_\pm=\frac{1}{\sqrt{2}}(Q^2_\pm-Q^1_\pm)$. We also introduce the nilpotent supercharge
\begin{align*}
\QQ=\tl{Q}_++\tl{Q}_-.
\end{align*}

Now, the $(1,1)$ fundamental fields $\Psi_\pm$ are valued in (the pull-back of) the tangent bundle of $M$ and therefore we can split them using the pair of para-Hermitian structures $K_\pm$:
\begin{align*}
\Psi_\pm=\psi_\pm+\tl{\psi}_\pm,\quad \psi_\pm=\frac{1}{2}(\id+K_\pm),\ \tl{\psi}_\pm=\frac{1}{2}(\id-K_\pm)
\end{align*}

\section*{Example:K\"ahler Model}
The usual K\"ahler model is a $(2,2)$ theory of $n$ chiral superfields. The results are well-known and we will use it to show the relationship between the cohomology of the nilpotent charge $\QQ$ and the Lie algebroid cohomology of the GC structures defining the GK geometry. We will show that this relationship is given exactly by the isomorphism discussed in Section \ref{sec:isomorphism}.

The complex supercharges furnishing the $(2,2)$ SUSY are defined by
\begin{align*}
Q_\pm=\frac{\p}{\p \theta^\pm}+i\bar{\theta}^\pm\p_\pm,\quad \bar{Q}_\pm=-\frac{\p}{\p \bar{\theta}^\pm}-i\theta^\pm\p_\pm
\end{align*}
The chiral field and its complex conjugate, anti-chiral field, is given by
\begin{align*}
\Phi^i&=\phi^i(y^\pm)+\psi^i_+(y^\pm)\theta^++\psi^i_-(y^\pm)\theta^-+F^i(y^\pm)\theta^+\theta^-\\
\bar{\Phi}^i&=\bar{\phi}^i(\bar{y}^\pm)+\bar{\psi}^i_+(\bar{y}^\pm)\bar{\theta}^++\bar{\psi}^i_-(\bar{y}^\pm)\bar{\theta}^-+\bar{F}^i(\bar{y}^\pm)\bar{\theta}^+\bar{\theta}^-,
\end{align*}
where $y^\pm=x^\pm-i\theta^\pm\bar{\theta}^\pm$. The SUSY variations of the multiplet $(\phi,\psi_\pm)$ (eliminating $F$ via equations of motion) are given by
\begin{align}\label{eq:susy_vars}
\begin{aligned}
\delta \phi^i &= \epsilon_+ \psi^i_--\epsilon_- \psi^i_+\\
\delta \psi^i_\pm &= \pm 2i\bar{\epsilon}_\mp\p_\pm \phi^i+\epsilon_\pm (\Gamma^-)^{i}_{jk}\psi_-^k\psi_+^j
\end{aligned}
\end{align}
where
\begin{align*}
\delta=\epsilon_+Q_--\epsilon_-Q_+-\bar{\epsilon}_+\bar{Q}_-+\bar{\epsilon}_-\bar{Q}_+,
\end{align*}
and variations of $(\bar{\phi},\bar{\psi})$ are given by complex conjugations of \eqref{eq:susy_vars}.

For the A-twist, we define
\begin{align*}
\QQ_A=\bar{Q}_++Q_-,
\end{align*}
which transforms the fields as
\begin{align*}
\{\QQ_A, \phi^i\}&=\psi^i_-\\
\{\QQ_A, \bar{\phi}^i\}&=\bar{\psi}^i_+\\
\{\QQ_A, \psi^i_-\}&=0
\end{align*}

\section*{The $(1,1)$ Action in Components}
We will now expand the action \eqref{eq:(1,1)action} in component fields of the $(1,1)$ multiplet $\Phi=(\phi,\psi_\pm,F)$. First, we note
\begin{align*}
\Phi^i&=\phi^i+\theta^+\psi^i_++\theta^-\psi^i_-+\theta^+\theta^-F^i\\
D_\pm\Phi^i&=\psi^i_\pm\pm\theta^\mp F^i-\theta^\pm\p_\pm\phi^i\mp\theta^+\theta^-\p_\pm\psi^i_\mp\\
[g(\Phi)+b(\Phi)]_{ij}&=[g(\phi)+b(\phi)]_{ij}+\p_k[g(\phi)+b(\phi)]_{ij}(\theta^+\psi_+^k+\theta^-\psi_-^k+\theta^+\theta^-F^k)\\
&+\frac{1}{2}\p_k\p_l[g(\phi)+b(\phi)]_{ij}(\theta^+\psi_+^k+\theta^-\psi_-^k)(\theta^+\psi_+^l+\theta^-\psi_-^l).
\end{align*}
The action is then
\begin{align*}
S_{(1,1)}(\Phi)&=\int_{\hat{\Sigma}}[g(\Phi)+b(\Phi)]_{ij}D_+\Phi^iD_-\Phi^j.
\end{align*}
After performing the odd integration, the only terms that survive are the $\theta^+\theta^-$ coefficients:
\begin{align*}
\theta^+\theta^-&\left[(g+b)_{ij}(\psi_+^i\p_-\psi^j_++\psi^j_-\p_-\psi^i_-+F^iF^j+\p_+\phi^i\p_-\phi^j)\right. \\
&+\p_k(g+b)_{ij}\left(F^k\psi^i_+\psi^j_-+\psi^k_+(-F^i\psi^j_--\psi^i_+\p_-\phi^j)+\psi^k_-(-\p_+\phi^i\psi^j_-+\psi_+^iF^j)\right)\\
&\left. +\frac{1}{2}\p_k\p_l(g+b)_{ij}(-\psi_+^k\psi_-^l\psi_+^i\psi_-^j+\psi_-^k\psi_+^l\psi^i_+\psi^j_-) \right].
\end{align*}
We now use the formula $\p_kg_{ij}=\Gamma_{ikj}+\Gamma_{jki}$
%as well as the following integration by parts:
%\begin{align*}
%\int b_{ij}\psi^i_+\p_-\psi_+^j=-\int\p_-(b_{ij}\psi^i_+)\psi_+^j =-\int (\p_k b_{ij})\p_-\phi^k\psi^i_+\psi^j_+-\int b_{ij}(\p_-\psi^i_+)\psi_+^j.
%\end{align*}
%Because $b_{ij}(\p_-\psi^i_+)\psi^j_+=b_{ij}\psi_+^i\p_-\psi^j_+$, we get the identity
%\begin{align*}
%\int b_{ij}\psi^i_+\p_-\psi_+^j=-\frac{1}{2}\int (\p_k b_{ij})\p_-\phi^k\psi^i_+\psi^j_+
%\end{align*}
and collect the terms involving $F$:
\begin{align*}
g_{ij}F^iF^j+&(\Gamma_{ikj}+\Gamma_{jki})(F^k\psi^i_+\psi^j_--F^i\psi^k_+\psi^j_-+F^j\psi^k_-\psi_+^i)\\
+&F^k\psi^i_+\psi^j_-(\p_kb_{ij}+\p_ib_{jk}+\p_jb_{ki}).
\end{align*}
Using $\Gamma_{ikj}=\Gamma_{kij}$ and $H_{ijk}=(\p_kb_{ij}+\p_ib_{jk}+\p_jb_{ki})$, we can rewrite this as
\begin{align*}
g_{ij}F^iF^j+2\Gamma_{ikj}F^j\psi^k_-\psi_+^i+F^k\psi^i_+\psi^j_-H_{ijk}=g_{ij}(F^iF^j+2F^j(\Gamma^-)_{lk}^i\psi_-^k\psi_+^l),
\end{align*}
where $\Gamma^-$ are the Christoffel symbols of the connection $\n^-=\lc-\frac{1}{2}g^{-1}H$. This yields the equation of motion for $F$,
\begin{align}
F^i=-(\Gamma^-)^i_{jk}\psi^k_-\psi^j_+
\end{align}

%After mild rearrangements, we get
%\begin{align*}
%(g+b)_{ij}\p_+\phi^i\p_-\phi^j-g_{ij}F^iF^j+g_{ij}\psi_+^i\p_-\psi^j_++g_{ij}\psi_-^i\p_+\psi^j_-
%\end{align*}

\section*{The twist in a $(1,1)$ language}
Recalling (setting $\theta^\pm_1\coloneqq \theta^\pm$ for simplicity)
\begin{align*}
Q^1_\pm&=\frac{\p}{\p\theta^\pm}+\theta^\pm\p_\pm\\
Q^2_\pm\Phi^i&=(K_\pm)^i_j(\Phi)D_\pm\Phi^j\\
D^1&=\frac{\p}{\p\theta^\pm}-\theta^\pm\p_\pm
\end{align*}

We define $Q_L=\frac{1}{2}( Q^1_++Q^2_+)$ and $Q_R=\frac{1}{2}( Q^1_-+Q^2_-)$. We will now check how these act on a $(1,1)$ multiplet $\Phi=(\phi,\psi_\pm,F)$ in superfield description given by 
\begin{align*}
\Phi^i(\sigma,\tau,\theta^+,\theta^-)=\phi^i(\sigma,\tau)+\theta^+\psi^i_+(\sigma,\tau)+\theta^-\psi^i_-(\sigma,\tau)+\theta^+\theta^-F^i(\sigma,\tau).
\end{align*}

We have
\begin{align*}
\{Q_\pm^1 ,\phi^i\}&=\psi_\pm^i,\\
\{Q_\pm^1 ,\psi^i_\pm\}&=\p_\pm\phi^i\\
\{Q_\pm^1 ,\psi^i_\mp\}&=\pm F^i.
\end{align*}
For the variations $Q^2_\pm$ we first need to expand $T_\pm(\Phi)\coloneqq K_\pm(\Phi)$:
\begin{align}
(K_\pm)^i_j(\Phi)=(K_\pm)^i_j(\phi)+\p_k(K_\pm)^i_j\theta^+\psi_+^k+\p_k(K_\pm)^i_j\theta^-\psi_-^k+\p_k(K_\pm)\theta^+\theta^-F^k,
\end{align}
so that $Q^2_\pm\Phi^i=(K_\pm)^i_j(\Phi)D_+\Phi^j$ is given by
\begin{align}
Q^2_\pm\Phi^i&=(K_\pm)^i_j(\Phi)(\psi^j_\pm\pm\theta^\mp F^j-\theta^\pm\p_\pm\phi^j\mp\theta^+\theta^-\p_\pm\psi^j_\mp),
\end{align}
and
\begin{align}
\{Q_\pm^2 ,\phi^i\}&=(K_\pm)^i_j\psi_\pm^j,\\
\{Q_+^2 ,\psi^i_+\}&=-(K_+)^i_j\p_+\phi^j{\textcolor{red}{+}}\p_k(K_\pm)^i_j\psi_+^k\psi_+^j\\
\{Q_\pm^2 ,\psi^i_\mp\}&=(K_\pm)^i_jF^j+\p_k(K_\pm)^i_j\psi^k_\mp\psi^j_\pm.
\end{align}
\textcolor{red}{There's a sign issue above, the $+$ needs to be $-$.}
Now, we introduce the usual notation $\chi=\frac{1}{2}(\id+K_+)\psi_+=P_+\psi_+=\psi_+^{(1,0)_+}$ and $\lambda=\frac{1}{2}(\id+K_-)\psi_-=P_-\psi_-=\psi_-^{(1,0)_-}$. We further denote the variations with respect to $Q_{L/R}$ by $\delta_{L/R}$. We have
\begin{align}
\{Q_L,\phi^i\}=\frac{1}{2}\{Q_+^1+Q^2_+,\phi^i\}=\chi^i.
\end{align}
Now, %$\delta_L\chi^i=\delta_L[(P_+)^i_j\psi^j]=\delta_L[(P_+)^i_j]\psi^j+(P_+)^i_j[\delta_L\psi^j]$
\begin{align}
\{Q_L,\chi^i\}=\{Q_L,(P_+)^i_j\psi_+^j\}=\{Q_L,(P_+)^i_j\}\psi_+^j\textcolor{red}{+}(P_+)^i_j\{Q_L,\psi_+^j\}.
\end{align}
\textcolor{red}{Or maybe here?}
Because $K_+$ is a function of the bosonic coordinates, we also have $P_+=P_+(\phi)$ and so

\begin{align}
\{Q_L,(P_+)^i_j\}=\p_k(P_+)^i_j\{Q_L,\phi^k\}=\p_k(P_+)^i_j\chi^k.
\end{align}
Combining this, we arrive at
\begin{align*}
\{Q_L,\chi^i\}&=\p_k(P_+)^i_j\chi^k\psi_+^j+(P_+)^i_j[(\tl{P}_+)^j_k\p_+\phi^k+\frac{1}{2}\p_k(K_+)^j_l\psi_+^k\psi_+^l]\\
&=\p_k(P_+)^i_j(P_+)^k_l\psi_+^l\psi_+^j+(P_+)^i_j\p_k(P_+)^j_l\psi_+^k\psi_+^l=0,
\end{align*}
due to integrability of $K_+$. To see this, we expand the projectors, $(P_+)^i_j=\frac{1}{2}(\delta^i_j+(K_+)^i_j)$:
\begin{align*}
\p_k&(P_+)^i_j(P_+)^k_l\psi_+^l\psi_+^j+(P_+)^i_j\p_k(P_+)^j_l\psi_+^k\psi_+^l\\
&=\p_k(P_+)^i_j\psi_+^k\psi_+^j+\p_k(P_+)^i_l\psi_+^k\psi_+^l\\
=&\frac{1}{2}(\p_j(K_+)^i_l(P_+)^j_k+(P_+)^i_j\p_k(K_+)^j_l)\psi_+^k\psi_+^l\\
=&\frac{1}{4}(\p_j(K_+)^i_l(K_+)^j_k+(K_+)^i_j\p_k(K_+)^j_l)\psi_+^k\psi_+^l+\frac{1}{4}(\p_j(K_+)^i_l\psi_+^j\psi_+^l+\p_k(K_+)^i_l\psi_+^k\psi_+^l)
\end{align*}

\subsubsection*{Try $Q_L=\frac{1}{2}(Q_1-Q_2)$}

Now $\chi=\tl{P}_+\psi_+$.
\begin{align*}
[Q_L,\phi^i]&=\chi^i\\
[Q_L,\chi^i]&=\p_k(\tl{P}_+)^i_j\chi^k\psi_+^j+(\tl{P}_+)^i_j((P_+)^j_k\p_+\phi^k-\frac{1}{2}\p_k(K_+)^j_l\psi_+^k\psi_+^l)\\
&=-\frac{1}{2}\p_k (K_+)^i_j(\tl{P}_+)^k_l\psi^l_+\psi_+^j-\frac{1}{2}(\tl{P}_+)^i_j\p_k (K_+)^j_l\psi_+^k\psi_+^l\\
&=-\p_k(K)^i_j\psi^k\psi^j-\p_k(K)^i_j\psi^k\psi^j
\end{align*}

Now we have
\begin{align*}
\{Q_L,\psi_-^i\}=(P_+)^i_jF^j+\frac{1}{2}\p_k(K_+)^i_j\psi^k_-\psi_+^j,
\end{align*}
so that
\begin{align*}
\{Q_L,\lambda^i\}=\{Q_L,(P_-)^i_j\psi_-^j\}&=\{Q_L,(P_-)^i_j\}\psi_-^j+(P_-)^i_j\{Q_L,\psi_-^j\}\\
&=\p_k(P_-)^i_j\chi^k\psi_-^j+(P_-)^i_k((P_+)^k_jF^j+\frac{1}{2}\p_l(K_+)^k_j\psi^l_-\psi_+^j)
\end{align*}
Next, we expand
\begin{align*}
\p_k(P_-)^i_j=\n^-_k(P_-)^i_j-(\Gamma^-)^i_{kl}(P_-)^l_j+(\Gamma^-)^l_{kj}(P_-)^i_l=-(\Gamma^-)^i_{kl}(P_-)^l_j+(\Gamma^-)^l_{kj}(P_-)^i_l,
\end{align*}
so that
\begin{align}\label{eq:calc1}
\begin{aligned}
\p_k(P_-)^i_j\chi^k\psi_-^j=(-(\Gamma^-)^i_{kl}(P_-)^l_j+(\Gamma^-)^l_{kj}(P_-)^i_l)(P_+)^k_m\psi_+^m\psi_-^j.
\end{aligned}
\end{align}
Similarly,
\begin{align}\label{eq:calc2}
\begin{aligned}
(P_-)^i_k\frac{1}{2}\p_l(K_+)^k_j\psi^l_-\psi_+^j&=(P_-)^i_k\p_l(P_+)^k_j\psi^l_-\psi_+^j\\
&=(P_-)^i_k(-(\Gamma^+)^k_{lm}(P_+)^m_j+(\Gamma^+)^m_{lj}(P_+)^k_m)\psi^l_-\psi_+^j
\end{aligned}
\end{align}
Next, we use
\begin{align*}
(\Gamma^+)^i_{jk}=g^{im}(\Gamma_{jkm}+\frac{1}{2}H_{jkm})=g^{im}(\Gamma_{kjm}-\frac{1}{2}H_{kjm})=(\Gamma^-)^i_{kj},
\end{align*}
so that in \eqref{eq:calc1} and \eqref{eq:calc2} terms cancel (\textcolor{red}{up to another relative minus sign!}) as well as cancelling the term $(P_-)^i_k(P_+)^k_jF^j$ by
\begin{align*}
(P_-)^i_k(\Gamma^+)^m_{lj}(P_+)^k_m\psi^l_-\psi_+^j=(P_-)^i_k(P_+)^k_j(\Gamma^-)^j_{ml}\psi^l_-\psi_+^m=-(P_-)^i_k(P_+)^k_jF^j
\end{align*}
and we arrive at
\begin{align*}
\{Q_L,\lambda^i\}=-(\Gamma^-)^i_{kl}\chi^k\lambda^l.
\end{align*}

Now for $Q_R$, we have
\begin{align*}
\{Q_R,\phi^i\}=\lambda^i
\end{align*}

\subsection{The geometric output}
Let's now assume the signs work out so that $Q_{L/R}$ act as:\textcolor{red}{what is the analogy here for the complex conjugates of $\lambda,\chi$?}
\begin{align}\label{eq:Qcoh}
\begin{aligned}
[Q_L,\phi^i]&=\chi^i & [Q_R,\phi^i]&=\lambda^i\\
[Q_L,\chi^i]&=0 & [Q_R,\lambda^i]&=0\\
[Q_L,\lambda^i]&=-(\Gamma^-)^i_{jk}\chi^j\lambda^k & [Q_R,\chi^i]&=-(\Gamma^+)^i_{jk}\lambda^j\chi^k.
\end{aligned}
\end{align}
%We therefore define ${\cal Q}=Q_L+Q_R$
The observables are therefore polynomials in the odd variables $\chi,\lambda$ with even coefficients dependent on $\phi$:
\begin{align*}
{\cal O}_f=f(\phi)_{i_1\cdots i_a,j_1\cdots j_b}\chi^{i_1}\cdots\chi^{i_a}\lambda^{j_1}\cdots\lambda^{j_b}.
\end{align*}
Because $\chi \in \XX^{(1,0)_+}$ and $\lambda \in \XX^{(1,0)_-}$, we can identify ${\cal O}_f$ with a function on the supermanifold $(T^{(1,0)_+}\oplus T^{(1,0)_-})[1]$, which in turn can be identified with differential form
\begin{align*}
\Omega_f=f(\phi)_{i_1\cdots i_a,j_1\cdots j_b}dx^{i_1}_+\cdots dx^{i_a}_+ dx^{j_1}_- \cdots dx^{j_b}_-,
\end{align*}
where $dx_\pm$ are the one-forms satisfying $K_\pm dx_\pm=dx_\pm$, i.e. sections of the bundle $T^{*(1,0)_\pm}$. Via this identification, the operator ${\cal Q}\coloneqq Q_L+Q_R$ defines a differential $\rd_\QQ$, which
% The action of $Q_{L/R}$ is then given by
%\begin{align*}
%[Q_L,\Omega_f] = (\p_k f_{i_1\cdots i_a,j_1\cdots j_b}-(\Gamma^-)^{m}_{kj_1}f_{i_1\cdots i_a,m\cdots j_b}&-\cdots-(\Gamma^-)^{m}_{kj_b}f_{i_1\cdots i_a,j_1\cdots m})\\
%& \times dx^k_+dx^{i_1}_+\cdots dx^{i_a}_+ dx^{j_1}_- \cdots dx^{j_b}_-\\
%[Q_R,\Omega_f] = (\p_k f_{i_1\cdots i_a,j_1\cdots j_b}-(\Gamma^+)^{m}_{ki_1}f_{m\cdots i_a,j_1\cdots j_b}&-\cdots-(\Gamma^+)^{m}_{ki_a}f_{i_1\cdots m,j_1\cdots j_b})\\
%& \times dx^k_-dx^{i_1}_+\cdots dx^{i_a}_+ dx^{j_1}_- \cdots dx^{j_b}_-
%\end{align*}
acts on the sections of $\bigwedge^k(T^{*(1,0)_+}\oplus T^{*(1,0)_-})$ and because $\QQ$ squares to zero $\rd_\QQ$ also squares to zero. Therefore, $\rd_\QQ$ gives rise to a Chevalley-Eilenberg complex $\text{CE}(L)$ of a certain Lie algebroid $L$ which we now describe.

\paragraph{Lie algebroid from bi-para-Hermitian data} The underlying vector bundle is $L=T^{(1,0)_+}\oplus T^{(1,0)_-}$, and the anchor is the sum of the two inclusions $\imath_\pm:\ T^{(1,0)_\pm}\hookrightarrow T$, i.e.
\begin{align*}
a:L=T^{(1,0)_+}\oplus T^{(1,0)_-} &\rightarrow T\\
 e=(x_+,x_-) &\mapsto \imath_+(x_+)+\imath_-(x_-).
\end{align*}
From \eqref{eq:Qcoh} we can read off the action of $\rd_\QQ$ on degree one elements, i.e. sections $\alpha=(\alpha^+,\alpha^-)$ of $L^*=T^*_{(1,0)_+}\oplus T^*_{(1,0)_-}$:
\begin{align*}
\rd_\QQ\alpha&=\p_k\ap_i^+[dx_+^k+dx_-^k]\w dx_+^i-\ap^+_i(\Gamma^+)^i_{jk}dx_-^j\w dx_+^k\\
&+\p_k\ap_i^-[dx_+^k+dx_-^k]\w dx_-^i-\ap^-_i(\Gamma^-)^i_{jk}dx_+^j\w dx_-^k.
\end{align*}
%In coordinate-free form, we get
%\begin{align*}
%\rd_\QQ\ap=(\p_++\n^+_{P_-(\bullet)})\ap^++(\p_-+\n^-_{P_+(\bullet)})\ap^-,
%\end{align*}
By contracting in two sections of $L$, $e_1=x_++x_-$, $e_2=y_-+y_-$, we get a coordinate-free expression
\begin{align}\label{eq:dQ}
\begin{aligned}
(\rd_\QQ\ap)(e_1,e_2)&=(\p_+\ap^+)(x_+,y_+)+\n^+_{x_-}\ap^+(y_+)-\n^+_{y_-}\ap^+(x_+)\\
&+(\p_-\ap^-)(x_-,y_-)+\n^-_{x_+}\ap^-(y_-)-\n^-_{y_+}\ap^-(x_-),
\end{aligned}
\end{align}
where $\p_\pm$ denotes the para-complex Dolbeault operators $\p$ for $K_\pm$. We can further simplify this expression by writing $\ap=(\eta(\tl{z}_+),\eta(\tl{z}_-))$ for $\tl{z}_\pm \in \se(T^{(1,0)_\pm})$, invoking the formula $\p_\pm\ap^\pm(x_\pm,y_\pm)=\lc_{x_\pm}\ap^\pm(y_\pm)-\lc_{y_\pm}\ap^\pm(x_\pm)$ and recalling $\n^\pm=\lc\pm \frac{1}{2}\eta^{-1}H$:
\begin{align}
\begin{aligned}
(\rd_\QQ\ap)(e_1,e_2)&=\eta((\lc_{x_+}+\n_{x_-}^+)\zt_+,y_+)-\eta((\lc_{y_+}+\n_{y_-}^+)\zt_+,x_+)\\
&+\eta((\lc_{x_-}+\n_{x_+}^-)\zt_-,y_-)-\eta((\lc_{y_-}+\n_{y_+}^-)\zt_-,x_-)\\
&=\eta(\n^+_{x_++x_-}\zt_+,y_+)-\eta(\n_{y_++y_-}^+\zt_+,x_+)-H(x_+,\zt_+,y_+)\\
&+\eta(\n_{x_++x_-}^-\zt_-,y_-)-\eta(\n_{y_++y_-}^-\zt_-,x_-)+H(x_-,\zt_-,y_-)
\end{aligned}
\end{align}

\paragraph{Lie algebroid from generalized para-K\"ahler data} Recall that the GpK structure gives rise to the following splitting of the bundle $\TT$:
\begin{align*}
\TT=\ell_+\oplus\ell_-\oplus \ellt_+\oplus \ellt_-,
\end{align*}
such that the eigenbundles of $\KK_+$ are $\Lb_+=\ell_+\oplus\ell_-$ and $\tl{\Lb}_+=\ellt_+\oplus \ellt_-$, the eigenbundles of $\KK_-$ are $\Lb_-=\ell_+\oplus\ellt_-$ and $\tl{\Lb}_-=\ell_-\oplus \ellt_+$ and the eigenbundles of the generalized metric are $C_\pm=\ell_\pm\oplus\ellt_\pm$. All $\ell_\pm$ and $\ellt_\pm$ are isotropic and integrable under the Dorfman bracket and bundles with opposite chirality are orthogonal. Because $\Lb$ is a Dirac structure, it defines a Lie algebroid by restriction of the Courant algebroid to $\Lb$, i.e. the Lie algebroid bracket and anchor are given by the restriction of the Dorfman bracket and the projection onto tangent bundle, respectively.

\begin{theorem}
The Lie algebroids $(L,a,\rd_\QQ)$ and $(\Lb_+,\pi_T\!\!\mid_{\Lb_+},\brac\!\!\mid_{\Lb_+})$ are isomorphic via the map $\pi=\pi_+\oplus \pi_-$.
\end{theorem}
\begin{proof}
First, we notice that the bundles themselves are related by $\pi$,  $\pi(\Lb_+)=\pi(\ell_+\oplus \ell_-)=\pi_+(\ell_+)\oplus \pi_-(\ell_-)=T^{(1,0)_+}\oplus T^{(1,0)_-}=L$ and also $\pi$ is clearly an isomorphism since both $\pi_\pm$ are. Additionally, the anchors are related by $a\circ\pi=\pi_T\!\!\mid_{\Lb_+}$. The only non-trivial task is therefore to show that the respective differentials satisfy
\begin{align}\label{eq:d_pi}
\pi^*\circ\rd_Q  =\rd_{\Lb_+}\circ \pi^*,
\end{align}
where $\pi^*=\pi^*_+\oplus\pi_-^*$ and $\pi^*_\pm$ are dual maps to $\pi_\pm:\ell_+\rightarrow T^{(1,0)_\pm}$, extended to a map $\pi^*:\Lambda^k(L^*)\rightarrow\Lambda^k(\Lb_+^*)$.

Because of the chain rule, we only need to check this on degree $0$ and degree $1$ elements in the respective complexes. Degree $0$ follows immediately:
\begin{align*}
(\rd_Q f)(\pi(u))= a\circ \pi(u)[f]=\pi_T\!\!\mid_{\Lb_+}(u)[f]=(\rd_{\Lb_+}f)(u),
\end{align*}
%For degree one, we use the decomposition of the respective bundles and check for each component
%\begin{alignat*}{2}
%\rd_Q:&&T^*_{(1,0)_+}\oplus T^*_{(1,0)_-} &\rightarrow \Lambda^2(T^*_{(1,0)_+}\oplus T^*_{(1,0)_-})\\
%\rd_{\Lb_+}:&& \ell_+^*\oplus \ell_-^* &\rightarrow \Lambda^2(\ell_+^*\oplus \ell_-^*)
%\end{alignat*}
and we will now prove \ref{eq:d_pi} for degree $1$ elements. In the following we will make use of the identifications provided by the metric $\eta$ and pairing $\lara$:
\begin{alignat*}{2}
\eta:&& T^*_{(1,0)_\pm} &\leftrightarrow T^{(0,1)_\pm}\\
\lara:&& \ell^*_\pm &\leftrightarrow \ellt_\pm,
\end{alignat*}
so that elements in $T^*_{(1,0)_\pm}$ can be written as $\eta(\tl{z}_\pm)$ with $\tl{z}_\pm$ vector in $T^{(0,1)_\pm}$ and similarly, elements in $\ell^*_\pm$ can be expressed as $\la \tl{w}_\pm, \cdot\ra$ with $\tl{w}_\pm$ section of $\ellt_\pm$. To declutter notation, we shall also denote the bracket and anchor on $\Lb_+$ by $\brac$ and $\pi$, respectively.

The differential $\rd_{\Lb_+}$ is defined by the bracket on the Lie algebroid $\Lb_+$ via the following formula:
\begin{align}\label{eq:proof_Liethm}
\rd_{\Lb_+}  w^* (u,v)=\pi(u) w^*(v)-\pi(u) w^*(v)- w^*([u,v]),
\end{align}
where $ w^* \in \se(\Lb_+^*)$ and $u,v\in \se(\Lb_+)$. Writing $ w^*$ as $\la \tl{w},\cdot\ra$, with $\tl{w}\in\se (\tl{\Lb}_+)$ we can rewrite this as
\begin{align}\label{dL}
\begin{aligned}
\rd_{\Lb_+}  w^* (u,v)&=\pi(u)\la v ,\tl{w}\ra-\pi(v)\la u,\tl{w}\ra-\la [u,v],\tl{w}\ra\\
&=\la D_uv,\tl{w}\ra+\la v,D_u \tl{w}\ra-\la D_v u,\tl{w}\ra-\la u,D_v\tl{w}\ra-\la D_uv-D_vu,\tl{w}\ra\\
&+{T}(u,v,\tl{w})\\
&=\la D_u \tl{w},v\ra-\la D_v\tl{w},u\ra+{T}(u,v,\tl{w})\\
&=\la D_u \tl{w}_+,v_+\ra-\la D_v\tl{w}_+,u_+\ra+{T}(u_+,v_+,\tl{w}_+)\\
&+\la D_u \tl{w}_-,v_-\ra-\la D_v\tl{w}_-,u_-\ra+{T}(u_-,v_-,\tl{w}_-),
\end{aligned}
\end{align}
where $D$ is the generalized Bismut connection of the generalized metric for the GpK structure, we used the fact that $D$ preserves $\lara$, $C_\pm$ as well as $\Lb_+$ and we also plugged in the definition of a generalized torsion ${T}$ \cite[Def.~3]{Gualtieri:2010fd} to write $\brac$ in terms of $D$. Lastly, we also used the fact that $T$ only has components in $\Lambda^3 C_+\oplus\Lambda^3 C_-$ \cite{Gualtieri:2010fd}.

We will now show that $\rd_{\Lb_+}$ is related to $\rd_\QQ$ via \eqref{eq:d_pi}, so that $\rd_\QQ=(\pi^{-1})^*\circ \rd_{\Lb_+}\circ \pi^*$, i.e.
\begin{align*}
\rd_\QQ\ap(e_1,e_2)=\rd_{\Lb_+}(\pi^*\ap)(\pi^{-1}e_1,\pi^{-1}e_2).
\end{align*}
To read this off from \eqref{dL}, we need to express $\pi^*\ap$ as $\pi^*\ap=w^*=\la \tl{w},\cdot\ra$ for some $\tl{w}\in\se (\tl{\Lb}_+)$:
\begin{align*}
\pi^*\ap=\pi^*(\eta(\zt_+),\eta(\zt_-))=(\eta(\zt_+,\pi_+\cdot),\eta(\zt_-,\pi_-\cdot))=\frac{1}{2}\la\pi^{-1}(\zt_+,-\zt_-),\cdot\ra,
\end{align*}
where $\zt_\pm\in \se(T^{(1,0)_\pm})$ and we used the formula 
\begin{align}\label{eq:eta_pi}
\eta(X,Y)=\pm\frac{1}{2}(\pi_\pm^{-1}X,\pi_\pm^{-1}Y). 
\end{align}
Therefore, \eqref{dL} yields (denoting $e_1=(x_+,x_-)$ and $e_2=(y_+,y_-)$ as in \eqref{eq:dQ})
\begin{align*}
\rd_{\Lb_+}(&\pi^*\ap)(\pi^{-1}e_1,\pi^{-1}e_2)\\
&=\eta(\n^+_{x_++x_-}\zt_+,y_+)-\eta(\n^+_{y_++y_-}\zt_+,x_+)+\frac{1}{2}T(\pi_+^{-1}x_+,\pi_+^{-1}y_+,\pi_+^{-1}\zt_+)\\
&+\eta(\n^-_{x_++x_-}\zt_-,y_-)-\eta(\n^-_{y_++y_-}\zt_-,x_-)-\frac{1}{2}T(\pi_-^{-1}x_-,\pi_-^{-1}y_-,\pi_-^{-1}\zt_-),
\end{align*}
where we expressed $D$ in terms of the connections $\n^\pm$ as
\begin{align*}
D_uv=\pi^{-1}_+\n^+_{\pi u}\pi_+ v_++\pi^{-1}_-\n^-_{\pi u}\pi_- v_-,
\end{align*}
and once again used \eqref{eq:eta_pi}. Finally, invoking \cite[Prop.~2.29]{Hu:2019zro}, we arrive at \eqref{eq:dQ}, proving \eqref{eq:d_pi} and completing the proof.
%%\begin{align*}
%%\la \tl{w},\cdot\ra=\pi^*\eta(\zt,\cdot)=(\pi_+^*\eta(z_+),\pi_-^*\eta(z_-)),
%%\end{align*}
%\begin{align*}
%\rd_{\Lb_+}(\pi^*\ap)(\pi^{-1}e_1,\pi^{-1}e_2)&=e_1\pi^*\ap(\pi^{-1}e_2)-e_2\pi^*\ap(\pi^{-1}e_1)-\pi^*\ap([\pi^{-1}e_1,\pi^{-1}e_2])\\
%&=e_1\ap(e_2)-e_2\ap(e_1)-\la [\pi^{-1}e_1,\pi^{-1}e_2],\pi^*\ap\ra
%\end{align*}
%Now, we rewrite $\brac$ in terms of the generalized Bismut connection $D$ and its generalized torsion $T$ (see \cite[Def.~3]{Gualtieri:2010fd}):
%\begin{align}\label{eq:D-torsion}
%\begin{aligned}
%\la [\pi^{-1}e_1,\pi^{-1}e_2],\pi^*\ap\ra&=\la D_{\pi^{-1}e_1}\pi^{-1}e_2-D_{\pi^{-1}e_2}\pi^{-1}e_1,\pi^*\ap\ra\\
%&-T(\pi^{-1}e_1,\pi^{-1}e_2,\pi^*\ap),
%\end{aligned}
%\end{align}
%where we used the fact that $D$ preserves eigenbundles of $\KK_+$, which are isotropic, so that $\la D_{\pi^*\ap}\pi^{-1}e_1,\pi^{-1}e_1\ra=0$. \eqref{eq:D-torsion} can be further simplified by expressing $D$ in terms of the connections $\n^\pm$ as
%\begin{align*}
%D_uv=\pi^{-1}_+\n^+_{\pi u}\pi_+ v_++\pi^{-1}_-\n^-_{\pi u}\pi_- v_-.
%\end{align*}
%Plugging this into \eqref{eq:D-torsion}, we get
%\begin{align*}
%\la [\pi^{-1}e_1,\pi^{-1}e_2],\pi^*\ap\ra&=
%\end{align*}
%

%We do this component by component, simplifying the notation for $\brac\!\!\mid_{\Lb_+}$ to $\brac$, calculating the contracted expressions $\la [u,v],w\ra$ and $\eta([X,Y]_\QQ,Z)$, while using the following property:
%\begin{align*}
%\pm \frac{1}{2}\la \pi^{-1}_\pm X,\pi_\pm^{-1}Y\ra=\eta(X,Y).
%\end{align*}
%We also note that because $\brac$ closes on $\Lb_+$, the only non-zero components of $\la [u,v],w\ra$ for $u,v\in \se(\Lb_+)$ are for $w\in \se(\tl{\Lb}_+)=\ellt_+\oplus \ellt_-$.
%
%
%We will check that $\rd_\QQ$ and $\rd_{\Lb_+}$ match by checking each component in $L^*=T^*_{(1,0)_+}\oplus T^*_{(1,0)_-}$ and $\Lb_+^*\overset{\la\ ,\ \ra}{\simeq}\tl{\Lb}_+=\ellt_+\oplus\ellt_-$, respectively. Let us start with $\rd_\QQ:\Omega^{(1,0)_+}\rightarrow \Omega^{(2,0)_+}$, which corresponds to plugging $x_+,y_+\in T^{(1,0)_+}$ and $\ap^+\in \Omega^{(1,0)_-}$ in \eqref{eq:dQ}, yielding $\rd_\QQ=(\p_+\ap^+)(x_+,y_+)$. On the other hand, denoting $u_+=\pi_+^{-1}x_+$ and $v_+=\pi^{-1}_+y_+$, $u_+,v_+\in \se(\ell_+)$, we get
%\begin{align*}
%\rd_{\Lb_+}\ap(u_+,v_+)=\pi_+(u_+)\la v_+,\tl{w}_+ \ra - \pi_+(v_+)\la u_+,\tl{w}_+ \ra - \la [u_+,v_+],\tl{w}_+\ra
%\end{align*}
%where $\ap=\la \tl{w}_+,\cdot\ra\in \se(\ell_+^*)$ with $\tl{w}_+\in \se(\ellt_+)$.
%
%% of $\rd_\QQ:\Omega^{(1,0)_-}\rightarrow \Omega^{(2,0)}_+$, which corresponds to plugging $x_+,y_+\in T^{(1,0)_+}$ and $\ap^-\in \Omega^{(1,0)_-}$ in\eqref{eq:dQ}, which vanishes. We now check that $\rd_{\Lb_+)$, the differential given by $\brac$ via \eqref{eq:proof_Liethm} also vanishes. Denoting $u_+=\pi_+^{-1}x_+$ and $v_+=\pi^{-1}_+y_+$, $u_+,v_+\in \se(\ell_+)$
%%\begin{align*}
%%\rd_{\Lb_+)\ap(u_+,v_+)=\pi_+(u_+)\la \ra - \pi_+(v_+)\la \ra-\la 
%%\end{align*}
%
%
%% we glean that because $[u_+,v_+]$ is itself in $\ell_+$ by integrability, $\la [u_+,v_+],\tl{w}_-\ra=0$ for $\tl{w}_-\in \se(\ellt_-)$ since $\ell_+,\ellt_-\subset \tl{\Lb}_+$, which is isotropic. Therefore, we need to check that $\eta([x_+,y_+]_\QQ,\tl{z}_-)=0$ for $\tl{z}_-$ in $T^{(0,1)_-}=\pi_-(\ellt_-)$.
%From , we see that and \eqref{eq:proof_Liethm} with $\ap=\eta(\tl{z}_-)\in \se(T^*_{(1,0)_-})$,
%\begin{align*}
%\eta([x_+,y_+],\tl{z}_-)=x_+\eta(y_+,\tl{z}_-)-y_+\eta(x_+,\tl{z}_-)-
%\end{align*}

\end{proof}
%\begin{align*}
%[\QQ,\Omega_f](X,Y)=a(X)\Omega_f(Y)-a(Y)\Omega_f(X)-\Omega_f([X,Y]_L),
%\end{align*}
%where $\Omega_f \in \se(L^*)$ and $X,Y\in \se(L)$. In coordinates, we have
%\begin{align*}
%\Omega_f=f^+_{i} dx_+^{i}+f^-_{j} dx_-^{j_1},\quad X=X^i_+\p^+_i+X_-^j\p_j^-,\ Y=Y^i_+\p^+_i+Y_-^j\p_j^-,
%\end{align*}
%so that
%\begin{align*}
%[\QQ,\Omega_f](X,Y)=
%\end{align*}
%
%\begin{align*}
%\Omega_f([X,Y]_L)=(X^i_+\p^+_i+X_-^j\p_j^-)[Y_+^if^+_i+Y_-^jf_j^-]-(Y^i_+\p^+_i+Y_-^j\p_j^-)[X_+^if^+_i+X_-^jf_j^-]
%\end{align*}

%\begin{remark}
%Here we see we're getting the $A$-model (i.e. just differential forms) when $K_+=K_-$, and $B$-model (i.e. just 
%\end{remark}

\section*{$(2,2)$ para-SUSY and para-K\"ahler model}

\subsection*{$(2,2)$ para-SUSY}
The $(2,2)$ para-SUSY is in the $(2,2)$ formalism given, using the coordinates on $\RR^{2\mid 4}$ $\{x^\pm,\theta^\pm,\tth^\pm\}$, by
\begin{align*}
Q_\pm=\frac{\p}{\p \tth^\pm}-\theta^\pm\p_\pm,\quad \tl{Q}_\pm=\frac{\p}{\p \theta^\pm}-\tth^\pm\p_\pm,
\end{align*}
and the anti-commutators are given by
\begin{align*}
\{Q_\pm,\tl{Q}_\pm\}=-2\p_\pm.
\end{align*}
We also define the differential operators $D_\pm,\tl{D}_\pm$:
\begin{align*}
D_\pm=\frac{\p}{\p \tth^\pm}+\theta^\pm\p_\pm,\quad \tl{D}_\pm=\frac{\p}{\p \theta^\pm}+\tth^\pm\p_\pm.
\end{align*}

\subsection*{Para-K\"ahler model}
Let $(\PS,\eta,K)$ be a $2n$-dimensional para-K\"ahler manifold. We now consider a sigma model with target $\PS$, given by
\begin{align*}
S(\Phi,\tl{\Phi})=\int d^2x d^2 \theta d^2 \tth K(\Phi,\tl{\Phi}),
\end{align*}
where $K$ is the para-K\"ahler potential and $(\Phi,\tl{\Phi}):\RR^{2\mid 4}\rightarrow \PS$ is a chiral $(2,2)$ field defined by
\begin{align*}
\tl{D}_\pm \Phi=D_\pm \tl{\Phi}=0.
\end{align*}
The individual fields can be expressed as
\begin{align*}
\Phi^i&=\phi^i(y^\pm)+\psi^i_+(y^\pm)\theta^++\psi^i_-(y^\pm)\theta^-+F^i(y^\pm)\theta^+\theta^-\\
\tl{\Phi}^i&=\tl{\phi}^i(\tl{y}^\pm)+\tl{\psi}^i_+(\tl{y}^\pm)\tth^++\tl{\psi}^i_-(\tl{y}^\pm)\tth^-+\tl{F}^i(\tl{y}^\pm)\tth^+\tth^-,
\end{align*}
where $y^\pm=x^\pm+\theta^\pm\tth^\pm$, $\tl{y}^\pm=x^\pm-\theta^\pm\tth^\pm$ and $i=1,\cdots,n$. Therefore, the fundamental fields are $\phi^i,\tl{\phi}^i$, playing the roles of the coordinates on the target, $\psi^i_\pm,\tl{\psi}^i_\pm$, spinors valued in $(\phi,\tl{\phi})^*(L)$ and $(\phi,\tl{\phi})^*(\tl{L})$ ($L, \tl{L} \subset T\PS$ being eigenbundles of $K$), and auxiliary fields $F^i,\tl{F}^i$.

There is an $SO(1,1)\times SO(1,1)$ R-symmetry. This can be seen from the ``diagonal" form of the superalgebra:
\begin{align*}
\{Q_\pm^1,Q_\pm^1\}&=\p_\pm\\
\{Q_\pm^2,Q_\pm^2\}&=-\p_\pm,
\end{align*}
where $Q_\pm^1=\frac{1}{\sqrt{2}}( Q_\pm-\tl{Q}_\pm)$ and $Q_\pm^2=\frac{1}{\sqrt{2}}( Q_\pm+\tl{Q}_\pm)$. This is equivalent to introducing the coordinates $\theta^1_\pm=\frac{1}{\sqrt{2}}(\theta_\pm-\tth_\pm)$, $\theta^2_\pm=\frac{1}{\sqrt{2}}(\theta_\pm+\tth_\pm)$ and defining $Q^1_\pm=\frac{\p}{\p \theta^1_\pm}+\theta_1\p_\pm$, $Q^2_\pm=\frac{\p}{\p \theta^2_\pm}-\theta_2\p_\pm$.

%The R-symmetry then acts as
%\begin{align*}
%\begin{pmatrix}
%\theta^1_\pm \\
%\theta^2_\pm	
%\end{pmatrix}
%\mapsto
%\begin{pmatrix}
%\cosh(\alpha_\pm) & \sinh(\alpha_\pm) \\
%\sinh(\alpha_\pm) & \cosh(\alpha_\pm)
%\end{pmatrix}
%\begin{pmatrix}
%\theta^1_\pm \\
%\theta^2_\pm	
%\end{pmatrix}
%\end{align*}
%or, equivalently, $(\theta^\pm,\tth^\pm)\mapsto (e^{\alpha_\pm} \theta^\pm,e^{-\alpha_\pm}\tth^\pm)$. There are therefore two inequivalent embeddings of the Lorentz group $SO(1,1)$ into the R-symmetry group, we label them by $V$ and $A$:
%\begin{align*}
%R_V(\alpha)&:(\theta^\pm,\tth^\pm)\mapsto (e^\alpha \theta^\pm,e^{-\alpha}\tth^\pm)\\
%R_A(\alpha)&:(\theta^\pm,\tth^\pm)\mapsto (e^{\pm \alpha} \theta^\pm,e^{\mp \alpha}\tth^\pm),
%\end{align*}
%mapping the supercharges as
%\begin{align*}
%R_V(\alpha):& (Q_\pm,\tl{Q}_\pm)\mapsto (e^{-\alpha}Q_\pm,e^{\alpha}\tl{Q}_\pm)\\
%R_A(\alpha):& (Q_\pm,\tl{Q}_\pm)\mapsto (e^{\mp\alpha}Q_\pm,e^{\pm}\tl{Q}_\pm).
%\end{align*}
%The generators of these transformations is
%\begin{align*}
%F_{V/A}=\theta^+\frac{\p}{\p\theta^+}-\tth^+\frac{\p}{\p\tth^+}\pm \theta^-\frac{\p}{\p\theta^-}\mp\tth^-\frac{\p}{\p\tth^-}.
%\end{align*}
%
%Because $F_{V/A}$ has same commutators with other operators as $M$, the Lorentz generator, and additionally all $F_{V/A}$ and $M$ commute among themselves, we can define a new "Lorentz" generators in one of the two following ways:
%\begin{align*}
%M_A=M+F_V,\quad M_B=M+F_A.
%\end{align*}
If we now take in account the charges of $\psi_\pm$ and $\tl{\psi}_\pm$ under $M$, $F_V$ and $F_A$, we see that for $F_A$, $\psi_+,\tl{\psi}_-$ become scalars and for $F_B$ this happens for $\psi_+,\psi_-$.
\begin{center}
\begin{tabular}{c|ccc|cc}
			 & $M$ & $F_V$ & $F_A$ & $A$-twist & $B$-twist\\ \hline
$\psi_+$	 & $-1$& $1$   & $1$   & $0$       & $0$ \\
$\tl{\psi}_+$& $-1$& $-1$  & $-1$  & $-2$      & $-2$ \\
$\psi_-$	 & $1$& $1$   & $-1$  & $2$       & $0$ \\
$\tl{\psi}_-$& $1$& $-1$  & $1$  & $0$      & $2$ \\
\end{tabular}
\end{center}

\section*{Future Deadlines and Tasks}
\paragraph*{Next meeting: Tuesday July 23 afternoon}
\begin{itemize}
\item [\textbf{David}]
\item Para-geometry of $(2,0)$ SUSY - discuss half GC structures and SKT
\item Write about isomorphism between $\TT$ and $T\oplus T$ and figure out relationship between cohomologies (explicitly) in the chiral case for now
\end{itemize}

\begin{itemize}
\item [\textbf{Brian}]
\item Set up Lie algebroid formalism, language of stacks (not too scary, but correct)
\item Cohomology from the AKSZ description
\item Table of contents/outline in a new merged file
\end{itemize}

\bibliographystyle{JHEP}
\bibliography{mybib}

\end{document}

### 2019-11-25 newdraft.tex
newdraft

--- 2019-11-22 oldstuff/draft.tex
@@
 \newcommand{\cE}{\mathcal{E}}
+\newcommand{\cN}{\mathcal{N}}
 %----------------------------------------
@@
 \newcommand{\kk}{\mathrm{k}}
+\newcommand{\Mt}{\tl{M}}
+\newcommand{\pd}{\p\!\!\!\p}
+\newcommand{\Mb}{\mathbb{M}}
+\newcommand{\Drm}{\mathrm{D}}
+\newcommand{\Dcal}{\mathcal{D}}
+\newcommand{\wtl}{\widetilde}
 %----------------------------------------
@@
 \maketitle
-
+\begin{abstract}
+We study a class of $2d$ topological sigma models that are formulated on generalized para-complex target manifolds via the AKSZ framework.
+When the target is additionally generalized para-K\"ahler, these topological theories can be realized as topological twists of $(2,2)$ para-supersymmetric sigma models of Abou-Zeid and Hull.
+We compare our results to the case of generalized complex and generalized K\"ahler geometry, where similar results have been described in the context of the usual $(2,2)$ SUSY by Kapustin and Li.
+We present several examples and show that our construction recovers the A-model and the Poisson sigma model as special cases.
+Moreover, we also introduce new examples of topological theories inherently tied to the para-complex geometry, the para-B-model and a para-complex version of the Landau-Ginzburg model.
+
+\end{abstract}
+\newpage
 \tableofcontents
-
+\newpage
 \section{Introduction}
+
+In \cite{HullTwistedSUSY}, Abou-Zeid and Hull studied the target geometry of certain $2D$ $(2,2)$ supersymmetric sigma models, which compared to the usual $(2,2)$ supersymmetry differ by a choice of sign in the supercommutator relations of its $4$ real supercharges:
+\begin{align*}
+\{Q_\pm,\tl{Q}_\pm\}=-2\p_\pm,
+\end{align*}
+with all other anti-brackets vanishing.
+The geometry of the target space of these sigma models reflects this sign change and in contrast to complex geometry needed for the usual supersymmetry, the target needs to be para-complex.
+More precisely, the required target geometry must be bi-para-Hermitian.
+In \cite{HullTwistedSUSY}, this type of supersymmetry was dubbed {twisted} SUSY, while the name {pseudo}-SUSY was used in various other works.
+Here we use the name {\bf para-SUSY} to reflect its relationship to para-complex geometry and to reserve the adjective ``twisted'' for the context of topological twists.
+
+Para-complex structure on a manifold $\Mb$ is given by the data of an integrable endomorphism $K \in \End(T\Mb)$ such that $K^2=\id$ and its two eigenbundles corresponding to the $+1$ and $-1$ eigenvalues have the same rank.
+Consequently, $\Mb$ needs to have an even dimension $2n$.
+A para-Hermitian structure on $(\Mb,\eta)$ is then obtained by adding a compatible metric $\eta$:
+\begin{align*}
+\eta(K\cdot,K\cdot)=-\eta(\cdot,\cdot).
+\end{align*}
+This condition forces $\eta$ to be of signature $(n,n)$ and implies that $\omega=\eta K$ is an almost symplectic structure called the fundamental form of $K$.
+A bi-para-Hermitian geometry is then defined as a pair of para-Hermitian structures $(\eta,K_\pm)$ sharing the same metric and satisfying an additional condition
+\begin{align}
+\rd^p_\pm\omega_\pm=\pm H \in \Omega^3_{cl.}(\Mb),
+\end{align}
+where $\rd^p_\pm=K^*\circ \rd\circ K_\pm^*$ is the para-complex twisted differential and $\omega_\pm=\eta K_\pm$ are the fundamental forms of $K_\pm$.
+
+In \cite{Hu:2019zro}, it is shown that the bi-para-Hermitian geometry $(\Mb,\eta,K_\pm,H)$ is equivalent to the data of a generalized para-K\"ahler geometry, which is defined as a pair of {\it generalized} para-complex (GpC) structures $\KK_\pm$ \cite{wade2004dirac,Zabzine:2006uz,Hu:2019zro} on $\Mb$,
+\begin{align*}
+\KK_\pm \in \End((\TT)\Mb), \quad \KK^2=\id, \quad \la \KK\cdot,\KK\cdot\ra=-\la\cdot,\cdot \ra,
+\end{align*}
+that commute and whose product $\GG=\KK_+\KK_-$ defines a split signature metric $G$ on $(\TT)\Mb$ via $G(\cdot,\cdot)=\la \GG\cdot,\cdot\ra$.
+Here, $\la\cdot,\cdot \ra$ is the symmetric duality pairing on $(\TT)M$ and the generalized para-complex endomorphisms $\KK_\pm$ satisfy a Courant integrability condition which ensures that its $\pm 1$-eigenbundles are Dirac structures \cite{courant1990dirac}.
+
+Para-complex and para-Hermitian geometry was also recently studied as the description of the extended geometry in the context of T-duality \cite{freidel2017generalised,Freidel:2018tkj,Svoboda:2018rci,Marotta:2018myj}, following the earlier work of Vaisman \cite{vaisman2012geometry,vaisman2013towards}.
+In \cite{Marotta:2019eqc}, Szabo and Marotta described the bosonic sector of the $2D$ sigma models targeted in this extended geometry.
+Various topological models in the AKSZ framework on the para-Hermitian manifold $\Mb=T^*M\simeq M^n\times \RR^n$ were studied in \cite{Kokenyesi:2018xgj} and $3D$ membrane sigma models with this target were the subject of \cite{Chatzistavrakidis:2018ztm}.
+The generalized geometry corresponding to Para-Hermitian geometry and its refined version, Born geometry, has been studied in \cite{Hu:2019zro}.
+
+\paragraph{Main results} In this paper, we combine the results of \cite{HullTwistedSUSY} and \cite{Hu:2019zro} to study the $2D$ topological sigma models with a generalized para-complex target manifold $(\Mb,\KK_+)$.
+This geometry leads to a $2D$ topological theory via the AKSZ formalism as follows.
+The Courant algebroid $(\TT)\Mb$ defines a $3D$ topological theory with a $2$-shifted symplectic NQ target space $({\cal E},\Omega)$ \cite{Roytenberg:2002nu}.
+Because the $\pm 1$-eigenbundles of $\KK$ are Dirac structures in $(\TT)\Mb$, they each define a Lagrangian in $({\cal E},\Omega)$, which are $1$-shifted symplectic NQ manifolds and as such define a $2D$ topological boundary theories.
+
+Additionally, we show that when the GpC manifold $(\Mb,\KK_+)$ additionally admits a generalized para-K\"ahler structure $(\Mb,\KK_+,\KK_-)$, the topological theories for $(\Mb,\KK_+)$ described above can be realized as topological twists of the $(2,2)$ para-SUSY theory attached to $(\Mb,\KK_\pm)$.
+
+We also present several explicit examples of our construction. The well-known examples include the Poisson sigma model of a real Poisson manifold $(\Mb,\Pi)$ that is described by the GpC structure
+\begin{align*}
+\KK_\Pi=
+\begin{pmatrix}
+\id & 2\Pi \\
+0 & -\id
+\end{pmatrix},
+\end{align*}
+the A-model of a symplectic manifold $(\Mb,\omega)$ described by the GpC structure
+\begin{align*}
+\KK_\omega=
+\begin{pmatrix}
+0 & \omega^{-1} \\
+\omega & 0
+\end{pmatrix},
+\end{align*}
+and also the BFF theory (?) that is simply given by the trivial GpC structure
+\begin{align*}
+\KK_0=
+\begin{pmatrix}
+\id & 0 \\
+0 & -\id
+\end{pmatrix}.
+\end{align*}
+
+The new examples that we describe are all tied to para-complex geometry. They are the para-complex version of the B-model of a para-complex manifold $(\Mb,K)$ that is given by the GpC structure
+\begin{align*}
+\KK_K=
+\begin{pmatrix}
+K & 0 \\
+0 & -K^*
+\end{pmatrix},
+\end{align*}
+and the para-complex topological Landau-Ginzburg model that can be seen as a deformation of the above geometry by a para-holomorphic poisson bi-vector $Q$
+\begin{align*}
+\KK_Q=
+\begin{pmatrix}
+K & Q \\
+0 & -K^*
+\end{pmatrix}.
+\end{align*}
+
+Importantly, our construction can also be applied to the more notoriously known generalized complex (GC) geometry, which was in the context of topological sigma models extensively studied in \cite{Zucchini:2004ta,Ikeda:2004cm,Kapustin:2004gv,Pestun:2006rj,Cattaneo:2009zx} to name some of the works, but to the authors' knowledge a similar construction to ours via a boundary reduction was not proposed before.
+Similarly in the GpC case, the GC structure defines a pair of Dirac structures (that are now tied by complex conjugation) and the $2D$ topological theory is recovered again as a boundary theory of the $3D$ theory defined by the underlying Courant algebroid.
+The advantage of our approach is that it provides a unified way to extract the data of a topological theory from any GC structure via a clear geometric procedure on the underlying shifted symplectic spaces.
+In the special case when the manifold is generalized K\"ahler \cite{Gualtieri:2003dx,Gualtieri:2010fd} -- implying it admits a $(2,2)$ SUSY --  the topological theories can again be realized as topological twists \cite{Kapustin:2004gv} of the $(2,2)$ theory.
+Here, the main examples are given by the A- and B- model corresponding to the GC structures $\JJ_\omega$ and $\JJ_I$, respectively:
+\begin{align*}
+\JJ_\omega=
+\begin{pmatrix}
+0 & -\omega^{-1} \\
+\omega & 0
+\end{pmatrix}, \quad
+\JJ_I=
+\begin{pmatrix}
+I & 0 \\
+0 & -I^*
+\end{pmatrix},
+\end{align*}
+as well as the topological Landau-Ginzburg model which is again viewed via the deformation of $\JJ_I$ by a holomorphic poisson bi-vector \cite{Gualtieri:2007bq} $\sigma=-\frac{1}{4}(IQ+iQ)$:
+\begin{align*}
+\JJ_Q=
+\begin{pmatrix}
+I & Q \\
+0 & -I^*
+\end{pmatrix}.
+\end{align*}
+
+Notice, however, that for example the usual Poisson sigma model cannot be obtained in the realm of GC geometry because no GC structure is defined by a real Poisson structure $\Pi$.
+
+%Since the work of (..) \cite{?} it has been known that on any K\"ahler manifold $(M,I,\omega)$, one can define a $2d$ sigma model admitting a $(2,2)$ supersymmetry (SUSY) and such model has a simple local description in terms of the K\"ahler potential.
+Moreover, Witten has shown \cite{?} that such sigma model gives rise to two distinct topological theories -- the A- and B-models -- via a procedure called topological twisting.
+These topological theories have an important interpretation in terms of their underlying geometry: the A-model only depends on the symplectic structure $(M,\omega)$, while the B-model only depends on the complex structure $(M,I)$.
+Additionally, there exists an ${\mathbb Z}_2$ automorphism acting on the original $(2,2)$ supersymmetric theory that exchanges its A- and B-models.
+This is the simplest way one can observe the phenomenon of mirror symmetry in the context of $2d$ sigma models.
+%
+%The K\"ahler geometry does not describe the most general $(2,2)$ sigma model, as was shown in \cite{Gates-hull-rocek-biherm}.
+Instead, the most general geometry is described by a bi-Hermitian geometry, defined by a pair of complex structures $I_\pm$ compatible with the same Riemannian metric $g$ and satisfying the compatibility relation
+%\begin{align*}
+%\rd^c_\pm\omega_\pm=\pm H \in \Omega^3_{cl.}(M),
+%\end{align*}
+%$\omega_\pm$ being the fundamental forms of $I_\pm$ and $\rd^c_\pm$ the associated $\rd^c$-operators.
+For this geometry, the local description is more complicated than in the K\"ahler case, in particular because the analogue of the K\"ahler potential is much harder to describe.
+Consequently, the topological twists are also  more complicated.
+%
+%This problem is nevertheless partially mitigated by an alternative geometric formulation in terms of generalized K\"ahler (GK) geometry, which has been shown in \cite{Gualtieri:2003dx} to be equivalent to the above-described bi-Hermitian geometry $(g,I_\pm,H)$.
+A GK structure on $M$ is given by the data of two complex endomorphisms $\JJ_\pm$ of the bundle $(\TT)M$:
+%\begin{align*}
+%\JJ_\pm \in \End((\TT)M),\quad \JJ_\pm^2=-\id, \quad \la \JJ \cdot,\JJ\cdot \ra= \lara,
+%\end{align*}
+%where $\lara$ denotes the natural duality pairing on $(\TT)M$:
+%\begin{align*}
+%\la X+\ap,Y+\bt\ra=\ap(Y)+\bt(X),\quad X,Y\in \se(TM),\quad \ap,\bt \in \se(T^*M).
+%\end{align*}
+%Additionally, $\JJ_\pm$ are required to commute and their product $\GG\coloneqq -\JJ_+\JJ_-$ to define a
 
@@
 This is one of the main differences between complex and para-complex geometry; one of the eigenbundles can be integrable while the other is not.
-For this reason, it is useful to introduce the notion of {\bf half-integrability}:
-
-%\begin{Def}
-%Let $K$ be an almost para-complex.
-If the $+1$ (respectively $-1$) eigenbundle is Frobenius integrable, we call $K$ a {\bf p-para-complex} (respectively {\bf $n$-para-complex}) structure.
-A $K$ that is both $p$- and $n$- para-complex is simply a para-complex structure.
-%\end{Def}
-
-%\brian{The slash notation complex/product made it really hard to parse the definition since you already put parentheses. 
-%If you want to add a definition for the product case make it another definition, or say "the same definition applies to integrability of product structures.
-%Though, it doesn't seem like we use product structures at all below this, so maybe there is no point.}
-
-\paragraph{Para-Complexification}
-The analogy between complex and para-complex geometry can be made manifest by {\it para-complexification}. \brian{sentence split} 
-This amounts to introducing the algebra of para-complex numbers $$\Cc=\RR\oplus \kk\RR,$$
-\brian{This does not appear to be the most common mathematical terminology for this algebra. 
-We should at least remark that these are more commonly referred to as ``split complex numbers", or "hyperbolic numbers".}
-where $\kk^2=1$ is the para-complex unit, and take linear combinations over $\Cc$. 
-The algebra $\Cc$ has the familiar natural operations
-\begin{align}
-\begin{aligned}
-&\bullet\quad \text{Conjugation: }x+\kk y\mapsto \overline{x+\kk y}=x-\kk y\\
-&\bullet\quad \text{Real part: } x+\kk y \mapsto \text{Re}(x+\kk y)=x\\
-&\bullet\quad \text{Imaginary part: } x+\kk y \mapsto \text{Im}(x+\kk y)=y.
-\end{aligned}
-\end{align}
-
-All tensorial objects can be extended to be $\Cc$-linear, in particular, the para-complexified tangent bundle decomposes as $T\PS\otimes \Cc\coloneqq T\PS^\Cc=T^{(1,0)}\oplus T^{(0,1)}$ to the $\pm \kk$ eigenbundles of the endomorphism $K$, now extended by linearity to $\End(T\PS^\Cc)$.
-There is an isomorphism between the para-complex vector spaces $\Cc^n$ and $\RR^{2n}$, explicitly (see \cite[Ch.~15]{Cortes:2010ykx} for more details):
-\begin{align}\label{tab:identification}
-\begin{array}{ccc}
-(\Cc^n,\kk)&\simeq &(\RR^{2n},\id\times -\id)\\
-(x^i+\kk y^i)_{i=1,\cdots,n} &\mapsto & (x^i+y^i,x^i-y^i)_{i=1,\cdots,n}\\
-(\frac{x^i+\xt_i}{2}+\kk\frac{x^i-\xt_i}{2})_{i=1,\cdots,n} &\mapsfrom & (x^i,\xt_i)_{i=1,\cdots,n}.
+In such cases, we call $\PS$ {\bf half-integrabile}.
+For more details, see for example \cite{??,??}.
+
+\paragraph{Type decomposition} The splitting of the tangent bundle $T\PS=L\oplus \Lt$ gives rise to a decomposition of tensors analogous to the $(p,q)$-decomposition in complex geometry.
+For differential forms, we denote the decomposition as
+\begin{align}\label{eq_plusminus_decomp}
+\Lambda^k (T^*\mathcal{P})&=\bigoplus_{k=m+n}\Lambda^{(m,n)}(T^*\mathcal{P}),
+\end{align}
+where $\Lambda^{(m,n)}(T^*\mathcal{P})=\Lambda^m(T^{*}_{1,0})\otimes \Lambda^n(T^{*}_{0,1})$ and the corresponding sections are denoted by $\Omega^{(m,n)}(\mathcal{P})$.
+The bigradings \eqref{eq_plusminus_decomp} yield the natural projections
+\begin{align*}
+\Pi^{(p,q)}:\Lambda^k(T^*\mathcal{P})&\rightarrow \Lambda^{(p,q)}(T^*\mathcal{P}),
+\end{align*}
+so that when $K$ is integrable, the de-Rham differential splits as $\rd=\p+\tl{\p}$, where
+\begin{align*}
+\begin{array}{cc}
+\p \coloneqq \Pi^{(p+1,q)}\circ \rd, & \tl{\p} \coloneqq \Pi^{(p,q+1)}\circ \rd,
 \end{array}
-\end{align}
+\end{align*}
+are the \textbf{para-complex Dolbeault operators}, satisfying
+\begin{align*}
+\p^2=\tl{\p}^2=\p\tl{\p}+\tl{\p}\p=0.
+\end{align*}
+
+One can also introduce the {\it twisted differential $\rd^p\coloneqq(\Lambda^{k+1}K^*)\circ\rd\circ (\Lambda^kK^*)$}.
+When $K$ is integrable, it can be simply written as $\rd^p=(\p_++\p_-)$ on real forms and $\rd^p=\kk (\p+\bar{\p})$ on para-complex forms.
 
 \paragraph{Para-Holomorphic structure}
-Let now $(\mathcal{P},K)$ be an almost para-complex manifold.
+Let now $(\mathcal{P},K)$ be an almost para-complex manifold of dimension $2n$.
 If $K$ is integrable, we get a set of $2n$ coordinates $(x^i,\tilde{x}_i)$ called {\bf adapted coordinates}, $\mathcal{P}$ locally splits as $M\times \tilde{M}$, and $K$ acts as identity on $TM=L$ and negative identity on $T\tilde{M}=\tilde{L}$.
-The adapted coordinates therefore define two complimentary foliations of $\PS$.
-After para-complexification, we get $n$ {\bf holomorphic coordinates} \footnote{We should use the word para-holomorphic instead of holomorphic but we choose to omit the prefix ``para-" whenever no confusion with complex geometry is possible and recovering it only when needed.} $z^i=\frac{x^i+\xt_i}{2}+\kk \frac{x^i-\xt_i}{2}$, and the conjugate {\bf anti-holomorphic coordinates} $\bar{z}^i=\frac{x^i+\xt_i}{2}-\kk \frac{x^i-\xt_i}{2}$.
-The notion of holomorphicity in the context of para-complex geometry is now entirely analogous to complex geometry.
+The adapted coordinates therefore define two complimentary foliations that we will call {\bf canonical foliations} of the para-complex manifold $\PS$ and denote $M$ and $\Mt$.
+Both $M$ and $\Mt$ are therefore $n$-dimensional manifolds composed of connected components called leafs $M_i$, $\Mt_i$:
+\begin{align*}
+M=\bigcup_i M_i,\quad \Mt=\bigcup_i \Mt_i,
+\end{align*}
+and each are as sets equal to $\PS$.
+
 As usual, a map of para-complex manifolds is called para-holomorphic if its pushforward commutes with the respective para-complex structures
@@
 \end{Def}
+\begin{remark}
+In the following we will omit the prefix ``para-'' in para-holomorphic whenever no confusion with complex holomorphicity is possible.
+\end{remark}
 
@@
 \end{align*}
-where $(x^k,\xt_l)$ and $(y^i,\yt_j)$ are the adapted coordinates on $M$ and $N$, respectively, or (after para-complexification) as a map
-\begin{align*}
-F&: \Cc^n\rightarrow \Cc^m\\
-F&=F^i(z^k,\bar{z}^k)^{i=1,\cdots,m}_{k=1,\cdots, n}, 
-\end{align*}
-It is easy to check from \eqref{eq:def_parahol} that $F$ is a para-holomorphic map iff its components do not depend on anti-holomorphic coordinates on $M$, i.e.
-\begin{align}\label{eq:holomorphic}
-\frac{\p}{\p \bar{z}^k} F^j=\frac{\p}{\p z^k} \bar{F}^j=0.
-\end{align}
-In the real, adapted coordinates, the condition \eqref{eq:def_parahol} reads
+where $(x^k,\xt_l)$ and $(y^i,\yt_j)$ are adapted local coordinates on $M$ and $N$, respectively.
+It is easy to check from \eqref{eq:def_parahol} that $F$ is a holomorphic map iff the components satisfy
 \begin{align}\label{eq:holomorphic_real}
@@
 \end{align}
-The equivalence between \eqref{eq:holomorphic} and \eqref{eq:holomorphic_real} can be checked using the relationships \eqref{tab:identification}.
-
-The conditions \eqref{eq:holomorphic_real} tell us that the holomorphic functions preserve the foliations defined by the adapted coordinates on $M$ and $N$.
-This also means that the transition functions on a para-complex manifold (seen as maps $\RR^{2n}\rightarrow \RR^{2n}$) are holomorphic since the foliations must be preserved, i.e.
+
+The conditions \eqref{eq:holomorphic_real} tell us that the holomorphic functions map the canonical foliations of the para-complex manifolds $M$ and $N$.
+This also means that the transition functions on a para-complex manifold (seen as maps $\RR^{2n}\rightarrow \RR^{2m}$) are holomorphic since the foliations must be preserved, i.e.
 the coordinates transform as
-\begin{align*}
+\begin{align}\label{para-coordinate-transf}
 (x^i,\xt_i)\mapsto (y^j(x^i),\yt_j(\xt_i)).
-\end{align*}
-
-\paragraph{Type decomposition} The splitting of the tangent bundle $T\PS=L\oplus \Lt$ in the real case and $T\PS^\Cc$ in the para-complex case gives rise to a decomposition of tensors analogous to the $(p,q)$-decomposition in complex geometry.
-For differential forms, we denote the real and para-complex decompositions as
-\begin{align}\label{eq_plusminus_decomp}
-\Lambda^k (T^*\mathcal{P})&=\bigoplus_{k=m+n}\Lambda^{(+m,-n)}(T^*\mathcal{P}),\\
-\Lambda^k (T^*\mathcal{P}^\Cc)&=\bigoplus_{k=m+n}\Lambda^{(m,n)}(T^*\mathcal{P}),
-\end{align}
-where $\Lambda^{(+m,-n)}(T^*\mathcal{P})=\Lambda^m(L^*)\otimes \Lambda^n(\Lt^*)$ and $\Lambda^{(m,n)}(T^*\mathcal{P})=\Lambda^m(T^{(1,0)*})\otimes \Lambda^n(T^{(0,1)*})$.
-The corresponding sections are denoted by $\Omega^{(+m,-n)}(\mathcal{P})$ and $\Omega^{(m,n)}$, respectively.
-The bigradings \eqref{eq_plusminus_decomp} yield the natural projections
-\begin{align*}
-\Pi^{(+p,-q)}:\Lambda^k(T^*\mathcal{P})&\rightarrow \Lambda^{(+p,-q)}(T^*\mathcal{P}),\\
-\Pi^{(p,q)}:\Lambda^k(T^*\mathcal{P}^\Cc)&\rightarrow \Lambda^{(p,q)}(T^*\mathcal{P}),
-\end{align*}
-so that when $K$ is integrable, the de-Rham differential splits as $\rd=\p_++\p_-$, in the real case and $\rd=\p+\bar{\p}$ in the para-complexified case, where
-\begin{align*}
-\begin{array}{cc}
-\p_+ \coloneqq \Pi^{(+p+1,-q)}\circ \rd, & \p_- \coloneqq \Pi^{(+p,-q-1)}\circ \rd,\\
-\p \coloneqq \Pi^{(p+1,q)}\circ \rd, & \bar{\p} \coloneqq \Pi^{(p,q+1)}\circ \rd,
-\end{array}
-\end{align*}
-are the \textbf{para-complex Dolbeault operators}, satisfying
-%\begin{align}\label{eq:partials_plusminus}
-%\begin{aligned}
-%\p_+&:\Omega^{(+p,-q)}(\mathcal{P})\rightarrow \Omega^{(+p+1,-q)}(\mathcal{P})\\
-%\p_-&:\Omega^{(+p,-q)}(\mathcal{P})\rightarrow \Omega^{(+p,-q-1)}(\mathcal{P}),
-%\end{aligned}
-%\end{align}
-\begin{align*}
-\p_+^2=\p_-^2=\p_+\p_-+\p_-\p_+&=0\\
-\p^2=\bar{\p}^2=\p\bar{\p}+\bar{\p}\p&=0
-\end{align*}
-
-One can also introduce the {\it twisted differential $\rd^p\coloneqq(\Lambda^{k+1}K^*)\circ\rd\circ (\Lambda^kK^*)$}.
-When $K$ is integrable, it can be simply written as $\rd^p=(\p_++\p_-)$ on real forms and $\rd^p=\kk (\p+\bar{\p})$ on para-complex forms.
-
+\end{align}
+
+This also gives us an intuition into what holomorphic bundles and their holomorphic sections look like.
+First, we notice that the tangent bundle $T\PS$ itself is a holomorphic bundle (see for example \cite{Cortes:2003zd,Hu:2019zro}); this is simply because of the form of the transition functions \eqref{para-coordinate-transf} that induce a holomorphic structure on the tangent bundle.
+The holomorphic sections of $T\PS$ -- the holomorphic vector fields -- are locally of the form
+\begin{align*}
+X= X^i(x)\p_i+\tl{X}_i(\xt)\pt^i,
+\end{align*}
+i.e. the components in $L$ and $\Lt$ individually define vector fields on the foliations $M$ and $\Mt$, respectively.
+
+Similarly, the cotangent bundle is a holomorphic bundle.
+For the higher wedge powers, we find that only $\Lambda^{(k,0)+(0,k)}(T^*\PS)$, $1\leq k\leq n$, are holomorphic bundles.
+The {\bf para-complex Dolbeault complex} is therefore given by
+\begin{align}
+\left(\Omega^{(\bullet,0)}\otimes\Omega^{(0,\bullet)},(\p,\pt)\right)\coloneqq \left(\mathbf{\Omega}^{\bullet,0},\pd\right).
+\end{align}
 %\begin{lemma}
@@
 
-\subsection{Generalized para-geometry}
-In this paper, the term {\it generalized geometry} is used for the study of geometric \brian{geometrical is not a word} structures on the bundle $TM \oplus T^*M$ over some manifold $M$.
+\subsection{Basics of generalized geometry}
+In this paper, the term {\it generalized geometry} is used for the study of geometric structures on the bundle $TM \oplus T^*M$ over some manifold $M$.
 We will typically abbreviate this bundle to $\TT$ whenever the base is understood or unimportant for the discussion.
@@
 \subsubsection{The exact Courant algebroid structure}
-\brian{David, how do you feel about moving this later in the Courant/AKSZ section?}
-We recall basic facts about Courant algebroids in Section \ref{sec: courant}. 
-For now, we record a relationship between generalized paracomplex structures and exact Courant algebroids.
-
 The bundle $\TT$ has a natural Courant algebroid structure given by the symmetric pairing
@@
 
-\subsection{Generalized para-K\"ahler geometry}
-\brian{I don't think this should be the title of this section. It's mostly about paracomplex geometry}
-
+\subsection{Generalized para-complex geometry}
 We now recall the notion of a generalized para-complex \cite{wade2004dirac,Zabzine:2006uz,Hu:2019zro} and a generalized para-K\"ahler \cite{Hu:2019zro} structure.
@@
 
+\subsection{Generalized para-K\"ahler geometry}\label{sec:GpK}
 \begin{Def}
@@
 \cite{Gualtieri:2003dx,Hu:2019zro}) that such metric can be always locally expressed in terms of a two-form $b$ and a metric $g$
-\begin{align*}
+\begin{align}\label{genmetric}
 \GG=\GG(g,b)=\begin{pmatrix}
@@
 \end{pmatrix},
-\end{align*}
+\end{align}
 and the signature of $g$ then determines the signature of $\GG(g,b)$.
@@
 In the usual splitting $\TT$, we then have $C_\pm=graph(b\pm g)$.
-
-\begin{remark}
-The most general $2D$ $(1,1)$ sigma model on a pseudo-Riemannian target $(M,g)$ is locally given by the action functional
-\begin{align}\label{rem:sigmamodel}
-S_{(1,1)}(\Phi)&=\int_{\hat{\Sigma}}[g(\Phi)+b(\Phi)]_{ij}D_+\Phi^iD_-\Phi^j,
-\end{align}
-where $\rd b=H$ is a global closed three-form. Therefore, the data of a generalized metric $\GG$ is equivalent to a specification of the sigma model  \eqref{rem:sigmamodel}.
-\end{remark}
 
@@
 
-In this section we introduce the parasupersymmetry algebra in two-dimensions. 
-\brian{add more}
+In this section we introduce the $(2,2)$ para-SUSY algebra in two dimensions, which is an extension of the $(1,1)$ SUSY similarly to the usual $(2,2)$ SUSY.
+We then realize this superalgebra as a symmetry of a $2D$ $\sigma$-model.
+
+It was shown in \cite{HullTwistedSUSY} that in order to do this, one needs to introduce a pair of para-Hermitian structures $(\eta,K_\pm)$ that form a so-called bi-para-Hermitian geometry.
+In \cite{Hu:2019zro} it was then shown that such geometry can be equivalently described by {\bf generalized para-K\"ahler} geometry.
+Because generalized para-K\"ahler geometry is defined by a pair of generalized para-complex structures that obey extra algebraic conditions (see Section \ref{sec:GpK}), this geometry supports the topological $\sigma$-models discussed in Section \ref{sec:GpC_AKSZ}.
+
+The main content of the present section is therefore to define the topological twists of the $(2,2)$ para-SUSY sigma models and show that they are exactly equal to the topological sigma models defined by the pair of GpC structures.
+%
+%It has been known since \cite{Zumino:1979et} that the $(1,1)$ supersymmetric $\sigma$-model \eqref{eq:(1,1)action} admits $(2,2)$ supersymmetry when $(M,g)$ is a K\"{a}hler manifold.
+In general, $(2,2)$ supersymmetry in fact requires the target to be {\bf generalized K\"ahler} \cite{Gualtieri:2003dx}, which is equivalent to a data of a bi-Hermitian geometry discovered in \cite{Gates:1984nk}.
+For $(2,2)$ para-SUSY, the story is analogous.
+%
+%will see later that in order to realize the para-$(2,2)$ superalgebra as a symmetry of a $2D$ $\sigma$ model, the target manifold must carry a pair of para-complex structures $K_\pm$.
+This is in contrast to the usual case that requires complex structures $I_\pm$ on the target instead.
 
@@
 
-The most general $(1,1)$ supersymmetric sigma model into a target pseudo-Riemannian manifold $(M,g)$ is given by the action functional
+The most general $(1,1)$ supersymmetric sigma model into a target pseudo-Riemannian manifold $(M,\eta)$ is given by the action functional
 \begin{align}\label{eq:(1,1)action}
@@
 where $\Phi=(\Phi^i)_{i=1\cdots n}$ are local representatives for the $(1,1)$ {superfields} which are maps $\Phi: \Sigma^{2|2} \rightarrow M$.
-In the action, $b$ denotes a local two-form potential for a closed three-form, $H=\rd b$, and $D_\pm$ are the superderivatives
+In the action, $b$ denotes a local two-form potential for a closed three-form, $H=\rd b$, and $D^1_\pm$ are the superderivatives
 \begin{align}\label{eq:D1}
@@
 \end{align}
-where $\p_\pm=\frac{\p}{\p x_\pm}$ are derivatives along the lightcone coordinates on $\Sigma$, $x_\pm=\tau\pm\sigma$.
-
-In superworldsheet coordinates, the superfields decompose as
-\begin{align*}
-\Phi^i(\sigma,\tau,\theta_+,\theta_-)=\phi^i(\sigma,\tau)+\psi^i_+(\sigma,\tau)\theta^++\psi_-(\sigma,\tau)\theta^-+F^i(\sigma,\tau)\theta^+\theta^-.
-\end{align*}
+where $\p_\pm=\frac{\p}{\p x_\pm}$ are derivatives along the lightcone coordinates on $\Sigma$, $x_\pm=\tau\pm\sigma$. In superworldsheet coordinates, the superfields decompose as
+\begin{align}\label{fields_(1,1)}
+\Phi^i(\sigma,\tau,\theta_+,\theta_-)=\phi^i(\sigma,\tau)+\theta^+\psi^i_+(\sigma,\tau)+\theta^-\psi_-(\sigma,\tau)+\theta^+\theta^-F^i(\sigma,\tau).
+\end{align}
 Here, $(\phi^i)$ are local representatives for a smooth map $\phi: \Sigma \rightarrow M$.
-
 The fact that this action carries $(1,1)$ supersymmetry means that the action \eqref{eq:(1,1)action} is invariant under transformations generated by the two {supercharges} $Q^1_\pm$,
@@
 obeying the supercommutation relations of the $(1,1)$ supersymmetry algebra (\ref{eq:(1,1)_susy}). 
-
-\subsection{$(2,2)$ parasupersymmetry}
-
-\brian{point to references who have also discussed versions of (2,2) para susy}
-The {\bf (2,2) parasupersymmetry algebra} has the underlying supervector space
+\begin{remark}
+The sigma model \eqref{eq:(1,1)action} is fully determined by the geometric data of the generalized pseudo-metric $\GG(g=\eta,b)$ \eqref{genmetric}.
+\end{remark}
+
+\paragraph{Expanding the $(1,1)$ action}
+We now expand the action \eqref{eq:(1,1)action} by plugging in \eqref{fields_(1,1)} and \eqref{eq:D1}. The expansions read
+%In components, the superfield has the form
+%\[
+%\Phi^i =\phi^i+\theta^+\psi^i_++\theta^-\psi^i_-+\theta^+\theta^-F^i
+%\]
+%The super covariant derivatives $D_{\pm}$ applied to $\Phi^i$ read
 \[
-\mathfrak{t}_{(2,2)} = \RR^{1,1} \oplus \Pi(S_+ \oplus S_+) \oplus \Pi(S_- \oplus S_-) .
+D_\pm\Phi^i =\psi^i_\pm\pm\theta^\mp F^i-\theta^\pm\p_\pm\phi^i\mp\theta^+\theta^-\p_\pm\psi^i_\mp,
 \]
-The Lie brackets are described as follows. 
-If we choose a basis $\{Q^1_{\pm}, Q^2_\pm\}$ for $S_\pm \oplus S_\pm$ then the nontrivial brackets read 
-\begin{equation}\label{(2,2)para}
-(2,2) \; {\rm para} \;\; : \;\; [Q_\pm^1, Q_\pm^1] = 2 \partial_{\pm} \;\; , \;\; [Q_{\pm}^2, Q_{\pm}^2] = -2 \partial_{\pm} .
+and
+\begin{align*}
+[\eta(\Phi)+b(\Phi)]_{ij} = & [\eta(\phi)+b(\phi)]_{ij}+\p_k[\eta(\phi)+b(\phi)]_{ij}(\theta^+\psi_+^k+\theta^-\psi_-^k+\theta^+\theta^-F^k)\\
+& +\frac{1}{2}\p_k\p_l[\eta(\phi)+b(\phi)]_{ij}(\theta^+\psi_+^k+\theta^-\psi_-^k)(\theta^+\psi_+^l+\theta^-\psi_-^l).
+\end{align*}
+After plugging the above in the action and performing the odd integration, the only terms that survive are the $\theta^+\theta^-$ coefficients. From this we find that
+%\begin{align*}
+%\theta^+\theta^-&\left[(g+b)_{ij}(\psi_+^i\p_-\psi^j_++\psi^j_-\p_-\psi^i_-+F^iF^j+\p_+\phi^i\p_-\phi^j)\right. \\
+%&+\p_k(g+b)_{ij}\left(F^k\psi^i_+\psi^j_-+\psi^k_+(-F^i\psi^j_--\psi^i_+\p_-\phi^j)+\psi^k_-(-\p_+\phi^i\psi^j_-+\psi_+^iF^j)\right)\\
+%&\left. +\frac{1}{2}\p_k\p_l(g+b)_{ij}(-\psi_+^k\psi_-^l\psi_+^i\psi_-^j+\psi_-^k\psi_+^l\psi^i_+\psi^j_-) \right].
+%\end{align*}
+the field $F$ enters only algebraically and not via its derivatives. Therefore, it is auxiliary and can be integrated out. To obtain the equations of motion for $F$,
+%we use the formula $\p_kg_{ij}=\Gamma_{ikj}+\Gamma_{jki}$ and collect the terms involving $F$:
+%\begin{align*}
+%g_{ij}F^iF^j+&(\Gamma_{ikj}+\Gamma_{jki})(F^k\psi^i_+\psi^j_--F^i\psi^k_+\psi^j_-+F^j\psi^k_-\psi_+^i)\\
+%+&F^k\psi^i_+\psi^j_-(\p_kb_{ij}+\p_ib_{jk}+\p_jb_{ki}).
+%\end{align*}
+%Using $\Gamma_{ikj}=\Gamma_{kij}$ and $H_{ijk}=(\p_kb_{ij}+\p_ib_{jk}+\p_jb_{ki})$, we can rewrite this as
+%\begin{align*}
+%g_{ij}F^iF^j+2\Gamma_{ikj}F^j\psi^k_-\psi_+^i+F^k\psi^i_+\psi^j_-H_{ijk}=g_{ij}(F^iF^j+2F^j(\Gamma^-)_{lk}^i\psi_-^k\psi_+^l),
+%\end{align*}
+%where $\Gamma^-$ are the Christoffel symbols of the connection $\n^-=\lc-\frac{1}{2}g^{-1}H$. This yields the equation of motion for $F$,
+we vary the resulting bosonic action with respect to $F^i$:
+\begin{align} \label{F_EoM}
+\frac{\delta S_{(1,1)}}{\delta F^i}=0\quad \Longleftrightarrow\quad  F^i=-(\Gamma^-)^i_{jk}\psi^k_-\psi^j_+.
+\end{align}
+Here, $\Gamma^-$ are the Christoffel symbols of the connection $\n^-=\lc-\frac{1}{2}\eta^{-1}H$.
+\david{we can show more of the calculations or put some more in the appendix but this is fairly standard knowledge and I think the above is sufficient}
+\subsection{$(2,2)$ para-supersymmetry}\label{sec:(2,2)parasusy}
+We continue by extending the above $(1,1)$ picture to the $(2,2)$ para-SUSY setting. This version of supersymmetry and the corresponding sigma models were first discussed in \cite{HullTwistedSUSY}.
+
+The {\bf (2,2) para-supersymmetry algebra} has the underlying supervector space
+\[
+\mathfrak{t}_{(2,2)} = \RR^{1,1} \oplus \Pi(S_+ \oplus S_+) \oplus \Pi(S_- \oplus S_-),
+\]
+with the Lie brackets defined as follows: we choose a basis $\{Q^1_{\pm}, Q^2_\pm\}$ for $S_\pm \oplus S_\pm$ in which the nontrivial brackets read 
+\begin{equation}\label{eq:(2,2)para}
+(2,2)\ \text{para-SUSY:}\quad [Q_\pm^1, Q_\pm^1] = 2 \partial_{\pm}, \quad [Q_{\pm}^2, Q_{\pm}^2] = -2 \partial_{\pm} .
 \end{equation}
@@
 Note that this differs from ordinary $(2,2)$ supersymmetry by a sign:
-\begin{equation}\label{(2,2)para}
-(2,2) \; {\rm ordinary} \;\; : \;\; [Q_\pm^1, Q_\pm^1] = 2 \partial_{\pm} \;\; , \;\; [Q_{\pm}^2, Q_{\pm}^2] =  2 \partial_{\pm} .
-\end{equation}
+\begin{equation*}
+(2,2)\ \text{(ordinary) SUSY:}\quad [Q_\pm^1, Q_\pm^1] = 2 \partial_{\pm}, \quad [Q_{\pm}^2, Q_{\pm}^2] = 2 \partial_{\pm} .
+\end{equation*}
 \end{remark}
+
+We can also write the para-SUSY algebra in the more conventional off-diagonal basis $\{{Q}_\pm,\wtl{Q}_\pm\}$, in which the only non-zero brackets read:
+\begin{align*}
+[{Q}_\pm,\wtl{Q}_\pm]=-2\p_\pm.
+\end{align*}
+The two bases $\{Q^1_{\pm}, Q^2_\pm\}$ and $\{{Q}_\pm,\wtl{Q}_\pm\}$ are related by
+\begin{align*}
+Q_\pm=\frac{1}{\sqrt{2}}(Q^2_\pm+Q^1_\pm),\quad \wtl{Q}_\pm=\frac{1}{\sqrt{2}}(Q^2_\pm-Q^1_\pm).
+\end{align*}
+Again, this is analogous to the complex basis of the ordinary $(2,2)$ superalgebra
+\begin{align*}
+[Q_\pm,\overline{Q}_\pm]=2\p_\pm.
+\end{align*}
+
+\david{is the following paragraph needed?}
+\brian{I think it's nice to point out how it  generalizes.}
+
+\begin{remark}
 
@@
 \] 
+This is a general form of the $\cN = (k_+, k_-)$ supersymmetry algebra for which ordinary supersymmetry and para-supersymmetry are special cases.
 The case of $\mathfrak{t}_{(2,2)}$, which will be of most interested to us, corresponds to taking $k_+ = k_- = 2$ and $\eta_\pm^{11} = 1$, $\eta^{22}_\pm = - 1$, $\eta^{12}_{\pm} = 0$.
 
-\brian{Can change basis to off diagonal and write in more conventional way.}
-
-\subsubsection{R-symmetry}
-We have seen above that the $(2,2)$ para-SUSY algebra $\mathfrak{t}_{(2,2)}$ can be diagonalised in terms of the charges\footnote{Note that for the usual $(2,2)$ SUSY one cannot diagonalize the algebra over $\RR$.}
-\begin{align}\label{eq:R-sym_charges}
-\begin{aligned}
-[Q_\pm^1,Q_\pm^1]&=2\p_\pm\\
-[Q_\pm^2,Q_\pm^2]&=-2\p_\pm.
-\end{aligned}
-\end{align}
-We make a change of basis by the formulas $Q_\pm=\frac{1}{\sqrt{2}}(Q^2_\pm+Q^1_\pm)$ and $\tl{Q}_\pm=\frac{1}{\sqrt{2}}(Q^2_\pm-Q^1_\pm)$. 
-Equations \eqref{eq:R-sym_charges} can be written collectively as
+\end{remark}
+
+\paragraph{R-symmetry}
+%We have seen above that the $(2,2)$ para-SUSY algebra $\mathfrak{t}_{(2,2)}$ is diagonalised in terms of the charges
+%\begin{align}\label{eq:R-sym_charges}
+%\begin{aligned}
+%[Q_\pm^1,Q_\pm^1]&=2\p_\pm\\
+%[Q_\pm^2,Q_\pm^2]&=-2\p_\pm.
+%\end{aligned}
+%\end{align}
+%We make a change of basis by the formulas $Q_\pm=\frac{1}{\sqrt{2}}(Q^2_\pm+Q^1_\pm)$ and $\tl{Q}_\pm=\frac{1}{\sqrt{2}}(Q^2_\pm-Q^1_\pm)$. 
+There is a symmetry of the $(2,2)$ para-SUSY algebra \eqref{eq:(2,2)para} that separately rotates the $\pm$-chirality charges, called the R-symmetry.
+To see this, we write the equations \eqref{eq:(2,2)para} collectively as
 \begin{align}\label{eq:R-sym_eta}
-[Q_\pm^a,Q_\pm^b]=2\eta^{ab}\p_\pm,
-\end{align}
-where $\eta^{ab}=\begin{pmatrix}
+[Q_\pm^a,Q_\pm^b]=2\eta^{ab}\p_\pm, \quad 
+\eta^{ab}=\begin{pmatrix}
 1 & 0 \\
 0 & -1
-\end{pmatrix}$. From here it is easy to see that matrices $(M_\pm)^a_b$ that rotate the $\pm$-chirality charges among each other while preserving the commutation relations \eqref{eq:R-sym_eta},
+\end{pmatrix}
+\end{align}
+From here it is easy to see that matrices $(M_\pm)^a_b$ that rotate the $\pm$-chirality charges among each other while preserving the commutation relations \eqref{eq:R-sym_eta},
 \begin{align*}
@@
 i.e. $M_\pm$ have to lie in $SO(1,1)$ for each subscript $\pm$ and the R-symmetry group is therefore $G_R=SO(1,1)_+\times SO(1,1)_-$.
-\david{this is only relevant for the (2,2) formalism, will se if we need this or not}
-The R-symmetry acts on the odd coordinates accordingly as
-\begin{align*}
-\begin{pmatrix}
-\theta^1_\pm \\
-\theta^2_\pm	
-\end{pmatrix}
-\mapsto
-\begin{pmatrix}
-\cosh(\alpha_\pm) & \sinh(\alpha_\pm) \\
-\sinh(\alpha_\pm) & \cosh(\alpha_\pm)
-\end{pmatrix}
-\begin{pmatrix}
-\theta^1_\pm \\
-\theta^2_\pm	
-\end{pmatrix}
-\end{align*}
-or, equivalently, $(\theta^\pm,\tth^\pm)\mapsto (e^{\alpha_\pm} \theta^\pm,e^{-\alpha_\pm}\tth^\pm)$.
+%\david{this is only relevant for the (2,2) formalism, will se if we need this or not}
+%The R-symmetry acts on the odd coordinates accordingly as
+%\begin{align*}
+%\begin{pmatrix}
+%\theta^1_\pm \\
+%\theta^2_\pm	
+%\end{pmatrix}
+%\mapsto
+%\begin{pmatrix}
+%\cosh(\alpha_\pm) & \sinh(\alpha_\pm) \\
+%\sinh(\alpha_\pm) & \cosh(\alpha_\pm)
+%\end{pmatrix}
+%\begin{pmatrix}
+%\theta^1_\pm \\
+%\theta^2_\pm	
+%\end{pmatrix}
+%\end{align*}
+%or, equivalently, $(\theta^\pm,\tth^\pm)\mapsto (e^{\alpha_\pm} \theta^\pm,e^{-\alpha_\pm}\tth^\pm)$.
 There are therefore two inequivalent embeddings of the Lorentz group $SO(1,1)$ into the R-symmetry group, we label them by $V$ and $A$:
-\begin{align*}
-R_V(\alpha)&:(\theta^\pm,\tth^\pm)\mapsto (e^\alpha \theta^\pm,e^{-\alpha}\tth^\pm)\\
-R_A(\alpha)&:(\theta^\pm,\tth^\pm)\mapsto (e^{\pm \alpha} \theta^\pm,e^{\mp \alpha}\tth^\pm),
-\end{align*}
-mapping the supercharges as
-\begin{align*}
-R_V(\alpha):& (Q_\pm,\tl{Q}_\pm)\mapsto (e^{-\alpha}Q_\pm,e^{\alpha}\tl{Q}_\pm)\\
-R_A(\alpha):& (Q_\pm,\tl{Q}_\pm)\mapsto (e^{\mp\alpha}Q_\pm,e^{\pm \alpha}\tl{Q}_\pm).
-\end{align*}
-The generators of these transformations are
-\begin{align*}
-F_{V/A}=\theta^+\frac{\p}{\p\theta^+}-\tth^+\frac{\p}{\p\tth^+}\pm \theta^-\frac{\p}{\p\theta^-}\mp\tth^-\frac{\p}{\p\tth^-}.
-\end{align*}
-
-Because $F_{V/A}$ has same commutators with other operators as $M$, the Lorentz generator, and additionally all $F_{V/A}$ and $M$ commute among themselves, we can define new "Lorentz" generators in one of the two following ways:
-\begin{align*}
-M_A=M+F_V,\quad M_B=M+F_A.
-\end{align*}
-
-\subsection{The $(2,2)$ parasupersymmetric $\sigma$-model}
-It has been known since \cite{Zumino:1979et} that the $(1,1)$ supersymmetric $\sigma$-model \eqref{eq:(1,1)action} admits $(2,2)$ supersymmetry when $(M,g)$ is a K\"{a}hler manifold.
-In general, $(2,2)$ supersymmetry in fact requires the target to be {\bf generalized K\"ahler} \cite{Gualtieri:2003dx}, which is equivalent to a data of a bi-Hermitian geometry discovered by \cite{Gates:1984nk}.
-For $(2,2)$ para-SUSY, the story is analogous.
-It was shown in \cite{HullTwistedSUSY} that in order to extend the $(1,1)$ SUSY of \ref{eq:(1,1)action} to $(2,2)$ para-SUSY, one needs a para-complex version of the biHermitian geometry.
-In \cite{Hu:2019zro} it was then shown that this can be equivalently described by {\bf generalized para-K\"ahler} geometry.
-
-\paragraph{Expanding the $(1,1)$ action}
-
-First, we further analyze the $(1,1)$ supersymmetric theory. 
-Recall the $(1,1)$ supersymmetric $\sigma$-model is described by the action
-\begin{align*}
-S_{(1,1)}(\Phi)&=\int_{\hat{\Sigma}}[g(\Phi)+b(\Phi)]_{ij}D_+\Phi^iD_-\Phi^j.
-\end{align*}
-In components, the superfield has the form
-\[
-\Phi^i =\phi^i+\theta^+\psi^i_++\theta^-\psi^i_-+\theta^+\theta^-F^i
-\]
-The super covariant derivatives $D_{\pm}$ applied to $\Phi^i$ read
-\[
-D_\pm\Phi^i =\psi^i_\pm\pm\theta^\mp F^i-\theta^\pm\p_\pm\phi^i\mp\theta^+\theta^-\p_\pm\psi^i_\mp .
-\]
-Further, we can expand the contributions from the metric and $b$-field as
-\begin{align*}
-[g(\Phi)+b(\Phi)]_{ij} = & [g(\phi)+b(\phi)]_{ij}+\p_k[g(\phi)+b(\phi)]_{ij}(\theta^+\psi_+^k+\theta^-\psi_-^k+\theta^+\theta^-F^k)\\
-& +\frac{1}{2}\p_k\p_l[g(\phi)+b(\phi)]_{ij}(\theta^+\psi_+^k+\theta^-\psi_-^k)(\theta^+\psi_+^l+\theta^-\psi_-^l).
-\end{align*}
-
-After performing the odd integration, the only terms that survive are the $\theta^+\theta^-$ coefficients:
-\begin{align*}
-\theta^+\theta^-&\left[(g+b)_{ij}(\psi_+^i\p_-\psi^j_++\psi^j_-\p_-\psi^i_-+F^iF^j+\p_+\phi^i\p_-\phi^j)\right. \\
-&+\p_k(g+b)_{ij}\left(F^k\psi^i_+\psi^j_-+\psi^k_+(-F^i\psi^j_--\psi^i_+\p_-\phi^j)+\psi^k_-(-\p_+\phi^i\psi^j_-+\psi_+^iF^j)\right)\\
-&\left. +\frac{1}{2}\p_k\p_l(g+b)_{ij}(-\psi_+^k\psi_-^l\psi_+^i\psi_-^j+\psi_-^k\psi_+^l\psi^i_+\psi^j_-) \right].
-\end{align*}
-
-The field $F$ is auxiliary (since it enters only algebraically: no derivations of $F$ appear in the action), and therefore can be integrated out.
-To obtain the equations of motion for $F$, we use the formula $\p_kg_{ij}=\Gamma_{ikj}+\Gamma_{jki}$ and collect the terms involving $F$:
-\begin{align*}
-g_{ij}F^iF^j+&(\Gamma_{ikj}+\Gamma_{jki})(F^k\psi^i_+\psi^j_--F^i\psi^k_+\psi^j_-+F^j\psi^k_-\psi_+^i)\\
-+&F^k\psi^i_+\psi^j_-(\p_kb_{ij}+\p_ib_{jk}+\p_jb_{ki}).
-\end{align*}
-Using $\Gamma_{ikj}=\Gamma_{kij}$ and $H_{ijk}=(\p_kb_{ij}+\p_ib_{jk}+\p_jb_{ki})$, we can rewrite this as
-\begin{align*}
-g_{ij}F^iF^j+2\Gamma_{ikj}F^j\psi^k_-\psi_+^i+F^k\psi^i_+\psi^j_-H_{ijk}=g_{ij}(F^iF^j+2F^j(\Gamma^-)_{lk}^i\psi_-^k\psi_+^l),
-\end{align*}
-where $\Gamma^-$ are the Christoffel symbols of the connection $\n^-=\lc-\frac{1}{2}g^{-1}H$. This yields the equation of motion for $F$,
-\begin{align} \label{F_EoM}
-\frac{\delta S_{(1,1)}}{\delta F^i}=0\quad \Longleftrightarrow\quad  F^i=-(\Gamma^-)^i_{jk}\psi^k_-\psi^j_+
-\end{align}
-
+%\begin{align*}
+%R_V(\alpha)&:(\theta^\pm,\tth^\pm)\mapsto (e^\alpha \theta^\pm,e^{-\alpha}\tth^\pm)\\
+%R_A(\alpha)&:(\theta^\pm,\tth^\pm)\mapsto (e^{\pm \alpha} \theta^\pm,e^{\mp \alpha}\tth^\pm),
+%\end{align*}
+%mapping the supercharges as
+%\begin{align*}
+%R_V(\alpha):& (Q_\pm,\tl{Q}_\pm)\mapsto (e^{-\alpha}Q_\pm,e^{\alpha}\tl{Q}_\pm)\\
+%R_A(\alpha):& (Q_\pm,\tl{Q}_\pm)\mapsto (e^{\mp\alpha}Q_\pm,e^{\pm \alpha}\tl{Q}_\pm).
+%\end{align*}
+%The generators of these transformations are
+%\begin{align*}
+%F_{V/A}=\theta^+\frac{\p}{\p\theta^+}-\tth^+\frac{\p}{\p\tth^+}\pm \theta^-\frac{\p}{\p\theta^-}\mp\tth^-\frac{\p}{\p\tth^-}.
+%\end{align*}
+%
+%Because $F_{V/A}$ has same commutators with other operators as $M$, the Lorentz generator, and additionally all $F_{V/A}$ and $M$ commute among themselves, we can define new "Lorentz" generators in one of the two following ways:
+%\begin{align*}
+%M_A=M+F_V,\quad M_B=M+F_A.
+%\end{align*}
+
+\subsubsection{The $(2,2)$ parasupersymmetric $\sigma$-model}
+We now describe the $2D$ sigma models that carry the $(2,2)$ para-supersymmetry described above.
 %\paragraph{(2,2) SUSY}
-
 %We propose the following symmetry by the $(2,2)$ parasupersymmetry algebra (\ref{(2,2)para}) (setting $\theta^\pm_1\coloneqq \theta^\pm$ for simplicity), which read in superspace notation:
@@
 %where $D_\pm =\frac{\p}{\p\theta^\pm}-\theta^\pm\p_\pm$. 
-
 \paragraph{Extended supersymmetry}
 
-The $\sigma$-model we have just described has manifest $(1,1)$ supersymmetry. 
-We now propose the a symmetry of the action $S_{(1,1)}$ by the extended $(2,2)$ parasupersymmetry algebra (\ref{(2,2)para}).
-In general, this extended symmetry exists only after we make some additional assumptions on the geometric data prescribing the action.
-
-Setting $\theta^\pm_1\coloneqq \theta^\pm$ for simplicity, we propose the following $(2,2)$ parasupersymmetry in $(1,1)$ superfield notation:
+The $\sigma$-model \eqref{eq:(1,1)action} has manifest $(1,1)$ supersymmetry.
+We now impose additional symmetries of the action $S_{(1,1)}$ that generate the $(2,2)$ parasupersymmetry algebra (\ref{eq:(2,2)para}) and discuss the required geometric properties of the target manifold for such extension.
+%In general, this extended symmetry exists only after we make some additional assumptions on the geometric data prescribing the action.
+
+Setting $\theta^\pm_1\coloneqq \theta^\pm$ for notational simplicity, we propose the following $(2,2)$ para-supersymmetry algebra representation on the $(1,1)$ superfields:
 \begin{align}
 \label{q1} Q^1_\pm&=\frac{\p}{\p\theta^\pm}+\theta^\pm\p_\pm \\
-\label{q2} Q^2_\pm\Phi^i&=(K_\pm)^i_j(\Phi)D_\pm\Phi^j
+\label{q2} Q^2_\pm\Phi^i&=(K_\pm)^i_j(\Phi)D_\pm\Phi^j,
 \end{align}
 where $D_\pm =\frac{\p}{\p\theta^\pm}-\theta^\pm\p_\pm$.
-\brian{We need to either recall what $K_{\pm}$ is geometrically, or state that it is a free parameter which we will interpret momentarily.}
-In other words, the infinitesimal action of the element $Q^1_{\pm} \in \mathfrak{t}_{(2,2)}$ is:
-\[
+In \cite{HullTwistedSUSY}, it was shown that in order for \eqref{q1} and \eqref{q2} to generate the superalgebra \eqref{eq:(2,2)para}, the bosonic part of $(K_\pm)^i_j(\Phi)$, $(K_\pm)^i_j(\phi)$, must be a tangent bundle endomorphism on the target manifold such that $K^2=\id$.
+Moreover, $K_\pm$ must be integrable in the sense that the Nijenhuis tensors $N_{K_\pm}$ \eqref{eq:nijenhuis} vanish and $K_\pm$ are parallel with respect to the following connections $\n^\pm$
+\begin{align*}
+\n^\pm K_\pm=0, \quad \n^\pm=\lc\pm\frac{1}{2}\eta^{-1}H,
+\end{align*}
+$\lc$ being the Levi-Civita connection of $\eta$.
+Additionally, the requirement that \eqref{q2} is a symmetry of the action \eqref{eq:(1,1)action} imposes the following algebraic relations between $K,\eta$ and $b$:
+\begin{align*}
+g(T_\pm\cdot,\cdot)+g(\cdot,T_\pm\cdot)&=0\\
+b(T_\pm\cdot,\cdot)+b(\cdot,T_\pm\cdot)&=0.
+\end{align*}
+
+We conclude that $(\eta,K_\pm,b)$, where $\rd b=H$ is a local potential for the $3$-form flux $H\in\Omega_{cl}^3$, is a {\bf bi-para-Hermitian} structure.
+Equivalently, this is the defining data of a {\bf generalized para-K\"ahler structure} $(\KK_\pm)$ on the Courant algebroid $(\TT)$ with a flux $H$.
+
+\paragraph{Action on superfields} The infinitesimal action of the element $Q^1_{\pm} \in \mathfrak{t}_{(2,2)}$ is:
+\begin{align}\label{Q1_phi}
 \Phi^i \mapsto \Phi^i + \epsilon^{\pm}_1 \left( \frac{\p}{\p\theta^\pm}+\theta^\pm\p_\pm \right) \Phi^i
-\]
-where $\epsilon^{\pm}_1$ is an infinitesimal parameter. 
-Similarly, the infinitesimal action by the element $Q^2_{\pm} \in \mathfrak{t}_{(2,2)}$ is:
-\[
+\end{align}
+where $\epsilon^{\pm}_1$ is an infinitesimal odd parameter. Similarly, the infinitesimal action by the element $Q^2_{\pm} \in \mathfrak{t}_{(2,2)}$ is:
+
+\begin{align}\label{Q2_phi}
  \Phi \mapsto \Phi + \epsilon^{\pm}_2 (K_\pm)^i_j(\Phi)D_\pm\Phi^j
-\]
-where $\epsilon^\pm_2$ is an infinitesimal parameter.
-
-\begin{lemma}
-Expanding out in the components of the $(1,1)$ superfield, the infinitesimal action by $Q^1_{+}$ and in Equation (\ref{q1}) reads:
-\[
-Q^1_{+} : (\phi^i, \psi^i_+, \psi^i_-, F^i) \mapsto (\phi^i, \psi^i_{\pm}, F^i) + \epsilon^+_1 (\psi^i_+, \partial_+ \phi, F^i, \partial_+ \psi^i_-) . 
-\]
-and by $Q^1_-$:
-\[
-Q^1_{-} : (\phi^i, \psi^i_+, \psi^i_-, F^i)  \mapsto (\phi^i, \psi^i_{\pm}, F^i) + \epsilon^-_1 (\psi^i_-, \partial^i_- \phi^i, - F^i, - \partial_- \psi^i_+)
-\]
-Similarly, the infinitesimal action by $Q^2_{+}$ in Equation (\ref{q2}) reads:
-\begin{equation}\label{q2plus}
-Q^2_{+} : (\phi^i, \psi^i_+, \psi^i_-, F^i) \mapsto ((K_+)^i_j \psi_+ ^j , - (K_+)^{i}_{j} \partial_+ \phi^j - \partial_k(K_+)^i_j \psi_+^k \psi_+^k, (K_+)^i_j F^j+\p_k(K_+)^i_j\psi^k_-\psi^j_+, \brian{F term})
-\end{equation}
-and for $Q^2_-$:
-\begin{equation}\label{q2minus}
-Q^2_{-} : (\phi^i, \psi^i_+, \psi^i_-, F^i) \mapsto ((K_-)^i_j \psi_- ^j , - (K_-)^{i}_{j} \partial_- \phi^j - \partial_k(K_-)^i_j \psi_-^k \psi_-^k, (K_-)^i_j F^j+\p_k(K_-)^i_j\psi^k_+\psi^j_-, \brian{F term})
-\end{equation}
-\end{lemma}
-
-%\begin{align}\label{Q12_action}
-%\begin{aligned}
-%[Q_\pm^1 ,\phi^i]&=\psi_\pm^i,& [Q_\pm^2 ,\phi^i] &=(K_\pm)^i_j\psi_\pm^j,\\
-%[Q_\pm^1 ,\psi^i_\pm] &=\p_\pm\phi^i,& [Q_\pm^2 ,\psi^i_\pm] &=-(K_\pm)^i_j\p_+\phi^j{\textcolor{red}{+}}\p_k(K_\pm)^i_j\psi_+^k\psi_+^j\\
-%[Q_\pm^1 ,\psi^i_\mp]&=\pm F^i,& [Q_\pm^2 ,\psi^i_\mp] &=(K_\pm)^i_jF^j+\p_k(K_\pm)^i_j\psi^k_\mp\psi^j_\pm.
-%\end{aligned}
+\end{align}
+where $\epsilon^\pm_2$ is again an infinitesimal parameter. Expanding \eqref{Q1_phi}, we get
+\begin{align}\label{Q1_action}
+\begin{aligned}
+Q^1_{+} : (\phi^i, \psi^i_+, \psi^i_-, F^i) &\mapsto (\phi^i, \psi^i_+,\psi^i_-, F^i) + \epsilon^+_1 (\psi^i_+, -\partial_+ \phi, -F^i, \partial_+ \psi^i_-),\\
+Q^1_{-} : (\phi^i, \psi^i_+, \psi^i_-, F^i)  &\mapsto (\phi^i, \psi^i_+,\psi^i_-, F^i) + \epsilon^-_1 (\psi^i_-, -\partial^i_- \phi^i, + F^i, - \partial_- \psi^i_+). 
+\end{aligned}
+\end{align}
+Similarly, expanding \eqref{Q2_phi} gives \textcolor{red}{variations of $F$ are still wrong, need to be finished}
+\begin{align}\label{Q2_action}
+\begin{aligned}
+Q^2_{+} : (\phi^i, \psi^i_+, \psi^i_-, F^i) \mapsto &\  (\phi^i, \psi^i_+, \psi^i_-, F^i)
++\epsilon_2^+\Big((K_+)^i_j \psi_+ ^j\ ,\  (K_+)^{i}_{j} \partial_+ \phi^j\\
+& -\partial_k(K_+)^i_j \psi_+^k \psi_+^j\ ,\ -(K_+)^i_j F^j{-}\p_k(K_+)^i_j\psi^k_-\psi^j_+\ ,\ \\
+&-(K_+)^i_j\p_+\psi_-^j+\p_k(K_+)^i_j\psi^k_+F^j+\p_k(K_+)^i_j\psi^k_-\p_+\phi^j\Big)\\
+Q^2_{-} : (\phi^i, \psi^i_+, \psi^i_-, F^i) \mapsto &\ (\phi^i, \psi^i_+, \psi^i_-, F^i)
++\epsilon_2^-\Big((K_-)^i_j \psi_- ^j\ ,\ - (K_-)^i_j F^j  \\
+&-\partial_k(K_-)^i_j \psi_+^k \psi_-^j\ ,\ -\p_k(K_-)^i_j\psi^k_-\psi^j_-+(K_-)^{i}_{j} \partial_- \phi^j\ ,\  \\
+&(K_-)^i_j\p_-\psi_+^j+\p_k(K_-)^i_j\psi^k_-F^j-\p_k(K_-)^i_j\psi^k_+\p_-\phi^j\Big).
+\end{aligned}
+\end{align}
+%
+%\begin{lemma}
+%Expanding out in the components of the $(1,1)$ superfield, the infinitesimal action by $Q^1_{+}$ and in Equation (\ref{q1}) reads:
+%\[
+%Q^1_{+} : (\phi^i, \psi^i_+, \psi^i_-, F^i) \mapsto (\phi^i, \psi^i_{\pm}, F^i) + \epsilon^+_1 (\psi^i_+, \partial_+ \phi, F^i, \partial_+ \psi^i_-) . 
+%\]
+%and by $Q^1_-$:
+%\[
+%Q^1_{-} : (\phi^i, \psi^i_+, \psi^i_-, F^i)  \mapsto (\phi^i, \psi^i_{\pm}, F^i) + \epsilon^-_1 (\psi^i_-, \partial^i_- \phi^i, - F^i, - \partial_- \psi^i_+)
+%\]
+%Similarly, the infinitesimal action by $Q^2_{+}$ in Equation (\ref{q2}) reads:
+%\begin{equation}\label{q2plus}
+%Q^2_{+} : (\phi^i, \psi^i_+, \psi^i_-, F^i) \mapsto ((K_+)^i_j \psi_+ ^j , - (K_+)^{i}_{j} \partial_+ \phi^j - \partial_k(K_+)^i_j \psi_+^k \psi_+^k, (K_+)^i_j F^j+\p_k(K_+)^i_j\psi^k_-\psi^j_+, \brian{F term})
+%\end{equation}
+%and for $Q^2_-$:
+%\begin{equation}\label{q2minus}
+%Q^2_{-} : (\phi^i, \psi^i_+, \psi^i_-, F^i) \mapsto ((K_-)^i_j \psi_- ^j , - (K_-)^{i}_{j} \partial_- \phi^j - \partial_k(K_-)^i_j \psi_-^k \psi_-^k, (K_-)^i_j F^j+\p_k(K_-)^i_j\psi^k_+\psi^j_-, \brian{F term})
+%\end{equation}
+%\end{lemma}
+%
+%%\begin{align}\label{Q12_action}
+%%\begin{aligned}
+%%[Q_\pm^1 ,\phi^i]&=\psi_\pm^i,& [Q_\pm^2 ,\phi^i] &=(K_\pm)^i_j\psi_\pm^j,\\
+%%[Q_\pm^1 ,\psi^i_\pm] &=\p_\pm\phi^i,& [Q_\pm^2 ,\psi^i_\pm] &=-(K_\pm)^i_j\p_+\phi^j{\textcolor{red}{+}}\p_k(K_\pm)^i_j\psi_+^k\psi_+^j\\
+%%[Q_\pm^1 ,\psi^i_\mp]&=\pm F^i,& [Q_\pm^2 ,\psi^i_\mp] &=(K_\pm)^i_jF^j+\p_k(K_\pm)^i_j\psi^k_\mp\psi^j_\pm.
+%%\end{aligned}
+%%\end{align}
+%%
+%%\textcolor{red}{There's a sign issue above, the $+$ needs to be $-$.}
+%\begin{proof}
+%Recall, in components the superfield is of the form
+%\[
+%\Phi^i =\phi^i+\theta^+\psi^i_++\theta^-\psi^i_-+\theta^+\theta^-F^i .
+%\]
+%The action of the $Q^1_\pm$ charges is straightforward and can be simply read off from the infinitesimal action. 
+%%\begin{align*}
+%%[Q^1_\pm,\Phi]=[Q_\pm^1,\phi^i]+[Q_\pm^1,\psi^i_\pm]\theta^\pm+[Q_\pm^1,\psi^i_\mp]\theta^\mp+[Q_\pm^1,F]\theta^\pm\theta^\mp.
+%%\end{align*}
+%%For instance $[Q_{\pm}^1, \phi^i] = \theta^{\pm} \partial_{\pm} \phi^i$, thus 
+%To obtain the action by the charges $Q^2_\pm$ on the individual components we first need to expand $K_\pm(\Phi)$ in terms of the components of the superfield:
+%\begin{align*}
+%(K_\pm)^i_j(\Phi)=(K_\pm)^i_j(\phi)+\p_k(K_\pm)^i_j\theta^+\psi_+^k+\p_k(K_\pm)^i_j\theta^-\psi_-^k+\p_k(K_\pm)\theta^+\theta^-F^k,
+%\end{align*}
+%so that the infinitesimal action by $Q^2_\pm$ on $\Phi^i$ is:
+%\begin{align}
+%\Phi^i + \epsilon_2^\pm (K_\pm)^i_j(\Phi)(\psi^j_\pm\pm\theta^\mp F^j-\theta^\pm\p_\pm\phi^j\mp\theta^+\theta^-\p_\pm\psi^j_\mp) .
 %\end{align}
+%Reading off the various components this expression yields Equations (\ref{q2plus}) and (\ref{q2minus}).
+%\end{proof}
+
 %
-%\textcolor{red}{There's a sign issue above, the $+$ needs to be $-$.}
-\begin{proof}
-Recall, in components the superfield is of the form
-\[
-\Phi^i =\phi^i+\theta^+\psi^i_++\theta^-\psi^i_-+\theta^+\theta^-F^i .
-\]
-The action of the $Q^1_\pm$ charges is straightforward and can be simply read off from the infinitesimal action. 
-%\begin{align*}
-%[Q^1_\pm,\Phi]=[Q_\pm^1,\phi^i]+[Q_\pm^1,\psi^i_\pm]\theta^\pm+[Q_\pm^1,\psi^i_\mp]\theta^\mp+[Q_\pm^1,F]\theta^\pm\theta^\mp.
-%\end{align*}
-%For instance $[Q_{\pm}^1, \phi^i] = \theta^{\pm} \partial_{\pm} \phi^i$, thus 
-To obtain the action by the charges $Q^2_\pm$ on the individual components we first need to expand $K_\pm(\Phi)$ in terms of the components of the superfield:
-\begin{align*}
-(K_\pm)^i_j(\Phi)=(K_\pm)^i_j(\phi)+\p_k(K_\pm)^i_j\theta^+\psi_+^k+\p_k(K_\pm)^i_j\theta^-\psi_-^k+\p_k(K_\pm)\theta^+\theta^-F^k,
-\end{align*}
-so that the infinitesimal action by $Q^2_\pm$ on $\Phi^i$ is:
-\begin{align}
-\Phi^i + \epsilon_2^\pm (K_\pm)^i_j(\Phi)(\psi^j_\pm\pm\theta^\mp F^j-\theta^\pm\p_\pm\phi^j\mp\theta^+\theta^-\p_\pm\psi^j_\mp) .
-\end{align}
-Reading off the various components this expression yields Equations (\ref{q2plus}) and (\ref{q2minus}).
-\end{proof}
-
-\paragraph{The $(2,2)$ formalism}
-\brian{
-There is the following superspace model for $(2,2)$ parasupersymmetry. 
-Consider the superspace $\RR^{1,1 | 4}$ 
-}
+%\paragraph{The $(2,2)$ formalism}
+%\brian{
+%There is the following superspace model for $(2,2)$ parasupersymmetry. 
+%Consider the superspace $\RR^{1,1 | 4}$ 
+%}
 
 \subsection{$(2,1)$ and $(2,0)$ parasupersymmetry}
-
-Many of the constructions above make sense when there is less total supersymmetry, and we briefly mention two important cases.
-
-The first concerns the $(2,1)$ parasupersymmetry algebra.
-This algebra $\mathfrak{t}_{(2,1)}$ consists of generators $\{Q^1_\pm, Q^2_+\}$ satisfying the same algebra as in (\ref{(2,2)para}). 
+\david{maybe we can just make this a paragraph and say in words (as opposed to propositions) what the geometries are?}
+\brian{I agree. I can do this.}
+Many of the constructions above make sense when there is less total supersymmetry, and we briefly mention two important cases. The first concerns the $(2,1)$ parasupersymmetry algebra.
+This algebra $\mathfrak{t}_{(2,1)}$ consists of generators $\{Q^1_\pm, Q^2_+\}$ satisfying the same algebra as in (\ref{eq:(2,2)para}). 
 Starting with the $(1,1)$ supersymmetric $\sigma$-model (\ref{eq:(1,1)action}), and labeling the odd coordinates by $\theta^\pm = \theta_1^\pm$, one can ask for an additional odd symmetry 
 \[
-Q_2^+ :  \Phi \mapsto \Phi + \epsilon_2^+ K_+(\Phi)^j_i D_+ \Phi^i
+Q^2_+ :  \Phi \mapsto \Phi + \epsilon_2^+ K_+(\Phi)^j_i D_+ \Phi^i
 \]
@@
 
-\section{The AKSZ formalism and 3d TFT}
-\def\fg{\mathfrak{g}}
-In this section we will show how to associate $2D$ topological theories to a generalized (para-)complex structure and relate them to the topological twists of $2D$ $(2,2)$ (para-)SUSY sigma models described in Section \ref{sec:toptwist} and in \cite{Kapustin:2004gv}.
-The key to our construction is to realize the data of a G(p)C structure in terms of its eigenbundles, which are Dirac structures $L$ in the Courant algebroid $\TT$. 
-Via the AKSZ construction \cite{AKSZ}, this correspondence translates into the statement that the Dirac structure $L$ defines a topological boundary theory of a $3D$ topological theory defined by the Courant algebroid $\TT$ \cite{Roytenberg:2002nu}.
-
-Throughout, we will use symplectic $NQ$ manifold as our model for shifted symplectic geometry. 
-We will recall the general setup of associating a $3D$ topological field theory to the data of a Courant algebroid. 
-For a reference, see \cite{Roytenberg:2002nu,??}.
-
-\subsection{Courant algebroids, $3D$ TFTs, and boundary conditions}
-From the point of view of topological field theory, Courant algebroids are important because they provide geometric examples of $2$-shifted symplectic spaces. 
-Via the AKSZ construction, $2$-shifted symplectic spaces are the natural home for $3$-dimensional topological field theories in the BV formalism. 
-\brian{give citations here.}
-
-In \cite{Roytenberg:2002nu}, it is shown how to associate a $2$-shifted symplectic NQ manifold from the data of a Courant algebroid.
-
-\begin{theorem}[\cite{Roytenberg:2002nu}]
-There is an equivalence between isomorphism classes of $2$-shifted symplectic NQ manifolds with body $M$ and isomorphism classes of Courant algebroids on $M$.
-\end{theorem}
-
-We briefly recall this construction.
-
-Recall, the data of a Courant algebroid on a manifold $M$ is a vector bundle $E$, whose sheaf of sections we denote $\cE$, together with a nondegenerate symmetric bilinear pairing $\langle -, -\rangle : \cE \otimes \cE \to C^\infty(M)$ , an anchor map $a : E \to T M$, and a bilinear operator
-\[
-[-,-] : \cE \times \cE \to \cE
-\]
-called the Courant-Dorfman bracket. 
-\brian{spell out properties, find a good reference}
-Denote by $a^* : T^* M \to E^*$ the bundle map dual to $a$.
-
-To every Courant algebroid we can define the following sequence of vector bundles on $M$
-\[
-T^*M \xto{a^*} E \xto{a} TM .
-\]
-A Courant algebroid is called {\em exact} if this sequence of bundles is exact.
-
-\def\Sym{{\rm Sym}}
-
-Using this sequence, we can define the associated $NQ$ manifold $X_E$, following \cite{Ryotenberg:2002nu}.
-The body of the NQ manifold is $M$, and the underlying graded vector bundle is given by $T^*[2] \oplus E[1]$. 
-Define the degree $+1$ vector field 
-\[
-Q : \Gamma(M , \Sym \left(T^*[2] \oplus E[1]\right)^*) \to \Gamma(M , \Sym \left(T^*[2] \oplus E[1]\right)^*) 
-\]
-as follows: for $\psi \in \Sym^{k + \ell + 2} \left(T^*[2] \oplus E[1]\right)^*)$ and
-\[
-(\xi_0 \otimes \cdots \otimes \xi_k) \otimes (\alpha_0 \otimes \cdots \otimes \alpha_\ell) \in \Sym^{k+1}(T^*[2]) \otimes \Sym^{\ell + 1}(E[1]) 
-\]
-define
-\begin{align*}
-(Q \psi) ((\xi_0 \otimes \cdots \otimes \xi_k) \otimes (\alpha_0 \otimes \cdots \otimes \alpha_\ell)) = \brian{finish}
-\end{align*}
-
-All that remains is to describe the $2$-shifted symplectic structure on the NQ manifold $X_E$. 
-This is defined via the obvious pairing between $T^*[2]$ and $T$ together with the pairing $\langle - ,- \rangle$ on $E[1]$.
-In local coordinates \brian{finish}
-
-The simplest type of Courant algebroid is one over a point.
-
-\begin{Ex}\label{ex: cs}
-Any Lie algebra $\fg$ together with a non-degenerate invariant pairing defines a $2$-shifted symplectic structure on the graded manifold $\fg[1]$ living over a point. 
-The dg algebra of functions is the Chevalley-Eilenberg cochain complex computing Lie algebra cohomology $C^*(\fg)$. 
-All such $2$-symplectic NQ manifolds over a point are of this form. 
-%The resulting AKSZ theory is Chern-Simons theory. 
-\end{Ex}
-
-\subsubsection*{The $2$-shifted symplectic space of an exact Courant Algebroid}
-
-We recall the description of the $2$-shifted symplectic NQ manifold $X_E$ associated to an exact Courant algebroid $E$.
-Of course, as a vector bundle $E = \TT$, and hence as a graded manifold $X_E$ is of the form $T^*[2] T[1] M$.
-Concretely, the coordinates on this manifold are given by $(x^i,v^a,p_i,\mu_a)_{i,a=1\cdots n}$, where $x^i$ are the usual coordinates on $M$ with degree $0$, $v^a$ are the corresponding ``velocities'', i.e.
-the fibre coordinates on $T[1]M$ with a degree $1$, and $p_i,\mu_a$ are the momenta corresponding to $x^i,v^a$ with degrees $2,1$, respectively.
-The canonical symplectic form
-\begin{align*}
-\Omega= dx^idp_i+dv^ad\mu_a,
-\end{align*}
-is then of degree $2$.
-$T^*[2]T[1]M$ is the minimal symplectic realization of the shifted bundle $(\TT)[1]M$, which is recovered by setting $p_i=0$.
-The symmetric part of $\Omega$ represents the pairing $\lara$ on $(\TT)M$; this is because we can identify $d\mu_a\leftrightarrow \p_i$ and $dv^a\leftrightarrow dx^i$
-
-\brian{Severa classification}
-
-\begin{theorem}\label{thm: severa}
-The set of isomorphism classes of exact Courant algebroids is a torsor for $H^3(X)$. 
-\end{theorem}
-
-\subsubsection*{The Poisson Courant algebroid}
-
-\brian{Both real and holomorphic versions}
-
-\subsubsection{The AKSZ theory associated to a Courant algebroid}
-
-To any Courant algebroid $E$, we can associate an NQ manifold $X_E$ which carries a $2$-shifted symplectic structure that we denote by $\omega_E$. 
-In the case that the Courant algebroid is exact, call the associated $2$-shifted symplectic space $X_H$, where $H$ labels the Severa class.
-
-\def\sA{\mathcal{A}}
-\def\d{{\rm d}}
-\def\dbar{\Bar{\partial}}
-
-The starting point of the AKSZ construction is the mapping space
-\[
-{\rm Map}\left((M, (\sA^*_M, \d_M)), X_E\right)
-\]
-where $(M, (\sA^*_M, \d_M))$ is a dg manifold with body a smooth oriented manifold $M$. 
-That is, $\sA^*_M$ is a sheaf of graded commutative algebras over the de Rham complex $\Omega^*_M$ and $\d_M$ is a linear operator of degree $+1$ satisfying:
-\begin{itemize}
-\item[(1)] $\sA_M$ is concentrated in finitely many degrees;
-\item[(2)] For each $k$, $\sA^k_M$ is a locally free sheaf of $C^\infty_M$-modules of finite rank;
-\item[(3)] The differential $\d_M : \sA_M^* \to \sA_M^{*+1}$ is square zero differential operator making $(\sA_M , \d_M)$ into a sheaf of commutative dg algebras over the de Rham complex $\Omega^*_M$
-\end{itemize}
-
-\begin{Ex}
-The most important example for us will be the source dg manifold $(M, \Omega^*_M)$, that is $\sA_M = \Omega^*_M$ with de Rham differential. 
-We denote this dg manifold by $M_{\rm dR}$.
-\end{Ex}
-
-\begin{Ex}
-If $M$ has a para-complex structure, then $(M, \Omega^{0,*}_M)$ has the structure of a dg manifold with differential given by the para $\dbar$-operator. 
-\brian{David, is this consistent notation?}
-We will denote this dg manifold by $M_{p \dbar}$. 
-\end{Ex}
-
-\begin{Ex}
-If $\fg$ is a Lie algebra equipped with a non-degenerate invariant pairing, and $X_E = \fg[1]$ as in Example \ref{ex: cs}, then the AKSZ theory (whose target base manifold is a point) is equivalent to Chern-Simons theory on $M$.
-\end{Ex}
-
-\subsubsection{Dirac structures and boundary conditions}
-
-\subsection{Two dimensional TFT from GpC structures}
-
-\brian{Recall that a generalized (para-)complex structure $\JJ$ defines a Dirac structure in $\TT$, and hence a Lagrangian inside of the $2$-shifted symplectic space $\XX_H$.  
-%More generally, if $\JJ$ is a generalized complex structure in an arbitrary Courant algebroid $E$, then we obtain a $2$-shifted Lagrangian inside of the $2$-shifted symplectic space $\XX_E$. 
-This Lagrangian then defines a boundary condition for the three-dimensional AKSZ theory. }
-
-\subsubsection*{Trivial GpC structure}
-
-\subsubsection*{(Real) Poisson $\sigma$-model}
-
-\subsubsection*{Para-complex $A/B$-models}
-
-We point out two special cases of the above general construction.
-
-\brian{The $A$-model is the usual thing.}
-
-\begin{Def}
-The {\bf para-complex $B$-model} with source a closed Riemann surface $\Sigma$ and target a para-complex manifold $X$ is the AKSZ theory with source the de Rham space $\Sigma_{\rm dR}$ and target the $1$-shifted symplectic space $T^*[1] X_{p \dbar}$:
-\[
-{\rm Map}\left(\Sigma_{dR}, T^*[1]  X_{p \dbar}\right) .
-\]
-\end{Def}
-
-\brian{Discuss Si's work on perturbative quantization}
-
-\hrulefill
-
-\brian{***para Kahler example, **example where the paracomplex structures commute but are not equal (this is where people see ``twisted chiral"), para version of T-duality, **Poisson $\sigma$-model, going back and forth between generalized (para) complex.
-}
-
- \brian{discuss anomalies}
-
-\subsection{Para holomorphic variants}
-
-So far, in each of the $\sigma$-models we have discussed in the AKSZ formalism, the fields have depended only topologically on the source Riemann surface. 
-There are closely related $\sigma$-models which depending {\em para-holomorphically} on the source Riemann surface that we briefly discuss.
-
-\section{Twisted parasupersymmetry}\label{sec:toptwist}
-
-In this section we will present how para-supersymmetry theories can be twisted, in exact analogy with twisting in ordinary supersymmetry.
-Applied to the $(2,2)$ parasupersymmetric theories that we have constructed in \S \ref{sec: parasusy}, we find that twisting yield topological field field theories. 
-In the next section, we will construct these topological theories geometrically using the AKSZ formalism.
-
-The procedure for twisting will again follow the analogy between generalized K\"{a}hler (GK) and generalized para-K\"{a}hler (GpK).
-geometries, and we will follow the approach presented in \cite{Kapustin:2004gv} for the GK case.
+\subsection{Topological twists}\label{sec:toptwist}
+
+\brian{I still think this should be a separate section. It can go before AKSZ, if you want, but the answers won't make sense until we introduce the topological theories.}
+
+\brian{Give a general prescription of twisting.}
+
+In this section we show that the R-symmetry of the para-$(2,2)$ superalgebra can be used to produce topological theories from the $(2,2)$ para-supersymmetric model presented in the Section \ref{sec:(2,2)parasusy} via a procedure called topological twisting, exactly analogous to topological twisting in ordinary supersymmetry.
+We show that the theories we obtain match the topological theories constructed in the Section \ref{sec:GpC_AKSZ} in the AKSZ formalism.
+
+In our presentation, we use the similarities between the generalized K\"{a}hler (GK) and generalized para-K\"{a}hler (GpK) geometries, and we follow the approach presented in \cite{Kapustin:2004gv} for the GK case.
 
@@
 
-For the topological twist, we will use the following nilpotent supercharge
-\begin{align}
+Let $(\eta,K_\pm,H=\rd b)$ be the bi-para-Hermitian geometry of the $(2,2)$ para-SUSY sigma model and let $\{Q^1_\pm,Q^1_\pm\}$ be the basis of the superalgebra \eqref{eq:(2,2)para}.
+We define the following nilpotent supercharge
+\begin{align}\label{QQ_nilpotent}
 \QQ=Q_L+Q_R,\quad Q_L=\frac{1}{2}(Q^1_++Q^2_+),\quad Q_R=\frac{1}{2}(Q^1_-+Q^2_-),
@@
 
-\begin{proposition}
+The action of $\QQ$ on these fields is the content of the following statement:
+\begin{proposition}\label{prop_toptwist}
 The action of $Q_{L/R}$ on the fields $\chi$, $\lambda$ and $\phi$ is given by
@@
 \begin{proof}
-The action of $Q_{L/R}$ on $\phi$ can be immediately read off \eqref{Q12_action}:
-\begin{align}
-[Q_L,\phi^i]=\frac{1}{2}[Q_+^1+Q^2_+,\phi^i]=\chi^i.
-\end{align}
-
-We now prove the formulas for the action of $Q_{L/R}$ on $\chi$, the action on $\lambda$ is entirely analogous. First, we expand
-\begin{align}\label{QL_chi}
-[Q_L,\chi^i]=[Q_L,(P_+)^i_j\psi_+^j]=[Q_L,(P_+)^i_j]\psi_+^j\textcolor{red}{+}(P_+)^i_j[Q_L,\psi_+^j].
-\end{align}
-\textcolor{red}{Or maybe here? I think this is the one}
-Because $K_+$ is a function of the bosonic coordinates, we also have $P_+=P_+(\phi)$ and so
-\begin{align}\label{QL_P}
-[Q_L,(P_+)^i_j]=\p_k(P_+)^i_j[Q_L,\phi^k]=\p_k(P_+)^i_j\chi^k.
-\end{align}
-Combining \eqref{QL_chi} and \eqref{QL_P} and using \eqref{Q12_action}, we arrive at
-\begin{align*}
-[Q_L,\chi^i]&=\p_k(P_+)^i_j\chi^k\psi_+^j\textcolor{red}{\overset{?}{\pm}}(P_+)^i_j[(\tl{P}_+)^j_k\p_+\phi^k\textcolor{red}{+}\frac{1}{2}\p_k(K_+)^j_l\psi_+^k\psi_+^l]\\
-&=\p_k(P_+)^i_j(P_+)^k_l\psi_+^l\psi_+^j\textcolor{red}{-}(P_+)^i_j\p_k(P_+)^j_l\psi_+^k\psi_+^l,
-\end{align*}
-where we denoted $\tl{P}_+=\frac{1}{2}(\id-K_+)$ and used $P_+\tl{P}_+=0$. We now expand the projectors, $(P_+)^i_j=\frac{1}{2}(\delta^i_j+(K_+)^i_j)$:
-
-\begin{align*}
-[Q_L,\chi^i]&=\p_k(P_+)^i_j(P_+)^k_l\psi_+^l\psi_+^j\textcolor{red}{-}(P_+)^i_j\p_k(P_+)^j_l\psi_+^k\psi_+^l\\
-&=\frac{1}{2}(\p_j(K_+)^i_l(P_+)^j_k\textcolor{red}{-}(P_+)^i_j\p_k(K_+)^j_l)\psi_+^k\psi_+^l\\
-&=\frac{1}{4}(\p_j(K_+)^i_l(K_+)^j_k\textcolor{red}{-}(K_+)^i_j\p_k(K_+)^j_l)\psi_+^k\psi_+^l\\
-&+\frac{1}{4}(\p_j(K_+)^i_l\psi_+^j\psi_+^l\textcolor{red}{-}\p_k(K_+)^i_l\psi_+^k\psi_+^l)=-\frac{1}{2}(N_{K_+})^i_{kl}\psi_+^k\psi^l_+,
-\end{align*}
-\textcolor{red}{This must be the right sign choice} where in the last line we rewrote $\psi_+^k\psi^l_+=\frac{1}{2}(\psi^k\psi^l-\psi^l\psi^k)$ to get the expression for the Nijenhuis tensor of $K_+$:
-\begin{align*}
-4(N_{K_+})^i_{kl}=(K_+)^j_k\p_j(K_+)^i_l-(K_+)^j_l\p_j(K_+)^i_k \textcolor{red}{-} (K_+)^i_j(\p_k(K_+)^j_l-\p_l(K_+)^j_k).
-\end{align*}
-Invoking integrability of $K_+$, $N_{K_+}=$ and we conclude that $[Q_L,\chi^i]=0$.
-
-Similarly, $[Q_L,\lambda]$ can be expanded
-\begin{align}\label{QL_lambda}
-[Q_L,\lambda^i]&=[Q_L,(P_-)^i_j\psi_-^j]=[Q_L,(P_-)^i_j]\psi_-^j+(P_-)^i_j[Q_L,\psi_-^j]\\
-&=\p_k(P_-)^i_j\chi^k\psi_-^j+(P_-)^i_k((P_+)^k_jF^j+\frac{1}{2}\p_l(K_+)^k_j\psi^l_-\psi_+^j),
-\end{align}
-where we used
-\begin{align*}
-[Q_L,\psi_-^i]=(P_+)^i_jF^j+\frac{1}{2}\p_k(K_+)^i_j\psi^k_-\psi_+^j.
-\end{align*}
-Next, we rewrite the derivative in terms of $\n^-$ and use the property $\n^-P_-=0$:
-\begin{align*}
-\p_k(P_-)^i_j&=\n^-_k(P_-)^i_j-(\Gamma^-)^i_{kl}(P_-)^l_j+(\Gamma^-)^l_{kj}(P_-)^i_l\\
-&=-(\Gamma^-)^i_{kl}(P_-)^l_j+(\Gamma^-)^l_{kj}(P_-)^i_l,
-\end{align*}
-so that
-\begin{align}\label{eq:calc1}
-\begin{aligned}
-\p_k(P_-)^i_j\chi^k\psi_-^j=(-(\Gamma^-)^i_{kl}(P_-)^l_j+(\Gamma^-)^l_{kj}(P_-)^i_l)(P_+)^k_m\psi_+^m\psi_-^j.
-\end{aligned}
-\end{align}
-Similarly,
-\begin{align}\label{eq:calc2}
-\begin{aligned}
-\frac{1}{2}(P_-)^i_k\p_l(K_+)^k_j\psi^l_-\psi_+^j&=(P_-)^i_k\p_l(P_+)^k_j\psi^l_-\psi_+^j\\
-&=(P_-)^i_k(-(\Gamma^-)^k_{ml}(P_+)^m_j+(\Gamma^-)^m_{jl}(P_+)^k_m)\psi^l_-\psi_+^j,
-\end{aligned}
-\end{align}
-where we used
-\begin{align*}
-(\Gamma^+)^i_{jk}=g^{im}(\Gamma_{mjk}+\frac{1}{2}H_{jkm})=g^{im}(\Gamma_{mkj}-\frac{1}{2}H_{kjm})=(\Gamma^-)^i_{kj}.
-\end{align*}
-Plugging \eqref{eq:calc1} and \eqref{eq:calc2} into \eqref{QL_lambda} with use of the equation of motion for $F$ \eqref{F_EoM} then yields
-\begin{align*}
-[Q_L,\lambda^i]&=((\Gamma^-)^i_{km}(P_-)^m_l-(\Gamma^-)^m_{kl}(P_-)^i_m)(P_+)^k_j\psi_-^l\psi_+^j\\
-&+(P_-)^i_k(-(\Gamma^-)^k_{ml}(P_+)^m_j+(\Gamma^-)^m_{jl}(P_+)^k_m)\psi^l_-\psi_+^j\\
-&-(P_-)^i_k(P_+)^k_m(\Gamma^-)^m_{jl}\psi_-^l\psi_+^j
- \end{align*}
-
- terms cancel (\textcolor{red}{up to another relative minus sign!}) as well as cancelling the term $(P_-)^i_k(P_+)^k_jF^j$ by
-\begin{align*}
-(P_-)^i_k(\Gamma^+)^m_{lj}(P_+)^k_m\psi^l_-\psi_+^j=(P_-)^i_k(P_+)^k_j(\Gamma^-)^j_{ml}\psi^l_-\psi_+^m=-(P_-)^i_k(P_+)^k_jF^j
-\end{align*}
-and we arrive at
-\begin{align*}
-\{Q_L,\lambda^i\}=-(\Gamma^-)^i_{kl}\chi^k\lambda^l.
-\end{align*}
-
-Now for $Q_R$, we have
-\begin{align*}
-\{Q_R,\phi^i\}=\lambda^i
-\end{align*}
+See Appendix \ref{appendix:proof_prop}.
 \end{proof}
@@
 \end{align*}
-Because $\chi \in \XX^{(1,0)_+}$ and $\lambda \in \XX^{(1,0)_-}$, we can identify ${\cal O}_f$ with a function on the supermanifold $(T^{(1,0)_+}\oplus T^{(1,0)_-})[1]$, which in turn can be identified with differential form
+Because $\chi \in \XX^{(1,0)_+}$ and $\lambda \in \XX^{(1,0)_-}$, we can identify ${\cal O}_f$ with a function on the supermanifold $(T^{(1,0)_+}\oplus T^{(1,0)_-})[1]$, which in turn can be identified with the differential form
 \begin{align*}
@@
 where $dx_\pm$ are the one-forms satisfying $K_\pm dx_\pm=dx_\pm$, i.e.
-sections of the bundle $T^{*(1,0)_\pm}$.
-Via this identification, the operator ${\cal Q}\coloneqq Q_L+Q_R$ defines a differential $\rd_\QQ$, which acts on the sections of $\bigwedge^k(T^{*(1,0)_+}\oplus T^{*(1,0)_-})$ and because $\QQ$ squares to zero $\rd_\QQ$ also squares to zero.
-Therefore, $\rd_\QQ$ gives rise to a Chevalley-Eilenberg complex $\text{CE}(L)$ of a certain Lie algebroid $L$ which we now describe.
-
-\paragraph{Lie algebroid from bi-para-Hermitian data} The underlying vector bundle of the Lie algebroid is $L=T^{(1,0)_+}\oplus T^{(1,0)_-}$, and the anchor is the sum of the two inclusions $\imath_\pm:\ T^{(1,0)_\pm}\hookrightarrow T$, i.e.
+sections of the bundle $T^*_{(1,0)_\pm}$.
+Via this identification, the operator ${\cal Q}\coloneqq Q_L+Q_R$ defines a differential
+\begin{align*}
+\rd_\QQ:\ \Lambda^\bullet(T^{*(1,0)_+}\oplus T^{*(1,0)_-})\rightarrow \Lambda^{\bullet +1}(T^{*(1,0)_+}\oplus T^{*(1,0)_-})
+\end{align*}
+and because $\QQ$ squares to zero $\rd_\QQ$ also squares to zero. Therefore, $\rd_\QQ$ gives rise to a Chevalley-Eilenberg complex $\text{CE}(L)$ of a certain Lie algebroid $L$ which we now describe.
+
+\paragraph{Lie algebroid from bi-para-Hermitian data} Consider the Lie algebroid $L\overset{a}{\rightarrow} T$ with $L=T^{(1,0)_+}\oplus T^{(1,0)_-}$ and anchor given by the sum of the two inclusions $\imath_\pm:\ T^{(1,0)_\pm}\hookrightarrow T$:
 \begin{align*}
@@
 where $\p_\pm$ denotes the para-complex Dolbeault operators $\p$ for $K_\pm$.
-We can further simplify this expression by writing $\ap=(\eta(\tl{z}_+),\eta(\tl{z}_-))$ for $\tl{z}_\pm \in \se(T^{(1,0)_\pm})$, invoking the formula $\p_\pm\ap^\pm(x_\pm,y_\pm)=\lc_{x_\pm}\ap^\pm(y_\pm)-\lc_{y_\pm}\ap^\pm(x_\pm)$ and recalling $\n^\pm=\lc\pm \frac{1}{2}\eta^{-1}H$:
+We can further rewrite this expression by writing $\ap=(\eta(\tl{z}_+),\eta(\tl{z}_-))$ for $\tl{z}_\pm \in \se(T^{(1,0)_\pm})$, invoking the formula $\p_\pm\ap^\pm(x_\pm,y_\pm)=\lc_{x_\pm}\ap^\pm(y_\pm)-\lc_{y_\pm}\ap^\pm(x_\pm)$ and recalling $\n^\pm=\lc\pm \frac{1}{2}\eta^{-1}H$:
 \begin{align}
@@
 &=\eta(\n^+_{x_++x_-}\zt_+,y_+)-\eta(\n_{y_++y_-}^+\zt_+,x_+)-H(x_+,\zt_+,y_+)\\
-&+\eta(\n_{x_++x_-}^-\zt_-,y_-)-\eta(\n_{y_++y_-}^-\zt_-,x_-)+H(x_-,\zt_-,y_-)
+&+\eta(\n_{x_++x_-}^-\zt_-,y_-)-\eta(\n_{y_++y_-}^-\zt_-,x_-)+H(x_-,\zt_-,y_-).
 \end{aligned}
 \end{align}
+This fully determines the Lie algebroid structure of $L$. However, in the following paragraph we will discuss how the same Lie algebroid arises from the data of a generalized para-K\"ahler structure.
 
@@
 \end{align*}
-where the the eigenbundles of $\KK_+$ are $\Lb_+=\ell_+\oplus\ell_-$ and $\tl{\Lb}_+=\ellt_+\oplus \ellt_-$.
+where the the eigenbundles of $\KK_+$ are $\Lb_+=\ell_+\oplus\ell_-$ and $\wtl{\Lb}_+=\ellt_+\oplus \ellt_-$.
 Because $\Lb$ is a Dirac structure, it defines a Lie algebroid by restriction of the Courant algebroid on $\TT$ to $\Lb$, i.e.
-the Lie algebroid bracket and anchor are given by the restriction of the Dorfman bracket and the projection onto tangent bundle, respectively (see Proposition \ref{prop:dirac_Liealg}.
-
+the Lie algebroid bracket and anchor are given by the restriction of the Dorfman bracket and the projection onto tangent bundle, respectively (see Proposition \ref{prop:dirac_Liealg}).
+We now show that such Lie algebroid is isomorphic to the Lie algebroid defined by $(L,a,\rd_\QQ)$ above:
 \begin{theorem}
@@
 \end{align}
-where $\pi^*=\pi^*_+\oplus\pi_-^*$ and $\pi^*_\pm$ are dual maps to $\pi_\pm:\ell_+\rightarrow T^{(1,0)_\pm}$, extended to a map $\pi^*:\Lambda^k(L^*)\rightarrow\Lambda^k(\Lb_+^*)$.
-
-Because of the chain rule, we only need to check this on degree $0$ and degree $1$ elements in the respective complexes. Degree $0$ follows immediately:
+where $\pi^*=\pi^*_+\oplus\pi_-^*$ is given by the dual maps to $\pi_\pm:\ell_+\rightarrow T^{(1,0)_\pm}$, extended to a map $\pi^*:\Lambda^k(L^*)\rightarrow\Lambda^k(\Lb_+^*)$.
+
+Because of the chain rule, we only need to check \eqref{eq:d_pi} on degree $0$ and degree $1$ elements in the respective complexes. Degree $0$ follows immediately:
 \begin{align*}
@@
 \begin{alignat*}{2}
-\eta:&& T^*_{(1,0)_\pm} &\leftrightarrow T^{(0,1)_\pm}\\
+\eta:&&\  T^*_{(1,0)_\pm} &\leftrightarrow T^{(0,1)_\pm}\\
 \lara:&& \ell^*_\pm &\leftrightarrow \ellt_\pm,
@@
 
-\subsection{Topological twists of the $(2,2)$-model}
-
-\subsection{The (para)holomorphic twist of the $(2,0)$-model}
+We have therefore shown that the observables in the topologically twisted theories are given by the Lie algebroid cohomology of $\Lb$, which is exactly the same as the $2D$ boundary topological theories constructed in the Section \ref{??}:
+\begin{corollary}
+Let $\Phi:\Sigma^{2|2}\rightarrow \Mb$ be a $(2,2)$ para-supersymmetric $\sigma$-model with the target $(\Mb,\KK_\pm,\GG(\eta,b))$ a Generalized para-K\"ahler manifold.
+Then the topological twist of this $\sigma$-model defined by the nilpotent charge $\QQ$ \eqref{QQ_nilpotent} agrees with the $2D$ topological boundary theory determined by the generalized para-complex structure on the Courant algebroid $(\TT)\Mb$ with flux $H\overset{loc.}{=}\rd b$.
+\end{corollary}
+
+\section{The AKSZ formalism and 3d TFT}
+
+\brian{Merge at some point.}
+
+\appendix
+\section{Proof of Proposition \ref{prop_toptwist}}\label{appendix:proof_prop}
+\begin{proof}
+The action of $Q_{L/R}$ on $\phi$ can be immediately read off \eqref{Q12_action}:
+\begin{align}
+[Q_L,\phi^i]=\frac{1}{2}[Q_+^1+Q^2_+,\phi^i]=\chi^i.
+\end{align}
+
+We now prove the formulas for the action of $Q_{L/R}$ on $\chi$, the action on $\lambda$ is entirely analogous. First, we expand
+\begin{align}\label{QL_chi}
+[Q_L,\chi^i]=[Q_L,(P_+)^i_j\psi_+^j]=[Q_L,(P_+)^i_j]\psi_+^j{+}(P_+)^i_j[Q_L,\psi_+^j].
+\end{align}
+Because $K_+$ is a function of the bosonic coordinates, we also have $P_+=P_+(\phi)$ and so
+\begin{align}\label{QL_P}
+[Q_L,(P_+)^i_j]=\p_k(P_+)^i_j[Q_L,\phi^k]=\p_k(P_+)^i_j\chi^k.
+\end{align}
+Combining \eqref{QL_chi} and \eqref{QL_P} and using \eqref{Q12_action}, we arrive at
+\begin{align*}
+[Q_L,\chi^i]&=\p_k(P_+)^i_j\chi^k\psi_+^j{+}(P_+)^i_j\left(-(\tl{P}_+)^j_k\p_+\phi^k{-}\frac{1}{2}\p_k(K_+)^j_l\psi_+^k\psi_+^l\right)\\
+&=\p_k(P_+)^i_j(P_+)^k_l\psi_+^l\psi_+^j{-}(P_+)^i_j\p_k(P_+)^j_l\psi_+^k\psi_+^l,
+\end{align*}
+where we denoted $\tl{P}_+=\frac{1}{2}(\id-K_+)$ and used $P_+\tl{P}_+=0$. We now expand the projectors, $(P_+)^i_j=\frac{1}{2}(\delta^i_j+(K_+)^i_j)$:
+
+\begin{align*}
+[Q_L,\chi^i]&=\p_k(P_+)^i_j(P_+)^k_l\psi_+^l\psi_+^j{-}(P_+)^i_j\p_k(P_+)^j_l\psi_+^k\psi_+^l\\
+&=\frac{1}{2}(\p_j(K_+)^i_l(P_+)^j_k{-}(P_+)^i_j\p_k(K_+)^j_l)\psi_+^k\psi_+^l\\
+&=\frac{1}{4}(\p_j(K_+)^i_l(K_+)^j_k{-}(K_+)^i_j\p_k(K_+)^j_l)\psi_+^k\psi_+^l\\
+&+\frac{1}{4}(\p_j(K_+)^i_l\psi_+^j\psi_+^l{-}\p_k(K_+)^i_l\psi_+^k\psi_+^l)=-\frac{1}{2}(N_{K_+})^i_{kl}\psi_+^k\psi^l_+,
+\end{align*}
+where in the last line we rewrote $\psi_+^k\psi^l_+=\frac{1}{2}(\psi^k\psi^l-\psi^l\psi^k)$ to get the expression for the Nijenhuis tensor of $K_+$:
+\begin{align*}
+4(N_{K_+})^i_{kl}=(K_+)^j_k\p_j(K_+)^i_l-(K_+)^j_l\p_j(K_+)^i_k {-} (K_+)^i_j(\p_k(K_+)^j_l-\p_l(K_+)^j_k).
+\end{align*}
+Invoking integrability of $K_+$, $N_{K_+}=$ and we conclude that $[Q_L,\chi^i]=0$.
+
+Similarly, $[Q_L,\lambda]$ can be expanded
+\begin{align}\label{QL_lambda}
+[Q_L,\lambda^i]&=[Q_L,(P_-)^i_j\psi_-^j]=[Q_L,(P_-)^i_j]\psi_-^j+(P_-)^i_j[Q_L,\psi_-^j]\\
+&=\p_k(P_-)^i_j\chi^k\psi_-^j-(P_-)^i_k\left((P_+)^k_jF^j+\frac{1}{2}\p_l(K_+)^k_j\psi^l_-\psi_+^j\right),
+\end{align}
+where we used
+\begin{align*}
+[Q_L,\psi_-^i]=-(P_+)^i_jF^j\textcolor{red}{-}\frac{1}{2}\p_k(K_+)^i_j\psi^k_-\psi_+^j.
+\end{align*}
+Next, we rewrite the derivative in terms of $\n^-$ and use the property $\n^-P_-=0$:
+\begin{align*}
+\p_k(P_-)^i_j&=\n^-_k(P_-)^i_j-(\Gamma^-)^i_{kl}(P_-)^l_j+(\Gamma^-)^l_{kj}(P_-)^i_l\\
+&=-(\Gamma^-)^i_{kl}(P_-)^l_j+(\Gamma^-)^l_{kj}(P_-)^i_l,
+\end{align*}
+so that
+\begin{align}\label{eq:calc1}
+\begin{aligned}
+\p_k(P_-)^i_j\chi^k\psi_-^j=\left(-(\Gamma^-)^i_{kl}(P_-)^l_j+(\Gamma^-)^l_{kj}(P_-)^i_l\right)(P_+)^k_m\psi_+^m\psi_-^j.
+\end{aligned}
+\end{align}
+Similarly,
+\begin{align}\label{eq:calc2}
+\begin{aligned}
+\frac{1}{2}(P_-)^i_k\p_l(K_+)^k_j\psi^l_-\psi_+^j&=(P_-)^i_k\p_l(P_+)^k_j\psi^l_-\psi_+^j\\
+&=(P_-)^i_k\left(-(\Gamma^-)^k_{ml}(P_+)^m_j+(\Gamma^-)^m_{jl}(P_+)^k_m\right)\psi^l_-\psi_+^j,
+\end{aligned}
+\end{align}
+where we used
+\begin{align*}
+(\Gamma^+)^i_{jk}=g^{im}(\Gamma_{mjk}+\frac{1}{2}H_{jkm})=g^{im}(\Gamma_{mkj}-\frac{1}{2}H_{kjm})=(\Gamma^-)^i_{kj}.
+\end{align*}
+Plugging \eqref{eq:calc1} and \eqref{eq:calc2} into \eqref{QL_lambda} with use of the equation of motion \eqref{F_EoM} for $F$ then yields
+\begin{align*}
+[Q_L,\lambda^i]&=((\Gamma^-)^i_{km}(P_-)^m_l-(\Gamma^-)^m_{kl}(P_-)^i_m)(P_+)^k_j\psi_-^l\psi_+^j\\
+&{-}(P_-)^i_k(-(\Gamma^-)^k_{ml}(P_+)^m_j+(\Gamma^-)^m_{jl}(P_+)^k_m)\psi^l_-\psi_+^j\\
+&+(P_-)^i_k(P_+)^k_m(\Gamma^-)^m_{jl}\psi_-^l\psi_+^j.
+ \end{align*}
+Here all terms cancel except for one, which finally reads
+\begin{align*}
+[Q_L,\lambda^i]=-(\Gamma^-)^i_{kl}\chi^k\lambda^l.
+\end{align*}
+\end{proof}
 

### 2019-12-15 newdraft.tex
edits
comments

@@
 \newcommand{\Mt}{\tl{M}}
-\newcommand{\pd}{\p\!\!\!\p}
+\newcommand{\pd}{\overline{\p\!\!\!\p}}
 \newcommand{\Mb}{\mathbb{M}}
@@
 
-\subsection{Paracomplex geometry}
+\subsection{Paracomplex geometry} \label{sec: paracomplex}
 
@@
 \paragraph{Para-Holomorphic structure}
+
 Let now $(\mathcal{P},K)$ be an almost para-complex manifold of dimension $2n$.
@@
 \end{align}
+\brian{Should this be the thing resolving paraholomorphic functions or anti paraholomorphic functions? If paraholomorphic it should be $\mathbf{\Omega}^{0,\bullet}$. }
 %\begin{lemma}
@@
 
+\brian{I think the approach needs to be explained here.
+The type of twisting that seems to be used here is a bit weaker than the twisting I know. 
+In this section we are claiming everything at the level of observables not at the level of fields.
+This is a small difference, but we should point it out.}
+
+\brian{
+To say that we know what the observables of the twisted theory are, we should first describe what the observables of the untwisted theory are. 
+``Twisting" is then a procedure for deforming this.
+Then, the first fact we need to state is: the observables of the twisted theory are given by the Lie algebroid cohomology of some Lie algebroid. 
+I think this is basically done below, but state it as a proposition.
+}
+
+\brian{
+I'm happy to then use the definition of a ``theory" in terms of the observables for the topological theories. 
+This will make the AKSZ description more concise.
+}
+
 The observables of the twisted theory are therefore polynomials in the odd variables $\chi,\lambda$ with even coefficients dependent on $\phi$:
@@
 \end{align*}
+\brian{This already seems like we're in the twisted theory.
+For instance, why don't derivatives in the fields $\chi$ and $\lambda$ appear?
+When you topologically twist, all observables involving derivatives become cohomologically trivial, and so can be discarded.}
 Because $\chi \in \XX^{(1,0)_+}$ and $\lambda \in \XX^{(1,0)_-}$, we can identify ${\cal O}_f$ with a function on the supermanifold $(T^{(1,0)_+}\oplus T^{(1,0)_-})[1]$, which in turn can be identified with the differential form

### 2019-12-17 AKSZ.tex
AKSZ

--- 2019-11-22 draft2.tex
@@
 \newcommand{\kk}{\mathrm{k}}
-\def\fg{\mathfrak{g}}
+\newcommand{\Mt}{\tl{M}}
+\newcommand{\pd}{\overline{\p\!\!\!\p}}
+\newcommand{\Mb}{\mathbb{M}}
+\newcommand{\Drm}{\mathrm{D}}
+\newcommand{\Dcal}{\mathcal{D}}
+\newcommand{\wtl}{\widetilde}
 %----------------------------------------
@@
 
-\title{Topological Sigma Models from Generalized Para-Complex Geometry}
-
 \begin{document}
 
-\maketitle
-\begin{abstract}
-We study a class of $2d$ topological sigma models that are formulated on generalized para-complex target manifolds via the AKSZ framework.
-When the target is additionally generalized para-K\"ahler, these topological theories can be realized as topological twists of $(2,2)$ para-supersymmetric sigma models of Abou-Zeid and Hull.
-We compare our results to the case of generalized complex and generalized K\"ahler geometry, where similar results have been described in the context of the usual $(2,2)$ SUSY by Kapustin and Li.
-We present several examples and show that our construction recovers the A-model and the Poisson sigma model as special cases.
-Moreover, we also introduce new examples of topological theories inherently tied to the para-complex geometry, the para-B-model and a para-complex version of the Landau-Ginzburg model.
+\section{The AKSZ formalism and para-geometry}
+\def\fg{\mathfrak{g}}
+In this section we will show how to associate a class of $2D$ topological field theories to generalized para-complex structures.
+The construction closely follows the relationship between ordinary (non-para) generalized complex structures and $2D$ topological field theories developed by Gualtieri, Pestun, \brian{other references?}.
 
-\end{abstract}
-\newpage
-\tableofcontents
-\newpage
-\section{Introduction}
-Since the work of (..) \cite{?} it has been known that on any K\"ahler manifold $(M,I,\omega)$, one can define a $2d$ sigma model admitting a $(2,2)$ supersymmetry (SUSY) and such model has a simple local description in terms of the K\"ahler potential.
-Moreover, Witten has shown \cite{?} that such sigma model gives rise to two distinct topological theories -- the A- and B-models -- via a procedure called topological twisting.
-These topological theories have an important interpretation in terms of their underlying geometry: the A-model only depends on the symplectic structure $(M,\omega)$, while the B-model only depends on the complex structure $(M,I)$.
-Additionally, there exists an ${\mathbb Z}_2$ automorphism acting on the original $(2,2)$ supersymmetric theory that exchanges its A- and B-models.
-This is the simplest way one can observe the phenomenon of mirror symmetry in the context of $2d$ sigma models.
+The prescription of defining the $2D$ topological theory associated to a GpC structure starts with a $3D$ topological field theory which is defined for any manifold $M$. 
+More generally, this $3D$ theory can be defined for any {\em Courant algebroid} on $M$ \cite{Roytenberg:2002nu}., but for most examples we will only consider the standard exact Courant algebroid (or twisted versions) defined by the Dorfman bracket.
+The key to our construction is to realize the data of a G(p)C structure in terms of its eigenbundles, which are Dirac structures $L$ in the Courant algebroid $\TT$.
 
-The K\"ahler geometry does not describe the most general $(2,2)$ sigma model, as was shown in \cite{Gates-hull-rocek-biherm}.
-Instead, the most general geometry is described by a bi-Hermitian geometry, defined by a pair of complex structures $I_\pm$ compatible with the same Riemannian metric $g$ and satisfying the compatibility relation
+Via the AKSZ construction \cite{AKSZ}, this correspondence translates into the statement that the Dirac structure $L$ defines a topological boundary theory of the $3D$ topological theory defined by the standard Courant algebroid.
+\brian{cite Severa} \cite{SeveraTduality}.
+
+In Section \ref{??}, we will relate these theories topological twists of $2D$ $(2,2)$ (para-)SUSY sigma models described in Section \ref{sec:toptwist} and in \cite{Kapustin:2004gv}.
+
+All of the topological field theories in this section are of $\sigma$-model type and arise through the AKSZ formalism. 
+Throughout, we will use symplectic $NQ$ manifold as our model for shifted symplectic geometry which is the essential ingredient in this construction.
+
+%Later we will use the idea of Lagrangian intersections \brian{PTVV, ButsonYoo, Costello,...}.
+
+\subsection{Courant algebroids, $3D$ TFTs, and boundary conditions}
+First, we recall the general setup of associating a $3D$ topological field theory to the data of a Courant algebroid. 
+For a reference, see \cite{Roytenberg:2002nu,??}.
+
+From the point of view of topological field theory, Courant algebroids are important because they provide geometric examples of $2$-shifted symplectic spaces. 
+Via the AKSZ construction, $2$-shifted symplectic spaces are the natural home for $3$-dimensional topological field theories in the BV formalism. 
+\brian{give citations here.}
+
+\brian{recollection on shifted symplectic NQ manifolds}
+
+In \cite{Roytenberg:2002nu}, it is shown how to associate a $2$-shifted symplectic NQ manifold from the data of a Courant algebroid.
+
+\begin{theorem}[\cite{Roytenberg:2002nu}]
+There is an equivalence between isomorphism classes of $2$-shifted symplectic NQ manifolds with body $M$ and isomorphism classes of Courant algebroids on $M$.
+\end{theorem}
+
+\begin{remark}
+In \cite{PymSafronov} it was shown that a more general class of $2$-shifted symplectic derived spaces, called $L_\infty$ algebroids, are equivalent to {\em twisted} Courant algebroids. 
+This is similar to a Courant algebroid, where the Jacobi identity only holds up to homotopy given by some closed $4$-form. 
+\end{remark}
+
+We briefly recount the construction of the $2$-shifted symplectic NQ manifold from the data of a Courant algebroid.
+
+\def\Sym{{\rm Sym}}
+
+Given any Courant algebroid $E \to M$, we can have the following sequence of maps $T^* \to E \to T$, the latter is the anchor and the first map is the linear dual to the anchor.
+Using this sequence, we can define the associated $NQ$ manifold $X_E$, following \cite{Ryotenberg:2002nu}.
+The body of the NQ manifold is $M$, and the underlying graded vector bundle is given by $T^*[2] \oplus E[1]$. 
+Define the degree $+1$ vector field 
+\[
+Q : \Gamma(M , \Sym \left(T^*[2] \oplus E[1]\right)^*) \to \Gamma(M , \Sym \left(T^*[2] \oplus E[1]\right)^*) 
+\]
+as follows: for $\psi \in \Sym^{k + \ell + 2} \left(T^*[2] \oplus E[1]\right)^*)$ and
+\[
+(\xi_0 \otimes \cdots \otimes \xi_k) \otimes (\alpha_0 \otimes \cdots \otimes \alpha_\ell) \in \Sym^{k+1}(T^*[2]) \otimes \Sym^{\ell + 1}(E[1]) 
+\]
+define
 \begin{align*}
-\rd^c_\pm\omega_\pm=\pm H \in \Omega^3_{cl.}(M),
-\end{align*}
-$\omega_\pm$ being the fundamental forms of $I_\pm$ and $\rd^c_\pm$ the associated $\rd^c$-operators.
-For this geometry, the local description is more complicated than in the K\"ahler case, in particular because the analogue of the K\"ahler potential is much harder to describe.
-Consequently, the topological twists are also  more complicated.
-
-This problem is nevertheless partially mitigated by an alternative geometric formulation in terms of generalized K\"ahler (GK) geometry, which has been shown in \cite{Gualtieri:2003dx} to be equivalent to the above-described bi-Hermitian geometry $(g,I_\pm,H)$.
-A GK structure on $M$ is given by the data of two complex endomorphisms $\JJ_\pm$ of the bundle $(\TT)M$:
-\begin{align*}
-\JJ_\pm \in \End((\TT)M),\quad \JJ_\pm^2=-\id, \quad \la \JJ \cdot,\JJ\cdot \ra= \lara,
-\end{align*}
-where $\lara$ denotes the natural duality pairing on $(\TT)M$:
-\begin{align*}
-\la X+\ap,Y+\bt\ra=\ap(Y)+\bt(X),\quad X,Y\in \se(TM),\quad \ap,\bt \in \se(T^*M).
-\end{align*}
-Additionally, $\JJ_\pm$ are required to commute and their product $\GG\coloneqq -\JJ_+\JJ_-$ to define a
-
-\subsection{Notations and conventions}
-
-\brian{Conventions for odd Lie brackets $[-,-]$ and $\{-,-\}$.}
-
-\section{Background on paracomplex and generalized geometry}
-\david{would just put the introduction of paracomplex geometry (minus the generalized part) in appendix, we did that even in the other paper which is literally a differential geometry paper}
-
-\subsection{Paracomplex geometry}
-
-In this section we introduce para-complex geometry with emphasis on the analogy with complex geometry.
-More details can be found in \cite{Hu:2019zro} or \cite[Ch.~15]{Cortes:2010ykx}, for example.
-\brian{I think you should cite your work here too.}
-
-\begin{Def}\label{def:paracpx}
-An (almost) {\bf product structure} on a smooth manifold $\PS$ is an endomorphism $K\in \Endo(T\PS)$ which squares to the identity, $K^2=\id_{T\PS}$, $K\neq \id$.
-An (almost) \textbf{para-complex structure} is a product structure such that the $+1$ and $-1$ eigenbundles of $K$ have the same rank.
-\end{Def}
-A direct consequence of above definition is that any para-complex manifold is of even dimension.
-From now on, the $+1$ and $-1$ eigenbundles of an almost product/para-complex structure will be denoted $L$ and $\Lt$, respectively.
-
-\paragraph{Integrability} The use of the word {\it almost} as usual refers to integrability of the endomorphism, i.e.
-whether its eigenbundles are involutive with respect to the Lie bracket and therefore define a foliation of the underlying manifold.
-Similarly to the complex case, the integrability is governed by the \textbf{Nijenhuis tensor}
-\begin{align}\label{eq:nijenhuis}
-\begin{aligned}
-N_K(X,Y)&=[X,Y]+[KX,KY]-K([KX,Y]+[X,KY])\\
-&=(\n_{KX}K)Y+(\n_XK)KY-(\n_{KY}K)X-(\n_YK)KX\\
-&=4(\PP[\PPt X,\PPt Y]+\PPt[\PP X,\PP Y]),
-\end{aligned}
-\end{align}
-where $\n$ is any torsionless connection and $\PP\coloneqq\frac{1}{2}(\id+K)$ and $\PPt\coloneqq\frac{1}{2}(\id-K)$ are the projections onto $L$ and $\Lt$, respectively.
-We say $K$ is integrable and call $K$ a product/para-complex manifold if $N_K=0$.
-From \eqref{eq:nijenhuis} it is apparent that $K$ is integrable if and only if {\it both} eigenbundles are simultaneously Frobenius integrable, i.e.
-involutive distributions in $T\PS$.
-This is one of the main differences between complex and para-complex geometry; one of the eigenbundles can be integrable while the other is not.
-For this reason, it is useful to introduce the notion of {\bf half-integrability}:
-
-%\begin{Def}
-%Let $K$ be an almost para-complex.
-If the $+1$ (respectively $-1$) eigenbundle is Frobenius integrable, we call $K$ a {\bf p-para-complex} (respectively {\bf $n$-para-complex}) structure.
-A $K$ that is both $p$- and $n$- para-complex is simply a para-complex structure.
-%\end{Def}
-
-%\brian{The slash notation complex/product made it really hard to parse the definition since you already put parentheses. 
-%If you want to add a definition for the product case make it another definition, or say "the same definition applies to integrability of product structures.
-%Though, it doesn't seem like we use product structures at all below this, so maybe there is no point.}
-
-\paragraph{Type decomposition} \david{simplify this section} The splitting of the tangent bundle $T\PS=L\oplus \Lt$ in the real case and $T\PS^\Cc$ in the para-complex case gives rise to a decomposition of tensors analogous to the $(p,q)$-decomposition in complex geometry.
-For differential forms, we denote the real and para-complex decompositions as
-\begin{align}\label{eq_plusminus_decomp}
-\Lambda^k (T^*\mathcal{P})&=\bigoplus_{k=m+n}\Lambda^{(+m,-n)}(T^*\mathcal{P}),\\
-\Lambda^k (T^*\mathcal{P}^\Cc)&=\bigoplus_{k=m+n}\Lambda^{(m,n)}(T^*\mathcal{P}),
-\end{align}
-where $\Lambda^{(+m,-n)}(T^*\mathcal{P})=\Lambda^m(L^*)\otimes \Lambda^n(\Lt^*)$ and $\Lambda^{(m,n)}(T^*\mathcal{P})=\Lambda^m(T^{(1,0)*})\otimes \Lambda^n(T^{(0,1)*})$.
-The corresponding sections are denoted by $\Omega^{(+m,-n)}(\mathcal{P})$ and $\Omega^{(m,n)}$, respectively.
-The bigradings \eqref{eq_plusminus_decomp} yield the natural projections
-\begin{align*}
-\Pi^{(+p,-q)}:\Lambda^k(T^*\mathcal{P})&\rightarrow \Lambda^{(+p,-q)}(T^*\mathcal{P}),\\
-\Pi^{(p,q)}:\Lambda^k(T^*\mathcal{P}^\Cc)&\rightarrow \Lambda^{(p,q)}(T^*\mathcal{P}),
-\end{align*}
-so that when $K$ is integrable, the de-Rham differential splits as $\rd=\p_++\p_-$, in the real case and $\rd=\p+\bar{\p}$ in the para-complexified case, where
-\begin{align*}
-\begin{array}{cc}
-\p_+ \coloneqq \Pi^{(+p+1,-q)}\circ \rd, & \p_- \coloneqq \Pi^{(+p,-q-1)}\circ \rd,\\
-\p \coloneqq \Pi^{(p+1,q)}\circ \rd, & \bar{\p} \coloneqq \Pi^{(p,q+1)}\circ \rd,
-\end{array}
-\end{align*}
-are the \textbf{para-complex Dolbeault operators}, satisfying
-%\begin{align}\label{eq:partials_plusminus}
-%\begin{aligned}
-%\p_+&:\Omega^{(+p,-q)}(\mathcal{P})\rightarrow \Omega^{(+p+1,-q)}(\mathcal{P})\\
-%\p_-&:\Omega^{(+p,-q)}(\mathcal{P})\rightarrow \Omega^{(+p,-q-1)}(\mathcal{P}),
-%\end{aligned}
-%\end{align}
-\begin{align*}
-\p_+^2=\p_-^2=\p_+\p_-+\p_-\p_+&=0\\
-\p^2=\bar{\p}^2=\p\bar{\p}+\bar{\p}\p&=0
+(Q \psi) ((\xi_0 \otimes \cdots \otimes \xi_k) \otimes (\alpha_0 \otimes \cdots \otimes \alpha_\ell)) = \brian{finish}
 \end{align*}
 
-One can also introduce the {\it twisted differential $\rd^p\coloneqq(\Lambda^{k+1}K^*)\circ\rd\circ (\Lambda^kK^*)$}.
-When $K$ is integrable, it can be simply written as $\rd^p=(\p_++\p_-)$ on real forms and $\rd^p=\kk (\p+\bar{\p})$ on para-complex forms.
+All that remains is to describe the $2$-shifted symplectic structure on the NQ manifold $X_E$. 
+This is defined via the obvious pairing between $T^*[2]$ and $T$ together with the pairing $\langle - ,- \rangle$ on $E[1]$.
+In local coordinates \brian{finish}
 
-%\begin{lemma}
-%Let $(\PS,K)$ be a paracomplex manifold. Then $\rd^p\coloneqq(\Lambda^{k+1}K)\circ\rd\circ (\Lambda^kK)$ can be expressed as
-%\begin{align}\label{eq:dp-operator}
-%\rd^p=\p_+-\p_-.
-%\end{align}
-%\end{lemma}
-%\begin{proof}
-%Let $\ap \in \Omega^{+m,-n}(\PS)$. Then we have
-%\begin{align*}
-%\rd^p\ap=(-1)^n(\Lambda^kK)\rd\ap=(-1)^{2n}\p_+ \ap +(-1)^{2n+1}\p_-\ap=(\p_+-\p_-)\ap,
-%\end{align*}
-%\end{proof}
+\subsubsection{The AKSZ construction}
 
-\subsection{Generalized para-geometry}
+\def\sA{\mathcal{A}}
+\def\d{{\rm d}}
+\def\dbar{\Bar{\partial}}
 
-\brian{motivate generalized geometry through courant algebroids}
+The starting point of the AKSZ construction is the mapping space
+\begin{equation}\label{eqn: map}
+\cE (M, X) = {\rm Map}\left((M, (\sA^*_M, \d_M)), X\right)
+\end{equation}
+where 
+\begin{itemize}
+\item $(M, (\sA^*_M, \d_M))$ is an {\em $n$-oriented} dg manifold with body a smooth oriented manifold $M$. \brian{recall $n$-orientation.}
+\item $X$ is a $(n-1)$-shifted symplectic NQ manifold. 
+\end{itemize}
 
-\brian{get rid of repetitions and references to dg / NQ manifolds.}
+The dg manifold $(M, \sA^*_M)$ is specified by a sheaf of graded commutative algebras $\sA^*_M$ over the de Rham complex $\Omega^*_M$.
+Here, $\d_M$ is a linear differential operator of degree $+1$, and together the data must satisfy the following conditions:
+\begin{itemize}
+\item[(1)] $\sA_M$ is concentrated in finitely many degrees;
+\item[(2)] For each $k$, $\sA^k_M$ is a locally free sheaf of $C^\infty_M$-modules of finite rank;
+\item[(3)] The differential $\d_M : \sA_M^* \to \sA_M^{*+1}$ is square zero differential operator making $(\sA_M , \d_M)$ into a sheaf of commutative dg algebras over the de Rham complex $\Omega^*_M$
+\end{itemize}
 
-In this paper, the term {\it generalized geometry} is used for the study of geometric \brian{geometrical is not a word} structures on the bundle $TM \oplus T^*M$ over some manifold $M$.
-We will typically abbreviate this bundle to $\TT$ whenever the base is understood or unimportant for the discussion.
+In particular, as a graded algebra $\sA^*_M$ is given by functions on a graded manifold $A_M$ with body $M$.
+In other words, $A_M$ is the total space of some graded vector bundle on $M$ (which is of finite rank and concentrated in finitely many degrees). 
+As a graded manifold, the mapping space $\cE(M,X)$ is given by the space of smooth maps between the underlying graded manifolds $A_M$ and $X$.
 
-For now, we record a relationship between generalized paracomplex structures and Courant algebroids.
+\begin{Ex}
+The most important example for us will be the source dg manifold $(M, \Omega^*_M)$, that is $\sA_M = \Omega^*_M$ equipped with de Rham differential. 
+We denote this dg manifold by $M_{\rm dR}$.
+Take the dg manifold $(M, \Omega^*_M)$ where $M$ is any smooth manifold. 
+If $M$ is closed and oriented there exists an integration map
+\[
+\int_M : \Omega^*_M \to \RR[n]
+\]
+of degree $-n$ thus equipping the dg manifold $M_{\rm dR}$ with an $n$-orientation. 
+\end{Ex}
 
-\subsubsection{Background on Courant algebroids}
+\begin{Ex}
+If $M$ has a para-complex structure, $(M, \mathbf{\Omega}^{0,\bullet})$ has the structure of a dg manifold. 
+Here $\mathbf{\Omega}^{0,\bullet}$ is the para-Dolbeault complex from Section \ref{sec: paracomplex} with differential given by the para $\pd$-operator. 
+We will denote this dg manifold by $M_{\pd}$. 
+To equip the dg manifold $(M, \mathbf{\Omega}^{0,\bullet})$ with an orientation, one must fix additional data. 
+One way to do this is to assume that the para-complex manifold $M$ is equipped with a para-holomorphic volume form $\Omega_X$. \brian{is this defined earlier?}
+\end{Ex}
 
-Recall, a Courant algebroid on a manifold $M$ is a vector bundle $E$, whose sheaf of sections we denote $\cE$, together with a nondegenerate symmetric bilinear pairing $\langle -, -\rangle : \cE \otimes \cE \to C^\infty(M)$ , an anchor map $a : E \to T M$, and a bilinear operator
+In this case, that $\dim(M) = n$ and $X = (X, \omega_X)$ is an $(n-1)$-shifted symplectic NQ manifold, then the AKSZ construction endows the mapping space $\cE(M, X)$ in (\ref{eqn: map}) with a $(-1)$-shifted symplectic symplectic form.
+The fundamental observation is that the diagram
+\[
+\xymatrix{
+& M \times \cE(M, X) \ar[dr]^-{{\rm ev}} \ar[dl]_-{\pi_M} & \\
+M & & X
+}
+\]
+induces a pairing
+\[
+\begin{array}{ccccc}
+ \Omega^p_M & \times & \Omega^q_N & \to & \Omega^{p+q-n}_{\cE(M, X)} \\
+\displaystyle \alpha & \times & \beta & \mapsto & \displaystyle \int_M \pi_M^* \alpha \wedge {\rm ev}^* \beta 
+ \end{array}
+ \]
+Applied to the element $1 \times \omega_X \in \Omega^0_M \times \Omega^{\brian{??}}_X$ we obtain a $(-1)$-shifted symplectic form that we denote $\int_M \omega_X$.
+
+\brian{Hamiltonians and action functional}
+
+\subsubsection{The AKSZ theory associated to a Courant algebroid}
+
+From here on, to any Courant algebroid $E$ we associate the NQ manifold $X_E$ which carries a $2$-shifted symplectic structure. 
+In the case that the Courant algebroid is exact, call the associated $2$-shifted symplectic space $X_H$, where $H$ labels the Severa class.
+
+We first review some basic examples of AKSZ theories associated to Courant algebroids. 
+The simplest type of Courant algebroid is one over a point, see Example \ref{Ex: point}. 
+The resulting AKSZ theory is a familiar one.
+
+\begin{Ex}\label{ex: cs}
+Any Lie algebra $\fg$ together with a non-degenerate invariant pairing defines a $2$-shifted symplectic structure on the graded manifold $\fg[1]$ living over a point. 
+The dg algebra of functions is the Chevalley-Eilenberg cochain complex computing Lie algebra cohomology $C^*(\fg)$. 
+All such $2$-symplectic NQ manifolds over a point are of this form. 
+%The resulting AKSZ theory is Chern-Simons theory. 
+The resulting AKSZ theory on a $3$-manifold $M$ (whose target base manifold is a point) is equivalent to Chern-Simons theory on $M$. 
+\end{Ex}
+
+\begin{Ex} \label{ex: exact CA}
+The action functional is
+\[
+S = \int_M p_i \d x^i + \frac{1}{2} g_{ab} e^a \d e^b - a_a^i(x) p_i e^a + \frac{1}{6} c(x)_{abc} e^{a} e^b e^c .
+\]
+\end{Ex}
+\subsubsection{Dirac structures and boundary conditions}
+
+The AKSZ formalism is a construction which produces a $(-1)$-shifted symplectic space from the data of a closed manifold and a target shifted symplectic manifold. 
+There is a generalization of this construction which produces $(-1)$-shifted symplectic spaces on manifolds with boundary.
+
+Suppose $M$ is a manifold with boundary, and let $\cE(M)$ denote the space of fields of a classical theory on $M$. 
+For us, $\cE(M)$ will be a mapping space of the form ${\rm Map}(M, X)$ where $X$ is shifted symplectic. 
+Let $\cE(\partial M)$ denote the restriction of the fields to the boundary of $M$. 
+For the mapping space example, this is simply the space of maps ${\rm Map}(\partial M, X)$.
+
+In general, when $M$ is not closed, the pairing defined by the AKSZ construction will not endow $\cE(M)$ will with $(-1)$-shifted symplectic structure. 
+However, the space $\cE(\partial M)$ does carry a natural ordinary ($0$-shifted) symplectic structure from the restriction of the pairing defined on $\cE(M)$. 
+Morever, the natural restriction map $\cE(M) \to \cE(\partial M)$ is a Lagrangian morphism in the sense of \cite{PTVV}.
+
+\def\cL{\mathcal{L}}
+
+A boundary condition is the choice of an additional Lagrangian subspace $\cL$ of $\cE(\partial M)$.
+The intersection $\cL \times_{\cE(M)} \cE(\partial M)$ of the two Lagrangians $\cL$ and $\cE(\partial M)$
+
+For an algebraic proof of the fact that the Lagrangian intersection \brian{finish} \cite{Calaque}
+
+\begin{Ex}
+Suppose $(X, \pi)$ is a Poisson manifold. 
+Then consider the graph of $\pi$ as a Lagrangian subbundle of $\TT$:
+\[
+{\rm Graph}(\pi) = \{(\pi \vee \alpha , \alpha) \; | \; \alpha \in T^* \} \subset \TT .
+\]
+By the Jacobi identity, this subbundle is integrable and so determines a Dirac structure. 
+If we place the 3D AKSZ theory with target the Courant algebroid $\TT$ on $M^3$ with $\partial M = \Sigma$, the boundary condition determined by this Dirac structure is equivalent to the Poisson $\sigma$-model.
+\brian{reference}
+\end{Ex}
+
+\subsection{Two dimensional TFT from GpC structures}
+
+\brian{Recall that a generalized (para-)complex structure $\JJ$ defines a Dirac structure in $\TT$, and hence a Lagrangian inside of the $2$-shifted symplectic space $\XX_H$.  
+%More generally, if $\JJ$ is a generalized complex structure in an arbitrary Courant algebroid $E$, then we obtain a $2$-shifted Lagrangian inside of the $2$-shifted symplectic space $\XX_E$. 
+This Lagrangian then defines a boundary condition for the three-dimensional AKSZ theory. }
+
+\subsubsection*{Trivial GpC structure}
+
+\subsubsection*{(Real) Poisson $\sigma$-model}
+
+\subsubsection*{Para-complex $A/B$-models}
+
+We have seen that symplectic structures are a special case of a generalized para-complex structure. 
+If $(X, \omega)$ is a symplectic the resulting 2D AKSZ theory is equivalent to the ordinary $A$-model on $X$.
+
+Another special case of a generalized para-complex structure is para-complex structure.
+
+\begin{Def}
+The {\bf para-$B$-model} with source a closed Riemann surface $\Sigma$ and target a para-complex manifold $X$ is the AKSZ theory with source the de Rham space $\Sigma_{\rm dR}$ and target the $1$-shifted symplectic space $T^*[1] X_{\pd}$:
+\[
+{\rm Map}\left(\Sigma_{dR}, T^*[1]  X_{\pd}\right) .
+\]
+\end{Def}
+
+\brian{Discuss Si's work on perturbative quantization}
+
+\hrulefill
+
+\brian{***para Kahler example, **example where the paracomplex structures commute but are not equal (this is where people see ``twisted chiral"), para version of T-duality, **Poisson $\sigma$-model, going back and forth between generalized (para) complex.
+}
+
+ \brian{discuss anomalies}
+
+\subsection{Para holomorphic variants}
+
+\brian{My plan is to just turn this into an extended remark}
+
+So far, in each of the $\sigma$-models we have discussed in the AKSZ formalism, the fields have depended only topologically on the source Riemann surface. 
+There are closely related $\sigma$-models which depending {\em para-holomorphically} on the source Riemann surface that we briefly discuss.
+
+\end{document}
+
+\section{The AKSZ formalism and 3d TFT}
+\def\fg{\mathfrak{g}}
+In this section we will show how to associate $2D$ topological theories to a generalized (para-)complex structure and relate them to the topological twists of $2D$ $(2,2)$ (para-)SUSY sigma models described in Section \ref{sec:toptwist} and in \cite{Kapustin:2004gv}.
+The key to our construction is to realize the data of a G(p)C structure in terms of its eigenbundles, which are Dirac structures $L$ in the Courant algebroid $\TT$. 
+Via the AKSZ construction \cite{AKSZ}, this correspondence translates into the statement that the Dirac structure $L$ defines a topological boundary theory of a $3D$ topological theory defined by the Courant algebroid $\TT$ \cite{Roytenberg:2002nu}.
+
+Throughout, we will use symplectic $NQ$ manifold as our model for shifted symplectic geometry. 
+We will recall the general setup of associating a $3D$ topological field theory to the data of a Courant algebroid. 
+For a reference, see \cite{Roytenberg:2002nu,??}.
+
+\subsection{Courant algebroids, $3D$ TFTs, and boundary conditions}
+From the point of view of topological field theory, Courant algebroids are important because they provide geometric examples of $2$-shifted symplectic spaces. 
+Via the AKSZ construction, $2$-shifted symplectic spaces are the natural home for $3$-dimensional topological field theories in the BV formalism. 
+\brian{give citations here.}
+
+In \cite{Roytenberg:2002nu}, it is shown how to associate a $2$-shifted symplectic NQ manifold from the data of a Courant algebroid.
+
+\begin{theorem}[\cite{Roytenberg:2002nu}]
+There is an equivalence between isomorphism classes of $2$-shifted symplectic NQ manifolds with body $M$ and isomorphism classes of Courant algebroids on $M$.
+\end{theorem}
+
+We briefly recall this construction.
+
+Recall, the data of a Courant algebroid on a manifold $M$ is a vector bundle $E$, whose sheaf of sections we denote $\cE$, together with a nondegenerate symmetric bilinear pairing $\langle -, -\rangle : \cE \otimes \cE \to C^\infty(M)$ , an anchor map $a : E \to T M$, and a bilinear operator
 \[
@@
 A Courant algebroid is called {\em exact} if this sequence of bundles is exact.
-
-The simplest type of Courant algebroid is one over a point.
-
-\begin{Ex}\label{ex: cs}
-Any Lie algebra $\fg$ together with a non-degenerate invariant pairing defines a $2$-shifted symplectic structure on the graded manifold $\fg[1]$ living over a point. 
-The dg algebra of functions is the Chevalley-Eilenberg cochain complex computing Lie algebra cohomology $C^*(\fg)$. 
-All such $2$-symplectic NQ manifolds over a point are of this form. 
-%The resulting AKSZ theory is Chern-Simons theory. 
-\end{Ex}
-
-\paragraph{The $2$-shifted symplectic space of an exact Courant Algebroid}
-
-We recall the description of the $2$-shifted symplectic NQ manifold $X_E$ associated to an exact Courant algebroid $E$.
-Of course, as a vector bundle $E = \TT$, and hence as a graded manifold $X_E$ is of the form $T^*[2] T[1] M$.
-Concretely, the coordinates on this manifold are given by $(x^i,v^a,p_i,\mu_a)_{i,a=1\cdots n}$, where $x^i$ are the usual coordinates on $M$ with degree $0$, $v^a$ are the corresponding ``velocities'', i.e.
-the fibre coordinates on $T[1]M$ with a degree $1$, and $p_i,\mu_a$ are the momenta corresponding to $x^i,v^a$ with degrees $2,1$, respectively.
-The canonical symplectic form
-\begin{align*}
-\Omega= dx^idp_i+dv^ad\mu_a,
-\end{align*}
-is then of degree $2$.
-$T^*[2]T[1]M$ is the minimal symplectic realization of the shifted bundle $(\TT)[1]M$, which is recovered by setting $p_i=0$.
-The symmetric part of $\Omega$ represents the pairing $\lara$ on $(\TT)M$; this is because we can identify $d\mu_a\leftrightarrow \p_i$ and $dv^a\leftrightarrow dx^i$
-
-\brian{Severa classification}
-
-\begin{theorem}\label{thm: severa}
-The set of isomorphism classes of exact Courant algebroids is a torsor for $H^3(X)$. 
-\end{theorem}
-
-\paragraph{The Poisson Courant algebroid}
-
-\brian{Both real and holomorphic versions}
-
-\subsubsection{The exact Courant algebroid structure}
-
-The bundle $\TT$ has a natural Courant algebroid structure given by the symmetric pairing
-\begin{align*}
-\langle X+\ap,Y+\bt\rangle=\ap(Y)+\bt(Y),
-\end{align*}
-the Dorfman bracket,
-\begin{align}\label{eq:dorfman}
-[ X+\ap,Y+\bt]=[X,Y]+\Lie_X\bt-\imath_Y\rd \ap, 
-\end{align}
-and the anchor $\pi:X+\ap\mapsto X$.
-In the above, $X+\ap$ denotes a section of $\TT$ with the splitting to tangent and cotangent parts given explicitly.
-The Dorfman bracket can be thought of as an extension of the Lie bracket from $T$ to $\TT$ and therefore we opt to use the same notation for both brackets; the expression $[X,Y]$ is always the Lie bracket of vector fields whether we think of $\brac$ as the Lie bracket or the Dorfman bracket and no confusion is therefore possible.
-
-The Courant algebroid on $\TT$ is exact
-In fact, all possible Courant algebroid structures on $\TT$ are parametrized by a closed three-form $H\in \Omega^3_{cl}$, which enters the definition of the bracket \eqref{eq:dorfman}, changing it to a {\it twisted} Dorfman bracket
-\begin{align*}
-[ X+\ap,Y+\bt]_H=[X,Y]+\Lie_X\bt-\imath_Y\rd \ap+\imath_Y\imath_X H.
-\end{align*}
-Moreover, any isotropic splitting of \eqref{eq:exact_seq} $s:T\rightarrow \TT$ is given by a two-form $b$, such that $X\overset{s}{\mapsto}X+b(X)$.
-This is equivalent to an action of a $b$-field transformation on $\TT$\footnote{Here we are using the term $b$-field transformation more liberally as it is customary to use the term only in the cases when $\rd b=0$ so that $e^b$ is a symmetry of $\brac$.}
-\begin{align*}
-e^b=
-\begin{pmatrix}
-\id & 0 \\
-b & \id
-\end{pmatrix}
-\in \End(\TT),
-\end{align*}
-which consequently changes the bracket as
-\begin{align*}
-[ e^b(X+\ap),e^b(Y+\bt)]_H=e^b([ X+\ap,Y+\bt]_{H+\rd b}),
-\end{align*}
-which implies that when $H$ is trivial in cohomology, then a choice of a $b$-field transformation such that $\rd b=-H$ brings the twisted bracket $\brac_H$ into the standard form \eqref{eq:dorfman}.
-When $H$ is cohomologically non-trivial this can be done at least locally.
-This also means that any choice of splitting with a non-trivial $b$-field can be absorbed in the Courant algebroid bracket in terms of the {\it flux}\footnote{Flux is a term used mainly in physics, in this context simply meaning the ``tensorial contribution to the bracket''.} $\rd b$.
-
-\paragraph{Dirac Structures}
-An important object in Dirac geometry are (almost) dirac structures, which are subbundles $L\subset \TT$ with special properties.
-\begin{Def}
-An {\bf almost Dirac structure} $L$ is a maximally isotropic subbundle of $\TT$, i.e.
-$\la u,v\ra=0$ for any $u,v \in \se(L)$ and $\text{rank}(L)=\text{rank}(T)$.
-When $L$ is involutive under the Dorfman bracket, i.e.
-it satisfies $[L,L]\subset L$, we call $L$ simply a {\bf Dirac structure}.
-\end{Def}
-An important fact we will repeatedly use is the following:
-
-\begin{proposition}[\cite{courant1990dirac}]\label{prop:dirac_Liealg}
-Let $L$ be a Dirac structure in the Courant algebroid $\TT$ with a flux $H$.
-Then the restriction of the Dorfman bracket to $L$, $\brac\mid_L$ is skew and gives $L$ a structure of a Lie algebroid compatible with the anchor $\pi\mid_L$, a restriction of the projection $\pi:\TT\rightarrow T$ to $L$.
-\end{proposition}
-
-We remark here that all the results in this paper remain valid for any exact courant algebroid $E$ (i.e.
-$E$ fits in the sequence \eqref{eq:exact_seq}), which can be always identified with $\TT$ by the choice of splitting equivalent to a choice of a representative $H\in\Omega^3_{cl}$.
-This also amounts to setting $b=0$ in all formulas since the $b$-field appears as a difference of two splittings.
-
-We now recall the notion of a generalized para-complex \cite{wade2004dirac,Zabzine:2006uz,Hu:2019zro} and a generalized para-K\"ahler \cite{Hu:2019zro} structure.
-We follow the discussion presented in \cite{Hu:2019zro}.
-
-\begin{Def}
-A \textbf{(twisted) generalized para-complex} (GpC) structure $\KK$ is an endomorphism of $\TT$, such that $\KK^2=\id$ and $\la\KK,\KK\ra=-\lara$, whose generalized Nijenhuis tensor vanishes:
-\begin{align}\label{eq:gen_nijenhuis}
-\mathcal{N}_\KK(u,v)=[\KK u,\KK v]_H+\KK^2[ u,v]_H-\KK([\KK u,v]_H+[ u,\KK v]_H)=0.
-\end{align}
-\end{Def}
-It is easy to check that the condition \eqref{eq:gen_nijenhuis} is equivalent to the $\pm 1$ eigenbundles of $\KK$ to be involutive under the twisted Dorfman bracket.
-Since in this paper the flux $H$ will be generically non-zero but all results hold for the special case $H=0$ as well, we will drop the word ``twisted" from our definitions.
-
-Generalized para-complex structures can be understood as the data one needs to specify a splitting of $\TT$ to a pair of integrable Dirac structures:
-
-\begin{theorem*}[\cite{wade2004dirac}]\label{thm:pairofdirac}
-There is a one-to-one correspondence between generalized para-complex structures on $M$ and pairs of transversal Dirac subbundles of $\TT$.
-\end{theorem*}
-
-Combining this result with the well-known result of \cite{Liu:1995lsa} which states that any pair of transversal Dirac structures $(L,\Lt)$ forms a Lie bialgebroid $(L,L^*\simeq \Lt)$, one can immediately infer the following
-
-\begin{corollary}
-Generalized para-complex structures on $\TT$ are in one-to-one correspondence with Lie bialgebroid pairs $(L,L^*)$ such that $L\oplus L^*=\TT$. 
-\end{corollary}
-
-\begin{Ex}[The trivial structure and its deformations]\label{ex:GpC_trivial}
-Any manifold supports the following GpC structure
-\begin{align*}
-\KK_0=
-\begin{pmatrix}
-\id & 0 \\
-0 & -\id
-\end{pmatrix},
-\end{align*}
-that has eigenbundles $T$ and $T^*$ and is always integrable. The following two GpC structures can be seen as deformations of $\KK_0$ by either a two-form $b$ or a bi-vector $\beta$:
-\begin{align*}
-\KK_b=
-\begin{pmatrix}
-\id & 0 \\
-2b & -\id
-\end{pmatrix},\quad
-\KK_\beta=
-\begin{pmatrix}
-\id & 2\beta \\
-0 & -\id
-\end{pmatrix}.
-\end{align*}
-$\KK_b$ is integrable iff $\rd b =-H$, and its eigenbundles are $\Lb_b=\text{graph}(b)=\{X+b(X)\mid X \in \XX\}$ and $\widetilde{\Lb}=T^*$.
-Similarly, $\KK_\beta$ is integrable iff $\beta$ is a Poisson structure, (see \cite[Lemma~2.13]{Hu:2019zro}) and its eigenbundles are $\Lb=T$ and $\widetilde{\Lb}=\text{graph}(-\beta)=\{\ap-\beta(\ap)\}\mid \ap \in \Omega\}$.
-\end{Ex}
-
-\begin{Ex}[Para-complex structures]
-A para-complex structure $K\in \Endo(T)$, defines the diagonal generalized para-complex structure:
-\begin{align*}
-\KK_K=
-\begin{pmatrix}
-K & 0 \\
-0 & -K^*
-\end{pmatrix}.
-\end{align*}
-The corresponding Dirac structures are given by $\Lb=T^{(1,0)}\oplus T^{*(0,1)}$ and $\widetilde{\Lb}=T^{(0,1)}\oplus T^{*(1,0)}$, where the bigrading is with respect to $K$.
-The integrability of $\KK_K$ is equivalent to Frobenius integrability of $K$ , i.e.
-vanishing of the Nijenhuis tensor of $K$.
-%
-%The structure $\KK_P$ can be generalized to the following
-%\begin{align*}
-%\KK=
-%\begin{pmatrix}
-%P & \Pi \\
-%\Omega & -P^*
-%\end{pmatrix},
-%\end{align*}
-%where we can read off from the constraints in \eqref{eq:GpC_generalform} that $P^2=\id$ implies that $\Pi\Omega=0$ and both $\Pi$ and $\Omega$ have to be of type $(2,0)+(0,2)$ with respect to the grading given by $P$.
-
-\end{Ex}
-
-\begin{Ex}[Symplectic structures]\label{ex:GpC_sympl}
-A symplectic form $\omega$ defines the anti-diagonal GpC structure
-\begin{align*}
-\KK_\omega=
-\begin{pmatrix}
-0 & \omega^{-1} \\
-\omega & 0
-\end{pmatrix}.
-\end{align*}
-The $\pm 1$ eigenbundles are given by $\text{graph}(\pm\omega)=\{X\pm\omega(X)\mid X\in \XX\}$, and the integrability of $\KK_\omega$ is equivalent to $\rd\omega=0$.
-\end{Ex}
-
-\brian{Can we import some of the other examples here?
-Maybe some explicit ones like the toric fibrations you mentioned.}
-
-\paragraph{Comparision with generalized complex structures}
-Example \ref{ex:GpC_sympl} shows that a symplectic manifold $(M,\omega)$ is a GpC manifold and it is well-known \cite{Gualtieri:2003dx} that $(M,\omega)$ is also generalized complex (GC).
-However, while almost GC structures exist only on almost complex manifolds \cite{Gualtieri:2003dx}, Example \ref{ex:GpC_trivial} demonstrates that GpC structures exist on any Poisson manifold and in particular on any smooth manifold (with trivial Poisson structure).
-Another feature of GpC geometry that is not present in GC geometry is that the GpC structures can be half-integrable (similarly to ordinary para-complex structures): see the cases of $\KK_b$ and $\KK_\beta$ from Example \ref{ex:GpC_trivial} which are always at least half integrable and are fully integrable iff $b$ is closed and $\beta$ is Poisson, respectively.
-On the other hand, $\KK_\omega$ in Example \ref{ex:GpC_sympl} can only be half-integrable when the $H$-flux is non-zero.
-
-\subsection{Generalized para-K\"ahler geometry}
-\brian{add buffer}
-
-\begin{Def}
-A \textbf{generalized para-K\"ahler structure} (GpK) is a commuting pair $(\KK_+,\KK_-)$ of GpC structures, such that their product $\GG=\KK_+\KK_-$ defines a split-signature metric $G$ on $\TT$ via
-\begin{align*}
-G(\cdot,\cdot)\coloneqq \la \GG\cdot,\cdot\ra.
-\end{align*}
-\end{Def}
-
-Because $\KK_\pm$ are GpC structures, they induce the splitting $\TT= \Lb_\pm\oplus\widetilde{\Lb}_\pm$.
-Moreover, because they commute, each of $\Lb_+$ and $\widetilde{\Lb}_+$ further splits to eigenbundles of $\KK_-$, so that one arrives at the decomposition of $\TT$ into four bundles:
-\begin{align}\label{GpK_bundles}
-\TT=\ell_+\oplus\ell_-\oplus \ellt_+\oplus \ellt_-,
-\end{align}
-such that the eigenbundles of $\KK_+$ are $\Lb_+=\ell_+\oplus\ell_-$ and $\tl{\Lb}_+=\ellt_+\oplus \ellt_-$, the eigenbundles of $\KK_-$ are $\Lb_-=\ell_+\oplus\ellt_-$ and $\tl{\Lb}_-=\ell_-\oplus \ellt_+$ and the eigenbundles of the generalized metric are $C_\pm=\ell_\pm\oplus\ellt_\pm$.
-All $\ell_\pm$ and $\ellt_\pm$ are isotropic and integrable under the Dorfman bracket \cite{Hu:2019zro} and bundles with opposite chirality are orthogonal.
-
-Similarly to generalized K\"ahler structures, the GpK structures can be equivalently given in terms of a pair of para-Hermitian structures satisfying a particular integrability condition:
-\begin{theorem}[\cite{Hu:2019zro}]
-The data of a GpK structure is equivalent to a pair of para-Hermitian structures $(\eta,K_+,K_-)$, such that $\KK_\pm$ are given by
-\begin{align}\label{eq:GpK_genform}
-\KK_{\pm}=\frac{1}{2}
-\begin{pmatrix}
-\id & 0 \\
-b & \id
-\end{pmatrix}
-\begin{pmatrix}
-K_+\pm K_- & \omega^{-1}_+\mp \omega^{-1}_- \\
-\omega_+\mp \omega_- & -(K_+^*\pm K_-^*)
-\end{pmatrix}
-\begin{pmatrix}
-\id & 0 \\
--b & \id
-\end{pmatrix},
-\end{align}
-for some $2$-form $b$. The integrability of $\KK_\pm$ then translates into $K_\pm$ being integrable and satisfying
-\begin{align*}
-\n^\pm K_\pm=0,
-\end{align*}
-where the connections $\n^\pm$ are defined by the Levi-Civita connection $\lc$ of $\eta$ and the $H$-flux:
-\begin{align*}
-\eta(\n^\pm_XY,Z)=\eta(\lc_XY,Z)\pm\frac{1}{2}(H+\rd b).
-\end{align*}
-\end{theorem}
-
-The additional integrability condition on $K_\pm$, $\n^\pm K_\pm$, can be equivalently expressed using the fundamental forms associated to $K_\pm$, $\omega_\pm=\eta K_\pm$, and a para-complex version of the $\rd^c$-operator, which we call $\rd^p$:
-\begin{align*}
-\n^\pm K_\pm=0 \Longleftrightarrow \rd^p_\pm\omega_\pm=\pm (H+\rd b).
-\end{align*}
-$\rd^p_\pm$ here denote the $\rd^p$ operators associated to $K_\pm$, $\rd^p_\pm\coloneqq K_\pm^*\circ \rd\circ K_\pm^*$.
-We will call the geometry given by the data $(\eta, K_\pm, H+\rd b)$ above a {\bf bi-para-Hermitian} geometry.
-
-\subsubsection{Isomorphism between $\TT$ and $T\oplus T$}\label{sec:isomorphism}
-In both the GK and GpK cases, the product of the pair of G(p)C structures defines a generalized (indefinite) metric $\GG$, which means that
-\begin{align*}
-G(\cdot,\cdot)\coloneqq \la \GG\cdot,\cdot\ra,
-\end{align*}
-defines a genuine (indefinite) metric on the bundle $\TT$.
-It can be shown (see eg.
-\cite{Gualtieri:2003dx,Hu:2019zro}) that such metric can be always locally expressed in terms of a two-form $b$ and a metric $g$
-\begin{align*}
-\GG=\GG(g,b)=\begin{pmatrix}
-\id & 0 \\
-b & \id
-\end{pmatrix}
-\begin{pmatrix}
-0 & g^{-1} \\
-g & 0
-\end{pmatrix}
-\begin{pmatrix}
-\id & 0 \\
--b & \id
-\end{pmatrix},
-\end{align*}
-and the signature of $g$ then determines the signature of $\GG(g,b)$.
-Therefore, a generalized metric determines a splitting of $\TT\simeq e^b(T)\oplus T^*$ in which the eigenbundles $C_\pm$ of $\GG$ are $C_\pm=graph(\pm g)$ and the flux of this splitting is given by the closed three-form $H\overset{loc.}{=}\rd b$.
-In the usual splitting $\TT$, we then have $C_\pm=graph(b\pm g)$.
-
-\begin{remark}
-\brian{maybe this should go later?}
-The most general $2D$ $(1,1)$ sigma model on a pseudo-Riemannian target $(M,g)$ is locally given by the action functional
-\begin{align}\label{rem:sigmamodel}
-S_{(1,1)}(\Phi)&=\int_{\hat{\Sigma}}[g(\Phi)+b(\Phi)]_{ij}D_+\Phi^iD_-\Phi^j,
-\end{align}
-where $\rd b=H$ is a global closed three-form. Therefore, the data of a generalized metric $\GG$ is equivalent to a specification of the sigma model  \eqref{rem:sigmamodel}.
-\end{remark}
-
-An important property of the generalized metric $\GG$ is that its  eigenbundles $C_\pm$ are isomorphic to the tangent bundle $T$ via the projection:
-\begin{align}\label{pi_iso}
-\begin{aligned}
-\pi_\pm:C_\pm &\simeq T,\\
-X+\ap &\overset{\pi_\pm}{\longmapsto} X,\\
-X+(b\pm g)X &\overset{\pi^{-1}_\pm}{\longmapsfrom} X,
-\end{aligned}
-\end{align}
-where $g$ and $b$ are the defining data of $\GG$. Therefore, since $\TT=C\oplus C_-$, we also have $\TT\simeq T\oplus T$:
-\begin{align}
-\begin{aligned}
-(X_+,X_-)\overset{\pi^{-1}_+\oplus \pi^{-1}_-}{\longmapsto}& X_++(b+g)X_++X_-+(b-g)X_-\\
-&=
-\begin{pmatrix}
- X_++X_- \\
- g(X_+-X_-)+b(X_++X_-)
-\end{pmatrix}.
-\end{aligned}\label{map_pi_pm}
-\end{align}
-In particular, one can check that $\pi_+\oplus \pi_-$ maps the eigenbundles of the generalized structures $\KK_\pm$ ($\JJ_\pm$) to eigenbundles of the corresponding pair of tangent bundle endomorphisms $\KK_\pm$ ($\JJ_\pm$).
-This is because of the following relationship \cite{Hu:2019zro},
-\begin{align*}
-K_+=\pi_+\KK_\pm\pi_+^{-1},\quad K_-=\pm\pi_-\KK_\pm\pi_-^{-1},
-\end{align*}
-and analogously for $\JJ_\pm$ and $J_\pm$. From here, it is easy to see that the $+1$ eigenbundle of $\KK_+$ $\Lb_+$, for example, is given by
-\begin{align*}
-\Lb_+=\pi_+^{-1}(T^{(1,0)_+})\oplus\pi_-^{-1}(T^{(1,0)_-}),
-\end{align*}
-where $T^{(1,0)_\pm}$ denotes the $+1$ eigenbundle of $K_\pm$. Analogously, the $-1$ eigenbundle of $\KK_-$,
-$\widetilde{\Lb}_-$, is given by
-\begin{align*}
-\widetilde{\Lb}_-=\pi_+^{-1}(T^{(0,1)_+})\oplus\pi_-^{-1}(T^{(1,0)_-}),
-\end{align*}
-and so on.
-Therefore, one should think about the pair $K_\pm$ corresponding to the GpK structure as each of the $K_\pm$ acting on its own copy of $T$, which are then mapped via $\pi_\pm$ to $C_\pm$ in $\TT$.
-
-We will also notice that $\pi_\pm$ map the the pseudo-Riemannian structures $G$ and $g$ on each other:
-\begin{align}\label{pi:gG_relationship}
-g(X,Y)=\pm\frac{1}{2}\la \pi_\pm^{-1}X,\pi_\pm^{-1}Y\ra = \frac{1}{2}\la \GG \pi_\pm^{-1}X,\pi_\pm^{-1}Y\ra =\frac{1}{2}G(\pi_\pm^{-1}X,\pi_\pm^{-1}Y).
-\end{align}
-Another important property we will make use of is the fact that the connections $\n^\pm$ give rise via $\pi_\pm$ to a generalized connection $D$ on $\TT$ called the generalized Bismut connection \cite{Gualtieri:2007bq}:
-\begin{align}\label{genBismut_pi_nabla_pm}
-D_uv=\pi^{-1}_+\n^+_{\pi u}\pi_+ v_++\pi^{-1}_-\n^-_{\pi u}\pi_- v_-.
-\end{align}
-This connection preserves $\lara$ and $\GG$ and in the case when $\GG$ is a generalized metric corresponding to a GpK structure, $D$ also preserves all the eigenbundles in \eqref{GpK_bundles}.
-
-There is a tensorial quantity associated to any generalized connection called generalized torsion, which is defined as \cite{Gualtieri:2007bq}
-\begin{align}\label{gentorsion_def}
-T^D(u,v,w)=\la D_uv-D_vu-[u,v]_H,w\ra +\la D_wu,v\ra.
-\end{align}
-For the generalized Bismut connection, this torsion has only pure components in $\Lambda^3C_\pm$ and satisfies the following formula \cite[Prop.~2.29]{Hu:2019zro}:
-\begin{align}\label{gentorsion_H}
-T^D(\pi_\pm^{-1}X,\pi_\pm^{-1}Y,\pi_\pm^{-1}Z)=2H_b(X,Y,Z).
-\end{align}
-
-%\paragraph*{Relationship to Kapustin-Li}
-%On pg. 12 of Kapustin-Li paper they implicitly use the isomorphisms $\pi_\pm$ to map the sections $\chi \in \se(T^{(0,1)_+})$ and $\lambda \in \se(T^{(0,1)_-})$ to the $-i$ eigenbundle of $\JJ_+$ as 
-%\begin{align*}
-%\begin{pmatrix}
-%\chi+\lambda \\
-%g(\chi-\lambda)
-%\end{pmatrix},
-%\end{align*}
-%which is the same as \eqref{map_pi_pm} with $b=0$, which they implicitly absorb inside the $H$-flux.
-
-\section{Two-dimensional parasupersymmetry}  \label{sec: parasusy}
-
-In this section we introduce the parasupersymmetry algebra in two-dimensions. 
-\brian{add more}
-
-\subsection{A reminder on $(1,1)$ supersymmetry}
-
-The $2$-dimensional $(1,1)$ supertranslation algebra is the super Lie algebra
-\[
-\mathfrak{t}_{(1,1)} = \RR^{1,1} \oplus \Pi (S_+) \oplus \Pi(S_-)
-\]
-where $S_\pm \cong \RR$ are the semi-spin representations of ${\rm Spin}(1,1)$ labeled by helicities $\pm \frac{1}{2}$. 
-Note that there are natural ${\rm Spin}(1,1)$-equivariant maps
-\[
-\Gamma_{\pm} : {\rm Sym}^2(S_\pm) \to \RR^{1,1}
-\]
-which are non-degenerate and whose images hit the subalgebras spanned by $\partial_{\pm}$, respectively. 
-The only nonvanishing Lie brackets in $\mathfrak{t}_{(1,1)}$ are defined by
-\[
-[Q_+, Q_+'] = \Gamma_+(Q_+ \otimes Q_+') \;\; , \;\; [Q_-, Q_-'] = \Gamma_-(Q_- \otimes Q_-')
-\]  
-where $Q_\pm, Q_\pm'$ are generic elements in $S_\pm$.
-
-We will use the lightcone basis $\p_{\pm}$ for $\RR^{1,1}$ and we also fix a basis $Q_\pm^1$ for $S_{\pm}$ with a relative normalization so that
-\begin{align}\label{eq:(1,1)_susy}
-[Q^1_\pm,Q^1_\pm] = 2\p_\pm.
-\end{align}
-
-\subsubsection{The $(1,1)$ supersymmetric $\sigma$-model}
-
-Let $\Sigma^{2|2}$ be a super Riemann surface with two real odd directions. 
-The even part of this supermanifold is a Riemann surface (with coordinates $\sigma$, $\tau$).
-For instance, in the flat case we consider the superspace $\RR^{2|2} = \{(x^i , \theta_1^{\pm}) \; | \; i = 1,2\}$, where $\theta_1^{\pm}$ are odd variables.
-
-The most general $(1,1)$ supersymmetric sigma model into a target pseudo-Riemannian manifold $(M,g)$ is given by the action functional
-\begin{align}\label{eq:(1,1)action}
-S_{(1,1)}(\Phi)=\int_{\Sigma^{2|2}} [g(\Phi)+b(\Phi)]_{ij}D^1_+\Phi^iD^1_-\Phi^j,
-\end{align}
-where $\Phi=(\Phi^i)_{i=1\cdots n}$ are local representatives for the $(1,1)$ {superfields} which are maps $\Phi: \Sigma^{2|2} \rightarrow M$.
-In the action, $b$ denotes a local two-form potential for a closed three-form, $H=\rd b$, and $D_\pm$ are the superderivatives
-\begin{align}\label{eq:D1}
-D^1_\pm=\frac{\p}{\p \theta_1^\pm}-\theta_1^\pm \p_\pm,
-\end{align}
-where $\p_\pm=\frac{\p}{\p x_\pm}$ are derivatives along the lightcone coordinates on $\Sigma$, $x_\pm=\tau\pm\sigma$.
-
-In superworldsheet coordinates, the superfields decompose as
-\begin{align*}
-\Phi^i(\sigma,\tau,\theta_+,\theta_-)=\phi^i(\sigma,\tau)+\psi^i_+(\sigma,\tau)\theta^++\psi_-(\sigma,\tau)\theta^-+F^i(\sigma,\tau)\theta^+\theta^-.
-\end{align*}
-Here, $(\phi^i)$ are local representatives for a smooth map $\phi: \Sigma \rightarrow M$.
-
-The fact that this action carries $(1,1)$ supersymmetry means that the action \eqref{eq:(1,1)action} is invariant under transformations generated by the two {supercharges} $Q^1_\pm$, 
-\begin{align}\label{eq:Q1}
-Q^1_\pm=\frac{\p}{\p \theta_1^\pm}+\theta_1^\pm \p_\pm,
-\end{align}
-obeying the supercommutation relations of the $(1,1)$ supersymmetry algebra (\ref{eq:(1,1)_susy}).
-
-\subsection{$(2,2)$ para-supersymmetry}
-\david{Import paragraph on (2,2)}
-
-\brian{point to references who have also discussed versions of (2,2) para susy}
-
-\begin{Def}
-The {\bf (2,2) para-supersymmetry algebra} has the underlying supervector space
-\[
-\mathfrak{t}_{(2,2)} = \RR^{1,1} \oplus \Pi(S_+ \oplus S_+) \oplus \Pi(S_- \oplus S_-) .
-\]
-The Lie brackets are described as follows. 
-If we choose a basis $\{Q^1_{\pm}, Q^2_\pm\}$ for $S_\pm \oplus S_\pm$ then the nontrivial brackets read 
-\begin{equation}\label{(2,2)para}
-(2,2) \; {\rm para} \;\; : \;\; [Q_\pm^1, Q_\pm^1] = 2 \partial_{\pm} \;\; , \;\; [Q_{\pm}^2, Q_{\pm}^2] = -2 \partial_{\pm} .
-\end{equation}
-\end{Def}
-
-\begin{remark}
-Note that this differs from ordinary $(2,2)$ supersymmetry by a sign:
-\begin{equation}\label{(2,2)para}
-(2,2) \; {\rm ordinary} \;\; : \;\; [Q_\pm^1, Q_\pm^1] = 2 \partial_{\pm} \;\; , \;\; [Q_{\pm}^2, Q_{\pm}^2] =  2 \partial_{\pm} .
-\end{equation}
-\end{remark}
-
-More generally, suppose $W_\pm$ are vector spaces of dimension $k_\pm$, respectively.
-In addition, suppose $\eta_\pm$ are symmetric nondegenerate forms on $W_\pm$. 
-Then, we can define a super Lie algebra of the form
-\[
-\mathfrak{t}_{W} =  \RR^{1,1} \oplus \Pi(S_+ \otimes W_+) \oplus \Pi(S_- \otimes W_-)
-\]
-with brackets defined by
-\[
-[Q_\pm^{a}, Q_\pm^{b}] = 2 \eta^{ab}_\pm \partial_\pm .
-\] 
-The case of $\mathfrak{t}_{(2,2)}$, which will be of most interested to us, corresponds to taking $k_+ = k_- = 2$ and $\eta_\pm^{11} = 1$, $\eta^{22}_\pm = - 1$, $\eta^{12}_{\pm} = 0$.
-
-\brian{Can change basis to off diagonal and write in more conventional way.}
-
-\subsubsection{R-symmetry}
-\david{Move to mirror symmetry speculation section}
-
-We have seen above that the $(2,2)$ para-SUSY algebra $\mathfrak{t}_{(2,2)}$ can be diagonalised in terms of the charges\footnote{Note that for the usual $(2,2)$ SUSY one cannot diagonalize the algebra over $\RR$.}
-\begin{align}\label{eq:R-sym_charges}
-\begin{aligned}
-[Q_\pm^1,Q_\pm^1]&=2\p_\pm\\
-[Q_\pm^2,Q_\pm^2]&=-2\p_\pm.
-\end{aligned}
-\end{align}
-We make a change of basis by the formulas $Q_\pm=\frac{1}{\sqrt{2}}(Q^2_\pm+Q^1_\pm)$ and $\tl{Q}_\pm=\frac{1}{\sqrt{2}}(Q^2_\pm-Q^1_\pm)$. 
-Equations \eqref{eq:R-sym_charges} can be written collectively as
-\begin{align}\label{eq:R-sym_eta}
-[Q_\pm^a,Q_\pm^b]=2\eta^{ab}\p_\pm,
-\end{align}
-where $\eta^{ab}=\begin{pmatrix}
-1 & 0 \\
-0 & -1
-\end{pmatrix}$. From here it is easy to see that matrices $(M_\pm)^a_b$ that rotate the $\pm$-chirality charges among each other while preserving the commutation relations \eqref{eq:R-sym_eta},
-\begin{align*}
-[(M_\pm)^a_cQ_\pm^c,(M_\pm)^b_dQ_\pm^d]=2\eta^{ab}\p_\pm
-\end{align*}
-have to satisfy
-\begin{align*}
-(M_\pm)^a_c\eta^{cd}(M_\pm)^a_d=\eta^{ab},
-\end{align*}
-i.e. $M_\pm$ have to lie in $SO(1,1)$ for each subscript $\pm$ and the R-symmetry group is therefore $G_R=SO(1,1)_+\times SO(1,1)_-$.
-\david{this is only relevant for the (2,2) formalism, will se if we need this or not}
-The R-symmetry acts on the odd coordinates accordingly as
-\begin{align*}
-\begin{pmatrix}
-\theta^1_\pm \\
-\theta^2_\pm	
-\end{pmatrix}
-\mapsto
-\begin{pmatrix}
-\cosh(\alpha_\pm) & \sinh(\alpha_\pm) \\
-\sinh(\alpha_\pm) & \cosh(\alpha_\pm)
-\end{pmatrix}
-\begin{pmatrix}
-\theta^1_\pm \\
-\theta^2_\pm	
-\end{pmatrix}
-\end{align*}
-or, equivalently, $(\theta^\pm,\tth^\pm)\mapsto (e^{\alpha_\pm} \theta^\pm,e^{-\alpha_\pm}\tth^\pm)$.
-There are therefore two inequivalent embeddings of the Lorentz group $SO(1,1)$ into the R-symmetry group, we label them by $V$ and $A$:
-\begin{align*}
-R_V(\alpha)&:(\theta^\pm,\tth^\pm)\mapsto (e^\alpha \theta^\pm,e^{-\alpha}\tth^\pm)\\
-R_A(\alpha)&:(\theta^\pm,\tth^\pm)\mapsto (e^{\pm \alpha} \theta^\pm,e^{\mp \alpha}\tth^\pm),
-\end{align*}
-mapping the supercharges as
-\begin{align*}
-R_V(\alpha):& (Q_\pm,\tl{Q}_\pm)\mapsto (e^{-\alpha}Q_\pm,e^{\alpha}\tl{Q}_\pm)\\
-R_A(\alpha):& (Q_\pm,\tl{Q}_\pm)\mapsto (e^{\mp\alpha}Q_\pm,e^{\pm \alpha}\tl{Q}_\pm).
-\end{align*}
-The generators of these transformations are
-\begin{align*}
-F_{V/A}=\theta^+\frac{\p}{\p\theta^+}-\tth^+\frac{\p}{\p\tth^+}\pm \theta^-\frac{\p}{\p\theta^-}\mp\tth^-\frac{\p}{\p\tth^-}.
-\end{align*}
-
-Because $F_{V/A}$ has same commutators with other operators as $M$, the Lorentz generator, and additionally all $F_{V/A}$ and $M$ commute among themselves, we can define new "Lorentz" generators in one of the two following ways:
-\begin{align*}
-M_A=M+F_V,\quad M_B=M+F_A.
-\end{align*}
-
-\subsection{The $(2,2)$ parasupersymmetric $\sigma$-model}
-It has been known since \cite{Zumino:1979et} that the $(1,1)$ supersymmetric $\sigma$-model \eqref{eq:(1,1)action} admits $(2,2)$ supersymmetry when $(M,g)$ is a K\"{a}hler manifold.
-In general, $(2,2)$ supersymmetry in fact requires the target to be {\bf generalized K\"ahler} \cite{Gualtieri:2003dx}, which is equivalent to a data of a bi-Hermitian geometry discovered by \cite{Gates:1984nk}.
-For $(2,2)$ para-SUSY, the story is analogous.
-It was shown in \cite{HullTwistedSUSY} that in order to extend the $(1,1)$ SUSY of \ref{eq:(1,1)action} to $(2,2)$ para-SUSY, one needs a para-complex version of the biHermitian geometry.
-In \cite{Hu:2019zro} it was then shown that this can be equivalently described by {\bf generalized para-K\"ahler} geometry.
-
-\paragraph{Expanding the $(1,1)$ action}
-
-First, we further analyze the $(1,1)$ supersymmetric theory. 
-Recall the $(1,1)$ supersymmetric $\sigma$-model is described by the action
-\begin{align*}
-S_{(1,1)}(\Phi)&=\int_{\hat{\Sigma}}[g(\Phi)+b(\Phi)]_{ij}D_+\Phi^iD_-\Phi^j.
-\end{align*}
-In components, the superfield has the form
-\[
-\Phi^i =\phi^i+\theta^+\psi^i_++\theta^-\psi^i_-+\theta^+\theta^-F^i
-\]
-The super covariant derivatives $D_{\pm}$ applied to $\Phi^i$ read
-\[
-D_\pm\Phi^i =\psi^i_\pm\pm\theta^\mp F^i-\theta^\pm\p_\pm\phi^i\mp\theta^+\theta^-\p_\pm\psi^i_\mp .
-\]
-Further, we can expand the contributions from the metric and $b$-field as
-\begin{align*}
-[g(\Phi)+b(\Phi)]_{ij} = & [g(\phi)+b(\phi)]_{ij}+\p_k[g(\phi)+b(\phi)]_{ij}(\theta^+\psi_+^k+\theta^-\psi_-^k+\theta^+\theta^-F^k)\\
-& +\frac{1}{2}\p_k\p_l[g(\phi)+b(\phi)]_{ij}(\theta^+\psi_+^k+\theta^-\psi_-^k)(\theta^+\psi_+^l+\theta^-\psi_-^l).
-\end{align*}
-
-After performing the odd integration, the only terms that survive are the $\theta^+\theta^-$ coefficients:
-\begin{align*}
-\theta^+\theta^-&\left[(g+b)_{ij}(\psi_+^i\p_-\psi^j_++\psi^j_-\p_-\psi^i_-+F^iF^j+\p_+\phi^i\p_-\phi^j)\right. \\
-&+\p_k(g+b)_{ij}\left(F^k\psi^i_+\psi^j_-+\psi^k_+(-F^i\psi^j_--\psi^i_+\p_-\phi^j)+\psi^k_-(-\p_+\phi^i\psi^j_-+\psi_+^iF^j)\right)\\
-&\left. +\frac{1}{2}\p_k\p_l(g+b)_{ij}(-\psi_+^k\psi_-^l\psi_+^i\psi_-^j+\psi_-^k\psi_+^l\psi^i_+\psi^j_-) \right].
-\end{align*}
-
-The field $F$ is auxiliary (since it enters only algebraically: no derivations of $F$ appear in the action), and therefore can be integrated out.
-To obtain the equations of motion for $F$, we use the formula $\p_kg_{ij}=\Gamma_{ikj}+\Gamma_{jki}$ and collect the terms involving $F$:
-\begin{align*}
-g_{ij}F^iF^j+&(\Gamma_{ikj}+\Gamma_{jki})(F^k\psi^i_+\psi^j_--F^i\psi^k_+\psi^j_-+F^j\psi^k_-\psi_+^i)\\
-+&F^k\psi^i_+\psi^j_-(\p_kb_{ij}+\p_ib_{jk}+\p_jb_{ki}).
-\end{align*}
-Using $\Gamma_{ikj}=\Gamma_{kij}$ and $H_{ijk}=(\p_kb_{ij}+\p_ib_{jk}+\p_jb_{ki})$, we can rewrite this as
-\begin{align*}
-g_{ij}F^iF^j+2\Gamma_{ikj}F^j\psi^k_-\psi_+^i+F^k\psi^i_+\psi^j_-H_{ijk}=g_{ij}(F^iF^j+2F^j(\Gamma^-)_{lk}^i\psi_-^k\psi_+^l),
-\end{align*}
-where $\Gamma^-$ are the Christoffel symbols of the connection $\n^-=\lc-\frac{1}{2}g^{-1}H$. This yields the equation of motion for $F$,
-\begin{align} \label{F_EoM}
-\frac{\delta S_{(1,1)}}{\delta F^i}=0\quad \Longleftrightarrow\quad  F^i=-(\Gamma^-)^i_{jk}\psi^k_-\psi^j_+
-\end{align}
-
-%\paragraph{(2,2) SUSY}
-
-%We propose the following symmetry by the $(2,2)$ parasupersymmetry algebra (\ref{(2,2)para}) (setting $\theta^\pm_1\coloneqq \theta^\pm$ for simplicity), which read in superspace notation:
-%\begin{align*}
-%Q^1_\pm&=\frac{\p}{\p\theta^\pm}+\theta^\pm\p_\pm \\
-%Q^2_\pm\Phi^i&=(K_\pm)^i_j(\Phi)D_\pm\Phi^j \\
-%\end{align*}
-%where $D_\pm =\frac{\p}{\p\theta^\pm}-\theta^\pm\p_\pm$.
-
-\paragraph{Extended supersymmetry}
-
-The $\sigma$-model we have just described has manifest $(1,1)$ supersymmetry. 
-We now propose the a symmetry of the action $S_{(1,1)}$ by the extended $(2,2)$ parasupersymmetry algebra (\ref{(2,2)para}).
-In general, this extended symmetry exists only after we make some additional assumptions on the geometric data prescribing the action.
-
-Setting $\theta^\pm_1\coloneqq \theta^\pm$ for simplicity, we propose the following $(2,2)$ parasupersymmetry in $(1,1)$ superfield notation:
-\begin{align}
-\label{q1} Q^1_\pm&=\frac{\p}{\p\theta^\pm}+\theta^\pm\p_\pm \\
-\label{q2} Q^2_\pm\Phi^i&=(K_\pm)^i_j(\Phi)D_\pm\Phi^j
-\end{align}
-where $D_\pm =\frac{\p}{\p\theta^\pm}-\theta^\pm\p_\pm$. 
-\brian{We need to either recall what $K_{\pm}$ is geometrically, or state that it is a free parameter which we will interpret momentarily.}
-In other words, the infinitesimal action of the element $Q^1_{\pm} \in \mathfrak{t}_{(2,2)}$ is:
-\[
-\Phi^i \mapsto \Phi^i + \epsilon^{\pm}_1 \left( \frac{\p}{\p\theta^\pm}+\theta^\pm\p_\pm \right) \Phi^i
-\]
-where $\epsilon^{\pm}_1$ is an infinitesimal parameter. 
-Similarly, the infinitesimal action by the element $Q^2_{\pm} \in \mathfrak{t}_{(2,2)}$ is:
-\[
-\Phi \mapsto \Phi + \epsilon^{\pm}_2 (K_\pm)^i_j(\Phi)D_\pm\Phi^j 
-\]
-where $\epsilon^\pm_2$ is an infinitesimal parameter.
-
-\begin{lemma}
-Expanding out in the components of the $(1,1)$ superfield, the infinitesimal action by $Q^1_{+}$ and in Equation (\ref{q1}) reads:
-\[
-Q^1_{+} : (\phi^i, \psi^i_+, \psi^i_-, F^i) \mapsto (\phi^i, \psi^i_{\pm}, F^i) + \epsilon^+_1 (\psi^i_+, \partial_+ \phi, F^i, \partial_+ \psi^i_-) . 
-\]
-and by $Q^1_-$:
-\[
-Q^1_{-} : (\phi^i, \psi^i_+, \psi^i_-, F^i)  \mapsto (\phi^i, \psi^i_{\pm}, F^i) + \epsilon^-_1 (\psi^i_-, \partial^i_- \phi^i, - F^i, - \partial_- \psi^i_+)
-\]
-Similarly, the infinitesimal action by $Q^2_{+}$ in Equation (\ref{q2}) reads:
-\begin{equation}\label{q2plus}
-Q^2_{+} : (\phi^i, \psi^i_+, \psi^i_-, F^i) \mapsto ((K_+)^i_j \psi_+ ^j , - (K_+)^{i}_{j} \partial_+ \phi^j - \partial_k(K_+)^i_j \psi_+^k \psi_+^k, (K_+)^i_j F^j+\p_k(K_+)^i_j\psi^k_-\psi^j_+, \brian{F term})
-\end{equation}
-and for $Q^2_-$:
-\begin{equation}\label{q2minus}
-Q^2_{-} : (\phi^i, \psi^i_+, \psi^i_-, F^i) \mapsto ((K_-)^i_j \psi_- ^j , - (K_-)^{i}_{j} \partial_- \phi^j - \partial_k(K_-)^i_j \psi_-^k \psi_-^k, (K_-)^i_j F^j+\p_k(K_-)^i_j\psi^k_+\psi^j_-, \brian{F term})
-\end{equation}
-\end{lemma}
-
-%\begin{align}\label{Q12_action}
-%\begin{aligned}
-%[Q_\pm^1 ,\phi^i]&=\psi_\pm^i,& [Q_\pm^2 ,\phi^i] &=(K_\pm)^i_j\psi_\pm^j,\\
-%[Q_\pm^1 ,\psi^i_\pm] &=\p_\pm\phi^i,& [Q_\pm^2 ,\psi^i_\pm] &=-(K_\pm)^i_j\p_+\phi^j{\textcolor{red}{+}}\p_k(K_\pm)^i_j\psi_+^k\psi_+^j\\
-%[Q_\pm^1 ,\psi^i_\mp]&=\pm F^i,& [Q_\pm^2 ,\psi^i_\mp] &=(K_\pm)^i_jF^j+\p_k(K_\pm)^i_j\psi^k_\mp\psi^j_\pm.
-%\end{aligned}
-%\end{align}
-%
-%\textcolor{red}{There's a sign issue above, the $+$ needs to be $-$.}
-\begin{proof}
-Recall, in components the superfield is of the form
-\[
-\Phi^i =\phi^i+\theta^+\psi^i_++\theta^-\psi^i_-+\theta^+\theta^-F^i .
-\]
-The action of the $Q^1_\pm$ charges is straightforward and can be simply read off from the infinitesimal action. 
-%\begin{align*}
-%[Q^1_\pm,\Phi]=[Q_\pm^1,\phi^i]+[Q_\pm^1,\psi^i_\pm]\theta^\pm+[Q_\pm^1,\psi^i_\mp]\theta^\mp+[Q_\pm^1,F]\theta^\pm\theta^\mp.
-%\end{align*}
-%For instance $[Q_{\pm}^1, \phi^i] = \theta^{\pm} \partial_{\pm} \phi^i$, thus 
-To obtain the action by the charges $Q^2_\pm$ on the individual components we first need to expand $K_\pm(\Phi)$ in terms of the components of the superfield:
-\begin{align*}
-(K_\pm)^i_j(\Phi)=(K_\pm)^i_j(\phi)+\p_k(K_\pm)^i_j\theta^+\psi_+^k+\p_k(K_\pm)^i_j\theta^-\psi_-^k+\p_k(K_\pm)\theta^+\theta^-F^k,
-\end{align*}
-so that the infinitesimal action by $Q^2_\pm$ on $\Phi^i$ is:
-\begin{align}
-\Phi^i + \epsilon_2^\pm (K_\pm)^i_j(\Phi)(\psi^j_\pm\pm\theta^\mp F^j-\theta^\pm\p_\pm\phi^j\mp\theta^+\theta^-\p_\pm\psi^j_\mp) .
-\end{align}
-Reading off the various components this expression yields Equations (\ref{q2plus}) and (\ref{q2minus}).
-\end{proof}
-
-\paragraph{The $(2,2)$ formalism}
-\brian{
-There is the following superspace model for $(2,2)$ parasupersymmetry. 
-Consider the superspace $\RR^{1,1 | 4}$ 
-}
-\brian{maybe leave this as a remark that we are aware of this...but we don't need it.}
-
-\subsection{$(2,1)$ and $(2,0)$ parasupersymmetry}
-
-Many of the constructions above make sense when there is less total supersymmetry, and we briefly mention two important cases.
-
-The first concerns the $(2,1)$ parasupersymmetry algebra.
-This algebra $\mathfrak{t}_{(2,1)}$ consists of generators $\{Q^1_\pm, Q^2_+\}$ satisfying the same algebra as in (\ref{(2,2)para}). 
-Starting with the $(1,1)$ supersymmetric $\sigma$-model (\ref{eq:(1,1)action}), and labeling the odd coordinates by $\theta^\pm = \theta_1^\pm$, one can ask for an additional odd symmetry 
-\[
-Q_2^+ :  \Phi \mapsto \Phi + \epsilon_2^+ K_+(\Phi)^j_i D_+ \Phi^i
-\]
-which determines a symmetry by the $(2,1)$ parasupersymmetry algebra.
-
-\brian{SKT, Witten-Hull}
-
-\begin{proposition}
-The odd vector field $Q_2^+$ is a symmetry of the $(1,1)$ supersymmetric $\sigma$-model provided $(K_+)^{j}_i$ is a paracomplex structure satisfying \brian{What conditions here?}
-Thus, the $(1,1)$ supersymmetric $\sigma$-model has $(2,1)$ parasupersymmetry provided the target is \brian{same conditions}. 
-\end{proposition}
-
-The next symmetry algebra we wish to consider is the $(2,0)$ parasupersymmetry algebra $\mathfrak{t}_{(2,0)}$. 
-This algebra has the same even generators as the $(2,1)$ and $(2,2)$ algebras, and odd generators $\{Q^1_+, Q^2_+\}$ satisfying the relations
-\[
-[Q^1_+, Q^1_+] =  2 \partial_\pm \;\;\; , \;\;\; [Q^2_+, Q^2_+] = - 2 \partial_\pm
-\]
-
-\brian{The (1,0) action}
-
-We propose an extended symmetry of the $(1,0)$ $\sigma$-model by the following action by the odd vector field $Q_+^2$:
-\[
-Q^2_+ : \Phi \mapsto \Phi + \epsilon_2^+ K_+(\Phi)^j_i D_+ \Phi^i .
-\]
-
-\begin{proposition}
-The odd vector field $Q_2^+$ is a symmetry of the $(1,0)$ supersymmetric $\sigma$-model provided $(K_+)^{j}_i$ is a paracomplex structure. 
-Thus, the $(1,0)$ supersymmetric $\sigma$-model has $(2,0)$ parasupersymmetry provided the target is paracomplex. \brian{there is a version for a target vector bundle as well...}
-\end{proposition}
-
-\section{AKSZ and generailzed para-geometry}
-
-In this section we will show how to associate $2D$ topological theories to a generalized (para-)complex structure.
-Later on, in Section \ref{sec:toptwist}, we relate these theories to topological twists of $2D$ $(2,2)$ para-SUSY sigma models introduced in Section \ref{sec: parasusy}. 
-%and in \cite{Kapustin:2004gv}. 
-The key to our construction is to realize the data of a G(p)C structure in terms of its eigenbundles, which are Dirac structures $L$ in the Courant algebroid $\TT$. 
-Via the AKSZ construction \cite{AKSZ}, this correspondence translates into the statement that the Dirac structure $L$ defines a topological boundary theory of a $3D$ topological theory defined by the Courant algebroid $\TT$ \cite{Roytenberg:2002nu}.
-
-Throughout, we will use symplectic $NQ$ manifold as our model for shifted symplectic geometry. 
-We will recall the general setup of associating a $3D$ topological field theory to the data of a Courant algebroid. 
-For a reference, see \cite{Roytenberg:2002nu,??}.
-Later we will use the idea of Lagrangian intersections \brian{Toen, ButsonYoo, Costello,...}.
-
-\subsection{Courant algebroids, $3D$ TFTs, and boundary conditions}
-From the point of view of topological field theory, Courant algebroids are important because they provide geometric examples of $2$-shifted symplectic spaces. 
-Via the AKSZ construction, $2$-shifted symplectic spaces are the natural home for $3$-dimensional topological field theories in the BV formalism. 
-\brian{give citations here.}
-
-In \cite{Roytenberg:2002nu}, it is shown how to associate a $2$-shifted symplectic NQ manifold from the data of a Courant algebroid.
-
-\begin{theorem}[\cite{Roytenberg:2002nu}]
-There is an equivalence between isomorphism classes of $2$-shifted symplectic NQ manifolds with body $M$ and isomorphism classes of Courant algebroids on $M$.
-\end{theorem}
-
-We briefly recount this construction.
 
@@
 
+The simplest type of Courant algebroid is one over a point.
+
+\begin{Ex}\label{ex: cs}
+Any Lie algebra $\fg$ together with a non-degenerate invariant pairing defines a $2$-shifted symplectic structure on the graded manifold $\fg[1]$ living over a point. 
+The dg algebra of functions is the Chevalley-Eilenberg cochain complex computing Lie algebra cohomology $C^*(\fg)$. 
+All such $2$-symplectic NQ manifolds over a point are of this form. 
+%The resulting AKSZ theory is Chern-Simons theory. 
+\end{Ex}
+
+\subsubsection*{The $2$-shifted symplectic space of an exact Courant Algebroid}
+
+We recall the description of the $2$-shifted symplectic NQ manifold $X_E$ associated to an exact Courant algebroid $E$.
+Of course, as a vector bundle $E = \TT$, and hence as a graded manifold $X_E$ is of the form $T^*[2] T[1] M$.
+Concretely, the coordinates on this manifold are given by $(x^i,v^a,p_i,\mu_a)_{i,a=1\cdots n}$, where $x^i$ are the usual coordinates on $M$ with degree $0$, $v^a$ are the corresponding ``velocities'', i.e.
+the fibre coordinates on $T[1]M$ with a degree $1$, and $p_i,\mu_a$ are the momenta corresponding to $x^i,v^a$ with degrees $2,1$, respectively.
+The canonical symplectic form
+\begin{align*}
+\Omega= dx^idp_i+dv^ad\mu_a,
+\end{align*}
+is then of degree $2$.
+$T^*[2]T[1]M$ is the minimal symplectic realization of the shifted bundle $(\TT)[1]M$, which is recovered by setting $p_i=0$.
+The symmetric part of $\Omega$ represents the pairing $\lara$ on $(\TT)M$; this is because we can identify $d\mu_a\leftrightarrow \p_i$ and $dv^a\leftrightarrow dx^i$
+
+\brian{Severa classification}
+
+\begin{theorem}\label{thm: severa}
+The set of isomorphism classes of exact Courant algebroids is a torsor for $H^3(X)$. 
+\end{theorem}
+
+\subsubsection*{The Poisson Courant algebroid}
+
+\brian{Both real and holomorphic versions}
+
 \subsubsection{The AKSZ theory associated to a Courant algebroid}
 
-To any Courant algebroid $E$, we associate an NQ manifold $X_E$ which carries a $2$-shifted symplectic structure. 
+To any Courant algebroid $E$, we can associate an NQ manifold $X_E$ which carries a $2$-shifted symplectic structure that we denote by $\omega_E$. 
 In the case that the Courant algebroid is exact, call the associated $2$-shifted symplectic space $X_H$, where $H$ labels the Severa class.
@@
 where $(M, (\sA^*_M, \d_M))$ is a dg manifold with body a smooth oriented manifold $M$. 
-That is, $\sA^*_M$ is a sheaf of graded commutative algebras over the de Rham complex $\Omega^*_M$ and $\d_M$ is a linear differential operator of degree $+1$ satisfying:
+That is, $\sA^*_M$ is a sheaf of graded commutative algebras over the de Rham complex $\Omega^*_M$ and $\d_M$ is a linear operator of degree $+1$ satisfying:
 \begin{itemize}
@@
 \begin{Ex}
-The most important example for us will be the source dg manifold $(M, \Omega^*_M)$, that is $\sA_M = \Omega^*_M$ equipped with de Rham differential. 
+The most important example for us will be the source dg manifold $(M, \Omega^*_M)$, that is $\sA_M = \Omega^*_M$ with de Rham differential. 
 We denote this dg manifold by $M_{\rm dR}$.
@@
 
-The AKSZ formalism is a construction which produces a $(-1)$-shifted symplectic space from the data of a closed manifold and a target shifted symplectic manifold. 
-There is a generalization of this construction which produces $(-1)$-shifted symplectic spaces on manifolds with boundary.
-
-Suppose $M$ is a manifold with boundary, and let $\cE(M)$ denote the space of fields of a classical theory on $M$. 
-For us, $\cE(M)$ will be a mapping space of the form ${\rm Map}(M, X)$ where $X$ is shifted symplectic. 
-Let $\cE(\partial M)$ denote the restriction of the fields to the boundary of $M$. 
-For the mapping space example, this is simply the space of maps ${\rm Map}(\partial M, X)$.
-
-In general, when $M$ is not closed, $\cE(M)$ will not carry a $(-1)$-shifted symplectic structure.
-However,
-
 \subsection{Two dimensional TFT from GpC structures}
-
+\label{sec:GpC_AKSZ}
 \brian{Recall that a generalized (para-)complex structure $\JJ$ defines a Dirac structure in $\TT$, and hence a Lagrangian inside of the $2$-shifted symplectic space $\XX_H$.  
@@
 There are closely related $\sigma$-models which depending {\em para-holomorphically} on the source Riemann surface that we briefly discuss.
-
-\section{Twisted parasupersymmetry}\label{sec:toptwist}
-
-In this section we will present how para-supersymmetry theories can be twisted, in exact analogy with twisting in ordinary supersymmetry.
-Applied to the $(2,2)$ parasupersymmetric theories that we have constructed in \S \ref{sec: parasusy}, we find that twisting yield topological field field theories. 
-In the next section, we will construct these topological theories geometrically using the AKSZ formalism.
-
-The procedure for twisting will again follow the analogy between generalized K\"{a}hler (GK) and generalized para-K\"{a}hler (GpK).
-geometries, and we will follow the approach presented in \cite{Kapustin:2004gv} for the GK case.
-
-\brian{geometry, change in gradings}
-\david{how does the embedding of $SO(1,1)$ into $G_R$ reflect on the definition of $\QQ$?}
-
-For the topological twist, we will use the following nilpotent supercharge
-\begin{align}
-\QQ=Q_L+Q_R,\quad Q_L=\frac{1}{2}(Q^1_++Q^2_+),\quad Q_R=\frac{1}{2}(Q^1_-+Q^2_-),
-\end{align}
-and we also introduce the usual notation 
-\begin{align*}
-\chi=\frac{1}{2}(\id+K_+)\psi_+=P_+\psi_+=\psi_+^{(1,0)_+},\quad\lambda=\frac{1}{2}(\id+K_-)\psi_-=P_-\psi_-=\psi_-^{(1,0)_-}.
-\end{align*}
-
-\begin{proposition}
-The action of $Q_{L/R}$ on the fields $\chi$, $\lambda$ and $\phi$ is given by
-\begin{align}\label{eq:Qcoh}
-\begin{aligned}
-[Q_L,\phi^i]&=\chi^i & [Q_R,\phi^i]&=\lambda^i\\
-[Q_L,\chi^i]&=0 & [Q_R,\lambda^i]&=0\\
-[Q_L,\lambda^i]&=-(\Gamma^-)^i_{jk}\chi^j\lambda^k & [Q_R,\chi^i]&=-(\Gamma^+)^i_{jk}\lambda^j\chi^k.
-\end{aligned}
-\end{align}
-\end{proposition}
-\begin{proof}
-The action of $Q_{L/R}$ on $\phi$ can be immediately read off \eqref{Q12_action}:
-\begin{align}
-[Q_L,\phi^i]=\frac{1}{2}[Q_+^1+Q^2_+,\phi^i]=\chi^i.
-\end{align}
-
-We now prove the formulas for the action of $Q_{L/R}$ on $\chi$, the action on $\lambda$ is entirely analogous. First, we expand
-\begin{align}\label{QL_chi}
-[Q_L,\chi^i]=[Q_L,(P_+)^i_j\psi_+^j]=[Q_L,(P_+)^i_j]\psi_+^j\textcolor{red}{+}(P_+)^i_j[Q_L,\psi_+^j].
-\end{align}
-\textcolor{red}{Or maybe here? I think this is the one}
-Because $K_+$ is a function of the bosonic coordinates, we also have $P_+=P_+(\phi)$ and so
-\begin{align}\label{QL_P}
-[Q_L,(P_+)^i_j]=\p_k(P_+)^i_j[Q_L,\phi^k]=\p_k(P_+)^i_j\chi^k.
-\end{align}
-Combining \eqref{QL_chi} and \eqref{QL_P} and using \eqref{Q12_action}, we arrive at
-\begin{align*}
-[Q_L,\chi^i]&=\p_k(P_+)^i_j\chi^k\psi_+^j\textcolor{red}{\overset{?}{\pm}}(P_+)^i_j[(\tl{P}_+)^j_k\p_+\phi^k\textcolor{red}{+}\frac{1}{2}\p_k(K_+)^j_l\psi_+^k\psi_+^l]\\
-&=\p_k(P_+)^i_j(P_+)^k_l\psi_+^l\psi_+^j\textcolor{red}{-}(P_+)^i_j\p_k(P_+)^j_l\psi_+^k\psi_+^l,
-\end{align*}
-where we denoted $\tl{P}_+=\frac{1}{2}(\id-K_+)$ and used $P_+\tl{P}_+=0$. We now expand the projectors, $(P_+)^i_j=\frac{1}{2}(\delta^i_j+(K_+)^i_j)$:
-
-\begin{align*}
-[Q_L,\chi^i]&=\p_k(P_+)^i_j(P_+)^k_l\psi_+^l\psi_+^j\textcolor{red}{-}(P_+)^i_j\p_k(P_+)^j_l\psi_+^k\psi_+^l\\
-&=\frac{1}{2}(\p_j(K_+)^i_l(P_+)^j_k\textcolor{red}{-}(P_+)^i_j\p_k(K_+)^j_l)\psi_+^k\psi_+^l\\
-&=\frac{1}{4}(\p_j(K_+)^i_l(K_+)^j_k\textcolor{red}{-}(K_+)^i_j\p_k(K_+)^j_l)\psi_+^k\psi_+^l\\
-&+\frac{1}{4}(\p_j(K_+)^i_l\psi_+^j\psi_+^l\textcolor{red}{-}\p_k(K_+)^i_l\psi_+^k\psi_+^l)=-\frac{1}{2}(N_{K_+})^i_{kl}\psi_+^k\psi^l_+,
-\end{align*}
-\textcolor{red}{This must be the right sign choice} where in the last line we rewrote $\psi_+^k\psi^l_+=\frac{1}{2}(\psi^k\psi^l-\psi^l\psi^k)$ to get the expression for the Nijenhuis tensor of $K_+$:
-\begin{align*}
-4(N_{K_+})^i_{kl}=(K_+)^j_k\p_j(K_+)^i_l-(K_+)^j_l\p_j(K_+)^i_k \textcolor{red}{-} (K_+)^i_j(\p_k(K_+)^j_l-\p_l(K_+)^j_k).
-\end{align*}
-Invoking integrability of $K_+$, $N_{K_+}=$ and we conclude that $[Q_L,\chi^i]=0$.
-
-Similarly, $[Q_L,\lambda]$ can be expanded
-\begin{align}\label{QL_lambda}
-[Q_L,\lambda^i]&=[Q_L,(P_-)^i_j\psi_-^j]=[Q_L,(P_-)^i_j]\psi_-^j+(P_-)^i_j[Q_L,\psi_-^j]\\
-&=\p_k(P_-)^i_j\chi^k\psi_-^j+(P_-)^i_k((P_+)^k_jF^j+\frac{1}{2}\p_l(K_+)^k_j\psi^l_-\psi_+^j),
-\end{align}
-where we used
-\begin{align*}
-[Q_L,\psi_-^i]=(P_+)^i_jF^j+\frac{1}{2}\p_k(K_+)^i_j\psi^k_-\psi_+^j.
-\end{align*}
-Next, we rewrite the derivative in terms of $\n^-$ and use the property $\n^-P_-=0$:
-\begin{align*}
-\p_k(P_-)^i_j&=\n^-_k(P_-)^i_j-(\Gamma^-)^i_{kl}(P_-)^l_j+(\Gamma^-)^l_{kj}(P_-)^i_l\\
-&=-(\Gamma^-)^i_{kl}(P_-)^l_j+(\Gamma^-)^l_{kj}(P_-)^i_l,
-\end{align*}
-so that
-\begin{align}\label{eq:calc1}
-\begin{aligned}
-\p_k(P_-)^i_j\chi^k\psi_-^j=(-(\Gamma^-)^i_{kl}(P_-)^l_j+(\Gamma^-)^l_{kj}(P_-)^i_l)(P_+)^k_m\psi_+^m\psi_-^j.
-\end{aligned}
-\end{align}
-Similarly,
-\begin{align}\label{eq:calc2}
-\begin{aligned}
-\frac{1}{2}(P_-)^i_k\p_l(K_+)^k_j\psi^l_-\psi_+^j&=(P_-)^i_k\p_l(P_+)^k_j\psi^l_-\psi_+^j\\
-&=(P_-)^i_k(-(\Gamma^-)^k_{ml}(P_+)^m_j+(\Gamma^-)^m_{jl}(P_+)^k_m)\psi^l_-\psi_+^j,
-\end{aligned}
-\end{align}
-where we used
-\begin{align*}
-(\Gamma^+)^i_{jk}=g^{im}(\Gamma_{mjk}+\frac{1}{2}H_{jkm})=g^{im}(\Gamma_{mkj}-\frac{1}{2}H_{kjm})=(\Gamma^-)^i_{kj}.
-\end{align*}
-Plugging \eqref{eq:calc1} and \eqref{eq:calc2} into \eqref{QL_lambda} with use of the equation of motion for $F$ \eqref{F_EoM} then yields
-\begin{align*}
-[Q_L,\lambda^i]&=((\Gamma^-)^i_{km}(P_-)^m_l-(\Gamma^-)^m_{kl}(P_-)^i_m)(P_+)^k_j\psi_-^l\psi_+^j\\
-&+(P_-)^i_k(-(\Gamma^-)^k_{ml}(P_+)^m_j+(\Gamma^-)^m_{jl}(P_+)^k_m)\psi^l_-\psi_+^j\\
-&-(P_-)^i_k(P_+)^k_m(\Gamma^-)^m_{jl}\psi_-^l\psi_+^j
- \end{align*}
-
- terms cancel (\textcolor{red}{up to another relative minus sign!}) as well as cancelling the term $(P_-)^i_k(P_+)^k_jF^j$ by
-\begin{align*}
-(P_-)^i_k(\Gamma^+)^m_{lj}(P_+)^k_m\psi^l_-\psi_+^j=(P_-)^i_k(P_+)^k_j(\Gamma^-)^j_{ml}\psi^l_-\psi_+^m=-(P_-)^i_k(P_+)^k_jF^j
-\end{align*}
-and we arrive at
-\begin{align*}
-\{Q_L,\lambda^i\}=-(\Gamma^-)^i_{kl}\chi^k\lambda^l.
-\end{align*}
-
-Now for $Q_R$, we have
-\begin{align*}
-\{Q_R,\phi^i\}=\lambda^i
-\end{align*}
-\end{proof}
-
-The observables of the twisted theory are therefore polynomials in the odd variables $\chi,\lambda$ with even coefficients dependent on $\phi$:
-\begin{align*}
-{\cal O}_f=f(\phi)_{i_1\cdots i_a,j_1\cdots j_b}\chi^{i_1}\cdots\chi^{i_a}\lambda^{j_1}\cdots\lambda^{j_b}.
-\end{align*}
-Because $\chi \in \XX^{(1,0)_+}$ and $\lambda \in \XX^{(1,0)_-}$, we can identify ${\cal O}_f$ with a function on the supermanifold $(T^{(1,0)_+}\oplus T^{(1,0)_-})[1]$, which in turn can be identified with differential form
-\begin{align*}
-\Omega_f=f(\phi)_{i_1\cdots i_a,j_1\cdots j_b}dx^{i_1}_+\cdots dx^{i_a}_+ dx^{j_1}_- \cdots dx^{j_b}_-,
-\end{align*}
-where $dx_\pm$ are the one-forms satisfying $K_\pm dx_\pm=dx_\pm$, i.e.
-sections of the bundle $T^{*(1,0)_\pm}$.
-Via this identification, the operator ${\cal Q}\coloneqq Q_L+Q_R$ defines a differential $\rd_\QQ$, which acts on the sections of $\bigwedge^k(T^{*(1,0)_+}\oplus T^{*(1,0)_-})$ and because $\QQ$ squares to zero $\rd_\QQ$ also squares to zero.
-Therefore, $\rd_\QQ$ gives rise to a Chevalley-Eilenberg complex $\text{CE}(L)$ of a certain Lie algebroid $L$ which we now describe.
-
-\paragraph{Lie algebroid from bi-para-Hermitian data} The underlying vector bundle of the Lie algebroid is $L=T^{(1,0)_+}\oplus T^{(1,0)_-}$, and the anchor is the sum of the two inclusions $\imath_\pm:\ T^{(1,0)_\pm}\hookrightarrow T$, i.e.
-\begin{align*}
-a:L=T^{(1,0)_+}\oplus T^{(1,0)_-} &\rightarrow T\\
- e=(x_+,x_-) &\mapsto \imath_+(x_+)+\imath_-(x_-).
-\end{align*}
-From \eqref{eq:Qcoh} we can read off the action of $\rd_\QQ$ on degree one elements, i.e. sections $\alpha=(\alpha^+,\alpha^-)$ of $L^*=T^*_{(1,0)_+}\oplus T^*_{(1,0)_-}$:
-\begin{align*}
-\rd_\QQ\alpha&=\p_k\ap_i^+[dx_+^k+dx_-^k]\w dx_+^i-\ap^+_i(\Gamma^+)^i_{jk}dx_-^j\w dx_+^k\\
-&+\p_k\ap_i^-[dx_+^k+dx_-^k]\w dx_-^i-\ap^-_i(\Gamma^-)^i_{jk}dx_+^j\w dx_-^k.
-\end{align*}
-%In coordinate-free form, we get
-%\begin{align*}
-%\rd_\QQ\ap=(\p_++\n^+_{P_-(\bullet)})\ap^++(\p_-+\n^-_{P_+(\bullet)})\ap^-,
-%\end{align*}
-By contracting in two sections of $L$, $e_1=x_++x_-$, $e_2=y_-+y_-$, we get the coordinate-free expression
-\begin{align}\label{eq:dQ}
-\begin{aligned}
-(\rd_\QQ\ap)(e_1,e_2)&=(\p_+\ap^+)(x_+,y_+)+\n^+_{x_-}\ap^+(y_+)-\n^+_{y_-}\ap^+(x_+)\\
-&+(\p_-\ap^-)(x_-,y_-)+\n^-_{x_+}\ap^-(y_-)-\n^-_{y_+}\ap^-(x_-),
-\end{aligned}
-\end{align}
-where $\p_\pm$ denotes the para-complex Dolbeault operators $\p$ for $K_\pm$.
-We can further simplify this expression by writing $\ap=(\eta(\tl{z}_+),\eta(\tl{z}_-))$ for $\tl{z}_\pm \in \se(T^{(1,0)_\pm})$, invoking the formula $\p_\pm\ap^\pm(x_\pm,y_\pm)=\lc_{x_\pm}\ap^\pm(y_\pm)-\lc_{y_\pm}\ap^\pm(x_\pm)$ and recalling $\n^\pm=\lc\pm \frac{1}{2}\eta^{-1}H$:
-\begin{align}
-\begin{aligned}
-(\rd_\QQ\ap)(e_1,e_2)&=\eta((\lc_{x_+}+\n_{x_-}^+)\zt_+,y_+)-\eta((\lc_{y_+}+\n_{y_-}^+)\zt_+,x_+)\\
-&+\eta((\lc_{x_-}+\n_{x_+}^-)\zt_-,y_-)-\eta((\lc_{y_-}+\n_{y_+}^-)\zt_-,x_-)\\
-&=\eta(\n^+_{x_++x_-}\zt_+,y_+)-\eta(\n_{y_++y_-}^+\zt_+,x_+)-H(x_+,\zt_+,y_+)\\
-&+\eta(\n_{x_++x_-}^-\zt_-,y_-)-\eta(\n_{y_++y_-}^-\zt_-,x_-)+H(x_-,\zt_-,y_-)
-\end{aligned}
-\end{align}
-
-\paragraph{Lie algebroid from generalized para-K\"ahler data} Recall that a GpK structure defines the decomposition \eqref{GpK_bundles}
-\begin{align*}
-\TT=\ell_+\oplus\ell_-\oplus \ellt_+\oplus \ellt_-,
-\end{align*}
-where the the eigenbundles of $\KK_+$ are $\Lb_+=\ell_+\oplus\ell_-$ and $\tl{\Lb}_+=\ellt_+\oplus \ellt_-$.
-Because $\Lb$ is a Dirac structure, it defines a Lie algebroid by restriction of the Courant algebroid on $\TT$ to $\Lb$, i.e.
-the Lie algebroid bracket and anchor are given by the restriction of the Dorfman bracket and the projection onto tangent bundle, respectively (see Proposition \ref{prop:dirac_Liealg}.
-
-\begin{theorem}
-The Lie algebroids $(L,a,\rd_\QQ)$ and $(\Lb_+,\pi_T\!\!\mid_{\Lb_+},\brac\!\!\mid_{\Lb_+})$ are isomorphic via the map $\pi=\pi_+\oplus \pi_-$.
-\end{theorem}
-\begin{proof}
-First, we notice that the bundles themselves are related by $\pi$,  $\pi(\Lb_+)=\pi(\ell_+\oplus \ell_-)=\pi_+(\ell_+)\oplus \pi_-(\ell_-)=T^{(1,0)_+}\oplus T^{(1,0)_-}=L$ and also $\pi$ is clearly an isomorphism since both $\pi_\pm$ are.
-Additionally, the anchors are related by $a\circ\pi=\pi_T\!\!\mid_{\Lb_+}$.
-The only non-trivial task is therefore to show that the respective differentials satisfy
-\begin{align}\label{eq:d_pi}
-\pi^*\circ\rd_Q  =\rd_{\Lb_+}\circ \pi^*,
-\end{align}
-where $\pi^*=\pi^*_+\oplus\pi_-^*$ and $\pi^*_\pm$ are dual maps to $\pi_\pm:\ell_+\rightarrow T^{(1,0)_\pm}$, extended to a map $\pi^*:\Lambda^k(L^*)\rightarrow\Lambda^k(\Lb_+^*)$.
-
-Because of the chain rule, we only need to check this on degree $0$ and degree $1$ elements in the respective complexes. Degree $0$ follows immediately:
-\begin{align*}
-(\rd_Q f)(\pi(u))= a\circ \pi(u)[f]=\pi_T\!\!\mid_{\Lb_+}(u)[f]=(\rd_{\Lb_+}f)(u),
-\end{align*}
-%For degree one, we use the decomposition of the respective bundles and check for each component
-%\begin{alignat*}{2}
-%\rd_Q:&&T^*_{(1,0)_+}\oplus T^*_{(1,0)_-} &\rightarrow \Lambda^2(T^*_{(1,0)_+}\oplus T^*_{(1,0)_-})\\
-%\rd_{\Lb_+}:&& \ell_+^*\oplus \ell_-^* &\rightarrow \Lambda^2(\ell_+^*\oplus \ell_-^*)
-%\end{alignat*}
-and we will now prove \ref{eq:d_pi} for degree $1$ elements. In the following we will make use of the identifications provided by the metric $\eta$ and pairing $\lara$:
-\begin{alignat*}{2}
-\eta:&& T^*_{(1,0)_\pm} &\leftrightarrow T^{(0,1)_\pm}\\
-\lara:&& \ell^*_\pm &\leftrightarrow \ellt_\pm,
-\end{alignat*}
-so that elements in $T^*_{(1,0)_\pm}$ can be written as $\eta(\tl{z}_\pm)$ with $\tl{z}_\pm$ vector in $T^{(0,1)_\pm}$ and similarly, elements in $\ell^*_\pm$ can be expressed as $\la \tl{w}_\pm, \cdot\ra$ with $\tl{w}_\pm$ section of $\ellt_\pm$.
-To declutter notation, we shall also denote the bracket and anchor on $\Lb_+$ by $\brac$ and $\pi$, respectively.
-
-The differential $\rd_{\Lb_+}$ is defined by the bracket on the Lie algebroid $\Lb_+$ via the following formula:
-\begin{align}\label{eq:proof_Liethm}
-\rd_{\Lb_+}  w^* (u,v)=\pi(u) w^*(v)-\pi(u) w^*(v)- w^*([u,v]),
-\end{align}
-where $ w^* \in \se(\Lb_+^*)$ and $u,v\in \se(\Lb_+)$. Writing $ w^*$ as $\la \tl{w},\cdot\ra$, with $\tl{w}\in\se (\tl{\Lb}_+)$ we can rewrite this as
-\begin{align}\label{dL}
-\begin{aligned}
-\rd_{\Lb_+}  w^* (u,v)&=\pi(u)\la v ,\tl{w}\ra-\pi(v)\la u,\tl{w}\ra-\la [u,v],\tl{w}\ra\\
-&=\la D_uv,\tl{w}\ra+\la v,D_u \tl{w}\ra-\la D_v u,\tl{w}\ra-\la u,D_v\tl{w}\ra-\la D_uv-D_vu,\tl{w}\ra\\
-&+{T}(u,v,\tl{w})\\
-&=\la D_u \tl{w},v\ra-\la D_v\tl{w},u\ra+{T}(u,v,\tl{w})\\
-&=\la D_u \tl{w}_+,v_+\ra-\la D_v\tl{w}_+,u_+\ra+{T}(u_+,v_+,\tl{w}_+)\\
-&+\la D_u \tl{w}_-,v_-\ra-\la D_v\tl{w}_-,u_-\ra+{T}(u_-,v_-,\tl{w}_-),
-\end{aligned}
-\end{align}
-where we used \eqref{gentorsion_def} to express $\brac$ in terms of $D$, the generalized Bismut connection of the generalized metric for the GpK structure.
-We then used the fact that $D$ preserves $\lara$, $C_\pm$ as well as $\Lb_+$ and that $T$ only has components in $\Lambda^3 C_+\oplus\Lambda^3 C_-$ \cite{Gualtieri:2010fd}.
-
-We will now show that $\rd_{\Lb_+}$ is related to $\rd_\QQ$ via \eqref{eq:d_pi}, so that $\rd_\QQ=(\pi^{-1})^*\circ \rd_{\Lb_+}\circ \pi^*$, i.e.
-\begin{align*}
-\rd_\QQ\ap(e_1,e_2)=\rd_{\Lb_+}(\pi^*\ap)(\pi^{-1}e_1,\pi^{-1}e_2).
-\end{align*}
-To read this off from \eqref{dL} and compare with \eqref{eq:dQ}, we need to express $\pi^*\ap$ as $\pi^*\ap=w^*=\la \tl{w},\cdot\ra$ for some $\tl{w}\in\se (\tl{\Lb}_+)$ and $\ap=(\eta(\zt_+),\eta(\zt_-))$:
-\begin{align*}
-\pi^*\ap=\pi^*(\eta(\zt_+),\eta(\zt_-))=(\eta(\zt_+,\pi_+\cdot),\eta(\zt_-,\pi_-\cdot))=\frac{1}{2}\la\pi^{-1}(\zt_+,-\zt_-),\cdot\ra,
-\end{align*}
-where $\zt_\pm\in \se(T^{(1,0)_\pm})$ and we used \eqref{pi:gG_relationship}.
-Therefore, denoting $e_1=(x_+,x_-)$ and $e_2=(y_+,y_-)$ as in \eqref{eq:dQ}, \eqref{dL} yields (denoting $e_1=(x_+,x_-)$ and $e_2=(y_+,y_-)$ as in \eqref{eq:dQ})
-\begin{align*}
-\rd_{\Lb_+}(&\pi^*\ap)(\pi^{-1}e_1,\pi^{-1}e_2)\\
-&=\eta(\n^+_{x_++x_-}\zt_+,y_+)-\eta(\n^+_{y_++y_-}\zt_+,x_+)+\frac{1}{2}T(\pi_+^{-1}x_+,\pi_+^{-1}y_+,\pi_+^{-1}\zt_+)\\
-&+\eta(\n^-_{x_++x_-}\zt_-,y_-)-\eta(\n^-_{y_++y_-}\zt_-,x_-)-\frac{1}{2}T(\pi_-^{-1}x_-,\pi_-^{-1}y_-,\pi_-^{-1}\zt_-),
-\end{align*}
-where we used \eqref{genBismut_pi_nabla_pm} and once again \eqref{pi:gG_relationship}.
-Finally, invoking \eqref{gentorsion_H}, we arrive at \eqref{eq:dQ}, showing that \eqref{eq:d_pi} holds and completing the proof.
-\end{proof}
-
-\subsection{Topological twists of the $(2,2)$-model}
-
-\subsection{The (para)holomorphic twist of the $(2,0)$-model}
-
-\bibliographystyle{JHEP}
-\bibliography{mybib}
-\end{document}

### 2019-12-20 AKSZ.tex
some changes

@@
 
+By this general construction, we see that any GpC structure $\KK$ defines a 2D TFT as a boundary theory to the 3D theory whose target is the standard Dorfman Courant algebroid.
+
+Recall that Theorem \ref{thm:pairofdirac} tells us that the choice of a GpC structure $\KK$ determines a pair of tansversal Dirac structures $L$ and $\tilde{L}$. 
+Moreover, by Proposition \ref{prop:dirac_Liealg} the eigenbundle $L$ has the structure of a Lie algebroid compatible with the anchor and Dorfman bracket on $\TT$.
+
+\begin{proposition}
+The BRST cohomology of the local observables of the 2D TFT determined by the GpC structure $\KK$ is equivalent to the Lie algebroid cohomology of $L$. 
+\end{proposition}
+
 \subsubsection*{Trivial GpC structure}

### 2019-12-20 newdraft.tex
some changes

@@
 
+\section{AKSZ}
+
 \section{Two-dimensional parasupersymmetry}  \label{sec: parasusy}
@@
 
-\paragraph{Lie algebroid from generalized para-K\"ahler data} Recall that a GpK structure defines the decomposition \eqref{GpK_bundles}
+\paragraph{Lie algebroid from generalized para-K\"ahler data}
+
+\brian{Do we use the full GpK structure, or are we only using the GpC?}
+Recall that a GpK structure defines the decomposition \eqref{GpK_bundles}
 \begin{align*}
@@
 
-\section{The AKSZ formalism and 3d TFT}
-
-\brian{Merge at some point.}
-
 \appendix

### 2019-12-21 newdraft.tex
dbro comments

--- 2019-11-25 newdraft.tex
@@
 \def\david{\textcolor{red}{DB: }\textcolor{red}}
+\def\btd{\textcolor{orange}{BM to DB: }\textcolor{orange}}
 
@@
 If there is a negative-chirality half structure $\JJ_{C_-}$, then $(\GG,\JJ\coloneqq \JJ_{C_+}\oplus \JJ_{C_-})$ defines a genuine G(p)K structure.
+
+\section{The AKSZ formalism and para-geometry} \label{sec: AKSZ}
 
@@
 
-\brian{I still think this should be a separate section. It can go before AKSZ, if you want, but the answers won't make sense until we introduce the topological theories.}
-
-\brian{Give a general prescription of twisting.}
+\btd{Can you outline what is meant here by twisting?
+We aren't going to use the full language of twisting as in Kevin's paper, but it'd be good to highlight two things: (1) how to use the $R$-symmetry to twist the transformation properties of the fields and (2) how the supercharge deforms the BRST differential.
+I think you already do both below, but it'd be good to add some more discussion. 
+For instance, in accomplishing (1) we should say concretely which bundles each of the fields live in.}
 
@@
 \end{align*}
+\btd{Where do $\chi$ and $\lambda$ live?}
 
@@
 \end{align*}
+
 Because $\chi \in \XX^{(1,0)_+}$ and $\lambda \in \XX^{(1,0)_-}$, we can identify ${\cal O}_f$ with a function on the supermanifold $(T^{(1,0)_+}\oplus T^{(1,0)_-})[1]$, which in turn can be identified with the differential form
@@
 \end{align*}
-where $dx_\pm$ are the one-forms satisfying $K_\pm dx_\pm=dx_\pm$, i.e.
-sections of the bundle $T^*_{(1,0)_\pm}$.
-Via this identification, the operator ${\cal Q}\coloneqq Q_L+Q_R$ defines a differential
+where $dx_\pm$ are the one-forms satisfying $K_\pm dx_\pm=dx_\pm$, i.e. sections of the bundle $T^*_{(1,0)_\pm}$. Via this identification, the operator ${\cal Q}\coloneqq Q_L+Q_R$ defines an operator
 \begin{align*}
@@
 \end{align*}
-and because $\QQ$ squares to zero $\rd_\QQ$ also squares to zero. Therefore, $\rd_\QQ$ gives rise to a Chevalley-Eilenberg complex $\text{CE}(L)$ of a certain Lie algebroid $L$ which we now describe.
-
-\paragraph{Lie algebroid from bi-para-Hermitian data} Consider the Lie algebroid $L\overset{a}{\rightarrow} T$ with $L=T^{(1,0)_+}\oplus T^{(1,0)_-}$ and anchor given by the sum of the two inclusions $\imath_\pm:\ T^{(1,0)_\pm}\hookrightarrow T$:
+Since $\QQ$ squares to zero the operator $\rd_\QQ$ also squares to zero, hence it defines a differential. 
+In fact, we will see that $\rd_\QQ$ gives rise to a Chevalley-Eilenberg complex $\text{CE}(L)$ computing the Lie algebroid cohomology of a certain Lie algebroid.
+
+\paragraph{Lie algebroid from bi-para-Hermitian data} 
+\btd{I suggest renaming $L$ to $L_{twist}$, or something else to denote the fact that is the Lie algebroid obtained via twisting.}
+Consider the Lie algebroid $L\overset{a}{\rightarrow} T$ with $L=T^{(1,0)_+}\oplus T^{(1,0)_-}$ and anchor given by the sum of the two inclusions $\imath_\pm:\ T^{(1,0)_\pm}\hookrightarrow T$:
 \begin{align*}
@@
 
-\paragraph{Lie algebroid from generalized para-K\"ahler data} Recall that a GpK structure defines the decomposition \eqref{GpK_bundles}
+\paragraph{Lie algebroid from generalized para-K\"ahler data}
+
+\brian{Do we use the full GpK structure, or are we only using the GpC?}
+\btd{The title of this section is OK, but we should stress that the Lie algebroid {\em explicitly} does not depend on any Kahler data.}
+\btd{I suggest renaming $\Lb_+$ to $L_{AKSZ}$, or something else to denote the fact that is the Lie algebroid coming from the AKSZ description in Section \ref{sec: AKSZ}.}
+
+Recall that a GpK structure defines the decomposition \eqref{GpK_bundles}
 \begin{align*}
@@
 We have therefore shown that the observables in the topologically twisted theories are given by the Lie algebroid cohomology of $\Lb$, which is exactly the same as the $2D$ boundary topological theories constructed in the Section \ref{??}:
+
 \begin{corollary}
@@
 \end{corollary}
-
-\section{The AKSZ formalism and 3d TFT}
-
-\brian{Merge at some point.}
 

### 2019-12-21 newdraft.tex
added holo. volume form

@@
 The {\bf para-complex Dolbeault complex} is therefore given by
-\begin{align}
-\left(\Omega^{(\bullet,0)}\otimes\Omega^{(0,\bullet)},(\p,\pt)\right)\coloneqq \left(\mathbf{\Omega}^{\bullet,0},\pd\right).
-\end{align}
-\brian{Should this be the thing resolving paraholomorphic functions or anti paraholomorphic functions? If paraholomorphic it should be $\mathbf{\Omega}^{0,\bullet}$. }
+\begin{align}\label{para-dolbeault}
+\left(\Omega^{(\bullet,0)}\otimes\Omega^{(0,\bullet)},(\p,\pt)\right)\coloneqq \left(\mathbf{\Omega}^{0,\bullet},\pd\right).
+\end{align}
+
 %\begin{lemma}
@@
 %\end{proof}
+\paragraph{The para-holomorphic volume form}
+In K\"ahler geometry, the notion of a holomorphic volume form is very important and in particular gives rise to Calabi-Yau manifolds, perhaps the most important subclass of K\"ahler manifolds.
+Here we discuss the para-complex version of this story because it plays an important role when considering the anomalies of the R-symmetry at the quantum level.
+
+Remember that a holomorphic volume form on a complex manifold $M$ of complex dimension $k$ is a non-vanishing section of the canonical bundle, $\Omega \in \Omega^{k,0}(M)$, that is holomorphic, $\bar{\p}\Omega=0$.
+Recalling the para-complex Dolbeault complex \eqref{para-dolbeault}, we can immediately infer what should be the analogous object in para-complex geometry:
+\begin{Def}
+Let $(\PS,K)$ be a para-complex manifold of dimension $2n$.
+We define a para-holomorphic volume form to be a nowhere vanishing section $\hat{\Omega}=(\Omega,\tl{\Omega})\in \Omega^{(n,0)+(0,n)}(\PS)$, where $\Omega \in \Omega^{(n,0)}(\PS)$ and $\tl{\Omega}\in \Omega^{(0,n)}(\PS)$ are each non-vanishing and satisfy
+\begin{align*}
+\pt \Omega=\p \tl{\Omega}=0.
+\end{align*}
+\end{Def}
+Because $\Omega^{(n,0)}(\PS)$ is naturally isomorphic to $\Omega^n(M)$, the section $\Omega$ is non-vanishing and $\pt \Omega=0$ implies it is invariant under the translation along $\Mt$, the above definition implies that $\Omega$ defines an honest volume form on $M$.
+Similarly, $\tl{\Omega}$ is a volume form on $\Mt$ and therefore both the canonical foliations $M$ and $\Mt$ of the para-complex manifold are orientable.
 
@@
 \end{Ex}
-
-\brian{Can we import some of the other examples here?
-Maybe some explicit ones like the toric fibrations you mentioned.}
 
@@
 Here, $\Gamma^-$ are the Christoffel symbols of the connection $\n^-=\lc-\frac{1}{2}\eta^{-1}H$.
-\david{we can show more of the calculations or put some more in the appendix but this is fairly standard knowledge and I think the above is sufficient}
+
 \subsection{$(2,2)$ para-supersymmetry}\label{sec:(2,2)parasusy}
@@
 \end{align*}
-
-\david{is the following paragraph needed?}
-\brian{I think it's nice to point out how it  generalizes.}
 

### 2019-12-21 newdraft.tex
added def. of para-CY

@@
 Let $(\PS,K)$ be a para-complex manifold of dimension $2n$.
-We define a para-holomorphic volume form to be a nowhere vanishing section $\hat{\Omega}=(\Omega,\tl{\Omega})\in \Omega^{(n,0)+(0,n)}(\PS)$, where $\Omega \in \Omega^{(n,0)}(\PS)$ and $\tl{\Omega}\in \Omega^{(0,n)}(\PS)$ are each non-vanishing and satisfy
+We define a {\bf para-holomorphic volume form} to be a nowhere vanishing section $\hat{\Omega}=(\Omega,\tl{\Omega})\in \Omega^{(n,0)+(0,n)}(\PS)$, where $\Omega \in \Omega^{(n,0)}(\PS)$ and $\tl{\Omega}\in \Omega^{(0,n)}(\PS)$ are each non-vanishing and satisfy
 \begin{align*}
@@
 Similarly, $\tl{\Omega}$ is a volume form on $\Mt$ and therefore both the canonical foliations $M$ and $\Mt$ of the para-complex manifold are orientable.
+
+As an extension of the above definition and the direct analogy with Calabi-Yau manifolds, we can introduce a definition of the para-Calabi-Yau manifolds:
+\begin{Def}
+A {\bf para-Calabi-Yau manifold} is a compact, para-K\"ahler manifold $(\PS,\eta,K)$ with a para-Holomorphic volume form $\hat{\Omega}$.
+\end{Def}
 

### 2020-01-05 newdraft.tex
please only add .tex files

@@
 
-\brian{geometry, change in gradings}
 \david{how does the embedding of $SO(1,1)$ into $G_R$ reflect on the definition of $\QQ$?}
+\brian{In Euclidean space, we choose an embedding $SO(2) \hookrightarrow G_R$. 
+Then, the twisting supercharge is required to be invariant.
+The obvious analog is to require an embedding $SO(1,1) \to G_R$ for which $\QQ$ is invariant.
+This is the twisting homomorphism which tells us how to modify the Lorentz group.
+}
+
+\brian{
+There is another piece of data we have to fix to get the $\mathbb{Z}$-grading in the twisted theory. 
+Ordinarily this amounts to picking a homomorphism $U(1) \to G_R$ for which $\QQ$ is weight one. 
+It appears no such twisting homomorphism is possible.
+Indeed, every group homomorphism $U(1) \to SO(1,1) \times SO(1,1)$  are necessarily trivial since $U(1)$ is compact and $SO(1,1) \cong \RR \oplus \RR$ (the first copy is the connected component of the identity, and the second component is the connected component of minus identity).
+This means we may have to slightly reimagine what ``twisting data" is here.
+Since there is at least a copy of $\RR$ in $SO(1,1)$ we can probably use this to define a ``weight".}
 
@@
 \end{align}
+\brian{Should we call this the  ``generalized para B twist"?
+It is invariant with respect to the anti-diagonal twisting homomorphism $SO(1,1) \to SO(1,1) \times SO(1,1)$.
+I think Kapustin-Li call this the axial.}
 and we also introduce the usual notation 

### 2020-01-08 newdraft.tex
Update newdraft.tex

--- 2019-12-21 newdraft.tex
@@
 so that when $K$ is integrable, the de-Rham differential splits as $\rd=\p+\tl{\p}$, where
-\begin{align*}
+\begin{align}\label{paracomplex_dels}
 \begin{array}{cc}
@@
 \end{array}
-\end{align*}
+\end{align}
 are the \textbf{para-complex Dolbeault operators}, satisfying
@@
 have to satisfy
-\begin{align*}
+\begin{align}\label{r_symmetry_matrix}
 (M_\pm)^a_c\eta^{cd}(M_\pm)^a_d=\eta^{ab},
-\end{align*}
+\end{align}
 i.e. $M_\pm$ have to lie in $SO(1,1)$ for each subscript $\pm$ and the R-symmetry group is therefore $G_R=SO(1,1)_+\times SO(1,1)_-$.
@@
 In our presentation, we use the similarities between the generalized K\"{a}hler (GK) and generalized para-K\"{a}hler (GpK) geometries, and we follow the approach presented in \cite{Kapustin:2004gv} for the GK case.
-
-\brian{geometry, change in gradings}
-\david{how does the embedding of $SO(1,1)$ into $G_R$ reflect on the definition of $\QQ$?}
+Let us briefly review the construction now.
 
 Let $(\eta,K_\pm,H=\rd b)$ be the bi-para-Hermitian geometry of the $(2,2)$ para-SUSY sigma model and let $\{Q^1_\pm,Q^1_\pm\}$ be the basis of the superalgebra \eqref{eq:(2,2)para}.
-We define the following nilpotent supercharge
+Our goal is to use the data of the $(2,2)$ para-SUSY theory to define a new, {\it topological} theory.
+In this section, we will show how to define the BRST complex for this new theory, which in particular requires the definition of a nilpotent BRST operator $\QQ^2=0$.
+Additionally, we want all fields in this complex to be scalars under the Lorentz group.
+For this, we must alter the original Lorentz group $SO(1,1)$ by its embedding in the R-symmetry group, $SO(1,1)_{G_R}\hookrightarrow G_R=SO(1,1)_+\times SO(1,1)_-$, so that the new Lorentz group action is given by the diagonal embedding of $SO(1,1)$ into $SO(1,1)\times SO(1,1)_{G_R}$
+\begin{align}\label{embeddings}
+SO(1,1)\overset{diag.}{\hookrightarrow} SO(1,1)\!\times\! SO(1,1)_{G_R}\!\!\hookrightarrow SO(1,1)\!\times\! \overbrace{SO(1,1)_+\!\times\! SO(1,1)_-}^{G_R},
+\end{align}
+defining a new Lorentz action, which will be a sum of the original one and the action of $SO(1,1)_{G_R}$ in $G_R$.
+In this sense, the Lorentz group gets {\it twisted} by the embedding into the R-symmetry group.
+Finally, the operator $\QQ$ must be chosen accordingly to the choice of $SO(1,1)_{G_R}\hookrightarrow G_R$ so that it transforms as a scalar itself under the new Lorentz action, which ensures that the fields in the BRST complex it defines are all scalars too.
+
+%\david{how does the embedding of $SO(1,1)$ into $G_R$ reflect on the definition of $\QQ$?}
+%\brian{In Euclidean space, we choose an embedding $SO(2) \hookrightarrow G_R$. 
+%Then, the twisting supercharge is required to be invariant.
+%The obvious analog is to require an embedding $SO(1,1) \to G_R$ for which $\QQ$ is invariant.
+%This is the twisting homomorphism which tells us how to modify the Lorentz group.
+%}
+%
+%\brian{
+%There is another piece of data we have to fix to get the $\mathbb{Z}$-grading in the twisted theory. 
+%Ordinarily this amounts to picking a homomorphism $U(1) \to G_R$ for which $\QQ$ is weight one. 
+%It appears no such twisting homomorphism is possible.
+%Indeed, every group homomorphism $U(1) \to SO(1,1) \times SO(1,1)$  are necessarily trivial since $U(1)$ is compact and $SO(1,1) \cong \RR \oplus \RR$ (the first copy is the connected component of the identity, and the second component is the connected component of minus identity).
+%This means we may have to slightly reimagine what ``twisting data" is here.
+%Since there is at least a copy of $\RR$ in $SO(1,1)$ we can probably use this to define a ``weight".}
+\bigskip
+Let us start with the second, twisting, embedding in \eqref{embeddings}
+\begin{align*}
+\rho:\ SO(1,1)_{G_R}\hookrightarrow G_R=SO(1,1)_+\times SO(1,1)_-.
+\end{align*}
+Clearly, there are two inequivalent choices -- the diagonal and anti-diagonal -- and we shall label them as $SO(1,1)_V$ and $SO(1,1)_A$, respectivelly, and  calling the twist by $SO(1,1)_{V/A}$ the {\bf generalized para-A/B-twist}.
+Explicitly, if we represent $M_\pm\in SO(1,1)$ in \eqref{r_symmetry_matrix} as
+\begin{align*}
+ M_\pm(\alpha)\begin{pmatrix}
+ Q^1_\pm\\
+ Q^2_\pm
+ \end{pmatrix}=\begin{pmatrix}
+ \cosh(\alpha) & \sinh(\alpha) \\
+ \sinh(\alpha) & \cosh(\alpha)
+ \end{pmatrix}
+ \begin{pmatrix}
+ Q^1_\pm\\
+ Q^2_\pm
+ \end{pmatrix},
+ \end{align*}
+then the diagonal embedding is given by $M(\alpha) \mapsto (M(\alpha),M(\alpha))$ while the anti-diagonal is $M(\alpha) \mapsto (M(\alpha),M(-\alpha))$.
+
+To determine the corresponding nilpotent operators $\QQ_{V/A}$ on which $V$ and $A$ act trivially, we find that the following combinations of the supercharges
+\begin{align*}
+Q_{L\pm}=\frac{1}{2}(Q^1_+\pm Q^2_+),\quad Q_{R\pm}=\frac{1}{2}(Q^1_-\pm Q^2_-),
+\end{align*}
+are all nilpotent and satisfy $[Q_{L\pm},Q_{L\pm}]=0$, so that their sums and differences will also be nilpotent.
+However, they are charged under the Lorentz group.
+Their Lorentz charges along with their charges under $SO(1,1)_{V/A}$ are summarized in the following table
+\bigskip
+\begin{center}
+\begin{tabular}{c|c c c}
+		& $SO(1,1)_{Lor.}$ & $SO(1,1)_V$ & $SO(1,1)_A$\\ \hline
+$Q_{L+}$& $-1$ & $+1$ & $+1$\\
+$Q_{L-}$& $-1$ & $-1$ & $+1$\\
+$Q_{R+}$& $+1$ & $+1$ & $-1$\\
+$Q_{R-}$& $+1$ & $-1$ & $+1$
+\end{tabular}.
+\end{center}
+\bigskip
+From the above table, we can read off that the combination $\QQ_V=Q_{L+}+Q_{R-}$ will transform as a scalar under the new Lorentz group twisted by $U(1,1)_V$ and $\QQ_A=Q_{L+}+Q_{R+}$ will transform as a scalar under the new Lorentz group twisted by $U(1,1)_A$.
+Note also that the two are related by $Q_-^2\mapsto -Q_-^2$ and because $Q_-^2=K_-D_-$, this is acheived by changing the sign of $K_-$.
+Therefore, in the following we will study without loss of generality the twist given by $U(1,1)_A$ and $\QQ_B$, i.e.
+the generalized para-B-model:
+
+\begin{Def}\label{def:B-twist}
+The generalized para-B-model is a topological twist (in the above sense) of a $(2,2)$ para-SUSY sigma model given by the diagonal embedding of the Lorentz group $SO(1,1)\hookrightarrow SO(1,1)\times SO(1,1)_A$, where $SO(1,1)_A$ denotes the anti-diagonal embedding of $SO(1,1)$ into the R-symmetry group $G_R=SO(1,1)\times SO(1,1)$, and the nilpotent scalar BRST operator
 \begin{align}\label{QQ_nilpotent}
-\QQ=Q_L+Q_R,\quad Q_L=\frac{1}{2}(Q^1_++Q^2_+),\quad Q_R=\frac{1}{2}(Q^1_-+Q^2_-),
-\end{align}
-and we also introduce the usual notation 
-\begin{align*}
-\chi=\frac{1}{2}(\id+K_+)\psi_+=P_+\psi_+=\psi_+^{(1,0)_+},\quad\lambda=\frac{1}{2}(\id+K_-)\psi_-=P_-\psi_-=\psi_-^{(1,0)_-}.
-\end{align*}
-\btd{Where do $\chi$ and $\lambda$ live?}
-
-The action of $\QQ$ on these fields is the content of the following statement:
+\QQ=Q_L+Q_R,\quad Q_L=\frac{1}{2}(Q^1_++Q^2_+),\quad Q_R=\frac{1}{2}(Q^1_-+Q^2_-).
+\end{align}
+\end{Def}
+\bigskip
+We now turn to the BRST complex that describes the scalar fields in the twisted theory. For this, we introduce the usual notation 
+\begin{align*}
+\chi=\frac{1}{2}(\id+K_+)\psi_+=P_+\psi_+=\psi_+^{(1,0)_+},\quad\lambda=\frac{1}{2}(\id+K_-)\psi_-=P_-\psi_-=\psi_-^{(1,0)_-},
+\end{align*}
+where both $\chi$ and $\lambda$ are scalars under the twisted Lorentz action, which is the content of the following statement:
 \begin{proposition}\label{prop_toptwist}
@@
 \end{proof}
-
+Recalling that $(\Gamma^+)^i_{jk}=(\Gamma^-)^i_{kj}$ (see \eqref{Gamma-pm}), we find that the BRST degrees of the fields are given by the following complex
+\begin{align*}
+&\phi \overset{\QQ}{\longrightarrow}\chi+\lambda\overset{\QQ}{\longrightarrow} 0\\
+&0 \phantom{\longrightarrow\longrightarrow} 1
+\end{align*}
+\noindent
 The observables of the twisted theory are therefore polynomials in the odd variables $\chi,\lambda$ with even coefficients dependent on $\phi$:
@@
 
-Because $\chi \in \XX^{(1,0)_+}$ and $\lambda \in \XX^{(1,0)_-}$, we can identify ${\cal O}_f$ with a function on the supermanifold $(T^{(1,0)_+}\oplus T^{(1,0)_-})[1]$, which in turn can be identified with the differential form
+Because $\chi \in \XX^{(1,0)_+}$ and $\lambda \in \XX^{(1,0)_-}$, we can identify ${\cal O}_f$ with a function on the supermanifold $(T^{(1,0)_+}\oplus T^{(1,0)_-})[1]$, which in turn can be identified with the mixed differential form
 \begin{align*}
@@
 Since $\QQ$ squares to zero the operator $\rd_\QQ$ also squares to zero, hence it defines a differential. 
-In fact, we will see that $\rd_\QQ$ gives rise to a Chevalley-Eilenberg complex $\text{CE}(L)$ computing the Lie algebroid cohomology of a certain Lie algebroid.
+In fact, we will see that $\rd_\QQ$ gives rise to a Chevalley-Eilenberg complex $\text{CE}(L_{twist})$ computing the Lie algebroid cohomology of a certain Lie algebroid.
 
 \paragraph{Lie algebroid from bi-para-Hermitian data} 
-\btd{I suggest renaming $L$ to $L_{twist}$, or something else to denote the fact that is the Lie algebroid obtained via twisting.}
-Consider the Lie algebroid $L\overset{a}{\rightarrow} T$ with $L=T^{(1,0)_+}\oplus T^{(1,0)_-}$ and anchor given by the sum of the two inclusions $\imath_\pm:\ T^{(1,0)_\pm}\hookrightarrow T$:
-\begin{align*}
-a:L=T^{(1,0)_+}\oplus T^{(1,0)_-} &\rightarrow T\\
+Consider the Lie algebroid $L_{twist}\overset{a}{\rightarrow} T$ with $L_{twist}=T^{(1,0)_+}\oplus T^{(1,0)_-}$ and anchor given by the sum of the two inclusions $\imath_\pm:\ T^{(1,0)_\pm}\hookrightarrow T$:
+\begin{align*}
+a:L_{twist}=T^{(1,0)_+}\oplus T^{(1,0)_-} &\rightarrow T\\
  e=(x_+,x_-) &\mapsto \imath_+(x_+)+\imath_-(x_-).
 \end{align*}
-From \eqref{eq:Qcoh} we can read off the action of $\rd_\QQ$ on degree one elements, i.e. sections $\alpha=(\alpha^+,\alpha^-)$ of $L^*=T^*_{(1,0)_+}\oplus T^*_{(1,0)_-}$:
+From \eqref{eq:Qcoh} we can read off the action of $\rd_\QQ$ on degree one elements, i.e. sections $\alpha=(\alpha^+,\alpha^-)$ of $L^*_{twist}=T^*_{(1,0)_+}\oplus T^*_{(1,0)_-}$:
 \begin{align*}
@@
 %\end{align*}
-By contracting in two sections of $L$, $e_1=x_++x_-$, $e_2=y_-+y_-$, we get the coordinate-free expression
+By contracting in two sections of $L_{twist}$, $e_1=x_++x_-$, $e_2=y_-+y_-$, we get the coordinate-free expression
 \begin{align}\label{eq:dQ}
@@
 \end{align}
-where $\p_\pm$ denotes the para-complex Dolbeault operators $\p$ for $K_\pm$.
+where $\p_\pm$ denotes the para-complex Dolbeault operators \eqref{paracomplex_dels} of the para-complex structure $K_\pm$.
 We can further rewrite this expression by writing $\ap=(\eta(\tl{z}_+),\eta(\tl{z}_-))$ for $\tl{z}_\pm \in \se(T^{(1,0)_\pm})$, invoking the formula $\p_\pm\ap^\pm(x_\pm,y_\pm)=\lc_{x_\pm}\ap^\pm(y_\pm)-\lc_{y_\pm}\ap^\pm(x_\pm)$ and recalling $\n^\pm=\lc\pm \frac{1}{2}\eta^{-1}H$:
@@
 \end{align}
-This fully determines the Lie algebroid structure of $L$. However, in the following paragraph we will discuss how the same Lie algebroid arises from the data of a generalized para-K\"ahler structure.
+This fully determines the Lie algebroid structure of $L_{twist}$.
+Therefore, the topological twist gives rise to the Lie algebroid we just described explicitly using only the data of the bi-para-Hermitian geometry $(\eta,K_\pm,H)$.
+In the following paragraph, we will discuss how the same Lie algebroid arises from the data of the corresponding generalized para-K\"ahler structure.
 
 \paragraph{Lie algebroid from generalized para-K\"ahler data}
-
-\brian{Do we use the full GpK structure, or are we only using the GpC?}
-\btd{The title of this section is OK, but we should stress that the Lie algebroid {\em explicitly} does not depend on any Kahler data.}
-\btd{I suggest renaming $\Lb_+$ to $L_{AKSZ}$, or something else to denote the fact that is the Lie algebroid coming from the AKSZ description in Section \ref{sec: AKSZ}.}
+%
+%\brian{Do we use the full GpK structure, or are we only using the GpC?}
+%\btd{The title of this section is OK, but we should stress that the Lie algebroid {\em explicitly} does not depend on any Kahler data.}
+%\btd{I suggest renaming $\Lb_+$ to $L_{AKSZ}$, or something else to denote the fact that is the Lie algebroid coming from the AKSZ description in Section \ref{sec: AKSZ}.}
+We will now show that the Lie algberoid $(L_{twist},\rd_\QQ,a)$ is isomorphic to one defined by the $+1$-eigenbundle of the generalized para-complex structure $\KK_+$ of the generalized para-K\"ahler structure $(\KK_+,\KK_-)$ underlying the $(2,2)$ para-SUSY theory.
+Therefore, $(L_{twist},\rd_\QQ,a)$ coincides with the Lie algebroid used in Section \ref{sec: AKSZ} to define a topological theory in the AKSZ formalism from an arbitrary generalized para-complex structure $\KK$.
+Consequently, we find that the theories constructed in Section \ref{sec: AKSZ} labeled by a GpC structure $\KK$ can be realized as topological twists of a $2D$ $(2,2)$ para-SUSY $\sigma$-models whenever $\KK$ is a part of a GpK data $(\KK_+=\KK,\KK_-)$.
 
@@
 where the the eigenbundles of $\KK_+$ are $\Lb_+=\ell_+\oplus\ell_-$ and $\wtl{\Lb}_+=\ellt_+\oplus \ellt_-$.
-Because $\Lb$ is a Dirac structure, it defines a Lie algebroid by restriction of the Courant algebroid on $\TT$ to $\Lb$, i.e.
+Because $\Lb$ is a Dirac structure, it defines a Lie algebroid by restriction of the Courant algebroid on $\TT$ to $\Lb_+$, i.e.
 the Lie algebroid bracket and anchor are given by the restriction of the Dorfman bracket and the projection onto tangent bundle, respectively (see Proposition \ref{prop:dirac_Liealg}).
-We now show that such Lie algebroid is isomorphic to the Lie algebroid defined by $(L,a,\rd_\QQ)$ above:
+We now show that such Lie algebroid is isomorphic to the Lie algebroid defined by $(L_{twist},\rd_\QQ,a)$ above:
 \begin{theorem}
@@
 
-We have therefore shown that the observables in the topologically twisted theories are given by the Lie algebroid cohomology of $\Lb$, which is exactly the same as the $2D$ boundary topological theories constructed in the Section \ref{??}:
+We have therefore shown that the observables in the topologically twisted theories are given by the Lie algebroid cohomology of $\Lb$, which is exactly the same as for the $2D$ boundary topological theories constructed in the Section \ref{sec: AKSZ}:
 
@@
 Let $\Phi:\Sigma^{2|2}\rightarrow \Mb$ be a $(2,2)$ para-supersymmetric $\sigma$-model with the target $(\Mb,\KK_\pm,\GG(\eta,b))$ a Generalized para-K\"ahler manifold.
-Then the topological twist of this $\sigma$-model defined by the nilpotent charge $\QQ$ \eqref{QQ_nilpotent} agrees with the $2D$ topological boundary theory determined by the generalized para-complex structure on the Courant algebroid $(\TT)\Mb$ with flux $H\overset{loc.}{=}\rd b$.
+Then the generalozed para-B-twist of this $\sigma$-model defined in Definition \ref{def:B-twist} coincides with the $2D$ topological boundary theory determined by the generalized para-complex structure on the Courant algebroid $(\TT)\Mb$ with flux $H\overset{loc.}{=}\rd b$.
 \end{corollary}
@@
 where we used
-\begin{align*}
+\begin{align}\label{Gamma-pm}
 (\Gamma^+)^i_{jk}=g^{im}(\Gamma_{mjk}+\frac{1}{2}H_{jkm})=g^{im}(\Gamma_{mkj}-\frac{1}{2}H_{kjm})=(\Gamma^-)^i_{kj}.
-\end{align*}
+\end{align}
 Plugging \eqref{eq:calc1} and \eqref{eq:calc2} into \eqref{QL_lambda} with use of the equation of motion \eqref{F_EoM} for $F$ then yields

### 2020-01-10 AKSZ.tex
dbro comments
changes

@@
 \newcommand{\wtl}{\widetilde}
+
+\def\sA{\mathcal{A}}
+\def\d{{\rm d}}
+\def\dbar{\Bar{\partial}}
+
 %----------------------------------------
@@
 In this section we will show how to associate a class of $2D$ topological field theories to generalized para-complex structures.
-The construction closely follows the relationship between ordinary (non-para) generalized complex structures and $2D$ topological field theories developed by Gualtieri, Pestun, \brian{other references?}.
+The construction closely follows the relationship between ordinary (non-para) generalized complex structures \cite{Gualtieri:2003dx} and $2D$ topological field theories developed in \cite{Cattaneo:2009zx, Pestun:2006rj} \btd{Please add any more references you think fit.}
 
 The prescription of defining the $2D$ topological theory associated to a GpC structure starts with a $3D$ topological field theory which is defined for any manifold $M$. 
-More generally, this $3D$ theory can be defined for any {\em Courant algebroid} on $M$ \cite{Roytenberg:2002nu}., but for most examples we will only consider the standard exact Courant algebroid (or twisted versions) defined by the Dorfman bracket.
+More generally, this $3D$ theory can be defined for any {\em Courant algebroid} on $M$ \cite{Roytenberg:2002nu}, but for most examples we will only consider the standard exact Courant algebroid (or twisted versions) defined by the Dorfman bracket.
 The key to our construction is to realize the data of a G(p)C structure in terms of its eigenbundles, which are Dirac structures $L$ in the Courant algebroid $\TT$.
@@
 Via the AKSZ construction \cite{AKSZ}, this correspondence translates into the statement that the Dirac structure $L$ defines a topological boundary theory of the $3D$ topological theory defined by the standard Courant algebroid.
-\brian{cite Severa} \cite{SeveraTduality}.
+For another class of $2D$ boundary theories to the $3D$ Courant algebroid $\sigma$-model see \cite{SeveraTduality}.
 
-In Section \ref{??}, we will relate these theories topological twists of $2D$ $(2,2)$ (para-)SUSY sigma models described in Section \ref{sec:toptwist} and in \cite{Kapustin:2004gv}.
+In Section \ref{sec: twist}, we will relate these theories topological twists of $2D$ $(2,2)$ (para-)SUSY sigma models described in Section \ref{sec:toptwist} closely following the methods in \cite{Kapustin:2004gv} for ordinary generalized complex geometry.
 
-All of the topological field theories in this section are of $\sigma$-model type and arise through the AKSZ formalism. 
+All of the topological field theories in this section are of $\sigma$-model type and arise through the AKSZ formalism \cite{AKSZ}. 
 Throughout, we will use symplectic $NQ$ manifold as our model for shifted symplectic geometry which is the essential ingredient in this construction.
@@
 \subsection{Courant algebroids, $3D$ TFTs, and boundary conditions}
-First, we recall the general setup of associating a $3D$ topological field theory to the data of a Courant algebroid. 
-For a reference, see \cite{Roytenberg:2002nu,??}.
 
@@
 Via the AKSZ construction, $2$-shifted symplectic spaces are the natural home for $3$-dimensional topological field theories in the BV formalism. 
-\brian{give citations here.}
+We recall the construction of the $3D$ topological field theory from the data of a Courant algebroid. 
+For other references, see \cite{Roytenberg:2002nu, Cattaneo:2009zx}.
 
-\brian{recollection on shifted symplectic NQ manifolds}
+\subsubsection{Shifted symplectic geometry} 
+\label{sec: dgman}
 
-In \cite{Roytenberg:2002nu}, it is shown how to associate a $2$-shifted symplectic NQ manifold from the data of a Courant algebroid.
+We begin by setting up our model for the theory of derived manifolds. 
+This is a well-behaved class of $NQ$ manifolds which are appropriate for setting up quantization of $\sigma$-models, see for instance \cite{CostelloSUSY}. 
+A dg manifold is a pair $\cN = (N, \sA^*_N)$ where $N$ is a smooth manifold, called the body, and $\sA^*_N$ a sheaf of graded commutative algebras over the de Rham complex $\Omega^*_N$.
+Here, $\d_N$ is a linear differential operator of degree $+1$, and together the data must satisfy the following conditions:
+\begin{itemize}
+\item[(1)] $\sA_N$ is concentrated in finitely many degrees;
+\item[(2)] For each $k$, $\sA^k_N$ is a locally free sheaf of $C^\infty_M$-modules of finite rank;
+\item[(3)] The differential $\d_N : \sA_N^* \to \sA_N^{*+1}$ is square zero differential operator making $(\sA_N , \d_N)$ into a sheaf of commutative dg algebras over the de Rham complex $\Omega^*_N$.
+\end{itemize}
+
+In particular, as a graded algebra $\sA^*_N$ is given by functions on a graded manifold $A_N$ with body $N$.
+In other words, $A_N$ is the total space of some graded vector bundle on $N$ (which is of finite rank and concentrated in finitely many degrees). 
+In the language of $NQ$ manifolds, the homological vector field $Q$ is $\d_N$.
+
+In \cite{Roytenberg:2002nu}, it is shown how to associate a $2$-shifted symplectic dg manifold from the data of a Courant algebroid.
 
@@
 
-We briefly recount the construction of the $2$-shifted symplectic NQ manifold from the data of a Courant algebroid.
+We briefly recount the equivalence between the data of a $2$-shifted symplectic NQ manifold $X_E$ and the data of a Courant algebroid $E$.
 
@@
 
-Given any Courant algebroid $E \to M$, we can have the following sequence of maps $T^* \to E \to T$, the latter is the anchor and the first map is the linear dual to the anchor.
-Using this sequence, we can define the associated $NQ$ manifold $X_E$, following \cite{Ryotenberg:2002nu}.
-The body of the NQ manifold is $M$, and the underlying graded vector bundle is given by $T^*[2] \oplus E[1]$. 
-Define the degree $+1$ vector field 
+%Given any Courant algebroid $E \to M$, we can have the following sequence of maps $T^* \xto{a^*} E \xto{a} T$ where $a$ is the anchor and $a^*$ is linear dual to the anchor.
+%Using this sequence, we can define the associated $NQ$ manifold $X_E$, following \cite{Ryotenberg:2002nu}.
+Let $E \to M$ be a vector bundle equipped with a fiberwise nondegenerate inner product $\left<-,-\right>$.
+The body of the NQ manifold is the manifold $M$, and the underlying graded manifold $X_E$ is given by $T^*[2] \oplus E[1]$.
+
+We will use coordinates $\{x^i\}$ on $M$, $\{p_i\}$ for the fiber coordinate of $T^*$, and $\{e^a\}$ for the fiber of $E$. 
+Note that $x^i$ is of degree zero, $\eta_i$ is of degree $2$, and $e^a$ is of degree $1$.
+Suppose also that $\left<e^a, e^b\right> = g^{ab}$ and let $(g_{ab})$ be the inverse to the inner product. 
+Notice, $X_E$ comes equipped with a natural $2$-shifted symplectic form, which in coordinates is 
 \[
-Q : \Gamma(M , \Sym \left(T^*[2] \oplus E[1]\right)^*) \to \Gamma(M , \Sym \left(T^*[2] \oplus E[1]\right)^*) 
+\omega_E = d x^i d p_i + g_{ab} d e^a d e^b .
 \]
-as follows: for $\psi \in \Sym^{k + \ell + 2} \left(T^*[2] \oplus E[1]\right)^*)$ and
+Denote by $\{-,-\}$ the shifted Poisson bracket corresponding to this symplectic structure. 
+An arbitrary degree $3$ function on the graded manifold $X_E$ has the form
 \[
-(\xi_0 \otimes \cdots \otimes \xi_k) \otimes (\alpha_0 \otimes \cdots \otimes \alpha_\ell) \in \Sym^{k+1}(T^*[2]) \otimes \Sym^{\ell + 1}(E[1]) 
+\Theta = p_i a_a^i (x) e^a + \frac{1}{6} f_{abc} (x) e^a e^b e^c .
 \]
-define
-\begin{align*}
-(Q \psi) ((\xi_0 \otimes \cdots \otimes \xi_k) \otimes (\alpha_0 \otimes \cdots \otimes \alpha_\ell)) = \brian{finish}
-\end{align*}
+Globally, $a = (a_a^i)$ defines a bundle map $a : E \to T$ and through the pairing the collection $(f_{abc})$ defines a bilinear map $[-,-] : E \times E \to E$. 
+It is a result of \cite{Roytenberg:2002nu} that this function satisfies $\{\Theta, \Theta\} = 0$ if and only if the data $(E, \left<-,-\right>, a, [-,-])$ has the structure of a Courant algebroid. 
+Here $a$ is the anchor map, and $[-,-]$ is the bracket.
 
-All that remains is to describe the $2$-shifted symplectic structure on the NQ manifold $X_E$. 
-This is defined via the obvious pairing between $T^*[2]$ and $T$ together with the pairing $\langle - ,- \rangle$ on $E[1]$.
-In local coordinates \brian{finish}
+%\[
+%Q : \Gamma(M , \Sym \left(T^*[2] \oplus E[1]\right)^*) \to \Gamma(M , \Sym \left(T^*[2] \oplus E[1]\right)^*) 
+%\]
+%as follows: for $\psi \in \Sym^{k + \ell + 2} \left(T^*[2] \oplus E[1]\right)^*)$ and
+%\[
+%(\xi_0 \otimes \cdots \otimes \xi_k) \otimes (\alpha_0 \otimes \cdots \otimes \alpha_\ell) \in \Sym^{k+1}(T^*[2]) \otimes \Sym^{\ell + 1}(E[1]) 
+%\]
+%define
+%\begin{align*}
+%(Q \psi) ((\xi_0 \otimes \cdots \otimes \xi_k) \otimes (\alpha_0 \otimes \cdots \otimes \alpha_\ell)) = \brian{finish}
+%\end{align*}
+%
+%All that remains is to describe the $2$-shifted symplectic structure on the NQ manifold $X_E$. 
+%This is defined via the obvious pairing between $T^*[2]$ and $T$ together with the pairing $\langle - ,- \rangle$ on $E[1]$.
+%In local coordinates \brian{finish}
 
@@
 
-\def\sA{\mathcal{A}}
-\def\d{{\rm d}}
-\def\dbar{\Bar{\partial}}
+Fix the following data:
+\begin{itemize}
+\item an {\em $n$-oriented} dg manifold $\cN = (N, (\sA^*_N, \d_\cN))$ with body a smooth oriented manifold $N$ and orientation $\mu$. 
+\item An $(n-1)$-shifted symplectic dg manifold $(X,\omega)$. 
+\end{itemize}
 
@@
 \begin{equation}\label{eqn: map}
-\cE (M, X) = {\rm Map}\left((M, (\sA^*_M, \d_M)), X\right)
+\cE (\cN, X) = {\rm Map}\left(\cN, X\right)
 \end{equation}
-where 
-\begin{itemize}
-\item $(M, (\sA^*_M, \d_M))$ is an {\em $n$-oriented} dg manifold with body a smooth oriented manifold $M$. \brian{recall $n$-orientation.}
-\item $X$ is a $(n-1)$-shifted symplectic NQ manifold. 
-\end{itemize}
+As a graded manifold, the mapping space $\cE(N,X)$ is given by the space of smooth maps between the underlying graded manifolds $A_N$ and $X$. 
+The graded manifold $\cE(\cN, X)$ is equipped with the homological vector field $\d_\cN + Q$ where $Q$ is the homological vector field on $X$.
 
-The dg manifold $(M, \sA^*_M)$ is specified by a sheaf of graded commutative algebras $\sA^*_M$ over the de Rham complex $\Omega^*_M$.
-Here, $\d_M$ is a linear differential operator of degree $+1$, and together the data must satisfy the following conditions:
-\begin{itemize}
-\item[(1)] $\sA_M$ is concentrated in finitely many degrees;
-\item[(2)] For each $k$, $\sA^k_M$ is a locally free sheaf of $C^\infty_M$-modules of finite rank;
-\item[(3)] The differential $\d_M : \sA_M^* \to \sA_M^{*+1}$ is square zero differential operator making $(\sA_M , \d_M)$ into a sheaf of commutative dg algebras over the de Rham complex $\Omega^*_M$
-\end{itemize}
-
-In particular, as a graded algebra $\sA^*_M$ is given by functions on a graded manifold $A_M$ with body $M$.
-In other words, $A_M$ is the total space of some graded vector bundle on $M$ (which is of finite rank and concentrated in finitely many degrees). 
-As a graded manifold, the mapping space $\cE(M,X)$ is given by the space of smooth maps between the underlying graded manifolds $A_M$ and $X$.
-
-\begin{Ex}
-The most important example for us will be the source dg manifold $(M, \Omega^*_M)$, that is $\sA_M = \Omega^*_M$ equipped with de Rham differential. 
-We denote this dg manifold by $M_{\rm dR}$.
-Take the dg manifold $(M, \Omega^*_M)$ where $M$ is any smooth manifold. 
-If $M$ is closed and oriented there exists an integration map
-\[
-\int_M : \Omega^*_M \to \RR[n]
-\]
-of degree $-n$ thus equipping the dg manifold $M_{\rm dR}$ with an $n$-orientation. 
-\end{Ex}
-
-\begin{Ex}
-If $M$ has a para-complex structure, $(M, \mathbf{\Omega}^{0,\bullet})$ has the structure of a dg manifold. 
-Here $\mathbf{\Omega}^{0,\bullet}$ is the para-Dolbeault complex from Section \ref{sec: paracomplex} with differential given by the para $\pd$-operator. 
-We will denote this dg manifold by $M_{\pd}$. 
-To equip the dg manifold $(M, \mathbf{\Omega}^{0,\bullet})$ with an orientation, one must fix additional data. 
-One way to do this is to assume that the para-complex manifold $M$ is equipped with a para-holomorphic volume form $\Omega_X$. \brian{is this defined earlier?}
-\end{Ex}
-
-In this case, that $\dim(M) = n$ and $X = (X, \omega_X)$ is an $(n-1)$-shifted symplectic NQ manifold, then the AKSZ construction endows the mapping space $\cE(M, X)$ in (\ref{eqn: map}) with a $(-1)$-shifted symplectic symplectic form.
+The AKSZ construction endows the mapping space $\cE(N, X)$ in (\ref{eqn: map}) with a $(-1)$-shifted symplectic symplectic form as follows, compatible with the homological vector field $\d_{\cN} + Q$ as follows.
 The fundamental observation is that the diagram
@@
 \xymatrix{
-& M \times \cE(M, X) \ar[dr]^-{{\rm ev}} \ar[dl]_-{\pi_M} & \\
-M & & X
+& N \times \cE(N, X) \ar[dr]^-{{\rm ev}} \ar[dl]_-{\pi_N} & \\
+N & & X
 }
@@
 \begin{array}{ccccc}
- \Omega^p_M & \times & \Omega^q_N & \to & \Omega^{p+q-n}_{\cE(M, X)} \\
-\displaystyle \alpha & \times & \beta & \mapsto & \displaystyle \int_M \pi_M^* \alpha \wedge {\rm ev}^* \beta 
+ \Omega^p_N& \times & \Omega^q_X & \to & \Omega^{p+q-n}_{\cE(N, X)} \\
+\displaystyle \alpha & \times & \beta & \mapsto & \displaystyle \int_N \pi_N^* \alpha \wedge {\rm ev}^* \beta 
  \end{array}
  \]
-Applied to the element $1 \times \omega_X \in \Omega^0_M \times \Omega^{\brian{??}}_X$ we obtain a $(-1)$-shifted symplectic form that we denote $\int_M \omega_X$.
+Applied to the element $1 \times \omega_X \in \Omega^0_N \times \Omega^{\brian{??}}_X$ we obtain a $(-1)$-shifted symplectic form that we denote $\int_N \omega_X$.
+
+\begin{Ex}
+The most important example for us will be the source dg manifold $(N, \Omega^*_N)$, that is $\sA_N = \Omega^*_N$ equipped with de Rham differential. 
+We denote this dg manifold by $N_{\rm dR}$.
+Take the dg manifold $(N, \Omega^*_N)$ where $N$ is any smooth manifold. 
+If $N$ is closed and oriented there exists an integration map
+\[
+\int_N : \Omega^*_N \to \RR[n]
+\]
+of degree $-n$ thus equipping the dg manifold $N_{\rm dR}$ with an $n$-orientation. 
+\end{Ex}
+
+\begin{Ex}
+If $N$ has a para-complex structure, $(N, \mathbf{\Omega}^{0,\bullet})$ has the structure of a dg manifold. 
+Here $\mathbf{\Omega}^{0,\bullet}$ is the para-Dolbeault complex from Section \ref{sec: paracomplex} with differential given by the para $\pd$-operator. 
+We will denote this dg manifold by $N_{\pd}$. 
+To equip the dg manifold $(N, \mathbf{\Omega}^{0,\bullet})$ with an orientation, one must fix additional data. 
+One way to do this is to assume that the para-complex manifold $N$ is equipped with a para-holomorphic volume form $\Omega_N$. \brian{Cite David's new section.}
+\end{Ex}
 
@@
 
-From here on, to any Courant algebroid $E$ we associate the NQ manifold $X_E$ which carries a $2$-shifted symplectic structure. 
+From here on, to any Courant algebroid $E$ on a manifold $M$ we associate the NQ manifold $X_E$ which carries a $2$-shifted symplectic structure. 
 In the case that the Courant algebroid is exact, call the associated $2$-shifted symplectic space $X_H$, where $H$ labels the Severa class.
@@
 \begin{Ex} \label{ex: exact CA}
+If $E$ is a Courant algebroid on $M$ let $X_E$ be the corresponding $2$-shifted symplectic manifold.
+We use the same coordinates as in Section \ref{sec: dgman}.
 The action functional is
 \[
-S = \int_M p_i \d x^i + \frac{1}{2} g_{ab} e^a \d e^b - a_a^i(x) p_i e^a + \frac{1}{6} c(x)_{abc} e^{a} e^b e^c .
+S = \int_N p_i \d x^i + \frac{1}{2} g_{ab}(x) e^a \d e^b - a_a^i(x) p_i e^a + \frac{1}{6} f_{abc} (x) e^{a} e^b e^c .
 \]
 \end{Ex}
+
 \subsubsection{Dirac structures and boundary conditions}
@@
 
-Suppose $M$ is a manifold with boundary, and let $\cE(M)$ denote the space of fields of a classical theory on $M$. 
-For us, $\cE(M)$ will be a mapping space of the form ${\rm Map}(M, X)$ where $X$ is shifted symplectic. 
-Let $\cE(\partial M)$ denote the restriction of the fields to the boundary of $M$. 
-For the mapping space example, this is simply the space of maps ${\rm Map}(\partial M, X)$.
+Suppose $N$ is a manifold with boundary, and let $\cE(N)$ denote the space of fields of a classical theory on $M$. 
+For us, $\cE(N)$ will be a mapping space of the form ${\rm Map}(M, X)$ where $X$ is shifted symplectic. 
+Let $\cE(\partial N)$ denote the restriction of the fields to the boundary of $N$. 
+For the mapping space example, this is simply the space of maps ${\rm Map}(\partial N, X)$.
 
-In general, when $M$ is not closed, the pairing defined by the AKSZ construction will not endow $\cE(M)$ will with $(-1)$-shifted symplectic structure. 
-However, the space $\cE(\partial M)$ does carry a natural ordinary ($0$-shifted) symplectic structure from the restriction of the pairing defined on $\cE(M)$. 
-Morever, the natural restriction map $\cE(M) \to \cE(\partial M)$ is a Lagrangian morphism in the sense of \cite{PTVV}.
+In general, when $N$ is not closed, the pairing defined by the AKSZ construction will not endow $\cE(N)$ will with $(-1)$-shifted symplectic structure. 
+However, the space $\cE(\partial N)$ does carry a natural ordinary ($0$-shifted) symplectic structure from the restriction of the pairing defined on $\cE(N)$. 
+Morever, the natural restriction map $\cE(N) \to \cE(\partial N)$ is a Lagrangian morphism in the sense of \cite{PTVV}.
 
@@
 
-A boundary condition is the choice of an additional Lagrangian subspace $\cL$ of $\cE(\partial M)$.
-The intersection $\cL \times_{\cE(M)} \cE(\partial M)$ of the two Lagrangians $\cL$ and $\cE(\partial M)$
+A boundary condition is the choice of an additional Lagrangian subspace $\cL$ of $\cE(\partial N)$.
+The intersection $\cL \times_{\cE(N)} \cE(\partial N)$ of the two Lagrangians $\cL$ and $\cE(\partial N)$
 
@@
 \begin{Ex}
-Suppose $(X, \pi)$ is a Poisson manifold. 
+Suppose $(M, \pi)$ is a Poisson manifold. 
 Then consider the graph of $\pi$ as a Lagrangian subbundle of $\TT$:
@@
 By the Jacobi identity, this subbundle is integrable and so determines a Dirac structure. 
-If we place the 3D AKSZ theory with target the Courant algebroid $\TT$ on $M^3$ with $\partial M = \Sigma$, the boundary condition determined by this Dirac structure is equivalent to the Poisson $\sigma$-model.
-\brian{reference}
+If we place the 3D AKSZ theory with target the Courant algebroid $\TT$ on $N^3$ with $\partial N = \Sigma$, the boundary condition determined by this Dirac structure is equivalent to the Poisson $\sigma$-model on $\Sigma$, see \cite{KSSdirac}, for instance.
 \end{Ex}
@@
 
-\brian{Recall that a generalized (para-)complex structure $\JJ$ defines a Dirac structure in $\TT$, and hence a Lagrangian inside of the $2$-shifted symplectic space $\XX_H$.  
-%More generally, if $\JJ$ is a generalized complex structure in an arbitrary Courant algebroid $E$, then we obtain a $2$-shifted Lagrangian inside of the $2$-shifted symplectic space $\XX_E$. 
-This Lagrangian then defines a boundary condition for the three-dimensional AKSZ theory. }
+Let $M$ be a manifold.
+Throughout this section we will only consider the standard Dorfman Courant algebroid $X_H$ on $M$, possibly twisted by an $H$-flux.
+By Theorem \ref{thm:pairofdirac}, the choice of a GpC structure $\KK$ determines a pair of transversal Dirac structures $L$ and $\tilde{L}$ on $M$ given by the positive and negative eigenbundles of $\KK$.
+In particular, $L$ determines a Lagrangian in the shifted symplectic space $X_{H}$. 
+This Lagrangian then defines a boundary condition for the three-dimensional AKSZ theory.
+Thus, we see that any GpC structure $\KK$ defines a 2D TFT living at the boundary of the 3D theory.
 
-By this general construction, we see that any GpC structure $\KK$ defines a 2D TFT as a boundary theory to the 3D theory whose target is the standard Dorfman Courant algebroid.
+\begin{remark}
+More generally, if $\KK$ is a generalized complex structure in an arbitrary Courant algebroid $E$, then we obtain a $2$-shifted Lagrangian inside of the $2$-shifted symplectic space $X_E$. 
+\end{remark}
 
-Recall that Theorem \ref{thm:pairofdirac} tells us that the choice of a GpC structure $\KK$ determines a pair of tansversal Dirac structures $L$ and $\tilde{L}$. 
 Moreover, by Proposition \ref{prop:dirac_Liealg} the eigenbundle $L$ has the structure of a Lie algebroid compatible with the anchor and Dorfman bracket on $\TT$.
@@
 
-\subsubsection*{Trivial GpC structure}
+\subsubsection*{Trivial GpC structures}
+
+Let $M$ be a smooth manifold.
+Consider the case of the trivial generalized para-complex structure on $M$ defined by
+\begin{align*}
+\KK_0=
+\begin{pmatrix}
+\id & 0 \\
+0 & -\id
+\end{pmatrix}.
+\end{align*}
+The positive eigenbundle is simply $L = T$.
+
+\brian{Trivial Poisson $\sigma$-model, AKA $BF$ theory.}
 
@@
 Another special case of a generalized para-complex structure is para-complex structure.
+In this case, the generalized AKSZ theory specializes to the following para-complex version of the $B$-model.
 
@@
 
+The classical BRST cohomology of the para-B-model is isomorphic to the cohomology of para-holomorphic polyvector fields on the target para-complex manifold $X$.
+To see the equivalence of this definition with the generalized description of the AKSZ model, note that the Lie algebroid $L$ \brian{finish}
+
+\brian{discuss anomalies. Para-holomorphic volume form.}
+
 \brian{Discuss Si's work on perturbative quantization}
+
+\brian{Case of para structure on $M \times M$. Two copies of $BF$ theory.}
 
@@
 }
-
- \brian{discuss anomalies}
 
@@
 
+\bibliographystyle{alpha}
+\bibliography{mybib}
 \end{document}
 
-\section{The AKSZ formalism and 3d TFT}
-\def\fg{\mathfrak{g}}
-In this section we will show how to associate $2D$ topological theories to a generalized (para-)complex structure and relate them to the topological twists of $2D$ $(2,2)$ (para-)SUSY sigma models described in Section \ref{sec:toptwist} and in \cite{Kapustin:2004gv}.
-The key to our construction is to realize the data of a G(p)C structure in terms of its eigenbundles, which are Dirac structures $L$ in the Courant algebroid $\TT$. 
-Via the AKSZ construction \cite{AKSZ}, this correspondence translates into the statement that the Dirac structure $L$ defines a topological boundary theory of a $3D$ topological theory defined by the Courant algebroid $\TT$ \cite{Roytenberg:2002nu}.
-
-Throughout, we will use symplectic $NQ$ manifold as our model for shifted symplectic geometry. 
-We will recall the general setup of associating a $3D$ topological field theory to the data of a Courant algebroid. 
-For a reference, see \cite{Roytenberg:2002nu,??}.
-
-\subsection{Courant algebroids, $3D$ TFTs, and boundary conditions}
-From the point of view of topological field theory, Courant algebroids are important because they provide geometric examples of $2$-shifted symplectic spaces. 
-Via the AKSZ construction, $2$-shifted symplectic spaces are the natural home for $3$-dimensional topological field theories in the BV formalism. 
-\brian{give citations here.}
-
-In \cite{Roytenberg:2002nu}, it is shown how to associate a $2$-shifted symplectic NQ manifold from the data of a Courant algebroid.
-
-\begin{theorem}[\cite{Roytenberg:2002nu}]
-There is an equivalence between isomorphism classes of $2$-shifted symplectic NQ manifolds with body $M$ and isomorphism classes of Courant algebroids on $M$.
-\end{theorem}
-
-We briefly recall this construction.
-
-Recall, the data of a Courant algebroid on a manifold $M$ is a vector bundle $E$, whose sheaf of sections we denote $\cE$, together with a nondegenerate symmetric bilinear pairing $\langle -, -\rangle : \cE \otimes \cE \to C^\infty(M)$ , an anchor map $a : E \to T M$, and a bilinear operator
-\[
-[-,-] : \cE \times \cE \to \cE
-\]
-called the Courant-Dorfman bracket. 
-\brian{spell out properties, find a good reference}
-Denote by $a^* : T^* M \to E^*$ the bundle map dual to $a$.
-
-To every Courant algebroid we can define the following sequence of vector bundles on $M$
-\[
-T^*M \xto{a^*} E \xto{a} TM .
-\]
-A Courant algebroid is called {\em exact} if this sequence of bundles is exact.
-
-\def\Sym{{\rm Sym}}
-
-Using this sequence, we can define the associated $NQ$ manifold $X_E$, following \cite{Ryotenberg:2002nu}.
-The body of the NQ manifold is $M$, and the underlying graded vector bundle is given by $T^*[2] \oplus E[1]$. 
-Define the degree $+1$ vector field 
-\[
-Q : \Gamma(M , \Sym \left(T^*[2] \oplus E[1]\right)^*) \to \Gamma(M , \Sym \left(T^*[2] \oplus E[1]\right)^*) 
-\]
-as follows: for $\psi \in \Sym^{k + \ell + 2} \left(T^*[2] \oplus E[1]\right)^*)$ and
-\[
-(\xi_0 \otimes \cdots \otimes \xi_k) \otimes (\alpha_0 \otimes \cdots \otimes \alpha_\ell) \in \Sym^{k+1}(T^*[2]) \otimes \Sym^{\ell + 1}(E[1]) 
-\]
-define
-\begin{align*}
-(Q \psi) ((\xi_0 \otimes \cdots \otimes \xi_k) \otimes (\alpha_0 \otimes \cdots \otimes \alpha_\ell)) = \brian{finish}
-\end{align*}
-
-All that remains is to describe the $2$-shifted symplectic structure on the NQ manifold $X_E$. 
-This is defined via the obvious pairing between $T^*[2]$ and $T$ together with the pairing $\langle - ,- \rangle$ on $E[1]$.
-In local coordinates \brian{finish}
-
-The simplest type of Courant algebroid is one over a point.
-
-\begin{Ex}\label{ex: cs}
-Any Lie algebra $\fg$ together with a non-degenerate invariant pairing defines a $2$-shifted symplectic structure on the graded manifold $\fg[1]$ living over a point. 
-The dg algebra of functions is the Chevalley-Eilenberg cochain complex computing Lie algebra cohomology $C^*(\fg)$. 
-All such $2$-symplectic NQ manifolds over a point are of this form. 
-%The resulting AKSZ theory is Chern-Simons theory. 
-\end{Ex}
-
-\subsubsection*{The $2$-shifted symplectic space of an exact Courant Algebroid}
-
-We recall the description of the $2$-shifted symplectic NQ manifold $X_E$ associated to an exact Courant algebroid $E$.
-Of course, as a vector bundle $E = \TT$, and hence as a graded manifold $X_E$ is of the form $T^*[2] T[1] M$.
-Concretely, the coordinates on this manifold are given by $(x^i,v^a,p_i,\mu_a)_{i,a=1\cdots n}$, where $x^i$ are the usual coordinates on $M$ with degree $0$, $v^a$ are the corresponding ``velocities'', i.e.
+%\section{The AKSZ formalism and 3d TFT}
+%\def\fg{\mathfrak{g}}
+%In this section we will show how to associate $2D$ topological theories to a generalized (para-)complex structure and relate them to the topological twists of $2D$ $(2,2)$ (para-)SUSY sigma models described in Section \ref{sec:toptwist} and in \cite{Kapustin:2004gv}.
+%The key to our construction is to realize the data of a G(p)C structure in terms of its eigenbundles, which are Dirac structures $L$ in the Courant algebroid $\TT$. 
+%Via the AKSZ construction \cite{AKSZ}, this correspondence translates into the statement that the Dirac structure $L$ defines a topological boundary theory of a $3D$ topological theory defined by the Courant algebroid $\TT$ \cite{Roytenberg:2002nu}.
+%
+%Throughout, we will use symplectic $NQ$ manifold as our model for shifted symplectic geometry. 
+%We will recall the general setup of associating a $3D$ topological field theory to the data of a Courant algebroid. 
+%For a reference, see \cite{Roytenberg:2002nu,??}.
+%
+%\subsection{Courant algebroids, $3D$ TFTs, and boundary conditions}
+%From the point of view of topological field theory, Courant algebroids are important because they provide geometric examples of $2$-shifted symplectic spaces. 
+%Via the AKSZ construction, $2$-shifted symplectic spaces are the natural home for $3$-dimensional topological field theories in the BV formalism. 
+%\brian{give citations here.}
+%
+%In \cite{Roytenberg:2002nu}, it is shown how to associate a $2$-shifted symplectic NQ manifold from the data of a Courant algebroid. 
+%
+%\begin{theorem}[\cite{Roytenberg:2002nu}]
+%There is an equivalence between isomorphism classes of $2$-shifted symplectic NQ manifolds with body $M$ and isomorphism classes of Courant algebroids on $M$.
+%\end{theorem}
+%
+%We briefly recall this construction. 
+%
+%Recall, the data of a Courant algebroid on a manifold $M$ is a vector bundle $E$, whose sheaf of sections we denote $\cE$, together with a nondegenerate symmetric bilinear pairing $\langle -, -\rangle : \cE \otimes \cE \to C^\infty(M)$ , an anchor map $a : E \to T M$, and a bilinear operator
+%\[
+%[-,-] : \cE \times \cE \to \cE
+%\]
+%called the Courant-Dorfman bracket. 
+%\brian{spell out properties, find a good reference}
+%Denote by $a^* : T^* M \to E^*$ the bundle map dual to $a$. 
+%
+%To every Courant algebroid we can define the following sequence of vector bundles on $M$
+%\[
+%T^*M \xto{a^*} E \xto{a} TM .
+%\]
+%A Courant algebroid is called {\em exact} if this sequence of bundles is exact. 
+%
+%\def\Sym{{\rm Sym}}
+%
+%Using this sequence, we can define the associated $NQ$ manifold $X_E$, following \cite{Ryotenberg:2002nu}.
+%The body of the NQ manifold is $M$, and the underlying graded vector bundle is given by $T^*[2] \oplus E[1]$. 
+%Define the degree $+1$ vector field 
+%\[
+%Q : \Gamma(M , \Sym \left(T^*[2] \oplus E[1]\right)^*) \to \Gamma(M , \Sym \left(T^*[2] \oplus E[1]\right)^*) 
+%\]
+%as follows: for $\psi \in \Sym^{k + \ell + 2} \left(T^*[2] \oplus E[1]\right)^*)$ and
+%\[
+%(\xi_0 \otimes \cdots \otimes \xi_k) \otimes (\alpha_0 \otimes \cdots \otimes \alpha_\ell) \in \Sym^{k+1}(T^*[2]) \otimes \Sym^{\ell + 1}(E[1]) 
+%\]
+%define
+%\begin{align*}
+%(Q \psi) ((\xi_0 \otimes \cdots \otimes \xi_k) \otimes (\alpha_0 \otimes \cdots \otimes \alpha_\ell)) = \brian{finish}
+%\end{align*}
+%
+%All that remains is to describe the $2$-shifted symplectic structure on the NQ manifold $X_E$. 
+%This is defined via the obvious pairing between $T^*[2]$ and $T$ together with the pairing $\langle - ,- \rangle$ on $E[1]$.
+%In local coordinates \brian{finish}
+%
+%The simplest type of Courant algebroid is one over a point.
+%
+%\begin{Ex}\label{ex: cs}
+%Any Lie algebra $\fg$ together with a non-degenerate invariant pairing defines a $2$-shifted symplectic structure on the graded manifold $\fg[1]$ living over a point. 
+%The dg algebra of functions is the Chevalley-Eilenberg cochain complex computing Lie algebra cohomology $C^*(\fg)$. 
+%All such $2$-symplectic NQ manifolds over a point are of this form. 
+%%The resulting AKSZ theory is Chern-Simons theory. 
+%\end{Ex}
+%
+%\subsubsection*{The $2$-shifted symplectic space of an exact Courant Algebroid}
+%
+%We recall the description of the $2$-shifted symplectic NQ manifold $X_E$ associated to an exact Courant algebroid $E$.
+%Of course, as a vector bundle $E = \TT$, and hence as a graded manifold $X_E$ is of the form $T^*[2] T[1] M$.
+%Concretely, the coordinates on this manifold are given by $(x^i,v^a,p_i,\mu_a)_{i,a=1\cdots n}$, where $x^i$ are the usual coordinates on $M$ with degree $0$, $v^a$ are the corresponding ``velocities'', i.e.
 the fibre coordinates on $T[1]M$ with a degree $1$, and $p_i,\mu_a$ are the momenta corresponding to $x^i,v^a$ with degrees $2,1$, respectively.
 The canonical symplectic form
-\begin{align*}
-\Omega= dx^idp_i+dv^ad\mu_a,
-\end{align*}
-is then of degree $2$.
+%\begin{align*}
+%\Omega= dx^idp_i+dv^ad\mu_a,
+%\end{align*}
+%is then of degree $2$.
 $T^*[2]T[1]M$ is the minimal symplectic realization of the shifted bundle $(\TT)[1]M$, which is recovered by setting $p_i=0$.
 The symmetric part of $\Omega$ represents the pairing $\lara$ on $(\TT)M$; this is because we can identify $d\mu_a\leftrightarrow \p_i$ and $dv^a\leftrightarrow dx^i$
-
-\brian{Severa classification}
-
-\begin{theorem}\label{thm: severa}
-The set of isomorphism classes of exact Courant algebroids is a torsor for $H^3(X)$. 
-\end{theorem}
-
-\subsubsection*{The Poisson Courant algebroid}
-
-\brian{Both real and holomorphic versions}
-
-\subsubsection{The AKSZ theory associated to a Courant algebroid}
-
-To any Courant algebroid $E$, we can associate an NQ manifold $X_E$ which carries a $2$-shifted symplectic structure that we denote by $\omega_E$. 
-In the case that the Courant algebroid is exact, call the associated $2$-shifted symplectic space $X_H$, where $H$ labels the Severa class.
-
-\def\sA{\mathcal{A}}
-\def\d{{\rm d}}
-\def\dbar{\Bar{\partial}}
-
-The starting point of the AKSZ construction is the mapping space
-\[
-{\rm Map}\left((M, (\sA^*_M, \d_M)), X_E\right)
-\]
-where $(M, (\sA^*_M, \d_M))$ is a dg manifold with body a smooth oriented manifold $M$. 
-That is, $\sA^*_M$ is a sheaf of graded commutative algebras over the de Rham complex $\Omega^*_M$ and $\d_M$ is a linear operator of degree $+1$ satisfying:
-\begin{itemize}
-\item[(1)] $\sA_M$ is concentrated in finitely many degrees;
-\item[(2)] For each $k$, $\sA^k_M$ is a locally free sheaf of $C^\infty_M$-modules of finite rank;
-\item[(3)] The differential $\d_M : \sA_M^* \to \sA_M^{*+1}$ is square zero differential operator making $(\sA_M , \d_M)$ into a sheaf of commutative dg algebras over the de Rham complex $\Omega^*_M$
-\end{itemize}
-
-\begin{Ex}
-The most important example for us will be the source dg manifold $(M, \Omega^*_M)$, that is $\sA_M = \Omega^*_M$ with de Rham differential. 
-We denote this dg manifold by $M_{\rm dR}$.
-\end{Ex}
-
-\begin{Ex}
-If $M$ has a para-complex structure, then $(M, \Omega^{0,*}_M)$ has the structure of a dg manifold with differential given by the para $\dbar$-operator. 
-\brian{David, is this consistent notation?}
-We will denote this dg manifold by $M_{p \dbar}$. 
-\end{Ex}
-
-\begin{Ex}
-If $\fg$ is a Lie algebra equipped with a non-degenerate invariant pairing, and $X_E = \fg[1]$ as in Example \ref{ex: cs}, then the AKSZ theory (whose target base manifold is a point) is equivalent to Chern-Simons theory on $M$.
-\end{Ex}
-
-\subsubsection{Dirac structures and boundary conditions}
-
-\subsection{Two dimensional TFT from GpC structures}
-\label{sec:GpC_AKSZ}
-\brian{Recall that a generalized (para-)complex structure $\JJ$ defines a Dirac structure in $\TT$, and hence a Lagrangian inside of the $2$-shifted symplectic space $\XX_H$.  
-%More generally, if $\JJ$ is a generalized complex structure in an arbitrary Courant algebroid $E$, then we obtain a $2$-shifted Lagrangian inside of the $2$-shifted symplectic space $\XX_E$. 
-This Lagrangian then defines a boundary condition for the three-dimensional AKSZ theory. }
-
-\subsubsection*{Trivial GpC structure}
-
-\subsubsection*{(Real) Poisson $\sigma$-model}
-
-\subsubsection*{Para-complex $A/B$-models}
-
-We point out two special cases of the above general construction.
-
-\brian{The $A$-model is the usual thing.}
-
-\begin{Def}
-The {\bf para-complex $B$-model} with source a closed Riemann surface $\Sigma$ and target a para-complex manifold $X$ is the AKSZ theory with source the de Rham space $\Sigma_{\rm dR}$ and target the $1$-shifted symplectic space $T^*[1] X_{p \dbar}$:
-\[
-{\rm Map}\left(\Sigma_{dR}, T^*[1]  X_{p \dbar}\right) .
-\]
-\end{Def}
-
-\brian{Discuss Si's work on perturbative quantization}
-
-\hrulefill
-
-\brian{***para Kahler example, **example where the paracomplex structures commute but are not equal (this is where people see ``twisted chiral"), para version of T-duality, **Poisson $\sigma$-model, going back and forth between generalized (para) complex.
-}
-
- \brian{discuss anomalies}
-
-\subsection{Para holomorphic variants}
-
-So far, in each of the $\sigma$-models we have discussed in the AKSZ formalism, the fields have depended only topologically on the source Riemann surface. 
-There are closely related $\sigma$-models which depending {\em para-holomorphically} on the source Riemann surface that we briefly discuss.
+%
+%\brian{Severa classification}
+%
+%\begin{theorem}\label{thm: severa}
+%The set of isomorphism classes of exact Courant algebroids is a torsor for $H^3(X)$. 
+%\end{theorem}
+%
+%\subsubsection*{The Poisson Courant algebroid}
+%
+%\brian{Both real and holomorphic versions}
+%
+%\subsubsection{The AKSZ theory associated to a Courant algebroid}
+%
+%To any Courant algebroid $E$, we can associate an NQ manifold $X_E$ which carries a $2$-shifted symplectic structure that we denote by $\omega_E$. 
+%In the case that the Courant algebroid is exact, call the associated $2$-shifted symplectic space $X_H$, where $H$ labels the Severa class. 
+%
+%\def\sA{\mathcal{A}}
+%\def\d{{\rm d}}
+%\def\dbar{\Bar{\partial}}
+%
+%The starting point of the AKSZ construction is the mapping space
+%\[
+%{\rm Map}\left((M, (\sA^*_M, \d_M)), X_E\right)
+%\]
+%where $(M, (\sA^*_M, \d_M))$ is a dg manifold with body a smooth oriented manifold $M$. 
+%That is, $\sA^*_M$ is a sheaf of graded commutative algebras over the de Rham complex $\Omega^*_M$ and $\d_M$ is a linear operator of degree $+1$ satisfying:
+%\begin{itemize}
+%\item[(1)] $\sA_M$ is concentrated in finitely many degrees;
+%\item[(2)] For each $k$, $\sA^k_M$ is a locally free sheaf of $C^\infty_M$-modules of finite rank;
+%\item[(3)] The differential $\d_M : \sA_M^* \to \sA_M^{*+1}$ is square zero differential operator making $(\sA_M , \d_M)$ into a sheaf of commutative dg algebras over the de Rham complex $\Omega^*_M$
+%\end{itemize}
+%
+%\begin{Ex}
+%The most important example for us will be the source dg manifold $(M, \Omega^*_M)$, that is $\sA_M = \Omega^*_M$ with de Rham differential. 
+%We denote this dg manifold by $M_{\rm dR}$.
+%\end{Ex}
+%
+%\begin{Ex}
+%If $M$ has a para-complex structure, then $(M, \Omega^{0,*}_M)$ has the structure of a dg manifold with differential given by the para $\dbar$-operator. 
+%\brian{David, is this consistent notation?}
+%We will denote this dg manifold by $M_{p \dbar}$. 
+%\end{Ex}
+%
+%\begin{Ex}
+%If $\fg$ is a Lie algebra equipped with a non-degenerate invariant pairing, and $X_E = \fg[1]$ as in Example \ref{ex: cs}, then the AKSZ theory (whose target base manifold is a point) is equivalent to Chern-Simons theory on $M$.
+%\end{Ex}
+%
+%\subsubsection{Dirac structures and boundary conditions}
+%
+%\subsection{Two dimensional TFT from GpC structures}
+%\label{sec:GpC_AKSZ}
+%\brian{Recall that a generalized (para-)complex structure $\JJ$ defines a Dirac structure in $\TT$, and hence a Lagrangian inside of the $2$-shifted symplectic space $\XX_H$.  
+%%More generally, if $\JJ$ is a generalized complex structure in an arbitrary Courant algebroid $E$, then we obtain a $2$-shifted Lagrangian inside of the $2$-shifted symplectic space $\XX_E$. 
+%This Lagrangian then defines a boundary condition for the three-dimensional AKSZ theory. }
+%
+%\subsubsection*{Trivial GpC structure}
+%
+%\subsubsection*{(Real) Poisson $\sigma$-model}
+%
+%\subsubsection*{Para-complex $A/B$-models}
+%
+%We point out two special cases of the above general construction. 
+%
+%\brian{The $A$-model is the usual thing.}
+%
+%\begin{Def}
+%The {\bf para-complex $B$-model} with source a closed Riemann surface $\Sigma$ and target a para-complex manifold $X$ is the AKSZ theory with source the de Rham space $\Sigma_{\rm dR}$ and target the $1$-shifted symplectic space $T^*[1] X_{p \dbar}$:
+%\[
+%{\rm Map}\left(\Sigma_{dR}, T^*[1]  X_{p \dbar}\right) .
+%\]
+%\end{Def}
+%
+%\brian{Discuss Si's work on perturbative quantization}
+%
+%\hrulefill
+%
+%\brian{***para Kahler example, **example where the paracomplex structures commute but are not equal (this is where people see ``twisted chiral"), para version of T-duality, **Poisson $\sigma$-model, going back and forth between generalized (para) complex.
+%}  
+%
+% \brian{discuss anomalies}
+%
+%\subsection{Para holomorphic variants}
+%
+%So far, in each of the $\sigma$-models we have discussed in the AKSZ formalism, the fields have depended only topologically on the source Riemann surface. 
+%There are closely related $\sigma$-models which depending {\em para-holomorphically} on the source Riemann surface that we briefly discuss.

### 2020-01-13 AKSZ.tex
AKSZ

@@
 \newcommand{\cN}{\mathcal{N}}
+\newcommand{\cO}{\mathcal{O}}
 %----------------------------------------
@@
 In this section we will show how to associate a class of $2D$ topological field theories to generalized para-complex structures.
-The construction closely follows the relationship between ordinary (non-para) generalized complex structures \cite{Gualtieri:2003dx} and $2D$ topological field theories developed in \cite{Cattaneo:2009zx, Pestun:2006rj} \btd{Please add any more references you think fit.}
+The construction closely follows the relationship between ordinary (non-para) generalized complex structures \cite{Gualtieri:2003dx} and $2D$ topological field theories developed in \cite{Cattaneo:2009zx, Pestun:2006rj}.
+For another class of $2D$ boundary theories to the $3D$ Courant algebroid $\sigma$-model see \cite{SeveraTduality}. \btd{Please add any more references you think fit.}
 
-The prescription of defining the $2D$ topological theory associated to a GpC structure starts with a $3D$ topological field theory which is defined for any manifold $M$. 
-More generally, this $3D$ theory can be defined for any {\em Courant algebroid} on $M$ \cite{Roytenberg:2002nu}, but for most examples we will only consider the standard exact Courant algebroid (or twisted versions) defined by the Dorfman bracket.
+For us, the prescription of defining the $2D$ topological theory associated to a GpC structure starts with a $3D$ topological field theory which is defined for any manifold $M$. 
+More generally, this $3D$ theory can be defined for any Courant algebroid on $M$ \cite{Roytenberg:2002nu}, but for most examples we will only consider the standard exact Courant algebroid (or twisted versions) defined by the Dorfman bracket.
 The key to our construction is to realize the data of a G(p)C structure in terms of its eigenbundles, which are Dirac structures $L$ in the Courant algebroid $\TT$.
@@
 Via the AKSZ construction \cite{AKSZ}, this correspondence translates into the statement that the Dirac structure $L$ defines a topological boundary theory of the $3D$ topological theory defined by the standard Courant algebroid.
-For another class of $2D$ boundary theories to the $3D$ Courant algebroid $\sigma$-model see \cite{SeveraTduality}.
+In turn, we will directly describe the BRST observables of the $2D$ theory in terms of the cohomology of the Lie algebroid $L$.
 
@@
 All of the topological field theories in this section are of $\sigma$-model type and arise through the AKSZ formalism \cite{AKSZ}. 
-Throughout, we will use symplectic $NQ$ manifold as our model for shifted symplectic geometry which is the essential ingredient in this construction.
-
+Throughout, we will use the formalism of dg manifolds and shifted symplectic geometry. 
 %Later we will use the idea of Lagrangian intersections \brian{PTVV, ButsonYoo, Costello,...}.
@@
 We begin by setting up our model for the theory of derived manifolds. 
-This is a well-behaved class of $NQ$ manifolds which are appropriate for setting up quantization of $\sigma$-models, see for instance \cite{CostelloSUSY}. 
-A dg manifold is a pair $\cN = (N, \sA^*_N)$ where $N$ is a smooth manifold, called the body, and $\sA^*_N$ a sheaf of graded commutative algebras over the de Rham complex $\Omega^*_N$.
-Here, $\d_N$ is a linear differential operator of degree $+1$, and together the data must satisfy the following conditions:
+For us, this is a well-behaved class of $NQ$ manifolds which are appropriate for setting up quantization of $\sigma$-models, see for instance \cite{CostelloSUSY}. 
+A dg manifold is a pair $\cN = (N, \sA^*_\cN)$ where $N$ is a smooth manifold, called the body, and $\sA^*_\cN$ a sheaf of graded commutative algebras over the de Rham complex $\Omega^*_N$.
+Here, $\d_\cN$ is a linear differential operator of degree $+1$, and together the data must satisfy the following conditions:
 \begin{itemize}
-\item[(1)] $\sA_N$ is concentrated in finitely many degrees;
-\item[(2)] For each $k$, $\sA^k_N$ is a locally free sheaf of $C^\infty_M$-modules of finite rank;
-\item[(3)] The differential $\d_N : \sA_N^* \to \sA_N^{*+1}$ is square zero differential operator making $(\sA_N , \d_N)$ into a sheaf of commutative dg algebras over the de Rham complex $\Omega^*_N$.
+\item[(1)] $\sA_\cN$ is concentrated in finitely many degrees;
+\item[(2)] For each $k$, $\sA^k_\cN$ is a locally free sheaf of $C^\infty_N$-modules of finite rank;
+\item[(3)] The differential $\d_N : \sA_\cN^* \to \sA_\cN^{*+1}$ is square zero differential operator making $(\sA_\cN , \d_\cN)$ into a sheaf of commutative dg algebras over the de Rham complex $\Omega^*_N$.
 \end{itemize}
 
-In particular, as a graded algebra $\sA^*_N$ is given by functions on a graded manifold $A_N$ with body $N$.
-In other words, $A_N$ is the total space of some graded vector bundle on $N$ (which is of finite rank and concentrated in finitely many degrees). 
-In the language of $NQ$ manifolds, the homological vector field $Q$ is $\d_N$.
+In particular, as a graded algebra $\sA^*_\cN$ is given by functions on the total space of some graded vector bundle $A_\cN$ on $N$ (which is of finite rank and concentrated in finitely many degrees).
+In the language of $NQ$ manifolds, the homological vector field defining the $Q$-structure is $\d_\cN$.
 
-In \cite{Roytenberg:2002nu}, it is shown how to associate a $2$-shifted symplectic dg manifold from the data of a Courant algebroid.
+\brian{Symplectic form}
+
+A striking result of \cite{Roytenberg:2002nu} classifies all $2$-shifted symplectic spaces in terms of Courant algebroids.
 
@@
 
-We briefly recount the equivalence between the data of a $2$-shifted symplectic NQ manifold $X_E$ and the data of a Courant algebroid $E$.
+We briefly recount the equivalence between the data of a $2$-shifted symplectic dg manifold and the data of a Courant algebroid.
 
@@
 Let $E \to M$ be a vector bundle equipped with a fiberwise nondegenerate inner product $\left<-,-\right>$.
-The body of the NQ manifold is the manifold $M$, and the underlying graded manifold $X_E$ is given by $T^*[2] \oplus E[1]$.
+The body of the dg manifold is the manifold $M$, and the underlying graded manifold $X_E$ is given by $T^*M [2] \oplus E[1]$.
 
@@
 
-From here on, to any Courant algebroid $E$ on a manifold $M$ we associate the NQ manifold $X_E$ which carries a $2$-shifted symplectic structure. 
+From here on, to any Courant algebroid $E$ on a manifold $M$ we associate the dg manifold $X_E$ which carries a $2$-shifted symplectic structure. 
 In the case that the Courant algebroid is exact, call the associated $2$-shifted symplectic space $X_H$, where $H$ labels the Severa class.
@@
 The dg algebra of functions is the Chevalley-Eilenberg cochain complex computing Lie algebra cohomology $C^*(\fg)$. 
-All such $2$-symplectic NQ manifolds over a point are of this form. 
+All such $2$-symplectic dg manifolds over a point are of this form. 
 %The resulting AKSZ theory is Chern-Simons theory. 
@@
 Throughout this section we will only consider the standard Dorfman Courant algebroid $X_H$ on $M$, possibly twisted by an $H$-flux.
-By Theorem \ref{thm:pairofdirac}, the choice of a GpC structure $\KK$ determines a pair of transversal Dirac structures $L$ and $\tilde{L}$ on $M$ given by the positive and negative eigenbundles of $\KK$.
+By Theorem \ref{thm:pairofdirac}, the choice of a GpC structure $\KK$ determines a pair of transversal Dirac structures $L_{\KK}$ and $\tilde{L}_{\KK}$ on $M$ given by the positive and negative eigenbundles of $\KK$.
 In particular, $L$ determines a Lagrangian in the shifted symplectic space $X_{H}$. 
@@
 Thus, we see that any GpC structure $\KK$ defines a 2D TFT living at the boundary of the 3D theory. 
+By Proposition \ref{prop:dirac_Liealg} the eigenbundle $L_\KK$ has the structure of a Lie algebroid compatible with the anchor and Dorfman bracket on $\TT$.
 
@@
 
-Moreover, by Proposition \ref{prop:dirac_Liealg} the eigenbundle $L$ has the structure of a Lie algebroid compatible with the anchor and Dorfman bracket on $\TT$.
+Before stating the main result of this section, we recall the following general construction.
+Given any Lie algebroid $L$ on $M$ consider the graded manifold $L[1]$ with body $M$. 
+Functions on this graded manifold are given by sections of the graded vector bundle
+\[
+\cO(L[1]) = \bigoplus_{k \geq 0} \wedge^k L [-k] .
+\]
+Here, $\wedge^k(L)$ is placed in cohomological degree $+k$. 
+There is square-zero derivation $\d_L$ of degree $+1$ on $\cO(L[1])$ defined by the following rule. 
+If $\varphi$ is a section of $\wedge^k L$, then
+\begin{align*}
+\left( \d_L \varphi \right) (\ell_0, \ldots, \ell_k) & = \sum_{i = 0}^k (-1)^i a (\ell_i) \varphi(\ell_0, \ldots, \Hat{\ell_i}, \ldots, \ell_k) \\ & + \sum_{i < j} (-1)^{i+j} \varphi([\ell_i, \ell_j] , \ell_0 \cdots, \Hat{\ell_i}, \ldots, \Hat{\ell_j}, \ldots, \ell_k)
+\end{align*}
+Here $a : L \to T_M$ is the anchor and $[-,-]$ is the bracket on $L$. 
+In other words $\d_L$ is a homological vector field on $L$, which can be written in coordinates:
+\[
+\d_L = a_a^i \theta^a \frac{\partial}{\partial x^i} + f_{ab}^c \theta^a \theta^b \frac{\partial}{\partial \theta^c}
+\]
+where $\{x^i\}$ are the coordinates on $M$ and $\{\theta^a\}$ are the coordinates for the fiber of $L[1]$.
+
+Equipped with this differential, the cohomology
+\[
+H^*( \cO(L[1]), \d_L )
+\]
+is called the Lie algebroid cohomology of $L$.
 
 \begin{proposition}
-The BRST cohomology of the local observables of the 2D TFT determined by the GpC structure $\KK$ is equivalent to the Lie algebroid cohomology of $L$. 
+Let $\KK$ be a generalized para-complex structure on $M$ and $L_{\KK}$ the corresponding positive eigenbundle. 
+The BRST cohomology of the local observables of the 2D TFT determined by $\KK$ is equivalent to the Lie algebroid cohomology of $L_{\KK}$. 
 \end{proposition}
@@
 \end{align*}
-The positive eigenbundle is simply $L = T$.
+The positive eigenbundle is simply $L_\KK = T$ and the resulting Lie algebroid structure is the trivial one with zero anchor.
 
@@
 
-Another special case of a generalized para-complex structure is para-complex structure.
+Another special case of a generalized para-complex structure is para-complex structure, see Example \ref{eg: pc}. 
 In this case, the generalized AKSZ theory specializes to the following para-complex version of the $B$-model.
@@
 The classical BRST cohomology of the para-B-model is isomorphic to the cohomology of para-holomorphic polyvector fields on the target para-complex manifold $X$.
-To see the equivalence of this definition with the generalized description of the AKSZ model, note that the Lie algebroid $L$ \brian{finish}
+To see the equivalence of this definition with the generalized description of the AKSZ model, note that the Lie algebroid $L_{\KK}$ can be identified with $T^{1,0} \oplus T^{*0,1}$.  
+Its dual is $\Bar{L}_{\KK} = T^{0,1} \oplus T^{*1,0}$.
+
+The Lie algebroid cohomology $H^*(\cO(L_{\KK}[1]), \d_{L_\KK})$ is computed by a differential of the form
+\[
+\d_{L_\KK} : \Gamma(M , \wedge^k (T^{1,0} \oplus T^{*0,1})) \to \Gamma(M , \wedge^{k+1} (T^{1,0} \oplus T^{*0,1})) 
+\]
+Using the splitting $\wedge^*(T^{1,0} \oplus T^{*0,1}) = \wedge^* T^{1,0} \otimes \wedge^*(T^{*0,1})$ we can identify this differential with the Dobleault differential for the bundle of para-holomorphic polyvector fields $\Theta = \wedge^* T^{1,0}$:
+\[
+\d_L = \pd : \mathbf{\Omega}^{0,q} (M , \Theta) \to \mathbf{\Omega}^{0,q+1} (M , \Theta)  .
+\]
+Thus, the BRST cohomology is precisely the Dolbeault cohomology of para-holomorphic polyvector fields.
 
@@
 
-\brian{Case of para structure on $M \times M$. Two copies of $BF$ theory.}
-
 \hrulefill
@@
 }
+
+\brian{Case of para structure on $M \times M$. Two copies of $BF$ theory.}
 

### 2020-01-14 newdraft.tex
Added para-complexification

@@
 \documentclass{article}
-\usepackage{amssymb, amsmath, amsthm, mathtools, bbm, tikz-cd,stmaryrd,enumerate,hyperref}
+\usepackage{amssymb, amsmath, amsthm, mathtools, bbm, tikz-cd,stmaryrd,enumerate,hyperref,bm}
 %-------------------
@@
 \newcommand{\Mt}{\tl{M}}
-\newcommand{\pd}{\overline{\p\!\!\!\p}}
+\newcommand{\pd}{\overline{\bm{\p}}}
 \newcommand{\Mb}{\mathbb{M}}
@@
 
+\subsubsection{Para-Complexified Version}
+In order to make the analogy between complex and para-complex geometry more explicit, one can \textit{paracomplexify} all objects by tensoring with the algebra $\mathbf{C}$ of \textbf{para-complex numbers}, which are given by ordered pairs $(x,y)\in \mathbb{R}\otimes (1,k)$ generated by $1$ and the symbol $k$, satisfying $k^2=1$ and called the para-complex unit.
+The elements $(x,y)\in \mathbf{C}$ can be therefore written as
+\begin{align*}
+\mathbf{C} \ni z=(x,y)=x+k\cdot y.
+\end{align*}
+On $\mathbf{C}$, we define following operations: para-complex conjugation $z=(x,y)\mapsto \bar{z}=(x,-y)$, i.e.
+$\overline{x+ky}=x-ky$, the real and imaginary parts given by $Re(z)=\frac{1}{2}(z+\bar{z})$, $Im(z)=k\frac{1}{2}(z-\bar{z})$, i.e.
+$Re(x+ky)=x,\ Im(x+ky)=y$.
+
+Therefore, we see that $\mathbf{C}^n$ is a paracomplex vector space with the paracomplex structure given by the multiplication by $k$.
+Conversely, any $2n$-dimensional paracomplex vector space $(V,K)$ can be identified with $(\mathbf{C}^n,k)$; the $\mathbf{C}$-module structure is defined as $(a+kb)v=av+bK(v)$ and if $(x^i, \xt^i)$ is a basis of $V$ spanning the $\pm 1$ eigenspaces of $K$, then $z^i\coloneqq \frac{1+k}{2}x^i+\frac{1-k}{2}\xt^i$ is a basis of $\Cc^n$.
+In other words, we have the following identification of paracomplex vector spaces
+\begin{align}\label{para-complexification}
+\begin{aligned}
+\begin{array}{ccc}
+(\RR^n\times\RR^n,\id \times -\id) &\longleftrightarrow &(\Cc^n, k)\\
+(x^i,\xt^i) &\mapsto &\frac{1+k}{2}x^i+\frac{1-k}{2}\xt^i\\
+(u^i+v^i,u^i-v^i) &\mapsfrom &u^i+kv^i,
+\end{array}
+\end{aligned}
+\end{align}
+where $i=1,\cdots,n$.
+If $(V,K)$ is a paracomplex vector space, then its paracomplexification, $V\otimes_\mathbb{R} \mathbf{C}\coloneqq V^\Cc$, splits to $\pm k$ eigenspaces of $K$, which is extended to $V^\Cc$ by linearity: $V^\Cc=V^{1,0}\oplus V^{0,1}$.
+The conjugation map is then an isomorphism between the two eigenspaces, i.e.
+$\overline{{V^{1,0}}}=V^{0,1}$.
+The splitting is given by the projections
+\begin{align}
+\PP^{1,0}=\frac{1}{2}(\id +kK),\quad \PP^{0,1}=\frac{1}{2}(\id -kK). \label{eq:projections_parac}
+\end{align}
+
+Let now $(\PS,K)$ be an almost paracomplex manifold.
+The para-complexified tangent bundle, $T\mathcal{P}^\mathbf{C}=T\mathcal{P}\otimes_\mathbb{R} \mathbf{C}$, splits to a $\pm k$ eigenbundles of $K$ as $T\mathcal{P}^\mathbf{C}=T\mathcal{P}^{1,0}\oplus T\mathcal{P}^{0,1}$.
+%and $T\mathcal{P}^{1,0}$ is isomorphic to $T\PS$ as real vector bundles:
+%\begin{align*}
+%\begin{aligned}
+%\begin{array}{ccc}
+%T\PS &\simeq &T\mathcal{P}^{1,0} \\
+%X &\longmapsto &\frac{1}{2}(X+kKX) \\
+%Re(X^{1,0})=\frac{1}{2}(X^{1,0}+\overline{X^{1,0}})&\longmapsfrom &X^{1,0}
+%\end{array}
+%\end{aligned}
+%\end{align*}
+Similarly to the real case, this induces a splitting of $\Lambda^k(T^*\mathcal{P}^\mathbf{C})$:
+\begin{align*}
+\Lambda^k(T^*\mathcal{P}^\mathbf{C})=\bigoplus_{k=p+q}\Lambda^{p,q}(T^*\mathcal{P}^\mathbf{C}),
+\end{align*}
+with the sections denoted as $\Omega^{p,q}_\mathbf{C}(\PS)$.
+\begin{notation*}
+To distinguish between the real and para-complexified bigradings, the former being with respect to the $\pm 1$ eigenvalues of $K$, while the latter is with respect to the $\pm k$ eigenvalues of $K$, we denote the real bigrading in round brackets, $(p,q)$, and the para-complexified grading without brackets, $p,q$.
+\end{notation*}
+
+The de-Rham differential also splits accordingly into the \textbf{para-complexified Dolbeault operators}
+\begin{align*}
+\p^\mathbf{C}&:\Omega^{p,q}_\mathbf{C}(\mathcal{P})\rightarrow \Omega_\mathbf{C}^{p+1,q}(\mathcal{P}),\\
+\bar{\p}^\mathbf{C}&:\Omega_\mathbf{C}^{p,q}(\mathcal{P})\rightarrow \Omega_\mathbf{C}^{p,q+1}(\mathcal{P})\ .
+\end{align*}
+
+\newcommand{\Cp}{{\mathbf{C}}}
+The isomorphism of para-complex vector spaces \eqref{para-complexification} induces an isomorphism between $\Lambda^{(p,q)}(T^*\PS)$ and $\Lambda^{p,q}(T^*\PS^\mathbf{C})$ as well as between the sections $\Omega^{(p,q)}$ and $\Omega_\Cp^{p,q}$, where the bigrading of the real bundle is with respect to the $\pm 1$ eigenvalues of $K$, while the bigrading of the para-complexified bundle is with respect to the $\pm k$ eigenvalues of $K$.
+Explicitly, we have
+\begin{align}\label{isom_bigradings1}
+\phi:\ (\ap,\tl{\ap})\ \in\ \Omega^{(p,q)}\otimes \Omega^{(q,p)}\longmapsto \frac{1+k}{2}\ap + \frac{1-k}{2}\tl{\ap}\ \in\ \Omega_\Cp^{p,q}
+\end{align}
+with the inverse
+\begin{align}
+\phi^{-1}:\ \bm{\ap}\ \in\ \Omega_\Cp^{p,q}\longmapsto (\text{Re}(\bm{\alpha})+\text{Im}(\bm{\ap}),\text{Re}(\bm{\alpha})-\text{Im}(\bm{\ap}))\ \in\ \Omega^{(p,q)}\otimes \Omega^{(q,p)}.
+\end{align}
+The point we would like to emphasize here is that to one para-complex differential form of degree $p,q$ corresponds a {\it pair} of real forms in degrees $(p,q)$ and $(q,p)$.
+In particular, a para-complex form in degree $k,0$ corresponds to a pair of forms in degrees $(k,0)$ and $(0,k)$, i.e.
+a two $k$-forms on the two canonical para-complex foliations.
+Consequently, recalling the para-complex Dolbeault complex \eqref{para-dolbeault}, we can easily deduce that the corresponding {\bf para-complexified Dolbeault complex} is given by
+\begin{align}
+\left( \Omega^{0,\bullet}_\Cp,\bar{\p}^\Cp\right),
+\end{align}
+In particular, the condition of holomorphicity in the para-complex coordinates $z^i\coloneqq \frac{1+k}{2}x^i+\frac{1-k}{2}\xt^i$ and $\bar{z}^i$ is equivalent to a local independence of the coordinates $\bar{z}^i$ and is therefore entirely analogous to complex geometry.
 %\begin{lemma}
@@
 
-Remember that a holomorphic volume form on a complex manifold $M$ of complex dimension $k$ is a non-vanishing section of the canonical bundle, $\Omega \in \Omega^{k,0}(M)$, that is holomorphic, $\bar{\p}\Omega=0$.
+Remember that a holomorphic volume form on a complex manifold $M$ of complex dimension $k$ is a non-vanishing section of the canonical bundle, $\Omega \in \Omega^{(k,0)}(M)$, that is holomorphic, $\bar{\p}\Omega=0$.
 Recalling the para-complex Dolbeault complex \eqref{para-dolbeault}, we can immediately infer what should be the analogous object in para-complex geometry:
@@
 On the other hand, $\KK_\omega$ in Example \ref{ex:GpC_sympl} can only be half-integrable when the $H$-flux is non-zero.
+
+\paragraph{Para-Complexified version}
+One can also carry out all the above discussion in the setting of the para-complexified generalized tangent bundle $\TT\otimes_\RR \Cp$.
+In particular, one gets a one-to-one correspondence of GpC structures with {\it paracomplex} Dirac structures:
+\begin{proposition}
+A generalized paracomplex structure is equivalent to a paracomplex Dirac structure $L \subset (\TT)\otimes_\mathbb{R} \mathbf{C}$ of real index zero, i.e. $L \cap \bar{L}=0$.
+\end{proposition}
+\begin{proof}
+The proof is entirely analogous to []; if $\KK$ is a generalized paracomplex structure and $L_\KK$ is its $+k$ eigenbundle, $L_\KK$ is automatically maximally isotropic by 
+\begin{align*}
+\langle x,y \rangle = -\langle\KK x,\KK y \rangle = -\langle k x,k y \rangle = -\langle x,y\rangle=0.
+\end{align*}
+The para-complex conjugate $\bar{L}_\KK$ is then a $-k$ eigenbundle and $L\cap\bar{L}=0$.
+Conversely, given $L$ and $\bar{L}$, we can define $\KK$ to be the multiplication by $+k$ on $L$ and $-k$ on $\bar{L}$.
+\end{proof}
 
@@
 $Q_{L+}$& $-1$ & $+1$ & $+1$\\
-$Q_{L-}$& $-1$ & $-1$ & $+1$\\
+$Q_{L-}$& $-1$ & $-1$ & $-1$\\
 $Q_{R+}$& $+1$ & $+1$ & $-1$\\

### 2020-01-14 newdraft.tex
Just page formatting
merge

@@
-\documentclass{article}
+\documentclass[letterpaper,12pt]{article}
 \usepackage{amssymb, amsmath, amsthm, mathtools, bbm, tikz-cd,stmaryrd,enumerate,hyperref,bm}
@@
 \fancyhead[R]{\thepage}
+\addtolength{\headwidth}{\marginparsep}
+\addtolength{\headwidth}{\marginparwidth}
+\addtolength{\headwidth}{0.25in}
 %----------------
+%\setlength{\marginparwidth}{0pt} % width of margin notes
+%\setlength{\marginparsep}{0pt} % width of space between body text and margin notes
+\setlength{\evensidemargin}{0.125in} % Adds 1/8 in. to binding side of all 
+\setlength{\oddsidemargin}{0.125in} % Adds 1/8 in. to the left of all pages
+\setlength{\textwidth}{6.375in} % assuming US letter paper (8.5 in. x 11 in.) and 
+\raggedbottom
+\setlength{\parskip}{\medskipamount}
+\renewcommand{\baselinestretch}{1}
+%---------------------------------
 \newcommand{\TT}{{T\oplus T^*}}
@@
 
-\begin{Ex}[Para-complex structures]
+\begin{Ex}[Para-complex structures]\label{eg: pc}
 A para-complex structure $K\in \Endo(T)$, defines the diagonal generalized para-complex structure:

### 2020-01-15 newdraft.tex
edits

@@
 \paragraph{Dirac Structures}
-An important object in Dirac geometry are (almost) dirac structures, which are subbundles $L\subset \TT$ with special properties.
+An important object in Dirac geometry are (almost) Dirac structures, which are subbundles $L\subset \TT$ with special properties.
 \begin{Def}
@@
 \end{Def}
+Let $L_\KK$ and $\Tilde{L}_{\KK}$ denote the $+1$ and $-1$ eigenbundles of $\KK$, respectively. 
 It is easy to check that the condition \eqref{eq:gen_nijenhuis} is equivalent to the $\pm 1$ eigenbundles of $\KK$ to be involutive under the twisted Dorfman bracket.
@@
 \end{align*} 
-$\KK_b$ is integrable iff $\rd b =-H$, and its eigenbundles are $\Lb_b=\text{graph}(b)=\{X+b(X)\mid X \in \XX\}$ and $\widetilde{\Lb}=T^*$.
-Similarly, $\KK_\beta$ is integrable iff $\beta$ is a Poisson structure, (see \cite[Lemma~2.13]{Hu:2019zro}) and its eigenbundles are $\Lb=T$ and $\widetilde{\Lb}=\text{graph}(-\beta)=\{\ap-\beta(\ap)\}\mid \ap \in \Omega\}$.
+$\KK_b$ is integrable iff $\rd b =-H$, and its eigenbundles are $L_{b} = \text{graph}(b)=\{X+b(X)\mid X \in \XX\}$ and $\widetilde{L}_b =T^*$.
+Similarly, $\KK_\beta$ is integrable iff $\beta$ is a Poisson structure, (see \cite[Lemma~2.13]{Hu:2019zro}) and its eigenbundles are $L_\beta =T$ and $\widetilde{L}_\beta =\text{graph}(-\beta)=\{\ap-\beta(\ap)\}\mid \ap \in \Omega\}$.
+The Lie algebroid $L_{\beta}$ is equivalent to the Lie algebroid with underlying bundle $T^*$ and anchor given by the Poisson bivector $\beta : T^* \to T$. 
 \end{Ex}
@@
 \begin{Ex}[Para-complex structures]\label{eg: pc}
-A para-complex structure $K\in \Endo(T)$, defines the diagonal generalized para-complex structure:
+An almost para-complex structure $K\in \Endo(T)$, defines the diagonal generalized almost para-complex structure:
 \begin{align*}
@@
 \end{align*}
-The corresponding Dirac structures are given by $\Lb=T^{(1,0)}\oplus T^{*(0,1)}$ and $\widetilde{\Lb}=T^{(0,1)}\oplus T^{*(1,0)}$, where the bigrading is with respect to $K$.
-The integrability of $\KK_K$ is equivalent to Frobenius integrability of $K$ , i.e.
-vanishing of the Nijenhuis tensor of $K$.
+The integrability of $\KK_K$ is equivalent to Frobenius integrability of $K$ , i.e. vanishing of the Nijenhuis tensor of $K$.
+Thus a para-complex structure defines a generalized para-complex structure of the above form. 
+The corresponding Dirac structures are given by the $+1$ eigenbundle $L_K =T^{(1,0)}\oplus T^{*(0,1)}$ and $-1$ eigenbundle $\widetilde{L}_K =T^{(0,1)}\oplus T^{*(1,0)}$, where the bigrading is with respect to $K$.
 %
@@
 %where we can read off from the constraints in \eqref{eq:GpC_generalform} that $P^2=\id$ implies that $\Pi\Omega=0$ and both $\Pi$ and $\Omega$ have to be of type $(2,0)+(0,2)$ with respect to the grading given by $P$.
-
 \end{Ex}
@@
 \begin{Ex}[Symplectic structures]\label{ex:GpC_sympl}
-A symplectic form $\omega$ defines the anti-diagonal GpC structure
+A pre-symplectic form $\omega$ defines the anti-diagonal almost generalized para-complex structure
 \begin{align*}
@@
 \end{align*}
-The $\pm 1$ eigenbundles are given by $\text{graph}(\pm\omega)=\{X\pm\omega(X)\mid X\in \XX\}$, and the integrability of $\KK_\omega$ is equivalent to $\rd\omega=0$.
+The integrability of $\KK_\omega$ is equivalent to $\rd\omega=0$.
+Thus, if $\omega$ is symplectic then $\KK_\omega$ is a generalized para-complex structure.
+The $\pm 1$ eigenbundles are given by $\text{graph}(\pm\omega)=\{X\pm\omega(X)\mid X\in \XX\}$.
 \end{Ex}
+
+\btd{Is there a classification of a most general GpC that can be written in the form
+\[
+\KK = 
+\begin{pmatrix}
+K & P \\
+\omega & -K^*
+\end{pmatrix}
+\]
+where $K \in {\rm End}(T)$, $P \in \wedge^2 T$ and $\omega \in \wedge^2 T^*$ satisfying some integrability conditions?
+}
 
@@
 \paragraph{Para-Complexified version}
-One can also carry out all the above discussion in the setting of the para-complexified generalized tangent bundle $\TT\otimes_\RR \Cp$.
+One can also carry out all the above discussion in the setting of the para-complexified generalized tangent bundle $(\TT)\otimes_\RR \Cp$.
 In particular, one gets a one-to-one correspondence of GpC structures with {\it paracomplex} Dirac structures:
@@
 
-\bibliographystyle{JHEP}
+\bibliographystyle{alpha}
 \bibliography{mybib}

### 2020-01-16 AKSZ.tex
edits

@@
 
-For us, the prescription of defining the $2D$ topological theory associated to a GpC structure starts with a $3D$ topological field theory which is defined for any manifold $M$. 
+For us, the prescription of defining the $2D$ topological theory associated to a generalized para-complex structure starts with a $3D$ topological field theory which is defined for any manifold $M$. 
 More generally, this $3D$ theory can be defined for any Courant algebroid on $M$ \cite{Roytenberg:2002nu}, but for most examples we will only consider the standard exact Courant algebroid (or twisted versions) defined by the Dorfman bracket.
-The key to our construction is to realize the data of a G(p)C structure in terms of its eigenbundles, which are Dirac structures $L$ in the Courant algebroid $\TT$.
+The key to our construction is to realize the data of a generalized para-complex structure in terms of its eigenbundles, which are Dirac structures in the real Courant algebroid $\TT$.
+More precisely, we obtain a pair of Dirac structures $L, \Tilde{L}$ corresponding to the $\pm$ eigenbundles of the generalized para-complex structure.
 
-Via the AKSZ construction \cite{AKSZ}, this correspondence translates into the statement that the Dirac structure $L$ defines a topological boundary theory of the $3D$ topological theory defined by the standard Courant algebroid.
-In turn, we will directly describe the BRST observables of the $2D$ theory in terms of the cohomology of the Lie algebroid $L$.
+Via the AKSZ construction \cite{AKSZ}, this correspondence translates into the statement that the pair of Dirac structures define a pair of topological boundary theories of the $3D$ topological theory.
+In turn, we will directly describe the BRST observables of the $2D$ theories in terms of the cohomology of the Lie algebroid $L$.
+
+By similar reasoning, one can obtain a single $2D$ TFT from the data of a generalized para-complex structure. 
+One considers the para-complexification $(\TT) \otimes_{\RR} \Cc$ of the standard Courant algebroid. 
+The real Dirac structures $L, \Tilde{L}$ combine to give a para-complex Dirac structure $L \oplus \Tilde{L}$. 
+In turn, we obtain a single $2D$ TFT defined over the para-complex numbers.
 
@@
  \]
-Applied to the element $1 \times \omega_X \in \Omega^0_N \times \Omega^{\brian{??}}_X$ we obtain a $(-1)$-shifted symplectic form that we denote $\int_N \omega_X$.
+Applied to the element $1 \times \omega_X \in \Omega^0_N \times \Omega^{2}_X$ we obtain a $(-1)$-shifted symplectic form that we denote $\int_N \omega_X$.
 
 \begin{Ex}
-The most important example for us will be the source dg manifold $(N, \Omega^*_N)$, that is $\sA_N = \Omega^*_N$ equipped with de Rham differential. 
-We denote this dg manifold by $N_{\rm dR}$.
+The most important example for us will be the source dg manifold $\cN = (N, \Omega^*_N)$, that is $\sA_\cN = \Omega^*_N$ equipped with de Rham differential. 
+We denote this dg manifold by $\cN = N_{\rm dR}$.
 Take the dg manifold $(N, \Omega^*_N)$ where $N$ is any smooth manifold. 
@@
 To equip the dg manifold $(N, \mathbf{\Omega}^{0,\bullet})$ with an orientation, one must fix additional data. 
-One way to do this is to assume that the para-complex manifold $N$ is equipped with a para-holomorphic volume form $\Omega_N$. \brian{Cite David's new section.}
+One way to do this is to assume that the para-complex manifold $N$ is equipped with a para-holomorphic volume form $\Omega_N$.
 \end{Ex}
@@
 
-\subsection{Two dimensional TFT from GpC structures}
+\subsection{Two dimensional TFT from generalized para-complex structures}
 
@@
 Throughout this section we will only consider the standard Dorfman Courant algebroid $X_H$ on $M$, possibly twisted by an $H$-flux.
-By Theorem \ref{thm:pairofdirac}, the choice of a GpC structure $\KK$ determines a pair of transversal Dirac structures $L_{\KK}$ and $\tilde{L}_{\KK}$ on $M$ given by the positive and negative eigenbundles of $\KK$.
-In particular, $L$ determines a Lagrangian in the shifted symplectic space $X_{H}$. 
+By Theorem \ref{thm:pairofdirac}, the choice of a generalized para-complex structure $\KK$ determines a pair of transversal Dirac structures $L_{\KK}$ and $\tilde{L}_{\KK}$ on $M$ given by the positive and negative eigenbundles of $\KK$.
+In particular, $L_{\KK}$ determines a Lagrangian in the shifted symplectic space $X_{H}$. 
 This Lagrangian then defines a boundary condition for the three-dimensional AKSZ theory.
-Thus, we see that any GpC structure $\KK$ defines a 2D TFT living at the boundary of the 3D theory. 
+Thus, we see that any generalized para-complex structure $\KK$ defines a 2D TFT living at the boundary of the 3D theory. 
 By Proposition \ref{prop:dirac_Liealg} the eigenbundle $L_\KK$ has the structure of a Lie algebroid compatible with the anchor and Dorfman bracket on $\TT$.
@@
 
-\subsubsection*{Trivial GpC structures}
+\subsubsection*{Trivial generalized para-complex structures}
 
@@
 %
-%\subsection{Two dimensional TFT from GpC structures}
-%\label{sec:GpC_AKSZ}
+%\subsection{Two dimensional TFT from generalized para-complex structures}
+%\label{sec:generalized para-complex_AKSZ}
 %\brian{Recall that a generalized (para-)complex structure $\JJ$ defines a Dirac structure in $\TT$, and hence a Lagrangian inside of the $2$-shifted symplectic space $\XX_H$.  
@@
 %
-%\subsubsection*{Trivial GpC structure}
+%\subsubsection*{Trivial generalized para-complex structure}
 %

### 2020-01-17 newdraft.tex
old stuff folder

@@
 \newcommand{\cN}{\mathcal{N}}
+\newcommand{\sA}{\mathcal{A}}
+\newcommand{\cO}{\mathcal{O}}
+\def\d{{\rm d}}
+\def\dbar{\Bar{\partial}}
 %----------------------------------------
@@
 Similarly, $\KK_\beta$ is integrable iff $\beta$ is a Poisson structure, (see \cite[Lemma~2.13]{Hu:2019zro}) and its eigenbundles are $L_\beta =T$ and $\widetilde{L}_\beta =\text{graph}(-\beta)=\{\ap-\beta(\ap)\}\mid \ap \in \Omega\}$.
-The Lie algebroid $L_{\beta}$ is equivalent to the Lie algebroid with underlying bundle $T^*$ and anchor given by the Poisson bivector $\beta : T^* \to T$. 
+The Lie algebroid $\Tilde{L}_{\beta}$ is equivalent to the Lie algebroid with underlying bundle $T^*$ and anchor given by the Poisson bivector $\beta : T^* \to T$. 
 \end{Ex}
@@
 In particular, one gets a one-to-one correspondence of GpC structures with {\it paracomplex} Dirac structures:
-\begin{proposition}
+\begin{proposition}\label{prop: pcomplexified}
 A generalized paracomplex structure is equivalent to a paracomplex Dirac structure $L \subset (\TT)\otimes_\mathbb{R} \mathbf{C}$ of real index zero, i.e. $L \cap \bar{L}=0$.
@@
 
+\def\fg{\mathfrak{g}}
+
+In this section we will see how to associate a class of $2D$ topological field theories to generalized para-complex structures.
+The construction closely follows the relationship between ordinary (non-para) generalized complex structures \cite{Gualtieri:2003dx} and $2D$ topological field theories developed in \cite{Cattaneo:2009zx, Pestun:2006rj}.
+For another class of $2D$ boundary theories to the $3D$ Courant algebroid $\sigma$-model see \cite{SeveraTduality}. \btd{Please add any more references you think fit.}
+
+For us, the prescription of defining the $2D$ topological theory associated to a generalized para-complex structure starts with a $3D$ topological field theory which is defined for any manifold $M$. 
+More generally, this $3D$ theory can be defined for any Courant algebroid on $M$ \cite{Roytenberg:2002nu}, but for most examples we will only consider the standard exact Courant algebroid (or twisted versions) defined by the Dorfman bracket.
+The key to our construction is to realize the data of a generalized para-complex structure in terms of its eigenbundles, which are Dirac structures in the real Courant algebroid $\TT$.
+More precisely, we obtain a pair of Dirac structures $L, \Tilde{L}$ corresponding to the $\pm$ eigenbundles of the generalized para-complex structure.
+
+Via the AKSZ construction \cite{AKSZ}, this correspondence translates into the statement that the pair of Dirac structures define a pair of topological boundary theories of the $3D$ topological theory.
+In turn, we will directly describe the BRST observables of the $2D$ theories in terms of the cohomology of the Lie algebroid $L$.
+
+By similar reasoning, one can obtain a single $2D$ TFT from the data of a generalized para-complex structure. 
+One considers the para-complexification $(\TT) \otimes_{\RR} \Cc$ of the standard Courant algebroid. 
+The real Dirac structures $L, \Tilde{L}$ combine to give a para-complex Dirac structure $L \oplus \Tilde{L}$. 
+In turn, we obtain a single $2D$ TFT defined over the para-complex numbers.
+
+In Section \ref{sec: twist}, we will relate these theories topological twists of $2D$ $(2,2)$ (para-)SUSY sigma models described in Section \ref{sec:toptwist} closely following the methods in \cite{Kapustin:2004gv} for ordinary generalized complex geometry.
+
+All of the topological field theories in this section are of $\sigma$-model type and arise through the AKSZ formalism \cite{AKSZ}. 
+Throughout, we will use the formalism of dg manifolds and shifted symplectic geometry. 
+%Later we will use the idea of Lagrangian intersections \brian{PTVV, ButsonYoo, Costello,...}.
+
+\subsection{Courant algebroids, $3D$ TFTs, and boundary conditions}
+
+From the point of view of topological field theory, Courant algebroids are important because they provide geometric examples of $2$-shifted symplectic spaces. 
+Via the AKSZ construction, $2$-shifted symplectic spaces are the natural home for $3$-dimensional topological field theories in the BV formalism. 
+We recall the construction of the $3D$ topological field theory from the data of a Courant algebroid. 
+For other references, see \cite{Roytenberg:2002nu, Cattaneo:2009zx}.
+
+\subsubsection{Shifted symplectic geometry} 
+\label{sec: dgman}
+
+We begin by setting up our model for the theory of derived manifolds. 
+For us, this is a well-behaved class of $NQ$ manifolds which are appropriate for setting up quantization of $\sigma$-models, see for instance \cite{CostelloSUSY}. 
+A dg manifold is a pair $\cN = (N, \sA^*_\cN)$ where $N$ is a smooth manifold, called the body, and $\sA^*_\cN$ a sheaf of graded commutative algebras over the de Rham complex $\Omega^*_N$.
+Here, $\d_\cN$ is a linear differential operator of degree $+1$, and together the data must satisfy the following conditions:
+\begin{itemize}
+\item[(1)] $\sA_\cN$ is concentrated in finitely many degrees;
+\item[(2)] For each $k$, $\sA^k_\cN$ is a locally free sheaf of $C^\infty_N$-modules of finite rank;
+\item[(3)] The differential $\d_N : \sA_\cN^* \to \sA_\cN^{*+1}$ is square zero differential operator making $(\sA_\cN , \d_\cN)$ into a sheaf of commutative dg algebras over the de Rham complex $\Omega^*_N$.
+\end{itemize}
+
+In particular, as a graded algebra $\sA^*_\cN$ is given by functions on the total space of some graded vector bundle $A_\cN$ on $N$ (which is of finite rank and concentrated in finitely many degrees).
+In the language of $NQ$ manifolds, the homological vector field defining the $Q$-structure is $\d_\cN$.
+
+\brian{Symplectic form}
+
+A striking result of \cite{Roytenberg:2002nu} classifies all $2$-shifted symplectic spaces in terms of Courant algebroids.
+
+\begin{theorem}[\cite{Roytenberg:2002nu}]
+There is an equivalence between isomorphism classes of $2$-shifted symplectic NQ manifolds with body $M$ and isomorphism classes of Courant algebroids on $M$.
+\end{theorem}
+
+\begin{remark}
+In \cite{PymSafronov} it was shown that a more general class of $2$-shifted symplectic derived spaces, called $L_\infty$ algebroids, are equivalent to {\em twisted} Courant algebroids. 
+This is similar to a Courant algebroid, where the Jacobi identity only holds up to homotopy given by some closed $4$-form. 
+\end{remark}
+
+We briefly recount the equivalence between the data of a $2$-shifted symplectic dg manifold and the data of a Courant algebroid.
+
+\def\Sym{{\rm Sym}}
+
+%Given any Courant algebroid $E \to M$, we can have the following sequence of maps $T^* \xto{a^*} E \xto{a} T$ where $a$ is the anchor and $a^*$ is linear dual to the anchor.
+%Using this sequence, we can define the associated $NQ$ manifold $X_E$, following \cite{Ryotenberg:2002nu}.
+Let $E \to M$ be a vector bundle equipped with a fiberwise nondegenerate inner product $\left<-,-\right>$.
+The body of the dg manifold is the manifold $M$, and the underlying graded manifold $X_E$ is given by $T^*M [2] \oplus E[1]$.
+
+We will use coordinates $\{x^i\}$ on $M$, $\{p_i\}$ for the fiber coordinate of $T^*$, and $\{e^a\}$ for the fiber of $E$. 
+Note that $x^i$ is of degree zero, $\eta_i$ is of degree $2$, and $e^a$ is of degree $1$.
+Suppose also that $\left<e^a, e^b\right> = g^{ab}$ and let $(g_{ab})$ be the inverse to the inner product. 
+Notice, $X_E$ comes equipped with a natural $2$-shifted symplectic form, which in coordinates is 
+\[
+\omega_E = d x^i d p_i + g_{ab} d e^a d e^b .
+\]
+Denote by $\{-,-\}$ the shifted Poisson bracket corresponding to this symplectic structure. 
+An arbitrary degree $3$ function on the graded manifold $X_E$ has the form
+\[
+\Theta = p_i a_a^i (x) e^a + \frac{1}{6} f_{abc} (x) e^a e^b e^c .
+\]
+Globally, $a = (a_a^i)$ defines a bundle map $a : E \to T$ and through the pairing the collection $(f_{abc})$ defines a bilinear map $[-,-] : E \times E \to E$. 
+It is a result of \cite{Roytenberg:2002nu} that this function satisfies $\{\Theta, \Theta\} = 0$ if and only if the data $(E, \left<-,-\right>, a, [-,-])$ has the structure of a Courant algebroid. 
+Here $a$ is the anchor map, and $[-,-]$ is the bracket.
+
+%\[
+%Q : \Gamma(M , \Sym \left(T^*[2] \oplus E[1]\right)^*) \to \Gamma(M , \Sym \left(T^*[2] \oplus E[1]\right)^*) 
+%\]
+%as follows: for $\psi \in \Sym^{k + \ell + 2} \left(T^*[2] \oplus E[1]\right)^*)$ and
+%\[
+%(\xi_0 \otimes \cdots \otimes \xi_k) \otimes (\alpha_0 \otimes \cdots \otimes \alpha_\ell) \in \Sym^{k+1}(T^*[2]) \otimes \Sym^{\ell + 1}(E[1]) 
+%\]
+%define
+%\begin{align*}
+%(Q \psi) ((\xi_0 \otimes \cdots \otimes \xi_k) \otimes (\alpha_0 \otimes \cdots \otimes \alpha_\ell)) = \brian{finish}
+%\end{align*}
+%
+%All that remains is to describe the $2$-shifted symplectic structure on the NQ manifold $X_E$. 
+%This is defined via the obvious pairing between $T^*[2]$ and $T$ together with the pairing $\langle - ,- \rangle$ on $E[1]$.
+%In local coordinates \brian{finish}
+
+\subsubsection{The AKSZ construction}
+
+Fix the following data:
+\begin{itemize}
+\item an {\em $n$-oriented} dg manifold $\cN = (N, (\sA^*_N, \d_\cN))$ with body a smooth oriented manifold $N$ and orientation $\mu$. 
+\item An $(n-1)$-shifted symplectic dg manifold $(X,\omega)$. 
+\end{itemize}
+
+The starting point of the AKSZ construction is the mapping space
+\begin{equation}\label{eqn: map}
+\cE (\cN, X) = {\rm Map}\left(\cN, X\right)
+\end{equation}
+As a graded manifold, the mapping space $\cE(N,X)$ is given by the space of smooth maps between the underlying graded manifolds $A_N$ and $X$. 
+The graded manifold $\cE(\cN, X)$ is equipped with the homological vector field $\d_\cN + Q$ where $Q$ is the homological vector field on $X$.
+
+The AKSZ construction endows the mapping space $\cE(N, X)$ in (\ref{eqn: map}) with a $(-1)$-shifted symplectic symplectic form as follows, compatible with the homological vector field $\d_{\cN} + Q$ as follows.
+The fundamental observation is that the diagram
+\[
+\xymatrix{
+& N \times \cE(N, X) \ar[dr]^-{{\rm ev}} \ar[dl]_-{\pi_N} & \\
+N & & X
+}
+\]
+induces a pairing
+\[
+\begin{array}{ccccc}
+ \Omega^p_N& \times & \Omega^q_X & \to & \Omega^{p+q-n}_{\cE(N, X)} \\
+\displaystyle \alpha & \times & \beta & \mapsto & \displaystyle \int_N \pi_N^* \alpha \wedge {\rm ev}^* \beta 
+ \end{array}
+ \]
+Applied to the element $1 \times \omega_X \in \Omega^0_N \times \Omega^{2}_X$ we obtain a $(-1)$-shifted symplectic form that we denote $\int_N \omega_X$.
+
+\begin{Ex}
+The most important example for us will be the source dg manifold $\cN = (N, \Omega^*_N)$, that is $\sA_\cN = \Omega^*_N$ equipped with de Rham differential. 
+We denote this dg manifold by $\cN = N_{\rm dR}$.
+Take the dg manifold $(N, \Omega^*_N)$ where $N$ is any smooth manifold. 
+If $N$ is closed and oriented there exists an integration map
+\[
+\int_N : \Omega^*_N \to \RR[n]
+\]
+of degree $-n$ thus equipping the dg manifold $N_{\rm dR}$ with an $n$-orientation. 
+\end{Ex}
+
+\begin{Ex}
+If $N$ has a para-complex structure, $(N, \mathbf{\Omega}^{0,\bullet})$ has the structure of a dg manifold. 
+Here $\mathbf{\Omega}^{0,\bullet}$ is the para-Dolbeault complex from Section \ref{sec: paracomplex} with differential given by the para $\pd$-operator. 
+We will denote this dg manifold by $N_{\pd}$. 
+To equip the dg manifold $(N, \mathbf{\Omega}^{0,\bullet})$ with an orientation, one must fix additional data. 
+One way to do this is to assume that the para-complex manifold $N$ is equipped with a para-holomorphic volume form $\Omega_N$.
+\brian{Relate to Lie algebroid description.}
+\end{Ex}
+
+\brian{Hamiltonians and action functional}
+
+\subsubsection{The AKSZ theory associated to a Courant algebroid}
+
+From here on, to any Courant algebroid $E$ on a manifold $M$ we associate the dg manifold $X_E$ which carries a $2$-shifted symplectic structure. 
+In the case that the Courant algebroid is exact, call the associated $2$-shifted symplectic space $X_H$, where $H$ labels the Severa class.
+
+We first review some basic examples of AKSZ theories associated to Courant algebroids. 
+The simplest type of Courant algebroid is one over a point, see Example \ref{Ex: point}. 
+The resulting AKSZ theory is a familiar one.
+
+\begin{Ex}\label{ex: cs}
+Any Lie algebra $\fg$ together with a non-degenerate invariant pairing defines a $2$-shifted symplectic structure on the graded manifold $X_E = \fg[1]$ living over a point. 
+The dg algebra of functions is the Chevalley-Eilenberg cochain complex computing Lie algebra cohomology $C^*(\fg)$. 
+The differential is the Chevalley-Eilenberg differential.
+All such $2$-symplectic dg manifolds over a point are of this form. 
+%The resulting AKSZ theory is Chern-Simons theory. 
+The resulting AKSZ theory on a $3$-manifold $M$ is Chern-Simons theory on $M$. 
+Indeed, the space of graded maps $N_{dR} \to \fg[1]$ is identified as a graded vector space with $\Omega^*(N, \fg)[1]$.
+The linear part of the BRST operator encodes the de Rham differential on $M$ and the remaining piece encodes the Lie bracket on $\fg$. 
+\end{Ex}
+
+\begin{Ex} \label{ex: exact CA}
+If $E$ is an exact Courant algebroid on $M$ let $X_E$ be the corresponding $2$-shifted symplectic manifold.
+We use the same coordinates as in Section \ref{sec: dgman}.
+The fields are the graded maps $M_{dR} \to X_E = T^*[2] T[1] M$ which we can identify in local coordinates with
+\begin{align*}
+x^i &\in C^\infty(N) \\
+p_i & \in \Omega^2(N) \\
+e^a & \in \Omega^1(N) 
+\end{align*}
+where $i = 1,\ldots, {\rm dim}(M)$ indexes the local coordinates on $M$ and $a = 1, \ldots, {\rm rank}(E)$ the coordinates on the fiber of $E$.
+The action functional is
+\[
+S = \int_N p_i \d x^i + \frac{1}{2} g_{ab}(x) e^a \d e^b - a_a^i(x) p_i e^a + \frac{1}{6} f_{abc} (x) e^{a} e^b e^c .
+\]
+\end{Ex}
+
+\subsubsection{Dirac structures and boundary conditions}
+
+The AKSZ formalism is a construction which produces a $(-1)$-shifted symplectic space from the data of a closed manifold and a target shifted symplectic manifold. 
+There is a generalization of this construction which produces $(-1)$-shifted symplectic spaces on manifolds with boundary.
+
+Suppose $N$ is a manifold with boundary, and let $\cE(N)$ denote the space of fields of a classical theory on $M$. 
+For us, $\cE(N)$ will be a mapping space of the form ${\rm Map}(M, X)$ where $X$ is shifted symplectic. 
+Let $\cE(\partial N)$ denote the restriction of the fields to the boundary of $N$. 
+For the mapping space example, this is simply the space of maps ${\rm Map}(\partial N, X)$.
+
+In general, when $N$ is not closed, the pairing defined by the AKSZ construction will not endow $\cE(N)$ will with $(-1)$-shifted symplectic structure. 
+However, the space $\cE(\partial N)$ does carry a natural ordinary ($0$-shifted) symplectic structure from the restriction of the pairing defined on $\cE(N)$. 
+Moreover, the natural restriction map $\cE(N) \to \cE(\partial N)$ is a Lagrangian morphism.
+
+\def\cL{\mathcal{L}}
+
+A boundary condition is the choice of an additional Lagrangian subspace $\cL$ of $\cE(\partial N)$.
+One then forms the intersection $\cL \times_{\cE(\partial N)} \cE(N)$ of the two Lagrangians $\cL$ and $\cE(\partial N)$ inside of the phase space $\cE(\partial N)$. 
+The intersection defines the fields of the theory on $\partial N$. 
+When the bulk theory is trivial, so there are no degrees of freedom, the resulting theory on $\partial N$ is also equipped with a $(-1)$-symplectic structure. 
+For proofs of these facts about the Lagrangian intersection we refer to \cite{Calaque,PTVV}.
+
+This formalism can be made explicit in the case of the $3D$/$2D$ system. \brian{finish}
+
+\begin{Ex}
+Suppose $(M, \pi)$ is a Poisson manifold. 
+Then consider the graph of $\pi$ as a Lagrangian subbundle of $\TT$:
+\[
+{\rm Graph}(\pi) = \{(\pi \vee \alpha , \alpha) \; | \; \alpha \in T^* \} \subset \TT .
+\]
+By the Jacobi identity, this subbundle is integrable and so determines a Dirac structure. 
+If we place the 3D AKSZ theory with target the Courant algebroid $\TT$ on $N^3$ with $\partial N = \Sigma$, the boundary condition determined by this Dirac structure is equivalent to the Poisson $\sigma$-model on $\Sigma$, see \cite{KSSdirac}, for instance.
+\end{Ex}
+
+\subsection{Two dimensional TFT from generalized para-complex structures}
+
+Let $M$ be a manifold.
+Throughout this section we will only consider the standard Dorfman Courant algebroid $X_H$ on $M$, possibly twisted by an $H$-flux.
+By Theorem \ref{thm:pairofdirac}, the choice of a generalized para-complex structure $\KK$ determines a pair of transversal Dirac structures $L_{\KK}$ and $\tilde{L}_{\KK}$ on $M$ given by the positive and negative eigenbundles of $\KK$.
+In particular, both $L_{\KK}, \Tilde{L}_{\KK}$determine Lagrangians in the shifted symplectic space $X_{H}$. 
+This Lagrangian then defines a pair of boundary conditions for the three-dimensional AKSZ theory.
+Thus, we see that any generalized para-complex structure $\KK$ defines a 2D TFT living at the boundary of the 3D theory. 
+%By Proposition \ref{prop:dirac_Liealg} the eigenbundle $L_\KK$ has the structure of a Lie algebroid compatible with the anchor and Dorfman bracket on $\TT$.
+
+More generally, if $\KK$ is a generalized para-complex structure in an arbitrary Courant algebroid $E$, then we obtain a pair of $2$-shifted Lagrangians inside of the $2$-shifted symplectic space $X_E$.
+Many of our examples take $E$ to be the standard Courant algebroid, but the following discussion applies in general. 
+We will continue to denote $L_{\KK}$ and $\Tilde{L}_{\KK}$ the $\pm$ eigenbundles in $E$.
+
+There is a different presentation of the $2$-symplectic manifold $X_E$ in terms of $L_{\KK}$ and $\Tilde{L}_{\KK}$ that we will use in our identification of the boundary $2D$ TFT's. 
+Consider the graded manifold $T^*[2] \Tilde{L}_{\KK} [1]$.
+In coordinates, we can parametrize this graded manifold by: $\{l^m, \Tilde{l}_n, x^i, p_j\}$ where $l^m$ parameterizes the fiber of $\Tilde{L}^*[1] \cong L [1]$ and is of degree $1$, $\Tilde{l}_n$ parametrizes the fiber of $\Tilde{L}[1]$ and is of degree $1$, and $x^i, p_j$ are as before.
+
+\brian{define $\omega_{\KK}$ see Appendix A of \cite{Cattaneo:2009zx}.}
+
+\begin{proposition}\label{prop: symp}
+Suppose $\KK$ is a generalized para-complex structure on a Courant algebroid $E$.
+Then, there are symplectomorphisms of $2$-shifted symplectic dg manifolds
+\[
+\left(T^*[2] \Tilde{L}, \omega_{\KK} \right) \cong X_E \cong \left(T^*[2] \overset{\;}{L}, \Tilde{\omega}_{\KK} \right) .
+\]
+\end{proposition}
+\begin{proof}
+The proof is completely analogous to the proofs of the results in Appendix A of \cite{Cattaneo:2009zx}.
+\end{proof}
+
+Equipped with the description of the $2$-symplectic manifold $X_E$ in terms of the generalized para-complex structure of $E$, we can read off the resulting $2D$ boundary TFT as follows.
+The $3D$ theory is given by the AKSZ formalism as ${\rm Map}(N_{dR}, X_E)$ where $N_{dR}$ is a smooth oriented $3$-manifold.
+In the case that $\partial N = \Sigma$, we see that by Proposition \ref{prop: symp} the phase space can be written as
+\[
+{\rm Map}(\Sigma_{dR} , X_E) \cong {\rm Map}(\Sigma_{dR}, T^*[2] \Tilde{L}_{\KK}) 
+\]
+which is a dg manifold equipped with a natural $0$-shifted symplectic structure.
+On the right-hand side, we use the symplectic structure defined by $\omega_{\KK}$.
+
+The $2D$ theory is given as a Lagrangian inside of this symplectic dg manifold. 
+In the coordinates granted by Proposition \ref{prop: symp} this Lagrangian takes a particularly nice form.
+The Dirac structure $L_\KK$ defines the Lagrangian submanifold $L_\KK[1] \subset T^*[2] \Tilde{L}_{\KK}$. 
+At the level of the AKSZ theory, this Lagrangian is simply
+\[
+{\rm Map}(\Sigma_{dR}, L_{\KK} [1])  \hookrightarrow {\rm Map}(\Sigma_{dR} , T^*[2] \Tilde{L}_{\KK}) .
+\]
+For a general Courant algebroid $E$, this graded manifold is equipped with a natural $(-1)$-shifted Poisson structure. 
+In the case that $E$ is exact, the AKSZ construction equips the $\sigma$-model with a $(-1)$-shifted symplectic structure. 
+We will refer to this boundary condition as the {\bf positive} $2D$ TFT corresponding to the generalized para-complex structure $\KK$.
+
+An analogous construction applies to the $(-)$-eigenbundle.
+There, we present the phase space as ${\rm Map}(\Sigma_{dR}, T^*[2] L_{\KK})$ equipped with the symplectic structure $\Tilde{\omega}_{\KK}$. 
+The Lagrangian is ${\rm Map}(\Sigma_{dR}, \Tilde{L}_{\KK} [1])$. 
+Again, when $E$ is exact this is equipped with a $(-1)$-symplectic structure. 
+We will refer to this boundary condition as the {\bf negative} $2D$ TFT corresponding to the generalized para-complex structure $\KK$.
+
+A completely similar construction works at the level of the para-complexification. 
+By Proposition \ref{prop: pcomplexified} the sum $L_\KK \oplus \Tilde{L}_{\KK}$ determines a Dirac structure on $E \otimes_\RR \Cc$. 
+The proof of the following is identical to Proposition \ref{prop: symp}.
+
+\begin{proposition}\label{prop: complexifiedsymp}
+Suppose $\KK$ is a generalized para-complex structure on a Courant algebroid $E$, and consider the para-complexified Courant algebroid $E \otimes_{\RR} \Cc$. 
+Then, there is a symplectomorphisms of $2$-shifted symplectic dg manifolds
+\[
+X_{E\otimes \Cc} \cong \left(T^*[2] (L \oplus \Tilde{L}), \Tilde{\omega}_{\KK} \right) .
+\]
+\end{proposition}
+
+By the same reasoning as above, we see that the Lagrangian $(L \oplus \Tilde{L})[1] \subset T^*[2] (L \oplus \Tilde{L})$ determines a the $2D$ TFT with fields
+\[
+{\rm Map} \left(\Sigma_{dR}, (L \oplus \Tilde{L})[1]\right)
+\]
+lying at the boundary of the para-complexified Courant $\sigma$-model. 
+Again, in the case that $E$ is exact, the AKSZ construction endows this $2D$ $\sigma$-model with a $(-1)$-symplectic structure. 
+We will refer to this boundary condition as the {\bf full} $2D$ TFT corresponding to the generalized para-complex structure $\KK$.
+
+There is a familiar description of the local BRST operators of the resulting theory.
+First, we recall the following general construction.
+Given any Lie algebroid $L$ on $M$ consider the graded manifold $L[1]$ with body $M$. 
+Functions on this graded manifold are given by sections of the graded vector bundle
+\[
+\cO(L[1]) = \bigoplus_{k \geq 0} \wedge^k L [-k] .
+\]
+Here, $\wedge^k(L)$ is placed in cohomological degree $+k$. 
+There is square-zero derivation $\d_L$ of degree $+1$ on $\cO(L[1])$ defined by the following rule. 
+If $\varphi$ is a section of $\wedge^k L$, then
+\begin{align*}
+\left( \d_L \varphi \right) (\ell_0, \ldots, \ell_k) & = \sum_{i = 0}^k (-1)^i a (\ell_i) \varphi(\ell_0, \ldots, \Hat{\ell_i}, \ldots, \ell_k) \\ & + \sum_{i < j} (-1)^{i+j} \varphi([\ell_i, \ell_j] , \ell_0 \cdots, \Hat{\ell_i}, \ldots, \Hat{\ell_j}, \ldots, \ell_k)
+\end{align*}
+Here $a : L \to T_M$ is the anchor and $[-,-]$ is the bracket on $L$. 
+In other words $\d_L$ is a homological vector field on $L$, which can be written in coordinates:
+\[
+\d_L = a_a^i \theta^a \frac{\partial}{\partial x^i} + f_{ab}^c \theta^a \theta^b \frac{\partial}{\partial \theta^c}
+\]
+where $\{x^i\}$ are the coordinates on $M$ and $\{\theta^a\}$ are the coordinates for the fiber of $L[1]$.
+
+Equipped with this differential, the cohomology
+\[
+H^*( \cO(L[1]), \d_L )
+\]
+is called the Lie algebroid cohomology of $L$.
+
+\begin{proposition}
+Let $\KK$ be a generalized para-complex structure on a Courant algebroid $E$.
+The following is true about the local observables of the $2D$ TFTs determined by $\KK$:
+\begin{itemize}
+\item[(1)] the BRST cohomology of the positive $2D$ TFT associated to $\KK$ is isomorphic to the Lie algebroid cohomology of the real Lie algebroid $L_{\KK}$; 
+\item[(2)] the BRST cohomology of the negative $2D$ TFT associated to $\KK$ is isomorphic to the Lie algebroid cohomology of the real Lie algebroid $\Tilde{L}_{\KK}$;
+\item[(3)] the BRST cohomology of the full $2D$ TFT is isomorphic to the Lie algebroid cohomology of para-complex Lie algebroid $L_{\KK} \oplus \Tilde{L}_{\KK}$.
+ \end{itemize}
+\end{proposition}
+
+We now restrict to the case $E = \TT$ with its standard Courant algebroid structure and outline important special cases.
+
+\subsubsection*{Trivial generalized para-complex structures}
+
+Let $M$ be a smooth manifold.
+Consider the case of the trivial generalized para-complex structure on $M$ defined by
+\begin{align*}
+\KK_0=
+\begin{pmatrix}
+\id & 0 \\
+0 & -\id
+\end{pmatrix}.
+\end{align*}
+The positive eigenbundle is simply $L_\KK = T$ and the resulting Lie algebroid structure is the standard one.
+The positive $2D$ theory is the trivial $2D$ theory.
+
+The negative eigenbundle is $L_{\KK} = T^*$ with zero Lie algebroid structure.
+The negative $2D$ theory is given by the AKSZ theory
+\[
+{\rm Map}(\Sigma_{dR} , T^*[1] M)
+\]
+where $T^*[1]M$ is equipped with its standard $1$-symplectic structure.
+
+\subsubsection*{Poisson $\sigma$-model}
+Consider the case of the generalized para-complex structure on $M$ defined by
+\begin{align*}
+\KK_0=
+\begin{pmatrix}
+\id & 2 \beta \\
+0 & -\id
+\end{pmatrix}.
+\end{align*}
+where $\beta \in \wedge^2 T$.
+We have seen that this is integrable if and only if the bivector $\beta$ is a Poisson structure.
+
+The positive eigenbundle is $L_{\KK} = T$ with standard Lie algebroid structure. 
+Thus, the negative $2D$ theory is the same as in the previous example.
+
+The negative eigenbundle is $\Tilde{L}_\KK = T^*$ equipped with Lie algebroid structure determined by the Poisson structure $\beta$. 
+The $2D$ TFT is the Poisson $\sigma$-model with target $(M, \beta)$.
+
+\subsubsection*{Para-complex $A/B$-models}
+Consider the case of the generalized para-complex structure on $M$ defined by
+\begin{align*}
+\KK_\omega =
+\begin{pmatrix}
+0 & \omega^{-1} \\
+\omega & 0
+\end{pmatrix}.
+\end{align*}
+where $\omega \in \wedge^2 T^*$ is a symplectic form.
+
+The positive and negative eigenbundles are isomorphic to $L = T^*$ with anchor $\omega^{-1} : T^* \to T$. 
+The $2D$ AKSZ theory is equivalent to the usual $A$-model.
+
+Finally, consider 
+\begin{align*}
+\KK_K =
+\begin{pmatrix}
+K & 0 \\
+0 & -K^*
+\end{pmatrix}.
+\end{align*}
+where $K$ is an ordinary para-complex structure, see Example \ref{eg: pc}.
+
+In this case, the $2D$ theories specialize to the following para-complex versions of the $B$-model.
+First, $L_{\KK}$ can be identified with $T^{1,0} \oplus T^{*0,1}$ and $\Tilde{L}_{\KK}$ is $T^{0,1} \oplus T^{*1,0}$.
+
+\begin{Def}
+The {\bf para-$B$-model} with source a closed Riemann surface $\Sigma$ and target a para-complex manifold $X$ is the AKSZ theory with source the de Rham space $\Sigma_{\rm dR}$ and target the $1$-shifted symplectic space $T^*[1] X_{\pd}$:
+\[
+{\rm Map}\left(\Sigma_{dR}, T^*[1]  X_{\pd}\right) .
+\]
+\end{Def}
+
+The classical BRST cohomology of the para-B-model is isomorphic to the cohomology of para-holomorphic polyvector fields on the target para-complex manifold $X$.
+
+\brian{below needs to be fixed up a bit}
+
+The Lie algebroid cohomology $H^*(\cO(L_{\KK}[1]), \d_{L_\KK})$ is computed by a differential of the form
+\[
+\d_{L_\KK} : \Gamma(M , \wedge^k (T^{1,0} \oplus T^{*0,1})) \to \Gamma(M , \wedge^{k+1} (T^{1,0} \oplus T^{*0,1})) 
+\]
+Using the splitting $\wedge^*(T^{1,0} \oplus T^{*0,1}) = \wedge^* T^{1,0} \otimes \wedge^*(T^{*0,1})$ we can identify this differential with the Dobleault differential for the bundle of para-holomorphic polyvector fields $\Theta = \wedge^* T^{1,0}$:
+\[
+\d_L = \pd : \mathbf{\Omega}^{0,q} (M , \Theta) \to \mathbf{\Omega}^{0,q+1} (M , \Theta)  .
+\]
+Thus, the BRST cohomology is precisely the Dolbeault cohomology of para-holomorphic polyvector fields.
+
+\brian{discuss anomalies. Para-holomorphic volume form.}
+
+\brian{Discuss Si's work on perturbative quantization}
+
+\hrulefill
+
+\brian{***para Kahler example, **example where the paracomplex structures commute but are not equal (this is where people see ``twisted chiral"), para version of T-duality, **Poisson $\sigma$-model, going back and forth between generalized (para) complex.
+}
+
+\brian{Case of para structure on $M \times M$. Two copies of $BF$ theory.}
+
+\subsection{Para holomorphic variants}
+
+\brian{My plan is to just turn this into an extended remark}
+
+So far, in each of the $\sigma$-models we have discussed in the AKSZ formalism, the fields have depended only topologically on the source Riemann surface. 
+There are closely related $\sigma$-models which depending {\em para-holomorphically} on the source Riemann surface that we briefly discuss. 
 \section{Two-dimensional parasupersymmetry}  \label{sec: parasusy}
@@
 \subsection{$(2,1)$ and $(2,0)$ parasupersymmetry}
-\david{maybe we can just make this a paragraph and say in words (as opposed to propositions) what the geometries are?}
-\brian{I agree. I can do this.}
+\brian{Turn this whole section into a loose discussion.}
 Many of the constructions above make sense when there is less total supersymmetry, and we briefly mention two important cases. The first concerns the $(2,1)$ parasupersymmetry algebra.

### 2020-01-17 old stuff/AKSZ.tex
old stuff folder

--- 2020-01-17 newdraft.tex
@@
-\documentclass[letterpaper,12pt]{article}
-\usepackage{amssymb, amsmath, amsthm, mathtools, bbm, tikz-cd,stmaryrd,enumerate,hyperref,bm}
+\documentclass{article}
+\usepackage{amssymb, amsmath, amsthm, mathtools, bbm, tikz-cd,stmaryrd,enumerate,hyperref}
 %-------------------
@@
 \fancyhead[R]{\thepage}
-\addtolength{\headwidth}{\marginparsep}
-\addtolength{\headwidth}{\marginparwidth}
-\addtolength{\headwidth}{0.25in}
 %----------------
-%\setlength{\marginparwidth}{0pt} % width of margin notes
-%\setlength{\marginparsep}{0pt} % width of space between body text and margin notes
-\setlength{\evensidemargin}{0.125in} % Adds 1/8 in. to binding side of all 
-\setlength{\oddsidemargin}{0.125in} % Adds 1/8 in. to the left of all pages
-\setlength{\textwidth}{6.375in} % assuming US letter paper (8.5 in. x 11 in.) and 
-\raggedbottom
-\setlength{\parskip}{\medskipamount}
-\renewcommand{\baselinestretch}{1}
-%---------------------------------
 \newcommand{\TT}{{T\oplus T^*}}
@@
 \newcommand{\cN}{\mathcal{N}}
-\newcommand{\sA}{\mathcal{A}}
 \newcommand{\cO}{\mathcal{O}}
-\def\d{{\rm d}}
-\def\dbar{\Bar{\partial}}
 %----------------------------------------
@@
 \newcommand{\Mt}{\tl{M}}
-\newcommand{\pd}{\overline{\bm{\p}}}
+\newcommand{\pd}{\overline{\p\!\!\!\p}}
 \newcommand{\Mb}{\mathbb{M}}
@@
 
-\title{Topological Sigma Models for Generalized Para-Complex Geometry}
-
 \begin{document}
 
-\maketitle
-\begin{abstract}
-We study a class of $2d$ topological sigma models that are formulated on generalized para-complex target manifolds via the AKSZ framework.
-When the target is additionally generalized para-K\"ahler, these topological theories can be realized as topological twists of $(2,2)$ para-supersymmetric sigma models of Abou-Zeid and Hull.
-We compare our results to the case of generalized complex and generalized K\"ahler geometry, where similar results have been described in the context of the usual $(2,2)$ SUSY by Kapustin and Li.
-We present several examples and show that our construction recovers the A-model and the Poisson sigma model as special cases.
-Moreover, we also introduce new examples of topological theories inherently tied to the para-complex geometry, the para-B-model and a para-complex version of the Landau-Ginzburg model.
-
-\end{abstract}
-\newpage
-\tableofcontents
-\newpage
-\section{Introduction}
-
-In \cite{HullTwistedSUSY}, Abou-Zeid and Hull studied the target geometry of certain $2D$ $(2,2)$ supersymmetric sigma models, which compared to the usual $(2,2)$ supersymmetry differ by a choice of sign in the supercommutator relations of its $4$ real supercharges:
-\begin{align*}
-\{Q_\pm,\tl{Q}_\pm\}=-2\p_\pm,
-\end{align*}
-with all other anti-brackets vanishing.
-The geometry of the target space of these sigma models reflects this sign change and in contrast to complex geometry needed for the usual supersymmetry, the target needs to be para-complex.
-More precisely, the required target geometry must be bi-para-Hermitian.
-In \cite{HullTwistedSUSY}, this type of supersymmetry was dubbed {twisted} SUSY, while the name {pseudo}-SUSY was used in various other works.
-Here we use the name {\bf para-SUSY} to reflect its relationship to para-complex geometry and to reserve the adjective ``twisted'' for the context of topological twists.
-
-Para-complex structure on a manifold $\Mb$ is given by the data of an integrable endomorphism $K \in \End(T\Mb)$ such that $K^2=\id$ and its two eigenbundles corresponding to the $+1$ and $-1$ eigenvalues have the same rank.
-Consequently, $\Mb$ needs to have an even dimension $2n$.
-A para-Hermitian structure on $(\Mb,\eta)$ is then obtained by adding a compatible metric $\eta$:
-\begin{align*}
-\eta(K\cdot,K\cdot)=-\eta(\cdot,\cdot).
-\end{align*}
-This condition forces $\eta$ to be of signature $(n,n)$ and implies that $\omega=\eta K$ is an almost symplectic structure called the fundamental form of $K$.
-A bi-para-Hermitian geometry is then defined as a pair of para-Hermitian structures $(\eta,K_\pm)$ sharing the same metric and satisfying an additional condition
-\begin{align}
-\rd^p_\pm\omega_\pm=\pm H \in \Omega^3_{cl.}(\Mb),
-\end{align}
-where $\rd^p_\pm=K^*\circ \rd\circ K_\pm^*$ is the para-complex twisted differential and $\omega_\pm=\eta K_\pm$ are the fundamental forms of $K_\pm$.
-
-In \cite{Hu:2019zro}, it is shown that the bi-para-Hermitian geometry $(\Mb,\eta,K_\pm,H)$ is equivalent to the data of a generalized para-K\"ahler geometry, which is defined as a pair of {\it generalized} para-complex (GpC) structures $\KK_\pm$ \cite{wade2004dirac,Zabzine:2006uz,Hu:2019zro} on $\Mb$,
-\begin{align*}
-\KK_\pm \in \End((\TT)\Mb), \quad \KK^2=\id, \quad \la \KK\cdot,\KK\cdot\ra=-\la\cdot,\cdot \ra,
-\end{align*}
-that commute and whose product $\GG=\KK_+\KK_-$ defines a split signature metric $G$ on $(\TT)\Mb$ via $G(\cdot,\cdot)=\la \GG\cdot,\cdot\ra$.
-Here, $\la\cdot,\cdot \ra$ is the symmetric duality pairing on $(\TT)M$ and the generalized para-complex endomorphisms $\KK_\pm$ satisfy a Courant integrability condition which ensures that its $\pm 1$-eigenbundles are Dirac structures \cite{courant1990dirac}.
-
-Para-complex and para-Hermitian geometry was also recently studied as the description of the extended geometry in the context of T-duality \cite{freidel2017generalised,Freidel:2018tkj,Svoboda:2018rci,Marotta:2018myj}, following the earlier work of Vaisman \cite{vaisman2012geometry,vaisman2013towards}.
-In \cite{Marotta:2019eqc}, Szabo and Marotta described the bosonic sector of the $2D$ sigma models targeted in this extended geometry.
-Various topological models in the AKSZ framework on the para-Hermitian manifold $\Mb=T^*M\simeq M^n\times \RR^n$ were studied in \cite{Kokenyesi:2018xgj} and $3D$ membrane sigma models with this target were the subject of \cite{Chatzistavrakidis:2018ztm}.
-The generalized geometry corresponding to Para-Hermitian geometry and its refined version, Born geometry, has been studied in \cite{Hu:2019zro}.
-
-\paragraph{Main results} In this paper, we combine the results of \cite{HullTwistedSUSY} and \cite{Hu:2019zro} to study the $2D$ topological sigma models with a generalized para-complex target manifold $(\Mb,\KK_+)$.
-This geometry leads to a $2D$ topological theory via the AKSZ formalism as follows.
-The Courant algebroid $(\TT)\Mb$ defines a $3D$ topological theory with a $2$-shifted symplectic NQ target space $({\cal E},\Omega)$ \cite{Roytenberg:2002nu}.
-Because the $\pm 1$-eigenbundles of $\KK$ are Dirac structures in $(\TT)\Mb$, they each define a Lagrangian in $({\cal E},\Omega)$, which are $1$-shifted symplectic NQ manifolds and as such define a $2D$ topological boundary theories.
-
-Additionally, we show that when the GpC manifold $(\Mb,\KK_+)$ additionally admits a generalized para-K\"ahler structure $(\Mb,\KK_+,\KK_-)$, the topological theories for $(\Mb,\KK_+)$ described above can be realized as topological twists of the $(2,2)$ para-SUSY theory attached to $(\Mb,\KK_\pm)$.
-
-We also present several explicit examples of our construction. The well-known examples include the Poisson sigma model of a real Poisson manifold $(\Mb,\Pi)$ that is described by the GpC structure
-\begin{align*}
-\KK_\Pi=
-\begin{pmatrix}
-\id & 2\Pi \\
-0 & -\id
-\end{pmatrix},
-\end{align*}
-the A-model of a symplectic manifold $(\Mb,\omega)$ described by the GpC structure
-\begin{align*}
-\KK_\omega=
-\begin{pmatrix}
-0 & \omega^{-1} \\
-\omega & 0
-\end{pmatrix},
-\end{align*}
-and also the BFF theory (?) that is simply given by the trivial GpC structure
-\begin{align*}
-\KK_0=
-\begin{pmatrix}
-\id & 0 \\
-0 & -\id
-\end{pmatrix}.
-\end{align*}
-
-The new examples that we describe are all tied to para-complex geometry. They are the para-complex version of the B-model of a para-complex manifold $(\Mb,K)$ that is given by the GpC structure
-\begin{align*}
-\KK_K=
-\begin{pmatrix}
-K & 0 \\
-0 & -K^*
-\end{pmatrix},
-\end{align*}
-and the para-complex topological Landau-Ginzburg model that can be seen as a deformation of the above geometry by a para-holomorphic poisson bi-vector $Q$
-\begin{align*}
-\KK_Q=
-\begin{pmatrix}
-K & Q \\
-0 & -K^*
-\end{pmatrix}.
-\end{align*}
-
-Importantly, our construction can also be applied to the more notoriously known generalized complex (GC) geometry, which was in the context of topological sigma models extensively studied in \cite{Zucchini:2004ta,Ikeda:2004cm,Kapustin:2004gv,Pestun:2006rj,Cattaneo:2009zx} to name some of the works, but to the authors' knowledge a similar construction to ours via a boundary reduction was not proposed before.
-Similarly in the GpC case, the GC structure defines a pair of Dirac structures (that are now tied by complex conjugation) and the $2D$ topological theory is recovered again as a boundary theory of the $3D$ theory defined by the underlying Courant algebroid.
-The advantage of our approach is that it provides a unified way to extract the data of a topological theory from any GC structure via a clear geometric procedure on the underlying shifted symplectic spaces.
-In the special case when the manifold is generalized K\"ahler \cite{Gualtieri:2003dx,Gualtieri:2010fd} -- implying it admits a $(2,2)$ SUSY --  the topological theories can again be realized as topological twists \cite{Kapustin:2004gv} of the $(2,2)$ theory.
-Here, the main examples are given by the A- and B- model corresponding to the GC structures $\JJ_\omega$ and $\JJ_I$, respectively:
-\begin{align*}
-\JJ_\omega=
-\begin{pmatrix}
-0 & -\omega^{-1} \\
-\omega & 0
-\end{pmatrix}, \quad
-\JJ_I=
-\begin{pmatrix}
-I & 0 \\
-0 & -I^*
-\end{pmatrix},
-\end{align*}
-as well as the topological Landau-Ginzburg model which is again viewed via the deformation of $\JJ_I$ by a holomorphic poisson bi-vector \cite{Gualtieri:2007bq} $\sigma=-\frac{1}{4}(IQ+iQ)$:
-\begin{align*}
-\JJ_Q=
-\begin{pmatrix}
-I & Q \\
-0 & -I^*
-\end{pmatrix}.
-\end{align*}
-
-Notice, however, that for example the usual Poisson sigma model cannot be obtained in the realm of GC geometry because no GC structure is defined by a real Poisson structure $\Pi$.
-
-%Since the work of (..) \cite{?} it has been known that on any K\"ahler manifold $(M,I,\omega)$, one can define a $2d$ sigma model admitting a $(2,2)$ supersymmetry (SUSY) and such model has a simple local description in terms of the K\"ahler potential.
-Moreover, Witten has shown \cite{?} that such sigma model gives rise to two distinct topological theories -- the A- and B-models -- via a procedure called topological twisting.
-These topological theories have an important interpretation in terms of their underlying geometry: the A-model only depends on the symplectic structure $(M,\omega)$, while the B-model only depends on the complex structure $(M,I)$.
-Additionally, there exists an ${\mathbb Z}_2$ automorphism acting on the original $(2,2)$ supersymmetric theory that exchanges its A- and B-models.
-This is the simplest way one can observe the phenomenon of mirror symmetry in the context of $2d$ sigma models.
-%
-%The K\"ahler geometry does not describe the most general $(2,2)$ sigma model, as was shown in \cite{Gates-hull-rocek-biherm}.
-Instead, the most general geometry is described by a bi-Hermitian geometry, defined by a pair of complex structures $I_\pm$ compatible with the same Riemannian metric $g$ and satisfying the compatibility relation
-%\begin{align*}
-%\rd^c_\pm\omega_\pm=\pm H \in \Omega^3_{cl.}(M),
-%\end{align*}
-%$\omega_\pm$ being the fundamental forms of $I_\pm$ and $\rd^c_\pm$ the associated $\rd^c$-operators.
-For this geometry, the local description is more complicated than in the K\"ahler case, in particular because the analogue of the K\"ahler potential is much harder to describe.
-Consequently, the topological twists are also  more complicated.
-%
-%This problem is nevertheless partially mitigated by an alternative geometric formulation in terms of generalized K\"ahler (GK) geometry, which has been shown in \cite{Gualtieri:2003dx} to be equivalent to the above-described bi-Hermitian geometry $(g,I_\pm,H)$.
-A GK structure on $M$ is given by the data of two complex endomorphisms $\JJ_\pm$ of the bundle $(\TT)M$:
-%\begin{align*}
-%\JJ_\pm \in \End((\TT)M),\quad \JJ_\pm^2=-\id, \quad \la \JJ \cdot,\JJ\cdot \ra= \lara,
-%\end{align*}
-%where $\lara$ denotes the natural duality pairing on $(\TT)M$:
-%\begin{align*}
-%\la X+\ap,Y+\bt\ra=\ap(Y)+\bt(X),\quad X,Y\in \se(TM),\quad \ap,\bt \in \se(T^*M).
-%\end{align*}
-%Additionally, $\JJ_\pm$ are required to commute and their product $\GG\coloneqq -\JJ_+\JJ_-$ to define a
-
-\subsection{Notations and conventions}
-
-\brian{Conventions for odd Lie brackets $[-,-]$ and $\{-,-\}$.}
-
-\section{Background on paracomplex and generalized geometry}
-\david{would just put the introduction of paracomplex geometry (minus the generalized part) in appendix, we did that even in the other paper which is literally a differential geometry paper}
-
-\subsection{Paracomplex geometry} \label{sec: paracomplex}
-
-In this section we introduce para-complex geometry with emphasis on the analogy with complex geometry.
-More details can be found in \cite{Hu:2019zro} or \cite[Ch.~15]{Cortes:2010ykx}, for example.
-\brian{I think you should cite your work here too.}
-
-\begin{Def}\label{def:paracpx}
-An (almost) {\bf product structure} on a smooth manifold $\PS$ is an endomorphism $K\in \Endo(T\PS)$ which squares to the identity, $K^2=\id_{T\PS}$, $K\neq \id$.
-An (almost) \textbf{para-complex structure} is a product structure such that the $+1$ and $-1$ eigenbundles of $K$ have the same rank.
-\end{Def}
-A direct consequence of above definition is that any para-complex manifold is of even dimension.
-From now on, the $+1$ and $-1$ eigenbundles of an almost product/para-complex structure will be denoted $L$ and $\Lt$, respectively.
-
-\paragraph{Integrability} The use of the word {\it almost} as usual refers to integrability of the endomorphism, i.e.
-whether its eigenbundles are involutive with respect to the Lie bracket and therefore define a foliation of the underlying manifold.
-Similarly to the complex case, the integrability is governed by the \textbf{Nijenhuis tensor}
-\begin{align}\label{eq:nijenhuis}
-\begin{aligned}
-N_K(X,Y)&=[X,Y]+[KX,KY]-K([KX,Y]+[X,KY])\\
-&=(\n_{KX}K)Y+(\n_XK)KY-(\n_{KY}K)X-(\n_YK)KX\\
-&=4(\PP[\PPt X,\PPt Y]+\PPt[\PP X,\PP Y]),
-\end{aligned}
-\end{align}
-where $\n$ is any torsionless connection and $\PP\coloneqq\frac{1}{2}(\id+K)$ and $\PPt\coloneqq\frac{1}{2}(\id-K)$ are the projections onto $L$ and $\Lt$, respectively.
-We say $K$ is integrable and call $K$ a product/para-complex manifold if $N_K=0$.
-From \eqref{eq:nijenhuis} it is apparent that $K$ is integrable if and only if {\it both} eigenbundles are simultaneously Frobenius integrable, i.e.
-involutive distributions in $T\PS$.
-This is one of the main differences between complex and para-complex geometry; one of the eigenbundles can be integrable while the other is not.
-In such cases, we call $\PS$ {\bf half-integrabile}.
-For more details, see for example \cite{??,??}.
-
-\paragraph{Type decomposition} The splitting of the tangent bundle $T\PS=L\oplus \Lt$ gives rise to a decomposition of tensors analogous to the $(p,q)$-decomposition in complex geometry.
-For differential forms, we denote the decomposition as
-\begin{align}\label{eq_plusminus_decomp}
-\Lambda^k (T^*\mathcal{P})&=\bigoplus_{k=m+n}\Lambda^{(m,n)}(T^*\mathcal{P}),
-\end{align}
-where $\Lambda^{(m,n)}(T^*\mathcal{P})=\Lambda^m(T^{*}_{1,0})\otimes \Lambda^n(T^{*}_{0,1})$ and the corresponding sections are denoted by $\Omega^{(m,n)}(\mathcal{P})$.
-The bigradings \eqref{eq_plusminus_decomp} yield the natural projections
-\begin{align*}
-\Pi^{(p,q)}:\Lambda^k(T^*\mathcal{P})&\rightarrow \Lambda^{(p,q)}(T^*\mathcal{P}),
-\end{align*}
-so that when $K$ is integrable, the de-Rham differential splits as $\rd=\p+\tl{\p}$, where
-\begin{align}\label{paracomplex_dels}
-\begin{array}{cc}
-\p \coloneqq \Pi^{(p+1,q)}\circ \rd, & \tl{\p} \coloneqq \Pi^{(p,q+1)}\circ \rd,
-\end{array}
-\end{align}
-are the \textbf{para-complex Dolbeault operators}, satisfying
-\begin{align*}
-\p^2=\tl{\p}^2=\p\tl{\p}+\tl{\p}\p=0.
-\end{align*}
-
-One can also introduce the {\it twisted differential $\rd^p\coloneqq(\Lambda^{k+1}K^*)\circ\rd\circ (\Lambda^kK^*)$}.
-When $K$ is integrable, it can be simply written as $\rd^p=(\p_++\p_-)$ on real forms and $\rd^p=\kk (\p+\bar{\p})$ on para-complex forms.
-
-\paragraph{Para-Holomorphic structure}
-
-Let now $(\mathcal{P},K)$ be an almost para-complex manifold of dimension $2n$.
-If $K$ is integrable, we get a set of $2n$ coordinates $(x^i,\tilde{x}_i)$ called {\bf adapted coordinates}, $\mathcal{P}$ locally splits as $M\times \tilde{M}$, and $K$ acts as identity on $TM=L$ and negative identity on $T\tilde{M}=\tilde{L}$.
-The adapted coordinates therefore define two complimentary foliations that we will call {\bf canonical foliations} of the para-complex manifold $\PS$ and denote $M$ and $\Mt$.
-Both $M$ and $\Mt$ are therefore $n$-dimensional manifolds composed of connected components called leafs $M_i$, $\Mt_i$:
-\begin{align*}
-M=\bigcup_i M_i,\quad \Mt=\bigcup_i \Mt_i,
-\end{align*}
-and each are as sets equal to $\PS$.
-
-As usual, a map of para-complex manifolds is called para-holomorphic if its pushforward commutes with the respective para-complex structures
-\begin{Def}
-Let $(M,K_M)$ and $(N,K_N)$ be para-complex manifolds. A map $F:M\rightarrow N$ is called para-holomorphic if
-\begin{align}\label{eq:def_parahol}
-K_N\circ F_*=F_*\circ K_M
-\end{align}
-\end{Def}
-\begin{remark}
-In the following we will omit the prefix ``para-'' in para-holomorphic whenever no confusion with complex holomorphicity is possible.
-\end{remark}
-
-Locally, the map $F:M\rightarrow N$ of para-complex manifolds can be understood via composition of coordinates as a
-\begin{align*}
-F&: \RR^{2n}\rightarrow \RR^{2m}\\
-F=(f^i,\tl{f}_j)&=(y^i(x^k,\xt_l),\yt_j(x^k,\xt_l))^{i,j=1,\cdots,m}_{k,l=1,\cdots, n}, 
-\end{align*}
-where $(x^k,\xt_l)$ and $(y^i,\yt_j)$ are adapted local coordinates on $M$ and $N$, respectively.
-It is easy to check from \eqref{eq:def_parahol} that $F$ is a holomorphic map iff the components satisfy
-\begin{align}\label{eq:holomorphic_real}
-\frac{\p}{\p \xt_i}f^j=\frac{\p}{\p x^i}\tl{f}_j=0.
-\end{align}
-
-The conditions \eqref{eq:holomorphic_real} tell us that the holomorphic functions map the canonical foliations of the para-complex manifolds $M$ and $N$.
-This also means that the transition functions on a para-complex manifold (seen as maps $\RR^{2n}\rightarrow \RR^{2m}$) are holomorphic since the foliations must be preserved, i.e.
-the coordinates transform as
-\begin{align}\label{para-coordinate-transf}
-(x^i,\xt_i)\mapsto (y^j(x^i),\yt_j(\xt_i)).
-\end{align}
-
-This also gives us an intuition into what holomorphic bundles and their holomorphic sections look like.
-First, we notice that the tangent bundle $T\PS$ itself is a holomorphic bundle (see for example \cite{Cortes:2003zd,Hu:2019zro}); this is simply because of the form of the transition functions \eqref{para-coordinate-transf} that induce a holomorphic structure on the tangent bundle.
-The holomorphic sections of $T\PS$ -- the holomorphic vector fields -- are locally of the form
-\begin{align*}
-X= X^i(x)\p_i+\tl{X}_i(\xt)\pt^i,
-\end{align*}
-i.e. the components in $L$ and $\Lt$ individually define vector fields on the foliations $M$ and $\Mt$, respectively.
-
-Similarly, the cotangent bundle is a holomorphic bundle.
-For the higher wedge powers, we find that only $\Lambda^{(k,0)+(0,k)}(T^*\PS)$, $1\leq k\leq n$, are holomorphic bundles.
-The {\bf para-complex Dolbeault complex} is therefore given by
-\begin{align}\label{para-dolbeault}
-\left(\Omega^{(\bullet,0)}\otimes\Omega^{(0,\bullet)},(\p,\pt)\right)\coloneqq \left(\mathbf{\Omega}^{0,\bullet},\pd\right).
-\end{align}
-
-\subsubsection{Para-Complexified Version}
-In order to make the analogy between complex and para-complex geometry more explicit, one can \textit{paracomplexify} all objects by tensoring with the algebra $\mathbf{C}$ of \textbf{para-complex numbers}, which are given by ordered pairs $(x,y)\in \mathbb{R}\otimes (1,k)$ generated by $1$ and the symbol $k$, satisfying $k^2=1$ and called the para-complex unit.
-The elements $(x,y)\in \mathbf{C}$ can be therefore written as
-\begin{align*}
-\mathbf{C} \ni z=(x,y)=x+k\cdot y.
-\end{align*}
-On $\mathbf{C}$, we define following operations: para-complex conjugation $z=(x,y)\mapsto \bar{z}=(x,-y)$, i.e.
-$\overline{x+ky}=x-ky$, the real and imaginary parts given by $Re(z)=\frac{1}{2}(z+\bar{z})$, $Im(z)=k\frac{1}{2}(z-\bar{z})$, i.e.
-$Re(x+ky)=x,\ Im(x+ky)=y$.
-
-Therefore, we see that $\mathbf{C}^n$ is a paracomplex vector space with the paracomplex structure given by the multiplication by $k$.
-Conversely, any $2n$-dimensional paracomplex vector space $(V,K)$ can be identified with $(\mathbf{C}^n,k)$; the $\mathbf{C}$-module structure is defined as $(a+kb)v=av+bK(v)$ and if $(x^i, \xt^i)$ is a basis of $V$ spanning the $\pm 1$ eigenspaces of $K$, then $z^i\coloneqq \frac{1+k}{2}x^i+\frac{1-k}{2}\xt^i$ is a basis of $\Cc^n$.
-In other words, we have the following identification of paracomplex vector spaces
-\begin{align}\label{para-complexification}
-\begin{aligned}
-\begin{array}{ccc}
-(\RR^n\times\RR^n,\id \times -\id) &\longleftrightarrow &(\Cc^n, k)\\
-(x^i,\xt^i) &\mapsto &\frac{1+k}{2}x^i+\frac{1-k}{2}\xt^i\\
-(u^i+v^i,u^i-v^i) &\mapsfrom &u^i+kv^i,
-\end{array}
-\end{aligned}
-\end{align}
-where $i=1,\cdots,n$.
-If $(V,K)$ is a paracomplex vector space, then its paracomplexification, $V\otimes_\mathbb{R} \mathbf{C}\coloneqq V^\Cc$, splits to $\pm k$ eigenspaces of $K$, which is extended to $V^\Cc$ by linearity: $V^\Cc=V^{1,0}\oplus V^{0,1}$.
-The conjugation map is then an isomorphism between the two eigenspaces, i.e.
-$\overline{{V^{1,0}}}=V^{0,1}$.
-The splitting is given by the projections
-\begin{align}
-\PP^{1,0}=\frac{1}{2}(\id +kK),\quad \PP^{0,1}=\frac{1}{2}(\id -kK). \label{eq:projections_parac}
-\end{align}
-
-Let now $(\PS,K)$ be an almost paracomplex manifold.
-The para-complexified tangent bundle, $T\mathcal{P}^\mathbf{C}=T\mathcal{P}\otimes_\mathbb{R} \mathbf{C}$, splits to a $\pm k$ eigenbundles of $K$ as $T\mathcal{P}^\mathbf{C}=T\mathcal{P}^{1,0}\oplus T\mathcal{P}^{0,1}$.
-%and $T\mathcal{P}^{1,0}$ is isomorphic to $T\PS$ as real vector bundles:
-%\begin{align*}
-%\begin{aligned}
-%\begin{array}{ccc}
-%T\PS &\simeq &T\mathcal{P}^{1,0} \\
-%X &\longmapsto &\frac{1}{2}(X+kKX) \\
-%Re(X^{1,0})=\frac{1}{2}(X^{1,0}+\overline{X^{1,0}})&\longmapsfrom &X^{1,0}
-%\end{array}
-%\end{aligned}
-%\end{align*}
-Similarly to the real case, this induces a splitting of $\Lambda^k(T^*\mathcal{P}^\mathbf{C})$:
-\begin{align*}
-\Lambda^k(T^*\mathcal{P}^\mathbf{C})=\bigoplus_{k=p+q}\Lambda^{p,q}(T^*\mathcal{P}^\mathbf{C}),
-\end{align*}
-with the sections denoted as $\Omega^{p,q}_\mathbf{C}(\PS)$.
-\begin{notation*}
-To distinguish between the real and para-complexified bigradings, the former being with respect to the $\pm 1$ eigenvalues of $K$, while the latter is with respect to the $\pm k$ eigenvalues of $K$, we denote the real bigrading in round brackets, $(p,q)$, and the para-complexified grading without brackets, $p,q$.
-\end{notation*}
-
-The de-Rham differential also splits accordingly into the \textbf{para-complexified Dolbeault operators}
-\begin{align*}
-\p^\mathbf{C}&:\Omega^{p,q}_\mathbf{C}(\mathcal{P})\rightarrow \Omega_\mathbf{C}^{p+1,q}(\mathcal{P}),\\
-\bar{\p}^\mathbf{C}&:\Omega_\mathbf{C}^{p,q}(\mathcal{P})\rightarrow \Omega_\mathbf{C}^{p,q+1}(\mathcal{P})\ .
-\end{align*}
-
-\newcommand{\Cp}{{\mathbf{C}}}
-The isomorphism of para-complex vector spaces \eqref{para-complexification} induces an isomorphism between $\Lambda^{(p,q)}(T^*\PS)$ and $\Lambda^{p,q}(T^*\PS^\mathbf{C})$ as well as between the sections $\Omega^{(p,q)}$ and $\Omega_\Cp^{p,q}$, where the bigrading of the real bundle is with respect to the $\pm 1$ eigenvalues of $K$, while the bigrading of the para-complexified bundle is with respect to the $\pm k$ eigenvalues of $K$.
-Explicitly, we have
-\begin{align}\label{isom_bigradings1}
-\phi:\ (\ap,\tl{\ap})\ \in\ \Omega^{(p,q)}\otimes \Omega^{(q,p)}\longmapsto \frac{1+k}{2}\ap + \frac{1-k}{2}\tl{\ap}\ \in\ \Omega_\Cp^{p,q}
-\end{align}
-with the inverse
-\begin{align}
-\phi^{-1}:\ \bm{\ap}\ \in\ \Omega_\Cp^{p,q}\longmapsto (\text{Re}(\bm{\alpha})+\text{Im}(\bm{\ap}),\text{Re}(\bm{\alpha})-\text{Im}(\bm{\ap}))\ \in\ \Omega^{(p,q)}\otimes \Omega^{(q,p)}.
-\end{align}
-The point we would like to emphasize here is that to one para-complex differential form of degree $p,q$ corresponds a {\it pair} of real forms in degrees $(p,q)$ and $(q,p)$.
-In particular, a para-complex form in degree $k,0$ corresponds to a pair of forms in degrees $(k,0)$ and $(0,k)$, i.e.
-a two $k$-forms on the two canonical para-complex foliations.
-Consequently, recalling the para-complex Dolbeault complex \eqref{para-dolbeault}, we can easily deduce that the corresponding {\bf para-complexified Dolbeault complex} is given by
-\begin{align}
-\left( \Omega^{0,\bullet}_\Cp,\bar{\p}^\Cp\right),
-\end{align}
-In particular, the condition of holomorphicity in the para-complex coordinates $z^i\coloneqq \frac{1+k}{2}x^i+\frac{1-k}{2}\xt^i$ and $\bar{z}^i$ is equivalent to a local independence of the coordinates $\bar{z}^i$ and is therefore entirely analogous to complex geometry.
-%\begin{lemma}
-%Let $(\PS,K)$ be a paracomplex manifold. Then $\rd^p\coloneqq(\Lambda^{k+1}K)\circ\rd\circ (\Lambda^kK)$ can be expressed as
-%\begin{align}\label{eq:dp-operator}
-%\rd^p=\p_+-\p_-.
-%\end{align}
-%\end{lemma}
-%\begin{proof}
-%Let $\ap \in \Omega^{+m,-n}(\PS)$. Then we have
-%\begin{align*}
-%\rd^p\ap=(-1)^n(\Lambda^kK)\rd\ap=(-1)^{2n}\p_+ \ap +(-1)^{2n+1}\p_-\ap=(\p_+-\p_-)\ap,
-%\end{align*}
-%\end{proof}
-\paragraph{The para-holomorphic volume form}
-In K\"ahler geometry, the notion of a holomorphic volume form is very important and in particular gives rise to Calabi-Yau manifolds, perhaps the most important subclass of K\"ahler manifolds.
-Here we discuss the para-complex version of this story because it plays an important role when considering the anomalies of the R-symmetry at the quantum level.
-
-Remember that a holomorphic volume form on a complex manifold $M$ of complex dimension $k$ is a non-vanishing section of the canonical bundle, $\Omega \in \Omega^{(k,0)}(M)$, that is holomorphic, $\bar{\p}\Omega=0$.
-Recalling the para-complex Dolbeault complex \eqref{para-dolbeault}, we can immediately infer what should be the analogous object in para-complex geometry:
-\begin{Def}
-Let $(\PS,K)$ be a para-complex manifold of dimension $2n$.
-We define a {\bf para-holomorphic volume form} to be a nowhere vanishing section $\hat{\Omega}=(\Omega,\tl{\Omega})\in \Omega^{(n,0)+(0,n)}(\PS)$, where $\Omega \in \Omega^{(n,0)}(\PS)$ and $\tl{\Omega}\in \Omega^{(0,n)}(\PS)$ are each non-vanishing and satisfy
-\begin{align*}
-\pt \Omega=\p \tl{\Omega}=0.
-\end{align*}
-\end{Def}
-Because $\Omega^{(n,0)}(\PS)$ is naturally isomorphic to $\Omega^n(M)$, the section $\Omega$ is non-vanishing and $\pt \Omega=0$ implies it is invariant under the translation along $\Mt$, the above definition implies that $\Omega$ defines an honest volume form on $M$.
-Similarly, $\tl{\Omega}$ is a volume form on $\Mt$ and therefore both the canonical foliations $M$ and $\Mt$ of the para-complex manifold are orientable.
-
-As an extension of the above definition and the direct analogy with Calabi-Yau manifolds, we can introduce a definition of the para-Calabi-Yau manifolds:
-\begin{Def}
-A {\bf para-Calabi-Yau manifold} is a compact, para-K\"ahler manifold $(\PS,\eta,K)$ with a para-Holomorphic volume form $\hat{\Omega}$.
-\end{Def}
-
-\subsection{Basics of generalized geometry}
-In this paper, the term {\it generalized geometry} is used for the study of geometric structures on the bundle $TM \oplus T^*M$ over some manifold $M$.
-We will typically abbreviate this bundle to $\TT$ whenever the base is understood or unimportant for the discussion.
-
-\subsubsection{The exact Courant algebroid structure}
-The bundle $\TT$ has a natural Courant algebroid structure given by the symmetric pairing
-\begin{align*}
-\langle X+\ap,Y+\bt\rangle=\ap(Y)+\bt(Y),
-\end{align*}
-the Dorfman bracket,
-\begin{align}\label{eq:dorfman}
-[ X+\ap,Y+\bt]=[X,Y]+\Lie_X\bt-\imath_Y\rd \ap, 
-\end{align}
-and the anchor $\pi:X+\ap\mapsto X$.
-In the above, $X+\ap$ denotes a section of $\TT$ with the splitting to tangent and cotangent parts given explicitly.
-The Dorfman bracket can be thought of as an extension of the Lie bracket from $T$ to $\TT$ and therefore we opt to use the same notation for both brackets; the expression $[X,Y]$ is always the Lie bracket of vector fields whether we think of $\brac$ as the Lie bracket or the Dorfman bracket and no confusion is therefore possible.
-
-The Courant algebroid on $\TT$ is exact, meaning that the associated sequence
-\begin{align}\label{eq:exact_seq}
-0\longrightarrow T^* \overset{\pi^T}{\longrightarrow} \TT\overset{\pi}{\longrightarrow} T\longrightarrow 0,
-\end{align}
-is exact. Here, $\pi^T$ is the transpose of $\pi$ with respect to the pairing $\lara$,
-%\begin{align*}
-%\la \pi^T(\ap),Y+\bt\ra=\la \ap,\pi(Y+\bt)\ra=\la \ap,Y\ra
-%\end{align*}
-i.e.
-$\pi^T: \ap \mapsto \ap+0$.
-In fact, all possible Courant algebroid structures on $\TT$ are parametrized by a closed three-form $H\in \Omega^3_{cl}$, which enters the definition of the bracket \eqref{eq:dorfman}, changing it to a {\it twisted} Dorfman bracket
-\begin{align*}
-[ X+\ap,Y+\bt]_H=[X,Y]+\Lie_X\bt-\imath_Y\rd \ap+\imath_Y\imath_X H.
-\end{align*}
-Moreover, any isotropic splitting of \eqref{eq:exact_seq} $s:T\rightarrow \TT$ is given by a two-form $b$, such that $X\overset{s}{\mapsto}X+b(X)$.
-This is equivalent to an action of a $b$-field transformation on $\TT$\footnote{Here we are using the term $b$-field transformation more liberally as it is customary to use the term only in the cases when $\rd b=0$ so that $e^b$ is a symmetry of $\brac$.}
-\begin{align*}
-e^b=
-\begin{pmatrix}
-\id & 0 \\
-b & \id
-\end{pmatrix}
-\in \End(\TT),
-\end{align*}
-which consequently changes the bracket as
-\begin{align*}
-[ e^b(X+\ap),e^b(Y+\bt)]_H=e^b([ X+\ap,Y+\bt]_{H+\rd b}),
-\end{align*}
-which implies that when $H$ is trivial in cohomology, then a choice of a $b$-field transformation such that $\rd b=-H$ brings the twisted bracket $\brac_H$ into the standard form \eqref{eq:dorfman}.
-When $H$ is cohomologically non-trivial this can be done at least locally.
-This also means that any choice of splitting with a non-trivial $b$-field can be absorbed in the Courant algebroid bracket in terms of the {\it flux}\footnote{Flux is a term used mainly in physics, in this context simply meaning the ``tensorial contribution to the bracket''.} $\rd b$.
-
-\paragraph{Dirac Structures}
-An important object in Dirac geometry are (almost) Dirac structures, which are subbundles $L\subset \TT$ with special properties.
-\begin{Def}
-An {\bf almost Dirac structure} $L$ is a maximally isotropic subbundle of $\TT$, i.e.
-$\la u,v\ra=0$ for any $u,v \in \se(L)$ and $\text{rank}(L)=\text{rank}(T)$.
-When $L$ is involutive under the Dorfman bracket, i.e.
-it satisfies $[L,L]\subset L$, we call $L$ simply a {\bf Dirac structure}.
-\end{Def}
-An important fact we will repeatedly use is the following:
-
-\begin{proposition}[\cite{courant1990dirac}]\label{prop:dirac_Liealg}
-Let $L$ be a Dirac structure in the Courant algebroid $\TT$ with a flux $H$.
-Then the restriction of the Dorfman bracket to $L$, $\brac\mid_L$ is skew and gives $L$ a structure of a Lie algebroid compatible with the anchor $\pi\mid_L$, a restriction of the projection $\pi:\TT\rightarrow T$ to $L$.
-\end{proposition}
-
-We remark here that all the results in this paper remain valid for any exact courant algebroid $E$ (i.e.
-$E$ fits in the sequence \eqref{eq:exact_seq}), which can be always identified with $\TT$ by the choice of splitting equivalent to a choice of a representative $H\in\Omega^3_{cl}$.
-This also amounts to setting $b=0$ in all formulas since the $b$-field appears as a difference of two splittings.
-
-\subsection{Generalized para-complex geometry}
-We now recall the notion of a generalized para-complex \cite{wade2004dirac,Zabzine:2006uz,Hu:2019zro} and a generalized para-K\"ahler \cite{Hu:2019zro} structure.
-We follow the discussion presented in \cite{Hu:2019zro}.
-
-\begin{Def}
-A \textbf{(twisted) generalized para-complex} (GpC) structure $\KK$ is an endomorphism of $\TT$, such that $\KK^2=\id$ and $\la\KK,\KK\ra=-\lara$, whose generalized Nijenhuis tensor vanishes:
-\begin{align}\label{eq:gen_nijenhuis}
-\mathcal{N}_\KK(u,v)=[\KK u,\KK v]_H+\KK^2[ u,v]_H-\KK([\KK u,v]_H+[ u,\KK v]_H)=0.
-\end{align}
-\end{Def}
-Let $L_\KK$ and $\Tilde{L}_{\KK}$ denote the $+1$ and $-1$ eigenbundles of $\KK$, respectively. 
-It is easy to check that the condition \eqref{eq:gen_nijenhuis} is equivalent to the $\pm 1$ eigenbundles of $\KK$ to be involutive under the twisted Dorfman bracket.
-Since in this paper the flux $H$ will be generically non-zero but all results hold for the special case $H=0$ as well, we will drop the word ``twisted" from our definitions.
-
-Generalized para-complex structures can be understood as the data one needs to specify a splitting of $\TT$ to a pair of integrable Dirac structures:
-
-\begin{theorem*}[\cite{wade2004dirac}]\label{thm:pairofdirac}
-There is a one-to-one correspondence between generalized para-complex structures on $M$ and pairs of transversal Dirac subbundles of $\TT$.
-\end{theorem*}
-
-Combining this result with the well-known result of \cite{Liu:1995lsa} which states that any pair of transversal Dirac structures $(L,\Lt)$ forms a Lie bialgebroid $(L,L^*\simeq \Lt)$, one can immediately infer the following
-
-\begin{corollary}
-Generalized para-complex structures on $\TT$ are in one-to-one correspondence with Lie bialgebroid pairs $(L,L^*)$ such that $L\oplus L^*=\TT$. 
-\end{corollary}
-
-\begin{Ex}[The trivial structure and its deformations]\label{ex:GpC_trivial}
-Any manifold supports the following GpC structure
-\begin{align*}
-\KK_0=
-\begin{pmatrix}
-\id & 0 \\
-0 & -\id
-\end{pmatrix},
-\end{align*}
-that has eigenbundles $T$ and $T^*$ and is always integrable. The following two GpC structures can be seen as deformations of $\KK_0$ by either a two-form $b$ or a bi-vector $\beta$:
-\begin{align*}
-\KK_b=
-\begin{pmatrix}
-\id & 0 \\
-2b & -\id
-\end{pmatrix},\quad
-\KK_\beta=
-\begin{pmatrix}
-\id & 2\beta \\
-0 & -\id
-\end{pmatrix}.
-\end{align*} 
-$\KK_b$ is integrable iff $\rd b =-H$, and its eigenbundles are $L_{b} = \text{graph}(b)=\{X+b(X)\mid X \in \XX\}$ and $\widetilde{L}_b =T^*$.
-Similarly, $\KK_\beta$ is integrable iff $\beta$ is a Poisson structure, (see \cite[Lemma~2.13]{Hu:2019zro}) and its eigenbundles are $L_\beta =T$ and $\widetilde{L}_\beta =\text{graph}(-\beta)=\{\ap-\beta(\ap)\}\mid \ap \in \Omega\}$.
-The Lie algebroid $\Tilde{L}_{\beta}$ is equivalent to the Lie algebroid with underlying bundle $T^*$ and anchor given by the Poisson bivector $\beta : T^* \to T$. 
-\end{Ex}
-
-\begin{Ex}[Para-complex structures]\label{eg: pc}
-An almost para-complex structure $K\in \Endo(T)$, defines the diagonal generalized almost para-complex structure:
-\begin{align*}
-\KK_K=
-\begin{pmatrix}
-K & 0 \\
-0 & -K^*
-\end{pmatrix}.
-\end{align*}
-The integrability of $\KK_K$ is equivalent to Frobenius integrability of $K$ , i.e. vanishing of the Nijenhuis tensor of $K$.
-Thus a para-complex structure defines a generalized para-complex structure of the above form. 
-The corresponding Dirac structures are given by the $+1$ eigenbundle $L_K =T^{(1,0)}\oplus T^{*(0,1)}$ and $-1$ eigenbundle $\widetilde{L}_K =T^{(0,1)}\oplus T^{*(1,0)}$, where the bigrading is with respect to $K$.
-%
-%The structure $\KK_P$ can be generalized to the following
-%\begin{align*}
-%\KK=
-%\begin{pmatrix}
-%P & \Pi \\
-%\Omega & -P^*
-%\end{pmatrix},
-%\end{align*}
-%where we can read off from the constraints in \eqref{eq:GpC_generalform} that $P^2=\id$ implies that $\Pi\Omega=0$ and both $\Pi$ and $\Omega$ have to be of type $(2,0)+(0,2)$ with respect to the grading given by $P$.
-\end{Ex}
-
-\begin{Ex}[Symplectic structures]\label{ex:GpC_sympl}
-A pre-symplectic form $\omega$ defines the anti-diagonal almost generalized para-complex structure
-\begin{align*}
-\KK_\omega=
-\begin{pmatrix}
-0 & \omega^{-1} \\
-\omega & 0
-\end{pmatrix}.
-\end{align*}
-The integrability of $\KK_\omega$ is equivalent to $\rd\omega=0$.
-Thus, if $\omega$ is symplectic then $\KK_\omega$ is a generalized para-complex structure.
-The $\pm 1$ eigenbundles are given by $\text{graph}(\pm\omega)=\{X\pm\omega(X)\mid X\in \XX\}$.
-\end{Ex}
-
-\btd{Is there a classification of a most general GpC that can be written in the form
-\[
-\KK = 
-\begin{pmatrix}
-K & P \\
-\omega & -K^*
-\end{pmatrix}
-\]
-where $K \in {\rm End}(T)$, $P \in \wedge^2 T$ and $\omega \in \wedge^2 T^*$ satisfying some integrability conditions?
-}
-
-\paragraph{Comparision with generalized complex structures}
-Example \ref{ex:GpC_sympl} shows that a symplectic manifold $(M,\omega)$ is a GpC manifold and it is well-known \cite{Gualtieri:2003dx} that $(M,\omega)$ is also generalized complex (GC).
-However, while almost GC structures exist only on almost complex manifolds \cite{Gualtieri:2003dx}, Example \ref{ex:GpC_trivial} demonstrates that GpC structures exist on any Poisson manifold and in particular on any smooth manifold (with trivial Poisson structure).
-Another feature of GpC geometry that is not present in GC geometry is that the GpC structures can be half-integrable (similarly to ordinary para-complex structures): see the cases of $\KK_b$ and $\KK_\beta$ from Example \ref{ex:GpC_trivial} which are always at least half integrable and are fully integrable iff $b$ is closed and $\beta$ is Poisson, respectively.
-On the other hand, $\KK_\omega$ in Example \ref{ex:GpC_sympl} can only be half-integrable when the $H$-flux is non-zero.
-
-\paragraph{Para-Complexified version}
-One can also carry out all the above discussion in the setting of the para-complexified generalized tangent bundle $(\TT)\otimes_\RR \Cp$.
-In particular, one gets a one-to-one correspondence of GpC structures with {\it paracomplex} Dirac structures:
-\begin{proposition}\label{prop: pcomplexified}
-A generalized paracomplex structure is equivalent to a paracomplex Dirac structure $L \subset (\TT)\otimes_\mathbb{R} \mathbf{C}$ of real index zero, i.e. $L \cap \bar{L}=0$.
-\end{proposition}
-\begin{proof}
-The proof is entirely analogous to []; if $\KK$ is a generalized paracomplex structure and $L_\KK$ is its $+k$ eigenbundle, $L_\KK$ is automatically maximally isotropic by 
-\begin{align*}
-\langle x,y \rangle = -\langle\KK x,\KK y \rangle = -\langle k x,k y \rangle = -\langle x,y\rangle=0.
-\end{align*}
-The para-complex conjugate $\bar{L}_\KK$ is then a $-k$ eigenbundle and $L\cap\bar{L}=0$.
-Conversely, given $L$ and $\bar{L}$, we can define $\KK$ to be the multiplication by $+k$ on $L$ and $-k$ on $\bar{L}$.
-\end{proof}
-
-\subsection{Generalized para-K\"ahler geometry}\label{sec:GpK}
-\begin{Def}
-A \textbf{generalized para-K\"ahler structure} (GpK) is a commuting pair $(\KK_+,\KK_-)$ of GpC structures, such that their product $\GG=\KK_+\KK_-$ defines a split-signature metric $G$ on $\TT$ via
-\begin{align*}
-G(\cdot,\cdot)\coloneqq \la \GG\cdot,\cdot\ra.
-\end{align*}
-\end{Def}
-
-Because $\KK_\pm$ are GpC structures, they induce the splitting $\TT= \Lb_\pm\oplus\widetilde{\Lb}_\pm$.
-Moreover, because they commute, each of $\Lb_+$ and $\widetilde{\Lb}_+$ further splits to eigenbundles of $\KK_-$, so that one arrives at the decomposition of $\TT$ into four bundles:
-\begin{align}\label{GpK_bundles}
-\TT=\ell_+\oplus\ell_-\oplus \ellt_+\oplus \ellt_-,
-\end{align}
-such that the eigenbundles of $\KK_+$ are $\Lb_+=\ell_+\oplus\ell_-$ and $\tl{\Lb}_+=\ellt_+\oplus \ellt_-$, the eigenbundles of $\KK_-$ are $\Lb_-=\ell_+\oplus\ellt_-$ and $\tl{\Lb}_-=\ell_-\oplus \ellt_+$ and the eigenbundles of the generalized metric are $C_\pm=\ell_\pm\oplus\ellt_\pm$.
-All $\ell_\pm$ and $\ellt_\pm$ are isotropic and integrable under the Dorfman bracket \cite{Hu:2019zro} and bundles with opposite chirality are orthogonal.
-
-Similarly to generalized K\"ahler structures, the GpK structures can be equivalently given in terms of a pair of para-Hermitian structures satisfying a particular integrability condition:
-\begin{theorem}[\cite{Hu:2019zro}]
-The data of a GpK structure is equivalent to a pair of para-Hermitian structures $(\eta,K_+,K_-)$, such that $\KK_\pm$ are given by
-\begin{align}\label{eq:GpK_genform}
-\KK_{\pm}=\frac{1}{2}
-\begin{pmatrix}
-\id & 0 \\
-b & \id
-\end{pmatrix}
-\begin{pmatrix}
-K_+\pm K_- & \omega^{-1}_+\mp \omega^{-1}_- \\
-\omega_+\mp \omega_- & -(K_+^*\pm K_-^*)
-\end{pmatrix}
-\begin{pmatrix}
-\id & 0 \\
--b & \id
-\end{pmatrix},
-\end{align}
-for some $2$-form $b$. The integrability of $\KK_\pm$ then translates into $K_\pm$ being integrable and satisfying
-\begin{align*}
-\n^\pm K_\pm=0,
-\end{align*}
-where the connections $\n^\pm$ are defined by the Levi-Civita connection $\lc$ of $\eta$ and the $H$-flux:
-\begin{align*}
-\eta(\n^\pm_XY,Z)=\eta(\lc_XY,Z)\pm\frac{1}{2}(H+\rd b).
-\end{align*}
-\end{theorem}
-
-The additional integrability condition on $K_\pm$, $\n^\pm K_\pm$, can be equivalently expressed using the fundamental forms associated to $K_\pm$, $\omega_\pm=\eta K_\pm$, and a para-complex version of the $\rd^c$-operator, which we call $\rd^p$:
-\begin{align*}
-\n^\pm K_\pm=0 \Longleftrightarrow \rd^p_\pm\omega_\pm=\pm (H+\rd b).
-\end{align*}
-$\rd^p_\pm$ here denote the $\rd^p$ operators associated to $K_\pm$, $\rd^p_\pm\coloneqq K_\pm^*\circ \rd\circ K_\pm^*$.
-We will call the geometry given by the data $(\eta, K_\pm, H+\rd b)$ above a {\bf bi-para-Hermitian} geometry.
-
-\subsubsection{Isomorphism between $\TT$ and $T\oplus T$}\label{sec:isomorphism}
-In both the GK and GpK cases, the product of the pair of G(p)C structures defines a generalized (indefinite) metric $\GG$, which means that
-\begin{align*}
-G(\cdot,\cdot)\coloneqq \la \GG\cdot,\cdot\ra,
-\end{align*}
-defines a genuine (indefinite) metric on the bundle $\TT$.
-It can be shown (see eg.
-\cite{Gualtieri:2003dx,Hu:2019zro}) that such metric can be always locally expressed in terms of a two-form $b$ and a metric $g$
-\begin{align}\label{genmetric}
-\GG=\GG(g,b)=\begin{pmatrix}
-\id & 0 \\
-b & \id
-\end{pmatrix}
-\begin{pmatrix}
-0 & g^{-1} \\
-g & 0
-\end{pmatrix}
-\begin{pmatrix}
-\id & 0 \\
--b & \id
-\end{pmatrix},
-\end{align}
-and the signature of $g$ then determines the signature of $\GG(g,b)$.
-Therefore, a generalized metric determines a splitting of $\TT\simeq e^b(T)\oplus T^*$ in which the eigenbundles $C_\pm$ of $\GG$ are $C_\pm=graph(\pm g)$ and the flux of this splitting is given by the closed three-form $H\overset{loc.}{=}\rd b$.
-In the usual splitting $\TT$, we then have $C_\pm=graph(b\pm g)$.
-
-An important property of the generalized metric $\GG$ is that its  eigenbundles $C_\pm$ are isomorphic to the tangent bundle $T$ via the projection:
-\begin{align}\label{pi_iso}
-\begin{aligned}
-\pi_\pm:C_\pm &\simeq T,\\
-X+\ap &\overset{\pi_\pm}{\longmapsto} X,\\
-X+(b\pm g)X &\overset{\pi^{-1}_\pm}{\longmapsfrom} X,
-\end{aligned}
-\end{align}
-where $g$ and $b$ are the defining data of $\GG$. Therefore, since $\TT=C\oplus C_-$, we also have $\TT\simeq T\oplus T$:
-\begin{align}
-\begin{aligned}
-(X_+,X_-)\overset{\pi^{-1}_+\oplus \pi^{-1}_-}{\longmapsto}& X_++(b+g)X_++X_-+(b-g)X_-\\
-&=
-\begin{pmatrix}
- X_++X_- \\
- g(X_+-X_-)+b(X_++X_-)
-\end{pmatrix}.
-\end{aligned}\label{map_pi_pm}
-\end{align}
-In particular, one can check that $\pi_+\oplus \pi_-$ maps the eigenbundles of the generalized structures $\KK_\pm$ ($\JJ_\pm$) to eigenbundles of the corresponding pair of tangent bundle endomorphisms $\KK_\pm$ ($\JJ_\pm$).
-This is because of the following relationship \cite{Hu:2019zro},
-\begin{align*}
-K_+=\pi_+\KK_\pm\pi_+^{-1},\quad K_-=\pm\pi_-\KK_\pm\pi_-^{-1},
-\end{align*}
-and analogously for $\JJ_\pm$ and $J_\pm$. From here, it is easy to see that the $+1$ eigenbundle of $\KK_+$ $\Lb_+$, for example, is given by
-\begin{align*}
-\Lb_+=\pi_+^{-1}(T^{(1,0)_+})\oplus\pi_-^{-1}(T^{(1,0)_-}),
-\end{align*}
-where $T^{(1,0)_\pm}$ denotes the $+1$ eigenbundle of $K_\pm$. Analogously, the $-1$ eigenbundle of $\KK_-$,
-$\widetilde{\Lb}_-$, is given by
-\begin{align*}
-\widetilde{\Lb}_-=\pi_+^{-1}(T^{(0,1)_+})\oplus\pi_-^{-1}(T^{(1,0)_-}),
-\end{align*}
-and so on.
-Therefore, one should think about the pair $K_\pm$ corresponding to the GpK structure as each of the $K_\pm$ acting on its own copy of $T$, which are then mapped via $\pi_\pm$ to $C_\pm$ in $\TT$.
-
-We will also notice that $\pi_\pm$ map the the pseudo-Riemannian structures $G$ and $g$ on each other:
-\begin{align}\label{pi:gG_relationship}
-g(X,Y)=\pm\frac{1}{2}\la \pi_\pm^{-1}X,\pi_\pm^{-1}Y\ra = \frac{1}{2}\la \GG \pi_\pm^{-1}X,\pi_\pm^{-1}Y\ra =\frac{1}{2}G(\pi_\pm^{-1}X,\pi_\pm^{-1}Y).
-\end{align}
-Another important property we will make use of is the fact that the connections $\n^\pm$ give rise via $\pi_\pm$ to a generalized connection $D$ on $\TT$ called the generalized Bismut connection \cite{Gualtieri:2007bq}:
-\begin{align}\label{genBismut_pi_nabla_pm}
-D_uv=\pi^{-1}_+\n^+_{\pi u}\pi_+ v_++\pi^{-1}_-\n^-_{\pi u}\pi_- v_-.
-\end{align}
-This connection preserves $\lara$ and $\GG$ and in the case when $\GG$ is a generalized metric corresponding to a GpK structure, $D$ also preserves all the eigenbundles in \eqref{GpK_bundles}.
-
-There is a tensorial quantity associated to any generalized connection called generalized torsion, which is defined as \cite{Gualtieri:2007bq}
-\begin{align}\label{gentorsion_def}
-T^D(u,v,w)=\la D_uv-D_vu-[u,v]_H,w\ra +\la D_wu,v\ra.
-\end{align}
-For the generalized Bismut connection, this torsion has only pure components in $\Lambda^3C_\pm$ and satisfies the following formula \cite[Prop.~2.29]{Hu:2019zro}:
-\begin{align}\label{gentorsion_H}
-T^D(\pi_\pm^{-1}X,\pi_\pm^{-1}Y,\pi_\pm^{-1}Z)=2H_b(X,Y,Z).
-\end{align}
-
-%\paragraph*{Relationship to Kapustin-Li}
-%On pg. 12 of Kapustin-Li paper they implicitly use the isomorphisms $\pi_\pm$ to map the sections $\chi \in \se(T^{(0,1)_+})$ and $\lambda \in \se(T^{(0,1)_-})$ to the $-i$ eigenbundle of $\JJ_+$ as 
-%\begin{align*}
-%\begin{pmatrix}
-%\chi+\lambda \\
-%g(\chi-\lambda)
-%\end{pmatrix},
-%\end{align*}
-%which is the same as \eqref{map_pi_pm} with $b=0$, which they implicitly absorb inside the $H$-flux.
-
-\subsubsection{SKT Geometry and half generalized structures}
-\david{will see if we'll be using this}
-An {\bf SKT} structure is a Hermitian structure $(I,g)$ for which the fundamental form $\omega$ even though is not closed, is $\rd \rd^c$-closed, i.e.
-$\rd \rd^c \omega=0$.
-The version of this geometry is easily formulated for the para- case where we will call it para-SKT.
-It follows directly from the definition that the bi-para-Hermitian geometry consists of two such structures -- one for each chirality -- and here we will describe how one SKT structure can be described using the language of generalized geometry.
-
-For this purpose we define a positive-chirality\footnote{Similarly one could define a negative-chirality half G(p)C structure by changing $C_+$ for $C_-$} {\bf half generalized almost (para-)complex structure} as a pair $(\GG,\JJ_{C_+})$, where $\GG$ is a (neutral) generalized metric which induces a splitting $\TT=C_+\oplus C_-$ and an isomorphism $C_+\oplus C_-\simeq T\oplus T$, and $\JJ_{C_+}$ is a (para-)complex endomorphism of $C_+$, i.e.
-\begin{align*}
-\JJ_{C_+}\in \End(C_+),\quad \JJ_{C_+}=\pm \id_{C_+},\quad \la \JJ_{C_+} u_+,v_+\ra=-\la u_+,\JJ_{C_+} v_+\ra,
-\end{align*}
-for any $u_+,v_+ \in \se(C_+)$.
-The integrability condition on $\JJ_{C_+}$ is then that its eigenbundles $\ell_+\oplus \ell_-=C_+$ (in the complex case $\ell\oplus \bar{\ell}=C_+\otimes \mathbb{C}$) are involutive with respect to the (twisted) Dorfman bracket.
-It is easy to see that $\JJ_{C_+}$ defines a (para-)Hermitian structure $(J_+,g)$, where
-\begin{align*}
-g(X,Y)=\frac{1}{2}\la \pi_+^{-1}X,\pi_+^{-1}Y\ra,\quad J_+=\pi_+\JJ_{C_+}\pi^{-1}_+
-\end{align*}
-and the integrability condition on $\JJ_{C_+}$ translates into the condition
-\begin{align*}
-\n^+J_+=0,\ \n^+=\lc+\frac{1}{2}g^{-1}(H+\rd b) \Longleftrightarrow \rd^{c/p}\omega_+=H+\rd b,
-\end{align*}
-i.e.
-giving exactly half of the data of a G(p)K geometry.
-If there is a negative-chirality half structure $\JJ_{C_-}$, then $(\GG,\JJ\coloneqq \JJ_{C_+}\oplus \JJ_{C_-})$ defines a genuine G(p)K structure.
-
-\section{The AKSZ formalism and para-geometry} \label{sec: AKSZ}
-
+\section{The AKSZ formalism and para-geometry}
 \def\fg{\mathfrak{g}}
-
-In this section we will see how to associate a class of $2D$ topological field theories to generalized para-complex structures.
+In this section we will show how to associate a class of $2D$ topological field theories to generalized para-complex structures.
 The construction closely follows the relationship between ordinary (non-para) generalized complex structures \cite{Gualtieri:2003dx} and $2D$ topological field theories developed in \cite{Cattaneo:2009zx, Pestun:2006rj}.
@@
 One way to do this is to assume that the para-complex manifold $N$ is equipped with a para-holomorphic volume form $\Omega_N$.
-\brian{Relate to Lie algebroid description.}
 \end{Ex}
@@
 
-\brian{define $\omega_{\KK}$ see Appendix A of \cite{Cattaneo:2009zx}.}
+\brian{define $\omega_{\KK}$}
 
@@
 There are closely related $\sigma$-models which depending {\em para-holomorphically} on the source Riemann surface that we briefly discuss.
-\section{Two-dimensional parasupersymmetry}  \label{sec: parasusy}
-
-In this section we introduce the $(2,2)$ para-SUSY algebra in two dimensions, which is an extension of the $(1,1)$ SUSY similarly to the usual $(2,2)$ SUSY.
-We then realize this superalgebra as a symmetry of a $2D$ $\sigma$-model.
-
-It was shown in \cite{HullTwistedSUSY} that in order to do this, one needs to introduce a pair of para-Hermitian structures $(\eta,K_\pm)$ that form a so-called bi-para-Hermitian geometry.
-In \cite{Hu:2019zro} it was then shown that such geometry can be equivalently described by {\bf generalized para-K\"ahler} geometry.
-Because generalized para-K\"ahler geometry is defined by a pair of generalized para-complex structures that obey extra algebraic conditions (see Section \ref{sec:GpK}), this geometry supports the topological $\sigma$-models discussed in Section \ref{sec:GpC_AKSZ}.
-
-The main content of the present section is therefore to define the topological twists of the $(2,2)$ para-SUSY sigma models and show that they are exactly equal to the topological sigma models defined by the pair of GpC structures.
-%
-%It has been known since \cite{Zumino:1979et} that the $(1,1)$ supersymmetric $\sigma$-model \eqref{eq:(1,1)action} admits $(2,2)$ supersymmetry when $(M,g)$ is a K\"{a}hler manifold.
-In general, $(2,2)$ supersymmetry in fact requires the target to be {\bf generalized K\"ahler} \cite{Gualtieri:2003dx}, which is equivalent to a data of a bi-Hermitian geometry discovered in \cite{Gates:1984nk}.
-For $(2,2)$ para-SUSY, the story is analogous.
-%
-%will see later that in order to realize the para-$(2,2)$ superalgebra as a symmetry of a $2D$ $\sigma$ model, the target manifold must carry a pair of para-complex structures $K_\pm$.
-This is in contrast to the usual case that requires complex structures $I_\pm$ on the target instead.
-
-\subsection{A reminder on $(1,1)$ supersymmetry}
-
-The $2$-dimensional $(1,1)$ supertranslation algebra is the super Lie algebra
-\[
-\mathfrak{t}_{(1,1)} = \RR^{1,1} \oplus \Pi (S_+) \oplus \Pi(S_-)
-\]
-where $S_\pm \cong \RR$ are the semi-spin representations of ${\rm Spin}(1,1)$ labeled by helicities $\pm \frac{1}{2}$. 
-Note that there are natural ${\rm Spin}(1,1)$-equivariant maps
-\[
-\Gamma_{\pm} : {\rm Sym}^2(S_\pm) \to \RR^{1,1}
-\]
-which are non-degenerate and whose images hit the subalgebras spanned by $\partial_{\pm}$, respectively. 
-The only nonvanishing Lie brackets in $\mathfrak{t}_{(1,1)}$ are defined by
-\[
-[Q_+, Q_+'] = \Gamma_+(Q_+ \otimes Q_+') \;\; , \;\; [Q_-, Q_-'] = \Gamma_-(Q_- \otimes Q_-')
-\]  
-where $Q_\pm, Q_\pm'$ are generic elements in $S_\pm$.
-
-We will use the lightcone basis $\p_{\pm}$ for $\RR^{1,1}$ and we also fix a basis $Q_\pm^1$ for $S_{\pm}$ with a relative normalization so that
-\begin{align}\label{eq:(1,1)_susy}
-[Q^1_\pm,Q^1_\pm] = 2\p_\pm.
-\end{align}
-
-\subsubsection{The $(1,1)$ supersymmetric $\sigma$-model}
-
-Let $\Sigma^{2|2}$ be a super Riemann surface with two real odd directions. 
-The even part of this supermanifold is a Riemann surface (with coordinates $\sigma$, $\tau$).
-For instance, in the flat case we consider the superspace $\RR^{2|2} = \{(x^i , \theta_1^{\pm}) \; | \; i = 1,2\}$, where $\theta_1^{\pm}$ are odd variables.
-
-The most general $(1,1)$ supersymmetric sigma model into a target pseudo-Riemannian manifold $(M,\eta)$ is given by the action functional
-\begin{align}\label{eq:(1,1)action}
-S_{(1,1)}(\Phi)=\int_{\Sigma^{2|2}} [g(\Phi)+b(\Phi)]_{ij}D^1_+\Phi^iD^1_-\Phi^j,
-\end{align}
-where $\Phi=(\Phi^i)_{i=1\cdots n}$ are local representatives for the $(1,1)$ {superfields} which are maps $\Phi: \Sigma^{2|2} \rightarrow M$.
-In the action, $b$ denotes a local two-form potential for a closed three-form, $H=\rd b$, and $D^1_\pm$ are the superderivatives
-\begin{align}\label{eq:D1}
-D^1_\pm=\frac{\p}{\p \theta_1^\pm}-\theta_1^\pm \p_\pm,
-\end{align}
-where $\p_\pm=\frac{\p}{\p x_\pm}$ are derivatives along the lightcone coordinates on $\Sigma$, $x_\pm=\tau\pm\sigma$. In superworldsheet coordinates, the superfields decompose as
-\begin{align}\label{fields_(1,1)}
-\Phi^i(\sigma,\tau,\theta_+,\theta_-)=\phi^i(\sigma,\tau)+\theta^+\psi^i_+(\sigma,\tau)+\theta^-\psi_-(\sigma,\tau)+\theta^+\theta^-F^i(\sigma,\tau).
-\end{align}
-Here, $(\phi^i)$ are local representatives for a smooth map $\phi: \Sigma \rightarrow M$.
-The fact that this action carries $(1,1)$ supersymmetry means that the action \eqref{eq:(1,1)action} is invariant under transformations generated by the two {supercharges} $Q^1_\pm$,
-\begin{align}\label{eq:Q1}
-Q^1_\pm=\frac{\p}{\p \theta_1^\pm}+\theta_1^\pm \p_\pm,
-\end{align}
-obeying the supercommutation relations of the $(1,1)$ supersymmetry algebra (\ref{eq:(1,1)_susy}). 
-\begin{remark}
-The sigma model \eqref{eq:(1,1)action} is fully determined by the geometric data of the generalized pseudo-metric $\GG(g=\eta,b)$ \eqref{genmetric}.
-\end{remark}
-
-\paragraph{Expanding the $(1,1)$ action}
-We now expand the action \eqref{eq:(1,1)action} by plugging in \eqref{fields_(1,1)} and \eqref{eq:D1}. The expansions read
-%In components, the superfield has the form
-%\[
-%\Phi^i =\phi^i+\theta^+\psi^i_++\theta^-\psi^i_-+\theta^+\theta^-F^i
-%\]
-%The super covariant derivatives $D_{\pm}$ applied to $\Phi^i$ read
-\[
-D_\pm\Phi^i =\psi^i_\pm\pm\theta^\mp F^i-\theta^\pm\p_\pm\phi^i\mp\theta^+\theta^-\p_\pm\psi^i_\mp,
-\]
-and
-\begin{align*}
-[\eta(\Phi)+b(\Phi)]_{ij} = & [\eta(\phi)+b(\phi)]_{ij}+\p_k[\eta(\phi)+b(\phi)]_{ij}(\theta^+\psi_+^k+\theta^-\psi_-^k+\theta^+\theta^-F^k)\\
-& +\frac{1}{2}\p_k\p_l[\eta(\phi)+b(\phi)]_{ij}(\theta^+\psi_+^k+\theta^-\psi_-^k)(\theta^+\psi_+^l+\theta^-\psi_-^l).
-\end{align*}
-After plugging the above in the action and performing the odd integration, the only terms that survive are the $\theta^+\theta^-$ coefficients. From this we find that
-%\begin{align*}
-%\theta^+\theta^-&\left[(g+b)_{ij}(\psi_+^i\p_-\psi^j_++\psi^j_-\p_-\psi^i_-+F^iF^j+\p_+\phi^i\p_-\phi^j)\right. \\
-%&+\p_k(g+b)_{ij}\left(F^k\psi^i_+\psi^j_-+\psi^k_+(-F^i\psi^j_--\psi^i_+\p_-\phi^j)+\psi^k_-(-\p_+\phi^i\psi^j_-+\psi_+^iF^j)\right)\\
-%&\left. +\frac{1}{2}\p_k\p_l(g+b)_{ij}(-\psi_+^k\psi_-^l\psi_+^i\psi_-^j+\psi_-^k\psi_+^l\psi^i_+\psi^j_-) \right].
-%\end{align*}
-the field $F$ enters only algebraically and not via its derivatives. Therefore, it is auxiliary and can be integrated out. To obtain the equations of motion for $F$,
-%we use the formula $\p_kg_{ij}=\Gamma_{ikj}+\Gamma_{jki}$ and collect the terms involving $F$:
-%\begin{align*}
-%g_{ij}F^iF^j+&(\Gamma_{ikj}+\Gamma_{jki})(F^k\psi^i_+\psi^j_--F^i\psi^k_+\psi^j_-+F^j\psi^k_-\psi_+^i)\\
-%+&F^k\psi^i_+\psi^j_-(\p_kb_{ij}+\p_ib_{jk}+\p_jb_{ki}).
-%\end{align*}
-%Using $\Gamma_{ikj}=\Gamma_{kij}$ and $H_{ijk}=(\p_kb_{ij}+\p_ib_{jk}+\p_jb_{ki})$, we can rewrite this as
-%\begin{align*}
-%g_{ij}F^iF^j+2\Gamma_{ikj}F^j\psi^k_-\psi_+^i+F^k\psi^i_+\psi^j_-H_{ijk}=g_{ij}(F^iF^j+2F^j(\Gamma^-)_{lk}^i\psi_-^k\psi_+^l),
-%\end{align*}
-%where $\Gamma^-$ are the Christoffel symbols of the connection $\n^-=\lc-\frac{1}{2}g^{-1}H$. This yields the equation of motion for $F$,
-we vary the resulting bosonic action with respect to $F^i$:
-\begin{align} \label{F_EoM}
-\frac{\delta S_{(1,1)}}{\delta F^i}=0\quad \Longleftrightarrow\quad  F^i=-(\Gamma^-)^i_{jk}\psi^k_-\psi^j_+.
-\end{align}
-Here, $\Gamma^-$ are the Christoffel symbols of the connection $\n^-=\lc-\frac{1}{2}\eta^{-1}H$.
-
-\subsection{$(2,2)$ para-supersymmetry}\label{sec:(2,2)parasusy}
-We continue by extending the above $(1,1)$ picture to the $(2,2)$ para-SUSY setting. This version of supersymmetry and the corresponding sigma models were first discussed in \cite{HullTwistedSUSY}.
-
-The {\bf (2,2) para-supersymmetry algebra} has the underlying supervector space
-\[
-\mathfrak{t}_{(2,2)} = \RR^{1,1} \oplus \Pi(S_+ \oplus S_+) \oplus \Pi(S_- \oplus S_-),
-\]
-with the Lie brackets defined as follows: we choose a basis $\{Q^1_{\pm}, Q^2_\pm\}$ for $S_\pm \oplus S_\pm$ in which the nontrivial brackets read 
-\begin{equation}\label{eq:(2,2)para}
-(2,2)\ \text{para-SUSY:}\quad [Q_\pm^1, Q_\pm^1] = 2 \partial_{\pm}, \quad [Q_{\pm}^2, Q_{\pm}^2] = -2 \partial_{\pm} .
-\end{equation}
-
-\begin{remark}
-Note that this differs from ordinary $(2,2)$ supersymmetry by a sign:
-\begin{equation*}
-(2,2)\ \text{(ordinary) SUSY:}\quad [Q_\pm^1, Q_\pm^1] = 2 \partial_{\pm}, \quad [Q_{\pm}^2, Q_{\pm}^2] = 2 \partial_{\pm} .
-\end{equation*}
-\end{remark}
-
-We can also write the para-SUSY algebra in the more conventional off-diagonal basis $\{{Q}_\pm,\wtl{Q}_\pm\}$, in which the only non-zero brackets read:
-\begin{align*}
-[{Q}_\pm,\wtl{Q}_\pm]=-2\p_\pm.
-\end{align*}
-The two bases $\{Q^1_{\pm}, Q^2_\pm\}$ and $\{{Q}_\pm,\wtl{Q}_\pm\}$ are related by
-\begin{align*}
-Q_\pm=\frac{1}{\sqrt{2}}(Q^2_\pm+Q^1_\pm),\quad \wtl{Q}_\pm=\frac{1}{\sqrt{2}}(Q^2_\pm-Q^1_\pm).
-\end{align*}
-Again, this is analogous to the complex basis of the ordinary $(2,2)$ superalgebra
-\begin{align*}
-[Q_\pm,\overline{Q}_\pm]=2\p_\pm.
-\end{align*}
-
-\begin{remark}
-
-More generally, suppose $W_\pm$ are vector spaces of dimension $k_\pm$, respectively.
-In addition, suppose $\eta_\pm$ are symmetric nondegenerate forms on $W_\pm$. 
-Then, we can define a super Lie algebra of the form
-\[
-\mathfrak{t}_{W} =  \RR^{1,1} \oplus \Pi(S_+ \otimes W_+) \oplus \Pi(S_- \otimes W_-)
-\]
-with brackets defined by
-\[
-[Q_\pm^{a}, Q_\pm^{b}] = 2 \eta^{ab}_\pm \partial_\pm .
-\] 
-This is a general form of the $\cN = (k_+, k_-)$ supersymmetry algebra for which ordinary supersymmetry and para-supersymmetry are special cases.
-The case of $\mathfrak{t}_{(2,2)}$, which will be of most interested to us, corresponds to taking $k_+ = k_- = 2$ and $\eta_\pm^{11} = 1$, $\eta^{22}_\pm = - 1$, $\eta^{12}_{\pm} = 0$.
-
-\end{remark}
-
-\paragraph{R-symmetry}
-%We have seen above that the $(2,2)$ para-SUSY algebra $\mathfrak{t}_{(2,2)}$ is diagonalised in terms of the charges
-%\begin{align}\label{eq:R-sym_charges}
-%\begin{aligned}
-%[Q_\pm^1,Q_\pm^1]&=2\p_\pm\\
-%[Q_\pm^2,Q_\pm^2]&=-2\p_\pm.
-%\end{aligned}
-%\end{align}
-%We make a change of basis by the formulas $Q_\pm=\frac{1}{\sqrt{2}}(Q^2_\pm+Q^1_\pm)$ and $\tl{Q}_\pm=\frac{1}{\sqrt{2}}(Q^2_\pm-Q^1_\pm)$. 
-There is a symmetry of the $(2,2)$ para-SUSY algebra \eqref{eq:(2,2)para} that separately rotates the $\pm$-chirality charges, called the R-symmetry.
-To see this, we write the equations \eqref{eq:(2,2)para} collectively as
-\begin{align}\label{eq:R-sym_eta}
-[Q_\pm^a,Q_\pm^b]=2\eta^{ab}\p_\pm, \quad 
-\eta^{ab}=\begin{pmatrix}
-1 & 0 \\
-0 & -1
-\end{pmatrix}
-\end{align}
-From here it is easy to see that matrices $(M_\pm)^a_b$ that rotate the $\pm$-chirality charges among each other while preserving the commutation relations \eqref{eq:R-sym_eta},
-\begin{align*}
-[(M_\pm)^a_cQ_\pm^c,(M_\pm)^b_dQ_\pm^d]=2\eta^{ab}\p_\pm
-\end{align*}
-have to satisfy
-\begin{align}\label{r_symmetry_matrix}
-(M_\pm)^a_c\eta^{cd}(M_\pm)^a_d=\eta^{ab},
-\end{align}
-i.e. $M_\pm$ have to lie in $SO(1,1)$ for each subscript $\pm$ and the R-symmetry group is therefore $G_R=SO(1,1)_+\times SO(1,1)_-$.
-%\david{this is only relevant for the (2,2) formalism, will se if we need this or not}
-%The R-symmetry acts on the odd coordinates accordingly as
-%\begin{align*}
-%\begin{pmatrix}
-%\theta^1_\pm \\
-%\theta^2_\pm	
-%\end{pmatrix}
-%\mapsto
-%\begin{pmatrix}
-%\cosh(\alpha_\pm) & \sinh(\alpha_\pm) \\
-%\sinh(\alpha_\pm) & \cosh(\alpha_\pm)
-%\end{pmatrix}
-%\begin{pmatrix}
-%\theta^1_\pm \\
-%\theta^2_\pm	
-%\end{pmatrix}
-%\end{align*}
-%or, equivalently, $(\theta^\pm,\tth^\pm)\mapsto (e^{\alpha_\pm} \theta^\pm,e^{-\alpha_\pm}\tth^\pm)$.
-There are therefore two inequivalent embeddings of the Lorentz group $SO(1,1)$ into the R-symmetry group, we label them by $V$ and $A$:
-%\begin{align*}
-%R_V(\alpha)&:(\theta^\pm,\tth^\pm)\mapsto (e^\alpha \theta^\pm,e^{-\alpha}\tth^\pm)\\
-%R_A(\alpha)&:(\theta^\pm,\tth^\pm)\mapsto (e^{\pm \alpha} \theta^\pm,e^{\mp \alpha}\tth^\pm),
-%\end{align*}
-%mapping the supercharges as
-%\begin{align*}
-%R_V(\alpha):& (Q_\pm,\tl{Q}_\pm)\mapsto (e^{-\alpha}Q_\pm,e^{\alpha}\tl{Q}_\pm)\\
-%R_A(\alpha):& (Q_\pm,\tl{Q}_\pm)\mapsto (e^{\mp\alpha}Q_\pm,e^{\pm \alpha}\tl{Q}_\pm).
-%\end{align*}
-%The generators of these transformations are
-%\begin{align*}
-%F_{V/A}=\theta^+\frac{\p}{\p\theta^+}-\tth^+\frac{\p}{\p\tth^+}\pm \theta^-\frac{\p}{\p\theta^-}\mp\tth^-\frac{\p}{\p\tth^-}.
-%\end{align*}
-%
-%Because $F_{V/A}$ has same commutators with other operators as $M$, the Lorentz generator, and additionally all $F_{V/A}$ and $M$ commute among themselves, we can define new "Lorentz" generators in one of the two following ways:
-%\begin{align*}
-%M_A=M+F_V,\quad M_B=M+F_A.
-%\end{align*}
-
-\subsubsection{The $(2,2)$ parasupersymmetric $\sigma$-model}
-We now describe the $2D$ sigma models that carry the $(2,2)$ para-supersymmetry described above.
-%\paragraph{(2,2) SUSY}
-%We propose the following symmetry by the $(2,2)$ parasupersymmetry algebra (\ref{(2,2)para}) (setting $\theta^\pm_1\coloneqq \theta^\pm$ for simplicity), which read in superspace notation:
-%\begin{align*}
-%Q^1_\pm&=\frac{\p}{\p\theta^\pm}+\theta^\pm\p_\pm \\
-%Q^2_\pm\Phi^i&=(K_\pm)^i_j(\Phi)D_\pm\Phi^j \\
-%\end{align*}
-%where $D_\pm =\frac{\p}{\p\theta^\pm}-\theta^\pm\p_\pm$. 
-\paragraph{Extended supersymmetry}
-
-The $\sigma$-model \eqref{eq:(1,1)action} has manifest $(1,1)$ supersymmetry.
-We now impose additional symmetries of the action $S_{(1,1)}$ that generate the $(2,2)$ parasupersymmetry algebra (\ref{eq:(2,2)para}) and discuss the required geometric properties of the target manifold for such extension.
-%In general, this extended symmetry exists only after we make some additional assumptions on the geometric data prescribing the action.
-
-Setting $\theta^\pm_1\coloneqq \theta^\pm$ for notational simplicity, we propose the following $(2,2)$ para-supersymmetry algebra representation on the $(1,1)$ superfields:
-\begin{align}
-\label{q1} Q^1_\pm&=\frac{\p}{\p\theta^\pm}+\theta^\pm\p_\pm \\
-\label{q2} Q^2_\pm\Phi^i&=(K_\pm)^i_j(\Phi)D_\pm\Phi^j,
-\end{align}
-where $D_\pm =\frac{\p}{\p\theta^\pm}-\theta^\pm\p_\pm$.
-In \cite{HullTwistedSUSY}, it was shown that in order for \eqref{q1} and \eqref{q2} to generate the superalgebra \eqref{eq:(2,2)para}, the bosonic part of $(K_\pm)^i_j(\Phi)$, $(K_\pm)^i_j(\phi)$, must be a tangent bundle endomorphism on the target manifold such that $K^2=\id$.
-Moreover, $K_\pm$ must be integrable in the sense that the Nijenhuis tensors $N_{K_\pm}$ \eqref{eq:nijenhuis} vanish and $K_\pm$ are parallel with respect to the following connections $\n^\pm$
-\begin{align*}
-\n^\pm K_\pm=0, \quad \n^\pm=\lc\pm\frac{1}{2}\eta^{-1}H,
-\end{align*}
-$\lc$ being the Levi-Civita connection of $\eta$.
-Additionally, the requirement that \eqref{q2} is a symmetry of the action \eqref{eq:(1,1)action} imposes the following algebraic relations between $K,\eta$ and $b$:
-\begin{align*}
-g(T_\pm\cdot,\cdot)+g(\cdot,T_\pm\cdot)&=0\\
-b(T_\pm\cdot,\cdot)+b(\cdot,T_\pm\cdot)&=0.
-\end{align*}
-
-We conclude that $(\eta,K_\pm,b)$, where $\rd b=H$ is a local potential for the $3$-form flux $H\in\Omega_{cl}^3$, is a {\bf bi-para-Hermitian} structure.
-Equivalently, this is the defining data of a {\bf generalized para-K\"ahler structure} $(\KK_\pm)$ on the Courant algebroid $(\TT)$ with a flux $H$.
-
-\paragraph{Action on superfields} The infinitesimal action of the element $Q^1_{\pm} \in \mathfrak{t}_{(2,2)}$ is:
-\begin{align}\label{Q1_phi}
-\Phi^i \mapsto \Phi^i + \epsilon^{\pm}_1 \left( \frac{\p}{\p\theta^\pm}+\theta^\pm\p_\pm \right) \Phi^i
-\end{align}
-where $\epsilon^{\pm}_1$ is an infinitesimal odd parameter. Similarly, the infinitesimal action by the element $Q^2_{\pm} \in \mathfrak{t}_{(2,2)}$ is:
-
-\begin{align}\label{Q2_phi}
- \Phi \mapsto \Phi + \epsilon^{\pm}_2 (K_\pm)^i_j(\Phi)D_\pm\Phi^j
-\end{align}
-where $\epsilon^\pm_2$ is again an infinitesimal parameter. Expanding \eqref{Q1_phi}, we get
-\begin{align}\label{Q1_action}
-\begin{aligned}
-Q^1_{+} : (\phi^i, \psi^i_+, \psi^i_-, F^i) &\mapsto (\phi^i, \psi^i_+,\psi^i_-, F^i) + \epsilon^+_1 (\psi^i_+, -\partial_+ \phi, -F^i, \partial_+ \psi^i_-),\\
-Q^1_{-} : (\phi^i, \psi^i_+, \psi^i_-, F^i)  &\mapsto (\phi^i, \psi^i_+,\psi^i_-, F^i) + \epsilon^-_1 (\psi^i_-, -\partial^i_- \phi^i, + F^i, - \partial_- \psi^i_+). 
-\end{aligned}
-\end{align}
-Similarly, expanding \eqref{Q2_phi} gives \textcolor{red}{variations of $F$ are still wrong, need to be finished}
-\begin{align}\label{Q2_action}
-\begin{aligned}
-Q^2_{+} : (\phi^i, \psi^i_+, \psi^i_-, F^i) \mapsto &\  (\phi^i, \psi^i_+, \psi^i_-, F^i)
-+\epsilon_2^+\Big((K_+)^i_j \psi_+ ^j\ ,\  (K_+)^{i}_{j} \partial_+ \phi^j\\
-& -\partial_k(K_+)^i_j \psi_+^k \psi_+^j\ ,\ -(K_+)^i_j F^j{-}\p_k(K_+)^i_j\psi^k_-\psi^j_+\ ,\ \\
-&-(K_+)^i_j\p_+\psi_-^j+\p_k(K_+)^i_j\psi^k_+F^j+\p_k(K_+)^i_j\psi^k_-\p_+\phi^j\Big)\\
-Q^2_{-} : (\phi^i, \psi^i_+, \psi^i_-, F^i) \mapsto &\ (\phi^i, \psi^i_+, \psi^i_-, F^i)
-+\epsilon_2^-\Big((K_-)^i_j \psi_- ^j\ ,\ - (K_-)^i_j F^j  \\
-&-\partial_k(K_-)^i_j \psi_+^k \psi_-^j\ ,\ -\p_k(K_-)^i_j\psi^k_-\psi^j_-+(K_-)^{i}_{j} \partial_- \phi^j\ ,\  \\
-&(K_-)^i_j\p_-\psi_+^j+\p_k(K_-)^i_j\psi^k_-F^j-\p_k(K_-)^i_j\psi^k_+\p_-\phi^j\Big).
-\end{aligned}
-\end{align}
-%
-%\begin{lemma}
-%Expanding out in the components of the $(1,1)$ superfield, the infinitesimal action by $Q^1_{+}$ and in Equation (\ref{q1}) reads:
-%\[
-%Q^1_{+} : (\phi^i, \psi^i_+, \psi^i_-, F^i) \mapsto (\phi^i, \psi^i_{\pm}, F^i) + \epsilon^+_1 (\psi^i_+, \partial_+ \phi, F^i, \partial_+ \psi^i_-) . 
-%\]
-%and by $Q^1_-$:
-%\[
-%Q^1_{-} : (\phi^i, \psi^i_+, \psi^i_-, F^i)  \mapsto (\phi^i, \psi^i_{\pm}, F^i) + \epsilon^-_1 (\psi^i_-, \partial^i_- \phi^i, - F^i, - \partial_- \psi^i_+)
-%\]
-%Similarly, the infinitesimal action by $Q^2_{+}$ in Equation (\ref{q2}) reads:
-%\begin{equation}\label{q2plus}
-%Q^2_{+} : (\phi^i, \psi^i_+, \psi^i_-, F^i) \mapsto ((K_+)^i_j \psi_+ ^j , - (K_+)^{i}_{j} \partial_+ \phi^j - \partial_k(K_+)^i_j \psi_+^k \psi_+^k, (K_+)^i_j F^j+\p_k(K_+)^i_j\psi^k_-\psi^j_+, \brian{F term})
-%\end{equation}
-%and for $Q^2_-$:
-%\begin{equation}\label{q2minus}
-%Q^2_{-} : (\phi^i, \psi^i_+, \psi^i_-, F^i) \mapsto ((K_-)^i_j \psi_- ^j , - (K_-)^{i}_{j} \partial_- \phi^j - \partial_k(K_-)^i_j \psi_-^k \psi_-^k, (K_-)^i_j F^j+\p_k(K_-)^i_j\psi^k_+\psi^j_-, \brian{F term})
-%\end{equation}
-%\end{lemma}
-%
-%%\begin{align}\label{Q12_action}
-%%\begin{aligned}
-%%[Q_\pm^1 ,\phi^i]&=\psi_\pm^i,& [Q_\pm^2 ,\phi^i] &=(K_\pm)^i_j\psi_\pm^j,\\
-%%[Q_\pm^1 ,\psi^i_\pm] &=\p_\pm\phi^i,& [Q_\pm^2 ,\psi^i_\pm] &=-(K_\pm)^i_j\p_+\phi^j{\textcolor{red}{+}}\p_k(K_\pm)^i_j\psi_+^k\psi_+^j\\
-%%[Q_\pm^1 ,\psi^i_\mp]&=\pm F^i,& [Q_\pm^2 ,\psi^i_\mp] &=(K_\pm)^i_jF^j+\p_k(K_\pm)^i_j\psi^k_\mp\psi^j_\pm.
-%%\end{aligned}
-%%\end{align}
-%%
-%%\textcolor{red}{There's a sign issue above, the $+$ needs to be $-$.}
-%\begin{proof}
-%Recall, in components the superfield is of the form
-%\[
-%\Phi^i =\phi^i+\theta^+\psi^i_++\theta^-\psi^i_-+\theta^+\theta^-F^i .
-%\]
-%The action of the $Q^1_\pm$ charges is straightforward and can be simply read off from the infinitesimal action. 
-%%\begin{align*}
-%%[Q^1_\pm,\Phi]=[Q_\pm^1,\phi^i]+[Q_\pm^1,\psi^i_\pm]\theta^\pm+[Q_\pm^1,\psi^i_\mp]\theta^\mp+[Q_\pm^1,F]\theta^\pm\theta^\mp.
-%%\end{align*}
-%%For instance $[Q_{\pm}^1, \phi^i] = \theta^{\pm} \partial_{\pm} \phi^i$, thus 
-%To obtain the action by the charges $Q^2_\pm$ on the individual components we first need to expand $K_\pm(\Phi)$ in terms of the components of the superfield:
-%\begin{align*}
-%(K_\pm)^i_j(\Phi)=(K_\pm)^i_j(\phi)+\p_k(K_\pm)^i_j\theta^+\psi_+^k+\p_k(K_\pm)^i_j\theta^-\psi_-^k+\p_k(K_\pm)\theta^+\theta^-F^k,
-%\end{align*}
-%so that the infinitesimal action by $Q^2_\pm$ on $\Phi^i$ is:
-%\begin{align}
-%\Phi^i + \epsilon_2^\pm (K_\pm)^i_j(\Phi)(\psi^j_\pm\pm\theta^\mp F^j-\theta^\pm\p_\pm\phi^j\mp\theta^+\theta^-\p_\pm\psi^j_\mp) .
-%\end{align}
-%Reading off the various components this expression yields Equations (\ref{q2plus}) and (\ref{q2minus}).
-%\end{proof}
-
-%
-%\paragraph{The $(2,2)$ formalism}
-%\brian{
-%There is the following superspace model for $(2,2)$ parasupersymmetry. 
-%Consider the superspace $\RR^{1,1 | 4}$ 
-%}
-
-\subsection{$(2,1)$ and $(2,0)$ parasupersymmetry}
-\brian{Turn this whole section into a loose discussion.}
-Many of the constructions above make sense when there is less total supersymmetry, and we briefly mention two important cases. The first concerns the $(2,1)$ parasupersymmetry algebra.
-This algebra $\mathfrak{t}_{(2,1)}$ consists of generators $\{Q^1_\pm, Q^2_+\}$ satisfying the same algebra as in (\ref{eq:(2,2)para}). 
-Starting with the $(1,1)$ supersymmetric $\sigma$-model (\ref{eq:(1,1)action}), and labeling the odd coordinates by $\theta^\pm = \theta_1^\pm$, one can ask for an additional odd symmetry 
-\[
-Q^2_+ :  \Phi \mapsto \Phi + \epsilon_2^+ K_+(\Phi)^j_i D_+ \Phi^i
-\]
-which determines a symmetry by the $(2,1)$ parasupersymmetry algebra.
-
-\begin{proposition}
-The odd vector field $Q_2^+$ is a symmetry of the $(1,1)$ supersymmetric $\sigma$-model provided $(K_+)^{j}_i$ is a paracomplex structure satisfying \brian{What conditions here?}
-Thus, the $(1,1)$ supersymmetric $\sigma$-model has $(2,1)$ parasupersymmetry provided the target is \brian{same conditions}. 
-\end{proposition}
-
-The next symmetry algebra we wish to consider is the $(2,0)$ parasupersymmetry algebra $\mathfrak{t}_{(2,0)}$. 
-This algebra has the same even generators as the $(2,1)$ and $(2,2)$ algebras, and odd generators $\{Q^1_+, Q^2_+\}$ satisfying the relations
-\[
-[Q^1_+, Q^1_+] =  2 \partial_\pm \;\;\; , \;\;\; [Q^2_+, Q^2_+] = - 2 \partial_\pm
-\]
-
-\brian{The (1,0) action}
-
-We propose an extended symmetry of the $(1,0)$ $\sigma$-model by the following action by the odd vector field $Q_+^2$:
-\[
-Q^2_+ : \Phi \mapsto \Phi + \epsilon_2^+ K_+(\Phi)^j_i D_+ \Phi^i .
-\]
-
-\begin{proposition}
-The odd vector field $Q_2^+$ is a symmetry of the $(1,0)$ supersymmetric $\sigma$-model provided $(K_+)^{j}_i$ is a paracomplex structure. 
-Thus, the $(1,0)$ supersymmetric $\sigma$-model has $(2,0)$ parasupersymmetry provided the target is paracomplex. \brian{there is a version for a target vector bundle as well...}
-\end{proposition}
-
-\subsection{Topological twists}\label{sec:toptwist}
-
-\btd{Can you outline what is meant here by twisting?
-We aren't going to use the full language of twisting as in Kevin's paper, but it'd be good to highlight two things: (1) how to use the $R$-symmetry to twist the transformation properties of the fields and (2) how the supercharge deforms the BRST differential.
-I think you already do both below, but it'd be good to add some more discussion. 
-For instance, in accomplishing (1) we should say concretely which bundles each of the fields live in.}
-
-In this section we show that the R-symmetry of the para-$(2,2)$ superalgebra can be used to produce topological theories from the $(2,2)$ para-supersymmetric model presented in the Section \ref{sec:(2,2)parasusy} via a procedure called topological twisting, exactly analogous to topological twisting in ordinary supersymmetry.
-We show that the theories we obtain match the topological theories constructed in the Section \ref{sec:GpC_AKSZ} in the AKSZ formalism.
-
-In our presentation, we use the similarities between the generalized K\"{a}hler (GK) and generalized para-K\"{a}hler (GpK) geometries, and we follow the approach presented in \cite{Kapustin:2004gv} for the GK case.
-Let us briefly review the construction now.
-
-Let $(\eta,K_\pm,H=\rd b)$ be the bi-para-Hermitian geometry of the $(2,2)$ para-SUSY sigma model and let $\{Q^1_\pm,Q^1_\pm\}$ be the basis of the superalgebra \eqref{eq:(2,2)para}.
-Our goal is to use the data of the $(2,2)$ para-SUSY theory to define a new, {\it topological} theory.
-In this section, we will show how to define the BRST complex for this new theory, which in particular requires the definition of a nilpotent BRST operator $\QQ^2=0$.
-Additionally, we want all fields in this complex to be scalars under the Lorentz group.
-For this, we must alter the original Lorentz group $SO(1,1)$ by its embedding in the R-symmetry group, $SO(1,1)_{G_R}\hookrightarrow G_R=SO(1,1)_+\times SO(1,1)_-$, so that the new Lorentz group action is given by the diagonal embedding of $SO(1,1)$ into $SO(1,1)\times SO(1,1)_{G_R}$
-\begin{align}\label{embeddings}
-SO(1,1)\overset{diag.}{\hookrightarrow} SO(1,1)\!\times\! SO(1,1)_{G_R}\!\!\hookrightarrow SO(1,1)\!\times\! \overbrace{SO(1,1)_+\!\times\! SO(1,1)_-}^{G_R},
-\end{align}
-defining a new Lorentz action, which will be a sum of the original one and the action of $SO(1,1)_{G_R}$ in $G_R$.
-In this sense, the Lorentz group gets {\it twisted} by the embedding into the R-symmetry group.
-Finally, the operator $\QQ$ must be chosen accordingly to the choice of $SO(1,1)_{G_R}\hookrightarrow G_R$ so that it transforms as a scalar itself under the new Lorentz action, which ensures that the fields in the BRST complex it defines are all scalars too.
-
-%\david{how does the embedding of $SO(1,1)$ into $G_R$ reflect on the definition of $\QQ$?}
-%\brian{In Euclidean space, we choose an embedding $SO(2) \hookrightarrow G_R$. 
-%Then, the twisting supercharge is required to be invariant.
-%The obvious analog is to require an embedding $SO(1,1) \to G_R$ for which $\QQ$ is invariant.
-%This is the twisting homomorphism which tells us how to modify the Lorentz group.
-%}
-%
-%\brian{
-%There is another piece of data we have to fix to get the $\mathbb{Z}$-grading in the twisted theory. 
-%Ordinarily this amounts to picking a homomorphism $U(1) \to G_R$ for which $\QQ$ is weight one. 
-%It appears no such twisting homomorphism is possible.
-%Indeed, every group homomorphism $U(1) \to SO(1,1) \times SO(1,1)$  are necessarily trivial since $U(1)$ is compact and $SO(1,1) \cong \RR \oplus \RR$ (the first copy is the connected component of the identity, and the second component is the connected component of minus identity).
-%This means we may have to slightly reimagine what ``twisting data" is here.
-%Since there is at least a copy of $\RR$ in $SO(1,1)$ we can probably use this to define a ``weight".}
-\bigskip
-Let us start with the second, twisting, embedding in \eqref{embeddings}
-\begin{align*}
-\rho:\ SO(1,1)_{G_R}\hookrightarrow G_R=SO(1,1)_+\times SO(1,1)_-.
-\end{align*}
-Clearly, there are two inequivalent choices -- the diagonal and anti-diagonal -- and we shall label them as $SO(1,1)_V$ and $SO(1,1)_A$, respectivelly, and  calling the twist by $SO(1,1)_{V/A}$ the {\bf generalized para-A/B-twist}.
-Explicitly, if we represent $M_\pm\in SO(1,1)$ in \eqref{r_symmetry_matrix} as
-\begin{align*}
- M_\pm(\alpha)\begin{pmatrix}
- Q^1_\pm\\
- Q^2_\pm
- \end{pmatrix}=\begin{pmatrix}
- \cosh(\alpha) & \sinh(\alpha) \\
- \sinh(\alpha) & \cosh(\alpha)
- \end{pmatrix}
- \begin{pmatrix}
- Q^1_\pm\\
- Q^2_\pm
- \end{pmatrix},
- \end{align*}
-then the diagonal embedding is given by $M(\alpha) \mapsto (M(\alpha),M(\alpha))$ while the anti-diagonal is $M(\alpha) \mapsto (M(\alpha),M(-\alpha))$.
-
-To determine the corresponding nilpotent operators $\QQ_{V/A}$ on which $V$ and $A$ act trivially, we find that the following combinations of the supercharges
-\begin{align*}
-Q_{L\pm}=\frac{1}{2}(Q^1_+\pm Q^2_+),\quad Q_{R\pm}=\frac{1}{2}(Q^1_-\pm Q^2_-),
-\end{align*}
-are all nilpotent and satisfy $[Q_{L\pm},Q_{L\pm}]=0$, so that their sums and differences will also be nilpotent.
-However, they are charged under the Lorentz group.
-Their Lorentz charges along with their charges under $SO(1,1)_{V/A}$ are summarized in the following table
-\bigskip
-\begin{center}
-\begin{tabular}{c|c c c}
-		& $SO(1,1)_{Lor.}$ & $SO(1,1)_V$ & $SO(1,1)_A$\\ \hline
-$Q_{L+}$& $-1$ & $+1$ & $+1$\\
-$Q_{L-}$& $-1$ & $-1$ & $-1$\\
-$Q_{R+}$& $+1$ & $+1$ & $-1$\\
-$Q_{R-}$& $+1$ & $-1$ & $+1$
-\end{tabular}.
-\end{center}
-\bigskip
-From the above table, we can read off that the combination $\QQ_V=Q_{L+}+Q_{R-}$ will transform as a scalar under the new Lorentz group twisted by $U(1,1)_V$ and $\QQ_A=Q_{L+}+Q_{R+}$ will transform as a scalar under the new Lorentz group twisted by $U(1,1)_A$.
-Note also that the two are related by $Q_-^2\mapsto -Q_-^2$ and because $Q_-^2=K_-D_-$, this is acheived by changing the sign of $K_-$.
-Therefore, in the following we will study without loss of generality the twist given by $U(1,1)_A$ and $\QQ_B$, i.e.
-the generalized para-B-model:
-
-\begin{Def}\label{def:B-twist}
-The generalized para-B-model is a topological twist (in the above sense) of a $(2,2)$ para-SUSY sigma model given by the diagonal embedding of the Lorentz group $SO(1,1)\hookrightarrow SO(1,1)\times SO(1,1)_A$, where $SO(1,1)_A$ denotes the anti-diagonal embedding of $SO(1,1)$ into the R-symmetry group $G_R=SO(1,1)\times SO(1,1)$, and the nilpotent scalar BRST operator
-\begin{align}\label{QQ_nilpotent}
-\QQ=Q_L+Q_R,\quad Q_L=\frac{1}{2}(Q^1_++Q^2_+),\quad Q_R=\frac{1}{2}(Q^1_-+Q^2_-).
-\end{align}
-\end{Def}
-\bigskip
-We now turn to the BRST complex that describes the scalar fields in the twisted theory. For this, we introduce the usual notation 
-\begin{align*}
-\chi=\frac{1}{2}(\id+K_+)\psi_+=P_+\psi_+=\psi_+^{(1,0)_+},\quad\lambda=\frac{1}{2}(\id+K_-)\psi_-=P_-\psi_-=\psi_-^{(1,0)_-},
-\end{align*}
-where both $\chi$ and $\lambda$ are scalars under the twisted Lorentz action, which is the content of the following statement:
-\begin{proposition}\label{prop_toptwist}
-The action of $Q_{L/R}$ on the fields $\chi$, $\lambda$ and $\phi$ is given by
-\begin{align}\label{eq:Qcoh}
-\begin{aligned}
-[Q_L,\phi^i]&=\chi^i & [Q_R,\phi^i]&=\lambda^i\\
-[Q_L,\chi^i]&=0 & [Q_R,\lambda^i]&=0\\
-[Q_L,\lambda^i]&=-(\Gamma^-)^i_{jk}\chi^j\lambda^k & [Q_R,\chi^i]&=-(\Gamma^+)^i_{jk}\lambda^j\chi^k.
-\end{aligned}
-\end{align}
-\end{proposition}
-\begin{proof}
-See Appendix \ref{appendix:proof_prop}.
-\end{proof}
-Recalling that $(\Gamma^+)^i_{jk}=(\Gamma^-)^i_{kj}$ (see \eqref{Gamma-pm}), we find that the BRST degrees of the fields are given by the following complex
-\begin{align*}
-&\phi \overset{\QQ}{\longrightarrow}\chi+\lambda\overset{\QQ}{\longrightarrow} 0\\
-&0 \phantom{\longrightarrow\longrightarrow} 1
-\end{align*}
-\noindent
-The observables of the twisted theory are therefore polynomials in the odd variables $\chi,\lambda$ with even coefficients dependent on $\phi$:
-\begin{align*}
-{\cal O}_f=f(\phi)_{i_1\cdots i_a,j_1\cdots j_b}\chi^{i_1}\cdots\chi^{i_a}\lambda^{j_1}\cdots\lambda^{j_b}.
-\end{align*}
-
-Because $\chi \in \XX^{(1,0)_+}$ and $\lambda \in \XX^{(1,0)_-}$, we can identify ${\cal O}_f$ with a function on the supermanifold $(T^{(1,0)_+}\oplus T^{(1,0)_-})[1]$, which in turn can be identified with the mixed differential form
-\begin{align*}
-\Omega_f=f(\phi)_{i_1\cdots i_a,j_1\cdots j_b}dx^{i_1}_+\cdots dx^{i_a}_+ dx^{j_1}_- \cdots dx^{j_b}_-,
-\end{align*}
-where $dx_\pm$ are the one-forms satisfying $K_\pm dx_\pm=dx_\pm$, i.e. sections of the bundle $T^*_{(1,0)_\pm}$. Via this identification, the operator ${\cal Q}\coloneqq Q_L+Q_R$ defines an operator
-\begin{align*}
-\rd_\QQ:\ \Lambda^\bullet(T^{*(1,0)_+}\oplus T^{*(1,0)_-})\rightarrow \Lambda^{\bullet +1}(T^{*(1,0)_+}\oplus T^{*(1,0)_-})
-\end{align*}
-Since $\QQ$ squares to zero the operator $\rd_\QQ$ also squares to zero, hence it defines a differential. 
-In fact, we will see that $\rd_\QQ$ gives rise to a Chevalley-Eilenberg complex $\text{CE}(L_{twist})$ computing the Lie algebroid cohomology of a certain Lie algebroid.
-
-\paragraph{Lie algebroid from bi-para-Hermitian data} 
-Consider the Lie algebroid $L_{twist}\overset{a}{\rightarrow} T$ with $L_{twist}=T^{(1,0)_+}\oplus T^{(1,0)_-}$ and anchor given by the sum of the two inclusions $\imath_\pm:\ T^{(1,0)_\pm}\hookrightarrow T$:
-\begin{align*}
-a:L_{twist}=T^{(1,0)_+}\oplus T^{(1,0)_-} &\rightarrow T\\
- e=(x_+,x_-) &\mapsto \imath_+(x_+)+\imath_-(x_-).
-\end{align*}
-From \eqref{eq:Qcoh} we can read off the action of $\rd_\QQ$ on degree one elements, i.e. sections $\alpha=(\alpha^+,\alpha^-)$ of $L^*_{twist}=T^*_{(1,0)_+}\oplus T^*_{(1,0)_-}$:
-\begin{align*}
-\rd_\QQ\alpha&=\p_k\ap_i^+[dx_+^k+dx_-^k]\w dx_+^i-\ap^+_i(\Gamma^+)^i_{jk}dx_-^j\w dx_+^k\\
-&+\p_k\ap_i^-[dx_+^k+dx_-^k]\w dx_-^i-\ap^-_i(\Gamma^-)^i_{jk}dx_+^j\w dx_-^k.
-\end{align*}
-%In coordinate-free form, we get
-%\begin{align*}
-%\rd_\QQ\ap=(\p_++\n^+_{P_-(\bullet)})\ap^++(\p_-+\n^-_{P_+(\bullet)})\ap^-,
-%\end{align*}
-By contracting in two sections of $L_{twist}$, $e_1=x_++x_-$, $e_2=y_-+y_-$, we get the coordinate-free expression
-\begin{align}\label{eq:dQ}
-\begin{aligned}
-(\rd_\QQ\ap)(e_1,e_2)&=(\p_+\ap^+)(x_+,y_+)+\n^+_{x_-}\ap^+(y_+)-\n^+_{y_-}\ap^+(x_+)\\
-&+(\p_-\ap^-)(x_-,y_-)+\n^-_{x_+}\ap^-(y_-)-\n^-_{y_+}\ap^-(x_-),
-\end{aligned}
-\end{align}
-where $\p_\pm$ denotes the para-complex Dolbeault operators \eqref{paracomplex_dels} of the para-complex structure $K_\pm$.
-We can further rewrite this expression by writing $\ap=(\eta(\tl{z}_+),\eta(\tl{z}_-))$ for $\tl{z}_\pm \in \se(T^{(1,0)_\pm})$, invoking the formula $\p_\pm\ap^\pm(x_\pm,y_\pm)=\lc_{x_\pm}\ap^\pm(y_\pm)-\lc_{y_\pm}\ap^\pm(x_\pm)$ and recalling $\n^\pm=\lc\pm \frac{1}{2}\eta^{-1}H$:
-\begin{align}
-\begin{aligned}
-(\rd_\QQ\ap)(e_1,e_2)&=\eta((\lc_{x_+}+\n_{x_-}^+)\zt_+,y_+)-\eta((\lc_{y_+}+\n_{y_-}^+)\zt_+,x_+)\\
-&+\eta((\lc_{x_-}+\n_{x_+}^-)\zt_-,y_-)-\eta((\lc_{y_-}+\n_{y_+}^-)\zt_-,x_-)\\
-&=\eta(\n^+_{x_++x_-}\zt_+,y_+)-\eta(\n_{y_++y_-}^+\zt_+,x_+)-H(x_+,\zt_+,y_+)\\
-&+\eta(\n_{x_++x_-}^-\zt_-,y_-)-\eta(\n_{y_++y_-}^-\zt_-,x_-)+H(x_-,\zt_-,y_-).
-\end{aligned}
-\end{align}
-This fully determines the Lie algebroid structure of $L_{twist}$.
-Therefore, the topological twist gives rise to the Lie algebroid we just described explicitly using only the data of the bi-para-Hermitian geometry $(\eta,K_\pm,H)$.
-In the following paragraph, we will discuss how the same Lie algebroid arises from the data of the corresponding generalized para-K\"ahler structure.
-
-\paragraph{Lie algebroid from generalized para-K\"ahler data}
-%
-%\brian{Do we use the full GpK structure, or are we only using the GpC?}
-%\btd{The title of this section is OK, but we should stress that the Lie algebroid {\em explicitly} does not depend on any Kahler data.}
-%\btd{I suggest renaming $\Lb_+$ to $L_{AKSZ}$, or something else to denote the fact that is the Lie algebroid coming from the AKSZ description in Section \ref{sec: AKSZ}.}
-We will now show that the Lie algberoid $(L_{twist},\rd_\QQ,a)$ is isomorphic to one defined by the $+1$-eigenbundle of the generalized para-complex structure $\KK_+$ of the generalized para-K\"ahler structure $(\KK_+,\KK_-)$ underlying the $(2,2)$ para-SUSY theory.
-Therefore, $(L_{twist},\rd_\QQ,a)$ coincides with the Lie algebroid used in Section \ref{sec: AKSZ} to define a topological theory in the AKSZ formalism from an arbitrary generalized para-complex structure $\KK$.
-Consequently, we find that the theories constructed in Section \ref{sec: AKSZ} labeled by a GpC structure $\KK$ can be realized as topological twists of a $2D$ $(2,2)$ para-SUSY $\sigma$-models whenever $\KK$ is a part of a GpK data $(\KK_+=\KK,\KK_-)$.
-
-Recall that a GpK structure defines the decomposition \eqref{GpK_bundles}
-\begin{align*}
-\TT=\ell_+\oplus\ell_-\oplus \ellt_+\oplus \ellt_-,
-\end{align*}
-where the the eigenbundles of $\KK_+$ are $\Lb_+=\ell_+\oplus\ell_-$ and $\wtl{\Lb}_+=\ellt_+\oplus \ellt_-$.
-Because $\Lb$ is a Dirac structure, it defines a Lie algebroid by restriction of the Courant algebroid on $\TT$ to $\Lb_+$, i.e.
-the Lie algebroid bracket and anchor are given by the restriction of the Dorfman bracket and the projection onto tangent bundle, respectively (see Proposition \ref{prop:dirac_Liealg}).
-We now show that such Lie algebroid is isomorphic to the Lie algebroid defined by $(L_{twist},\rd_\QQ,a)$ above:
-\begin{theorem}
-The Lie algebroids $(L,a,\rd_\QQ)$ and $(\Lb_+,\pi_T\!\!\mid_{\Lb_+},\brac\!\!\mid_{\Lb_+})$ are isomorphic via the map $\pi=\pi_+\oplus \pi_-$.
-\end{theorem}
-\begin{proof}
-First, we notice that the bundles themselves are related by $\pi$,  $\pi(\Lb_+)=\pi(\ell_+\oplus \ell_-)=\pi_+(\ell_+)\oplus \pi_-(\ell_-)=T^{(1,0)_+}\oplus T^{(1,0)_-}=L$ and also $\pi$ is clearly an isomorphism since both $\pi_\pm$ are.
-Additionally, the anchors are related by $a\circ\pi=\pi_T\!\!\mid_{\Lb_+}$.
-The only non-trivial task is therefore to show that the respective differentials satisfy
-\begin{align}\label{eq:d_pi}
-\pi^*\circ\rd_Q  =\rd_{\Lb_+}\circ \pi^*,
-\end{align}
-where $\pi^*=\pi^*_+\oplus\pi_-^*$ is given by the dual maps to $\pi_\pm:\ell_+\rightarrow T^{(1,0)_\pm}$, extended to a map $\pi^*:\Lambda^k(L^*)\rightarrow\Lambda^k(\Lb_+^*)$.
-
-Because of the chain rule, we only need to check \eqref{eq:d_pi} on degree $0$ and degree $1$ elements in the respective complexes. Degree $0$ follows immediately:
-\begin{align*}
-(\rd_Q f)(\pi(u))= a\circ \pi(u)[f]=\pi_T\!\!\mid_{\Lb_+}(u)[f]=(\rd_{\Lb_+}f)(u),
-\end{align*}
-%For degree one, we use the decomposition of the respective bundles and check for each component
-%\begin{alignat*}{2}
-%\rd_Q:&&T^*_{(1,0)_+}\oplus T^*_{(1,0)_-} &\rightarrow \Lambda^2(T^*_{(1,0)_+}\oplus T^*_{(1,0)_-})\\
-%\rd_{\Lb_+}:&& \ell_+^*\oplus \ell_-^* &\rightarrow \Lambda^2(\ell_+^*\oplus \ell_-^*)
-%\end{alignat*}
-and we will now prove \ref{eq:d_pi} for degree $1$ elements. In the following we will make use of the identifications provided by the metric $\eta$ and pairing $\lara$:
-\begin{alignat*}{2}
-\eta:&&\  T^*_{(1,0)_\pm} &\leftrightarrow T^{(0,1)_\pm}\\
-\lara:&& \ell^*_\pm &\leftrightarrow \ellt_\pm,
-\end{alignat*}
-so that elements in $T^*_{(1,0)_\pm}$ can be written as $\eta(\tl{z}_\pm)$ with $\tl{z}_\pm$ vector in $T^{(0,1)_\pm}$ and similarly, elements in $\ell^*_\pm$ can be expressed as $\la \tl{w}_\pm, \cdot\ra$ with $\tl{w}_\pm$ section of $\ellt_\pm$.
-To declutter notation, we shall also denote the bracket and anchor on $\Lb_+$ by $\brac$ and $\pi$, respectively.
-
-The differential $\rd_{\Lb_+}$ is defined by the bracket on the Lie algebroid $\Lb_+$ via the following formula:
-\begin{align}\label{eq:proof_Liethm}
-\rd_{\Lb_+}  w^* (u,v)=\pi(u) w^*(v)-\pi(u) w^*(v)- w^*([u,v]),
-\end{align}
-where $ w^* \in \se(\Lb_+^*)$ and $u,v\in \se(\Lb_+)$. Writing $ w^*$ as $\la \tl{w},\cdot\ra$, with $\tl{w}\in\se (\tl{\Lb}_+)$ we can rewrite this as
-\begin{align}\label{dL}
-\begin{aligned}
-\rd_{\Lb_+}  w^* (u,v)&=\pi(u)\la v ,\tl{w}\ra-\pi(v)\la u,\tl{w}\ra-\la [u,v],\tl{w}\ra\\
-&=\la D_uv,\tl{w}\ra+\la v,D_u \tl{w}\ra-\la D_v u,\tl{w}\ra-\la u,D_v\tl{w}\ra-\la D_uv-D_vu,\tl{w}\ra\\
-&+{T}(u,v,\tl{w})\\
-&=\la D_u \tl{w},v\ra-\la D_v\tl{w},u\ra+{T}(u,v,\tl{w})\\
-&=\la D_u \tl{w}_+,v_+\ra-\la D_v\tl{w}_+,u_+\ra+{T}(u_+,v_+,\tl{w}_+)\\
-&+\la D_u \tl{w}_-,v_-\ra-\la D_v\tl{w}_-,u_-\ra+{T}(u_-,v_-,\tl{w}_-),
-\end{aligned}
-\end{align}
-where we used \eqref{gentorsion_def} to express $\brac$ in terms of $D$, the generalized Bismut connection of the generalized metric for the GpK structure.
-We then used the fact that $D$ preserves $\lara$, $C_\pm$ as well as $\Lb_+$ and that $T$ only has components in $\Lambda^3 C_+\oplus\Lambda^3 C_-$ \cite{Gualtieri:2010fd}.
-
-We will now show that $\rd_{\Lb_+}$ is related to $\rd_\QQ$ via \eqref{eq:d_pi}, so that $\rd_\QQ=(\pi^{-1})^*\circ \rd_{\Lb_+}\circ \pi^*$, i.e.
-\begin{align*}
-\rd_\QQ\ap(e_1,e_2)=\rd_{\Lb_+}(\pi^*\ap)(\pi^{-1}e_1,\pi^{-1}e_2).
-\end{align*}
-To read this off from \eqref{dL} and compare with \eqref{eq:dQ}, we need to express $\pi^*\ap$ as $\pi^*\ap=w^*=\la \tl{w},\cdot\ra$ for some $\tl{w}\in\se (\tl{\Lb}_+)$ and $\ap=(\eta(\zt_+),\eta(\zt_-))$:
-\begin{align*}
-\pi^*\ap=\pi^*(\eta(\zt_+),\eta(\zt_-))=(\eta(\zt_+,\pi_+\cdot),\eta(\zt_-,\pi_-\cdot))=\frac{1}{2}\la\pi^{-1}(\zt_+,-\zt_-),\cdot\ra,
-\end{align*}
-where $\zt_\pm\in \se(T^{(1,0)_\pm})$ and we used \eqref{pi:gG_relationship}.
-Therefore, denoting $e_1=(x_+,x_-)$ and $e_2=(y_+,y_-)$ as in \eqref{eq:dQ}, \eqref{dL} yields (denoting $e_1=(x_+,x_-)$ and $e_2=(y_+,y_-)$ as in \eqref{eq:dQ})
-\begin{align*}
-\rd_{\Lb_+}(&\pi^*\ap)(\pi^{-1}e_1,\pi^{-1}e_2)\\
-&=\eta(\n^+_{x_++x_-}\zt_+,y_+)-\eta(\n^+_{y_++y_-}\zt_+,x_+)+\frac{1}{2}T(\pi_+^{-1}x_+,\pi_+^{-1}y_+,\pi_+^{-1}\zt_+)\\
-&+\eta(\n^-_{x_++x_-}\zt_-,y_-)-\eta(\n^-_{y_++y_-}\zt_-,x_-)-\frac{1}{2}T(\pi_-^{-1}x_-,\pi_-^{-1}y_-,\pi_-^{-1}\zt_-),
-\end{align*}
-where we used \eqref{genBismut_pi_nabla_pm} and once again \eqref{pi:gG_relationship}.
-Finally, invoking \eqref{gentorsion_H}, we arrive at \eqref{eq:dQ}, showing that \eqref{eq:d_pi} holds and completing the proof.
-\end{proof}
-
-We have therefore shown that the observables in the topologically twisted theories are given by the Lie algebroid cohomology of $\Lb$, which is exactly the same as for the $2D$ boundary topological theories constructed in the Section \ref{sec: AKSZ}:
-
-\begin{corollary}
-Let $\Phi:\Sigma^{2|2}\rightarrow \Mb$ be a $(2,2)$ para-supersymmetric $\sigma$-model with the target $(\Mb,\KK_\pm,\GG(\eta,b))$ a Generalized para-K\"ahler manifold.
-Then the generalozed para-B-twist of this $\sigma$-model defined in Definition \ref{def:B-twist} coincides with the $2D$ topological boundary theory determined by the generalized para-complex structure on the Courant algebroid $(\TT)\Mb$ with flux $H\overset{loc.}{=}\rd b$.
-\end{corollary}
-
-\appendix
-\section{Proof of Proposition \ref{prop_toptwist}}\label{appendix:proof_prop}
-\begin{proof}
-The action of $Q_{L/R}$ on $\phi$ can be immediately read off \eqref{Q12_action}:
-\begin{align}
-[Q_L,\phi^i]=\frac{1}{2}[Q_+^1+Q^2_+,\phi^i]=\chi^i.
-\end{align}
-
-We now prove the formulas for the action of $Q_{L/R}$ on $\chi$, the action on $\lambda$ is entirely analogous. First, we expand
-\begin{align}\label{QL_chi}
-[Q_L,\chi^i]=[Q_L,(P_+)^i_j\psi_+^j]=[Q_L,(P_+)^i_j]\psi_+^j{+}(P_+)^i_j[Q_L,\psi_+^j].
-\end{align}
-Because $K_+$ is a function of the bosonic coordinates, we also have $P_+=P_+(\phi)$ and so
-\begin{align}\label{QL_P}
-[Q_L,(P_+)^i_j]=\p_k(P_+)^i_j[Q_L,\phi^k]=\p_k(P_+)^i_j\chi^k.
-\end{align}
-Combining \eqref{QL_chi} and \eqref{QL_P} and using \eqref{Q12_action}, we arrive at
-\begin{align*}
-[Q_L,\chi^i]&=\p_k(P_+)^i_j\chi^k\psi_+^j{+}(P_+)^i_j\left(-(\tl{P}_+)^j_k\p_+\phi^k{-}\frac{1}{2}\p_k(K_+)^j_l\psi_+^k\psi_+^l\right)\\
-&=\p_k(P_+)^i_j(P_+)^k_l\psi_+^l\psi_+^j{-}(P_+)^i_j\p_k(P_+)^j_l\psi_+^k\psi_+^l,
-\end{align*}
-where we denoted $\tl{P}_+=\frac{1}{2}(\id-K_+)$ and used $P_+\tl{P}_+=0$. We now expand the projectors, $(P_+)^i_j=\frac{1}{2}(\delta^i_j+(K_+)^i_j)$:
-
-\begin{align*}
-[Q_L,\chi^i]&=\p_k(P_+)^i_j(P_+)^k_l\psi_+^l\psi_+^j{-}(P_+)^i_j\p_k(P_+)^j_l\psi_+^k\psi_+^l\\
-&=\frac{1}{2}(\p_j(K_+)^i_l(P_+)^j_k{-}(P_+)^i_j\p_k(K_+)^j_l)\psi_+^k\psi_+^l\\
-&=\frac{1}{4}(\p_j(K_+)^i_l(K_+)^j_k{-}(K_+)^i_j\p_k(K_+)^j_l)\psi_+^k\psi_+^l\\
-&+\frac{1}{4}(\p_j(K_+)^i_l\psi_+^j\psi_+^l{-}\p_k(K_+)^i_l\psi_+^k\psi_+^l)=-\frac{1}{2}(N_{K_+})^i_{kl}\psi_+^k\psi^l_+,
-\end{align*}
-where in the last line we rewrote $\psi_+^k\psi^l_+=\frac{1}{2}(\psi^k\psi^l-\psi^l\psi^k)$ to get the expression for the Nijenhuis tensor of $K_+$:
-\begin{align*}
-4(N_{K_+})^i_{kl}=(K_+)^j_k\p_j(K_+)^i_l-(K_+)^j_l\p_j(K_+)^i_k {-} (K_+)^i_j(\p_k(K_+)^j_l-\p_l(K_+)^j_k).
-\end{align*}
-Invoking integrability of $K_+$, $N_{K_+}=$ and we conclude that $[Q_L,\chi^i]=0$.
-
-Similarly, $[Q_L,\lambda]$ can be expanded
-\begin{align}\label{QL_lambda}
-[Q_L,\lambda^i]&=[Q_L,(P_-)^i_j\psi_-^j]=[Q_L,(P_-)^i_j]\psi_-^j+(P_-)^i_j[Q_L,\psi_-^j]\\
-&=\p_k(P_-)^i_j\chi^k\psi_-^j-(P_-)^i_k\left((P_+)^k_jF^j+\frac{1}{2}\p_l(K_+)^k_j\psi^l_-\psi_+^j\right),
-\end{align}
-where we used
-\begin{align*}
-[Q_L,\psi_-^i]=-(P_+)^i_jF^j\textcolor{red}{-}\frac{1}{2}\p_k(K_+)^i_j\psi^k_-\psi_+^j.
-\end{align*}
-Next, we rewrite the derivative in terms of $\n^-$ and use the property $\n^-P_-=0$:
-\begin{align*}
-\p_k(P_-)^i_j&=\n^-_k(P_-)^i_j-(\Gamma^-)^i_{kl}(P_-)^l_j+(\Gamma^-)^l_{kj}(P_-)^i_l\\
-&=-(\Gamma^-)^i_{kl}(P_-)^l_j+(\Gamma^-)^l_{kj}(P_-)^i_l,
-\end{align*}
-so that
-\begin{align}\label{eq:calc1}
-\begin{aligned}
-\p_k(P_-)^i_j\chi^k\psi_-^j=\left(-(\Gamma^-)^i_{kl}(P_-)^l_j+(\Gamma^-)^l_{kj}(P_-)^i_l\right)(P_+)^k_m\psi_+^m\psi_-^j.
-\end{aligned}
-\end{align}
-Similarly,
-\begin{align}\label{eq:calc2}
-\begin{aligned}
-\frac{1}{2}(P_-)^i_k\p_l(K_+)^k_j\psi^l_-\psi_+^j&=(P_-)^i_k\p_l(P_+)^k_j\psi^l_-\psi_+^j\\
-&=(P_-)^i_k\left(-(\Gamma^-)^k_{ml}(P_+)^m_j+(\Gamma^-)^m_{jl}(P_+)^k_m\right)\psi^l_-\psi_+^j,
-\end{aligned}
-\end{align}
-where we used
-\begin{align}\label{Gamma-pm}
-(\Gamma^+)^i_{jk}=g^{im}(\Gamma_{mjk}+\frac{1}{2}H_{jkm})=g^{im}(\Gamma_{mkj}-\frac{1}{2}H_{kjm})=(\Gamma^-)^i_{kj}.
-\end{align}
-Plugging \eqref{eq:calc1} and \eqref{eq:calc2} into \eqref{QL_lambda} with use of the equation of motion \eqref{F_EoM} for $F$ then yields
-\begin{align*}
-[Q_L,\lambda^i]&=((\Gamma^-)^i_{km}(P_-)^m_l-(\Gamma^-)^m_{kl}(P_-)^i_m)(P_+)^k_j\psi_-^l\psi_+^j\\
-&{-}(P_-)^i_k(-(\Gamma^-)^k_{ml}(P_+)^m_j+(\Gamma^-)^m_{jl}(P_+)^k_m)\psi^l_-\psi_+^j\\
-&+(P_-)^i_k(P_+)^k_m(\Gamma^-)^m_{jl}\psi_-^l\psi_+^j.
- \end{align*}
-Here all terms cancel except for one, which finally reads
-\begin{align*}
-[Q_L,\lambda^i]=-(\Gamma^-)^i_{kl}\chi^k\lambda^l.
-\end{align*}
-\end{proof}
 
@@
 \end{document}
+
+%\section{The AKSZ formalism and 3d TFT}
+%\def\fg{\mathfrak{g}}
+%In this section we will show how to associate $2D$ topological theories to a generalized (para-)complex structure and relate them to the topological twists of $2D$ $(2,2)$ (para-)SUSY sigma models described in Section \ref{sec:toptwist} and in \cite{Kapustin:2004gv}.
+%The key to our construction is to realize the data of a G(p)C structure in terms of its eigenbundles, which are Dirac structures $L$ in the Courant algebroid $\TT$. 
+%Via the AKSZ construction \cite{AKSZ}, this correspondence translates into the statement that the Dirac structure $L$ defines a topological boundary theory of a $3D$ topological theory defined by the Courant algebroid $\TT$ \cite{Roytenberg:2002nu}.
+%
+%Throughout, we will use symplectic $NQ$ manifold as our model for shifted symplectic geometry. 
+%We will recall the general setup of associating a $3D$ topological field theory to the data of a Courant algebroid. 
+%For a reference, see \cite{Roytenberg:2002nu,??}.
+%
+%\subsection{Courant algebroids, $3D$ TFTs, and boundary conditions}
+%From the point of view of topological field theory, Courant algebroids are important because they provide geometric examples of $2$-shifted symplectic spaces. 
+%Via the AKSZ construction, $2$-shifted symplectic spaces are the natural home for $3$-dimensional topological field theories in the BV formalism. 
+%\brian{give citations here.}
+%
+%In \cite{Roytenberg:2002nu}, it is shown how to associate a $2$-shifted symplectic NQ manifold from the data of a Courant algebroid. 
+%
+%\begin{theorem}[\cite{Roytenberg:2002nu}]
+%There is an equivalence between isomorphism classes of $2$-shifted symplectic NQ manifolds with body $M$ and isomorphism classes of Courant algebroids on $M$.
+%\end{theorem}
+%
+%We briefly recall this construction. 
+%
+%Recall, the data of a Courant algebroid on a manifold $M$ is a vector bundle $E$, whose sheaf of sections we denote $\cE$, together with a nondegenerate symmetric bilinear pairing $\langle -, -\rangle : \cE \otimes \cE \to C^\infty(M)$ , an anchor map $a : E \to T M$, and a bilinear operator
+%\[
+%[-,-] : \cE \times \cE \to \cE
+%\]
+%called the Courant-Dorfman bracket. 
+%\brian{spell out properties, find a good reference}
+%Denote by $a^* : T^* M \to E^*$ the bundle map dual to $a$. 
+%
+%To every Courant algebroid we can define the following sequence of vector bundles on $M$
+%\[
+%T^*M \xto{a^*} E \xto{a} TM .
+%\]
+%A Courant algebroid is called {\em exact} if this sequence of bundles is exact. 
+%
+%\def\Sym{{\rm Sym}}
+%
+%Using this sequence, we can define the associated $NQ$ manifold $X_E$, following \cite{Ryotenberg:2002nu}.
+%The body of the NQ manifold is $M$, and the underlying graded vector bundle is given by $T^*[2] \oplus E[1]$. 
+%Define the degree $+1$ vector field 
+%\[
+%Q : \Gamma(M , \Sym \left(T^*[2] \oplus E[1]\right)^*) \to \Gamma(M , \Sym \left(T^*[2] \oplus E[1]\right)^*) 
+%\]
+%as follows: for $\psi \in \Sym^{k + \ell + 2} \left(T^*[2] \oplus E[1]\right)^*)$ and
+%\[
+%(\xi_0 \otimes \cdots \otimes \xi_k) \otimes (\alpha_0 \otimes \cdots \otimes \alpha_\ell) \in \Sym^{k+1}(T^*[2]) \otimes \Sym^{\ell + 1}(E[1]) 
+%\]
+%define
+%\begin{align*}
+%(Q \psi) ((\xi_0 \otimes \cdots \otimes \xi_k) \otimes (\alpha_0 \otimes \cdots \otimes \alpha_\ell)) = \brian{finish}
+%\end{align*}
+%
+%All that remains is to describe the $2$-shifted symplectic structure on the NQ manifold $X_E$. 
+%This is defined via the obvious pairing between $T^*[2]$ and $T$ together with the pairing $\langle - ,- \rangle$ on $E[1]$.
+%In local coordinates \brian{finish}
+%
+%The simplest type of Courant algebroid is one over a point.
+%
+%\begin{Ex}\label{ex: cs}
+%Any Lie algebra $\fg$ together with a non-degenerate invariant pairing defines a $2$-shifted symplectic structure on the graded manifold $\fg[1]$ living over a point. 
+%The dg algebra of functions is the Chevalley-Eilenberg cochain complex computing Lie algebra cohomology $C^*(\fg)$. 
+%All such $2$-symplectic NQ manifolds over a point are of this form. 
+%%The resulting AKSZ theory is Chern-Simons theory. 
+%\end{Ex}
+%
+%\subsubsection*{The $2$-shifted symplectic space of an exact Courant Algebroid}
+%
+%We recall the description of the $2$-shifted symplectic NQ manifold $X_E$ associated to an exact Courant algebroid $E$.
+%Of course, as a vector bundle $E = \TT$, and hence as a graded manifold $X_E$ is of the form $T^*[2] T[1] M$.
+%Concretely, the coordinates on this manifold are given by $(x^i,v^a,p_i,\mu_a)_{i,a=1\cdots n}$, where $x^i$ are the usual coordinates on $M$ with degree $0$, $v^a$ are the corresponding ``velocities'', i.e.
+the fibre coordinates on $T[1]M$ with a degree $1$, and $p_i,\mu_a$ are the momenta corresponding to $x^i,v^a$ with degrees $2,1$, respectively.
+The canonical symplectic form
+%\begin{align*}
+%\Omega= dx^idp_i+dv^ad\mu_a,
+%\end{align*}
+%is then of degree $2$.
+$T^*[2]T[1]M$ is the minimal symplectic realization of the shifted bundle $(\TT)[1]M$, which is recovered by setting $p_i=0$.
+The symmetric part of $\Omega$ represents the pairing $\lara$ on $(\TT)M$; this is because we can identify $d\mu_a\leftrightarrow \p_i$ and $dv^a\leftrightarrow dx^i$
+%
+%\brian{Severa classification}
+%
+%\begin{theorem}\label{thm: severa}
+%The set of isomorphism classes of exact Courant algebroids is a torsor for $H^3(X)$. 
+%\end{theorem}
+%
+%\subsubsection*{The Poisson Courant algebroid}
+%
+%\brian{Both real and holomorphic versions}
+%
+%\subsubsection{The AKSZ theory associated to a Courant algebroid}
+%
+%To any Courant algebroid $E$, we can associate an NQ manifold $X_E$ which carries a $2$-shifted symplectic structure that we denote by $\omega_E$. 
+%In the case that the Courant algebroid is exact, call the associated $2$-shifted symplectic space $X_H$, where $H$ labels the Severa class. 
+%
+%\def\sA{\mathcal{A}}
+%\def\d{{\rm d}}
+%\def\dbar{\Bar{\partial}}
+%
+%The starting point of the AKSZ construction is the mapping space
+%\[
+%{\rm Map}\left((M, (\sA^*_M, \d_M)), X_E\right)
+%\]
+%where $(M, (\sA^*_M, \d_M))$ is a dg manifold with body a smooth oriented manifold $M$. 
+%That is, $\sA^*_M$ is a sheaf of graded commutative algebras over the de Rham complex $\Omega^*_M$ and $\d_M$ is a linear operator of degree $+1$ satisfying:
+%\begin{itemize}
+%\item[(1)] $\sA_M$ is concentrated in finitely many degrees;
+%\item[(2)] For each $k$, $\sA^k_M$ is a locally free sheaf of $C^\infty_M$-modules of finite rank;
+%\item[(3)] The differential $\d_M : \sA_M^* \to \sA_M^{*+1}$ is square zero differential operator making $(\sA_M , \d_M)$ into a sheaf of commutative dg algebras over the de Rham complex $\Omega^*_M$
+%\end{itemize}
+%
+%\begin{Ex}
+%The most important example for us will be the source dg manifold $(M, \Omega^*_M)$, that is $\sA_M = \Omega^*_M$ with de Rham differential. 
+%We denote this dg manifold by $M_{\rm dR}$.
+%\end{Ex}
+%
+%\begin{Ex}
+%If $M$ has a para-complex structure, then $(M, \Omega^{0,*}_M)$ has the structure of a dg manifold with differential given by the para $\dbar$-operator. 
+%\brian{David, is this consistent notation?}
+%We will denote this dg manifold by $M_{p \dbar}$. 
+%\end{Ex}
+%
+%\begin{Ex}
+%If $\fg$ is a Lie algebra equipped with a non-degenerate invariant pairing, and $X_E = \fg[1]$ as in Example \ref{ex: cs}, then the AKSZ theory (whose target base manifold is a point) is equivalent to Chern-Simons theory on $M$.
+%\end{Ex}
+%
+%\subsubsection{Dirac structures and boundary conditions}
+%
+%\subsection{Two dimensional TFT from generalized para-complex structures}
+%\label{sec:generalized para-complex_AKSZ}
+%\brian{Recall that a generalized (para-)complex structure $\JJ$ defines a Dirac structure in $\TT$, and hence a Lagrangian inside of the $2$-shifted symplectic space $\XX_H$.  
+%%More generally, if $\JJ$ is a generalized complex structure in an arbitrary Courant algebroid $E$, then we obtain a $2$-shifted Lagrangian inside of the $2$-shifted symplectic space $\XX_E$. 
+%This Lagrangian then defines a boundary condition for the three-dimensional AKSZ theory. }
+%
+%\subsubsection*{Trivial generalized para-complex structure}
+%
+%\subsubsection*{(Real) Poisson $\sigma$-model}
+%
+%\subsubsection*{Para-complex $A/B$-models}
+%
+%We point out two special cases of the above general construction. 
+%
+%\brian{The $A$-model is the usual thing.}
+%
+%\begin{Def}
+%The {\bf para-complex $B$-model} with source a closed Riemann surface $\Sigma$ and target a para-complex manifold $X$ is the AKSZ theory with source the de Rham space $\Sigma_{\rm dR}$ and target the $1$-shifted symplectic space $T^*[1] X_{p \dbar}$:
+%\[
+%{\rm Map}\left(\Sigma_{dR}, T^*[1]  X_{p \dbar}\right) .
+%\]
+%\end{Def}
+%
+%\brian{Discuss Si's work on perturbative quantization}
+%
+%\hrulefill
+%
+%\brian{***para Kahler example, **example where the paracomplex structures commute but are not equal (this is where people see ``twisted chiral"), para version of T-duality, **Poisson $\sigma$-model, going back and forth between generalized (para) complex.
+%}  
+%
+% \brian{discuss anomalies}
+%
+%\subsection{Para holomorphic variants}
+%
+%So far, in each of the $\sigma$-models we have discussed in the AKSZ formalism, the fields have depended only topologically on the source Riemann surface. 
+%There are closely related $\sigma$-models which depending {\em para-holomorphically} on the source Riemann surface that we briefly discuss.

### 2020-01-20 newdraft.tex
few more comments to address

@@
 
-\brian{Symplectic form}
+\brian{Introduce symplectic form}
 
@@
 
-\brian{Hamiltonians and action functional}
+\brian{Hamiltonians and action functional. This is just more review and citations.}
 
@@
 
-This formalism can be made explicit in the case of the $3D$/$2D$ system. \brian{finish}
+This formalism can be made explicit in the case of the $3D$/$2D$ system. \brian{I basically do this already below, but I might add some filler statements here.}
 
@@
 
-\brian{define $\omega_{\KK}$ see Appendix A of \cite{Cattaneo:2009zx}.}
-
+\brian{define $\omega_{\KK}$ see Appendix A of \cite{Cattaneo:2009zx}. 
+If dbro is OK, I say we just translate his result and cite it. The proof seems to follow immediately.}
 \begin{proposition}\label{prop: symp}
@@
 
+\begin{proof}
+The BRST operator is of the form $\d_{dR} + Q$ where $Q$ is a degree $+1$ vector field on the target and $\d_{dR}$ is the de Rham differential on $\Sigma$.  
+Locally, the BRST cohomology reduces to the cohomology of functions on the target graded manifold equipped with differential $Q$.
+In each case at hand, the target is of the form $L[1]$ with differential $Q = \d_L$.
+\end{proof}
+
 We now restrict to the case $E = \TT$ with its standard Courant algebroid structure and outline important special cases.
@@
 
-\brian{below needs to be fixed up a bit}
+\btd{I'm getting snagged on this a bit. 
+What I want to show is that the full theory has as its BRST cohomology the complex I describe below. 
+Do you see how this works?
+}
 
@@
 
+%\brian{Case of para structure on $M \times M$. Two copies of $BF$ theory.}
+
+\subsection{Anomalies and para holomorphic variants}
+
 \brian{discuss anomalies. Para-holomorphic volume form.}
@@
 
-\hrulefill
-
-\brian{***para Kahler example, **example where the paracomplex structures commute but are not equal (this is where people see ``twisted chiral"), para version of T-duality, **Poisson $\sigma$-model, going back and forth between generalized (para) complex.
-}
-
-\brian{Case of para structure on $M \times M$. Two copies of $BF$ theory.}
-
-\subsection{Para holomorphic variants}
+%\brian{***para Kahler example, **example where the paracomplex structures commute but are not equal (this is where people see ``twisted chiral"), para version of T-duality, **Poisson $\sigma$-model, going back and forth between generalized (para) complex.
+%}
 

### 2020-01-20 newdraft.tex
Added a bunch
Added
-parahermitian section
-reworked para-calabi-yau
-mirror symmetry
-some refs

@@
 \end{align*}
-On $\mathbf{C}$, we define following operations: para-complex conjugation $z=(x,y)\mapsto \bar{z}=(x,-y)$, i.e.
-$\overline{x+ky}=x-ky$, the real and imaginary parts given by $Re(z)=\frac{1}{2}(z+\bar{z})$, $Im(z)=k\frac{1}{2}(z-\bar{z})$, i.e.
-$Re(x+ky)=x,\ Im(x+ky)=y$.
+On $\mathbf{C}$, we define the following familiar operations:\begin{align}
+\begin{aligned}
+&\bullet\quad \text{Para-complex conjugation: }x+\kk y\mapsto \overline{x+\kk y}=x-\kk y\\
+&\bullet\quad \text{Real part: } x+\kk y \mapsto \text{Re}(x+\kk y)=x\\
+&\bullet\quad \text{Imaginary part: } x+\kk y \mapsto \text{Im}(x+\kk y)=y.
+\end{aligned}
+\end{align}
 
@@
 %\end{proof}
-\paragraph{The para-holomorphic volume form}
-In K\"ahler geometry, the notion of a holomorphic volume form is very important and in particular gives rise to Calabi-Yau manifolds, perhaps the most important subclass of K\"ahler manifolds.
+
+%\paragraph{The para-holomorphic volume form}
+%In K\"ahler geometry, the notion of a holomorphic volume form is very important and in particular gives rise to Calabi-Yau manifolds, perhaps the most important subclass of K\"ahler manifolds.
 Here we discuss the para-complex version of this story because it plays an important role when considering the anomalies of the R-symmetry at the quantum level.
-
-Remember that a holomorphic volume form on a complex manifold $M$ of complex dimension $k$ is a non-vanishing section of the canonical bundle, $\Omega \in \Omega^{(k,0)}(M)$, that is holomorphic, $\bar{\p}\Omega=0$.
+%
+%Remember that a holomorphic volume form on a complex manifold $M$ of complex dimension $k$ is a non-vanishing section of the canonical bundle, $\Omega \in \Omega^{(k,0)}(M)$, that is holomorphic, $\bar{\p}\Omega=0$.
 Recalling the para-complex Dolbeault complex \eqref{para-dolbeault}, we can immediately infer what should be the analogous object in para-complex geometry:
+%\begin{Def}
+%Let $(\PS,K)$ be a para-complex manifold of dimension $2n$.
+We define a {\bf para-holomorphic volume form} to be a nowhere vanishing section $\hat{\Omega}=(\Omega,\tl{\Omega})\in \Omega^{(n,0)+(0,n)}(\PS)$, where $\Omega \in \Omega^{(n,0)}(\PS)$ and $\tl{\Omega}\in \Omega^{(0,n)}(\PS)$ are each non-vanishing and satisfy
+%\begin{align*}
+%\pt \Omega=\p \tl{\Omega}=0.
+%\end{align*}
+%\end{Def}
+%Because $\Omega^{(n,0)}(\PS)$ is naturally isomorphic to $\Omega^n(M)$, the section $\Omega$ is non-vanishing and $\pt \Omega=0$ implies it is invariant under the translation along $\Mt$, the above definition implies that $\Omega$ defines an honest volume form on $M$.
+Similarly, $\tl{\Omega}$ is a volume form on $\Mt$ and therefore both the canonical foliations $M$ and $\Mt$ of the para-complex manifold are orientable.
+%
+%As an extension of the above definition and the direct analogy with Calabi-Yau manifolds, we can introduce a definition of the para-Calabi-Yau manifolds:
+%\begin{Def}
+%A {\bf para-Calabi-Yau manifold} is a compact, para-K\"ahler manifold $(\PS,\eta,K)$ with a para-Holomorphic volume form $\hat{\Omega}$.
+%\end{Def}
+
+\subsubsection{Para-Hermitian Geometry}
+We now introduce a metric $\eta$ compatible with the para-complex structure $K$, which by contraction $\eta \circ  K$ induces a non-degenerate two-form $\omega$.
+This gives rise to para-Hermitian geometry:
 \begin{Def}
-Let $(\PS,K)$ be a para-complex manifold of dimension $2n$.
-We define a {\bf para-holomorphic volume form} to be a nowhere vanishing section $\hat{\Omega}=(\Omega,\tl{\Omega})\in \Omega^{(n,0)+(0,n)}(\PS)$, where $\Omega \in \Omega^{(n,0)}(\PS)$ and $\tl{\Omega}\in \Omega^{(0,n)}(\PS)$ are each non-vanishing and satisfy
-\begin{align*}
-\pt \Omega=\p \tl{\Omega}=0.
-\end{align*}
+	Let $(\PS,K)$ be a para-complex manifold and let $\eta$ be a pseudo-Riemannian metric that satisfies $\eta(K\cdot,K\cdot)=-\eta$.
+Then we call $(\PS,K,\eta)$ a \textbf{para-Hermitian manifold}\footnote{If $K$ is not integrable, i.e.
+$(\PS,K)$ is almost para-complex, we would call $(\PS,K,\eta)$ an almost para-Hermitian manifold.}.
 \end{Def}
-Because $\Omega^{(n,0)}(\PS)$ is naturally isomorphic to $\Omega^n(M)$, the section $\Omega$ is non-vanishing and $\pt \Omega=0$ implies it is invariant under the translation along $\Mt$, the above definition implies that $\Omega$ defines an honest volume form on $M$.
-Similarly, $\tl{\Omega}$ is a volume form on $\Mt$ and therefore both the canonical foliations $M$ and $\Mt$ of the para-complex manifold are orientable.
-
-As an extension of the above definition and the direct analogy with Calabi-Yau manifolds, we can introduce a definition of the para-Calabi-Yau manifolds:
+\noindent
+The above definition implies that the tensor $\omega\coloneqq \eta K$ is skew
+\begin{align*}
+\omega(X,Y)=\eta(KX,Y)=-\eta(X,KY)=-\omega(Y,X),
+\end{align*}
+and nondegenrate (because $\eta$ is nondegenerate), therefore $\omega$ is an almost symplectic form, sometimes called the \textbf{fundamental form}.
+From $K^2=\id$ we also have $K=\eta^{-1}\omega=\omega^{-1}\eta$.
+Another observation is that since the eigenbundles of $K$ have the same rank, $\eta$ has split signature $(d,d)$.
+Furthermore, the eigenbundles of $K$ are isotropic with respect to both $\eta$ and $\omega$.
+This means that the almost symplectic form $\omega$ is of the type $(1,1)$, $\omega \in \Omega^{(1,1)}(\PS)$.
+\begin{remark}
+	As shown above, the data $(\PS,K,\eta)$, $(\PS,\eta,\omega)$ and $(\PS,K,\omega)$ are on a para-Hermitian manifold equivalent and so we may use the different triples interchangeably to refer to a para-Hermitian manifold.
+\end{remark}
+Again, in a complete analogy with K\"ahler geometry, we get para-K\"ahler geometry whenever the fundamental form $\omega$ is closed
 \begin{Def}
-A {\bf para-Calabi-Yau manifold} is a compact, para-K\"ahler manifold $(\PS,\eta,K)$ with a para-Holomorphic volume form $\hat{\Omega}$.
+	Let $(\PS,\eta,\omega)$ be a para-Hermitian manifold with $\rd\omega=0$. We call $(\PS,\eta,\omega)$ a \textbf{para-K\"ahler manifold}.
 \end{Def}
+
+\paragraph{Para-Calabi-Yau geometry}
+
+In \cite{mythesis}, the notion of para-Calabi-Yau geometry is introduced.
+As the name suggests, these manifolds should play the role of the para-complex version of Calabi-Yau manifolds in complex geometry.
+We now recall some basic properties of para-Calabi-Yau manifolds, motivating the definition by Calabi-Yau geometry, which is a standard notion in the literature.
+
+There are many different ways to define what a Calabi-Yau manifold is, but for the purpose of our discussion we will call a Calabi-Yau manifold a K\"ahler manifold $(M,g,I)$ with the holonomy group of the underlying Riemannian metric to be $\text{Hol}(g)\subseteq SU(d)$, as opposed to $U(d)$, which is the case for ordinary K\"ahler manifolds.\footnote{Typically, a part of the definition of a Calabi-Yau manifold is the requirement of compactness of $M$ and sometimes, one requires that $\text{Hol}(g)$ is exactly equal to $SU(d)$.} A consequence of this property is that there exists a {\it holomorphic volume form}, i.e.
+a non-vanishing section $\Omega \in \Omega^{d,0}$ that is holomorphic, $\bar{\p}\Omega=0$ and satisfies
+\begin{align*}
+    \frac{\omega^d}{d!}=(-1)^\frac{d(d-1)}{2}\left(\frac{i}{2}\right)^d \Omega\w \bar{\Omega},
+\end{align*}
+where $\omega=gI$ is the K\"ahler form.
+
+% a Calabi-Yau manifolds
+
+% A Calabi-Yau manifold is a K\"ahler manifold $(M,\omega,I)$ of complex dimension $k$ with a non-vanishing holomorphic volume form $\Omega$,
+% \begin{align*}
+%     \Omega \in \Omega^{(k,0)}(M),\quad \bar{\p}\Omega=0,
+% \end{align*}
+% which satisfies a compatibility condition with the K\"ahler fundamental form $\omega$ (sometimes called the complex Monge-Ampere equation)
+% \begin{align*}
+%     \frac{\omega^k}{k!}=(-1)^\frac{k(k-1)}{2}\left(\frac{i}{2}\right)^k \Omega\w \bar{\Omega}.
+% \end{align*}
+% Calabi-Yau manifolds play an important role in theoretical physics, especially in string theory where they serve as the geometric model for string compactifications.
+For more details on Calabi-Yau manifolds, the reader may consult for example the book \cite{joyce2000compact}.
+
+We now turn to the analogue of the above notions in the para-complex setting.
+Let $(K,\eta,\omega)$ be a $2d$-dimensional para-K\"ahler manifold with $\lc$ the Levi-Civita conencion of $\eta$.
+From $\lc\omega=\lc\eta$, we have that the holonomy group of a para-K\"ahler manifold is $GL(d)=O(d,d)\cap Sp(2d)$.
+For a para-Calabi-Yau manifold, the natural definition is therefore the following:
+
+\begin{Def}
+A {\bf para-Calabi-Yau manifold} is a para-K\"ahler manifold $(\PS,K,\eta)$ of dimension $2d$ such that the holonomy group of $\eta$ is $\text{Hol}(\eta)\subseteq SL(d)$.
+\end{Def}
+\begin{remark}
+Note the interesting property that both $SU(d)$ and $SL(d)$ are real forms of $SL_\mathbb{C}(d)$.
+\end{remark}
+
+Let us now investigate what is the structure on para-Calabi-Yau analogous to the holomorphic volume form.
+We choose the local adapted coordinates $(x^i,\xt_j)$ in which $\eta$ and $\omega$ have the canonical form
+\begin{align*}
+    \eta=dx^i\otimes d\xt_i+d\xt_i\otimes dx^i,\quad \omega=dx^i\w d\xt_i.
+\end{align*}
+Because the holonomy of $\eta$ is now contained in $SL(d)$, there is also a covariantly constant tensor $\hat{\Omega}$
+\begin{align*}
+    \hat{\Omega}=dx^1\w\cdots\w dx^d+d\xt_1\w\cdots\w d\xt_d=\Omega+\tl{\Omega},
+\end{align*}
+which satisfies $\pt\Omega=\p\tl{\Omega}=0$ as well as
+\begin{align*}
+   \frac{\omega^d}{d!}=(-1)^\frac{d(d-1)}{2} \Omega\w \tl{\Omega}. 
+\end{align*}
+
+We call $\hat{\Omega}=(\Omega,\tl{\Omega})$ a {\bf para-holomorphic volume form}.
+Remember that on a para-complex manifold $\PS$ of dimension $2n$, the appropriate analogue of the holomorphic forms are the para-holomorphic forms, given by pairs $(\alpha,\tl{\alpha})\in\Omega^{(k,0)+(0,k)}(\PS)$ (here the bigrading is with respect to the para-complex structure), satisfying $\pt\ap=\p\tl{\ap}=0$.
+Therefore, the {para-holomorphic volume form} is exactly the correct analogue of the holomorphic volume form in case of the Calabi-Yau manifolds.
+Furthermore, because $\Omega^{(n,0)}(\PS)$ is naturally isomorphic to $\Omega^n(M)$, the section $\Omega$ is non-vanishing and $\pt \Omega=0$ implies it is invariant under the translation along $\Mt$, and so it defines a volume form on $M$.
+Similarly, $\tl{\Omega}$ is a volume form on $\Mt$ and we see that the para-Calabi-Yau structure on $\PS$ augments the canonical foliations $M$ and $\Mt$ of the para-complex manifold with volume forms and both the foliation manifolds are consequently orientable.
 
@@
 \end{Def}
+
+It is a straightforward exercise to check that the most general form of an almost GpC structure is given by
+\begin{align}\label{eq:GpC_generalform}
+ \KK =
+ \begin{pmatrix}
+ A & \Pi \\
+ \Omega & -A^*
+ \end{pmatrix}, \text{ with }
+ \begin{cases}
+  A^2 + \Pi \Omega & = \id\\
+  A\Pi - \Pi A^* & = 0\\
+  \Omega A + A^*\Omega & = 0
+ \end{cases}.
+\end{align}
+where $A \in \End(T)$ and $\Omega \in \Omega^2(M)$, $\Pi \in \se(\Lambda^2 T)$ are skew tensors.
+The integrability conditions on these tensors are a bit more involved and we will only discuss their special cases when discussing examples.
+An interested reader can consult \cite{crainic-integrability}, where the integrability is presented in the most general form for generalized complex structures, where the conditions are analogous.
+
 Let $L_\KK$ and $\Tilde{L}_{\KK}$ denote the $+1$ and $-1$ eigenbundles of $\KK$, respectively. 
@@
 \end{Ex}
-
-\btd{Is there a classification of a most general GpC that can be written in the form
-\[
-\KK = 
-\begin{pmatrix}
-K & P \\
-\omega & -K^*
-\end{pmatrix}
-\]
-where $K \in {\rm End}(T)$, $P \in \wedge^2 T$ and $\omega \in \wedge^2 T^*$ satisfying some integrability conditions?
-}
 
@@
 The fundamental observation is that the diagram
-\[
-\xymatrix{
-& N \times \cE(N, X) \ar[dr]^-{{\rm ev}} \ar[dl]_-{\pi_N} & \\
+%\[
+%\xymatrix{
+%& N \times \cE(N, X) \ar[dr]^-{{\rm ev}} \ar[dl]_-{\pi_N} & \\
+%N & & X
+%}
+%\]
+\begin{equation*}
+	\begin{tikzcd}
+	& N \times \cE(N, X)\arrow{rd}{{\rm ev}}\arrow[swap]{ld}{\pi_N} &\\
 	N & & X
-}
-\]
+	\end{tikzcd}
+\end{equation*}
 induces a pairing
@@
 \]
-where $T^*[1]M$ is equipped with its standard $1$-symplectic structure.
+where $T^*[1]M$ is equipped with its standard $1$-symplectic structure. \david{so is this the BFF theory?}
 
@@
 The two bases $\{Q^1_{\pm}, Q^2_\pm\}$ and $\{{Q}_\pm,\wtl{Q}_\pm\}$ are related by
-\begin{align*}
-Q_\pm=\frac{1}{\sqrt{2}}(Q^2_\pm+Q^1_\pm),\quad \wtl{Q}_\pm=\frac{1}{\sqrt{2}}(Q^2_\pm-Q^1_\pm).
-\end{align*}
+\begin{align}\label{parasusy_offdiagonal_basis}
+Q_\pm=\frac{1}{\sqrt{2}}(Q^2_\pm-Q^1_\pm),\quad \wtl{Q}_\pm=\frac{1}{\sqrt{2}}(Q^2_\pm+Q^1_\pm).
+\end{align}
 Again, this is analogous to the complex basis of the ordinary $(2,2)$ superalgebra
-\begin{align*}
-[Q_\pm,\overline{Q}_\pm]=2\p_\pm.
-\end{align*}
+\begin{align}\label{complex_(2,2)}
+[Q_\pm,\overline{Q}_\pm]=2i\p_\pm.
+\end{align}
 
@@
 
+\section{Para-complex semi-flat mirror symmetry}
+In this section we present our first observations about a possible notion of mirror symmetry for para-complex geometry.
+We show that the initial observations about $2D$ $(2,2)$ SUSY $\sigma$-models that initiated the vast research program of mirror symmetry apply perfectly well to $(2,2)$ para-SUSY models and therefore give rise to parallel statements in the para-holomorphic category.
+
+The original example of mirror symmetry in physics is based on the observation that the $(2,2)$ SUSY algebra (in its complex form) exhibits a $\mathbb{Z}_2$ outer endomorphism, which exchanges the vector and axial $U(1)$ generators and in particular then exchanges the two topological twists \cite{Witten_mirror_topological}.
+On the level of the supercharges \eqref{complex_(2,2)}, this is manifested by the exchange (see for example \cite{susy_hori} for details)
+\begin{align*}
+Q_-\longleftrightarrow \overline{Q}_-,
+\end{align*}
+which clearly preserves the commutation relations. In our case, the $\mathbb{Z}_2$ symmetry acts on \eqref{parasusy_offdiagonal_basis} as
+\begin{align*}
+Q_-\longleftrightarrow \widetilde{Q}_-,
+\end{align*}
+or, equvalently on the diagonal basis \eqref{eq:(2,2)para} $Q^2_-\mapsto -Q^2_-$, as discussed in Section \ref{sec:toptwist}, where we also argued that this exchanges the two types of topological twists.
+
+The geometric realization of the above-described $\mathbb{Z}_2$ action on the $(2,2)$ superalgebra was described in \cite{SYZ} and since has acquired the name SYZ mirror symmetry.
+There, the mirror symmetry is described as a correspondence between pairs of Calabi-Yau manifolds $M$ and $\Mt$, specifically ones that admit a particular types of fibrations over the same base $B$.
+The mirror symmetry in this case acts geometrically as an exchange of these fibrations, which are essentially linear duals to each other.
+One of the hallmarks of mirror symmetry is the feature that it relates the moduli space of symplectic structures on $M$ with a moduli space of complex structures on $\Mt$.
+On the physics side, this exchange is realized as a correspondence between an $A$-model on $M$ and a $B$-model on $\Mt$.
+
+In the following paragraphs, we will study the semi-flat case of SYZ mirror symmetry, where the pair of K\"ahler Calabi-Yau manifolds is given by $M=TB$ and $\Mt=T^*B$, the tangent and cotangent bundles of an affine manifold $B$.
+Our result is that this setting admits an equally natural description in terms of para-K\"ahler and para-Calabi-Yau geometry, where the mirror map exchanges the {\bf symplectic moduli} on $M$ with the {\bf para-complex moduli} on $\Mt$.
+The underlying symplectic fundamental forms of both the K\"ahler and para-K\"ahler gometries coincide, while the complex and para-complex structures anti-commute and therefore the triple $(\omega,K,I)$ defines {\it Born geometry} \cite{freidel2014born,Freidel:2018tkj,mythesis} (see also \cite{Marotta:2018myj,Hassler:2019wvn,Marotta:2018swj,Marotta:2019eqc}).
+Consequently, the mirror map in the semi-flat case relates Born geometries on $M$ and $\Mt$, mapping between the symplectic moduli on one side and the para-complex and complex moduli on the other side.
+
+In the following we closely follow the discussions presented in \cite{mythesis,mirror_w-o_corrections,hitchin1997moduli}
+
+\paragraph{The para-complex point of view} We start with the discussion of the para-Calabi-Yau geometry on the side of $M$ and then contrast it with the Calabi-Yau geometry of $M$.
+Consider an affine manifold $B$ and take a neighbourhood $U\subset B$ with local coordinates $u^i$.
+Let $U\times \RR^n$ with the coordinates $(u^i,v^i)$, $v^i$ denoting the coordinates on $\RR^n$, be the local model for $M=TB$.
+We define the para-complex structure on $M$ in terms of its adapted coordinates $(x^i=u^i+v^i,\xt_j=u^k-v^k)$.
+The fact that $M$ is affine means that the transition functions are in $GL_n(\RR)\ltimes \RR^n$, i.e.
+of the form
+\begin{align*}
+    u^i\mapsto u'^i(u^i)=A_{\ j}^{i}u^j+B^i,\quad A \in GL_n,\ B\in \RR^n.
+\end{align*}
+This implies that the natural fiber coordinates of $TM$, $v^i=du^i$,  transform as $u^i\mapsto A^i_{\ j}u^j$, so that the combinations $(x^i=u^i+v^i,\xt^j=u^k-v^k)$ transform by
+\begin{align*}
+    (x^i,\xt_j)\mapsto (A_{\ k}^{i}x^k+B^i,A_{\ k}^{j}\xt^k+B^j),
+\end{align*}
+which assures that the total space of $TB$ is an affine manifold with $(x^i,\xt^j)$ affine coordinates.
+In particular $(x^i,\xt^j)$ are adapted coordinates of an integrable para-complex structure on $TB$, because the transition functions are para-holomorphic.
+
+We now endow $M$ with a para-Calabi-Yau structure defined by the fundamental form $\omega$ and a para-Holomorphic volume form $\Omega$:
+\begin{align*}
+    \omega&=\omega_{ij}\ dx^i\w d \xt^j=2\omega_{ij}\ du^i\w dv^j,\\
+    \hat{\Omega} &=dx^1\w\cdots\w dx^n+d\xt^1\w\cdots\w d\xt^n=\Omega+\tl{\Omega}.
+\end{align*}
+We also assume that the local para-K\"ahler potential $\phi$ on $U\subset M$, which defines $\omega$ via
+\begin{align*}
+\omega_{ij}=\p_i\pt^j\phi=\left(\frac{\p^2}{\p u^i \p u^j}-\frac{\p^2}{\p v^i \p v^j}\right)\phi,
+\end{align*}
+is of the form $\phi(u,v)=\phi(u)$.
+This means it is invariant under the translations in the fiber directions of $TB$ and the geometry is therefore {\it semi-flat}, hence the name semi-flat mirror symmetry.
+The fact that the pair $(\omega,\hat{\Omega})$ defines a para-Calabi-Yau structure means that it satisfies the Monge-Ampere equation:
+\begin{align*}
+    C\omega^n=\Omega\w\tl{\Omega} \Longleftrightarrow   \text{det}(\frac{\p^2\phi}{\p u^i\p u^j})=C.
+\end{align*}
+The above has a unique solution for $\phi$ \cite{calabi1975construction} assuming $\phi\mid_{\p U}=0$ and $\phi$ is convex ($\p_i\p_j\phi>0$).
+For the Monge-Ampere equation to be invariant under the affine transformations, we must have $\text{det}(A)=1$, which is a requirement that defines a {\it special affine manifold}.
+Therefore, we will from now on require that $B$ is special affine.
+For completeness, we note that the para-K\"ahler metric $\eta$ takes the form
+\begin{align*}
+    \eta=\omega_{ij} (dx^i\otimes d\xt^j+d\xt^i\otimes dx^j)=2\omega_{ij}(du^i\otimes du^j-dv^i\otimes dv^j).
+\end{align*}
+
+\paragraph{The complex point of view}
+In the usual discussion of the semi-flat mirror symmetry, one considers a complex structure defined by the holomorphic coordinates $z^i=u^i+iv^i$ instead of the para-complex structure above.
+The fundamental form is then taken to be $\omega_I=i\p\bar{\p}\phi$, which in the semi-flat case $\phi(u,v)=\phi(u)$ coincides with $\omega$.
+The Riemannian K\"ahler metric is then
+\begin{align*}
+    g=\omega_{ij}(du^i\otimes du^j+dv^i\otimes dv^j).
+\end{align*}
+It is easy to show that $I$ and $K$ anticommute, and because $\omega_I=\omega$, we see that this geometric setting defines Born geometry.
+\newcommand{\uh}{\hat{u}}
+\newcommand{\vh}{\hat{v}}
+\newcommand{\xh}{\hat{x}}
+\newcommand{\xth}{\hat{\xt}}
+
+\paragraph{Legendre transform and the mirror map}
+Consider new coordinates $\uh_i$ on $U$ given by
+\begin{align*}
+\frac{\p\uh_i(u)}{\p u^j}=\omega_{ij}=  \frac{\p^2\phi}{\p u^i \p u^j},
+\end{align*}
+with the inverse transformation $\frac{\p u^i(\uh)}{\p \uh_j}=\omega^{ij}=(\omega_{ij})^{-1}$. Integrating this, we can write the relationship between the coordinates
+\begin{align*}
+    u^i(\uh)=\frac{\p \psi(\uh)}{\p \uh_i},
+\end{align*}
+for some local function $\psi(\uh)$ so that $\omega^{ij}=\frac{\p \psi(\uh)}{\p \uh_i\uh_j}$ and $\phi(u)$ and $\psi(\uh)$ are Legendre transforms of one another:
+\begin{align*}
+    \psi(\uh)=u^i \uh_i-\phi(u).
+\end{align*}
+This ensures that also $\psi$ satisfies the Monge-Ampere equation, but with an inverse constant
+\begin{align}\label{dual-monge-ampere}
+    \text{det}(\frac{\p^2\psi}{\p \uh_i\p \uh_j})=C^{-1}.
+\end{align}
+
+We continue by discussing the cotangent bundle $\Mt=T^*B$.
+The metric $\eta$ on $M=TB$ defines a negative-definite metric $-2\omega_{ij}dv^i\otimes dv^j$ on each fiber, which can be inverted to give a negative-definite metric on fibres of $T^*B$ and consequently on the whole $\Mt$:
+\begin{align*}
+    \hat{\eta}=2(\omega_{ij}du^i\otimes du^j-\omega^{ij}d\vh_i\otimes d\vh_j),
+\end{align*}
+denoting the fibre coordinates dual to $v^i=dx^i$ by $\vh_i=\frac{\p}{\p u^i}$. Using the canonical symplectic form on $T^*B$,
+\begin{align*}
+    \hat{\omega}=du^i\w d\vh_i
+\end{align*}
+we define a para-K\"ahler structure $\hat{K}$ via
+\begin{align*}
+    \hat{K}\coloneqq \hat{\eta}^{-1}\hat{\omega}.
+\end{align*}
+It can be checked that $\hat{K}$ is again integrable and the corresponding adapted coordinates are $(\xh_i=\uh_i+\vh_i,\xth_j=\uh_i-\vh_i)$, in terms of which we get
+\begin{align*}
+    \hat{\omega}&=\hat{\omega}^{ij}d\xh_i\w d\xth_j\\
+    \hat{\eta}&=\hat{\omega}^{ij}(d\xh_i\otimes d\xth_j + d\xth_i\otimes d\xh_j),
+\end{align*}
+where $\hat{\omega}^{ij}=\frac{\p^2 \psi}{\p \uh^i\p \uh^j}$.
+Crucially, $\Mt$ is also a para-Calabi-Yau manifold because $\psi$ satisfies the Monge-Ampere equation \eqref{dual-monge-ampere}.
+Moreover, we get a relationship between the moduli of symplectic structures on $M$ and para-complex structures on $\Mt$, since varying the symplectic structure on $M$ corresponds to a change of $\phi$, which also changes $\psi$ as well as the coordinates $\uh_i$.
+This in turn changes the para-complex structure $\hat{K}$ defined by its adapted coordinates, and in particular depends on $\uh_i$.
+
+We find that in this case the mirror symmetry not only relates the symplectic and complex moduli of the mirror manifolds $M$ and $\Mt$, but also relates the symplectic and para-complex moduli and therefore gives a map of moduli of Born geometries on $M$ and $\Mt$, where the variation of the symplectic structure on one side corresponds to a variation of the complex and para-complex structures on the other.
+
+\paragraph{Speculations about para-mirror symmetry}
+Because the semi-flat case is so simple, the mirror pair is the same in both the complex and para-complex cases.
+However, this does not always have to be the case and the para-complex mirror symmetry could relate pairs of manifolds that are not related by the usual mirror symmetry.
+Moreover, this new notion of mirror symmetry gives rise to a possibility of {\it mirror trialities}, i.e.
+situations when the symplectic moduli space on $M$ is related to the complex moduli on $\Mt$ as well as the para-complex moduli on $\Mt'$:
+\begin{equation*}
+\begin{tikzcd}
+& (M,\omega)\arrow[leftrightarrow,sloped,swap]{ld}{\mathclap{mirror}}\arrow[leftrightarrow,sloped]{rd}{\mathclap{para-mirror}}&\\
+(\Mt,I)\arrow[leftrightarrow, dotted]{rr}{?}&&(\Mt',K)
+\end{tikzcd}
+\end{equation*}
+
+Additionally, the para-mirror symmetry could open many doors, for example to study the symplectic invariants -- such as the Gromov-Witten invariants -- of manifolds that do not have mirrors but have para-mirrors, so that the corresponding A-model is mirror to a para-B-model but not to a usual B-model.
+Similarly, para-complex mirror symmetry could also prove useful in the homological approach to mirror symmetry, providing new insights about the Fukaya category on the symplectic side.
+
 \appendix

### 2020-01-29 newdraft.tex
edits

@@
 
-\subsubsection{SKT Geometry and half generalized structures}
-\david{will see if we'll be using this}
+\subsubsection{SKT Geometry and half generalized structures} \label{SKT}
+
 An {\bf SKT} structure is a Hermitian structure $(I,g)$ for which the fundamental form $\omega$ even though is not closed, is $\rd \rd^c$-closed, i.e.
@@
 
-The $2$-dimensional $(1,1)$ supertranslation algebra is the super Lie algebra
+The $2$-dimensional $(1,1)$ supertranslation algebra is the real super Lie algebra
 \[
@@
 \]
-where $S_\pm \cong \RR$ are the semi-spin representations of ${\rm Spin}(1,1)$ labeled by helicities $\pm \frac{1}{2}$. 
+where $S_\pm \cong \RR$ are the real spin representations of ${\rm Spin}(1,1)$ labeled by helicities $\pm \frac{1}{2}$. 
 Note that there are natural ${\rm Spin}(1,1)$-equivariant maps
@@
 
-Let $\Sigma^{2|2}$ be a super Riemann surface with two real odd directions. 
-The even part of this supermanifold is a Riemann surface (with coordinates $\sigma$, $\tau$).
-For instance, in the flat case we consider the superspace $\RR^{2|2} = \{(x^i , \theta_1^{\pm}) \; | \; i = 1,2\}$, where $\theta_1^{\pm}$ are odd variables.
+Let $\Sigma^{1,1|2}$ be a surface of split signature with two real odd directions. 
+The even part of this supermanifold is a real surface (with coordinates $\tau$, $\sigma$).
+For instance, in the flat case we consider the superspace $\RR^{1,1|2} = \{(\tau,\sigma ; \theta_1^{\pm})\}$, where $\theta_1^{\pm}$ are odd variables.
 
@@
 \begin{align}\label{eq:(1,1)action}
-S_{(1,1)}(\Phi)=\int_{\Sigma^{2|2}} [g(\Phi)+b(\Phi)]_{ij}D^1_+\Phi^iD^1_-\Phi^j,
-\end{align}
-where $\Phi=(\Phi^i)_{i=1\cdots n}$ are local representatives for the $(1,1)$ {superfields} which are maps $\Phi: \Sigma^{2|2} \rightarrow M$.
+S_{(1,1)}(\Phi)=\int_{\Sigma^{1,1|2}} [g(\Phi)+b(\Phi)]_{ij}D^1_+\Phi^iD^1_-\Phi^j,
+\end{align}
+where $\Phi=(\Phi^i)_{i=1\cdots n}$ are local representatives for the $(1,1)$ {superfields} which are maps $\Phi: \Sigma^{1,1|2} \rightarrow M$.
 In the action, $b$ denotes a local two-form potential for a closed three-form, $H=\rd b$, and $D^1_\pm$ are the superderivatives
@@
 \end{align}
-where $\p_\pm=\frac{\p}{\p x_\pm}$ are derivatives along the lightcone coordinates on $\Sigma$, $x_\pm=\tau\pm\sigma$. In superworldsheet coordinates, the superfields decompose as
+where $\p_\pm=\frac{\p}{\p x_\pm}$ are derivatives with respect to the lightcone coordinates on $\Sigma$, $x_\pm= \frac{1}{\sqrt{2}} (\tau\pm\sigma)$.
+In superworldsheet coordinates, the superfields decompose as
 \begin{align}\label{fields_(1,1)}
@@
 \paragraph{Expanding the $(1,1)$ action}
-We now expand the action \eqref{eq:(1,1)action} by plugging in \eqref{fields_(1,1)} and \eqref{eq:D1}. The expansions read
+We expand the action \eqref{eq:(1,1)action} by plugging in \eqref{fields_(1,1)} and \eqref{eq:D1}. The expansions read
 %In components, the superfield has the form
@@
 \subsection{$(2,2)$ para-supersymmetry}\label{sec:(2,2)parasusy}
-We continue by extending the above $(1,1)$ picture to the $(2,2)$ para-SUSY setting. This version of supersymmetry and the corresponding sigma models were first discussed in \cite{HullTwistedSUSY}.
-
-The {\bf (2,2) para-supersymmetry algebra} has the underlying supervector space
-\[
-\mathfrak{t}_{(2,2)} = \RR^{1,1} \oplus \Pi(S_+ \oplus S_+) \oplus \Pi(S_- \oplus S_-),
-\]
-with the Lie brackets defined as follows: we choose a basis $\{Q^1_{\pm}, Q^2_\pm\}$ for $S_\pm \oplus S_\pm$ in which the nontrivial brackets read 
+By requiring that the target manifold $M$ be equipped with additional geometric structure, it is possible to enhance the symmetry by the $(1,1)$-supersymmetry algebra to a bigger supersymmetry algebra.
+We will consider the so-called $(2,2)$ para-supersymmetry algebra. 
+This version of supersymmetry and the corresponding sigma models were first discussed in \cite{HullTwistedSUSY}.
+
+As before, let $S_\pm$ be the real spin representations of ${\rm Spin}(1,1)$.
+The para (2,2) super Poincar\'{e} Lie algebra is of the form $\mathfrak{so}(1,1) \ltimes \mathfrak{t}_{(2,2)}$ where $\mathfrak{t}_{(2,2)}$ is the {\bf (2,2) para-supersymmetry algebra} which has as its underlying supervector space
+\[
+\mathfrak{t}_{(2,2)} = \RR^{1,1} \oplus \Pi(S_+ \oplus S_+) \oplus \Pi(S_- \oplus S_-) ,
+\]
+with the Lie brackets defined as follows.
+Here $\RR^{1,1}$ is the abelian Lie algebras of translations generated in light cone coordinates by the basis elements $\{\partial_{\pm}\}$.
+To write down the Lie bracket, fix a basis $\{Q^1_{\pm}, Q^2_\pm\}$ for $S_\pm \oplus S_\pm$.
+The nontrivial brackets are defined by 
 \begin{equation}\label{eq:(2,2)para}
@@
 \end{align}
-Again, this is analogous to the complex basis of the ordinary $(2,2)$ superalgebra
-\begin{align}\label{complex_(2,2)}
-[Q_\pm,\overline{Q}_\pm]=2i\p_\pm.
-\end{align}
+%Again, this is analogous to the complex basis of the ordinary $(2,2)$ superalgebra
+%\begin{align}\label{complex_(2,2)}
+%[Q_\pm,\overline{Q}_\pm]=2i\p_\pm.
+%\end{align}
 
 \begin{remark}
-
+\label{rmk: generalsusy}
 More generally, suppose $W_\pm$ are vector spaces of dimension $k_\pm$, respectively.
@@
 This is a general form of the $\cN = (k_+, k_-)$ supersymmetry algebra for which ordinary supersymmetry and para-supersymmetry are special cases.
-The case of $\mathfrak{t}_{(2,2)}$, which will be of most interested to us, corresponds to taking $k_+ = k_- = 2$ and $\eta_\pm^{11} = 1$, $\eta^{22}_\pm = - 1$, $\eta^{12}_{\pm} = 0$.
+The case of $\mathfrak{t}_{(2,2)}$, which will be of most interested to us, corresponds to taking $k_+ = k_- = 2$ and 
+\[
+\eta^{ab}=\begin{pmatrix}
+1 & 0 \\
+0 & -1
+\end{pmatrix}
+\]
+whereas ordinary $(2,2)$ supersymmetry corresponds to taking $\eta^{ab} = \delta^{ab}$.
 
@@
 \end{align}
-i.e. $M_\pm$ have to lie in $SO(1,1)$ for each subscript $\pm$ and the R-symmetry group is therefore $G_R=SO(1,1)_+\times SO(1,1)_-$.
+i.e. $M_\pm$ have to lie in $SO(1,1)$ for each subscript $\pm$. 
+Thus, we find that the R-symmetry group $G_R=SO(1,1)_+\times SO(1,1)_-$ acts on $\mathfrak{t}_{(2,2)}$.
+
 %\david{this is only relevant for the (2,2) formalism, will se if we need this or not}
@@
 
-The $\sigma$-model \eqref{eq:(1,1)action} has manifest $(1,1)$ supersymmetry.
+When $\Sigma = \RR^{1,1|2}$, the $\sigma$-model \eqref{eq:(1,1)action} has manifest $(1,1)$ supersymmetry.
 We now impose additional symmetries of the action $S_{(1,1)}$ that generate the $(2,2)$ parasupersymmetry algebra (\ref{eq:(2,2)para}) and discuss the required geometric properties of the target manifold for such extension.
@@
 \subsection{$(2,1)$ and $(2,0)$ parasupersymmetry}
-\brian{Turn this whole section into a loose discussion.}
-Many of the constructions above make sense when there is less total supersymmetry, and we briefly mention two important cases. The first concerns the $(2,1)$ parasupersymmetry algebra.
-This algebra $\mathfrak{t}_{(2,1)}$ consists of generators $\{Q^1_\pm, Q^2_+\}$ satisfying the same algebra as in (\ref{eq:(2,2)para}). 
+Many of the constructions above make sense when there is less total supersymmetry, and we briefly mention two important cases.
+The first concerns the $(2,1)$ parasupersymmetry algebra, see Remark \ref{rmk: generalsusy}.
+This algebra $\mathfrak{t}_{(2,1)}$ consists of generators $\{Q^1_\pm, Q^2_+\}$ satisfying the same relations as in (\ref{eq:(2,2)para}). 
 Starting with the $(1,1)$ supersymmetric $\sigma$-model (\ref{eq:(1,1)action}), and labeling the odd coordinates by $\theta^\pm = \theta_1^\pm$, one can ask for an additional odd symmetry 
 \[
-Q^2_+ :  \Phi \mapsto \Phi + \epsilon_2^+ K_+(\Phi)^j_i D_+ \Phi^i
-\]
-which determines a symmetry by the $(2,1)$ parasupersymmetry algebra.
-
-\begin{proposition}
-The odd vector field $Q_2^+$ is a symmetry of the $(1,1)$ supersymmetric $\sigma$-model provided $(K_+)^{j}_i$ is a paracomplex structure satisfying \brian{What conditions here?}
-Thus, the $(1,1)$ supersymmetric $\sigma$-model has $(2,1)$ parasupersymmetry provided the target is \brian{same conditions}. 
-\end{proposition}
-
-The next symmetry algebra we wish to consider is the $(2,0)$ parasupersymmetry algebra $\mathfrak{t}_{(2,0)}$. 
-This algebra has the same even generators as the $(2,1)$ and $(2,2)$ algebras, and odd generators $\{Q^1_+, Q^2_+\}$ satisfying the relations
-\[
-[Q^1_+, Q^1_+] =  2 \partial_\pm \;\;\; , \;\;\; [Q^2_+, Q^2_+] = - 2 \partial_\pm
-\]
-
-\brian{The (1,0) action}
-
-We propose an extended symmetry of the $(1,0)$ $\sigma$-model by the following action by the odd vector field $Q_+^2$:
-\[
 Q^2_+ :  \Phi \mapsto \Phi + \epsilon_2^+ K_+(\Phi)^j_i D_+ \Phi^i .
 \]
-
-\begin{proposition}
-The odd vector field $Q_2^+$ is a symmetry of the $(1,0)$ supersymmetric $\sigma$-model provided $(K_+)^{j}_i$ is a paracomplex structure. 
-Thus, the $(1,0)$ supersymmetric $\sigma$-model has $(2,0)$ parasupersymmetry provided the target is paracomplex. \brian{there is a version for a target vector bundle as well...}
-\end{proposition}
+The odd vector field $Q_2^+$ is a symmetry of the $(1,1)$ supersymmetric $\sigma$-model provided the target has the structure of a para SKT manifold, see Section \ref{SKT}. 
+Thus, the $(1,1)$ supersymmetric $\sigma$-model has $(2,1)$ parasupersymmetry provided the target has the structure of a para SKT manifold.
+
+Similarly, by forgetting part of the supersymmetry, this means that the $(1,0)$ supersymmetric $\sigma$-model has $(2,0)$ parasupersymmetry provided the target is a para SKT manifold.
 

### 2020-01-29 newdraft.tex
added the paracpx. Lie algebroid stuff

--- 2020-01-20 newdraft.tex
@@
 \newcommand{\PH}{(\PS,\eta,\omega)}
-\newcommand{\Lt}{\tl{L}}
+\newcommand{\Lt}{{\tl{L}}}
 \newcommand{\Lb}{\mathbb{L}}
@@
 \theoremstyle{remark}
-\newtheorem{Ex}[theorem]{Example}
 \newtheorem{question}[theorem]{Question}
@@
 
+\newtheoremstyle{examples}%                % Name
+   {10pt}%                                     % Space above
+   {10pt}%                                     % Space below
+   {}%                                     % Body font
+   {}%                                     % Indent amount
+   {\bfseries}%                            % Theorem head font
+   {:}%                                    % Punctuation after theorem head
+   { }%                                    % Space after theorem head, ' ', or \newline
+   {}%                                     % Theorem head spec (can be left empty, meaning `normal')
+\theoremstyle{examples}
+\newtheorem{Ex}[theorem]{Example}
 \input xy
@@
 The holomorphic sections of $T\PS$ -- the holomorphic vector fields -- are locally of the form
-\begin{align*}
+\begin{align}\label{para-holo-vector}
 X= X^i(x)\p_i+\tl{X}_i(\xt)\pt^i,
-\end{align*}
+\end{align}
 i.e. the components in $L$ and $\Lt$ individually define vector fields on the foliations $M$ and $\Mt$, respectively.
@@
 with the inverse
-\begin{align}
+\begin{align}\label{isom_bigradings2}
 \phi^{-1}:\ \bm{\ap}\ \in\ \Omega_\Cp^{p,q}\longmapsto (\text{Re}(\bm{\alpha})+\text{Im}(\bm{\ap}),\text{Re}(\bm{\alpha})-\text{Im}(\bm{\ap}))\ \in\ \Omega^{(p,q)}\otimes \Omega^{(q,p)}.
@@
 
+\subsubsection{Lie algebroids of a para-complex manifold}\label{lie_algds_paracpx}
+Here we briefly discuss what Lie algebroids the para-complex structure on a manifold $\PS$ gives rise to.
+%First, we recall that a Lie algebroid over $\PS$ is the triple $(E,a,\brac_E)$, where $E\rightarrow \PS$ is a vector bundle, $a: E\rightarrow T\PS$ is a bundle map and $\brac$ is a bracket operation on the sheaf of sections of $E$.
+The three satisfy the following:
+%\begin{enumerate}
+%\item $a([e_1,e_2]_E)=[a(e_1),a(e_2)]$, $\brac$ being the Lie bracket on $T\PS$,
+%\item $[e_1,fe_2]_E=f[e_1,e_2]_E+a(e_1)[f]e_2$.
+%\end{enumerate}
+
+The first example is the tangent Lie algebroid
+\begin{Ex}[Tangent Lie algebroid]\label{ex:tangent_lie}
+The {\bf tangent Lie algebroid} exists on any manifold $\PS$ and is given by the data $E=T\PS$, $a=\id$ and $\brac_E=\brac$.
+\end{Ex}
+
+The following examples are of the same flavor, except we consider the subbbundle of the tangent bundle:
+\begin{Ex}[Lie algebroids of para-complex eigenbundles]\label{ex:real-lie-algds-on-paracpx}
+Let $(\PS,K)$ be a para-complex manifold with $\pm 1$ eigenbundles $L$ and $\Lt$. The following are Lie algebroids
+\begin{enumerate}
+\item $E=L$, $a=\imath_L:L\hookrightarrow T\PS$, $\brac_E=\brac\mid_L$, and
+\item $E=\Lt$, $a=\imath_\Lt:\Lt\hookrightarrow T\PS$, $\brac_E=\brac\mid_\Lt$,
+\end{enumerate}
+%\begin{itemize}
+%\item $E=TM\rightarrow M$, $a=\id_{TM}$, $\brac_E=\brac_M$, and
+%\item $E=T\Mt\rightarrow \Mt$, $a=\id_{T\Mt}$, $\brac_E=\brac_\Mt$,
+%\end{itemize}
+where $\imath_{L/\Lt}$ are the inclusion maps and $\brac\mid_{L/\Lt}$ are the restrictions of the Lie bracket to $L$ and $\Lt$.
+The above are Lie algebroids in particular because $K$ is integrable so that $[L,L]\subset L$ and $[\Lt,\Lt]\subset \Lt$.
+Moreover, the two above Lie algebroids are exactly the tangent Lie algebroids of the integral foliations of $L$ and $\Lt$, $M$ and $\Mt$ respectively, once we restrict the module from $C^\infty(\PS)$ to $C^\infty(M)$ and $C^\infty(\Mt)$.
+Note that the two Lie algebroids exist individually on half-integrable almost para-complex manifolds.
+
+The Chevalley-Eilenberg complexes of the two Lie algebroids are given by
+\begin{enumerate}
+\item $(\Lambda^\bullet L^*=\Lambda^{(\bullet,0)}(\PS),\p)$, and
+\item $(\Lambda^\bullet \Lt^*=\Lambda^{(0,\bullet)}(\PS),\pt)$,
+\end{enumerate}
+where $\p$ and $\pt$ are defined by \eqref{paracomplex_dels}.
+\end{Ex}
+
+If we now consider the para-complexified tangent bundle $T\PS_\Cc$, we get a para-complex Lie algebroid, which can be understood as certain sense as a {\it sum} of the two above Lie algebroids:
+\begin{Ex}[Para-holomorphic tangent bundle]\label{ex:para-hol-tangent}
+The $+k$-eigenbundle $T^{1,0}\subset T\PS_\Cc$ is a para-complex Lie algebroid with the bracket given by the extension of the usual Lie bracket to $T\PS_\Cc$ and restricted to $T^{1,0}$ and the anchor is again the inclusion $\imath:\  T^{1,0}\hookrightarrow T\PS_\Cc$.
+We can identify $T\PS_\Cc=T\oplus k T$, so that a section $X\in \XX_\Cc(\PS)$ is written as $X=U+kV=(U,V)$ for $U,V \in \XX(\PS)$ real vector fields and the Lie algebroid bracket is then given in terms of the usual Lie bracket of real vector fields as
+\begin{align*}
+[(U,V),(U',V')]=([U,U']+[V,V'],[U,V']+[V,U']).
+\end{align*}
+The Chevalley-Eilenberg complex is the para-complexified Dolbeault complex \eqref{para-dolbeault}.
+
+There is an analogous map to \eqref{isom_bigradings2} for vector fields (which we also denote $\phi^{-1}$) mapping $X \in \XX^{1,0}_\Cc(\PS)$ to a pair of vector fields
+\begin{align*}
+X=(U,V) \overset{\phi^{-1}}{\mapsto} (U+V,U-V) \in \XX^{(1,0)}(\PS)\otimes \XX^{(0,1)}(\PS),
+\end{align*}
+realizing the $\mathbb{R}$-linear isomorphism between $T^{1,0}$ and $T\PS=L\oplus \Lt$.
+This map can be used to map the para-complex Lie algebroid $T^{1,0}$ with a pair of real Lie algebroids.
+It is a simple exercise to check that $\phi^{-1}$ in fact maps to the pair of real Lie algebroids described in Example \ref{ex:real-lie-algds-on-paracpx}, so that the following diagram commutes
+\begin{equation*}
+\begin{tikzcd}
+T^{1,0} \arrow[hookrightarrow]{d}{\imath}\arrow{r}{\phi^{-1}} & L\oplus \Lt\arrow[hookrightarrow]{d}{\imath_L\oplus\imath_\Lt}\\
+TP_\Cc \arrow{r}{(\text{Re},\text{Im})} & T\oplus T
+\end{tikzcd}\ .
+\end{equation*}
+Note, however, that $L\otimes \Lt=T$ here is not a Lie algebroid (and in particular is not the tangent Lie algebroid) because the direct sum of anchors $\imath_L\oplus \imath_\Lt$ maps into $T\oplus T$ as opposed to $T$.
+
+Consequently, the Chevalley-Eilenberg complex then also splits and can be understood as a direct sum of the two complexes corresponding to $L$ and $\Lt$, as denoted in \eqref{para-dolbeault}.
+\end{Ex}
+
+\begin{remark}
+The Lie algebroid described above is again analogous to the complex Lie algebroid $T^{1,0}\subset T_{\mathbb{C}}M$ over a complex manifold $(M,I)$.
+The crucial difference is that because $I$ does not give rise to a splitting of the real bundle $TM$, there is no correspondence to a pair of real Lie algebroids as in the para-complex case.
+\end{remark}
+
 \subsubsection{Para-Hermitian Geometry}
@@
 
-There are many different ways to define what a Calabi-Yau manifold is, but for the purpose of our discussion we will call a Calabi-Yau manifold a K\"ahler manifold $(M,g,I)$ with the holonomy group of the underlying Riemannian metric to be $\text{Hol}(g)\subseteq SU(d)$, as opposed to $U(d)$, which is the case for ordinary K\"ahler manifolds.\footnote{Typically, a part of the definition of a Calabi-Yau manifold is the requirement of compactness of $M$ and sometimes, one requires that $\text{Hol}(g)$ is exactly equal to $SU(d)$.} A consequence of this property is that there exists a {\it holomorphic volume form}, i.e.
-a non-vanishing section $\Omega \in \Omega^{d,0}$ that is holomorphic, $\bar{\p}\Omega=0$ and satisfies
-\begin{align*}
-    \frac{\omega^d}{d!}=(-1)^\frac{d(d-1)}{2}\left(\frac{i}{2}\right)^d \Omega\w \bar{\Omega},
-\end{align*}
-where $\omega=gI$ is the K\"ahler form.
+We start with a recollection of Calabi-Yau manifolds.
+For more details, the reader may consult for example the book \cite{joyce2000compact}.
+There are many different ways to define what a Calabi-Yau manifold is, but for the purpose of our discussion we choose the following:
+\begin{Def}
+A Calabi-Yau manifold is a K\"ahler manifold $(M,g,I)$ of complex dimension $d$ such that the holonomy group of the underlying Riemannian metric $g$ is $\text{Hol}(g)\subseteq SU(d)$.
+\end{Def}
+Typically, a part of the definition of a Calabi-Yau manifold is the requirement of compactness of $M$ and sometimes, one requires that $\text{Hol}(g)$ is exactly equal to $SU(d)$.
+
+Remember that on any K\"ahler manifold we have $\text{Hol}(g)\subseteq U(d)$.
+A consequence of the property $\text{Hol}(g)\subseteq SU(d)\subset U(d)$ is that there exists a covariantly constant, non-vanishing section $\Omega \in \Omega^{(d,0)}(M)$ called the {\it holomorphic volume form}.
+On $\mathbb{C}^d$, the structures $(g,\omega,\Omega)$ take in the canonical holomorphic coordinates the form:
+\begin{align*}
+    g=\sum_{i=1}^d dz^i\otimes d\bar{z}^i,\quad \omega=\dfrac{i}{2}\sum_{i=1}^d dz^i\w d\bar{z}^i,
+ \quad   \Omega=dz^1\w\cdots\w dz^d.
+\end{align*}
+We can describe $\Omega$ in coordinate-independent way as follows:
+\begin{lemma}\label{lem:CY}
+Let $(M,g,I)$ be a Calabi-Yau manifold of complex dimension $d$ and $\omega=gI$ the fundamental form.
+There exists a nowhere vanishing section $\Omega \in \Omega^{(d,0)}(M)$ that is holomorphic, $\bar{\p}\Omega=0$ and satisfies
+\begin{align*}
+    \frac{\omega^d}{d!}=(-1)^\frac{d(d-1)}{2}\left(\frac{i}{2}\right)^d \Omega\w \bar{\Omega}.
+\end{align*}
+\end{lemma}
 
@@
 
-Let us now investigate what is the structure on para-Calabi-Yau analogous to the holomorphic volume form.
-We choose the local adapted coordinates $(x^i,\xt_j)$ in which $\eta$ and $\omega$ have the canonical form
-\begin{align*}
-    \eta=dx^i\otimes d\xt_i+d\xt_i\otimes dx^i,\quad \omega=dx^i\w d\xt_i.
-\end{align*}
-Because the holonomy of $\eta$ is now contained in $SL(d)$, there is also a covariantly constant tensor $\hat{\Omega}$
+Let us now investigate what is the structure on para-Calabi-Yau analogous to the holomorphic volume form. Consider the canonical para-K\"ahler structure on $\RR^{2d}$
+\begin{align*}
+    \eta=dx^i\otimes d\xt_i+d\xt_i\otimes dx^i,\quad \omega=dx^i\w d\xt_i,
+\end{align*}
+which is preserved by $GL(d)$. Introducing the following constant tensor
 \begin{align*}
@@
 \end{align*}
-which satisfies $\pt\Omega=\p\tl{\Omega}=0$ as well as
+we see that the triple $(\eta,\omega,\hat{\Omega})$ is preserved exactly by $SL(d)$ and $\hat{\Omega}$ satisfies
 \begin{align*}
@@
 \end{align*}
-
-We call $\hat{\Omega}=(\Omega,\tl{\Omega})$ a {\bf para-holomorphic volume form}.
+Therefore, we have the analogue of Lemma \ref{lem:CY}:
+\begin{lemma}
+Let $(\PS,\eta,K)$ be a para-Calabi-Yau manifold of dimension $2d$ and $\omega=\eta K$ the fundamental form.
+There exists a nowhere vanishing section $\hat{\Omega}=(\Omega,\tl{\Omega}) \in\Omega^{(d,0)+(0,d)}(\PS)$ that is para-holomorphic, $\pt\Omega=\p\tl{\Omega}=0$ and satisfies
+\begin{align*}
+   \frac{\omega^d}{d!}=(-1)^\frac{d(d-1)}{2} \Omega\w \tl{\Omega}. 
+\end{align*}
+\end{lemma}
+\begin{proof}
+The proof is exactly analogous to the complex case, see for example \cite[Lemma~4.4]{Joyce:2001xt}.
+\end{proof}
+
 Remember that on a para-complex manifold $\PS$ of dimension $2n$, the appropriate analogue of the holomorphic forms are the para-holomorphic forms, given by pairs $(\alpha,\tl{\alpha})\in\Omega^{(k,0)+(0,k)}(\PS)$ (here the bigrading is with respect to the para-complex structure), satisfying $\pt\ap=\p\tl{\ap}=0$.
@@
 To equip the dg manifold $(N, \mathbf{\Omega}^{0,\bullet})$ with an orientation, one must fix additional data. 
-One way to do this is to assume that the para-complex manifold $N$ is equipped with a para-holomorphic volume form $\Omega_N$.
-\brian{Relate to Lie algebroid description.}
+One way to do this is to assume that the para-complex manifold $N$ is equipped with a para-holomorphic volume form $\hat{\Omega_N}$.
+
+The Lie algebroid whose Chevalley-Eilenberg complex is the para-complex Dolbeault complex is the para-complex Lie algebroid on the para-Holomorphic tangent bundle $T^{0,1}$ described in Example \ref{ex:para-hol-tangent}.
+%The differential on the
 \end{Ex}
@@
 
-\paragraph{The para-complex point of view} We start with the discussion of the para-Calabi-Yau geometry on the side of $M$ and then contrast it with the Calabi-Yau geometry of $M$.
+\paragraph{The para-complex point of view} We start with the discussion of the para-Calabi-Yau geometry on the side of $M$ and then contrast it with the usual Calabi-Yau geometry of $M$.
 Consider an affine manifold $B$ and take a neighbourhood $U\subset B$ with local coordinates $u^i$.
@@
 \end{align*}
-This implies that the natural fiber coordinates of $TM$, $v^i=du^i$,  transform as $u^i\mapsto A^i_{\ j}u^j$, so that the combinations $(x^i=u^i+v^i,\xt^j=u^k-v^k)$ transform by
+This implies that the natural fiber coordinates of $TM$, $v^i=du^i$,  transform as $v^i\mapsto A^i_{\ j}v^j$, so that the combinations $(x^i=u^i+v^i,\xt^j=u^k-v^k)$ transform by
 \begin{align*}
@@
 
-We now endow $M$ with a para-Calabi-Yau structure defined by the fundamental form $\omega$ and a para-Holomorphic volume form $\Omega$:
+We now endow $M$ with a para-Calabi-Yau structure defined by the fundamental form $\omega$ and a para-Holomorphic volume form $\hat{\Omega}$:
 \begin{align*}
     \omega&=\omega_{ij}\ dx^i\w d \xt^j=2\omega_{ij}\ du^i\w dv^j,\\
-    \hat{\Omega} &=dx^1\w\cdots\w dx^n+d\xt^1\w\cdots\w d\xt^n=\Omega+\tl{\Omega}.
+    \hat{\Omega} &=\frac{1}{2} (dx^1\w\cdots\w dx^n+d\xt^1\w\cdots\w d\xt^n)=\Omega+\tl{\Omega}.
 \end{align*}
@@
 \paragraph{Legendre transform and the mirror map}
-Consider new coordinates $\uh_i$ on $U$ given by
+So far we described the geometry on the side of $TB$. Now, we will describe the corresponding mirror geometry on $T^*B$. We start by considering new coordinates $\uh_i$ on $U\subset B$ given by
 \begin{align*}
@@
 \end{align*}
-This ensures that also $\psi$ satisfies the Monge-Ampere equation, but with an inverse constant
+This ensures that $\psi$ also satisfies the Monge-Ampere equation, but with an inverse constant
 \begin{align}\label{dual-monge-ampere}
@@
 We continue by discussing the cotangent bundle $\Mt=T^*B$.
-The metric $\eta$ on $M=TB$ defines a negative-definite metric $-2\omega_{ij}dv^i\otimes dv^j$ on each fiber, which can be inverted to give a negative-definite metric on fibres of $T^*B$ and consequently on the whole $\Mt$:
+The metric $\eta$ on $M=TB$ defines a negative-definite metric $-2\omega_{ij}dv^i\otimes dv^j$ on each fiber, which can be inverted to give a negative-definite metric on fibres of $T^*B$ so that there is a metric on $\Mt$:
 \begin{align*}
@@
 \end{align*}
-denoting the fibre coordinates dual to $v^i=dx^i$ by $\vh_i=\frac{\p}{\p u^i}$. Using the canonical symplectic form on $T^*B$,
+where we denoted the fibre coordinates dual to $v^i=du^i$ by $\vh_i=\frac{\p}{\p u^i}$. Using the canonical symplectic form on $T^*B$,
 \begin{align*}
@@
 Moreover, we get a relationship between the moduli of symplectic structures on $M$ and para-complex structures on $\Mt$, since varying the symplectic structure on $M$ corresponds to a change of $\phi$, which also changes $\psi$ as well as the coordinates $\uh_i$.
-This in turn changes the para-complex structure $\hat{K}$ defined by its adapted coordinates, and in particular depends on $\uh_i$.
+This in turn changes the para-complex structure $\hat{K}$ defined by its adapted coordinates, and in particular depending on $\uh_i$.
 

### 2020-01-31 newdraft.tex
changes in section 2 and 3
mainly added para-complexified versions of things, went through around 1/2 of sec. 3

@@
 
-\subsubsection{Para-Complexified Version}
+\subsubsection{Para-complexified picture}
 In order to make the analogy between complex and para-complex geometry more explicit, one can \textit{paracomplexify} all objects by tensoring with the algebra $\mathbf{C}$ of \textbf{para-complex numbers}, which are given by ordered pairs $(x,y)\in \mathbb{R}\otimes (1,k)$ generated by $1$ and the symbol $k$, satisfying $k^2=1$ and called the para-complex unit.
@@
 \newcommand{\Cp}{{\mathbf{C}}}
+\subsubsection{Isomorphism between the real and para-complexified pictures}
 The isomorphism of para-complex vector spaces \eqref{para-complexification} induces an isomorphism between $\Lambda^{(p,q)}(T^*\PS)$ and $\Lambda^{p,q}(T^*\PS^\mathbf{C})$ as well as between the sections $\Omega^{(p,q)}$ and $\Omega_\Cp^{p,q}$, where the bigrading of the real bundle is with respect to the $\pm 1$ eigenvalues of $K$, while the bigrading of the para-complexified bundle is with respect to the $\pm k$ eigenvalues of $K$.
@@
 In particular, the condition of holomorphicity in the para-complex coordinates $z^i\coloneqq \frac{1+k}{2}x^i+\frac{1-k}{2}\xt^i$ and $\bar{z}^i$ is equivalent to a local independence of the coordinates $\bar{z}^i$ and is therefore entirely analogous to complex geometry.
+
+There is also an analogous map for vector (multivector) fields which we will also denote by $\phi$:
+\begin{align*}
+\phi&:\ (X,\tl{X})\ \in\ \XX^{(p,q)}\otimes \XX^{(q,p)}\longmapsto \frac{1+k}{2}X + \frac{1-k}{2}\tl{X}\ \in\ \XX_\Cp^{p,q}\\
+\phi^{-1}&:\ \bm{X}\ \in\ \XX_\Cp^{p,q}\longmapsto (\text{Re}(\bm{X})+\text{Im}(\bm{X}),\text{Re}(\bm{X})-\text{Im}(\bm{X}))\ \in\ \XX^{(p,q)}\otimes \XX^{(q,p)}.
+\end{align*}
+
+In particular, $\phi$ maps between two copies of $\TT$ and $\TT_\Cc$
+
 %\begin{lemma}
@@
 Here we briefly discuss what Lie algebroids the para-complex structure on a manifold $\PS$ gives rise to.
-%First, we recall that a Lie algebroid over $\PS$ is the triple $(E,a,\brac_E)$, where $E\rightarrow \PS$ is a vector bundle, $a: E\rightarrow T\PS$ is a bundle map and $\brac$ is a bracket operation on the sheaf of sections of $E$.
+First, we recall that a Lie algebroid over $\PS$ is the triple $(E,a,\brac_E)$, where $E\rightarrow \PS$ is a vector bundle, $a: E\rightarrow T\PS$ is a bundle map and $\brac$ is a bracket operation on the sheaf of sections of $E$.
 The three satisfy the following:
-%\begin{enumerate}
-%\item $a([e_1,e_2]_E)=[a(e_1),a(e_2)]$, $\brac$ being the Lie bracket on $T\PS$,
-%\item $[e_1,fe_2]_E=f[e_1,e_2]_E+a(e_1)[f]e_2$.
-%\end{enumerate}
+\begin{enumerate}
+\item $a([e_1,e_2]_E)=[a(e_1),a(e_2)]$, $\brac$ being the Lie bracket on $T\PS$,
+\item $[e_1,fe_2]_E=f[e_1,e_2]_E+a(e_1)[f]e_2$.
+\end{enumerate}
 
@@
 \begin{Ex}[Para-holomorphic tangent bundle]\label{ex:para-hol-tangent}
-The $+k$-eigenbundle $T^{1,0}\subset T\PS_\Cc$ is a para-complex Lie algebroid with the bracket given by the extension of the usual Lie bracket to $T\PS_\Cc$ and restricted to $T^{1,0}$ and the anchor is again the inclusion $\imath:\  T^{1,0}\hookrightarrow T\PS_\Cc$.
+The $-k$-eigenbundle $T^{0,1}\subset T\PS_\Cc$ is a para-complex Lie algebroid with the bracket given by the extension of the usual Lie bracket to $T\PS_\Cc$ and restricted to $T^{0,1}$ and the anchor is again the inclusion $\imath:\  T^{0,1}\hookrightarrow T\PS_\Cc$.
 We can identify $T\PS_\Cc=T\oplus k T$, so that a section $X\in \XX_\Cc(\PS)$ is written as $X=U+kV=(U,V)$ for $U,V \in \XX(\PS)$ real vector fields and the Lie algebroid bracket is then given in terms of the usual Lie bracket of real vector fields as
@@
 
-There is an analogous map to \eqref{isom_bigradings2} for vector fields (which we also denote $\phi^{-1}$) mapping $X \in \XX^{1,0}_\Cc(\PS)$ to a pair of vector fields
-\begin{align*}
-X=(U,V) \overset{\phi^{-1}}{\mapsto} (U+V,U-V) \in \XX^{(1,0)}(\PS)\otimes \XX^{(0,1)}(\PS),
-\end{align*}
-realizing the $\mathbb{R}$-linear isomorphism between $T^{1,0}$ and $T\PS=L\oplus \Lt$.
-This map can be used to map the para-complex Lie algebroid $T^{1,0}$ with a pair of real Lie algebroids.
-It is a simple exercise to check that $\phi^{-1}$ in fact maps to the pair of real Lie algebroids described in Example \ref{ex:real-lie-algds-on-paracpx}, so that the following diagram commutes
+There is an analogous map to \eqref{isom_bigradings2} for vector fields (which we also denote $\phi^{-1}$) mapping $X \in \XX^{0,1}_\Cc(\PS)$ to a pair of vector fields
+\begin{align*}
+X=(U,V) \overset{\phi^{-1}}{\mapsto} (U-V,U+V) \in \XX^{(1,0)}(\PS)\otimes \XX^{(0,1)}(\PS),
+\end{align*}
+realizing the $\mathbb{R}$-linear isomorphism between $T^{0,1}$ and $T\PS=L\oplus \Lt$.
+This map can be used to map the para-complex Lie algebroid $T^{0,1}$ to a pair of real Lie algebroids.
+It is a simple exercise to check that $\phi^{-1}$ in fact maps to the pair of real Lie algebroids $(L,\Lt)$ described in Example \ref{ex:real-lie-algds-on-paracpx}, so that the following diagram commutes
 \begin{equation*}
@@
 \end{equation*}
-Note, however, that $L\otimes \Lt=T$ here is not a Lie algebroid (and in particular is not the tangent Lie algebroid) because the direct sum of anchors $\imath_L\oplus \imath_\Lt$ maps into $T\oplus T$ as opposed to $T$.
-
-Consequently, the Chevalley-Eilenberg complex then also splits and can be understood as a direct sum of the two complexes corresponding to $L$ and $\Lt$, as denoted in \eqref{para-dolbeault}.
+Note, however, that $L\otimes \Lt=T$ here is not a Lie algebroid (and in particular not the tangent Lie algebroid) because the direct sum of anchors $\imath_L\oplus \imath_\Lt$ maps into $T\oplus T$ as opposed to $T$.
+
+Consequently, the Chevalley-Eilenberg complex also splits and can be understood as a direct sum of the two complexes corresponding to $L$ and $\Lt$, as denoted in \eqref{para-dolbeault}.
 \end{Ex}
@@
 
+\paragraph{Para-Complexified version}
+One can also carry out all the above discussion in the setting of the para-complexified generalized tangent bundle $(\TT)\otimes_\RR \Cp$.
+In particular, one gets a one-to-one correspondence of GpC structures with {\it paracomplex} Dirac structures:
+\begin{proposition}\label{prop: pcomplexified}
+A generalized paracomplex structure is equivalent to a paracomplex Dirac structure $L \subset (\TT)\otimes_\mathbb{R} \mathbf{C}$ of real index zero, i.e. $L \cap \bar{L}=0$.
+\end{proposition}
+\begin{proof}
+The proof is entirely analogous to []; if $\KK$ is a generalized paracomplex structure and $L_\KK$ is its $+k$ eigenbundle, $L_\KK$ is automatically maximally isotropic by 
+\begin{align*}
+\langle x,y \rangle = -\langle\KK x,\KK y \rangle = -\langle k x,k y \rangle = -\langle x,y\rangle=0.
+\end{align*}
+The para-complex conjugate $\bar{L}_\KK$ is then a $-k$ eigenbundle and $L\cap\bar{L}=0$.
+Conversely, given $L$ and $\bar{L}$, we can define $\KK$ to be the multiplication by $+k$ on $L$ and $-k$ on $\bar{L}$.
+\end{proof}
+
+Let us now present the main examples, examining both the real and para-complex aspects of the generalized para-complex structures.
+
 \begin{Ex}[The trivial structure and its deformations]\label{ex:GpC_trivial}
@@
 \end{align*}
-that has eigenbundles $T$ and $T^*$ and is always integrable. The following two GpC structures can be seen as deformations of $\KK_0$ by either a two-form $b$ or a bi-vector $\beta$:
+that has the real $\pm 1$-eigenbundles $T$ and $T^*$ and is always integrable. The para-complexified $+k$-eigenbundle is given by
+\begin{align*}
+L_{\KK_0,\Cc}=\left\{\frac{1+k}{2}X+\frac{1-k}{2}\ap\mid X\in\XX(\PS),\ \ap \in \Omega(\PS)\right\}.
+\end{align*}
+
+ The following two GpC structures can be seen as deformations of $\KK_0$ by either a two-form $b$ or a bi-vector $\beta$:
 \begin{align*}
@@
 \end{align*} 
-$\KK_b$ is integrable iff $\rd b =-H$, and its eigenbundles are $L_{b} = \text{graph}(b)=\{X+b(X)\mid X \in \XX\}$ and $\widetilde{L}_b =T^*$.
-Similarly, $\KK_\beta$ is integrable iff $\beta$ is a Poisson structure, (see \cite[Lemma~2.13]{Hu:2019zro}) and its eigenbundles are $L_\beta =T$ and $\widetilde{L}_\beta =\text{graph}(-\beta)=\{\ap-\beta(\ap)\}\mid \ap \in \Omega\}$.
-The Lie algebroid $\Tilde{L}_{\beta}$ is equivalent to the Lie algebroid with underlying bundle $T^*$ and anchor given by the Poisson bivector $\beta : T^* \to T$. 
+$\KK_b$ is integrable iff $\rd b =-H$, and its eigenbundles are $L_{\KK_b} = \text{graph}(b)=\{X+b(X)\mid X \in \XX\}$ and $\widetilde{L}_{\KK_b} =T^*$.
+Similarly, $\KK_\beta$ is integrable iff $\beta$ is a Poisson structure, (see \cite[Lemma~2.13]{Hu:2019zro}) and its eigenbundles are $L_{\KK_\beta} =T$ and $\widetilde{L}_{\KK_\beta} =\text{graph}(-\beta)=\{\ap-\beta(\ap)\mid \ap \in \Omega\}$.
+The Lie algebroid given by $\widetilde{L}_{\beta}$ is equivalent to the Poisson Lie algebroid, i.e.
+it can be understood as a Lie algebroid with the underlying bundle $T^*$ and the anchor given by the Poisson bivector $\beta : T^* \to T$.
+
+The para-complexified GpC structure $\KK_{b,\Cc}$ has the $+k$-eigenbundle
+\begin{align*}
+L_{\KK_b,\Cc}=\left\{\frac{1+k}{2}(X+b(X))+\frac{1-k}{2}\ap\mid X\in\XX(\PS),\ \ap \in \Omega(\PS)\right\},
+\end{align*}
+and similarly $\KK_{\bt,\Cc}$ has the $+k$-eigenbundle
+\begin{align*}
+L_{\KK_\bt,\Cc}=\left\{\frac{1+k}{2}X+\frac{1-k}{2}(\ap-\bt(\ap))\mid X\in\XX(\PS),\ \ap \in \Omega(\PS)\right\}.
+\end{align*}
 \end{Ex}
 
-\begin{Ex}[Para-complex structures]\label{eg: pc}
+\begin{Ex}[Para-complex structures]\label{ex: pc}
 An almost para-complex structure $K\in \Endo(T)$, defines the diagonal generalized almost para-complex structure:
@@
 Thus a para-complex structure defines a generalized para-complex structure of the above form. 
-The corresponding Dirac structures are given by the $+1$ eigenbundle $L_K =T^{(1,0)}\oplus T^{*(0,1)}$ and $-1$ eigenbundle $\widetilde{L}_K =T^{(0,1)}\oplus T^{*(1,0)}$, where the bigrading is with respect to $K$.
+The corresponding Dirac structures are given by the $+1$ eigenbundle $L_{\KK_K}=T^{(1,0)}\oplus T^{*(0,1)}$ and $-1$ eigenbundle $\widetilde{L}_{\KK_K} =T^{(0,1)}\oplus T^{*(1,0)}$, where the bigrading is with respect to $K$.
+The $+k$-eigenbundle of the para-complexified GpC structure is $L_{\KK_K}=T^{1,0}\oplus T^{*0,1}$, where the bigrading is now the para-complex one.
 %
@@
 Thus, if $\omega$ is symplectic then $\KK_\omega$ is a generalized para-complex structure.
-The $\pm 1$ eigenbundles are given by $\text{graph}(\pm\omega)=\{X\pm\omega(X)\mid X\in \XX\}$.
+The $\pm 1$ eigenbundles are given by $\text{graph}(\pm\omega)=\{X\pm\omega(X)\mid X\in \XX\}$ and the $+k$-eigenbundle is given by $\text{graph}(+k\omega)$.
 \end{Ex}
 
-\paragraph{Comparision with generalized complex structures}
-Example \ref{ex:GpC_sympl} shows that a symplectic manifold $(M,\omega)$ is a GpC manifold and it is well-known \cite{Gualtieri:2003dx} that $(M,\omega)$ is also generalized complex (GC).
-However, while almost GC structures exist only on almost complex manifolds \cite{Gualtieri:2003dx}, Example \ref{ex:GpC_trivial} demonstrates that GpC structures exist on any Poisson manifold and in particular on any smooth manifold (with trivial Poisson structure).
+\paragraph{Comparision with generalized complex geometry}
+We see that two of the main examples given by the symplectic (Example \ref{ex:GpC_sympl}) and para-complex (Example \ref{ex: pc}) structures are in the para-complexified form directly analogous to the symplectic and complex examples of generalized complex (GC) structures \cite{Gualtieri:2003dx}.
+However, we can also again see the distinguishing feature of para-complex geometry ensuring that the para-complex Dirac structure always corresponds to the pair of real Dirac structures and the correspondence is given by the isomorphism $\phi$ described in Section \ref{sec:isomorphism}.
+
+Furthermore, while almost GC structures exist only on almost complex manifolds \cite{Gualtieri:2003dx}, Example \ref{ex:GpC_trivial} demonstrates that GpC structures exist on any Poisson manifold and in particular on any smooth manifold (with trivial Poisson structure).
 Another feature of GpC geometry that is not present in GC geometry is that the GpC structures can be half-integrable (similarly to ordinary para-complex structures): see the cases of $\KK_b$ and $\KK_\beta$ from Example \ref{ex:GpC_trivial} which are always at least half integrable and are fully integrable iff $b$ is closed and $\beta$ is Poisson, respectively.
 On the other hand, $\KK_\omega$ in Example \ref{ex:GpC_sympl} can only be half-integrable when the $H$-flux is non-zero.
-
-\paragraph{Para-Complexified version}
-One can also carry out all the above discussion in the setting of the para-complexified generalized tangent bundle $(\TT)\otimes_\RR \Cp$.
-In particular, one gets a one-to-one correspondence of GpC structures with {\it paracomplex} Dirac structures:
-\begin{proposition}\label{prop: pcomplexified}
-A generalized paracomplex structure is equivalent to a paracomplex Dirac structure $L \subset (\TT)\otimes_\mathbb{R} \mathbf{C}$ of real index zero, i.e. $L \cap \bar{L}=0$.
-\end{proposition}
-\begin{proof}
-The proof is entirely analogous to []; if $\KK$ is a generalized paracomplex structure and $L_\KK$ is its $+k$ eigenbundle, $L_\KK$ is automatically maximally isotropic by 
-\begin{align*}
-\langle x,y \rangle = -\langle\KK x,\KK y \rangle = -\langle k x,k y \rangle = -\langle x,y\rangle=0.
-\end{align*}
-The para-complex conjugate $\bar{L}_\KK$ is then a $-k$ eigenbundle and $L\cap\bar{L}=0$.
-Conversely, given $L$ and $\bar{L}$, we can define $\KK$ to be the multiplication by $+k$ on $L$ and $-k$ on $\bar{L}$.
-\end{proof}
 
@@
 In this section we will see how to associate a class of $2D$ topological field theories to generalized para-complex structures.
-The construction closely follows the relationship between ordinary (non-para) generalized complex structures \cite{Gualtieri:2003dx} and $2D$ topological field theories developed in \cite{Cattaneo:2009zx, Pestun:2006rj}.
-For another class of $2D$ boundary theories to the $3D$ Courant algebroid $\sigma$-model see \cite{SeveraTduality}. \btd{Please add any more references you think fit.}
-
-For us, the prescription of defining the $2D$ topological theory associated to a generalized para-complex structure starts with a $3D$ topological field theory which is defined for any manifold $M$. 
+The construction follows the philosophy of \cite{Pestun:2006rj}, where $2D$ topological theories are constucted purely from the data of a generalized complex structures \cite{Gualtieri:2003dx}.
+Rather than constructing the theory from the Lie bi-algebroid defined by the generalized structure, we simply recover the $2D$ theory as a boundary theory of the (trivial) $3D$ topological model of the underlying exact Courant algebroid, defined by a Dirac structure.
+In this sense, our construction is similiar to the one presented in \cite{Cattaneo:2009zx} with the difference that we mainly focus on the para-complex aspects.
+For another class of $2D$ boundary theories to the $3D$ Courant algebroid $\sigma$-model see \cite{SeveraTduality}.
+A different approach to a construction of $2D$ theories from Dirac structures, see \cite{KSSdirac}.
+
+The prescription of defining the $2D$ topological theory associated to a generalized para-complex structure starts with a $3D$ topological field theory which is defined for any manifold $M$. 
 More generally, this $3D$ theory can be defined for any Courant algebroid on $M$ \cite{Roytenberg:2002nu}, but for most examples we will only consider the standard exact Courant algebroid (or twisted versions) defined by the Dorfman bracket.
 The key to our construction is to realize the data of a generalized para-complex structure in terms of its eigenbundles, which are Dirac structures in the real Courant algebroid $\TT$.
-More precisely, we obtain a pair of Dirac structures $L, \Tilde{L}$ corresponding to the $\pm$ eigenbundles of the generalized para-complex structure.
+In this way, we obtain a pair of (real) Dirac structures $L, \Tilde{L}$ corresponding to the $\pm$ eigenbundles of the generalized para-complex structure.
 
@@
 One considers the para-complexification $(\TT) \otimes_{\RR} \Cc$ of the standard Courant algebroid. 
-The real Dirac structures $L, \Tilde{L}$ combine to give a para-complex Dirac structure $L \oplus \Tilde{L}$. 
+The real Dirac structures $L, \Tilde{L}$ combine to give a para-complex Dirac structure $L_\Cc$. 
 In turn, we obtain a single $2D$ TFT defined over the para-complex numbers.
+This approach more closely resembles to the one of \cite{Cattaneo:2009zx}, where this was done for generalized complex structures, from which one recovers a complex Dirac structure $L_\mathbb{C}\subset (\TT) \otimes_{\RR} \mathbb{C}$.
+The interesting property of para-complex structures which one cannot see in the complex case is that the para-complex Dirac structure $L_\Cc$ corresponds to a pair of real Dirac structures and therefore represents a certain {\it double} on the level of the $2D$ theories.
 
@@
 We recall the construction of the $3D$ topological field theory from the data of a Courant algebroid. 
-For other references, see \cite{Roytenberg:2002nu, Cattaneo:2009zx}.
+For more details, see \cite{Roytenberg:2002nu, Cattaneo:2009zx}.
 
@@
 
-We begin by setting up our model for the theory of derived manifolds. 
-For us, this is a well-behaved class of $NQ$ manifolds which are appropriate for setting up quantization of $\sigma$-models, see for instance \cite{CostelloSUSY}. 
-A dg manifold is a pair $\cN = (N, \sA^*_\cN)$ where $N$ is a smooth manifold, called the body, and $\sA^*_\cN$ a sheaf of graded commutative algebras over the de Rham complex $\Omega^*_N$.
+We begin by setting up our model for the theory of derived manifolds \david{dg manifolds?}, which is a well-behaved class of $NQ$ manifolds appropriate for setting up quantization of $\sigma$-models (see for instance \cite{CostelloSUSY}).
+A dg manifold is a pair $\cN = (N, \sA^\bullet_\cN)$ where $N$ is a smooth manifold, called the body, and $\sA^\bullet_\cN$ a sheaf of graded commutative algebras over the de Rham complex $\Omega^\bullet_N$.
 Here, $\d_\cN$ is a linear differential operator of degree $+1$, and together the data must satisfy the following conditions:
@@
 \item[(2)] For each $k$, $\sA^k_\cN$ is a locally free sheaf of $C^\infty_N$-modules of finite rank;
-\item[(3)] The differential $\d_N : \sA_\cN^* \to \sA_\cN^{*+1}$ is square zero differential operator making $(\sA_\cN , \d_\cN)$ into a sheaf of commutative dg algebras over the de Rham complex $\Omega^*_N$.
+\item[(3)] The differential $\d_N : \sA_\cN^\bullet \to \sA_\cN^{\bullet+1}$ is square zero differential operator making $(\sA_\cN , \d_\cN)$ into a sheaf of commutative dg algebras over the de Rham complex $\Omega^\bullet_N$.
 \end{itemize}
 
-In particular, as a graded algebra $\sA^*_\cN$ is given by functions on the total space of some graded vector bundle $A_\cN$ on $N$ (which is of finite rank and concentrated in finitely many degrees).
+In particular, as a graded algebra $\sA^\bullet_\cN$ is given by functions on the total space of some graded vector bundle $A_\cN$ on $N$ (which is of finite rank and concentrated in finitely many degrees).
 In the language of $NQ$ manifolds, the homological vector field defining the $Q$-structure is $\d_\cN$.
@@
 This is similar to a Courant algebroid, where the Jacobi identity only holds up to homotopy given by some closed $4$-form.
+Note that this twisting is $1$-degree higher in the $L_\infty$ hierarchy than the usual closed $3$-form \v{S}evera class of the exact Courant algebroids.
 \end{remark}
@@
 %Using this sequence, we can define the associated $NQ$ manifold $X_E$, following \cite{Ryotenberg:2002nu}.
-Let $E \to M$ be a vector bundle equipped with a fiberwise nondegenerate inner product $\left<-,-\right>$.
+Let $E \to M$ be a vector bundle equipped with a fiberwise nondegenerate inner product $\lara$.
 The body of the dg manifold is the manifold $M$, and the underlying graded manifold $X_E$ is given by $T^*M [2] \oplus E[1]$.
@@
 Suppose also that $\left<e^a, e^b\right> = g^{ab}$ and let $(g_{ab})$ be the inverse to the inner product. 
-Notice, $X_E$ comes equipped with a natural $2$-shifted symplectic form, which in coordinates is 
-\[
+Notice, $X_E$ comes equipped with a natural $2$-shifted symplectic form, which is in the above coordinates given by 
+\begin{align}
+\label{eq:omega_E}
 \omega_E = d x^i d p_i + g_{ab} d e^a d e^b .
-\]
-Denote by $\{-,-\}$ the shifted Poisson bracket corresponding to this symplectic structure. 
+\end{align}
+
+In the following, we denote the shifted Poisson bracket corresponding to this symplectic structure by $\{\ ,\ \}$. 
 An arbitrary degree $3$ function on the graded manifold $X_E$ has the form
@@
 \]
-Globally, $a = (a_a^i)$ defines a bundle map $a : E \to T$ and through the pairing the collection $(f_{abc})$ defines a bilinear map $[-,-] : E \times E \to E$. 
-It is a result of \cite{Roytenberg:2002nu} that this function satisfies $\{\Theta, \Theta\} = 0$ if and only if the data $(E, \left<-,-\right>, a, [-,-])$ has the structure of a Courant algebroid. 
-Here $a$ is the anchor map, and $[-,-]$ is the bracket.
+Globally, $a = (a_a^i)$ defines a bundle map $a : E \to T$ and through the pairing the collection $(f_{abc})$ defines a bilinear map $\brac : E \times E \to E$. 
+It is a result of \cite{Roytenberg:2002nu} that this function satisfies $\{\Theta, \Theta\} = 0$ if and only if the data $(E, \lara, a, \brac)$ has the structure of a Courant algebroid. 
+Here $a$ is the anchor map, and $\brac$ is the bracket.
 
@@
 
-The AKSZ construction endows the mapping space $\cE(N, X)$ in (\ref{eqn: map}) with a $(-1)$-shifted symplectic symplectic form as follows, compatible with the homological vector field $\d_{\cN} + Q$ as follows.
+We will now describe a $(-1)$-shifted symplectic symplectic form on the mapping space $\cE(\cN, X)$, which is compatible with the homological vector field $\d_{\cN} + Q$.
+This is called the AKSZ construction \cite{AKSZ}.
 The fundamental observation is that the diagram
@@
 \displaystyle \alpha & \times & \beta & \mapsto & \displaystyle \int_N \pi_N^* \alpha \wedge {\rm ev}^* \beta 
- \end{array}
- \]
-Applied to the element $1 \times \omega_X \in \Omega^0_N \times \Omega^{2}_X$ we obtain a $(-1)$-shifted symplectic form that we denote $\int_N \omega_X$.
+ \end{array}\ .
+ \]
+Applying this pairing to the element $1 \times \omega_X \in \Omega^0_N \times \Omega^{2}_X$ we obtain a $(-1)$-shifted symplectic form on $\cE(N, X)$ that we denote $\int_N \omega_X$.
 
 \begin{Ex}
-The most important example for us will be the source dg manifold $\cN = (N, \Omega^*_N)$, that is $\sA_\cN = \Omega^*_N$ equipped with de Rham differential. 
+The most important example for us will be the source dg manifold $\cN = (N, \Omega^\bullet_N)$, that is $\sA_\cN = \Omega^\bullet_N$ equipped with de Rham differential. 
 We denote this dg manifold by $\cN = N_{\rm dR}$.
-Take the dg manifold $(N, \Omega^*_N)$ where $N$ is any smooth manifold. 
+Take the dg manifold $(N, \Omega^\bullet_N)$ where $N$ is any smooth manifold. 
 If $N$ is closed and oriented there exists an integration map
 \[
-\int_N : \Omega^*_N \to \RR[n]
+\int_N : \Omega^\bullet_N \to \RR[n]
 \]
@@
 \begin{Ex}
-If $N$ has a para-complex structure, $(N, \mathbf{\Omega}^{0,\bullet})$ has the structure of a dg manifold. 
-Here $\mathbf{\Omega}^{0,\bullet}$ is the para-Dolbeault complex from Section \ref{sec: paracomplex} with differential given by the para $\pd$-operator. 
+If $N$ has a para-complex structure, $(N, \mathbf{\Omega}^{0,\bullet}_\Cc)$ has the structure of a dg manifold. 
+Here $\mathbf{\Omega}_\Cc^{0,\bullet}$ is the para-Dolbeault complex \eqref{para-dolbeault} with differential given by the para $\pd$-operator. 
 We will denote this dg manifold by $N_{\pd}$. 
 To equip the dg manifold $(N, \mathbf{\Omega}^{0,\bullet})$ with an orientation, one must fix additional data. 
-One way to do this is to assume that the para-complex manifold $N$ is equipped with a para-holomorphic volume form $\hat{\Omega_N}$.
-
-The Lie algebroid whose Chevalley-Eilenberg complex is the para-complex Dolbeault complex is the para-complex Lie algebroid on the para-Holomorphic tangent bundle $T^{0,1}$ described in Example \ref{ex:para-hol-tangent}.
+One way to do this is to assume that the para-complex manifold $N$ is equipped with a para-holomorphic volume form $\hat{\Omega}_N$.
+
+The Lie algebroid whose Chevalley-Eilenberg complex is the para-complex Dolbeault complex is the para-complex Lie algebroid on the anti-holomorphic tangent bundle $T^{0,1}$ described in Example \ref{ex:para-hol-tangent}.
 %The differential on the
@@
 From here on, to any Courant algebroid $E$ on a manifold $M$ we associate the dg manifold $X_E$ which carries a $2$-shifted symplectic structure. 
-In the case that the Courant algebroid is exact, call the associated $2$-shifted symplectic space $X_H$, where $H$ labels the Severa class.
+In the case that the Courant algebroid is exact, we denote the associated $2$-shifted symplectic space $X_H$, where $H$ labels the \v{S}evera class.
 
 We first review some basic examples of AKSZ theories associated to Courant algebroids. 
-The simplest type of Courant algebroid is one over a point, see Example \ref{Ex: point}. 
+The simplest type of Courant algebroid is the one over a point, described in Example \ref{Ex: point}. 
 The resulting AKSZ theory is a familiar one.
@@
 Any Lie algebra $\fg$ together with a non-degenerate invariant pairing defines a $2$-shifted symplectic structure on the graded manifold $X_E = \fg[1]$ living over a point. 
-The dg algebra of functions is the Chevalley-Eilenberg cochain complex computing Lie algebra cohomology $C^*(\fg)$. 
+The dg algebra of functions is the Chevalley-Eilenberg cochain complex computing Lie algebra cohomology $C^\bullet(\fg)$. 
 The differential is the Chevalley-Eilenberg differential.
@@
 The resulting AKSZ theory on a $3$-manifold $M$ is Chern-Simons theory on $M$. 
-Indeed, the space of graded maps $N_{dR} \to \fg[1]$ is identified as a graded vector space with $\Omega^*(N, \fg)[1]$.
+Indeed, the space of graded maps $N_{dR} \to \fg[1]$ is identified as a graded vector space with $\Omega^\bullet(N, \fg)[1]$.
 The linear part of the BRST operator encodes the de Rham differential on $M$ and the remaining piece encodes the Lie bracket on $\fg$. 
@@
 \]
+
+\david{para-complexification: only the fiber coordinates $e^a$?}
 \end{Ex}
@@
 
-The AKSZ formalism is a construction which produces a $(-1)$-shifted symplectic space from the data of a closed manifold and a target shifted symplectic manifold. 
-There is a generalization of this construction which produces $(-1)$-shifted symplectic spaces on manifolds with boundary.
-
-Suppose $N$ is a manifold with boundary, and let $\cE(N)$ denote the space of fields of a classical theory on $M$. 
-For us, $\cE(N)$ will be a mapping space of the form ${\rm Map}(M, X)$ where $X$ is shifted symplectic. 
-Let $\cE(\partial N)$ denote the restriction of the fields to the boundary of $N$. 
-For the mapping space example, this is simply the space of maps ${\rm Map}(\partial N, X)$.
+As we have seen, the AKSZ construction produces a $(-1)$-shifted symplectic space from the data of a closed manifold and a target shifted symplectic manifold. 
+We will now study a geneeralization of this construction which produces $(-1)$-shifted symplectic spaces on manifolds with boundary.
+
+Suppose $N$ is a manifold with boundary, and let $\cE(N)$ denote the space of fields of a classical theory on $N$. 
+For us, $\cE(N)$ is a mapping space of the form ${\rm Map}(N, X)$ where $X$ is shifted symplectic. 
+Let also $\cE(\partial N)$ denote the restriction of the fields to the boundary of $N$, which for the mapping space example is simply the space of maps from the boundary of $N$ to $X$, ${\rm Map}(\partial N, X)$.
 
@@
 One then forms the intersection $\cL \times_{\cE(\partial N)} \cE(N)$ of the two Lagrangians $\cL$ and $\cE(\partial N)$ inside of the phase space $\cE(\partial N)$. 
-The intersection defines the fields of the theory on $\partial N$. 
-When the bulk theory is trivial, so there are no degrees of freedom, the resulting theory on $\partial N$ is also equipped with a $(-1)$-symplectic structure. 
-For proofs of these facts about the Lagrangian intersection we refer to \cite{Calaque,PTVV}.
+The intersection then defines the fields of the theory on $\partial N$ given boundary condition $\cL$. 
+When the bulk theory is trivial, so that there are no degrees of freedom, the resulting theory on $\partial N$ is also equipped with a $(-1)$-symplectic structure. 
+For proofs of these facts about the Lagrangian intersection we refer to \cite{Calaque,PTVV}.\david{seems like we dont have these refs in the bib file, can you add them?}
+
+Coming back to the case when the shifted symplectic target is given by $X_E=T^*[2]T[1]M$ as in Example \ref{ex: exact CA}, we find that any Dirac structure defines a Lagrangian in $X_E$ with respect to $\omega_E$ \eqref{eq:omega_E}, concentrated in degrees $0$ and $1$, in which it is an isotropic subspace with respect to the metric $g_{ab}$.
 
@@
 Suppose $(M, \pi)$ is a Poisson manifold. 
-Then consider the graph of $\pi$ as a Lagrangian subbundle of $\TT$:
+Then consider the graph of $\pi$ as a Dirac structure, i.e. a Lagrangian subbundle of $(\TT)M$:
 \[
@@
 By the Jacobi identity, this subbundle is integrable and so determines a Dirac structure. 
-If we place the 3D AKSZ theory with target the Courant algebroid $\TT$ on $N^3$ with $\partial N = \Sigma$, the boundary condition determined by this Dirac structure is equivalent to the Poisson $\sigma$-model on $\Sigma$, see \cite{KSSdirac}, for instance.
+If we place the 3D AKSZ theory with target the Courant algebroid $(\TT)M$ on $N^3$ with $\partial N = \Sigma$, the boundary condition determined by this Dirac structure is equivalent to the Poisson $\sigma$-model on $\Sigma$, see \cite{KSSdirac}, for instance.
+\david{do they actually discuss this?
+I thought their construction uses the dirac structures in a slightly different way}
 \end{Ex}
@@
 Let $M$ be a manifold.
-Throughout this section we will only consider the standard Dorfman Courant algebroid $X_H$ on $M$, possibly twisted by an $H$-flux.
+Throughout this section we will only consider the standard Courant algebroid $X_H$ on $M$, possibly twisted by an $H$-flux.
 By Theorem \ref{thm:pairofdirac}, the choice of a generalized para-complex structure $\KK$ determines a pair of transversal Dirac structures $L_{\KK}$ and $\tilde{L}_{\KK}$ on $M$ given by the positive and negative eigenbundles of $\KK$.
-In particular, both $L_{\KK}, \Tilde{L}_{\KK}$determine Lagrangians in the shifted symplectic space $X_{H}$. 
-This Lagrangian then defines a pair of boundary conditions for the three-dimensional AKSZ theory.
-Thus, we see that any generalized para-complex structure $\KK$ defines a 2D TFT living at the boundary of the 3D theory. 
+In particular, both $L_{\KK}, \Tilde{L}_{\KK}$ determine Lagrangians in the shifted symplectic space $X_{H}$. Analogously, by Proposition
+\ref{prop: pcomplexified} $\KK$ also determines a para-complex Dirac structure $L_{\KK,\Cc}$ in the para-complexified Courant algebroid and consequently a Lagrangian in the corresponding shifted symplectic space $X_{H,\Cc}$.
+All three Lagrangians then define boundary conditions for the three-dimensional AKSZ theories (real and para-complex, respectively).
+Thus, we see that any generalized para-complex structure $\KK$ defines a $3$ different 2D TFTs living at the boundary of the 3D theories.
 %By Proposition \ref{prop:dirac_Liealg} the eigenbundle $L_\KK$ has the structure of a Lie algebroid compatible with the anchor and Dorfman bracket on $\TT$.
@@
 \end{align*}
-where $K$ is an ordinary para-complex structure, see Example \ref{eg: pc}.
+where $K$ is an ordinary para-complex structure, see Example \ref{ex: pc}.
 

### 2020-02-12 newdraft.tex
details of prop. 3.8

@@
 
-There is a different presentation of the $2$-symplectic manifold $X_E$ in terms of $L_{\KK}$ and $\Tilde{L}_{\KK}$ that we will use in our identification of the boundary $2D$ TFT's. 
-Consider the graded manifold $T^*[2] \Tilde{L}_{\KK} [1]$.
-In coordinates, we can parametrize this graded manifold by: $\{l^m, \Tilde{l}_n, x^i, p_j\}$ where $l^m$ parameterizes the fiber of $\Tilde{L}^*[1] \cong L [1]$ and is of degree $1$, $\Tilde{l}_n$ parametrizes the fiber of $\Tilde{L}[1]$ and is of degree $1$, and $x^i, p_j$ are as before.
-
+In \cite{Cattaneo:2009zx}, the authors show that whenever there is a  generalized (para-)complex structure $\KK$ on the Courant algebroid $(\TT)M$, there is a different presentation of the $2$-symplectic manifold $X_E$ adapted to the splitting $(\TT)M=L_{\KK}\oplus \Tilde{L}_{\KK}$ (or $(\TT)_\mathbb{C}M=L_{\KK}\oplus \overline{L}_{\KK}$ in the complex case).
+
+%  and that we will use in our identification of the boundary $2D$ TFT's. 
+%Consider the graded manifold $T^*[2] \Tilde{L}_{\KK} [1]$.
+%In coordinates, we can parametrize this graded manifold by: $\{l^m, \Tilde{l}_n, x^i, p_j\}$ where $l^m$ parameterizes the fiber of $\Tilde{L}^*[1] \cong L [1]$ and is of degree $1$, $\Tilde{l}_n$ parametrizes the fiber of $\Tilde{L}[1]$ and is of degree $1$, and $x^i, p_j$ are as before.
 \brian{define $\omega_{\KK}$ see Appendix A of \cite{Cattaneo:2009zx}. 
@@
 \[
-\left(T^*[2] \Tilde{L}, \omega_{\KK} \right) \cong X_E \cong \left(T^*[2] \overset{\;}{L}, \Tilde{\omega}_{\KK} \right) .
+\left(T^*[2] \Tilde{L}[1], \omega_{\KK} \right) \cong X_E \cong \left(T^*[2] {L}[1], \Tilde{\omega}_{\KK} \right) .
 \]
@@
 \end{proof}
+The point of the construction in \cite{Cattaneo:2009zx} is to show that the existence of a generalized (para-)complex structure impplies that there always exists the local change of coordinates to $\{l^A, \Tilde{l}_B, x^i, p'_j\}$ adapted to the generalized (para-)complex structure and that $X_E$ with the symplectic form \eqref{eq:omega_E} takes in these coordinates the form
+\begin{align*}
+\omega_E=dp'_i dx^i+d\tl{l}_Adl^A.
+\end{align*}
+The fibre coordinates $l^A$ and $\Tilde{l}_B$ are simply given by the rotations of the standard degree $1$ coordinates $e^a$ of $T^*[2]T[1]M$ via the vielbeins $F^A_a$ (lower case indices are raised/lowered by the metric $g_{ab}$, upper case indices are raised/lowered by the flat metric $\delta_{AB}$)
+\begin{align*}
+l^A\coloneqq F^A_ae^a, \quad \Tilde{l}_B\coloneqq F_{Bb}e^b,
+\end{align*}
+which are adapted to the splitting $(\TT)M=L_{\KK}\oplus \Tilde{L}_{\KK}$ in the sense that
+\begin{align*}
+\KK_a^b F^A_b=F^A_a, quad \KK_a^b F_{bB}=-F_{bB},
+\end{align*}
+and the metric $g$ takes in the new coordinates the canonical form:
+\begin{align*}
+g^A_B=\la l^A,\Tilde{l}_B\ra = \delta^A_B, \quad g^{AB}=\la l^A,l^B\ra=0=g_{AB}=\la \Tilde{l}_A,\Tilde{l}_B\ra.
+\end{align*}
+
+The coordinates $\{p'_j\}$ are then defined by the following deformation of the original coordinates $\{p_j\}$ by terms quadratic in the vielbeins
+\begin{align*}
+p'_j=p_j+ \frac{1}{2}\left((\p_j F_{aA})F^{a}_Bl^Al^B +(\p_j F_{a}^A)F^{aB}_B \Tilde{l}_A\Tilde{l}_B-F_{a}^A(\p_j F^{a}_B)\Tilde{l}_Al^B\right).
+\end{align*}
 
@@
 The $2D$ theory is given as a Lagrangian inside of this symplectic dg manifold. 
-In the coordinates granted by Proposition \ref{prop: symp} this Lagrangian takes a particularly nice form.
+In the coordinates granted by Proposition \ref{prop: symp}, this Lagrangian takes a particularly nice form.
 The Dirac structure $L_\KK$ defines the Lagrangian submanifold $L_\KK[1] \subset T^*[2] \Tilde{L}_{\KK}$. 

### 2020-03-04 newdraft.tex
Edited intro

@@
 We present several examples and show that our construction recovers the A-model and the Poisson sigma model as special cases.
-Moreover, we also introduce new examples of topological theories inherently tied to the para-complex geometry, the para-B-model and a para-complex version of the Landau-Ginzburg model.
+Moreover, we introduce new examples of topological theories inherently tied to the para-complex geometry.
 
@@
 The Courant algebroid $(\TT)\Mb$ defines a $3D$ topological theory with a $2$-shifted symplectic NQ target space $({\cal E},\Omega)$ \cite{Roytenberg:2002nu}.
-Because the $\pm 1$-eigenbundles of $\KK$ are Dirac structures in $(\TT)\Mb$, they each define a Lagrangian in $({\cal E},\Omega)$, which are $1$-shifted symplectic NQ manifolds and as such define a $2D$ topological boundary theories.
-
-Additionally, we show that when the GpC manifold $(\Mb,\KK_+)$ additionally admits a generalized para-K\"ahler structure $(\Mb,\KK_+,\KK_-)$, the topological theories for $(\Mb,\KK_+)$ described above can be realized as topological twists of the $(2,2)$ para-SUSY theory attached to $(\Mb,\KK_\pm)$.
-
-We also present several explicit examples of our construction. The well-known examples include the Poisson sigma model of a real Poisson manifold $(\Mb,\Pi)$ that is described by the GpC structure
+Because the $\pm 1$-eigenbundles of $\KK_+$ are Dirac structures in $(\TT)\Mb$, they each define a Lagrangian in $({\cal E},\Omega)$, which are $1$-shifted symplectic NQ manifolds and as such define a {\bf pair} of $2D$ topological boundary theories.
+
+A new feature of the AKSZ theories formulated on the generalized para-complex target is that the above-described pair of $2D$ topological theories can be combined into a {\bf single} $2D$ {\bf paracomplexified} theory, i.e.
+the fields become $C^\infty(\Cc)$-modules (as opposed to $C^\infty(\RR)$- or $C^\infty(\mathbb{C})$-modules in the case of real and complex theories) \david{maybe there's a better defitition of para-complexified theory?
+Maybe we wanna call it para-complex instead of para-complexified?}, where $\Cc=\RR \otimes (1,k)$ is the algebra of {\bf para-complex numbers} and $k^2=1$ is the para-complex unit.
+Conversely, we find an analogue of the construction of the $2D$ theory in the para-complexified case.
+Let $(\Mb,\KK_+)$ be the same generalized para-complex target.
+Then $(\TT)_\Cc \Mb=((\TT)\otimes_\RR \Cc) \Mb$ defines a para-complexified $3D$ AKSZ theory and the $+k$-eigenbundle of $\KK_+$ in $(\TT)_\Cc \Mb$ defines a $2D$ topological boundary condition.
+This theory then corresponds to the two real theories we described in the previous paragraph.
+
+Additionally, we show that when the GpC manifold $(\Mb,\KK_+)$ also admits a generalized para-K\"ahler structure $(\Mb,\KK_+,\KK_-)$, the topological theories for $(\Mb,\KK_+)$ described above can be realized as topological twists of the $(2,2)$ para-SUSY theory attached to $(\Mb,\KK_\pm)$.
+A similar statement holds in the para-complexified case, in which case we consider a para-complexified $(2,2)$ para-SUSY algebra and the resulting theories are para-complexified as well.
+
+We also present several explicit examples of our construction.
+The well-known examples include the Poisson sigma model of a real Poisson manifold $(\Mb,\Pi)$ that arises by considering the $-1$-eigenbundle of the GpC structure
 \begin{align*}
@@
 0 & -\id
-\end{pmatrix},
-\end{align*}
-the A-model of a symplectic manifold $(\Mb,\omega)$ described by the GpC structure
+\end{pmatrix}.
+\end{align*}
+The A-model of a symplectic manifold $(\Mb,\omega)$ is recovered by considering either of the real eigenbundles of the GpC structure
 \begin{align*}
@@
 \end{align*}
-and also the BFF theory (?) that is simply given by the trivial GpC structure
+and the BF theory \david{(?)} is simply given by the trivial GpC structure
 \begin{align*}
@@
 
-The new examples that we describe are all tied to para-complex geometry. They are the para-complex version of the B-model of a para-complex manifold $(\Mb,K)$ that is given by the GpC structure
+The new examples that we describe are all tied to the para-complex geometry of the target.
+They are the para-complex version of the B-model of a para-complex manifold $(\Mb,K)$ that is given by the para-complex $+k$-eigenbundle of the GpC structure
 \begin{align*}
@@
 \end{align*}
-and the para-complex topological Landau-Ginzburg model that can be seen as a deformation of the above geometry by a para-holomorphic poisson bi-vector $Q$
-\begin{align*}
-\KK_Q=
-\begin{pmatrix}
-K & Q \\
-0 & -K^*
-\end{pmatrix}.
-\end{align*}
+and the two real theories defined by the real eigenbundles of $\KK_K$, which can be understood as the BF theories of the foliation manifolds corresponding to the eigenbundles of $K$, which are integrable subbundles of $T\Mb$.
+
+%and the para-complex topological Landau-Ginzburg model that can be seen as a deformation of the above geometry by a para-holomorphic poisson bi-vector $Q$
+%\begin{align*}
+%\KK_Q=
+%\begin{pmatrix}
+%K & Q \\
+%0 & -K^*
+%\end{pmatrix}.
+%\end{align*}
 
@@
 0 & -I^*
-\end{pmatrix},
-\end{align*}
-as well as the topological Landau-Ginzburg model which is again viewed via the deformation of $\JJ_I$ by a holomorphic poisson bi-vector \cite{Gualtieri:2007bq} $\sigma=-\frac{1}{4}(IQ+iQ)$:
-\begin{align*}
-\JJ_Q=
-\begin{pmatrix}
-I & Q \\
-0 & -I^*
 \end{pmatrix}.
 \end{align*}
-
-Notice, however, that for example the usual Poisson sigma model cannot be obtained in the realm of GC geometry because no GC structure is defined by a real Poisson structure $\Pi$.
+%as well as the topological Landau-Ginzburg model which is again viewed via the deformation of $\JJ_I$ by a holomorphic poisson bi-vector \cite{Gualtieri:2007bq} $\sigma=-\frac{1}{4}(IQ+iQ)$:
+%\begin{align*}
+%\JJ_Q=
+%\begin{pmatrix}
+%I & Q \\
+%0 & -I^*
+%\end{pmatrix}.
+%\end{align*}
+
+Notice, however, that for example the usual Poisson sigma model cannot be obtained in the realm of GC geometry because in general, a real Poisson manifold does not admit any GC structures.
 
